### 2024-05-16 src/tex/ms.tex
copy from galactic-dtd paper

% For TeXworks
\makeatletter
\declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
\makeatother

% Define document class
\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}

\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
% \usepackage{layouts}
\usepackage{xcolor}
% \usepackage{upgreek}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{xspace}

% user-defined commands
% \newcommand{\yes}{\textcolor{green}{\checkmark}\xspace}
% \newcommand{\meh}{\textcolor{black}{$\sim$}\xspace}
% \newcommand{\no}{\textcolor{red}{$\times$}\xspace}
\newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
\newcommand{\ccappaffil}{Center for Cosmology and AstroParticle Physics, The Ohio State University, 191 W. Woodruff Ave., Columbus OH 43210, USA}
\newcommand{\aFe}{[$\alpha$/Fe]\xspace}
\newcommand{\vice}{{\tt VICE}\xspace}
% \newcommand{\hydro}{{\tt h277}\xspace}
\newcommand{\todo}[1]{{\color{red}#1}}

% Citation aliases
% \defcitealias{Johnson2021-Migration}{J21}
% \defcitealias{Leung2023-Ages}{L23}

\shorttitle{Two-Infall in VICE}
\shortauthors{Dubay et al.}
% \linespread{1.8}

\begin{document}

% Title
\title{A Two-Infall Star Formation History with Outflows and Radial Migration}

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}

\correspondingauthor{Liam O.\ Dubay}
\email{dubay.11@osu.edu}

\begin{abstract}
    Abstract.
\end{abstract}

\section{Introduction}

\section{Methods}
\label{sec:methods}

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}). We omit some parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        % Multi-zone model parameters
        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-results} & Galactocentric radius \\
        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-results} & Width of each concentric ring \\
        \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
        z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
        \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-results} & Disk lifetime \\
        n               & 8         & \ref{sec:multizone-results} & Number of stellar populations formed per ring per time-step \\
        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-results} & Maximum radius of star formation \\
        M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
        \dot M_r    & continuous    & \ref{sec:multizone-results} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
        \hline
        % DTD
        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & delay-time distribution of Type Ia supernovae \\
        t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
        N_{\rm Ia}/M_\star  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
        \hline
        % Nucleosynthetic yields
        y_{\rm O}^{\rm CC}  & 0.015     & \ref{sec:yields}  & CCSN yield of O    \\
        y_{\rm Fe}^{\rm CC} & 0.0012    & \ref{sec:yields}  & CCSN yield of Fe   \\
        y_{\rm O}^{\rm Ia}  & 0         & \ref{sec:yields}  & SN Ia yield of O       \\
        y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
        \hline
        % Star formation histories
        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the inside-out SFR \\
        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
        \tau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
        \tau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst infall rate \\
        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall infall rate \\
        \hline
        % One-zone parameters
        \tau_\star                    & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
        \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
        \tau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
    \enddata
\end{deluxetable*}
\vspace{-24pt}

\subsection{Nucleosynthetic Yields}
\label{sec:yields}

\subsection{The SN Ia Delay-Time Distribution}
\label{sec:dtd}

\subsection{The Two-Infall Star Formation History}
\label{sec:sfh}

\todo{Copied from last paper.} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
\end{equation}
% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{Chiappini1997-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}. $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and their ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
\begin{equation}
    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}.
\end{equation}
Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
We note that most previous studies which use the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2006-BimodalDTDConsequences,Matteucci2009-DTDModels,Spitoni2019-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance. We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFHs, including two-infall. We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.

\subsection{Observational Sample}
\label{sec:observational-sample}

\begin{table*}
    \centering
    \caption{Sample selection parameters and median uncertainties from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
    \label{tab:sample}
    \begin{tabular}{lll}
        \hline\hline
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range or Value} & \multicolumn{1}{c}{Notes} \\
        \hline
        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages} \\
        \hline
        $\sigma({\rm [Fe/H]})$ & $9.2\times10^{-3}$ & Median uncertainty in [Fe/H] \\
        $\sigma({\rm [O/Fe]})$ & $1.8\times10^{-2}$ & Median uncertainty in [O/Fe] \\
        $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{Leung2023-Ages} \\
        \hline
    \end{tabular}
\end{table*}

\todo{Copied from last paper.}
We compare our model results to abundance measurements from the final data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}. APOGEE used infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory in the Southern Hemisphere. After the spectra were passed through the data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP} extracted chemical abundances using the model grids and interpolation method described by \citet{Jonsson2020-APOGEE-DR16}.

We restrict our sample to red giant branch and red clump stars with high-quality spectra. Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}. This produces a final sample of \variable{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements. APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.

We use estimated ages from \citet[][hereafter \citetalias{Leung2023-Ages}]{Leung2023-Ages}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations. Importantly, the \citetalias{Leung2023-Ages} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}. We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates. We note that we use the full sample of \variable{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates. Table \ref{tab:sample} also presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.

\section{One-Zone Models}
\label{sec:onezone-results}

\section{Multi-Zone Models}
\label{sec:multizone-results}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgements}

\todo{Personal acknowledgements.}

LOD and JAJ acknowledge support from National Science Foundation grant no.\ AST-2307621. JAJ and JWJ acknowledge support from National Science Foundation grant no.\ AST-1909841.
LOD acknowledges financial support from an Ohio State University Fellowship.
JWJ acknowledges financial support from an Ohio State University Presidential Fellowship and a Carnegie Theoretical Astrophysics Center postdoctoral fellowship. \todo{Update grants and fellowships.}

Funding for the Sloan Digital Sky 
Survey IV has been provided by the 
Alfred P.\ Sloan Foundation, the U.S.\ 
Department of Energy Office of 
Science, and the Participating 
Institutions.

SDSS-IV acknowledges support and 
resources from the Center for High 
Performance Computing  at the 
University of Utah. The SDSS 
website is \url{www.sdss4.org}.

SDSS-IV is managed by the 
Astrophysical Research Consortium 
for the Participating Institutions 
of the SDSS Collaboration including 
the Brazilian Participation Group, 
the Carnegie Institution for Science, 
Carnegie Mellon University, Center for 
Astrophysics | Harvard \& 
Smithsonian, the Chilean Participation 
Group, the French Participation Group, 
Instituto de Astrof\'isica de 
Canarias, The Johns Hopkins 
University, Kavli Institute for the 
Physics and Mathematics of the 
Universe (IPMU) / University of 
Tokyo, the Korean Participation Group, 
Lawrence Berkeley National Laboratory, 
Leibniz Institut f\"ur Astrophysik 
Potsdam (AIP),  Max-Planck-Institut 
f\"ur Astronomie (MPIA Heidelberg), 
Max-Planck-Institut f\"ur 
Astrophysik (MPA Garching), 
Max-Planck-Institut f\"ur 
Extraterrestrische Physik (MPE), 
National Astronomical Observatories of 
China, New Mexico State University, 
New York University, University of 
Notre Dame, Observat\'ario 
Nacional / MCTI, The Ohio State 
University, Pennsylvania State 
University, Shanghai 
Astronomical Observatory, United 
Kingdom Participation Group, 
Universidad Nacional Aut\'onoma 
de M\'exico, University of Arizona, 
University of Colorado Boulder, 
University of Oxford, University of 
Portsmouth, University of Utah, 
University of Virginia, University 
of Washington, University of 
Wisconsin, Vanderbilt University, 
and Yale University.

This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.

% From the Center for Belonging and Social Change, https://cbsc.osu.edu/about-us/land-acknowledgement
We would like to acknowledge the land that The Ohio State University occupies is the ancestral and contemporary territory of the Shawnee, Potawatomi, Delaware, Miami, Peoria, Seneca, Wyandotte, Ojibwe and many other Indigenous peoples. Specifically, the university resides on land ceded in the 1795 Treaty of Greeneville and the forced removal of tribes through the Indian Removal Act of 1830. As a land grant institution, we want to honor the resiliency of these tribal nations and recognize the historical contexts that has and continues to affect the Indigenous peoples of this land.

\software{\vice \citep{JohnsonWeinberg2020-Starbursts}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}

\appendix

\section{Reproducibility}
\label{app:reproducibility}

\todo{Blah.}

\bibliography{bib}

\end{document}

### 2024-05-16 src/tex/ms.tex
remove showyourwork dependency
Add bibfile

@@
 
-\usepackage{showyourwork}
+% \usepackage{showyourwork}
 \usepackage{amsmath}
@@
 
-\software{\vice \citep{JohnsonWeinberg2020-Starbursts}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}
+\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}
 
@@
 
-\bibliography{bib}
+\bibliography{references}
 

### 2024-05-20 src/tex/ms.tex

@@
 Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \variable{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
+This produces a final sample of \input{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
 APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
@@
 Importantly, the \citetalias{Leung2023-Ages} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \variable{output/age_sample_size.txt}APOGEE stars with age estimates.
-We note that we use the full sample of \variable{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \input{output/age_sample_size.txt}APOGEE stars with age estimates.
+We note that we use the full sample of \input{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
 Table \ref{tab:sample} also presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.

### 2024-08-06 src/tex/ms.tex

@@
 % Citation aliases
-% \defcitealias{Johnson2021-Migration}{J21}
-% \defcitealias{Leung2023-Ages}{L23}
+\defcitealias{johnson_stellar_2021}{J21}
+\defcitealias{leung_variational_2023}{L23}
+\defcitealias{dubay_galactic_2024}{D24}
 
@@
     \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).
-We omit some parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
+We omit some parameters that are unchanged from \citetalias{johnson_stellar_2021}; see their Table 1 for details.\label{tab:multizone-parameters}}
     \tablehead{
@@
 % In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
-where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{Chiappini1997-TwoInfall,Spitoni2020-TwoInfall,Spitoni2021-TwoInfall}.
+where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{chiappini_chemical_1997,spitoni_galactic_2020,spitoni_apogee_2021}.
 $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and their ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
@@
 \end{equation}
-Following \citet{BlandHawthornGerhard2016-MilkyWayReview}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
-We note that most previous studies which use the two-infall model \citep[e.g.,][]{Chiappini1997-TwoInfall,Matteucci2006-BimodalDTDConsequences,Matteucci2009-DTDModels,Spitoni2019-TwoInfall} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
-We adopt radially-dependent outflows as in \citetalias{Johnson2021-Migration} (see their Section 2.4 for details) for all our SFHs, including two-infall.
+Following \citet{bland-hawthorn_galaxy_2016}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
+We note that most previous studies which use the two-infall model \citep[e.g.][]{chiappini_chemical_1997,matteucci_new_2006,matteucci_effect_2009,spitoni_galactic_2019} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
+We adopt radially-dependent outflows as in \citetalias{johnson_stellar_2021} (see their Section 2.4 for details) for all our SFHs, including two-infall.
 We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.
@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages} \\
+        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
         \hline
@@
         $\sigma({\rm [O/Fe]})$ & $1.8\times10^{-2}$ & Median uncertainty in [O/Fe] \\
-        $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{Leung2023-Ages} \\
+        $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{leung_variational_2023} \\
         \hline
@@
 \todo{Copied from last paper.}
-We compare our model results to abundance measurements from the final data release \citep[DR17;][]{Abdurro'uf2022-SDSSIV-DR17} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{Majewski2017-APOGEE}.
-APOGEE used infrared spectrographs \citep{Wilson2019-APOGEE-Spectrographs} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{Gunn2006-SloanTelescope} at Apache Point Observatory in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{BowenVaughan1973-DuPontTelescope} at Las Campanas Observatory in the Southern Hemisphere.
-After the spectra were passed through the data reduction pipeline \citep{Nidever2015-APOGEE-DataReduction}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{Holtzmann2015-ASPCAP,GarciaPerez2016-ASPCAP} extracted chemical abundances using the model grids and interpolation method described by \citet{Jonsson2020-APOGEE-DR16}.
+We compare our model results to abundance measurements from the final data release \citep[DR17;][]{abdurrouf_seventeenth_2022} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{majewski_apache_2017}.
+APOGEE used infrared spectrographs \citep{wilson_apache_2019} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory in the Southern Hemisphere.
+After the spectra were passed through the data reduction pipeline \citep{nidever_data_2015}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{holtzman_abundances_2015,garcia_perez_aspcap_2016} extracted chemical abundances using the model grids and interpolation method described by \citet{jonsson_apogee_2020}.
 
@@
 This produces a final sample of \input{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
-APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{Gaia2016-Mission,Gaia2021-EDR3}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
+APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
 
-We use estimated ages from \citet[][hereafter \citetalias{Leung2023-Ages}]{Leung2023-Ages}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
-Importantly, the \citetalias{Leung2023-Ages} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{Leung2023-Ages}, which produces a total sample of \input{output/age_sample_size.txt}APOGEE stars with age estimates.
+We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
+Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt}APOGEE stars with age estimates.
 We note that we use the full sample of \input{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
@@
 
-\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy2013,astropy2018,astropy2022}, scikit-learn \citep{Pedregosa2011-ScikitLearn}, SciPy \citep{2020SciPy-NMeth}, Matplotlib \citep{Hunter2007-Matplotlib}}
+\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}}
 

### 2024-08-23 src/scripts/yields.py
add yields table

@@ -1,0 +1,35 @@
+"""
+This script generates a LaTeX table of IMF-averaged nucleosynthetic yields
+adopted in this paper.
+"""
+
+import pandas as pd
+import vice
+from multizone.src.yields import W23
+import paths
+
+def main():
+    ccsn_yields = []
+    snia_yields = []
+    elements = ['O', 'Mg', 'Si', 'Fe']
+    for el in elements:
+        ccsn_yields.append('\\num{%.2e}' % vice.yields.ccsne.settings[el])
+        snia_yields.append('\\num{%.2e}' % vice.yields.sneia.settings[el])
+    df = pd.DataFrame({
+        'Element': elements,
+        '$y_X^{\\rm CC}$': ccsn_yields,
+        '$y_X^{\\rm Ia}$': snia_yields,
+    })
+    latex_table = df.to_latex(column_format='c|cc', index=False)
+    # Replace float 0s with int
+    latex_table = latex_table.replace('0.00e+00', '0')
+    # Replace \toprule, \midrule, \bottomrule with \hline
+    latex_table = latex_table.replace('\\toprule', '\\hline\\hline')
+    latex_table = latex_table.replace('\\midrule', '\\hline')
+    latex_table = latex_table.replace('\\bottomrule', '\\hline')
+    # Write to output
+    with open(paths.output / 'yields.tex', 'w') as f:
+        f.write(latex_table)
+
+if __name__ == '__main__':
+    main()

### 2024-08-23 src/tex/ms.tex

@@
 % \author[0000-0001-7775-7261]{David H. Weinberg}
+\author{coauthors}
 
@@
 \section{Introduction}
+
+The two-infall model has long been proposed to explain the high- and low-$\alpha$ sequences observed in the Milky Way disk.
 
@@
 
+\begin{table*}
+    \centering
+    \caption{Yields.}
+    \label{tab:yields}
+    \include{output/yields.tex}
+\end{table*}
+
 \subsection{The SN Ia Delay-Time Distribution}
@@
 
-\todo{Copied from last paper.} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
+\todo{Copied from last paper.} First proposed by \citet{chiappini_chemical_1997}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
 \begin{equation}
@@
 We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.
+
+The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^N$, with $N=1.5$ following \citet{kennicutt_global_1998}.
+Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a simpler prescription to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
+In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
+\begin{equation}
+    \label{eq:sf-law}
+    \tau_\star = 
+    \begin{cases}
+        \epsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
+        \epsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
+    \end{cases}
+\end{equation}
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$ with $\gamma=1/2$ and $\tau_{\rm mol,0}=2$ Gyr.
+Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\epsilon$:
+\begin{equation}
+    \label{eq:sfe-prefactor}
+    \epsilon(t) = 
+    \begin{cases}
+        0.5, & t < t_{\rm on} \\
+        1.0, & t \ge t_{\rm on}.
+    \end{cases}
+\end{equation}
+\todo{Talk about the implications of this prefactor or reference a future section which discusses this.}
 

### 2024-09-06 src/tex/ms.tex
Updates from Overleaf

@@
 
-The two-infall model has long been proposed to explain the high- and low-$\alpha$ sequences observed in the Milky Way disk.
+The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks.
+The infall history of any given region of the disk is described by two successive, exponentially declining bursts, whose timescale may vary as a function of radius.
+The first infall, which forms the thick disk, has a short timescale, typically on the order of $\sim1$ Gyr.
+The second infall forms the thin disk and has a much longer timescale, typically $\sim4-10$ Gyr.
+
+% Summary of two-infall papers
+\citet{matteucci_galactic_1989} modeled the galaxy with a two-component model, a one-zone model for the halo and concentric shell zones for the disk.
+They used a simple exponential gas infall (so not yet a two-infall model), where the infall timescale increased proportionally with radius.
+They studied cases with primordial and pre-enriched gas infall, finding that the former produces a more realistic metallicity distribution in the Solar neighborhood.
+Their inside-out disk evolution produced good agreement with observed abundance gradients.
+
+\citet{chiappini_chemical_1997} presented the first two-infall model of the MW disk.
+They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall varying with radius.
+Their model parameters were constrained by the observed
+
+% Radial gas flows
+Some two-infall studies \citep[e.g.,][]{palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
 
@@
 
-\begin{table*}
+\begin{table}
     \centering
@@
     \include{output/yields.tex}
-\end{table*}
+\end{table}
 
@@
 \label{sec:onezone-results}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_sfr.pdf}
+    \caption{Caption.}
+    \label{fig:onezone-sfr}
+\end{figure}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/onezone_params.pdf}
+    \caption{Caption.}
+    \label{fig:onezone-params}
+\end{figure*}
 

### 2024-10-04 src/tex/ms.tex
Updates from Overleaf

@@
 Some two-infall studies \citep[e.g.,][]{palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
+
+% Three-infall
+Motivated by constraints on the SFH by {\it Gaia}, \citet{spitoni_beyond_2023} proposed the three-infall model, an extension with a third phase of exponential gas infall in the last few Gyr.
+
+\citet{palla_mapping_2024} compare model predictions to abundances and ages of open clusters from the {\it Gaia}-ESO survey.
+They find that the two-infall model over-predicts the metallicity of the youngest clusters, a problem which is fixed by the three-infall model.
+A version of the three-infall model with milder dilution (mild pre-enrichment of the gas with a smaller amount of infall) compared to \citet{spitoni_beyond_2023} can simultaneously match the metalliticy of old, intermediate, and young clusters across the disk.
 

### 2024-10-17 src/scripts/age_abundance_grid.py
end of day commit

@@ -158,8 +158,9 @@ def plot_age_abundance_grid(mzs, col, apogee_sample=None, fname='',
                 plot_apogee_median_ages(ax, apogee_subset, apogee_col, abund_bins, label='L23')
     
     # Add legend to top-right panel
-    axs[0,-1].legend(loc='upper left', frameon=False, handletextpad=0.1,
-                     borderpad=0.2, handlelength=1.5)
+    if medians:
+        axs[0,-1].legend(loc='upper left', frameon=False, handletextpad=0.1,
+                         borderpad=0.2, handlelength=1.5)
                              
     # Set x-axis scale and ticks
     if log:

### 2024-10-17 src/scripts/density_gradient.py

@@ -44,7 +44,9 @@ def main(style='paper'):
     ax.plot(rbin_centers, densities, 'r-', label='Static SFR (no outflow)')
     # Gas density
     sigma_gas, radii = gas_density_gradient(name)
-    ax.plot(radii + ZONE_WIDTH, sigma_gas, 'r:', label='Gas')
+    ax.plot(radii, sigma_gas, 'r:', label='Gas')
+    sigma_mstar, radii = mstar_density_gradient(name)
+    print(sigma_mstar[:-1] / total_disk)
     
     # Static IFR mode
     name = 'nomigration/outflow/no_gasflow/J21/static_infall/diskmodel'
@@ -53,7 +55,9 @@ def main(style='paper'):
     ax.plot(rbin_centers, densities, 'g--', label='Static IFR (outflows)')
     # Gas density
     sigma_gas, radii = gas_density_gradient(name)
-    ax.plot(radii + ZONE_WIDTH, sigma_gas, 'g:', label='Gas')
+    ax.plot(radii, sigma_gas, 'g:', label='Gas')
+    sigma_mstar, radii = mstar_density_gradient(name)
+    print(sigma_mstar[:-1] / total_disk)
     
     # Static IFR mode
     name = 'nomigration/no_outflow/no_gasflow/J21/static_infall/diskmodel'
@@ -62,7 +66,9 @@ def main(style='paper'):
     ax.plot(rbin_centers, densities, 'b--', label='Static IFR (no outflow)')
     # Gas density
     sigma_gas, radii = gas_density_gradient(name)
-    ax.plot(radii + ZONE_WIDTH, sigma_gas, 'b:', label='Gas')
+    ax.plot(radii, sigma_gas, 'b:', label='Gas')
+    sigma_mstar, radii = mstar_density_gradient(name)
+    print(sigma_mstar[:-1]/ total_disk)
     
     # Inside-out
     # insideout_name = 'nomigration/outflow/no_gasflow/J21/static_fine_dr/diskmodel'
@@ -181,6 +187,33 @@ def gas_density_gradient(name, zone_width=ZONE_WIDTH):
     radii = [i * zone_width for i in range(len(gas_mass_gradient))]
     areas = [m.pi * ((r + zone_width)**2 - r**2) for r in radii]
     return np.array(gas_mass_gradient) / np.array(areas), np.array(radii)
+
+
+def mstar_density_gradient(name, zone_width=ZONE_WIDTH):
+    """
[…]

### 2024-10-17 src/scripts/multizone/src/disks.py

@@ -122,6 +122,13 @@ class diskmodel(vice.milkyway):
             from .yields import F04
         elif yields == "W23":
             from .yields import W23
+            ycco = vice.yields.ccsne.settings['o']
+            yccfe = vice.yields.ccsne.settings['fe']
+            print(ycco)
+            print(yccfe)
+            print(vice.solar_z['o'])
+            print(vice.solar_z['fe'])
+            print(m.log10((ycco / yccfe) / (vice.solar_z['o'] / vice.solar_z['fe'])))
             # Mass-loading factor calibrated to produce equilibrium abundance
             self.mass_loading = models.equilibrium_mass_loading()
         else:

### 2024-10-17 src/scripts/multizone/src/models/mass_loading.py

@@ -10,13 +10,13 @@ class equilibrium_mass_loading:
     
     Parameters
     ----------
-    alpha_h_eq : float [default: 0.0]
-        The equilibrium [alpha/H] abundance at the Solar radius in dex.
+    equilibrium : float [default: 0.0]
+        The equilibrium [O/H] abundance at the Solar radius.
     recycling : float [default: 0.4]
         The instantaneous recycling parameter.
     tau_star : float [default: 2.0]
         The star formation efficiency timescale in Gyr.
-    tau_sfh : float [default: 10.0]
+    tau_sfh : float [default: 15.0]
         The star formation history timescale in Gyr.
     gradient : float [default: -0.08]
         The radial metallicity gradient in dex/kpc.
@@ -40,10 +40,10 @@ class equilibrium_mass_loading:
         - eta : float
             The mass-loading factor at the given radius.
     """
-    def __init__(self, alpha_h_eq=0.2, recycling=0.4, tau_star=2., tau_sfh=15.,
+    def __init__(self, equilibrium=0., recycling=0.4, tau_star=2., tau_sfh=15.,
                  gradient=-0.08):
         # Calculate eta for exponential SFH to reach desired equilibrium [O/H]
-        Z_alpha_eq = vice.solar_z["o"] * 10 ** alpha_h_eq
+        Z_alpha_eq = vice.solar_z["o"] * 10 ** equilibrium
         yield_ratio = vice.yields.ccsne.settings["o"] / Z_alpha_eq
         self._eta_sun = yield_ratio - 1 + recycling + tau_star / tau_sfh
         self._scale_radius = -1 / (gradient * m.log(10))

### 2024-10-17 src/scripts/multizone/src/yields/W23.py

@@ -11,6 +11,8 @@ Fexp = 0.75
 mfecc = 0.058
 # Mean SN Ia Fe yield (Msun)
 mfeia = 0.7
+# Fraction of solar Si produced by CC SNe
+Fsicc = 0.8
 
 # solar abundances by mass
 # based on Magg et al. (2022) Table 5 + 0.04 dex to correct for diffusion
@@ -24,7 +26,7 @@ vice.solar_z["fe"] = 1.37e-3
 afecc = {
     "o": 0.45,
     "mg": 0.45,
-    "si": 0.36,
+    "si": 0.35,
     "fe": 0.
 }
 Rcc = ccsn_ratio(Fexp=Fexp) # CCSNe per unit stellar mass
@@ -35,7 +37,7 @@ for el in ["o", "mg", "si", "fe"]:
 
 # population averaged SNIa Fe yield, integrated to t=infty
 # for a constant SFR, will evolve to afeeq at late times
-afeeq = -0.1
+afeeq = 0.0
 tau_sfh = 15
 tau_Ia = 1.5
 mu = tau_sfh / (tau_sfh - tau_Ia) # assuming tau_sfh >> minimum SN Ia delay time
@@ -43,4 +45,4 @@ Ria = (Rcc / mu) * (mfecc / mfeia) * (10 ** (afecc["o"] - afeeq) - 1.)
 vice.yields.sneia.settings["fe"] = Ria * mfeia
 vice.yields.sneia.settings["o"] = 0.
 vice.yields.sneia.settings["mg"] = 0.
-vice.yields.sneia.settings["si"] = 0.
+vice.yields.sneia.settings["si"] = (1 - Fsicc) / Fsicc * vice.yields.ccsne.settings["si"]

### 2024-10-17 src/scripts/multizone/src/yields/utils.py

@@ -6,7 +6,7 @@ import vice
 
 def ccsn_ratio(Fexp=0.75, Mmin=0.08, Mmax=120, Mthresh=8, dm=0.01, 
                imf=vice.imf.kroupa):
-    """
+    r"""
     Calculate the core-collapse supernova ratio per total mass of stars.
     
     Parameters
@@ -29,7 +29,7 @@ def ccsn_ratio(Fexp=0.75, Mmin=0.08, Mmax=120, Mthresh=8, dm=0.01,
     Returns
     -------
     float
-        The core-collapse supernova ratio Rcc.
+        The core-collapse supernova ratio $R_{\rm cc}$.
     """
     # Integration masses
     masses = [m * dm + Mmin for m in range(int((Mmax + dm - Mmin) / dm))]

### 2024-10-17 src/scripts/onezone_regions.py

@@ -18,7 +18,7 @@ from apogee_sample import APOGEESample
 from _globals import END_TIME, ONEZONE_DEFAULTS, TWO_COLUMN_WIDTH, ZONE_WIDTH
 from colormaps import paultol
 from track_and_mdf import setup_axes, plot_vice_onezone
-from utils import get_bin_centers
+from utils import get_bin_centers, twoinfall_gradient
 
 ONSET = 4.2
 XLIM = (-1.4, 0.6)
@@ -30,7 +30,7 @@ def main():
     gs = fig.add_gridspec(7, 22, wspace=0.)
     subfigs = [fig.add_subfigure(gs[:,i:i+w]) for i, w in zip((0, 8, 15), (8, 7, 7))]
     # Outflow mass-loading factor
-    eta_func = models.equilibrium_mass_loading(alpha_h_eq=0.2, tau_sfh=15., tau_star=2.)
+    eta_func = models.equilibrium_mass_loading(equilibrium=0.2, tau_sfh=15., tau_star=2.)
     # eta_func = vice.milkyway.default_mass_loading
     axs0 = plot_region(subfigs[0], 4, eta=eta_func, 
                        color=paultol.highcontrast.colors[2],
@@ -80,19 +80,19 @@ def plot_region(fig, radius, dr=2., eta=models.equilibrium_mass_loading(),
     
     sz = vice.singlezone(
         name = name,
-        func = twoinfall_gradient(
-            radius, 
-            first_timescale=1., 
-            second_timescale=models.insideout.timescale(radius), 
-            onset=ONSET,
-            mass_loading=eta),
-        # func = models.insideout(radius),
+        # func = twoinfall_gradient(
+        #     radius, 
+        #     first_timescale=1., 
+        #     second_timescale=models.insideout.timescale(radius), 
+        #     onset=ONSET,
+        #     mass_loading=eta),
+        func = insideout_gradient(radius),
         mode = "ifr",
         **ONEZONE_DEFAULTS
     )
     sz.eta = eta(radius)
-    sz.tau_star = models.twoinfall_sf_law(area, onset=ONSET)
-    # sz.tau_star = models.fiducial_sf_law(area)
+    # sz.tau_star = models.twoinfall_sf_law(area, onset=ONSET)
+    sz.tau_star = models.fiducial_sf_law(area)
     sz.run(simtime, overwrite=True)
     
[…]

### 2024-10-17 src/scripts/onezone_sfe.py

@@ -18,6 +18,7 @@ from track_and_mdf import setup_figure, plot_vice_onezone
 from colormaps import paultol
 import paths
 from _globals import END_TIME, ONEZONE_DEFAULTS, ONE_COLUMN_WIDTH, ZONE_WIDTH
+from utils import twoinfall_gradient
 
 RADIUS = 8.
 XLIM = (-1.6, 0.6)
@@ -43,9 +44,9 @@ def main():
     eta_func = equilibrium_mass_loading(
         tau_star=2., 
         tau_sfh=15., 
-        alpha_h_eq=0.2
+        equilibrium=0.
     )
-    ifr = models.twoinfall(
+    ifr = twoinfall_gradient(
         RADIUS, 
         first_timescale=1.,
         second_timescale=15., 

### 2024-10-17 src/scripts/onezone_sfr.py

@@ -8,19 +8,20 @@ import matplotlib.pyplot as plt
 
 import vice
 
-# from multizone.src.yields import W23
-from multizone.src.yields import J21
+from multizone.src.yields import W23
+# from multizone.src.yields import J21
 from multizone.src.models import twoinfall, twoinfall_sf_law, equilibrium_mass_loading
+from multizone.src.dtds import exponential
 from multizone.src.models.gradient import gradient
 from track_and_mdf import setup_figure, plot_vice_onezone
 from apogee_sample import APOGEESample
 import paths
-from utils import get_bin_centers
+from utils import get_bin_centers, twoinfall_gradient
 from _globals import ONEZONE_DEFAULTS, ZONE_WIDTH
 from colormaps import paultol
 
 RADIUS = 8.
-ONSET = 4.2
+ONSET = 6
 FIRST_TIMESCALE = 1.
 SECOND_TIMESCALE = 15.
 FEH_LIM = (-1.4, 0.6)
@@ -30,6 +31,10 @@ def main():
     plt.style.use(paths.styles / "paper.mplstyle")
     plt.rcParams["axes.prop_cycle"] = plt.cycler("color", paultol.vibrant.colors)
     fig, axs = setup_figure(xlim=FEH_LIM, ylim=OFE_LIM)
+    
+    print(vice.yields.ccsne.settings['fe'])
+    print(vice.yields.ccsne.settings['o'])
+    print(vice.yields.sneia.settings['fe'])
 
     # Plot underlying APOGEE contours
     apogee_data = APOGEESample.load()
@@ -62,12 +67,12 @@ def main():
     # One-zone model parameters
     simtime = np.arange(0, 13.21, 0.01)
     area = np.pi * ((RADIUS + ZONE_WIDTH)**2 - RADIUS**2)
-    # eta_func = equilibrium_mass_loading(
-    #     tau_star=4.,
-    #     tau_sfh=SECOND_TIMESCALE, 
-    #     alpha_h_eq=0.2
-    # )
-    eta_func = vice.milkyway.default_mass_loading
+    eta_func = equilibrium_mass_loading(
+        tau_star=2.,
+        tau_sfh=SECOND_TIMESCALE, 
+        equilibrium=0.2
+    )
+    # eta_func = vice.milkyway.default_mass_loading
     ifr = twoinfall_gradient(
         RADIUS, 
         first_timescale=FIRST_TIMESCALE, 
@@ -84,6 +89,7 @@ def main():
     )
[…]

### 2024-10-17 src/scripts/utils.py

@@ -3,6 +3,7 @@ Functions used by many plotting scripts.
 """
 
 from numbers import Number
+import math as m
 
 import numpy as np
 from numpy.random import default_rng
@@ -28,10 +29,11 @@ from _globals import RANDOM_SEED, MAX_SF_RADIUS, ZONE_WIDTH
 class twoinfall_gradient(twoinfall):
     """A sub-class of the twoinfall SFH which incorporates the value of the
     stellar surface density gradient when called."""
-    def __init__(self, radius, **kwargs):
-        super().__init__(radius, **kwargs)
-        self.first.norm *= gradient(radius)
-        self.second.norm *= gradient(radius)
+    def __init__(self, radius, dr=0.1, **kwargs):
+        super().__init__(radius, dr=dr, **kwargs)
+        area = m.pi * ((radius + dr/2.)**2 - (radius - dr/2.)**2)
+        self.first.norm *= gradient(radius) * area
+        self.second.norm *= gradient(radius) * area
 
 
 def vice_to_apogee_col(col):

### 2024-10-17 src/scripts/yields.py

@@ -17,8 +17,8 @@ def main():
         snia_yields.append('\\num{%.2e}' % vice.yields.sneia.settings[el])
     df = pd.DataFrame({
         'Element': elements,
-        '$y_X^{\\rm CC}$': ccsn_yields,
-        '$y_X^{\\rm Ia}$': snia_yields,
+        '$y_{\\rm X}^{\\rm CC}$': ccsn_yields,
+        '$y_{\\rm X}^{\\rm Ia}$': snia_yields,
     })
     latex_table = df.to_latex(column_format='c|cc', index=False)
     # Replace float 0s with int

### 2024-10-29 src/scripts/enriched_infall.py
add pre-enrichment to multizone

@@ -8,13 +8,14 @@ import numpy as np
 import matplotlib.pyplot as plt
 import vice
 
-# from multizone.src.yields import W24
-from multizone.src.yields import J21
+from multizone.src.yields import W24
+# from multizone.src.yields import J21
+# from vice.yields.presets import JW20
 from multizone.src.models import twoinfall, twoinfall_sf_law, equilibrium_mass_loading
 from track_and_mdf import setup_axes, plot_vice_onezone
 from apogee_sample import APOGEESample
 import paths
-from utils import get_bin_centers, twoinfall_gradient
+from utils import get_bin_centers, twoinfall_onezone
 from _globals import ONEZONE_DEFAULTS, ZONE_WIDTH, ONE_COLUMN_WIDTH, END_TIME
 from colormaps import paultol
 
@@ -37,10 +38,10 @@ def main():
     dt = ONEZONE_DEFAULTS['dt']
     simtime = np.arange(0, END_TIME + dt, dt)
     area = np.pi * ((RADIUS + ZONE_WIDTH)**2 - RADIUS**2)
-    # eta_func = equilibrium_mass_loading()
-    eta_func = vice.milkyway.default_mass_loading
+    eta_func = equilibrium_mass_loading()
+    # eta_func = vice.milkyway.default_mass_loading
     eta = eta_func(RADIUS)
-    ifr = twoinfall_gradient(RADIUS, mass_loading=eta_func, dt=dt, 
+    ifr = twoinfall_onezone(RADIUS, mass_loading=eta_func, dt=dt, 
                     dr=ZONE_WIDTH)
     tau_star = twoinfall_sf_law(area, onset=ifr.onset)
     parent_dir = paths.onezone / 'enriched_infall'

### 2024-10-29 src/scripts/multizone/__main__.py

@@ -133,6 +133,12 @@ an inward flow (default: 0).",
         help = "Disable mass-loaded outflows.",
         action = "store_true"
     )
+    parser.add_argument("--pre-enrichment",
+        help = "The [X/H] abundance of the infalling gas at late times. \
+If -inf, infalling gas is always pristine. (Default: -inf).",
+        default = float("-inf"),
+        type = float
+    )
 
     return parser
 
@@ -146,6 +152,10 @@ def model(args):
     args : argparse.Namespace
         The command line arguments parsed via argparse.
     """
+    # Create output dir (and parents) if it doesn't exist
+    fullpath = paths.multizone / args.name
+    if not fullpath.parents[0].exists():
+        fullpath.parents[0].mkdir(parents=True)
     # Parse RIa params into dict
     RIa_kwargs = {}
     if '=' in args.RIa_params:
@@ -159,7 +169,7 @@ def model(args):
         elements = args.elements.split('_')
     )
     kwargs = dict(
-        name = str(paths.multizone / args.name),
+        name = str(fullpath),
         spec = args.evolution,
         RIa = args.RIa,
         RIa_kwargs = RIa_kwargs,
@@ -167,7 +177,8 @@ def model(args):
         # yields = args.yields,
         seed = args.seed,
         radial_gas_velocity = args.radial_gas_velocity,
-        outflows = not args.no_outflows
+        outflows = not args.no_outflows,
+        pre_enrichment = args.pre_enrichment
     )
     if args.migration == "post-process":
         kwargs["simple"] = True

### 2024-10-29 src/scripts/multizone/src/disks.py

@@ -20,7 +20,7 @@ from .migration import diskmigration, gaussian_migration, no_migration
 from . import models
 from . import dtds
 from . import yields
-from .models.utils import get_bin_number, interpolate
+from .models.utils import get_bin_number, interpolate, modified_exponential
 from .models.gradient import gradient
 import math as m
 import sys
@@ -86,6 +86,11 @@ class diskmodel(vice.milkyway):
         Random number generator seed.
     radial_gas_velocity : ``float`` [default: 0]
         Radial gas flow velocity in km/s. Positive denotes an outward gas flow.
+    pre_enrichment : ``float`` [default: -inf]
+        The [X/H] abundance of the infalling gas at late times. The infall
+        metallicity starts at 0 and increases exponentially to the specified
+        value on a 2 Gyr timescale. If -inf, infalling gas is pristine 
+        throughout the simulation.
     kwargs : varying types
         Other keyword arguments to pass ``vice.milkyway``.
 
@@ -95,7 +100,8 @@ class diskmodel(vice.milkyway):
     def __init__(self, zone_width = 0.1, name = "diskmodel", spec = "twoinfall",
                  verbose = True, migration_mode = "gaussian", #yields="J21",
                  delay = 0.04, RIa = "plateau", RIa_kwargs={}, seed=42, 
-                 radial_gas_velocity = 0., outflows=True, **kwargs):
+                 radial_gas_velocity = 0., outflows=True, 
+                 pre_enrichment=float("-inf"), **kwargs):
         super().__init__(zone_width = zone_width, name = name,
             verbose = verbose, **kwargs)
         # Set the yields
@@ -147,7 +153,7 @@ class diskmodel(vice.milkyway):
             "static_infall"
         ]:
             self.mode = "ifr"
-            for zone in self.zones: zone.Mg0 = 1e5
+            for zone in self.zones: zone.Mg0 = 0.
             # specify mass-loading factor for infall mode normalization
             evol_kwargs["mass_loading"] = self.mass_loading
         else:
@@ -176,6 +182,17 @@ class diskmodel(vice.milkyway):
                     # Simplified SF law, single power-law with cutoff
                     self.zones[i].tau_star = models.fiducial_sf_law(
                         area, mode=self.mode)
+
+        # Metallicity of infalling gas
+        if not m.isinf(pre_enrichment):
+            for i in range(self.n_zones):
+                self.zones[i].Zin = {}
+                for e in self.zones[i].elements:
[…]

### 2024-10-29 src/scripts/yields.py
update yields

@@ -5,7 +5,7 @@ adopted in this paper.
 
 import pandas as pd
 import vice
-from multizone.src.yields import W23
+from multizone.src.yields import W24
 import paths
 
 def main():

### 2024-11-04 src/scripts/multizone/src/disks.py
tweak onezone plots

@@ -104,6 +104,7 @@ class diskmodel(vice.milkyway):
                  pre_enrichment=float("-inf"), **kwargs):
         super().__init__(zone_width = zone_width, name = name,
             verbose = verbose, **kwargs)
+        print(vice.yields.ccsne.settings["fe"])
         # Set the yields
         # if yields == "JW20":
         #     from vice.yields.presets import JW20

### 2024-11-04 src/scripts/onezone_params.py

@@ -33,7 +33,7 @@ LABELS = {
     'second_timescale': '\\tau_2',
     'onset': 't_{\\rm on}'
 }
-XLIM = (-1.4, 0.8)
+XLIM = (-1.4, 0.7)
 YLIM = (-0.18, 0.54)
 
 def main():
@@ -49,12 +49,12 @@ def main():
     print('\nSecond timescale')
     axs1 = vary_param(subfigs[1], second_timescale=[3, 5, 10, 30],
                       first_timescale=1, onset=4,
-                      xlim=XLIM, ylim=YLIM, ylabel=False,
+                      xlim=XLIM, ylim=YLIM, ylabel='',
                       label_index=1, verbose=True)
     print('\nOnset time')
     axs2 = vary_param(subfigs[2], onset=[1, 2, 3, 4, 5],
                       first_timescale=1, second_timescale=10,
-                      xlim=XLIM, ylim=YLIM, ylabel=False,
+                      xlim=XLIM, ylim=YLIM, ylabel='',
                       label_index=2, verbose=True)
     plt.subplots_adjust(bottom=0.13, top=0.98, left=0.16, right=0.98, wspace=0.5)
     fig.savefig(paths.figures / 'onezone_params', dpi=300)
@@ -101,7 +101,7 @@ def vary_param(subfig, first_timescale=0.1, second_timescale=3, onset=3,
         raise ValueError('Please specify one variable parameter.')
     multiline_title = '$\\tau_2=%s$ Gyr,' % second_timescale + '\n' + \
         '$t_{\\rm on}=%s$ Gyr' % onset
-    axs = setup_axes(subfig, title='', xname='[O/H]', **kwargs)
+    axs = setup_axes(subfig, title='', xlabel='[Fe/H]', **kwargs)
 
     dt = ONEZONE_DEFAULTS['dt']
     simtime = np.arange(0, END_TIME + dt, dt)
@@ -110,12 +110,12 @@ def vary_param(subfig, first_timescale=0.1, second_timescale=3, onset=3,
     for i, val in enumerate(values):
         param_dict[var] = val
         # Outflow mass-loading factor
-        # eta_func = models.equilibrium_mass_loading(
-        #     equilibrium=0.2, 
-        #     tau_sfh=param_dict['second_timescale'], 
-        #     tau_star=2.
-        # )
-        eta_func = vice.milkyway.default_mass_loading
+        eta_func = models.equilibrium_mass_loading(
[…]

### 2024-11-04 src/scripts/onezone_regions.py

@@ -28,7 +28,7 @@ XLIM = (-1.4, 0.6)
 YLIM = (-0.12, 0.48)
 
 def main():
-    plt.style.use(paths.styles / "paper.mplstyle")
+    plt.style.use(paths.styles / 'paper.mplstyle')
     fig = plt.figure(figsize=(TWO_COLUMN_WIDTH, 0.36*TWO_COLUMN_WIDTH))
     gs = fig.add_gridspec(7, 22, wspace=0.)
     subfigs = [fig.add_subfigure(gs[:,i:i+w]) for i, w in zip((0, 8, 15), (8, 7, 7))]
@@ -40,42 +40,42 @@ def main():
                        xlim=XLIM, ylim=YLIM, dr=ZONE_WIDTH)
     axs1 = plot_region(subfigs[1], 8, eta=eta_func,
                        color=paultol.highcontrast.colors[1],
-                       xlim=XLIM, ylim=YLIM, ylabel=False, dr=ZONE_WIDTH)
+                       xlim=XLIM, ylim=YLIM, ylabel='', dr=ZONE_WIDTH)
     axs2 = plot_region(subfigs[2], 10, eta=eta_func,
                        color=paultol.highcontrast.colors[0],
-                       xlim=XLIM, ylim=YLIM, ylabel=False, dr=ZONE_WIDTH)
+                       xlim=XLIM, ylim=YLIM, ylabel='', dr=ZONE_WIDTH)
     plt.subplots_adjust(bottom=0.13, top=0.98, left=0.16, right=0.98, wspace=0.5)
-    fig.savefig(paths.figures / "onezone_regions", dpi=300)
+    fig.savefig(paths.figures / 'onezone_regions', dpi=300)
     plt.close()
     
 def plot_region(fig, radius, dr=4., eta=models.equilibrium_mass_loading(), 
-                output_dir=paths.data/"onezone"/"regions", 
+                output_dir=paths.data/'onezone'/'regions', 
                 color=None, **kwargs):
-    axs = setup_axes(fig, title="", xname="[O/H]", **kwargs)
+    axs = setup_axes(fig, title='', xlabel='[O/H]', **kwargs)
     # Plot underlying APOGEE contours
     apogee_data = APOGEESample.load()
     apogee_solar = apogee_data.region(galr_lim=(radius - dr/2, radius + dr/2), 
                                       absz_lim=(0, 2))
[…]

### 2024-11-04 src/scripts/onezone_sfr.py

@@ -8,33 +8,28 @@ import matplotlib.pyplot as plt
 
 import vice
 
-from multizone.src.yields import W24
-# from multizone.src.yields import J21
-from multizone.src.models import twoinfall, twoinfall_sf_law, equilibrium_mass_loading
-from multizone.src.dtds import exponential
-from multizone.src.models.gradient import gradient
+# from multizone.src.yields import W24
+from multizone.src.yields import J21
+from multizone.src.models import twoinfall_sf_law, equilibrium_mass_loading
 from track_and_mdf import setup_figure, plot_vice_onezone
 from apogee_sample import APOGEESample
 import paths
-from utils import get_bin_centers, twoinfall_gradient
-from _globals import ONEZONE_DEFAULTS, ZONE_WIDTH
+from utils import get_bin_centers, twoinfall_onezone
+from _globals import ONEZONE_DEFAULTS
 from colormaps import paultol
 
 RADIUS = 8.
-ONSET = 6
+ZONE_WIDTH = 2.
+ONSET = 3.2
 FIRST_TIMESCALE = 1.
 SECOND_TIMESCALE = 15.
 FEH_LIM = (-1.4, 0.6)
-OFE_LIM = (-0.12, 0.48)
+OFE_LIM = (-0.08, 0.48)
 
 def main():
     plt.style.use(paths.styles / "paper.mplstyle")
     plt.rcParams["axes.prop_cycle"] = plt.cycler("color", paultol.vibrant.colors)
     fig, axs = setup_figure(xlim=FEH_LIM, ylim=OFE_LIM)
-    
-    print(vice.yields.ccsne.settings['fe'])
-    print(vice.yields.ccsne.settings['o'])
-    print(vice.yields.sneia.settings['fe'])
 
     # Plot underlying APOGEE contours
     apogee_data = APOGEESample.load()
@@ -66,19 +61,20 @@ def main():
     
     # One-zone model parameters
     simtime = np.arange(0, 13.21, 0.01)
-    area = np.pi * ((RADIUS + ZONE_WIDTH)**2 - RADIUS**2)
-    eta_func = equilibrium_mass_loading(
-        tau_star=2.,
-        tau_sfh=SECOND_TIMESCALE, 
-        equilibrium=0.2
-    )
-    # eta_func = vice.milkyway.default_mass_loading
-    ifr = twoinfall_gradient(
[…]

### 2024-11-04 src/scripts/track_and_mdf.py

@@ -208,8 +208,8 @@ def setup_figure(width=ONE_COLUMN_WIDTH, **kwargs):
     return fig, axs
 
 
-def setup_axes(fig, title='', xlim=(-2.1, 0.4), ylim=(-0.1, 0.52), xlabel=True, 
-               ylabel=True, xname='[Fe/H]', yname='[O/Fe]'):
+def setup_axes(fig, title='', xlim=(-2.1, 0.4), ylim=(-0.1, 0.52), 
+               xlabel='[Fe/H]', ylabel='[O/Fe]'):
     """
     Create three axes: the main abundance track axis plus two
     side panels for [Fe/H] and [O/Fe] distribution functions.
@@ -245,16 +245,16 @@ def setup_axes(fig, title='', xlim=(-2.1, 0.4), ylim=(-0.1, 0.52), xlabel=True,
     ax_main.xaxis.set_minor_locator(MultipleLocator(0.1))
     ax_main.yaxis.set_major_locator(MultipleLocator(0.1))
     ax_main.yaxis.set_minor_locator(MultipleLocator(0.02))
-    if xlabel:
-        ax_main.set_xlabel(xname)
-    else:
+    if xlabel == '':
         ax_main.xaxis.set_ticklabels([])
         gs.update(bottom=0.)
-    if ylabel:
-        ax_main.set_ylabel(yname, labelpad=-2)
     else:
+        ax_main.set_xlabel(xlabel)
+    if ylabel == '':
         ax_main.yaxis.set_ticklabels([])
         gs.update(left=0.02)
+    else:
+        ax_main.set_ylabel(ylabel)
     ax_main.set_xlim(xlim)
     ax_main.set_ylim(ylim)
     # Add panel above for MDF in [Fe/H]
@@ -264,20 +264,20 @@ def setup_axes(fig, title='', xlim=(-2.1, 0.4), ylim=(-0.1, 0.52), xlabel=True,
     ax_mdf.set_ylim((0, 1.2))
     ax_mdf.yaxis.set_major_locator(MultipleLocator(1))
     ax_mdf.yaxis.set_minor_locator(MultipleLocator(0.2))
-    if ylabel:
-        ax_mdf.set_ylabel(r'$P($%s$)$' % xname, size='small')
-    else:
+    if ylabel == '':
         ax_mdf.yaxis.set_ticklabels([])
+    else:
+        ax_mdf.set_ylabel(r'$P($%s$)$' % xlabel, size='small')
[…]

### 2024-11-04 src/tex/ms.tex

@@
 
+\subsection{Summary of Two-Infall Papers}
+
 % Summary of two-infall papers
@@
 \citet{chiappini_chemical_1997} presented the first two-infall model of the MW disk.
-They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall varying with radius.
-Their model parameters were constrained by the observed
+They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall increasing linearly with radius.
+They assume the formation timescale of the thick disk is 1 Gyr, and the time of the second infall is 2 Gyr.
+They also assume a lower threshold on the gas density required for star formation, which produces a star formation hiatus at the end of the thick disk phase.
+They also noted the ``loop'' that appears in the \aFe--[Fe/H] relation during the thin disk phase.
+
+\citet{palla_chemical_2020} explored radial gas flows, variable star formation efficiency of the thin disk, and the onset time of the second infall (but not the infall timescales).
+They find that inside-out formation (i.e., longer infall timescales in the outer disk) is not sufficient to reproduce observed abundance gradients, and that radial gas flows, possibly in combination with a radially-varying star formation law, are key.
+Pre-enriched infall in the inner disk ($R<8$ kpc) at the level of -0.5 dex also improves agreement with data.
 
@@
 
+The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain.
+This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
+We adopt the yields of \citet{weinberg_scale_2023}, who use a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau to infer population-averaged yields.
+The only difference here is that we assume that $20\%$ of Si in the Sun is produced by SNe Ia, which reduces the Si plateau to [Si/Fe]$_{\rm cc}=0.35$ and results in a non-zero value for $y_{\rm SI}^{\rm cc}$, unlike in \citet{weinberg_scale_2023}.
+Our yields are presented in Table \ref{tab:yields}.
+
 \begin{table}
     \centering
-    \caption{Yields.}
+    \caption{Nucleosynthetic yields.}
     \label{tab:yields}
@@
 
+\subsection{Outflows}
+\label{sec:outflows}
+
 \subsection{The SN Ia Delay-Time Distribution}
 \label{sec:dtd}
+
+We adopt the wide plateau DTD of \citet{dubay_galactic_2024} as our fiducial DTD.
+
+\begin{equation}
+    \label{eq:plateau-dtd}
+    f_{\rm Ia}^{\rm plat}(t) =
+    \begin{cases}
+        1, & t < 1\,{\rm Gyr} \\
+        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
+    \end{cases}
+\end{equation}
 

### 2024-11-15 src/scripts/multizone/src/yields/W24.py
return to Weinberg++2024 values

@@ -10,10 +10,6 @@ Fexp = 0.75
 mfecc = 0.058
 # Mean SN Ia Fe yield (Msun)
 mfeia = 0.7
-# Fraction of solar Si produced by CC SNe
-Fsicc = 0.8
-# Fraction of solar Fe produced by CC SNe
-# Ffecc = 0.3
 
 # solar abundances by mass
 # based on Magg et al. (2022) Table 5 + 0.04 dex to correct for diffusion
@@ -71,15 +67,16 @@ for el in ["o", "mg", "si", "fe"]:
 
 # population averaged SNIa Fe yield, integrated to t=infty
 # for a constant SFR, will evolve to afeeq at late times
-afeeq = -0.05
+afeeq = 0.
 tau_sfh = 15
-tau_Ia = 3
+tau_Ia = 1.5
 mu = tau_sfh / (tau_sfh - tau_Ia) # assuming tau_sfh >> minimum SN Ia delay time
-# print(mu)
 Ria = (Rcc / mu) * (mfecc / mfeia) * (10 ** (afecc["o"] - afeeq) - 1.)
-# Ria = 2.2e-3 # Maoz & Graur (2017)
 vice.yields.sneia.settings["fe"] = Ria * mfeia
-# vice.yields.sneia.settings["fe"] = (1 - Ffecc) / Ffecc * vice.yields.ccsne.settings["fe"]
+
+# Other SN Ia element yields
 vice.yields.sneia.settings["o"] = 0.
 vice.yields.sneia.settings["mg"] = 0.
+# Fraction of Solar Si produced by CC SNe
+Fsicc = 10 ** (afecc["si"] - afecc["o"])
 vice.yields.sneia.settings["si"] = (1 - Fsicc) / Fsicc * vice.yields.ccsne.settings["si"]

### 2024-12-12 src/scripts/migration_comparison.py
update migration_comparison.py

@@ -23,6 +23,7 @@ def main(style='paper', smooth_width=0.1, xlim=(-1.7, 0.7), nbins=100):
     mzs_nomig = MultizoneStars.from_output('nomigration/outflow/no_gasflow/pristine/J21/insideout/diskmodel')
     # mzs_post = MultizoneStars.from_output('post-process/outflow/no_gasflow/J21/twoinfall/diskmodel')
     mzs_fast = MultizoneStars.from_output('gaussian_fast/outflow/no_gasflow/pristine/J21/insideout/diskmodel')
+    mzs_strong = MultizoneStars.from_output('gaussian_strong/outflow/no_gasflow/pristine/J21/insideout/diskmodel')
     mzs_f18 = MultizoneStars.from_output('frankel2018/outflow/no_gasflow/pristine/J21/insideout/diskmodel')
     
     for i, ax in enumerate(axs.flatten()):
@@ -45,11 +46,11 @@ def main(style='paper', smooth_width=0.1, xlim=(-1.7, 0.7), nbins=100):
                                                smoothing=smooth_width)
         ax.plot(get_bin_centers(mdf_bins), fast_mdf, c='b', ls='--',
                 label=r'Gaussian ($\tau^{0.5}$)')
-        f18_subset = mzs_f18.region(galr_lim, absz_lim=(0, 2))
-        f18_mdf, mdf_bins = f18_subset.mdf('[fe/h]', bins=nbins, range=xlim,
+        strong_subset = mzs_strong.region(galr_lim, absz_lim=(0, 2))
+        strong_mdf, mdf_bins = strong_subset.mdf('[fe/h]', bins=nbins, range=xlim,
                                                smoothing=smooth_width)
-        ax.plot(get_bin_centers(mdf_bins), f18_mdf, c='g', ls=':',
-                label='Frankel et al. (2018)')
+        ax.plot(get_bin_centers(mdf_bins), strong_mdf, c='g', ls=':',
+                label=r'Gaussian ($\sigma_{RM8}=3.6$ kpc)')
         # Plot data
         # apogee_subset = apogee_data.region(galr_lim=galr_lim, absz_lim=(0, 2))
         # data_mdf, mdf_bins = apogee_subset.mdf(col='FE_H', bins=nbins,

### 2024-12-12 src/tex/ms.tex

@@
 
+\section{Outline}
+
+\subsection{Outline of Key Plots}
+
+\begin{itemize}
+    \item The turn-over in [O/Fe] evolution due to the second infall epoch produces a peak in the stellar distribution at intermediate [O/Fe], which is not observed in APOGEE.
+    \item Attempts to fix the problem with the [O/Fe] distribution in the thin disk end up creating issues with other observables, such as the thick/thin disk surface density ratio, the SN Ia DTD, or the age-metallicity relation.
+    \item The equilibrium model, if accurate, places very strict limits on the two-infall model, moreso than for other models.
+    \item A short ($\sim200$ Myr) star formation hiatus early in the history of the disk is sufficient to produce a bimodal distribution of [O/Fe] without altering the gas infall prescription.
+\end{itemize}
+
 \section{Introduction}
+
+% To add: Karma Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra
 
@@
 They also noted the ``loop'' that appears in the \aFe--[Fe/H] relation during the thin disk phase.
+They mostly compare to Solar neighborhood data.
+
+\citet{chiappini_abundance_2001} updated their model to fit the observed abundance, stellar, and gas gradients in the Milky Way disk.
+They find that a density threshold for star formation, making a gap in star formation between the halo and disk phases, is necessary to reproduce observational data.
+They argue that the details of halo formation also have a strong impact on the outer disk.
+No radial flows or outflows.
+I'm confused about their distinction between halo and thick disk, if any.
+
+\citet{chiappini_oxygen_2003} compare model predictions of C, N, and O to Milky Way and other spiral galaxy data.
+They predict a very slow enrichment between the birth of the Sun and present day, which they claim is due to their adopted gas density threshold for star formation (the infall rate is low enough that the SFR oscillates from timestep to timestep).
+
+\citet{matteucci_effect_2009} investigated different SN Ia delay time distributions using the \citep{chiappini_chemical_1997,chiappini_abundance_2001} model.
+They use a model for the full disk but compare only to Solar neighborhood data.
+They concluded that some prompt SN Ia enrichment is necessary to match observed abundance patterns.
+
+\citet{spitoni_effects_2009} relaxed the instantaneous recycling approximation in two different ways: galactic fountains (i.e., SN ejecta are launched out of the disk and take some time to return) and metal cooling (i.e., newly-enriched hot gas takes time to cool before it can form stars).
+They found that fountains do not strongly affect the evolution of the $\alpha$-elements for short (few hundred Myr) timescales.
+The effect of a metal cooling timescale is similarly negligible if the yields are not dependent on metallicity.
+
+\citet{spitoni_effects_2011} find that a two-infall model of the disk without gas exchange produces a radial metallicity gradient which is too shallow.
+They implement an inward radial gas flow on the order of $\sim0-4$ km s$^{-1}$ which varies with radius, and find that it improves agreement with the observed gradient.
+However, they found that a variable star formation efficiency with radius in combination with a gas density threshold for star formation could also reproduce the observed gradient without radial flows.
+
+\citet{spitoni_effect_2015}
 
@@
 % Radial gas flows
-Some two-infall studies \citep[e.g.,][]{palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
+Some two-infall studies \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
 
@@
 
-\section{One-Zone Models}
+\section{Exploring the Parameter Space in One-Zone Models}
 \label{sec:onezone-results}
@@
 \end{figure*}
+
+Figure \ref{fig:onezone-dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
+The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks.
+The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal.
+Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/onezone_dtd.pdf}
+    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr.}
+    \label{fig:onezone-dtd}
+\end{figure*}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/yield_outflow.pdf}
+    \caption{Caption.}
+    \label{fig:onezone-dtd}
+\end{figure}
 

### 2024-12-16 src/scripts/onezone_sfe_hiatus.py
burst -> hiatus 2

@@ -1,5 +1,5 @@
 """
-This script plots a one-zone VICE model with a short burst in the SFE.
+This script plots a one-zone VICE model with a short hiatus in the SFE.
 """
 
 import numpy as np
@@ -18,8 +18,8 @@ from colormaps import paultol
 
 RADIUS = 8.
 ZONE_WIDTH = 2.
-BURST_ONSET = 1.0
-BURST_DURATION = 0.3
+HIATUS_ONSET = 1.0
+HIATUS_DURATION = 0.3
 TAU_STAR_BASE = 2.0
 TAU_STAR_ENHANCEMENT = 10
 FEH_LIM = (-1.6, 0.6)
@@ -53,7 +53,7 @@ def main():
                 color='gray', linestyle='-', marker=None)
     
     # Set up output directory
-    output_dir = paths.data / 'onezone' / 'sfe_burst'
+    output_dir = paths.data / 'onezone' / 'sfe_hiatus'
     if not output_dir.exists():
         output_dir.mkdir(parents=True)
     
@@ -74,7 +74,7 @@ def main():
     plot_vice_onezone(name, fig=fig, axs=axs, label='Fiducial', 
                       linestyle='--', marker_labels=True)
 
-    # SFE burst model
+    # SFE hiatus model
     name = str(output_dir / 'onset13_width02')
     tau_star = tau_star_burst(onset=1.3, duration=0.2)
     sz = vice.singlezone(
@@ -85,16 +85,16 @@ def main():
     )
     sz.tau_star = tau_star
     sz.run(simtime, overwrite=True)
-    plot_vice_onezone(name, fig=fig, axs=axs, label='SFE Burst')
+    plot_vice_onezone(name, fig=fig, axs=axs, label='SFE Hiatus')
     axs[0].legend(loc='upper right')
     
-    plt.savefig(paths.figures / 'onezone_sfe_burst')
+    plt.savefig(paths.figures / 'onezone_sfe_hiatus')
     plt.close()
 
 
 class tau_star_burst:
-    def __init__(self, base=TAU_STAR_BASE, onset=BURST_ONSET, 
-                 duration=BURST_DURATION, enhancement=TAU_STAR_ENHANCEMENT):
+    def __init__(self, base=TAU_STAR_BASE, onset=HIATUS_ONSET, 
+                 duration=HIATUS_DURATION, enhancement=TAU_STAR_ENHANCEMENT):
         self.base = base
         self.onset = onset
         self.duration = duration

### 2025-01-07 src/tex/ms.tex

@@
     \item A short ($\sim200$ Myr) star formation hiatus early in the history of the disk is sufficient to produce a bimodal distribution of [O/Fe] without altering the gas infall prescription.
+This is distinct from the star formation hiatus produced by the two-infall model.
 \end{itemize}
@@
 
-\citet{spitoni_effect_2015}
+\citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
+They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
+This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
+They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
+Their only point of comparison with data is the local G-dwarf metallicity distribution.
+
+\citet{grisoni_ambre_2017} argue for a ``parallel'' scenario, where the thick and thin disks form simultaneously but with very different infall timescales (0.1 and 7 Gyr, respectively).
+They compare their models with stellar abundances from the AMBRE sample of solar-neighborhood dwarfs.
+They argue that the parallel scenario can produce metal-rich high-alpha stars in situ, whereas in the two-infall scenario these stars would have to migrate from the inner disk.
 
@@
 A version of the three-infall model with milder dilution (mild pre-enrichment of the gas with a smaller amount of infall) compared to \citet{spitoni_beyond_2023} can simultaneously match the metalliticy of old, intermediate, and young clusters across the disk.
+
+\citet{spitoni_remind_2024}
 
@@
 \label{sec:dtd}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/delay_time_distribution.pdf}
+    \caption{Caption.}
+    \label{fig:dtd}
+\end{figure*}
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_sfe_hiatus.pdf}
+    \caption{Caption.}
+    \label{fig:onezone-sfe-hiatus}
+\end{figure}
+
 \section{Conclusions}

### 2025-01-09 src/scripts/onezone_params_low_yields.py
adjust default onset time

@@ -22,11 +22,11 @@ def main():
     subfigs = [fig.add_subfigure(gs[:,i:i+w]) for i, w in zip((0, 8, 15), (8, 7, 7))]
     print('\nFirst timescale')
     axs0 = vary_param(subfigs[0], first_timescale=[0.1, 0.3, 1, 3],
-                      second_timescale=10, onset=3,
+                      second_timescale=10, onset=4,
                       xlim=XLIM, ylim=YLIM, label_index=2, verbose=True)
     print('\nSecond timescale')
     axs1 = vary_param(subfigs[1], second_timescale=[3, 5, 10, 30],
-                      first_timescale=1, onset=3,
+                      first_timescale=1, onset=4,
                       xlim=XLIM, ylim=YLIM, show_ylabel=False,
                       label_index=0, verbose=True)
     print('\nOnset time')

### 2025-01-09 src/tex/ms.tex

@@
 
-% To add: Karma Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra
+% To add: Carme Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra
 
@@
 The infall history of any given region of the disk is described by two successive, exponentially declining bursts, whose timescale may vary as a function of radius.
-The first infall, which forms the thick disk, has a short timescale, typically on the order of $\sim1$ Gyr.
+The first infall, which forms the thick disk, has a short timescale, typically on the order of $\sim0.1-1$ Gyr.
 The second infall forms the thin disk and has a much longer timescale, typically $\sim4-10$ Gyr.
@@
     \includegraphics{figures/delay_time_distribution.pdf}
-    \caption{Caption.}
+    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr.
+Key takeaway: the size of the thin disk loop can be reduced by using an SN Ia DTD with more prompt events.
+However, this messes up the location of the high-alpha sequence.}
     \label{fig:dtd}
 \end{figure*}
+
+Figure \ref{fig:dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
+The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks.
+The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal.
+Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
 
@@
     \includegraphics{figures/onezone_sfr.pdf}
-    \caption{Caption.}
+    \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
+This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
     \label{fig:onezone-sfr}
@@
     \label{fig:onezone-params}
-\end{figure*}
-
-Figure \ref{fig:onezone-dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
-The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks.
-The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal.
-Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/onezone_dtd.pdf}
-    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr.}
-    \label{fig:onezone-dtd}
 \end{figure*}

### 2025-01-09 src/tex/ms.tex
Updates from Overleaf
Manuscript updates

@@
     \centering
-    \includegraphics{figures/onezone_params.pdf}
-    \caption{Caption.}
-    \label{fig:onezone-params}
+    \includegraphics{figures/onezone_params_low_yields.pdf}
+    \caption{Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances.}
+    \label{fig:twoinfall-parameters-low-yields}
 \end{figure*}
+
+% \begin{figure*}
+%     \centering
+%     \includegraphics{figures/onezone_params_high_yields.pdf}
+%     \caption{Caption.}
+%     \label{fig:twoinfall-parameters-high-yields}
+% \end{figure*}
 
@@
     \includegraphics{figures/yield_outflow.pdf}
-    \caption{Caption.}
+    \caption{Key takeaway: the higher yields produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall.
+In contrast, the lower yields lead to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe].}
     \label{fig:onezone-dtd}

### 2025-01-21 src/scripts/multizone/_globals.py
add solar-scaled yield files

@@ -36,4 +36,4 @@ THICK_DISK_SCALE_RADIUS = 2.0 # kpc
 THICK_TO_THIN_RATIO = 0.27 # at r = 0
 GAS_DISK_SCALE_RADIUS = 3.6 # kpc
 
-YIELDS = "W24mod"
+YIELDS = "yZ1"

### 2025-01-21 src/scripts/multizone/src/yields/__init__.py

@@ -13,5 +13,9 @@ elif YIELDS == "W24":
     from . import W24
 elif YIELDS == "W24mod":
     from . import W24mod
+elif YIELDS == "yZ1":
+    from . import yZ1
+elif YIELDS == "yZ3":
+    from . import yZ3
 else:
     raise ValueError("Unrecognized yield specification in multizone/_globals.py.")

### 2025-01-21 src/scripts/multizone/src/yields/yZ1.py

@@ -1,0 +1,16 @@
+"""
+This file sets the Solar-scaled nucleosynthetic yields according to y/Z=1.
+"""
+import vice
+
+SOLAR_SCALE = 1.0 # y_O / Z_O,Sun
+AFE_CC = 0.45 # CCSN [a/Fe] plateau
+YIA_SCALE = 1.15 # arbitrary scaling of yIa to adjust chemical evolution endpoint
+
+# IMF-averaged CCSN yields
+vice.yields.ccsne.settings["o"] = SOLAR_SCALE * vice.solar_z["o"]
+vice.yields.ccsne.settings["fe"] = SOLAR_SCALE * 10**-AFE_CC * vice.solar_z["fe"]
+
+# population averaged SNIa Fe yield
+vice.yields.sneia.settings["o"] = 0.
+vice.yields.sneia.settings["fe"] = YIA_SCALE * SOLAR_SCALE * (1 - 10**-AFE_CC) * vice.solar_z["fe"]

### 2025-01-21 src/scripts/multizone/src/yields/yZ3.py

@@ -1,0 +1,16 @@
+"""
+This file sets the Solar-scaled nucleosynthetic yields according to y/Z=3.
+"""
+import vice
+
+SOLAR_SCALE = 3.0 # y_O / Z_O,Sun
+AFE_CC = 0.45 # CCSN [a/Fe] plateau
+YIA_SCALE = 1.5 # arbitrary scaling of yIa to adjust chemical evolution endpoint
+
+# IMF-averaged CCSN yields
+vice.yields.ccsne.settings["o"] = SOLAR_SCALE * vice.solar_z["o"]
+vice.yields.ccsne.settings["fe"] = SOLAR_SCALE * 10**-AFE_CC * vice.solar_z["fe"]
+
+# population averaged SNIa Fe yield
+vice.yields.sneia.settings["o"] = 0.
+vice.yields.sneia.settings["fe"] = YIA_SCALE * SOLAR_SCALE * (1 - 10**-AFE_CC) * vice.solar_z["fe"]

### 2025-01-21 src/scripts/yields.py

@@ -5,22 +5,18 @@ adopted in this paper.
 
 import pandas as pd
 import vice
-from multizone.src.yields import W24
 import paths
 
 def main():
-    ccsn_yields = []
-    snia_yields = []
-    elements = ['O', 'Mg', 'Si', 'Fe']
-    for el in elements:
-        ccsn_yields.append('\\num{%.2e}' % vice.yields.ccsne.settings[el])
-        snia_yields.append('\\num{%.2e}' % vice.yields.sneia.settings[el])
+    from multizone.src.yields import yZ1
+    yZ1_yields, yZ1_labels = make_column()
+    from multizone.src.yields import yZ3
+    yZ3_yields, yZ3_labels = make_column()
     df = pd.DataFrame({
-        'Element': elements,
-        '$y_{\\rm X}^{\\rm CC}$': ccsn_yields,
-        '$y_{\\rm X}^{\\rm Ia}$': snia_yields,
-    })
-    latex_table = df.to_latex(column_format='c|cc', index=False)
+        '$y/Z_\\odot=1$': yZ1_yields,
+        '$y/Z_\\odot=3$': yZ3_yields,
+    }, index=yZ1_labels)
+    latex_table = df.to_latex(column_format='c|cc', index=True)
     # Replace float 0s with int
     latex_table = latex_table.replace('0.00e+00', '0')
     # Replace \toprule, \midrule, \bottomrule with \hline
@@ -30,6 +26,18 @@ def main():
     # Write to output
     with open(paths.output / 'yields.tex', 'w') as f:
         f.write(latex_table)
+
+def make_column(elements = ['O', 'Fe']):
+    ccsn_yields = []
+    ccsn_labels = []
+    snia_yields = []
+    snia_labels = []
+    for el in elements:
+        ccsn_yields.append('\\num{%.2e}' % vice.yields.ccsne.settings[el])
+        ccsn_labels.append('$y_{\\rm %s}^{\\rm CC}$' % el)
+        snia_yields.append('\\num{%.2e}' % vice.yields.sneia.settings[el])
+        snia_labels.append('$y_{\\rm %s}^{\\rm Ia}$' % el)
+    return ccsn_yields + snia_yields, ccsn_labels + snia_labels
 
 if __name__ == '__main__':
     main()

### 2025-01-21 src/tex/outline.tex
Updates from Overleaf

\begin{enumerate}

    \item Introduction
    \begin{enumerate}
        \item Hook, summary of alpha-bimodality
        \item Summary of two-infall literature
        \item Summary of secular evolution models which claim alpha-bimodality
        \item Goal of the paper
    \end{enumerate}

    \item Methods
    \begin{enumerate}
        \item Description of GCE models
        \begin{enumerate}
            \item {\it Plot:} Two-infall parameters in one-zone models. The second infall timescale $\tau_2$ is the most important parameter for fitting the low-alpha sequence and the MDF.
        \end{enumerate}
        \item Motivate outflow prescription
        \item Discuss yields
        \begin{enumerate}
            \item {\it Plot:} Yield scaling in one-zone models. No yield set is fully compatible with the observed abundance history, so we investigate both the high yield and low yield cases in our multi-zone models.
        \end{enumerate}
        \item Describe data sources
    \end{enumerate}

    \item Multi-zone model results
    \begin{enumerate}
        \item Stellar abundance distributions
        \begin{enumerate}
            \item {\it Plot:} Stellar [O/Fe] distributions from multi-zone models with the low and high yield sets. Using the higher yields, the global [O/Fe] distribution is triple-peaked which does not fit the data.
            \item {\it Plot:} Abundance diagram from a high-yield one-zone model which illustrates that the turn-over in [O/Fe] evolution due to the second infall epoch produces an intermediate [O/Fe] peak in the stellar distribution.
        \end{enumerate}
        \item The radial abundance gradient
        \begin{enumerate}
            \item {\it Plot:} Radial abundance gradients predicted by multi-zone models with low and high yields.
            \item A variable second infall timescale
            \item Altering the outflow prescription
            \item Radial gas flows
        \end{enumerate}
        \item Abundance histories
        \begin{enumerate}
            \item {\it Plot:} Comparison of stellar age-abundance diagrams from multi-zone models with low and high yields. The second infall epoch produces substantial dilution of the ISM metallicity, for which there is little observational evidence. Higher yields help the system recover from perturbations more rapidly and are in less disagreement with the data.
            \item {\it Plot:} Similar, but showing the mode of the stellar abundance distributions over time compared to the data. Due to the dilution from the second infall, the Solar neighborhood spends less time in equilibrium in the high-yield case, and doesn't yet reach equilibrium in the low-yield case.
            \item Can CGM pre-enrichment mitigate dilution and/or approach to equilibrium issues?
            \item Other parameters that can mitigate these issues
        \end{enumerate}
    \end{enumerate}

    \item Discussion
    \begin{enumerate}
        \item Other ways to fix the thin disk abundances
        \begin{enumerate}
            \item {\it Plot:} The DTD in one-zone models. A prompt DTD can reduce the size of the low-alpha loop, but it messes up the high-alpha sequence.
            \item {\it Plot:} Adjusting the thick-to-thin disk prescription in one-zone models. If the mass in the first infall is significantly more substantial, the [O/Fe] distribution better matches the data in the high yield case.
        \end{enumerate}
        \item SF hiatus not driven by infall history
        \begin{enumerate}
            \item {\it Plot:} An SFE-driven hiatus in a one-zone model can produce alpha-bimodality without altering the gas inflow prescription.
        \end{enumerate}
    \end{enumerate}

    \item Conclusions
    \begin{enumerate}
        \item Summary of findings
        \begin{enumerate}
            \item Attempts to fix the problem with the [O/Fe] distribution in the thin disk end up creating issues with other observables, such as the thick/thin disk surface density ratio, the SN Ia DTD, or the age-metallicity relation.
            \item The equilibrium model, if accurate, places very strict limits on the two-infall model, moreso than for other models.
            \item A short ($\sim200$ Myr) star formation hiatus early in the history of the disk is sufficient to produce a bimodal distribution of [O/Fe] without altering the gas infall prescription. This is distinct from the star formation hiatus produced by the two-infall model.
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

### 2025-01-21 src/tex/ms.tex

--- 2025-01-09 src/tex/ms.tex
@@
 \section{Outline}
-
-\subsection{Outline of Key Plots}
-
-\begin{itemize}
-    \item The turn-over in [O/Fe] evolution due to the second infall epoch produces a peak in the stellar distribution at intermediate [O/Fe], which is not observed in APOGEE.
-    \item Attempts to fix the problem with the [O/Fe] distribution in the thin disk end up creating issues with other observables, such as the thick/thin disk surface density ratio, the SN Ia DTD, or the age-metallicity relation.
-    \item The equilibrium model, if accurate, places very strict limits on the two-infall model, moreso than for other models.
-    \item A short ($\sim200$ Myr) star formation hiatus early in the history of the disk is sufficient to produce a bimodal distribution of [O/Fe] without altering the gas infall prescription.
-This is distinct from the star formation hiatus produced by the two-infall model.
-\end{itemize}
+\input{outline.tex}
 
@@
         M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
-        \dot M_r    & continuous    & \ref{sec:multizone-results} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
+        \dot M_r    & continuous    & \ref{sec:multizone-results} & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
         \hline
         % DTD
-        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & delay-time distribution of Type Ia supernovae \\
+        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay-time distribution of Type Ia supernovae \\
         t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
@@
 
-\subsection{Outflows}
-\label{sec:outflows}
-
-\subsection{The SN Ia Delay-Time Distribution}
+\subsubsection{The SN Ia Delay-Time Distribution}
 \label{sec:dtd}
 
-\begin{figure*}
-    \centering
-    \includegraphics{figures/delay_time_distribution.pdf}
-    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr.
-Key takeaway: the size of the thin disk loop can be reduced by using an SN Ia DTD with more prompt events.
-However, this messes up the location of the high-alpha sequence.}
-    \label{fig:dtd}
-\end{figure*}
-
-Figure \ref{fig:dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
-The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks.
-The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal.
-Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
-
-We adopt the wide plateau DTD of \citet{dubay_galactic_2024} as our fiducial DTD.
-
+The SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
+\begin{equation}
+    R_{\rm Ia}(t) = 
+    \begin{cases}
+        \frac{N_{\rm Ia}}{M_\star}
+        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
+        0 & t < t_D,
+    \end{cases}
+    \label{eq:dtd-function}
+\end{equation}
+where $t_D$ is the minimum SN Ia delay time, $t_{\rm max}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}$ is the un-normalized form of the DTD.
+Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
 \begin{equation}
     \label{eq:plateau-dtd}
-    f_{\rm Ia}^{\rm plat}(t) =
+    f_{\rm Ia}(t) =
     \begin{cases}
@@
 \end{equation}
+
+\subsection{Outflows}
+\label{sec:outflows}
 
@@
     \centering
-    \includegraphics{figures/onezone_params.pdf}
-    \caption{Caption.}
-    \label{fig:onezone-params}
+    \includegraphics{figures/onezone_params_low_yields.pdf}
+    \caption{Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances.
+For consistency, all models use the {\tt W24mod} yield set and assume $\eta=0.43$.
+(a) The first infall timescale $\tau_1$ adjusts the position and spread of the high-$\alpha$ sequence.
+(b) The second infall timescale $\tau_2$ adjusts the width of the low-$\alpha$ peak (separation of the low-$\alpha$ peaks) and the width of the MDF.
+(c) The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr.
+While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions.
+Key takeaway: The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
+    \label{fig:twoinfall-parameters-low-yields}
 \end{figure*}
+
+% \begin{figure*}
+%     \centering
+%     \includegraphics{figures/onezone_params_high_yields.pdf}
+%     \caption{Caption.}
+%     \label{fig:twoinfall-parameters-high-yields}
+% \end{figure*}
 
@@
     \includegraphics{figures/yield_outflow.pdf}
-    \caption{Caption.}
+    \caption{We manually adjusted the outflow mass-loading parameter $\eta$ and SN Ia yield $y ^{\rm Ia}_{\rm Fe}$ to match the data in the youngest age bin.
+Key takeaway: the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall.
+In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.}
     \label{fig:onezone-dtd}
@@
 \label{sec:discussion}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/delay_time_distribution.pdf}
+    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr.
+Key takeaway: the size of the loop can be reduced by using an SN Ia DTD with more prompt events.
+However, this messes up the location of the high-alpha sequence.}
+    \label{fig:dtd}
+\end{figure*}
+
+Figure \ref{fig:dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
+The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks.
+The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal.
+Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
 

### 2025-01-21 src/tex/ms.tex
Updates from Overleaf

@@
 The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain. 
-This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
+% This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
 We adopt the yields of \citet{weinberg_scale_2023}, who use a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau to infer population-averaged yields.
@@
     \centering
-    \caption{Nucleosynthetic yields.}
+    \caption{Nucleosynthetic yield sets.}
     \label{tab:yields}
@@
 \end{table}
+
+Adopting a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$, the yield set $y/Z_\odot=1$ corresponds to an integrated SN Ia rate of $N_{\rm Ia}/M_\star=\num{1.37e-3}$ M$_\odot^{-1}$, and the higher set $y/Z_\odot=3$ corresponds to $N_{\rm Ia}/M_\star=\num{5.36e-3}$ M$_\odot^{-1}$
 

### 2025-01-22 src/scripts/multizone/src/yields/__init__.py
add yZ2 yields

@@ -15,6 +15,8 @@ elif YIELDS == "W24mod":
     from . import W24mod
 elif YIELDS == "yZ1":
     from . import yZ1
+elif YIELDS == "yZ2":
+    from . import yZ2
 elif YIELDS == "yZ3":
     from . import yZ3
 else:

### 2025-01-22 src/scripts/multizone/src/yields/yZ2.py

@@ -1,0 +1,16 @@
+"""
+This file sets the Solar-scaled nucleosynthetic yields according to y/Z=3.
+"""
+import vice
+
+SOLAR_SCALE = 2.0 # y_O / Z_O,Sun
+AFE_CC = 0.45 # CCSN [a/Fe] plateau
+YIA_SCALE = 1.25 # arbitrary scaling of yIa to adjust chemical evolution endpoint
+
+# IMF-averaged CCSN yields
+vice.yields.ccsne.settings["o"] = SOLAR_SCALE * vice.solar_z["o"]
+vice.yields.ccsne.settings["fe"] = SOLAR_SCALE * 10**-AFE_CC * vice.solar_z["fe"]
+
+# population averaged SNIa Fe yield
+vice.yields.sneia.settings["o"] = 0.
+vice.yields.sneia.settings["fe"] = YIA_SCALE * SOLAR_SCALE * (1 - 10**-AFE_CC) * vice.solar_z["fe"]

### 2025-01-22 src/scripts/yields.py
expand yields table

@@ -10,10 +10,13 @@ import paths
 def main():
     from multizone.src.yields import yZ1
     yZ1_yields, yZ1_labels = make_column()
+    from multizone.src.yields import yZ2
+    yZ2_yields, yZ2_labels = make_column()
     from multizone.src.yields import yZ3
     yZ3_yields, yZ3_labels = make_column()
     df = pd.DataFrame({
         '$y/Z_\\odot=1$': yZ1_yields,
+        '$y/Z_\\odot=2$': yZ2_yields,
         '$y/Z_\\odot=3$': yZ3_yields,
     }, index=yZ1_labels)
     latex_table = df.to_latex(column_format='c|cc', index=True)
@@ -23,11 +26,13 @@ def main():
     latex_table = latex_table.replace('\\toprule', '\\hline\\hline')
     latex_table = latex_table.replace('\\midrule', '\\hline')
     latex_table = latex_table.replace('\\bottomrule', '\\hline')
+    # Add horizontal rule between yields and SN Ia rates
+    latex_table = latex_table.replace('$N_', '\\hline\n$N_')
     # Write to output
     with open(paths.output / 'yields.tex', 'w') as f:
         f.write(latex_table)
 
-def make_column(elements = ['O', 'Fe']):
+def make_column(elements = ['O', 'Fe'], mfeia=0.7):
     ccsn_yields = []
     ccsn_labels = []
     snia_yields = []
@@ -37,6 +42,9 @@ def make_column(elements = ['O', 'Fe']):
         ccsn_labels.append('$y_{\\rm %s}^{\\rm CC}$' % el)
         snia_yields.append('\\num{%.2e}' % vice.yields.sneia.settings[el])
         snia_labels.append('$y_{\\rm %s}^{\\rm Ia}$' % el)
+    # Calculate SN Ia rates assuming a mean Fe mass per SN
+    snia_labels.append('$N_{\\rm Ia}/M_\\star$')
+    snia_yields.append('\\num{%.2e}' % (vice.yields.sneia.settings['fe'] / mfeia))
     return ccsn_yields + snia_yields, ccsn_labels + snia_labels
 
 if __name__ == '__main__':

### 2025-01-22 src/scripts/yields.py
fix number of table cols

@@ -19,7 +19,7 @@ def main():
         '$y/Z_\\odot=2$': yZ2_yields,
         '$y/Z_\\odot=3$': yZ3_yields,
     }, index=yZ1_labels)
-    latex_table = df.to_latex(column_format='c|cc', index=True)
+    latex_table = df.to_latex(column_format='c|ccc', index=True)
     # Replace float 0s with int
     latex_table = latex_table.replace('0.00e+00', '0')
     # Replace \toprule, \midrule, \bottomrule with \hline

### 2025-01-22 src/tex/ms.tex

@@
 
-Adopting a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$, the yield set $y/Z_\odot=1$ corresponds to an integrated SN Ia rate of $N_{\rm Ia}/M_\star=\num{1.37e-3}$ M$_\odot^{-1}$, and the higher set $y/Z_\odot=3$ corresponds to $N_{\rm Ia}/M_\star=\num{5.36e-3}$ M$_\odot^{-1}$
+Adopting a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$, the yield set $y/Z_\odot=1$ corresponds to an integrated SN Ia rate of $N_{\rm Ia}/M_\star=\num{1.79e-3}$ M$_\odot^{-1}$, and the higher set $y/Z_\odot=3$ corresponds to $N_{\rm Ia}/M_\star=\num{4.1e-3}$ M$_\odot^{-1}$.
 

### 2025-01-22 src/scripts/abundance_evolution_yields.py
add horizontal colorbar

@@ -37,31 +37,32 @@ def main(uncertainties=True, verbose=False, style='paper', cmap_name='winter_r')
     plt.style.use(paths.styles / f'{style}.mplstyle')
     fig, axs = plt.subplots(
         3, 2, sharex=True, sharey='row', 
-        figsize=(ONE_COLUMN_WIDTH, 1.5 * ONE_COLUMN_WIDTH),
+        figsize=(ONE_COLUMN_WIDTH, 1.67 * ONE_COLUMN_WIDTH),
         gridspec_kw={'hspace': 0, 'wspace': 0}
     )
     # Add colorbar
     birth_galr_bounds = [0, 2, 4, 6, 8, 10, 12, 14, MAX_SF_RADIUS]
     cbar = setup_colorbar(fig, cmap=cmap_name, bounds=birth_galr_bounds,
                           label=r'Birth $R_{\rm{gal}}$ [kpc]',
-                          width=0.04, pad=0.02, labelpad=2)
+                          width=0.02, pad=0.04, labelpad=2,
+                          orientation='horizontal')
 
     for j, yield_set in enumerate(YIELD_SETS):
-        axs[0,j].set_title(yield_set)
+        axs[0,j].set_title(f'{yield_set} yields')
         # Import VICE multizone outputs
         output_name = 'yields/%s/diskmodel' % yield_set
         mzs = MultizoneStars.from_output(output_name, verbose=verbose)
         mzs.region(galr_lim=(7, 9), absz_lim=(0, 2), inplace=True)
         # Model uncertainties
         if uncertainties:
-            mzs.model_uncertainty(apogee_sample.data, inplace=True)
+            mzs.model_uncertainty(solar_sample.data, inplace=True)
         for i, ycol in enumerate(['[o/h]', '[fe/h]', '[o/fe]']):
             mzs.scatter_plot(axs[i,j], 'age', ycol, color='galr_origin',
                              cmap=cmap_name, norm=cbar.norm)
             plot_gas_abundance(axs[i,j], mzs, 'lookback', ycol, ls='--', 
                                label='Gas abundance')
             plot_apogee_median_abundances(
-                axs[i,j], apogee_sample, vice_to_apogee_col(ycol), age_bins, 
+                axs[i,j], solar_sample, vice_to_apogee_col(ycol), age_bins, 
                 offset=-0.2, label='L23 medians'
             )
             plot_vice_median_abundances(

### 2025-01-22 src/scripts/scatter_plot_grid.py

@@ -49,7 +49,7 @@ def plot_gas_abundance(ax, mzs, xcol, ycol, c='k', ls='-', lw=0.5, label=''):
 
 def setup_colorbar(fig, cmap=None, vmin=None, vmax=None, label='', 
                    width=0.02, pad=0.01, labelpad=0, lognorm=False, 
-                   bounds=[], extend='neither'):
+                   bounds=[], extend='neither', orientation='vertical'):
     """
     Configure a vertical colorbar with a specified colormap and normalization.
 
@@ -85,12 +85,20 @@ def setup_colorbar(fig, cmap=None, vmin=None, vmax=None, label='',
     """
     if type(cmap) == str:
         cmap = plt.get_cmap(cmap)
-    # Adjust subplots
-    plt.subplots_adjust(right=fig.subplotpars.right - (width + pad + 0.03))
-    # Define colorbar axis
-    height = fig.subplotpars.top - fig.subplotpars.bottom
-    cax = plt.axes([fig.subplotpars.right + pad, fig.subplotpars.bottom, 
-                    width, height])
+    if orientation == 'horizontal':
+        # Define colorbar axis
+        height = fig.subplotpars.right - fig.subplotpars.left
+        cax = plt.axes([fig.subplotpars.left, fig.subplotpars.bottom, 
+                        height, width])
+        # Adjust subplots
+        plt.subplots_adjust(bottom=fig.subplotpars.bottom + (width + pad + 0.03))
+    else:
+        # Adjust subplots
+        plt.subplots_adjust(right=fig.subplotpars.right - (width + pad + 0.03))
+        # Define colorbar axis
+        height = fig.subplotpars.top - fig.subplotpars.bottom
+        cax = plt.axes([fig.subplotpars.right + pad, fig.subplotpars.bottom, 
+                        width, height])
     # Set normalization
     if len(bounds) > 0:
         norm = BoundaryNorm(bounds, cmap.N, extend=extend)
@@ -98,7 +106,8 @@ def setup_colorbar(fig, cmap=None, vmin=None, vmax=None, label='',
         norm = LogNorm(vmin=vmin, vmax=vmax)
     else:
         norm = Normalize(vmin=vmin, vmax=vmax)
-    cbar = fig.colorbar(ScalarMappable(norm, cmap), cax)
+    cbar = fig.colorbar(ScalarMappable(norm, cmap), cax, 
+                        orientation=orientation)
     cbar.set_label(label, labelpad=labelpad)
     return cbar
 

### 2025-01-24 src/scripts/abundance_evolution.py
add abundance evolution comparison plot

@@ -1,0 +1,131 @@
+"""
+This script compares the abundance evolution of multi-zone models with 
+different yield sets and outflow settings.
+"""
+
+import argparse
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator
+
+from age_abundance_grid import plot_apogee_median_abundances, \
+    plot_vice_median_abundances, AXES_MAJOR_LOCATOR, AXES_MINOR_LOCATOR
+from scatter_plot_grid import plot_gas_abundance, setup_colorbar
+from _globals import MAX_SF_RADIUS, END_TIME, TWO_COLUMN_WIDTH
+from utils import vice_to_apogee_col, capitalize_abundance
+from apogee_sample import APOGEESample
+from multizone_stars import MultizoneStars
+import paths
+
+OUTPUT_NAMES = [
+    'yields/yZ1/diskmodel',
+    'yields/yZ2/diskmodel',
+    'migration_strength/strength50/diskmodel',
+    'pre_enrichment/mh07_alpha00/diskmodel',
+]
+LABELS = [
+    'Fiducial',
+    r'$y/Z_\odot=2$',
+    r'$\sigma_{\rm RM8}=5.0$ kpc',
+    r'${\rm [X/H]}_{\rm CGM}=-0.7$',
+]
+AXES_LIM = {
+    '[o/h]': (-1.4, 0.4),
+    '[fe/h]': (-1.4, 0.4),
+    '[o/fe]': (-0.15, 0.5),
+    'age': (-1, 14.99)
+}
+
+
+def main(verbose=False, uncertainties=True, style='paper', cmap='winter_r'):
+    # Import APOGEE and astroNN data
+    apogee_sample = APOGEESample.load()
+    solar_sample = apogee_sample.region(galr_lim=(7, 9), absz_lim=(0, 2))
+    age_bins = np.arange(0, END_TIME + 2, 2)
+
+    # Set up figure
+    plt.style.use(paths.styles / f'{style}.mplstyle')
+    fig, axs = plt.subplots(
+        3, 4, sharex=True, sharey='row', 
+        figsize=(TWO_COLUMN_WIDTH, 0.7 * TWO_COLUMN_WIDTH),
+        gridspec_kw={'hspace': 0, 'wspace': 0}
+    )
+    # Add colorbar
+    birth_galr_bounds = [3, 5, 7, 9, 11, 13]
[…]

### 2025-01-24 src/tex/ms.tex
Updates from Overleaf

@@
 
+\todo{Copied from last paper.} We use the multi-zone GCE model tools in \vice developed by \citet{johnson_stellar_2021}.
+The basic setup of our models follows theirs.
+The disk is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
+Stellar populations migrate radially under the prescription we describe in Appendix C, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing (see discussion in Section \ref{sec:onezone-results}).
+Following \citet{johnson_stellar_2021}, we do not implement radial gas flows \citep[e.g.,][]{LaceyFall1985-RadialGasFlows,BilitewskiSchonrich2012-RadialFlows}.
+Stellar populations are also assigned a distance from the midplane according to their age and final radius as described in Appendix C.
+
+\todo{Copied from last paper.} We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
+Following \citet{johnson_stellar_2021}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_\star=0$ for $R_{\rm gal}>R_{\rm SF}$.
+The model has a full radial extent of 20 kpc, allowing a purely migrated population to arise in the outer 4.5 kpc.
+We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
+We summarize these parameters in Table \ref{tab:multizone-parameters}.
+
 \begin{deluxetable*}{Cccl}
@@
         t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
-        N_{\rm Ia}/M_\star  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
-        \hline
-        % Nucleosynthetic yields
-        y_{\rm O}^{\rm CC}  & 0.015     & \ref{sec:yields}  & CCSN yield of O    \\
-        y_{\rm Fe}^{\rm CC} & 0.0012    & \ref{sec:yields}  & CCSN yield of Fe   \\
-        y_{\rm O}^{\rm Ia}  & 0         & \ref{sec:yields}  & SN Ia yield of O       \\
-        y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
         \hline
@@
 The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain.
+This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
+Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau at low metallicity to infer population-averaged yields of $y^{\rm CC}/Z_\odot\approx1$ --- in other words, the scale of SN yields is similar to the Solar abundances.
 % This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
@@
 
-Adopting a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$, the yield set $y/Z_\odot=1$ corresponds to an integrated SN Ia rate of $N_{\rm Ia}/M_\star=\num{1.79e-3}$ M$_\odot^{-1}$, and the higher set $y/Z_\odot=3$ corresponds to $N_{\rm Ia}/M_\star=\num{4.1e-3}$ M$_\odot^{-1}$.
-
-\subsubsection{The SN Ia Delay-Time Distribution}
-\label{sec:dtd}
+The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \todo{(cite)}.
+We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 15--50\% relative to the Solar abundance in order to set the endpoint of our models at ${\rm [O/Fe]}\approx-0.05$ in the Solar neighborhood.
+Models which assume a lower value of $y_{\rm Fe}^{\rm Ia}$, in line with the value for $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot$ found by \citet{maoz_star_2017}, are not able to reach solar [O/Fe] within the disk lifetime.
 
@@
 
+We discuss the implications of using a different DTD in Section \ref{sec:dtd-discussion}.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/yield_outflow.pdf}
+    \caption{We manually adjusted the outflow mass-loading parameter $\eta$ and SN Ia yield $y ^{\rm Ia}_{\rm Fe}$ to match the data in the youngest age bin.
+Key takeaway: the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall.
+In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.}
+    \label{fig:onezone-dtd}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_sfr.pdf}
+    \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
+This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
+    \label{fig:onezone-sfr}
+\end{figure}
+
 \subsection{Outflows}
@@
 
-\subsection{The Two-Infall Star Formation History}
+\subsection{The Gas Supply}
 \label{sec:sfh}
 
-\todo{Copied from last paper.} First proposed by \citet{chiappini_chemical_1997}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
+The infall rate as a function of time and galactocentric radius can generically be described by
+\begin{equation}
+    \label{eq:infall-rate}
+    \dot\Sigma_{\rm in}(t,R_{\rm gal}) = A f_{\rm in}(t|R_{\rm gal}) g(R_{\rm gal}),
+\end{equation}
+where $g(R_{\rm gal})=\Sigma_\star(R_{\rm gal}) / \Sigma_\star(R_{\rm gal}=0)$ is the stellar density gradient, $f_{\rm in}$ is the infall rate over time, and $A$ is the normalization.
+Because we incorporate mass-loaded outflows, $A$ is not analytically solvable, so first we numerically integrate the star formation rate $\dot\Sigma_\star(t,R_{\rm gal})$ and then follow the procedure outlined in Appendix B of \citet{johnson_stellar_2021} to calculate $A$.
+The infall rate is normalized to produce a total disk stellar mass of $(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
+
+The infall rate is described by two successive, exponentially declining bursts in time.
+The first infall component induces the formation of the thick disk, and the second component produces the thin disk.
+At a given galactocentric radius $R_{\rm gal}$, the un-normalized infall rate is
 \begin{equation}
     \label{eq:twoinfall-ifr}
-    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
+    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
 \end{equation}
-% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
-where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{chiappini_chemical_1997,spitoni_galactic_2020,spitoni_apogee_2021}.
-$N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and their ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
+where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm on}$ is the onset time of the second infall epoch, and $f_{2/1}$ is the ratio of the second infall amplitude to the first.
+Because we include outflows, the infall normalization is not analytically solvable.
+Instead, we numerically integrate the infall history and calculate $f_{2/1}$ so that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
 \begin{equation}
-    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}.
+    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_{\Sigma,0} e^{R(1/R_2 - 1/R_1)}.
 \end{equation}
-Following \citet{bland-hawthorn_galaxy_2016}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
-We note that most previous studies which use the two-infall model \citep[e.g.][]{chiappini_chemical_1997,matteucci_new_2006,matteucci_effect_2009,spitoni_galactic_2019} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance.
-We adopt radially-dependent outflows as in \citetalias{johnson_stellar_2021} (see their Section 2.4 for details) for all our SFHs, including two-infall.
-We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.
+We adopt a thick disk scale radius of $R_1=2.0$ kpc, a thin disk scale radius of $R_2=2.5$ kpc, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citet{bland-hawthorn_galaxy_2016}.
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/onezone_params.pdf}
+    \caption{Abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the.
+Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances.
+For consistency, all models use the {\tt yZ1} yield set and assume $\eta=0.4$.
+(a) The first infall timescale $\tau_1$ adjusts the position and spread of the high-$\alpha$ sequence.
+(b) The second infall timescale $\tau_2$ adjusts the width of the low-$\alpha$ peak (separation of the low-$\alpha$ peaks) and the width of the MDF.
+(c) The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr.
+While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions.
+Key takeaway: The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
+    \label{fig:twoinfall-parameters-low-yields}
+\end{figure*}
+
+\subsection{The Star Formation Law}
+
+We run {\tt VICE} in ``infall mode,'' where the gas infall density $\dot\Sigma_{\rm in}$ is specified along with the star formation effieciency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$.
+The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities assuming our star formation law, which is described below.
+The initial gas mass is zero.
 
@@
 
-\section{Exploring the Parameter Space in One-Zone Models}
-\label{sec:onezone-results}
+\section{Multi-Zone Model Results}
+\label{sec:multizone-results}
 
@@
     \centering
-    \includegraphics{figures/onezone_sfr.pdf}
-    \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
-This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
-    \label{fig:onezone-sfr}
+    \includegraphics{figures/abundance_evolution_yields.pdf}
+    \caption{Caption.}
+    \label{fig:abund-evol-yields}
 \end{figure}
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/onezone_params_low_yields.pdf}
-    \caption{Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances.
-For consistency, all models use the {\tt W24mod} yield set and assume $\eta=0.43$.
-(a) The first infall timescale $\tau_1$ adjusts the position and spread of the high-$\alpha$ sequence.
-(b) The second infall timescale $\tau_2$ adjusts the width of the low-$\alpha$ peak (separation of the low-$\alpha$ peaks) and the width of the MDF.
-(c) The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr.
-While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions.
-Key takeaway: The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
-    \label{fig:twoinfall-parameters-low-yields}
-\end{figure*}
-
-% \begin{figure*}
-%     \centering
-%     \includegraphics{figures/onezone_params_high_yields.pdf}
-%     \caption{Caption.}
-%     \label{fig:twoinfall-parameters-high-yields}
-% \end{figure*}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/yield_outflow.pdf}
-    \caption{We manually adjusted the outflow mass-loading parameter $\eta$ and SN Ia yield $y ^{\rm Ia}_{\rm Fe}$ to match the data in the youngest age bin.
-Key takeaway: the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall.
-In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.}
-    \label{fig:onezone-dtd}
-\end{figure}
-
-\section{Multi-Zone Models}
-\label{sec:multizone-results}
 
@@
 \label{sec:discussion}
+
+\subsection{The SN Ia Delay-Time Distribution}
+\label{sec:dtd-discussion}
 
@@
 \end{figure}
+
+\subsection{Radial Gas Flows}
+\label{sec:radial-flows}
 

### 2025-01-24 src/tex/ms.tex
Updates from Overleaf

@@
     \includegraphics{figures/onezone_params.pdf}
-    \caption{Abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the.
-Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances.
-For consistency, all models use the {\tt yZ1} yield set and assume $\eta=0.4$.
-(a) The first infall timescale $\tau_1$ adjusts the position and spread of the high-$\alpha$ sequence.
-(b) The second infall timescale $\tau_2$ adjusts the width of the low-$\alpha$ peak (separation of the low-$\alpha$ peaks) and the width of the MDF.
-(c) The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr.
+    \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters.
+In each panel, one parameter is varied according to the legend while the other two are held fixed.
+The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b).
+The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
+All models use the {\tt yZ1} yield set and assume $\eta=0.4$.
+{\bf (a)} The first infall timescale $\tau_1$ primarily affects the stellar distribution along the high-$\alpha$ sequence.
+{\bf (b)} The second infall timescale $\tau_2$ affects the [O/Fe] distribution of the low-$\alpha$ sequence and the width of the MDF.
+{\bf (c)} The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr.
 While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions.
-Key takeaway: The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
+{\bf Key takeaway:} The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
     \label{fig:twoinfall-parameters-low-yields}

### 2025-01-24 src/tex/ms.tex

@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-    \includegraphics{figures/abundance_evolution_yields.pdf}
-    \caption{Caption.}
-    \label{fig:abund-evol-yields}
-\end{figure}
+    \includegraphics{figures/abundance_evolution.pdf}
+    \caption{Stellar age--abundance relations produced by select multi-zone models.
+Each point represents a stellar population drawn from the Solar neighborhood near the mid-plane ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq |z| \leq 0.5$ kpc) and is color-coded by its birth radius.
+For visual clarity, we plot a only random mass-weighted sample of \num{10000} points in each panel.
+The dashed line plots the ISM abundance at $R_{\rm gal}=8$ kpc over time.
+The black points plot the median abundance of stars in 2 Gyr-wide age bins, and the vertical error bars represent the 16th and 84th percentiles of the age distribution.
+Similarly, the red points with error bars plot the median APOGEE abundances for stars with age estimates from \citet{leung_variational_2023}.
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5$ kpc; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.
+{\bf Key takeaway:} the fiducial model shows two discrepancies with the data: a major dilution event at a lookback time of $\sim9$ Gyr and non-zero abundance evolution at late times.
+Only model (b) with higher yields can mitigate both of these issues.}
+    \label{fig:abundance-evolution}
+\end{figure*}
 

### 2025-01-27 src/tex/ms.tex
Updates from Overleaf

@@
 
+We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation effieciency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$.
+The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities according to our star formation law, which is described in Section \ref{sec:sf-law}, and assuming zero initial gas mass in all zones.
+
 The infall rate as a function of time and galactocentric radius can generically be described by
@@
 Because we incorporate mass-loaded outflows, $A$ is not analytically solvable, so first we numerically integrate the star formation rate $\dot\Sigma_\star(t,R_{\rm gal})$ and then follow the procedure outlined in Appendix B of \citet{johnson_stellar_2021} to calculate $A$.
-The infall rate is normalized to produce a total disk stellar mass of $(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
+The infall rate is normalized to produce a total disk stellar mass of $(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and to match the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
 
@@
 where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm on}$ is the onset time of the second infall epoch, and $f_{2/1}$ is the ratio of the second infall amplitude to the first.
-Because we include outflows, the infall normalization is not analytically solvable.
-Instead, we numerically integrate the infall history and calculate $f_{2/1}$ so that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
+We calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
 \begin{equation}
@@
 \subsection{The Star Formation Law}
-
-We run {\tt VICE} in ``infall mode,'' where the gas infall density $\dot\Sigma_{\rm in}$ is specified along with the star formation effieciency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$.
-The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities assuming our star formation law, which is described below.
-The initial gas mass is zero.
+\label{sec:sf-law}
 
@@
 
+\begin{figure*}
+    \centering
+    \includegrac
+\end{figure*}
+
 \section{Discussion}
@@
     \includegraphics{figures/delay_time_distribution.pdf}
-    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr.
-Key takeaway: the size of the loop can be reduced by using an SN Ia DTD with more prompt events.
-However, this messes up the location of the high-alpha sequence.}
+    \caption{The effect of the SN Ia delay-time distribution (DTD) on chemical abundance tracks and stellar distributions.
+{\it Left:} The relative SN Ia rate as a function of time after star formation for each DTD model.
+The points illustrate the median delay times for each DTD.
+{\it Right:} Output of one-zone models which assume different SN Ia DTDs with the {\tt yZ2} yield set.
+The infall parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=10$ Gyr, and $\tau_{\rm on}=3$ Gyr.
+{\bf Key takeaway:} the extent of the low-$\alpha$ sequence can be reduced by a more prompt SN Ia DTD, but the high-$\alpha$ sequence is also shifted to a more metal-poor regime.}
     \label{fig:dtd}

### 2025-01-27 src/tex/ms.tex
Updates from Overleaf

@@
     \centering
-    \includegrac
+    \includegraphics{src/tex/figures/ofe_df_yields.pdf}
+    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a, b) and as observed by APOGEE (c).
+Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows.
+Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
+{\bf (a)} Multi-zone model output assuming the {\tt yZ1} yield set.
+{\bf (b)} Model output assuming the {\tt yZ2} yield set.
+{\bf (c)} The distributions from APOGEE DR17 for reference.
+{\bf Key takeaway:} }
+    \label{fig:ofe-df-yields}
 \end{figure*}

### 2025-01-29 src/tex/ms.tex
Updates from Overleaf

@@
 The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks.
-The infall history of any given region of the disk is described by two successive, exponentially declining bursts, whose timescale may vary as a function of radius.
-The first infall, which forms the thick disk, has a short timescale, typically on the order of $\sim0.1-1$ Gyr.
-The second infall forms the thin disk and has a much longer timescale, typically $\sim4-10$ Gyr.
+The infall history of any given region of the disk is described by two successive, exponentially declining bursts, which explain the origin of the thick and thin disks respectively.
 
@@
 \begin{deluxetable*}{Cccl}
-    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).
-We omit some parameters that are unchanged from \citetalias{johnson_stellar_2021}; see their Table 1 for details.\label{tab:multizone-parameters}}
+    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:multizone-parameters}}
     \tablehead{
@@
         % Multi-zone model parameters
-        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-results} & Galactocentric radius \\
-        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-results} & Width of each concentric ring \\
-        \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
-        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
-        z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
-        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
-        \Delta t        & 10 Myr    & \ref{sec:multizone-results} & Time-step size \\
-        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-results} & Disk lifetime \\
-        n               & 8         & \ref{sec:multizone-results} & Number of stellar populations formed per ring per time-step \\
-        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-results} & Maximum radius of star formation \\
-        M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
-        \dot M_r    & continuous    & \ref{sec:multizone-results} & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
-        \hline
-        % DTD
-        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay-time distribution of Type Ia supernovae \\
-        t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
-        \hline
+        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength \\
+        % Outflows
+        R_\eta          & 5.4 kpc   & \ref{sec:outflows}    & Outflow scale radius \\
+        % Yields
+        y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
+        f_{\rm Ia}(t)   & Plateau   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
+        t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
         % Star formation histories
-        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the inside-out SFR \\
-        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
-        \tau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
-        \tau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
-        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst infall rate \\
-        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall infall rate \\
-        \hline
-        % One-zone parameters
-        \tau_\star                    & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
-        \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
-        \tau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
+        % f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate}   & \ref{sec:sfh} & Time-dependence of the gas infall rate \\
+        \tau_1          & 1 Gyr     & \ref{sec:sfh}     & Timescale of the first infall epoch \\
+        \tau_2          & 15 Gyr    & \ref{sec:sfh}     & Timescale of the second infall epoch \\
+        t_{\rm on}      & 4.2       & \ref{sec:sfh}     & Onset time of the second infall epoch \\
+        f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
+        {\rm [X/H]}_{\rm CGM}   & Pristine  &           & Pre-enrichment of infalling gas
     \enddata
@@
 
+\begin{equation}
+    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
+\end{equation}
+
+\begin{equation}
+    \eta_\odot = \frac{y_{\rm O}^{\rm CC}}{Z_{\rm O,\odot}} - 1 + r
+\end{equation}
+
+\begin{equation}
+    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}
+\end{equation}
+
 \subsection{The Gas Supply}
@@
 \end{equation}
-We adopt a thick disk scale radius of $R_1=2.0$ kpc, a thin disk scale radius of $R_2=2.5$ kpc, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citet{bland-hawthorn_galaxy_2016}.
+We adopt a thick disk scale radius of $R_1=2.0$ kpc, a thin disk scale radius of $R_2=2.5$ kpc, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
+
+The parameters of Equation \ref{eq:infall-rate} have an important effect on the model output.
+Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1$ Gyr, $\tau_2\sim4-10$ Gyr, and $t_{\rm on}\sim4$ Gyr.
+Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying each of these parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
+The first infall timescale $\tau_1$ primarily affects the stellar distribution along the high-$\alpha$ sequence, with negligible effect on the low-$\alpha$ sequence (a).
+On the other hand, the second infall timescale $\tau_2$ controls the width of the MDF and the [O/Fe] distribution of the low-$\alpha$ sequence, with a shorter $\tau_2$ producing a distribution which is skewed to higher [O/Fe] (b).
+The onset time $t_{\rm on}$ strongly affects the overall stellar abundance distribution for values $t_{\rm on}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic loop characteristic of the two-infall model.
+For $t_{\rm on}>2$ Gyr, varying $t_{\rm on}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
+We find that $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions.
 
@@
 The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
-All models use the {\tt yZ1} yield set and assume $\eta=0.4$.
-{\bf (a)} The first infall timescale $\tau_1$ primarily affects the stellar distribution along the high-$\alpha$ sequence.
-{\bf (b)} The second infall timescale $\tau_2$ affects the [O/Fe] distribution of the low-$\alpha$ sequence and the width of the MDF.
-{\bf (c)} The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr.
-While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions.
-{\bf Key takeaway:} The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
-    \label{fig:twoinfall-parameters-low-yields}
+All models use the {\tt yZ1} yield set and assume $\eta=0.4$.}
+    \label{fig:twoinfall-parameters}
 \end{figure*}
@@
 \todo{Talk about the implications of this prefactor or reference a future section which discusses this.}
+
+\subsection{Stellar Migration}
+\label{sec:migration}
+
+\begin{equation}
+    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61}
+    \label{eq:radial-migration}
+\end{equation}
+
+\begin{equation}
+    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z(\tau,R_{\rm final})}\Big).
+    \label{eq:sech-pdf}
+\end{equation}
+
+\begin{equation}
+    h_z(\tau,R_{\rm final}) = (h_{z,s}/e^2) \exp(\tau/\tau_s + R_{\rm final}/R_s)
+    \label{eq:scale-height}
+\end{equation}
+where $h_{z,s}=0.24$ kpc is the scale height at $\tau_s=7$ Gyr and $R_s=6$ kpc.
 
@@
 
+\subsection{Stellar Abundance Distributions}
+
+\begin{figure*}
+    \centering
+    \includegraphics{src/tex/figures/ofe_df_yields.pdf}
+    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (d).
+Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows.
+Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
+The median APOGEE abundance uncertainties were forward-modeled onto the model outputs.
+For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
+Model (a) assumes the fiducial parameters and the {\tt yZ1} yield set, whereas models (b--d) assume the {\tt yZ2} yield set.
+Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.
+The distributions from APOGEE DR17 are plotted in column (e) for reference.
+{\bf Key takeaway:} The high-yield case produces a peak at intermediate [O/Fe] which is prominent in most galactic regions, which can be mitigated by pre-enriched infall.}
+    \label{fig:ofe-df-yields}
+\end{figure*}
+
+\subsection{Age--Abundance Relations}
+
 \begin{figure*}
@@
     \label{fig:abundance-evolution}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics{src/tex/figures/ofe_df_yields.pdf}
-    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a, b) and as observed by APOGEE (c).
-Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows.
-Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
-{\bf (a)} Multi-zone model output assuming the {\tt yZ1} yield set.
-{\bf (b)} Model output assuming the {\tt yZ2} yield set.
-{\bf (c)} The distributions from APOGEE DR17 for reference.
-{\bf Key takeaway:} }
-    \label{fig:ofe-df-yields}
 \end{figure*}

### 2025-01-30 src/tex/ms.tex
Manuscript updates

@@
 
-\todo{Copied from last paper.} We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr.
+\todo{Copied from last paper.} We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm final}=13.2$ Gyr.
 Following \citet{johnson_stellar_2021}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_\star=0$ for $R_{\rm gal}>R_{\rm SF}$.
@@
     \startdata
-        % Multi-zone model parameters
-        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength \\
-        % Outflows
-        R_\eta          & 5.4 kpc   & \ref{sec:outflows}    & Outflow scale radius \\
         % Yields
         y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
+        N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
         f_{\rm Ia}(t)   & Plateau   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
-        t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
+        % t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
         % Star formation histories
+        % Outflows
+        \eta_\odot      & 0.4       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
+        R_\eta          & 5.4 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
         % f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate}   & \ref{sec:sfh} & Time-dependence of the gas infall rate \\
@@
         \tau_2          & 15 Gyr    & \ref{sec:sfh}     & Timescale of the second infall epoch \\
-        t_{\rm on}      & 4.2       & \ref{sec:sfh}     & Onset time of the second infall epoch \\
+        t_{\rm max}      & 4.2      & \ref{sec:sfh}     & Time of maximum gas infall (onset of second infall) \\
         f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
-        {\rm [X/H]}_{\rm CGM}   & Pristine  &           & Pre-enrichment of infalling gas
+        {\rm [X/H]}_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
+        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength
     \enddata
@@
 This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau at low metallicity to infer population-averaged yields of $y^{\rm CC}/Z_\odot\approx1$ --- in other words, the scale of SN yields is similar to the Solar abundances.
+Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$ --- in other words, the scale of SN yields relative to the Solar abundance is of order unity.
 % This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
@@
 
-The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \todo{(cite)}.
-We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 15--50\% relative to the Solar abundance in order to set the endpoint of our models at ${\rm [O/Fe]}\approx-0.05$ in the Solar neighborhood.
-Models which assume a lower value of $y_{\rm Fe}^{\rm Ia}$, in line with the value for $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot$ found by \citet{maoz_star_2017}, are not able to reach solar [O/Fe] within the disk lifetime.
+We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the {\tt yZ1} and {\tt yZ2} yield sets, respectively, to ensure our models could reach ${\rm [O/Fe]}\approx0.0$ by the end time.
+The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\bar m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009} \todo{(are there more recent citations?)}.
+The rate for the {\tt yZ1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
+The rate for the {\tt yZ2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}.
 
@@
 \end{equation}
-where $t_D$ is the minimum SN Ia delay time, $t_{\rm max}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}$ is the un-normalized form of the DTD.
+where $t_D=40$ Myr is the minimum SN Ia delay time, $t_{\rm max}=13.2$ Gyr is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
 Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
@@
 \end{equation}
+We discuss the implications of using a different DTD in Section \ref{sec:dtd-discussion}.
 
-We discuss the implications of using a different DTD in Section \ref{sec:dtd-discussion}.
+\todo{Compare these yields to previous studies.}
 
@@
 
+Most of the previous two-infall studies assume no mass-loaded outflows.
+Even in studies such as \citet{palicio_analytic_2023} which do incorporate Galactic winds, they are relatively weak ($\eta\approx0.2$).
+
+\todo{Motivate our use of outflows. Connect to James' equilibrium paper.}
+
+\citet{weinberg_equilibrium_2017} showed that in the limit of continuous star formation, the ISM abundance approaches an equilibrium which is determined by the balance of yields, outflows, and star formation.
+We calculate the mass-loading factor required to reach equilibrium at the Solar abundance as
+\begin{equation}
+    \eta_\odot = y_{\rm O}^{\rm CC} / Z_{\rm O,\odot} - 1 + r + \tau_\star / \tau_{\rm SFH},
+\end{equation}
+where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, and $\tau_{\rm SFH}$ is the star formation timescale.
+
+We adopt a fiducial prescription for the outflow mass-loading factor which increases exponentially with radius:
 \begin{equation}
@@
 \end{equation}
-
+where $R_\odot=8$ kpc. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
 \begin{equation}
-    \eta_\odot = \frac{y_{\rm O}^{\rm CC}}{Z_{\rm O,\odot}} - 1 + r
+    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}.
 \end{equation}
-
-\begin{equation}
-    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}
-\end{equation}
+We adopt $R_\eta=5.4$ kpc as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.08$ dex kpc$^{-1}$.
+\todo{Motivate exponential scale radius.}
 
@@
 
-We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation effieciency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$.
-The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities according to our star formation law, which is described in Section \ref{sec:sf-law}, and assuming zero initial gas mass in all zones.
+We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation effieciency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time.
+The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities according to our star formation law, which is described in Section \ref{sec:sf-law}, assuming zero initial gas mass in all zones.
 
@@
     \label{eq:twoinfall-ifr}
-    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
+    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
 \end{equation}
-where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm on}$ is the onset time of the second infall epoch, and $f_{2/1}$ is the ratio of the second infall amplitude to the first.
+where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall, and $f_{2/1}$ is the ratio of the second infall amplitude to the first.
 We calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
@@
 
-The parameters of Equation \ref{eq:infall-rate} have an important effect on the model output.
-Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1$ Gyr, $\tau_2\sim4-10$ Gyr, and $t_{\rm on}\sim4$ Gyr.
+The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model.
+Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1$ Gyr, $\tau_2\sim4-10$ Gyr, and $t_{\rm max}\sim4$ Gyr.
 Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying each of these parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
@@
 On the other hand, the second infall timescale $\tau_2$ controls the width of the MDF and the [O/Fe] distribution of the low-$\alpha$ sequence, with a shorter $\tau_2$ producing a distribution which is skewed to higher [O/Fe] (b).
-The onset time $t_{\rm on}$ strongly affects the overall stellar abundance distribution for values $t_{\rm on}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic loop characteristic of the two-infall model.
-For $t_{\rm on}>2$ Gyr, varying $t_{\rm on}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
+The time of maximum infall $t_{\rm max}$ strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic loop characteristic of the two-infall model.
+For $t_{\rm max}>2$ Gyr, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
 We find that $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions.
@@
 \end{figure*}
+
+In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
+However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, either from gas stripped from dwarf galaxies or from SNe in the halo \todo{(citations; any measurements of CGM metallicity?)}.
+For this reason, we also test cases where the infalling gas is pre-enriched and its metallicity is described by
+\begin{equation}
+    \label{eq:pre-enrichment}
+    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{{\rm [X/H]}_{\rm CGM}}.
+\end{equation}
+In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2$ Gyr and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$.
+We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.
 
@@
     \begin{cases}
-        0.5, & t < t_{\rm on} \\
-        1.0, & t \ge t_{\rm on}.
+        0.5, & t < t_{\rm max} \\
+        1.0, & t \ge t_{\rm max}.
     \end{cases}
@@
 
+The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
 \begin{equation}
-    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61}
+    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61},
     \label{eq:radial-migration}
 \end{equation}
+where we adopt $\sigma_{\rm RM8}=2.68$ kpc as the fiducial value for the strength of radial migration.
+This is smaller than the value of $\sigma_{\rm RM8}=3.6$ kpc found by \citet{frankel_measuring_2018}, but in \todo{Section X} we explore the effect of a stronger migration prescription.
 
+All stellar populations are born at the Galactic midplane and are assigned a final midplane distance $z$ drawn from the distribution
 \begin{equation}
-    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z_{\rm final}}{2 h_z(\tau,R_{\rm final})}\Big).
+    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big),
     \label{eq:sech-pdf}
 \end{equation}
-
+where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The width of the distribution $h_z$ is given by
 \begin{equation}
-    h_z(\tau,R_{\rm final}) = (h_{z,s}/e^2) \exp(\tau/\tau_s + R_{\rm final}/R_s)
+    h_z(\tau,R_{\rm final}) = \Big(\frac{0.24\,{\rm kpc}}{e^2}\Big) \exp\Big(\frac{\tau}{7\,{\rm Gyr}} + \frac{R_{\rm final}}{6\,{\rm kpc}}\Big).
     \label{eq:scale-height}
 \end{equation}
-where $h_{z,s}=0.24$ kpc is the scale height at $\tau_s=7$ Gyr and $R_s=6$ kpc.
+We note that the final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
+
+The parameters of Equations \ref{eq:radial-migration} and \ref{eq:scale-height} were chosen to fit the stellar migration patterns in the {\tt h277} hydrodynamical simulation \citep{christensen_implementing_2012}.
+A more complete discussion of the migration scheme and its consequences can be found in Appendix C of \citet{dubay_galactic_2024}.
 
@@
     \centering
-    \includegraphics{src/tex/figures/ofe_df_yields.pdf}
+    \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
     \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (d).

### 2025-01-30 src/scripts/yield_outflow.py
update yield-outflow plot

@@ -25,8 +25,8 @@ FIRST_INFALL = 1
 SECOND_INFALL = 15.
 ONSET = 4.2
 
-OH_LIM = (-1.2, 0.5)
-FEH_LIM = (-1.2, 0.5)
+OH_LIM = (-1.1, 0.6)
+FEH_LIM = (-1.1, 0.6)
 OFE_LIM = (-0.15, 0.5)
 
 
@@ -61,33 +61,33 @@ def main():
                  yerr=(oh_bins[0.5] - oh_bins[0.16], 
                        oh_bins[0.84] - oh_bins[0.5]),
                  linestyle='none', c=data_color, capsize=1, marker='.',
-                 zorder=0, label='Median (L23)')
+                 zorder=0, label='APOGEE')
     feh_bins = local_sample.binned_intervals('FE_H', 'L23_AGE', age_bins)
     ax3.errorbar(age_bin_centers, feh_bins[0.5], xerr=0.5,
                  yerr=(feh_bins[0.5] - feh_bins[0.16], 
                        feh_bins[0.84] - feh_bins[0.5]),
                  linestyle='none', c=data_color, capsize=1, marker='.',
-                 zorder=0, label='Median (L23)')
+                 zorder=0)
     ofe_bins = local_sample.binned_intervals('O_FE', 'L23_AGE', age_bins)
     ax5.errorbar(age_bin_centers, ofe_bins[0.5], xerr=0.5,
                  yerr=(ofe_bins[0.5] - ofe_bins[0.16], 
                        ofe_bins[0.84] - ofe_bins[0.5]),
                  linestyle='none', c=data_color, capsize=1, marker='.',
-                 zorder=0, label='Median (L23)')
+                 zorder=0)
     
     # Plot APOGEE abundance distributions in marginal panels
     oh_df, bin_edges = local_sample.mdf(col='O_H', range=OH_LIM, 
-                                        smoothing=0.05)
+                                        smoothing=0.1)
     ax0.plot(oh_df / max(oh_df), get_bin_centers(bin_edges),
-             color=data_color, linestyle='-', marker=None)
+             color=data_color, linestyle='-', linewidth=2, marker=None)
     feh_df, bin_edges = local_sample.mdf(col='FE_H', range=FEH_LIM, 
-                                         smoothing=0.05)
+                                         smoothing=0.1)
[…]

### 2025-01-30 src/tex/ms.tex

@@
     \includegraphics{figures/yield_outflow.pdf}
-    \caption{We manually adjusted the outflow mass-loading parameter $\eta$ and SN Ia yield $y ^{\rm Ia}_{\rm Fe}$ to match the data in the youngest age bin.
-Key takeaway: the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall.
-In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.}
+    \caption{{\bf Key takeaway:} the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall.
+In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.
+\todo{Replace APOGEE medians with modes and errors on the mode}}
     \label{fig:onezone-dtd}

### 2025-01-31 src/tex/ms.tex

@@
 
+Figure \ref{fig:yield-outflow} illustrates the effect of the yield scaling on the abundance evolution in one-zone models.
+All models feature a rapid dilution of the ISM metallicity by $\sim0.5-0.8$ dex, visible in the top two panels, brought on by the infall of pristine gas at $t_{\rm max}$.
+For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the present day.
+The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5$ Gyr ago.
+However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.
+
+Figure \ref{fig:yield-outflow} also indicates the mode of the APOGEE abundance distributions in 1 Gyr-wide age bins.
+As explained by \citet{johnson_milky_2024}, the mode is expected to be less sensitive to the effects of radial migration than other statistical measures.
+The data show that the evolution in [O/H] is close to flat over the past 5 Gyr.
+The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model shows significant evolution of $\sim0.2$ dex during the same time period.
+The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia.
+Between lookback times of $\sim5-9$ Gyr, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.
+The
+
 \begin{figure}
@@
     \includegraphics{figures/yield_outflow.pdf}
-    \caption{{\bf Key takeaway:} the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall.
-In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.
-\todo{Replace APOGEE medians with modes and errors on the mode}}
-    \label{fig:onezone-dtd}
+    \caption{The abundance evolution of three one-zone models with different yield and outflow settings.
+Table \ref{tab:yields} presents the population-averaged yields for each model.
+The gray points with error bars indicate the mode of the APOGEE abundances from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq0.5$ kpc) binned by the \citet{leung_variational_2023} age estimates.}
+    \label{fig:yield-outflow}
 \end{figure}

### 2025-01-31 src/tex/ms.tex
Updates from Overleaf

@@
 Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$ --- in other words, the scale of SN yields relative to the Solar abundance is of order unity.
-% This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-We adopt the yields of \citet{weinberg_scale_2023}, who use a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau to infer population-averaged yields.
-The only difference here is that we assume that $20\%$ of Si in the Sun is produced by SNe Ia, which reduces the Si plateau to [Si/Fe]$_{\rm cc}=0.35$ and results in a non-zero value for $y_{\rm SI}^{\rm cc}$, unlike in \citet{weinberg_scale_2023}.
-Our yields are presented in Table \ref{tab:yields}.
 
@@
 Between lookback times of $\sim5-9$ Gyr, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.
-The
+The [O/Fe] evolution of all three models is nearly identical over the past 5 Gyr, and shows a similar evolution to the data apart from a $\sim0.05$ dex offset.
+\todo{Is this offset a problem?
+I could raise the SN Ia yields, but the global distributions would not match quite as well.}
 
@@
 Table \ref{tab:yields} presents the population-averaged yields for each model.
-The gray points with error bars indicate the mode of the APOGEE abundances from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq0.5$ kpc) binned by the \citet{leung_variational_2023} age estimates.}
+The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq0.5$ kpc) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
     \label{fig:yield-outflow}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_sfr.pdf}
-    \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
-This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
-    \label{fig:onezone-sfr}
 \end{figure}
@@
 We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/onezone_sfr.pdf}
+    \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
+This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
+    \label{fig:onezone-sfr}
+\end{figure}
 

### 2025-01-31 src/tex/ms.tex

@@
 {\bf Key takeaway:} The high-yield case produces a peak at intermediate [O/Fe] which is prominent in most galactic regions, which can be mitigated by pre-enriched infall.}
-    \label{fig:ofe-df-yields}
+    \label{fig:ofe-df}
 \end{figure*}
+
+As noted by \citet{dubay_galactic_2024} two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+Figure \ref{fig:ofe-df} compares [O/Fe] distributions across the Galactic disk produced by four different multi-zone models with the distributions observed in APOGEE DR17.
+For the fiducial model (a) with $y/Z_\odot=1$, the latter two peaks are close together and the overall effect is similar to the observed distribution.
+With a higher yield set, however, there is a $\sim0.2$ dex separation between the low- and intermediate-$\alpha$ peaks, because the CCSN element production after the second infall is more efficient.
+As a result, model (b) predicts a high density of stars in the APOGEE ``trough.''
 

### 2025-01-31 src/scripts/apogee_regions_table.py
add table from last paper

@@ -1,0 +1,39 @@
+"""
+This script generates a LaTeX table which reports the number of APOGEE stars
+in each Galactic region.
+"""
+
+import pandas as pd
+import paths
+from apogee_sample import APOGEESample
+from _globals import GALR_BINS, ABSZ_BINS
+
+
+def main():
+    sample = APOGEESample.load()
+    data = sample.data
+    # Count number of targets in each region bounded by Rgal and |z|
+    counts = data.groupby([pd.cut(data['GALR'], GALR_BINS), 
+                           pd.cut(data['GALZ'], ABSZ_BINS)], 
+                          observed=False)['APOGEE_ID'].count()
+    # Unstack the above multi-indexed Series into a DataFrame
+    pivot = counts.unstack(level=0).iloc[::-1] # invert |z| bins
+    # Prettify row, column labels
+    idx = [f'${r}$ kpc' for r in pivot.index]
+    pivot.index = pd.Series(idx, name='$|z|\\in$')
+    cols = [f'${c}$ kpc' for c in pivot.columns]
+    pivot.columns = pd.Series(cols, name='$R_{\\rm gal}\\in$')
+    # Convert to LaTeX table
+    latex_table = pivot.style.to_latex(column_format='r|cccccc')
+    # Add horizontal lines
+    latex_table_list = latex_table.split('\n')
+    latex_table_list.insert(1, '\\hline\\hline')
+    latex_table_list.insert(4, '\\hline')
+    latex_table_list.insert(-2, '\\hline')
+    latex_table = '\n'.join(latex_table_list)
+    # Write to output file
+    with open(paths.output / 'apogee_regions_table.tex', 'w') as f:
+        f.write(latex_table)
+
+if __name__ == '__main__':
+    main()

### 2025-01-31 src/tex/ms.tex
Updates from Overleaf

@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
+        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages} \\
+        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
+        $|z|$               & $|z| < 2$ kpc                 & Eliminate halo stars \\
         \hline
-        $\sigma({\rm [Fe/H]})$ & $9.2\times10^{-3}$ & Median uncertainty in [Fe/H] \\
-        $\sigma({\rm [O/Fe]})$ & $1.8\times10^{-2}$ & Median uncertainty in [O/Fe] \\
-        $\sigma($log(Age/Gyr)) & $0.10$ & Median age uncertainty \citepalias{leung_variational_2023} \\
+    \end{tabular}
+\end{table*}
+
+\begin{table*}
+    \centering
+    \caption{Median and dispersion in APOGEE parameter uncertainties.}
+    \label{tab:uncertainties}
+    \begin{tabular}{lcc}
+        \hline\hline
+        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Median Uncertainty} & \multicolumn{1}{c}{Uncertainty Dispersion ($95\%-5\%$)} \\
+        \hline
+        [Fe/H]          & $0.0089$   & $0.0060$ \\
+        ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
+        log(Age/Gyr)    & $0.10$     & $0.16$ \\
         \hline
@@
 We restrict our sample to red giant branch and red clump stars with high-quality spectra.
-Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{Hayden2015-ChemicalCartography}.
-This produces a final sample of \input{output/sample_size.txt}stars with [O/Fe] and [Fe/H] abundance measurements.
-APOGEE stars are matched with their Bailer-Jones photo-geometric distance estimate from \textit{Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021}, which we use to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$.
+Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{hayden_chemical_2015}.
+This produces a final sample of \input{output/sample_size.txt} stars with calibrated [O/Fe] and [Fe/H] abundance measurements.
+We make use of the {\it Gaia} Early Data Release 3 (EDR3) data \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the catalog by the APOGEE team.
+Specifically, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$, assuming a Sun--Galactic center distance $R_\odot=8.122$ kpc \citep{gravity_collaboration_detection_2018} and height of the Sun above the midplane $z_\odot=20.8$ pc \citep{bennett_vertical_2019}.
+Table \ref{tab:apogee-regions} lists the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$.
+For some Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, the median distance error exceeds 1 kpc but remains within our bin width of 2 kpc, and the vast majority of stars have much smaller distance uncertainties.
 
 We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
-Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{Mackereth2019-astroNN-Ages}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt}APOGEE stars with age estimates.
-We note that we use the full sample of \input{output/sample_size.txt}APOGEE stars unless we explicitly compare to age estimates.
-Table \ref{tab:sample} also presents the median uncertainties in the data for [Fe/H], [O/Fe], and age.
+Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{mackereth_dynamical_2019}.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt} APOGEE stars with age estimates.
+We note that we use the full sample of \input{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates.
+Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).
 
@@
 Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.
-The distributions from APOGEE DR17 are plotted in column (e) for reference.
-{\bf Key takeaway:} The high-yield case produces a peak at intermediate [O/Fe] which is prominent in most galactic regions, which can be mitigated by pre-enriched infall.}
+The distributions from APOGEE DR17 are plotted in column (e) for reference.}
     \label{fig:ofe-df}
@@
 
-As noted by \citet{dubay_galactic_2024} two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+As discussed in Section \ref{sec:sfh}, the two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
 Figure \ref{fig:ofe-df} compares [O/Fe] distributions across the Galactic disk produced by four different multi-zone models with the distributions observed in APOGEE DR17.
@@
 As a result, model (b) predicts a high density of stars in the APOGEE ``trough.''
+
+In columns (c) and (d) of Figure \ref{fig:ofe-df}, we attempt to mitigate the issue of the intermediate-$\alpha$ peak for the $y/Z_\odot=2$ yield set.
+Model (c) switches out our fiducial DTD with a power-law DTD, which decreases the timescale for Fe production (see Figure \ref{fig:dtd}).
+However, as shown by \citet{dubay_galactic_2024}, models with a power-law DTD struggle to reproduce the high-$\alpha$ sequence for a wide range of star formation histories, and the results are no different for this two-infall model.
+Finally, in model (d) the metallicity of the infalling gas increases to ${\rm [X/H]}_{\rm CGM}=-0.7$ at late times, which results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
+We assume that the infalling gas has ${\rm [O/Fe]}=0$ at all times; an alternate run with ${\rm [O/Fe]}=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
+In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.
 

### 2025-02-03 src/scripts/apogee_sample.py
add [C/N] age cuts

@@ -8,8 +8,10 @@ from numbers import Number
 from pathlib import Path
 import numpy as np
 import pandas as pd
+from astropy.table import Table
 import paths
-from utils import fits_to_pandas, box_smooth, kde2D, galactic_to_galactocentric, quad_add
+from utils import box_smooth, kde2D, galactic_to_galactocentric, quad_add, \
+    decode, split_multicol
 from stats import skewnormal_mode_sample, jackknife_summary_statistic
 from _globals import RANDOM_SEED
 
@@ -17,7 +19,7 @@ from _globals import RANDOM_SEED
 GALR_LIM = (3., 15.)
 ABSZ_LIM = (0., 2.)
 # Data file names
-ALLSTAR_FNAME = 'allStarLite-dr17-synspec_rev1.fits'
+ALLSTAR_FNAME = 'allStar-dr17-synspec_rev1.fits'
 LEUNG23_FNAME = 'nn_latent_age_dr17.csv'
 # Coefficients for [C/N] age fit polynomial
 CN_AGE_COEF = np.array([-1.90931538,  0.75218328,  0.25786775,  0.22440967, 
@@ -154,11 +156,10 @@ class APOGEESample:
             # Download DR17 allStar file from SDSS server
             if verbose: 
                 print('Downloading allStar file (this will take a few minutes)...')
-            # get_allStar_dr17()
             url_write('https://data.sdss.org/sas/dr17/apogee/spectro/aspcap/dr17/synspec_rev1/%s' \
                       % ALLSTAR_FNAME, savedir=data_dir)
         if verbose: print('Importing allStar file...')
-        apogee_catalog = fits_to_pandas(apogee_catalog_path, hdu=1)
+        apogee_catalog = APOGEESample.allStar_to_pandas(apogee_catalog_path)
         # Add ages from row-matched datasets BEFORE any cuts
         # Add ages from Leung et al. (2023)
         leung23_catalog_path = data_dir / LEUNG23_FNAME
@@ -166,7 +167,6 @@ class APOGEESample:
             # Download Leung+ 2023 data from GitHub
             if verbose:
                 print('Downloading Leung et al. (2023) age data...')
-            # get_Leung2023_ages()
             url_write('https://raw.githubusercontent.com/henrysky/astroNN_ages/main/%s.gz' \
                       % LEUNG23_FNAME, savedir=data_dir)
[…]

### 2025-02-03 src/scripts/utils.py

@@ -216,6 +216,37 @@ def fits_to_pandas(path, **kwargs):
     return df
 
 
+def split_multicol(multicol, names=[]):
+    """
+    Split a multi-dimensional column from an Astropy table into a DataFrame.
+    
+    Parameters
+    ----------
+    multicol : astropy Table multidimensional column
+    names : list, optional
+        List of column names.
+    
+    Returns
+    -------
+    pandas.DataFrame
+    """
+    # Make sure it's a multidimensional column
+    if len(multicol.shape) != 2:
+        raise ValueError('Input column has wrong dimensionality.')
+    # Generate column names if needed
+    if names == []:
+        names = [multicol.name + str(i) for i in range(multicol.shape[1])]
+    if len(names) != multicol.shape[1]:
+        raise ValueError('Length of names does not match number of columns.')
+    # Convert to DataFrame
+    # This is kind of dumb but I needed to avoid an "endianness" problem
+    data = np.array(multicol.data)
+    data_dict = dict()
+    for i in range(multicol.shape[1]):
+        data_dict[names[i]] = list(data[:,i])
+    return pd.DataFrame(data_dict)
+
+
 def decode(df):
     """
     Decode DataFrame with byte strings into ordinary strings.

### 2025-02-03 src/tex/ms.tex

@@
 The disk is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
-Stellar populations migrate radially under the prescription we describe in Appendix C, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing (see discussion in Section \ref{sec:onezone-results}).
-Following \citet{johnson_stellar_2021}, we do not implement radial gas flows \citep[e.g.,][]{LaceyFall1985-RadialGasFlows,BilitewskiSchonrich2012-RadialFlows}.
+Stellar populations migrate radially under the prescription we describe in Appendix C, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing.
+Following \citet{johnson_stellar_2021}, we do not implement radial gas flows \citep[e.g.,][]{lacey_chemical_1985,bilitewski_radial_2012}.
 Stellar populations are also assigned a distance from the midplane according to their age and final radius as described in Appendix C.
@@
 The model has a full radial extent of 20 kpc, allowing a purely migrated population to arise in the outer 4.5 kpc.
-We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}.
+We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{johnson_impact_2020}.
 We summarize these parameters in Table \ref{tab:multizone-parameters}.
@@
     \caption{Nucleosynthetic yield sets.}
+    \include{output/yields.tex}
     \label{tab:yields}
-    \include{output/yields.tex}
 \end{table}
@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{Leung2023-Ages} \\
+        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
         $R_{\rm gal}$     & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
@@
     \end{tabular}
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{Number of APOGEE stars in each Galactic region.}
+\label{tab:apogee-regions}
+\input{output/apogee_regions_table.tex}
 \end{table*}
@@
     \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
-    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (d).
+    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (e).
 Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows.
@@
     \caption{Stellar age--abundance relations produced by select multi-zone models.
-Each point represents a stellar population drawn from the Solar neighborhood near the mid-plane ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq |z| \leq 0.5$ kpc) and is color-coded by its birth radius.
+Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq |z| \leq 0.5$ kpc) and is color-coded by its birth radius.
 For visual clarity, we plot a only random mass-weighted sample of \num{10000} points in each panel.
-The dashed line plots the ISM abundance at $R_{\rm gal}=8$ kpc over time.
-The black points plot the median abundance of stars in 2 Gyr-wide age bins, and the vertical error bars represent the 16th and 84th percentiles of the age distribution.
-Similarly, the red points with error bars plot the median APOGEE abundances for stars with age estimates from \citet{leung_variational_2023}.
+The black curve plots the ISM abundance at $R_{\rm gal}=8$ kpc over time.
+The red line segments plot the median abundance for APOGEE stars in 2 Gyr-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
 Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5$ kpc; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.
@@
 \end{figure*}
+
+The dilution effect discussed in \ref{sec:yields} is clearly seen in the multi-zone model results. Figure \ref{fig:abundance-evolution} shows stellar age--abundance relations for four model outputs.
 

### 2025-02-04 src/scripts/onezone_params.py
add 6 Gyr marker

@@ -179,7 +179,7 @@ def vary_param(subfig, first_timescale=1., second_timescale=10., onset=4.,
                           color=color, 
                           label=f'{val:.1f}', 
                           marker_labels=(i==label_index),
-                          markers=[0.3, 1, 3, 10])
+                          markers=[0.3, 1, 3, 6, 10])
         if verbose:
             print('Value:', val)
             print('Eta:', eta)

### 2025-02-04 src/tex/ms.tex

@@
 On the other hand, the second infall timescale $\tau_2$ controls the width of the MDF and the [O/Fe] distribution of the low-$\alpha$ sequence, with a shorter $\tau_2$ producing a distribution which is skewed to higher [O/Fe] (b).
-The time of maximum infall $t_{\rm max}$ strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic loop characteristic of the two-infall model.
+The time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic abundance loop.
 For $t_{\rm max}>2$ Gyr, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
@@
 The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^N$, with $N=1.5$ following \citet{kennicutt_global_1998}.
-Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a simpler prescription to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
+Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
 In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
@@
     \begin{cases}
-        \epsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
-        \epsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
+        \varepsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
+        \varepsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
     \end{cases}
@@
 where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$ with $\gamma=1/2$ and $\tau_{\rm mol,0}=2$ Gyr.
-Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\epsilon$:
+Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\varepsilon$:
 \begin{equation}
     \label{eq:sfe-prefactor}
-    \epsilon(t) = 
+    \varepsilon(t) = 
     \begin{cases}

### 2025-02-05 src/tex/ms.tex

@@
 \end{equation}
-\todo{Talk about the implications of this prefactor or reference a future section which discusses this.}
+A lower value of $\varepsilon(t<t_{\rm max})$ leads to more efficient star formation during the first infall epoch.
+Figure \ref{fig:sfe-prefactor} illustrates that this pre-factor largely affects the metallicity of the high-$\alpha$ sequence, with a smaller $\varepsilon$ producing faster enrichment during the first infall and stronger dilution after $t_{\rm max}$.
+The pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
+We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature.
+
+\begin{figure}
+    \centering
+    \includegraphics{src/tex/figures/sfe_prefactor.pdf}
+    \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
+All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
+    \label{fig:sfe-prefactor}
+\end{figure}
 
@@
 
-\todo{Copied from last paper.}
-We compare our model results to abundance measurements from the final data release \citep[DR17;][]{abdurrouf_seventeenth_2022} of the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{majewski_apache_2017}.
-APOGEE used infrared spectrographs \citep{wilson_apache_2019} mounted on two telescopes: the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory in the Northern Hemisphere, and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory in the Southern Hemisphere.
-After the spectra were passed through the data reduction pipeline \citep{nidever_data_2015}, the APOGEE Stellar Parameter and Chemical Abundance Pipeline \citep[ASPCAP;][]{holtzman_abundances_2015,garcia_perez_aspcap_2016} extracted chemical abundances using the model grids and interpolation method described by \citet{jonsson_apogee_2020}.
+We compare our models against stellar abundances from the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{majewski_apache_2017} data release 17 \citep[DR17;][]{abdurrouf_seventeenth_2022}.
+APOGEE data were obtained from infrared spectrographs \citep{wilson_apache_2019} mounted on the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory.
+The data reduction pipeline is described by \citet{nidever_data_2015}, and APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
 
-We restrict our sample to red giant branch and red clump stars with high-quality spectra.
-Table \ref{tab:sample} lists our selection criteria, which largely follow from \citet{hayden_chemical_2015}.
-This produces a final sample of \input{output/sample_size.txt} stars with calibrated [O/Fe] and [Fe/H] abundance measurements.
-We make use of the {\it Gaia} Early Data Release 3 (EDR3) data \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the catalog by the APOGEE team.
-Specifically, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates to calculate galactocentric radius $R_{\rm gal}$ and midplane distance $z$, assuming a Sun--Galactic center distance $R_\odot=8.122$ kpc \citep{gravity_collaboration_detection_2018} and height of the Sun above the midplane $z_\odot=20.8$ pc \citep{bennett_vertical_2019}.
-Table \ref{tab:apogee-regions} lists the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$.
-For some Galactic regions with $R_{\rm gal}<5$ kpc or $R_{\rm gal}>13$ kpc, the median distance error exceeds 1 kpc but remains within our bin width of 2 kpc, and the vast majority of stars have much smaller distance uncertainties.
+We obtain a sample of \input{output/sample_size.txt} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}.
+We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog.
+When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122$ kpc \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8$ pc \citep{bennett_vertical_2019}.
+Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.
+\todo{Mention calibrated abundances.}
 
-We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
+\todo{Taken from last paper.} We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
 Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{mackereth_dynamical_2019}.

### 2025-02-05 src/scripts/abundance_evolution.py
update apogee color/alpha

@@ -80,7 +80,7 @@ def main(verbose=False, uncertainties=True, style='paper', cmap='winter_r'):
             # )
             spatch, pcol = plot_apogee_median_abundances(
                 axs[i,j], solar_sample, vice_to_apogee_col(ycol), age_bins, 
-                age_col='L23_AGE', label='APOGEE data', color='Grey',
+                age_col='L23_AGE', label='APOGEE data'#, color='Grey',
             )
             if j == 0:
                 axs[i,j].set_ylabel(capitalize_abundance(ycol))

### 2025-02-05 src/scripts/age_abundance_grid.py

@@ -282,7 +282,7 @@ def plot_vice_median_ages(ax, mzs, col, bin_edges, label=None,
 
 def plot_apogee_median_abundances(ax, apogee_sample, col, bin_edges, label=None, 
                                   color='r', age_col='L23_AGE', min_stars=10,
-                                  alpha=0.3):
+                                  alpha=0.2):
     """
     Plot APOGEE stellar abundance medians and 1-sigma range binned by age.
     

### 2025-02-05 src/tex/ms.tex
Updates from Overleaf

@@
         \eta_\odot      & 0.4       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
-        R_\eta          & 5.4 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
+        R_\eta          & 7.2 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
         % f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate}   & \ref{sec:sfh} & Time-dependence of the gas infall rate \\
@@
 \end{equation}
-We adopt $R_\eta=5.4$ kpc as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.08$ dex kpc$^{-1}$.
+We adopt $R_\eta=7.2$ kpc as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
 \todo{Motivate exponential scale radius.}

### 2025-02-07 src/tex/ms.tex

@@
 The first infall component induces the formation of the thick disk, and the second component produces the thin disk.
-At a given galactocentric radius $R_{\rm gal}$, the un-normalized infall rate is
+At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
 \begin{equation}
@@
 
-The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model.
-Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1$ Gyr, $\tau_2\sim4-10$ Gyr, and $t_{\rm max}\sim4$ Gyr.
-Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying each of these parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
-The first infall timescale $\tau_1$ primarily affects the stellar distribution along the high-$\alpha$ sequence, with negligible effect on the low-$\alpha$ sequence (a).
-On the other hand, the second infall timescale $\tau_2$ controls the width of the MDF and the [O/Fe] distribution of the low-$\alpha$ sequence, with a shorter $\tau_2$ producing a distribution which is skewed to higher [O/Fe] (b).
-The time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic abundance loop.
-For $t_{\rm max}>2$ Gyr, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
-We find that $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions.
-
 \begin{figure*}
@@
 \end{figure*}
+
+% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
+% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1$ Gyr, $\tau_2\sim3-10$ Gyr, and $t_{\rm max}\sim3-5$ Gyr. 
+Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
+We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio.
+The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
+Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6$ Gyr.
+We adopt $\tau_1=1$ Gyr for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx+0.3$.
+
+Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that 
+% the second infall timescale $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions. 
+the second infall timescale $\tau_2$ controls the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
+A shorter $\tau_2$ produces a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces both a narrower low-$\alpha$ sequence and a narrower MDF.
+We note that our maximum value of $\tau_2=30$ Gyr is very close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns.
+Between $\tau_2=3-30$ Gyr, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
+We adopt a fiducial value of $\tau_2=15$ Gyr for the Solar neighborhood in order to minimize the width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times.
+This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}.
+In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.
+
+Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic abundance loop.
+For $t_{\rm max}>2$ Gyr, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
+The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}.
+We adopt a fiducial value of $t_{\rm max}=4.2$ Gyr so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05$ Gyr \citep{pinsonneault_apokasc-3_2024}.
+This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
 
@@
 \subsection{Stellar Abundance Distributions}
+\label{sec:abundance-distributions}
 
@@
 However, as shown by \citet{dubay_galactic_2024}, models with a power-law DTD struggle to reproduce the high-$\alpha$ sequence for a wide range of star formation histories, and the results are no different for this two-infall model.
-Finally, in model (d) the metallicity of the infalling gas increases to ${\rm [X/H]}_{\rm CGM}=-0.7$ at late times, which results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
+
+Finally, in model (d) the metallicity of the infalling gas increases to ${\rm [X/H]}_{\rm CGM}=-0.7$ at late times.
+We choose this value because it is the maximum which can plausibly still reproduce the disk abundances; any higher and the infalling gas would be more metal-rich than the most metal-poor thin disk stars.
+This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
 We assume that the infalling gas has ${\rm [O/Fe]}=0$ at all times; an alternate run with ${\rm [O/Fe]}=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
@@
 \subsection{Age--Abundance Relations}
+\label{sec:age-abundance}
 
@@
 The red line segments plot the median abundance for APOGEE stars in 2 Gyr-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5$ kpc; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.
-{\bf Key takeaway:} the fiducial model shows two discrepancies with the data: a major dilution event at a lookback time of $\sim9$ Gyr and non-zero abundance evolution at late times.
-Only model (b) with higher yields can mitigate both of these issues.}
+Age estimates from APOGEE stars come from \citet{leung_variational_2023}.
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5$ kpc; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.}
     \label{fig:abundance-evolution}
@@
 
-The dilution effect discussed in \ref{sec:yields} is clearly seen in the multi-zone model results. Figure \ref{fig:abundance-evolution} shows stellar age--abundance relations for four model outputs.
+The dilution effect discussed in \ref{sec:yields} is clearly seen in the multi-zone model results.
+Figure \ref{fig:abundance-evolution} shows stellar age--abundance relations for four model outputs.
+Column (a) plots the output of our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and $Z_{\rm CGM}=0$.
+The fiducial model shows two major discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9$ Gyr near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
+We also note the present-day metallicity is still sub-Solar in the fiducial model, but this can be corrected by decreasing $\eta$.
+A higher yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
+However, a consequence of these higher yields is a poor fit to the stellar [O/Fe] distribution, as discussed in Section \ref{sec:abundance-distributions}.
+
+The observed rise in the median abundance of stars with ages of $\sim4-8$ Gyr is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
+Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in column (a) have sub-Solar abundances.
+Column (c) of Figure \ref{fig:abundance-evolution} presents a model with $y/Z_\odot=1$ but with a stronger migration prescription of $\sigma_{\rm RM8}=5$ kpc.
+Here, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
+However, even though this prescription is much stronger than the estimates of, e.g., \citet{frankel_measuring_2018}, the model cannot reproduce the observed age--abundance trends in [O/H] and [Fe/H].
+
+Finally, as in Section \ref{sec:abundance-distributions}, we investigate a model where the gas infall is pre-enriched to ${\rm [O/H]}={\rm [Fe/H]}=-0.7$.
+As shown in column (d) of Figure \ref{fig:abundance-evolution}, this mitigates but does not completely solve the two discrepancies.
+The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution is also reduced, \todo{because why?}.
+The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity --- an effect which can be compensated by a slightly increased value of $\eta$.
+Overall, no modification to the $y/Z_\odot=1$ model is able to overcome both the dilution and late-time evolution issues.
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics{figures/delay_time_distribution.pdf}
-    \caption{The effect of the SN Ia delay-time distribution (DTD) on chemical abundance tracks and stellar distributions.
+% \begin{figure*}
+%     \centering
+%     \includegraphics{figures/delay_time_distribution.pdf}
+%     \caption{The effect of the SN Ia delay-time distribution (DTD) on chemical abundance tracks and stellar distributions.
 {\it Left:} The relative SN Ia rate as a function of time after star formation for each DTD model.
@@
 {\bf Key takeaway:} the extent of the low-$\alpha$ sequence can be reduced by a more prompt SN Ia DTD, but the high-$\alpha$ sequence is also shifted to a more metal-poor regime.}
-    \label{fig:dtd}
-\end{figure*}
+%     \label{fig:dtd}
+% \end{figure*}
 
-Figure \ref{fig:dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
+% Figure \ref{fig:dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
 The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks.

### 2025-02-11 src/scripts/delay_time_distribution.py
move outflows module

@@ -9,8 +9,8 @@ from matplotlib.ticker import FuncFormatter
 import vice
 
 from multizone.src.yields import yZ2
-from multizone.src import dtds
-from multizone.src.models import twoinfall_sf_law, equilibrium_mass_loading
+from multizone.src import dtds, outflows
+from multizone.src.models import twoinfall_sf_law
 from track_and_mdf import setup_axes, plot_vice_onezone
 from utils import twoinfall_onezone
 from colormaps import paultol
@@ -104,7 +104,7 @@ def plot_onezone(fig, dtd_list, labels=[]):
 
 
 def run_model(dtd, output_dir=paths.data / 'onezone' / 'dtd'):
-    eta_func = equilibrium_mass_loading(equilibrium=0., tau_star=0.)
+    eta_func = outflows.equilibrium(equilibrium=0., tau_star=0.)
     ifr = twoinfall_onezone(
         RADIUS, 
         first_timescale=FIRST_INFALL,

### 2025-02-11 src/scripts/enriched_infall.py

@@ -10,7 +10,8 @@ import vice
 
 # from multizone.src.yields import W24
 from multizone.src.yields import J21
-from multizone.src.models import twoinfall_sf_law, equilibrium_mass_loading
+from multizone.src.models import twoinfall_sf_law
+from multizone.src import outflows
 from track_and_mdf import setup_axes, plot_vice_onezone
 from apogee_sample import APOGEESample
 import paths
@@ -40,7 +41,7 @@ def main():
     dt = params['dt']
     simtime = np.arange(0, END_TIME + dt, dt)
     area = np.pi * ((RADIUS + ZONE_WIDTH/2)**2 - (RADIUS - ZONE_WIDTH/2)**2)
-    # eta_func = equilibrium_mass_loading()
+    # eta_func = outflows.equilibrium()
     eta_func = vice.milkyway.default_mass_loading
     params['eta'] = eta_func(RADIUS)
     ifr = twoinfall_onezone(RADIUS, onset=ONSET, mass_loading=eta_func, dt=dt, 

### 2025-02-11 src/scripts/mass_loading.py

@@ -6,8 +6,8 @@ radius.
 import numpy as np
 import matplotlib.pyplot as plt
 
-from multizone.src.yields import W24
-from multizone.src.models import equilibrium_mass_loading
+from multizone.src.yields import yZ1
+from multizone.src import outflows
 import paths
 
 
@@ -17,7 +17,7 @@ def main():
     fig, ax = plt.subplots(tight_layout=True)
     
     radii = np.arange(0, 15.5, 0.1)
-    eta_func = equilibrium_mass_loading()
+    eta_func = outflows.equilibrium()
     ax.plot(radii, [eta_func(r) for r in radii], "k-")
     
     ax.axvline(8, color="r", ls="--")

### 2025-02-11 src/scripts/multizone/src/disks.py

@@ -18,6 +18,7 @@ from .._globals import END_TIME, MAX_SF_RADIUS
 from .migration import diskmigration, gaussian_migration, no_migration
 from . import models
 from . import dtds
+from . import outflows
 from .models.utils import get_bin_number, interpolate, modified_exponential
 from .models.gradient import gradient
 import math as m
@@ -174,18 +175,15 @@ class diskmodel(vice.milkyway):
             self.mass_loading = vice.milkyway.default_mass_loading
         elif outflow_spec == "bespoke":
             if yields == "yZ1":
-                self.mass_loading = models.mass_loading.yZ1()
+                self.mass_loading = outflows.yZ1()
             elif yields == "yZ2":
-                self.mass_loading = models.mass_loading.yZ2()
+                self.mass_loading = outflows.yZ2()
+            elif yields == "yZ3":
+                self.mass_loading = outflows.yZ3()
             else:
-                self.mass_loading = models.equilibrium_mass_loading()
+                self.mass_loading = outflows.equilibrium()
         else:
-            self.mass_loading = models.equilibrium_mass_loading()
-        # self.mass_loading = {
-        #     "J21" : vice.milkyway.default_mass_loading,
-        #     "equilibrium" : models.equilibrium_mass_loading(),
-        #     "none" : models.mass_loading.no_outflows
-        # }[outflow_spec.lower()]
+            self.mass_loading = outflows.equilibrium()
         # Set the SF mode - infall vs star formation rate
         evol_kwargs = {}
         if spec.lower() in [

### 2025-02-11 src/scripts/multizone/src/models/__init__.py

@@ -14,7 +14,6 @@ __all__ = [
     "fiducial_sf_law", 
     "earlyburst_sf_law", 
     "twoinfall_sf_law", 
-    "equilibrium_mass_loading", 
     "two_component_disk",
 ]
 
@@ -32,5 +31,4 @@ from .twoinfall_inner import twoinfall_inner
 from .fiducial_sf_law import fiducial_sf_law
 from .earlyburst_sf_law import earlyburst_sf_law
 from .twoinfall_sf_law import twoinfall_sf_law
-from .mass_loading import equilibrium_mass_loading
 from .diskmodel import two_component_disk

### 2025-02-11 src/scripts/multizone/src/outflows.py

@@ -1,11 +1,15 @@
+"""
+Classes and methods for the outflow mass-loading factor.
+"""
+
 import math as m
+from numbers import Number
 import vice
-from ..._globals import ETA_SCALE_RADIUS
 
 
-class exponential_mass_loading:
+class exponential:
     r"""
-    An exponential outflow mass-loading parameter $\eta$.
+    An exponential outflow mass-loading parameter $\eta(R_{\rm gal})$.
 
     Parameters
     ----------
@@ -36,21 +40,65 @@ class exponential_mass_loading:
 
     def __call__(self, radius):
         return self.solar_value * m.exp((radius - 8.0) / self.scale_radius)
+    
+    @property
+    def solar_value(self):
+        """
+        float
+            The mass-loading factor at the Solar annulus.
+        """
+        return self._solar_value
+    
+    @solar_value.setter
+    def solar_value(self, value):
+        if isinstance(value, Number):
+            if value > 0:
+                self._solar_value = value
+            else:
+                raise ValueError("Mass-loading factor must be positive.")
+        else:
+            raise TypeError(f"Parameter ``solar_value`` must be a float. \
+Got: {type(value)}")
+        
+    @property
+    def scale_radius(self):
+        """
+        float
+            The exponential scale radius of the mass-loading factor in kpc.
+        """
+        return self._scale_radius
+    
+    @scale_radius.setter
+    def scale_radius(self, value):
+        if isinstance(value, Number):
+            if value > 0:
+                self._scale_radius = value
+            else:
+                raise ValueError("Scale radius must be positive.")
+        else:
+            raise TypeError(f"Parameter ``scale_radius`` must be a float. \
+Got: {type(value)}")
 
 
-class yZ1(exponential_mass_loading):
+class yZ1(exponential):
     """Subclass of ``exponential_mass_loading`` tuned to the yZ1 yields."""
     def __init__(self):
-        super().__init__(0.2, 4.0)
+        super().__init__(0.2, 4.2)
 
 
-class yZ2(exponential_mass_loading):
+class yZ2(exponential):
     """Subclass of ``exponential_mass_loading`` tuned to the yZ2 yields."""
     def __init__(self):
-        super().__init__(1.4, 5.0)
+        super().__init__(1.4, 5.4)
 
 
-class equilibrium_mass_loading(exponential_mass_loading):
+class yZ3(exponential):
[…]

### 2025-02-11 src/scripts/onezone_birth_radius.py

@@ -8,9 +8,10 @@ import matplotlib.pyplot as plt
 
 import vice
 
-from multizone.src.yields import W24mod
-from multizone.src.models import twoinfall_sf_law, equilibrium_mass_loading
+from multizone.src.yields import yZ1
+from multizone.src.models import twoinfall_sf_law
 from multizone.src.dtds import powerlaw, exponential
+from multizone.src import outflows
 from track_and_mdf import setup_figure, plot_vice_onezone
 # from apogee_sample import APOGEESample
 import paths
@@ -64,7 +65,7 @@ def main():
     # One-zone model parameters
     simtime = np.arange(0, 13.21, 0.01)
     area = np.pi * ((RADIUS + ZONE_WIDTH/2)**2 - (RADIUS - ZONE_WIDTH/2)**2)
-    eta_func = equilibrium_mass_loading(
+    eta_func = outflows.equilibrium(
         tau_star=0.,
         # tau_sfh=SECOND_TIMESCALE, 
         equilibrium=0.

### 2025-02-11 src/scripts/onezone_eta.py

@@ -8,8 +8,8 @@ import matplotlib.pyplot as plt
 
 import vice
 
-from multizone.src.yields import W24
-from multizone.src import models
+from multizone.src.yields import yZ1
+from multizone.src import models, outflows
 from track_and_mdf import setup_figure, plot_vice_onezone
 import paths
 from _globals import ONEZONE_DEFAULTS, ZONE_WIDTH
@@ -29,7 +29,7 @@ def main():
     
     simtime = np.arange(0, 13.21, 0.01)
     
-    eta_func = models.equilibrium_mass_loading(
+    eta_func = outflows.equilibrium(
         tau_star=2., tau_sfh=10., alpha_h_eq=0.1
     )
     

### 2025-02-11 src/scripts/onezone_regions.py

@@ -9,8 +9,8 @@ from tqdm import tqdm
 import vice
 
 import paths
-from multizone.src.yields import W24mod
-from multizone.src import models, dtds
+from multizone.src.yields import yZ1
+from multizone.src import models, dtds, outflows
 from multizone.src.models.gradient import gradient
 from apogee_sample import APOGEESample
 from _globals import END_TIME, ONEZONE_DEFAULTS, TWO_COLUMN_WIDTH
@@ -30,7 +30,7 @@ def main():
     gs = fig.add_gridspec(7, 22, wspace=0.)
     subfigs = [fig.add_subfigure(gs[:,i:i+w]) for i, w in zip((0, 8, 15), (8, 7, 7))]
     # Outflow mass-loading factor
-    eta_func = models.equilibrium_mass_loading(equilibrium=0.2, tau_star=0.)
+    eta_func = outflows.yZ1()
     # eta_func = vice.milkyway.default_mass_loading
     axs0 = plot_region(subfigs[0], 6, eta=eta_func, 
                        color=paultol.highcontrast.colors[2],
@@ -45,7 +45,7 @@ def main():
     fig.savefig(paths.figures / 'onezone_regions', dpi=300)
     plt.close()
     
-def plot_region(fig, radius, dr=4., eta=models.equilibrium_mass_loading(), 
+def plot_region(fig, radius, dr=4., eta=outflows.equilibrium(), 
                 output_dir=paths.data/'onezone'/'regions', 
                 color=None, **kwargs):
     axs = setup_axes(fig, title='', xlabel='[O/H]', **kwargs)

### 2025-02-11 src/scripts/onezone_sfr.py

@@ -9,9 +9,9 @@ import matplotlib.pyplot as plt
 import vice
 
 from multizone.src.yields import yZ1
-vice.yields.sneia.settings['fe'] *= 0.9
-from multizone.src.models import twoinfall_sf_law, equilibrium_mass_loading
-from multizone.src.models.mass_loading import no_outflows
+# vice.yields.sneia.settings['fe'] *= 0.9
+from multizone.src.models import twoinfall_sf_law
+from multizone.src import outflows
 from track_and_mdf import setup_figure, plot_vice_onezone
 from apogee_sample import APOGEESample
 import paths
@@ -63,13 +63,7 @@ def main():
     # One-zone model parameters
     simtime = np.arange(0, 13.21, 0.01)
     area = np.pi * ((RADIUS + ZONE_WIDTH/2)**2 - (RADIUS - ZONE_WIDTH/2)**2)
-    # eta_func = equilibrium_mass_loading(
-    #     tau_star=0.,
-    #     # tau_sfh=SECOND_TIMESCALE, 
-    #     equilibrium=0.2
-    # )
-    eta_func = no_outflows
-    # eta_func = vice.milkyway.default_mass_loading
+    eta_func = outflows.equilibrium(equilibrium=0.2, tau_star=0)
     ifr = twoinfall_onezone(
         RADIUS, 
         first_timescale=FIRST_TIMESCALE, 

### 2025-02-11 src/scripts/sfe_prefactor.py

@@ -9,7 +9,7 @@ import vice
 
 from multizone.src.yields import yZ1
 from multizone.src.models import twoinfall_sf_law
-from multizone.src.models import equilibrium_mass_loading
+from multizone.src import outflows
 from track_and_mdf import setup_figure, plot_vice_onezone
 from colormaps import paultol
 import paths
@@ -18,7 +18,7 @@ from utils import twoinfall_onezone
 
 RADIUS = 8.
 XLIM = (-2, 0.4)
-YLIM = (-0.12, 0.499)
+YLIM = (-0.08, 0.499)
 ONSET = 4.2
 ZONE_WIDTH = 2
 
@@ -38,10 +38,7 @@ def main():
     simtime = np.arange(0, END_TIME + dt, dt)
 
     area = np.pi * ((RADIUS + ZONE_WIDTH/2)**2 - (RADIUS - ZONE_WIDTH/2)**2)
-    eta_func = equilibrium_mass_loading(
-        tau_star=0., 
-        equilibrium=0.
-    )
+    eta_func = outflows.yZ1()
 
     tau_star_list = [twoinfall_sf_law(area, onset=ONSET, factor=1.),
                      twoinfall_sf_law(area, onset=ONSET, factor=0.5),

### 2025-02-11 src/scripts/yield_outflow.py

@@ -9,7 +9,7 @@ from matplotlib.ticker import MultipleLocator
 import vice
 
 from apogee_sample import APOGEESample
-from multizone.src.models import twoinfall_sf_law, equilibrium_mass_loading
+from multizone.src.models import twoinfall_sf_law
 from multizone.src import dtds
 from utils import twoinfall_onezone, get_bin_centers
 from track_and_mdf import plot_mdf_curve
@@ -168,8 +168,6 @@ def run_plot_model(axs, scale, params, yia_scale=1.,
         output_dir.mkdir(parents=True)
     
     scale_yields(scale, afe_cc=AFE_CC, yia_scale=yia_scale)
-    # params['eta'] = equilibrium_mass_loading(tau_star=0.)(RADIUS)
-    # params['eta'] *= eta_scale
     RIa = vice.yields.sneia.settings['fe'] / SNIA_FE_YIELD
     if label == '':
         label = r'$y/Z_\odot = %s$, $\eta=%s$' % (

### 2025-02-11 src/scripts/yields.py

@@ -6,14 +6,15 @@ adopted in this paper.
 import pandas as pd
 import vice
 import paths
+from multizone.src import outflows
 
 def main():
     from multizone.src.yields import yZ1
-    yZ1_yields, yZ1_labels = make_column()
+    yZ1_yields, yZ1_labels = make_column(eta=outflows.yZ1())
     from multizone.src.yields import yZ2
-    yZ2_yields, yZ2_labels = make_column()
+    yZ2_yields, yZ2_labels = make_column(eta=outflows.yZ2())
     from multizone.src.yields import yZ3
-    yZ3_yields, yZ3_labels = make_column()
+    yZ3_yields, yZ3_labels = make_column(eta=outflows.yZ3())
     df = pd.DataFrame({
         '$y/Z_\\odot=1$': yZ1_yields,
         '$y/Z_\\odot=2$': yZ2_yields,
@@ -32,7 +33,7 @@ def main():
     with open(paths.output / 'yields.tex', 'w') as f:
         f.write(latex_table)
 
-def make_column(elements = ['O', 'Fe'], mfeia=0.7):
+def make_column(elements = ['O', 'Fe'], mfeia=0.7, eta=outflows.yZ1()):
     ccsn_yields = []
     ccsn_labels = []
     snia_yields = []
@@ -43,9 +44,15 @@ def make_column(elements = ['O', 'Fe'], mfeia=0.7):
         snia_yields.append('\\num{%.2e}' % vice.yields.sneia.settings[el])
         snia_labels.append('$y_{\\rm %s}^{\\rm Ia}$' % el)
     # Calculate SN Ia rates assuming a mean Fe mass per SN
-    snia_labels.append('$N_{\\rm Ia}/M_\\star$')
+    snia_labels.append('$N_{\\rm Ia}/M_\\star\\,[{\\rm M}_\\odot^{-1}]$')
     snia_yields.append('\\num{%.2e}' % (vice.yields.sneia.settings['fe'] / mfeia))
-    return ccsn_yields + snia_yields, ccsn_labels + snia_labels
+    # Yield-specific outflow parameters
+    outflow_params = [f'{eta.solar_value:.1f}', f'{eta.scale_radius:.1f}']
+    outflow_labels = ['$\\eta_\\odot$', '$R_\\eta$ [kpc]']
+    # All parameters and labels
+    params = ccsn_yields + snia_yields + outflow_params
+    labels = ccsn_labels + snia_labels + outflow_labels
[…]

### 2025-02-11 src/scripts/onezone_params.py
update default tau1

@@ -11,7 +11,7 @@ import vice
 
 from multizone.src.yields import yZ1
 from utils import twoinfall_onezone
-from multizone.src import models
+from multizone.src import models, outflows
 from _globals import END_TIME, ONEZONE_DEFAULTS, TWO_COLUMN_WIDTH
 from track_and_mdf import setup_axes, plot_vice_onezone
 import paths
@@ -19,7 +19,7 @@ import paths
 RADIUS = 8.
 ZONE_WIDTH = 2.
 FIDUCIAL = {
-    'first_timescale': 1.,
+    'first_timescale': 0.3,
     'second_timescale': 10.,
     'onset': 4.
 }
@@ -30,7 +30,7 @@ LABELS = {
     'onset': 't_{\\rm max}'
 }
 XLIM = (-1.9, 0.7)
-YLIM = (-0.2, 0.499)
+YLIM = (-0.14, 0.499)
 
 def main(fiducial=FIDUCIAL, xlim=XLIM, ylim=YLIM, fname='onezone_params', 
          verbose=False, style='paper'):
@@ -155,11 +155,7 @@ def vary_param(subfig, first_timescale=1., second_timescale=10., onset=4.,
         else:
             color = None
         # Outflow mass-loading factor
-        eta_func = models.equilibrium_mass_loading(
-            equilibrium=0., 
-            tau_sfh=param_dict['second_timescale'], 
-            tau_star=0. # for a consistent value of eta
-        )
+        eta_func = outflows.yZ1()
         eta = eta_func(RADIUS)
         # Run one-zone model
         name = output_name(*param_dict.values())

### 2025-02-11 src/tex/ms.tex

@@
 
-\section{Methods}
+\section{Observational Sample}
+\label{sec:observational-sample}
+
+\begin{table*}
+    \centering
+    \caption{Sample selection parameters and median uncertainties from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
+    \label{tab:sample}
+    \begin{tabular}{lll}
+        \hline\hline
+        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range or Value} & \multicolumn{1}{c}{Notes} \\
+        \hline
+        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
+        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
+        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
+        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
+        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
+        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
+        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
+        $|z|$               & $|z| < 2$ kpc                 & Eliminate halo stars \\
+        \hline
+    \end{tabular}
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{Number of APOGEE stars in each Galactic region.}
+\label{tab:apogee-regions}
+\input{output/apogee_regions_table.tex}
+\end{table*}
+
+\begin{table*}
+    \centering
+    \caption{Median and dispersion in APOGEE parameter uncertainties.}
+    \label{tab:uncertainties}
+    \begin{tabular}{lcc}
+        \hline\hline
+        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Median Uncertainty} & \multicolumn{1}{c}{Uncertainty Dispersion ($95\%-5\%$)} \\
+        \hline
+        [Fe/H]          & $0.0089$   & $0.0060$ \\
+        ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
+        log(Age/Gyr)    & $0.10$     & $0.16$ \\
+        \hline
+    \end{tabular}
+\end{table*}
+
+We compare our models against stellar abundances from the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{majewski_apache_2017} data release 17 \citep[DR17;][]{abdurrouf_seventeenth_2022}.
+APOGEE data were obtained from infrared spectrographs \citep{wilson_apache_2019} mounted on the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory.
+The data reduction pipeline is described by \citet{nidever_data_2015}, and APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
+
+We obtain a sample of \input{output/sample_size.txt} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}.
+We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog.
+When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122$ kpc \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8$ pc \citep{bennett_vertical_2019}.
+Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.
+\todo{Mention calibrated abundances.}
+
+\todo{Taken from last paper.} We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
+Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{mackereth_dynamical_2019}.
+We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt} APOGEE stars with age estimates.
+We note that we use the full sample of \input{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates.
+Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).
+
+\section{Chemical Evolution Models \& Parameter Selection}
 \label{sec:methods}
@@
 We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the {\tt yZ1} and {\tt yZ2} yield sets, respectively, to ensure our models could reach ${\rm [O/Fe]}\approx0.0$ by the end time.
-The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\bar m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009} \todo{(are there more recent citations?)}.
+The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009} \todo{(are there more recent citations?)}.
 The rate for the {\tt yZ1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
@@
 
-\subsection{Observational Sample}
-\label{sec:observational-sample}
-
-\begin{table*}
-    \centering
-    \caption{Sample selection parameters and median uncertainties from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
-    \label{tab:sample}
-    \begin{tabular}{lll}
-        \hline\hline
-        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range or Value} & \multicolumn{1}{c}{Notes} \\
-        \hline
-        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
-        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
-        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
-        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
-        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
-        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
-        $|z|$               & $|z| < 2$ kpc                 & Eliminate halo stars \\
-        \hline
-    \end{tabular}
-\end{table*}
-
-\begin{table*}
-\centering
-\caption{Number of APOGEE stars in each Galactic region.}
-\label{tab:apogee-regions}
-\input{output/apogee_regions_table.tex}
-\end{table*}
-
-\begin{table*}
-    \centering
-    \caption{Median and dispersion in APOGEE parameter uncertainties.}
-    \label{tab:uncertainties}
-    \begin{tabular}{lcc}
-        \hline\hline
-        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Median Uncertainty} & \multicolumn{1}{c}{Uncertainty Dispersion ($95\%-5\%$)} \\
-        \hline
-        [Fe/H]          & $0.0089$   & $0.0060$ \\
-        ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
-        log(Age/Gyr)    & $0.10$     & $0.16$ \\
-        \hline
-    \end{tabular}
-\end{table*}
-
-We compare our models against stellar abundances from the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{majewski_apache_2017} data release 17 \citep[DR17;][]{abdurrouf_seventeenth_2022}.
-APOGEE data were obtained from infrared spectrographs \citep{wilson_apache_2019} mounted on the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory.
-The data reduction pipeline is described by \citet{nidever_data_2015}, and APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
-
-We obtain a sample of \input{output/sample_size.txt} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}.
-We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog.
-When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122$ kpc \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8$ pc \citep{bennett_vertical_2019}.
-Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.
-\todo{Mention calibrated abundances.}
-
-\todo{Taken from last paper.} We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
-Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{mackereth_dynamical_2019}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt} APOGEE stars with age estimates.
-We note that we use the full sample of \input{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates.
-Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).
-
 \section{Multi-Zone Model Results}
@@
 
-\subsection{The SN Ia Delay-Time Distribution}
-\label{sec:dtd-discussion}
+% \subsection{The SN Ia Delay-Time Distribution}
+% \label{sec:dtd-discussion}
 

### 2025-02-11 src/scripts/onezone_sfe_hiatus.py
update sfe hiatus plot

@@ -7,8 +7,10 @@ import matplotlib.pyplot as plt
 
 import vice
 
-from multizone.src.yields import J21
+from multizone.src.yields import yZ2
+vice.yields.sneia.settings['fe'] *= 10**-0.1
 from multizone.src.models.utils import exponential
+from multizone.src import outflows
 from track_and_mdf import setup_figure, plot_vice_onezone
 from apogee_sample import APOGEESample
 import paths
@@ -18,14 +20,14 @@ from colormaps import paultol
 
 RADIUS = 8.
 ZONE_WIDTH = 2.
-HIATUS_ONSET = 1.0
-HIATUS_DURATION = 0.3
+HIATUS_ONSET = 1.4
+HIATUS_DURATION = 0.2
 TAU_STAR_BASE = 2.0
 TAU_STAR_ENHANCEMENT = 10
 FEH_LIM = (-1.6, 0.6)
 OFE_LIM = (-0.08, 0.48)
 
-def main():
+def main(verbose=True):
     plt.style.use(paths.styles / 'paper.mplstyle')
     plt.rcParams['axes.prop_cycle'] = plt.cycler('color', paultol.bright.colors)
     fig, axs = setup_figure(xlim=FEH_LIM, ylim=OFE_LIM)
@@ -36,9 +38,9 @@ def main():
     # apogee_solar.plot_kde2D_contours(axs[0], 'FE_H', 'O_FE', c='k', lw=1,
     #                                  plot_kwargs={'zorder': 1})
     pcm = axs[0].hexbin(apogee_solar('FE_H'), apogee_solar('O_FE'),
-                  gridsize=50, bins='log',
+                  gridsize=50, #bins='log',
                   extent=[FEH_LIM[0], FEH_LIM[1], OFE_LIM[0], OFE_LIM[1]],
-                  cmap='Greys', linewidths=0.2)
+                  cmap='binary', linewidths=0.2)
     cax = axs[0].inset_axes([0.05, 0.05, 0.05, 0.8])
     fig.colorbar(pcm, cax=cax, orientation='vertical', label='# APOGEE Stars')
     
@@ -59,6 +61,9 @@ def main():
     
     # One-zone model parameters
     simtime = np.arange(0, 13.21, 0.01)
+    eta = outflows.equilibrium()
+    if verbose:
+        print('Eta = ', eta(RADIUS))
 
     # Reference: constant tau_star
     name = str(output_dir / 'constant')
[…]

### 2025-02-11 src/tex/ms.tex

@@
         % Outflows
-        \eta_\odot      & 0.4       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
-        R_\eta          & 7.2 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
+        \eta_\odot      & 0.2       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
+        R_\eta          & 4.2 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
         % f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate}   & \ref{sec:sfh} & Time-dependence of the gas infall rate \\
@@
 \end{equation}
-We discuss the implications of using a different DTD in Section \ref{sec:dtd-discussion}.
+We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.
 

### 2025-02-11 src/scripts/onezone_params.py
revert default parameters

@@ -19,7 +19,7 @@ import paths
 RADIUS = 8.
 ZONE_WIDTH = 2.
 FIDUCIAL = {
-    'first_timescale': 0.3,
+    'first_timescale': 1.,
     'second_timescale': 10.,
     'onset': 4.
 }

### 2025-02-11 src/tex/ms.tex

@@
 
+\subsection{Radial Gas Flows}
+\label{sec:radial-flows}
+
+\subsection{Star Formation Hiatus}
+\label{sec:sfe-hiatus}
+
+The two-infall model falls into the broader category of GCE models which reproduce the $\alpha$-bimodality by halting or severely limiting star formation for some duration.
+For the two-infall model, this phase of low star formation immediately precedes the second infall epoch and is due to the relatively short timescale of the first infall epoch.
+However, as we have shown, the dilution of the ISM resulting from the second infall poses a challenge when comparing to age--abundance data.
+
+A bursty infall history is not the only way to produce a gap in the star formation history. \citep{beane_rising_2024} present
+
 \begin{figure}
@@
     \includegraphics{figures/onezone_sfe_hiatus.pdf}
-    \caption{Caption.}
+    \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.
+The blue dashed curve represents the fiducial model that has an exponentially declining infall rate and constant star formation efficiency timescale $\tau_\star=2$ Gyr.
+The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4$ Gyr.
+The greyscale histogram presents the number density of APOGEE stars in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}
 \end{figure}
-
-\subsection{Radial Gas Flows}
-\label{sec:radial-flows}
 

### 2025-02-12 src/tex/ms.tex
Updates from Overleaf

@@
 Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
-We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio.
 The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
@@
 This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
+
+We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio regardless of the infall parameters.
+The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus.
+In our multi-zone models, most of the high-$\alpha$ stars present in the Solar neighborhood have migrated from the inner Galaxy.
 
@@
 
-\subsection{Stellar Abundance Distributions}
+\subsection{Present-Day Abundances}
 \label{sec:abundance-distributions}
@@
 
-\subsection{Age--Abundance Relations}
+\begin{figure}
+    \centering
+    \includegraphics{figures/ofe_feh_density.pdf}
+    \caption{The density of stars in the [O/Fe]--[Fe/H] plane from multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
+Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9$ kpc and $0.5\leq|z|<1$ kpc to highlight the $\alpha$-bimodality.}
+    \label{fig:ofe-feh-density}
+\end{figure}
+
+Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model at mid to high Galactic latitudes.
+Between $0.5\leq|z|<1$ kpc, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over (${\rm [Fe/H]}\approx-0.3$, ${\rm [O/Fe]}\approx0.1-0.2$), which is not seen in the APOGEE sample.
+Additionally, it is clear that the shape of the low-$\alpha$ sequence in the model results (a concave-down ``comma'') is different from the data (a concave-up ``swoosh'').
+
+\subsection{Abundance Evolution}
 \label{sec:age-abundance}
@@
 
+\subsection{Abundances Across the Disk}
+\label{sec:disk-abundances}
+
 \section{Discussion}
@@
 
-The two-infall model falls into the broader category of GCE models which reproduce the $\alpha$-bimodality by halting or severely limiting star formation for some duration.
-For the two-infall model, this phase of low star formation immediately precedes the second infall epoch and is due to the relatively short timescale of the first infall epoch.
-However, as we have shown, the dilution of the ISM resulting from the second infall poses a challenge when comparing to age--abundance data.
-
-A bursty infall history is not the only way to produce a gap in the star formation history. \citep{beane_rising_2024} present
-
 \begin{figure}
@@
 The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4$ Gyr.
-The greyscale histogram presents the number density of APOGEE stars in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
+Both models assume the {\tt yZ2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
+The greyscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq2$ kpc) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}
 \end{figure}
+
+The two-infall model falls into the broader category of GCE models which reproduce the $\alpha$-bimodality by halting or severely limiting star formation for some duration.
+For the two-infall model, this phase of low star formation immediately precedes the second infall epoch and is due to the relatively short timescale of the first infall epoch.
+However, as we have shown, the dilution of the ISM resulting from the second infall poses a challenge when comparing to age--abundance data.
+
+A bursty infall history is not the only way to produce a gap in the star formation history.
+\citet{beane_rising_2024} present a simulated galaxy from the Illustris TNG50 suite that exhibits MW-like bimodality.
+They argue that the $\alpha$-bimodality is brought on by a brief ($\sim300$ Myr) quiescent period caused by bar formation.
+The virial mass of their galaxy grows steadily throughout this period, unlike in our two-infall model where the mass grows by a factor of \todo{X} during the 1 Gyr following the second infall.
+
+While our semi-analytic model does not include a Galactic bar, we can explore the effects of a star formation hiatus by artificially boosting the SFE timescale $\tau_\star$ for a period of time.
+Figure \ref{fig:onezone-sfe-hiatus} illustrates the effect of this SFE-driven hiatus in a one-zone model with an exponentially declining infall rate.
+During the quiescent period, the [O/Fe] ratio slowly declines due to the delayed contribution of Fe from SNe Ia.
+Meanwhile, the gas mass continues to increase even as star formation is suppressed.
+When $\tau_\star$ is lowered at the end of the quiescent period, the high gas mass sparks a moderate star formation burst which causes stellar abundances to ``pile up'' at similar [O/Fe] values.
+The trough between the high- and low-$\alpha$ sequences results from the star formation returning to pre-quiescence behavior.
+
+Our simple hiatus model offers a few parameters which control the chemical evolution.
+The onset time of the SFE hiatus controls the position of the high-$\alpha$ sequence: a later onset places the peak at lower [O/Fe].
+The duration of the star formation hiatus \todo{(and the $\tau_\star$ enhancement factor?)} controls the strength of the high-$\alpha$ peak.
+
+The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
+However, there are some differences in detail, such as the dearth of stars at ${\rm [O/Fe]}\approx+0.35$ due to the star formation hiatus.
+We intend this model to illustrate another path to reproducing the $\alpha$-bimodality.
+Most of the high-$\alpha$ stars present in the Solar annulus have likely migrated from the inner Galaxy, where perhaps this SFE-driven hiatus was concentrated.
 

### 2025-02-13 src/scripts/abundance_evolution.py
make twoinfall_expvar the fiducial evolution

@@ -19,8 +19,8 @@ from multizone_stars import MultizoneStars
 import paths
 
 OUTPUT_NAMES = [
-    'yZ1/mass_loading/bespoke/diskmodel',
-    'yZ2/mass_loading/bespoke/diskmodel',
+    'yZ1/fiducial/diskmodel',
+    'yZ2/fiducial/diskmodel',
     'yZ1/migration_strength/strength50/diskmodel',
     'yZ1/pre_enrichment/mh07_alpha00/diskmodel',
 ]

### 2025-02-13 src/scripts/multizone/src/models/twoinfall_expvar.py

@@ -4,7 +4,6 @@ the two-infall model with a radially-dependent second infall timescale.
 """
 
 import math as m
-from .insideout import insideout
 from .twoinfall import twoinfall
 
 _SCALE_RADIUS_ = 7 # kpc
@@ -19,11 +18,9 @@ class twoinfall_expvar(twoinfall):
     ----------
     radius : float
         The galactocentric radius in kpc of a given annulus in the model.
-    Re : float [default: 5]
-        Effective radius of the Galaxy in kpc.
     
     Other parameters, arguments, and functionality are inherited from 
-    ``twoinfall``. The timescale function is inherited from ``insideout``.
+    ``twoinfall``.
     """
     def __init__(self, radius, **kwargs):
         super().__init__(

### 2025-02-13 src/scripts/ofe_df_comparison.py

@@ -14,8 +14,8 @@ import paths
 from _globals import TWO_COLUMN_WIDTH, GALR_BINS, ABSZ_BINS
 
 OUTPUT_NAMES = [
-    'yZ1/mass_loading/bespoke/diskmodel',
-    'yZ2/mass_loading/bespoke/diskmodel',
+    'yZ1/fiducial/diskmodel',
+    'yZ2/fiducial/diskmodel',
     'yZ2/dtd/powerlaw/diskmodel',
     'yZ2/pre_enrichment/mh07_alpha00/diskmodel'
 ]

### 2025-02-13 src/scripts/ofe_feh_density.py

@@ -14,8 +14,8 @@ import paths
 from colormaps import paultol
 
 OUTPUT_NAMES = [
-    'yZ1/mass_loading/bespoke/diskmodel',
-    'yZ2/mass_loading/bespoke/diskmodel'
+    'yZ1/fiducial/diskmodel',
+    'yZ2/fiducial/diskmodel'
 ]
 LABELS = [
     r'(a) $y/Z_\odot=1$',

### 2025-02-13 src/scripts/run_all_models.sh

@@ -2,33 +2,34 @@
 
 NSTARS=2
 OUTFLOWS=bespoke
+EVOLUTION=twoinfall_expvar
 
-NAME="yZ1/mass_loading/$OUTFLOWS/diskmodel"
+NAME="yZ1/fiducial/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ1 --outflows=$OUTFLOWS
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ1 --evolution=$EVOLUTION --outflows=$OUTFLOWS
 echo ""
 
 NAME="yZ1/migration_strength/strength50/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ1 --outflows=$OUTFLOWS --migration-strength=5.0
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ1 --evolution=$EVOLUTION --outflows=$OUTFLOWS --migration-strength=5.0
 echo ""
 
 NAME="yZ1/pre_enrichment/mh07_alpha00/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ1 --outflows=$OUTFLOWS --pre-enrichment=-0.7
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ1 --evolution=$EVOLUTION --outflows=$OUTFLOWS --pre-enrichment=-0.7
 echo ""
 
-NAME="yZ2/mass_loading/$OUTFLOWS/diskmodel"
+NAME="yZ2/fiducial/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --outflows=$OUTFLOWS
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --outflows=$OUTFLOWS
 echo ""
 
 NAME="yZ2/dtd/powerlaw/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --outflows=$OUTFLOWS --RIa=powerlaw
[…]

### 2025-02-13 src/tex/ms.tex

@@
 
-\todo{Copied from last paper.} We use the multi-zone GCE model tools in \vice developed by \citet{johnson_stellar_2021}.
-The basic setup of our models follows theirs.
-The disk is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
-Stellar populations migrate radially under the prescription we describe in Appendix C, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing.
-Following \citet{johnson_stellar_2021}, we do not implement radial gas flows \citep[e.g.,][]{lacey_chemical_1985,bilitewski_radial_2012}.
-Stellar populations are also assigned a distance from the midplane according to their age and final radius as described in Appendix C.
+We run multi-zone GCE models using the Versatile Integrator for Chemical Evolution \citep[{\tt VICE};][]{johnson_impact_2020}.
+The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}.
+We set up a disk with radial extent $0\leq R_{\rm gal}<20$ kpc that is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
+We use a time-step size of $\Delta t=10$ Myr and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2$ Gyr.
 
-\todo{Copied from last paper.} We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm final}=13.2$ Gyr.
-Following \citet{johnson_stellar_2021}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_\star=0$ for $R_{\rm gal}>R_{\rm SF}$.
-The model has a full radial extent of 20 kpc, allowing a purely migrated population to arise in the outer 4.5 kpc.
-We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{johnson_impact_2020}.
-We summarize these parameters in Table \ref{tab:multizone-parameters}.
+Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling.
+Stellar populations migrate between zones as described in Section \ref{sec:migration}, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones.
+We inhibit star formation past $R_{\rm gal}>15.5$ kpc, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
+We also assign a final midplane distance to each stellar population as described in Section \ref{sec:migration}.
+We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
+
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, and we detail our outflow prescription in Section \ref{sec:outflows}.
+We describe the infall history and parameter selection in Section \ref{sec:sfh}, and we present our star formation law in Section \ref{sec:sf-law}.
+We briefly summarize the stellar migration prescription in Section \ref{sec:migration}.
+Table \ref{tab:multizone-parameters} summarizes the most relevant variables and their fiducial values in this work.
 
@@
     \centering
-    \caption{Nucleosynthetic yield sets.}
+    \caption{Nucleosynthetic yields and outflow prescriptions.}
     \include{output/yields.tex}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/onezone_sfr.pdf}
-    \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
+% \begin{figure}
+%     \centering
+%     \includegraphics{figures/onezone_sfr.pdf}
+%     \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
 This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
-    \label{fig:onezone-sfr}
-\end{figure}
+%     \label{fig:onezone-sfr}
+% \end{figure}
 
@@
 
-\subsection{Present-Day Abundances}
+\subsection{Local Abundance Patterns}
 \label{sec:abundance-distributions}
@@
 
-As discussed in Section \ref{sec:sfh}, the two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
 Figure \ref{fig:ofe-df} compares [O/Fe] distributions across the Galactic disk produced by four different multi-zone models with the distributions observed in APOGEE DR17.
@@
 In columns (c) and (d) of Figure \ref{fig:ofe-df}, we attempt to mitigate the issue of the intermediate-$\alpha$ peak for the $y/Z_\odot=2$ yield set.
-Model (c) switches out our fiducial DTD with a power-law DTD, which decreases the timescale for Fe production (see Figure \ref{fig:dtd}).
+Model (c) switches out our fiducial DTD with a power-law DTD, which decreases the timescale for Fe production.
 However, as shown by \citet{dubay_galactic_2024}, models with a power-law DTD struggle to reproduce the high-$\alpha$ sequence for a wide range of star formation histories, and the results are no different for this two-infall model.
@@
     \caption{The density of stars in the [O/Fe]--[Fe/H] plane from multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
+The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of 1 Gyr.
 Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9$ kpc and $0.5\leq|z|<1$ kpc to highlight the $\alpha$-bimodality.}
@@
 Between $0.5\leq|z|<1$ kpc, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over (${\rm [Fe/H]}\approx-0.3$, ${\rm [O/Fe]}\approx0.1-0.2$), which is not seen in the APOGEE sample.
-Additionally, it is clear that the shape of the low-$\alpha$ sequence in the model results (a concave-down ``comma'') is different from the data (a concave-up ``swoosh'').
+This over-density occurs because the overall rate of chemical evolution slows $\sim2$ Gyr after the second infall, at the same time as the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
+This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in models (c) and (d) of Figure \ref{fig:ofe-df}.
+
+Additionally, the shape of the low-$\alpha$ sequence in the model results (a concave-down ``comma'') is clearly different from the data (a concave-up ``swoosh'').
+\todo{Not sure what this means because the inside-out SFH has the same issue.
+Maybe it's related to radial migration?}
 

### 2025-02-13 src/tex/ms.tex

@@
 We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, and we detail our outflow prescription in Section \ref{sec:outflows}.
-We describe the infall history and parameter selection in Section \ref{sec:sfh}, and we present our star formation law in Section \ref{sec:sf-law}.
+We describe the gas supply in Section \ref{sec:sfh}, we detail the infall parameter selection in Section \ref{sec:parameter-selection}, and we present our star formation law in Section \ref{sec:sf-law}.
 We briefly summarize the stellar migration prescription in Section \ref{sec:migration}.
@@
         R_\eta          & 4.2 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
-        % f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate}   & \ref{sec:sfh} & Time-dependence of the gas infall rate \\
-        \tau_1          & 1 Gyr     & \ref{sec:sfh}     & Timescale of the first infall epoch \\
-        \tau_2          & 15 Gyr    & \ref{sec:sfh}     & Timescale of the second infall epoch \\
-        t_{\rm max}      & 4.2      & \ref{sec:sfh}     & Time of maximum gas infall (onset of second infall) \\
         f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
         {\rm [X/H]}_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
+        \tau_1          & 1 Gyr     & \ref{sec:parameter-selection}     & Timescale of the first infall epoch \\
+        \tau_2(R_\odot)  & 15 Gyr    & \ref{sec:parameter-selection}     & Timescale of the second infall epoch at the Solar annulus \\
+        R_{\tau_2}   & 7 kpc     & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
+        t_{\rm max}      & 4.2 Gyr  & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
         \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength
@@
 
+In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
+However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, either from gas stripped from dwarf galaxies or from SNe in the halo \todo{(citations; any measurements of CGM metallicity?)}.
+For this reason, we also test cases where the infalling gas is pre-enriched and its metallicity is described by
+\begin{equation}
+    \label{eq:pre-enrichment}
+    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{{\rm [X/H]}_{\rm CGM}}.
+\end{equation}
+In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2$ Gyr and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$.
+We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.
+
+\subsection{Infall Rate Parameter Selection}
+\label{sec:parameter-selection}
+
 \begin{figure*}
@@
 This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}.
-In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.
+% In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.
+
+In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
+Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1$ Gyr in the inner disk and $\tau_2=7$ Gyr at the Solar annulus.
+This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
+We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15$ Gyr at the Solar annulus and a scale radius $R_{\tau_2}=7$ kpc.
+This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
+We also run models with a linear prescription and with a uniform value for $\tau_2$ and find little difference in our key results.
 
@@
 
-In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, either from gas stripped from dwarf galaxies or from SNe in the halo \todo{(citations; any measurements of CGM metallicity?)}.
-For this reason, we also test cases where the infalling gas is pre-enriched and its metallicity is described by
-\begin{equation}
-    \label{eq:pre-enrichment}
-    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{{\rm [X/H]}_{\rm CGM}}.
-\end{equation}
-In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2$ Gyr and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$.
-We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics{figures/onezone_sfr.pdf}
-%     \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over.
-This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
-%     \label{fig:onezone-sfr}
-% \end{figure}
-
 \subsection{The Star Formation Law}
@@
 Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
+
+\begin{figure}
+    \centering
+    \includegraphics{src/tex/figures/sfe_prefactor.pdf}
+    \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
+All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
+    \label{fig:sfe-prefactor}
+\end{figure}
+
 In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
@@
 We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature.
-
-\begin{figure}
-    \centering
-    \includegraphics{src/tex/figures/sfe_prefactor.pdf}
-    \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
-All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
-    \label{fig:sfe-prefactor}
-\end{figure}
 
@@
 
+\begin{itemize}
+    \item
+\end{itemize}
+
 \section*{Acknowledgements}

### 2025-02-17 src/tex/ms.tex

@@
 where we adopt $\sigma_{\rm RM8}=2.68$ kpc as the fiducial value for the strength of radial migration.
-This is smaller than the value of $\sigma_{\rm RM8}=3.6$ kpc found by \citet{frankel_measuring_2018}, but in \todo{Section X} we explore the effect of a stronger migration prescription.
+This is smaller than the value of $\sigma_{\rm RM8}=3.6$ kpc found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.
 
@@
 \label{sec:disk-abundances}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/mdf_evolution.pdf}
+    \caption{Caption.}
+    \label{fig:mdf-evolution}
+\end{figure*}
 

### 2025-02-17 src/scripts/star_formation_history.py
create star_formation_history.py

@@ -1,0 +1,105 @@
+"""
+This script plots the infall rate, star formation rate, gas mass, and 
+star formation efficiency timescale over time for one multi-zone model.
+"""
+
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator
+import vice
+
+from utils import get_color_list, get_bin_centers
+from _globals import ONE_COLUMN_WIDTH, ZONE_WIDTH, GALR_BINS
+import paths
+
+OUTPUT_NAME = 'yZ1/fiducial/diskmodel'
+
+def main(output_name=OUTPUT_NAME, style='paper', cmap='plasma_r', verbose=False):
+    # Set up figure
+    plt.style.use(paths.styles / f'{style}.mplstyle')
+    fig, axs = plt.subplots(
+        2, 2, 
+        sharex=True, 
+        # tight_layout=True,
+        figsize=(ONE_COLUMN_WIDTH, ONE_COLUMN_WIDTH),
+        gridspec_kw={'hspace': 0.25, 'wspace': 0.3}
+    )
+    # fig.subplots_adjust(left=0.05, right=0.95, bottom=0.05, top=0.95)
+    multioutput = vice.output(str(paths.multizone / output_name))
+    axs[0,0].set_title(r'$\dot \Sigma_{\rm in}$ [M$_{\odot}\,\rm{yr}^{-1}\,\rm{kpc}^{-2}$]')
+    axs[0,0].set_yscale('log')
+    axs[0,0].set_ylim((5e-6, 0.1))
+    axs[0,1].set_title(r'$\dot \Sigma_\star$ [M$_{\odot}\,\rm{yr}^{-1}\,\rm{kpc}^{-2}$]')
+    axs[0,1].set_yscale('log')
+    axs[0,1].set_ylim((1e-5, 1e-1))
+    axs[1,0].set_title(r'$\Sigma_g$ [M$_{\odot}\,\rm{kpc}^{-2}$]')
+    axs[1,0].set_yscale('log')
+    axs[1,0].set_ylim((1e5, 2e8))
+    axs[1,1].set_title(r'$\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ [Gyr]')
+    axs[1,1].set_ylim((0, 12))
+    axs[1,1].yaxis.set_major_locator(MultipleLocator(5))
+    axs[1,1].yaxis.set_minor_locator(MultipleLocator(1))
[…]

### 2025-02-17 src/tex/ms.tex
Updates from Overleaf

--- 2025-02-13 src/tex/ms.tex
@@
 They find that inside-out formation (i.e., longer infall timescales in the outer disk) is not sufficient to reproduce observed abundance gradients, and that radial gas flows, possibly in combination with a radially-varying star formation law, are key.
-Pre-enriched infall in the inner disk ($R<8$ kpc) at the level of -0.5 dex also improves agreement with data.
+Pre-enriched infall in the inner disk ($R<8\,{\rm kpc}$) at the level of -0.5 dex also improves agreement with data.
 
@@
         Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
-        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
-        $|z|$               & $|z| < 2$ kpc                 & Eliminate halo stars \\
+        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15\,{\rm kpc}$    & Eliminate bulge \& extreme outer-disk stars \\
+        $|z|$               & $|z| < 2\,{\rm kpc}$                 & Eliminate halo stars \\
         \hline
@@
 We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog.
-When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122$ kpc \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8$ pc \citep{bennett_vertical_2019}.
+When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8\,{\rm pc}$ \citep{bennett_vertical_2019}.
 Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.
@@
 \todo{Taken from last paper.} We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
-Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{mackereth_dynamical_2019}.
+Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10\,{\rm Gyr}$ as they do in astroNN \citep{mackereth_dynamical_2019}.
 We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt} APOGEE stars with age estimates.
@@
 The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}.
-We set up a disk with radial extent $0\leq R_{\rm gal}<20$ kpc that is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc.
-We use a time-step size of $\Delta t=10$ Myr and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2$ Gyr.
+We set up a disk with radial extent $0\leq R_{\rm gal}<20\,{\rm kpc}$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
+We use a time-step size of $\Delta t=10\,{\rm Myr}$ and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
 
@@
 Stellar populations migrate between zones as described in Section \ref{sec:migration}, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones.
-We inhibit star formation past $R_{\rm gal}>15.5$ kpc, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
+We inhibit star formation past $R_{\rm gal}>15.5\,{\rm kpc}$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
 We also assign a final midplane distance to each stellar population as described in Section \ref{sec:migration}.
@@
 \end{equation}
-where $t_D=40$ Myr is the minimum SN Ia delay time, $t_{\rm max}=13.2$ Gyr is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
+where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
 Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
@@
 For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the present day.
-The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5$ Gyr ago.
+The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5\,{\rm Gyr}$ ago.
 However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.
@@
 The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia.
-Between lookback times of $\sim5-9$ Gyr, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.
+Between lookback times of $\sim5-9\,{\rm Gyr}$, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.
 The [O/Fe] evolution of all three models is nearly identical over the past 5 Gyr, and shows a similar evolution to the data apart from a $\sim0.05$ dex offset.
@@
 Table \ref{tab:yields} presents the population-averaged yields for each model.
-The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq0.5$ kpc) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
+The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq|z|\leq0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
     \label{fig:yield-outflow}
@@
 \end{equation}
-where $R_\odot=8$ kpc. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
+where $R_\odot=8\,{\rm kpc}$. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
 \begin{equation}
@@
 \end{equation}
-We adopt $R_\eta=7.2$ kpc as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
+We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
 \todo{Motivate exponential scale radius.}
@@
 \end{equation}
-We adopt a thick disk scale radius of $R_1=2.0$ kpc, a thin disk scale radius of $R_2=2.5$ kpc, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
+We adopt a thick disk scale radius of $R_1=2.0\,{\rm kpc}$, a thin disk scale radius of $R_2=2.5\,{\rm kpc}$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
 
@@
 \end{equation}
-In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2$ Gyr and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$.
+In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$.
 We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.
@@
 % The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
-% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1$ Gyr, $\tau_2\sim3-10$ Gyr, and $t_{\rm max}\sim3-5$ Gyr. 
+% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
 Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
 The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
-Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6$ Gyr.
-We adopt $\tau_1=1$ Gyr for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx+0.3$.
+Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
+We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx+0.3$.
 
@@
 A shorter $\tau_2$ produces a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces both a narrower low-$\alpha$ sequence and a narrower MDF.
-We note that our maximum value of $\tau_2=30$ Gyr is very close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns.
-Between $\tau_2=3-30$ Gyr, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
-We adopt a fiducial value of $\tau_2=15$ Gyr for the Solar neighborhood in order to minimize the width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times.
+We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is very close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns.
+Between $\tau_2=3-30\,{\rm Gyr}$, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
+We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times.
 This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}.
@@
 In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
-Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1$ Gyr in the inner disk and $\tau_2=7$ Gyr at the Solar annulus.
+Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1\,{\rm Gyr}$ in the inner disk and $\tau_2=7\,{\rm Gyr}$ at the Solar annulus.
 This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
-We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15$ Gyr at the Solar annulus and a scale radius $R_{\tau_2}=7$ kpc.
+We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\,{\rm Gyr}$ at the Solar annulus and a scale radius $R_{\tau_2}=7\,{\rm kpc}$.
 This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
@@
 
-Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic abundance loop.
-For $t_{\rm max}>2$ Gyr, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
+Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\,{\rm Gyr}$, but in this case the gas tracks do not produce the characteristic abundance loop.
+For $t_{\rm max}>2\,{\rm Gyr}$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
 The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}.
-We adopt a fiducial value of $t_{\rm max}=4.2$ Gyr so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05$ Gyr \citep{pinsonneault_apokasc-3_2024}.
+We adopt a fiducial value of $t_{\rm max}=4.2\,{\rm Gyr}$ so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\,{\rm Gyr}$ \citep{pinsonneault_apokasc-3_2024}.
 This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
@@
 \end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$ with $\gamma=1/2$ and $\tau_{\rm mol,0}=2$ Gyr.
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$ with $\gamma=1/2$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$.
 Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\varepsilon$:
@@
 
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/star_formation_history.pdf}
+    \caption{(a) The infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
+Each panel plots the history for six different zones of width $\delta R_{\rm gal}=0.1\,{\rm kpc}$, color-coded by Galactocentric radius.}
+    \label{fig:sfh}
+\end{figure}
+
+Figure \ref{fig:sfh} plots the star formation history of several different zones from our fiducial model with $y/Z_\odot=1$.
+In the inner Galaxy, the infall rate $\dot\Sigma_{\rm in}$ is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
+In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
+The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a maximum of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
+
 \subsection{Stellar Migration}
@@
 \end{equation}
-where we adopt $\sigma_{\rm RM8}=2.68$ kpc as the fiducial value for the strength of radial migration.
-This is smaller than the value of $\sigma_{\rm RM8}=3.6$ kpc found by \citet{frankel_measuring_2018}, but in \todo{Section X} we explore the effect of a stronger migration prescription.
+where we adopt $\sigma_{\rm RM8}=2.68\,{\rm kpc}$ as the fiducial value for the strength of radial migration.
+This is smaller than the value of $\sigma_{\rm RM8}=3.6\,{\rm kpc}$ found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.
 
@@
     \caption{The density of stars in the [O/Fe]--[Fe/H] plane from multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
-The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of 1 Gyr.
-Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9$ kpc and $0.5\leq|z|<1$ kpc to highlight the $\alpha$-bimodality.}
+The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
+Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\,{\rm kpc}$ and $0.5\leq|z|<1\,{\rm kpc}$ to highlight the $\alpha$-bimodality.}
     \label{fig:ofe-feh-density}
@@
 Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model at mid to high Galactic latitudes.
-Between $0.5\leq|z|<1$ kpc, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over (${\rm [Fe/H]}\approx-0.3$, ${\rm [O/Fe]}\approx0.1-0.2$), which is not seen in the APOGEE sample.
-This over-density occurs because the overall rate of chemical evolution slows $\sim2$ Gyr after the second infall, at the same time as the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
+Between $0.5\leq|z|<1\,{\rm kpc}$, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over (${\rm [Fe/H]}\approx-0.3$, ${\rm [O/Fe]}\approx0.1-0.2$), which is not seen in the APOGEE sample.
+This over-density occurs because the overall rate of chemical evolution slows $\sim2\,{\rm Gyr}$ after the second infall, at the same time as the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
 This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in models (c) and (d) of Figure \ref{fig:ofe-df}.
@@
     \caption{Stellar age--abundance relations produced by select multi-zone models.
-Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq |z| \leq 0.5$ kpc) and is color-coded by its birth radius.
+Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius.
 For visual clarity, we plot a only random mass-weighted sample of \num{10000} points in each panel.
-The black curve plots the ISM abundance at $R_{\rm gal}=8$ kpc over time.
-The red line segments plot the median abundance for APOGEE stars in 2 Gyr-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
+The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time.
+The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
 Age estimates from APOGEE stars come from \citet{leung_variational_2023}.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5$ kpc; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.}
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.}
     \label{fig:abundance-evolution}
@@
 Figure \ref{fig:abundance-evolution} shows stellar age--abundance relations for four model outputs.
-Column (a) plots the output of our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and $Z_{\rm CGM}=0$.
-The fiducial model shows two major discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9$ Gyr near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
+Column (a) plots the output of our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and $Z_{\rm CGM}=0$.
+The fiducial model shows two major discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
 We also note the present-day metallicity is still sub-Solar in the fiducial model, but this can be corrected by decreasing $\eta$.
@@
 
-The observed rise in the median abundance of stars with ages of $\sim4-8$ Gyr is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
+The observed rise in the median abundance of stars with ages of $\sim4-8\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
 Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in column (a) have sub-Solar abundances.
-Column (c) of Figure \ref{fig:abundance-evolution} presents a model with $y/Z_\odot=1$ but with a stronger migration prescription of $\sigma_{\rm RM8}=5$ kpc.
+Column (c) of Figure \ref{fig:abundance-evolution} presents a model with $y/Z_\odot=1$ but with a stronger migration prescription of $\sigma_{\rm RM8}=5\,{\rm kpc}$.
 Here, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
@@
 \label{sec:disk-abundances}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
+    \caption{Evolution of the MDF across the Galactic disk.}
+    \label{fig:mdf-evolution}
+\end{figure*}
 
@@
 {\it Right:} Output of one-zone models which assume different SN Ia DTDs with the {\tt yZ2} yield set.
-The infall parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=10$ Gyr, and $\tau_{\rm on}=3$ Gyr.
+The infall parameters are fixed at $\tau_1=1\,{\rm Gyr}$, $\tau_2=10\,{\rm Gyr}$, and $\tau_{\rm on}=3\,{\rm Gyr}$.
 {\bf Key takeaway:} the extent of the low-$\alpha$ sequence can be reduced by a more prompt SN Ia DTD, but the high-$\alpha$ sequence is also shifted to a more metal-poor regime.}
@@
 
+Radial gas flows are hard :'(
+
 \subsection{Star Formation Hiatus}
@@
     \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.
-The blue dashed curve represents the fiducial model that has an exponentially declining infall rate and constant star formation efficiency timescale $\tau_\star=2$ Gyr.
-The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4$ Gyr.
+The blue dashed curve represents the fiducial model that has an exponentially declining infall rate and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
+The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4\,{\rm Gyr}$.
 Both models assume the {\tt yZ2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
-The greyscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq2$ kpc) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
+The greyscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq|z|\leq2\,{\rm kpc}$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}
@@
 \citet{beane_rising_2024} present a simulated galaxy from the Illustris TNG50 suite that exhibits MW-like bimodality.
-They argue that the $\alpha$-bimodality is brought on by a brief ($\sim300$ Myr) quiescent period caused by bar formation.
+They argue that the $\alpha$-bimodality is brought on by a brief ($\sim300\,{\rm Myr}$) quiescent period caused by bar formation.
 The virial mass of their galaxy grows steadily throughout this period, unlike in our two-infall model where the mass grows by a factor of \todo{X} during the 1 Gyr following the second infall.

### 2025-02-17 src/tex/ms.tex
Updates from Overleaf

@@
 \todo{Mention calibrated abundances.}
+
+We supplement the APOGEE DR17 abundance data with two different age catalogs.
 
@@
     \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
-    \caption{Evolution of the MDF across the Galactic disk.}
+    \caption{Evolution of the MDF across the Galactic disk.
+Each panel presents the normalized stellar [Fe/H] distribution within a {2 kpc}-wide annulus, color-coded by the age bin.
+Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
+Distributions are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} in all panels.}
     \label{fig:mdf-evolution}

### 2025-02-18 src/tex/ms.tex
Updates from Overleaf

@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
+        Latent age          & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
         $R_{\rm gal}$     & $3 < R_{\rm gal} < 15\,{\rm kpc}$    & Eliminate bulge \& extreme outer-disk stars \\
@@
         ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
-        log(Age/Gyr)    & $0.10$     & $0.16$ \\
+        $\tau_{\rm latent}/{\rm Gyr}$    & 1.0   & $0.16$ \\
+        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & \todo{N/A} \\
         \hline
@@
 
-We obtain a sample of \input{output/sample_size.txt} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}.
+We obtain a sample of \num{171635} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}.
+Table \ref{tab:uncertainties} presents the median statistical uncertainty and uncertainty dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the calibrated [Fe/H] and [O/Fe] abundances for our sample.
 We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog.
@@
 Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.
-\todo{Mention calibrated abundances.}
 
 We supplement the APOGEE DR17 abundance data with two different age catalogs.
+The first is the ``latent'' age estimates from \citet{leung_variational_2023}, who train a variational encoder-decoder network on asteroseismic data for APOGEE red giants.
+This catalog has two main advantages for our purposes: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and the recovered ages do not plateau at $\sim10\,{\rm Gyr}$ as they do in some other neural network-derived age catalogs \citep[e.g.,][]{mackereth_dynamical_2019}.
+Following the recommendations of \citet{leung_variational_2023}, we use an upper limit on the relative age uncertainty of 40\%.
+This produces a sample of \num{57607} stars with latent age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$).
+The median uncertainty in $\log({\rm age}/{\rm Gyr})$ is 0.10 (see Table \ref{tab:uncertainties}).
 
-\todo{Taken from last paper.} We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations.
-Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10\,{\rm Gyr}$ as they do in astroNN \citep{mackereth_dynamical_2019}.
-We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt} APOGEE stars with age estimates.
-We note that we use the full sample of \input{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates.
-Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).
+Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
+\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
+This method has the benefit of providing age estimates for luminous giants, which increases the sample size at farther distances from the Sun.
+However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr.
 

### 2025-02-18 src/tex/ms.tex
Manuscript updates

@@
 \affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
+\affiliation{\osuaffil}
+\affiliation{\ccappaffil}
+\author[0000-0002-2854-5796]{John D. Roberts}
 \affiliation{\osuaffil}
@@
 However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr.
+We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
 
@@
 \begin{itemize}
-    \item
+    \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a low-$\alpha$ sequence with a fundamentally different abundance structure than observed.
+A low yield set ($y/Z_\odot=1$) coupled with lower outflows, or pre-enrichment of the infalling gas, can bring the stellar [O/Fe] distributions more in line with the data.
+    \item The large quantity of pristine gas accreted in the Solar neighborhood during the second infall phase rapidly dilutes the ISM metallicity by $\sim0.5$ dex.
+Models with a low yield set ($y/Z_\odot=1$) remain at sub-Solar metallicity until the present day, in stark contrast to the observed local age--metallicity relation.
+This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
+    \item Our models predict that the MDF evolves to higher metallicity over time throughout the disk.
+This contrasts with the APOGEE data, which show very little change in the mode over the past $\sim6-8$ Gyr.
 \end{itemize}

### 2025-02-18 src/tex/ms.tex

@@
 We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the {\tt yZ1} and {\tt yZ2} yield sets, respectively, to ensure our models could reach ${\rm [O/Fe]}\approx0.0$ by the end time.
-The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009} \todo{(are there more recent citations?)}.
+The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
 The rate for the {\tt yZ1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
@@
 Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
+The vertical dotted lines in row (c) mark the mode of the distribution in the $0-2\,{\rm kpc}$ age bin.
 Distributions are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} in all panels.}
@@
 \end{figure*}
+
+The discrepancies between the predicted and observed abundance evolution discussed in Section \ref{sec:age-abundance} are also seen across the disk.
+Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins.
+We select the $y/Z_\odot=1$ and $y/Z_\odot=2$ models with pre-enriched infall due to the relative success of these models in the previous sections.
+We use the [C/N]-derived age estimates for the APOGEE sample due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages $\leq10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
+The two-infall model predicts a very broad MDF for ages $>10$ Gyr because of the rapid enrichment of the ISM during the first infall epoch.
+
+Figure \ref{fig:mdf-evolution} shows that even with pre-enriched infall, both of our models predict that the MDF shifts to the left going from younger to older populations.
+On the other hand, the data show that the MDF broadens with age, which we attribute to radial migration, but its peak does not shift substantially over the past $\sim6-8$ Gyr.
+While the mode of the MDF shifts depending on the radial bin, its evolution is remarkably consistent over the entire disk, in line with the equilibrium scenario of \citet{johnson_milky_2024}.
+
+On the other hand, the model predictions for the MDF in the $8-10\,{\rm Gyr}$ age bin are strikingly similar to the APOGEE MDF.
+The two-infall model predicts a bimodal distribution: the metal-rich component comprises stars formed during the last Gyr of the first infall epoch, and the metal-poor component is stars formed during the first Gyr of the second infall epoch (post-dilution).
+The data show this same bimodal structure in all but the outermost radial bin, with peaks at ${\rm [Fe/H]}\approx-0.3$ and $+0.3$.
+While the location of the model peaks depends on $R_{\rm gal}$, in the data they are quite consistent from the innermost to the outermost bin.
 
@@
 This contrasts with the APOGEE data, which show very little change in the mode over the past $\sim6-8$ Gyr.
+    \item The equilibrium scenario of chemical evolution, if correct, places stricter limits on the two-infall model than other evolutionary models.
 \end{itemize}

### 2025-02-19 src/tex/ms.tex
Updates from Overleaf

@@
 \affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
-\affiliation{\osuaffil}
-\affiliation{\ccappaffil}
-\author[0000-0002-2854-5796]{John D. Roberts}
+% \affiliation{\osuaffil}
+% \affiliation{\ccappaffil}
+\author[0000-0002-2854-5796]{John D.\ Roberts}
 \affiliation{\osuaffil}
@@
 \begin{abstract}
-    Abstract.
+    % The Milky Way's stellar disk can be separated into multiple chemically and kinematically distinct components. 
+    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion epochs.
+It has successfully reproduced observed abundance patterns in the Solar neighborhood and across the disk.
+However, few studies have explored a two-infall with significant mass-loaded outflows
 \end{abstract}
 
-\section{Outline}
-\input{outline.tex}
+% \section{Outline}
+% \input{outline.tex}
 
 \section{Introduction}
-
-% To add: Carme Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra
 
@@
 \subsection{Summary of Two-Infall Papers}
+
+% To add: Carme Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra
 
@@
 Pre-enriched infall in the inner disk ($R<8\,{\rm kpc}$) at the level of -0.5 dex also improves agreement with data.
+
+\citet{palla_mgfe_2022} test prescriptions for radial migration but assume that it does not affect supernova enrichment (i.e., that most supernovae explode near the star's birthplace).
 
@@
 Table \ref{tab:uncertainties} presents the median statistical uncertainty and uncertainty dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the calibrated [Fe/H] and [O/Fe] abundances for our sample.
-We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog.
-When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8\,{\rm pc}$ \citep{bennett_vertical_2019}.
+When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}.
 Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.
@@
 We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
+\todo{Note about metallicity cutoff for luminous giants.}
 
@@
 The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
-All models use the {\tt yZ1} yield set and assume $\eta=0.4$.}
+All models use the {\tt yZ1} yield set and assume $\eta=0.2$.}
     \label{fig:twoinfall-parameters}
@@
 While the mode of the MDF shifts depending on the radial bin, its evolution is remarkably consistent over the entire disk, in line with the equilibrium scenario of \citet{johnson_milky_2024}.
+\todo{Note about metallicity cutoff for luminous giants.}
 
@@
 
-\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}}
+\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}.}
 

### 2025-02-19 src/tex/ms.tex
Manuscript updates

@@
 Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
-The vertical dotted lines in row (c) mark the mode of the distribution in the $0-2\,{\rm kpc}$ age bin.
-Distributions are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} in all panels.}
+The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference.
+Also in row (c), the gray dashed line marks the cut at ${\rm [Fe/H]}>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at ${\rm [Fe/H]}<+0.45$ for all stars with [C/N]-based ages.
+Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex}.}
     \label{fig:mdf-evolution}

### 2025-02-20 src/scripts/ofe_feh_cn_age.py
add alternate absz version

@@ -18,7 +18,7 @@ AGE_BINS = [1, 2, 4, 6, 8, 10]
 # AGE_BINS = [0, 2, 4, 6, 8, 10, 13]
 FEH_LIM = (-0.9, 0.5)
 OFE_LIM = (-0.15, 0.55)
-ABSZ_LIM = (0, 2)
+ABSZ_LIM = (0, 0.5)
 GRIDSIZE = 20
 AGE_COL = 'CN_AGE'
 # VMAX = 0.11

### 2025-02-20 src/tex/ms.tex

@@
 \begin{abstract}
-    % The Milky Way's stellar disk can be separated into multiple chemically and kinematically distinct components. 
-    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion epochs.
-It has successfully reproduced observed abundance patterns in the Solar neighborhood and across the disk.
-However, few studies have explored a two-infall with significant mass-loaded outflows
+    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion episodes.
+It has successfully reproduced observed abundance patterns such as the [$\alpha$/Fe]-bimodality in the Solar neighborhood and across the disk.
+However, few studies have explored a two-infall model with significant mass-loaded outflows, nor compared model results with comprehensive age--abundance data across the disk.
+We run multi-zone galactic chemical evolution (GCE) models with a two-infall star formation history, radially-dependent mass-loaded outflows, and a prescription for radial migration of stellar populations.
+We compare our model results to abundance patterns across the disk from the Apache Point Observatory Galactic Evolution Experiment (APOGEE) data release 17, supplemented with stellar age estimates using multiple methods.
+We find that the two-infall model struggles to reproduce all the observed characteristics of the chemical thin disk.
+Models with low nucleosynthetic yields and outflows experience long-lasting dilution of the gas-phase metallicity which contradicts the local age--metallicity relation.
+Conversely, models with higher yields and outflows fail to reproduce stellar [$\alpha$/Fe] distributions across the disk \todo{(should I be more specific?)}.
+These issues can be mitigated, but not completely solved, by enriching the accreted gas to low metallicity.
 \end{abstract}

### 2025-02-21 src/tex/ms.tex

@@
 The fiducial model shows two major discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
-We also note the present-day metallicity is still sub-Solar in the fiducial model, but this can be corrected by decreasing $\eta$.
+The evolution of [Fe/H] is similar, but the approach to Solar abundance is slower because of the additional delay imposed on Fe production from SNe Ia.
 A higher yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
-However, a consequence of these higher yields is a poor fit to the stellar [O/Fe] distribution, as discussed in Section \ref{sec:abundance-distributions}.
+However, model (b) produces a poorer fit to the age--[O/Fe] relation; the decline in [O/Fe] over the thin disk epoch is much steeper than the data.
 
@@
 While the location of the model peaks depends on $R_{\rm gal}$, in the data they are quite consistent from the innermost to the outermost bin.
+\todo{I actually think the two-infall model gets this right for the wrong reasons.
+In the data, the left peak is the high-$\alpha$ sequence and the right is the high-metallicity end of the low-$\alpha$ sequence.
+In the model, the {\it right} peak is produced during the first infall (i.e., thick disk) and the {\it left} is immediately after the second infall (i.e., low-metallicity end of thin disk).}
 

### 2025-02-21 src/tex/ms.tex

@@
         ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
-        $\tau_{\rm latent}/{\rm Gyr}$    & 1.0   & $0.16$ \\
+        $\log_{10}(\tau_{\rm latent}/{\rm Gyr})$    & 0.10   & $0.16$ \\
         $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & \todo{N/A} \\
@@
 Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
-The median APOGEE abundance uncertainties were forward-modeled onto the model outputs.
+The median APOGEE abundance uncertainties were forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
 For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
@@
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius.
+A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
 For visual clarity, we plot a only random mass-weighted sample of \num{10000} points in each panel.
@@
 Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
+A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
 The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference.

### 2025-02-21 src/scripts/all_paper_plots.sh
add bash script for all plots

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+# Tables and other output
+python apogee_regions_table.py
+python yields.py
+
+# Plots
+python yield_outflow.py
+python onezone_params.py
+python sfe_prefactor.py
+python star_formation_history.py
+python ofe_df_comparison.py
+python ofe_feh_density.py
+python abundance_evolution.py
+python mdf_evolution.py
+python onezone_sfe_hiatus.py

### 2025-02-21 src/scripts/run_all_models.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-NSTARS=2
+NSTARS=8
 OUTFLOWS=bespoke
 EVOLUTION=twoinfall_expvar
 

### 2025-02-25 src/scripts/onezone_eta.py
plot updates

@@ -1,60 +1,0 @@
-"""
-This script plots a one-zone VICE model with the equilibrium-calibrated
-mass-loading factor.
-"""
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-import vice
-
-from multizone.src.yields import yZ1
-from multizone.src import models, outflows
-from track_and_mdf import setup_figure, plot_vice_onezone
-import paths
-from _globals import ONEZONE_DEFAULTS, ZONE_WIDTH
-
-RADIUS = 8.
-ONSET = 4. # Gyr
-
-
-def main():
-    plt.style.use(paths.styles / "paper.mplstyle")
-    fig, axs = setup_figure()
-    
-    output_dir = paths.data / "onezone" / "eta"
-    if not output_dir.exists():
-        output_dir.mkdir(parents=True)
-    name = str(output_dir / "equilibrium")
-    
-    simtime = np.arange(0, 13.21, 0.01)
-    
-    eta_func = outflows.equilibrium(
-        tau_star=2., tau_sfh=10., alpha_h_eq=0.1
-    )
-    
-    area = np.pi * ((RADIUS + ZONE_WIDTH)**2 - RADIUS**2)
-    
-    sz = vice.singlezone(
-        name = name,
-        func = models.twoinfall(
-            RADIUS, 
-            first_timescale=1., 
-            second_timescale=10., 
-            onset=ONSET),
-        mode = "ifr",
-        **ONEZONE_DEFAULTS
-    )
-    sz.eta = eta_func(RADIUS)
-    print(eta_func(RADIUS))
-    sz.tau_star = models.twoinfall_sf_law(area, onset=ONSET)
-    sz.run(simtime, overwrite=True)
-    
-    plot_vice_onezone(name, fig=fig, axs=axs)
-    
-    plt.savefig(paths.figures / 'onezone_eta')
-    plt.close()
-    
-
-if __name__ == "__main__":
-    main()

### 2025-02-25 src/tex/ms.tex
Updates from Overleaf

@@
 
-The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks.
-The infall history of any given region of the disk is described by two successive, exponentially declining bursts, which explain the origin of the thick and thin disks respectively.
+\todo{Hook, summary of alpha-bimodality.}
 
-\subsection{Summary of Two-Infall Papers}
+% Summary of two-infall literature
+The two-infall model was first developed by \citet{chiappini_chemical_1997} to explain the origin of the thick and thin disks.
+Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts.
+The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, and the delayed production of Fe by SNe Ia allows the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between.
+Varying the timescale of the second infall produced inside-out disk growth and a radial abundance gradient.
+Additionally, the two-infall model of \citet{chiappini_chemical_1997} successfully reproduced Solar neighborhood abundance distributions and the age--metallicity relation.
 
-% To add: Carme Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra
+Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, and others have explored in its context the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, modifications to the recycling treatment such as galactic fountains and a metal cooling timescale \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
+Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.
 
-% Summary of two-infall papers
-\citet{matteucci_galactic_1989} modeled the galaxy with a two-component model, a one-zone model for the halo and concentric shell zones for the disk.
-They used a simple exponential gas infall (so not yet a two-infall model), where the infall timescale increased proportionally with radius.
-They studied cases with primordial and pre-enriched gas infall, finding that the former produces a more realistic metallicity distribution in the Solar neighborhood.
-Their inside-out disk evolution produced good agreement with observed abundance gradients.
+\todo{Observational evidence.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model.
 
-\citet{chiappini_chemical_1997} presented the first two-infall model of the MW disk.
-They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall increasing linearly with radius.
-They assume the formation timescale of the thick disk is 1 Gyr, and the time of the second infall is 2 Gyr.
-They also assume a lower threshold on the gas density required for star formation, which produces a star formation hiatus at the end of the thick disk phase.
-They also noted the ``loop'' that appears in the \aFe--[Fe/H] relation during the thin disk phase.
-They mostly compare to Solar neighborhood data.
+\todo{Outflows. Their arguments against. Our arguments for.}
 
-\citet{chiappini_abundance_2001} updated their model to fit the observed abundance, stellar, and gas gradients in the Milky Way disk.
-They find that a density threshold for star formation, making a gap in star formation between the halo and disk phases, is necessary to reproduce observational data.
-They argue that the details of halo formation also have a strong impact on the outer disk.
-No radial flows or outflows.
-I'm confused about their distinction between halo and thick disk, if any.
+\todo{Summary of secular evolution models which claim alpha-bimodality.}
 
-\citet{chiappini_oxygen_2003} compare model predictions of C, N, and O to Milky Way and other spiral galaxy data.
-They predict a very slow enrichment between the birth of the Sun and present day, which they claim is due to their adopted gas density threshold for star formation (the infall rate is low enough that the SFR oscillates from timestep to timestep).
+\todo{Introduce equilibrium model.}
 
-\citet{matteucci_effect_2009} investigated different SN Ia delay time distributions using the \citep{chiappini_chemical_1997,chiappini_abundance_2001} model.
-They use a model for the full disk but compare only to Solar neighborhood data.
-They concluded that some prompt SN Ia enrichment is necessary to match observed abundance patterns.
-
-\citet{spitoni_effects_2009} relaxed the instantaneous recycling approximation in two different ways: galactic fountains (i.e., SN ejecta are launched out of the disk and take some time to return) and metal cooling (i.e., newly-enriched hot gas takes time to cool before it can form stars).
-They found that fountains do not strongly affect the evolution of the $\alpha$-elements for short (few hundred Myr) timescales.
-The effect of a metal cooling timescale is similarly negligible if the yields are not dependent on metallicity.
-
-\citet{spitoni_effects_2011} find that a two-infall model of the disk without gas exchange produces a radial metallicity gradient which is too shallow.
-They implement an inward radial gas flow on the order of $\sim0-4$ km s$^{-1}$ which varies with radius, and find that it improves agreement with the observed gradient.
-However, they found that a variable star formation efficiency with radius in combination with a gas density threshold for star formation could also reproduce the observed gradient without radial flows.
-
-\citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
-They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
-This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
-They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
-Their only point of comparison with data is the local G-dwarf metallicity distribution.
-
-\citet{grisoni_ambre_2017} argue for a ``parallel'' scenario, where the thick and thin disks form simultaneously but with very different infall timescales (0.1 and 7 Gyr, respectively).
-They compare their models with stellar abundances from the AMBRE sample of solar-neighborhood dwarfs.
-They argue that the parallel scenario can produce metal-rich high-alpha stars in situ, whereas in the two-infall scenario these stars would have to migrate from the inner disk.
-
-\citet{palla_chemical_2020} explored radial gas flows, variable star formation efficiency of the thin disk, and the onset time of the second infall (but not the infall timescales).
-They find that inside-out formation (i.e., longer infall timescales in the outer disk) is not sufficient to reproduce observed abundance gradients, and that radial gas flows, possibly in combination with a radially-varying star formation law, are key.
-Pre-enriched infall in the inner disk ($R<8\,{\rm kpc}$) at the level of -0.5 dex also improves agreement with data.
-
-\citet{palla_mgfe_2022} test prescriptions for radial migration but assume that it does not affect supernova enrichment (i.e., that most supernovae explode near the star's birthplace).
-
-% Radial gas flows
-Some two-infall studies \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
-
-% Three-infall
-Motivated by constraints on the SFH by {\it Gaia}, \citet{spitoni_beyond_2023} proposed the three-infall model, an extension with a third phase of exponential gas infall in the last few Gyr.
-
-\citet{palla_mapping_2024} compare model predictions to abundances and ages of open clusters from the {\it Gaia}-ESO survey.
-They find that the two-infall model over-predicts the metallicity of the youngest clusters, a problem which is fixed by the three-infall model.
-A version of the three-infall model with milder dilution (mild pre-enrichment of the gas with a smaller amount of infall) compared to \citet{spitoni_beyond_2023} can simultaneously match the metalliticy of old, intermediate, and young clusters across the disk.
-
-\citet{spitoni_remind_2024}
+\todo{Goal of paper.}
 
@@
 We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.
+\todo{Other GCE models that do this:} \citet{palla_chemical_2020,spitoni_remind_2024,johnson_milky_2024}
 
@@
 
+\todo{Summary of problem: the two-infall model is boxed in by data.}
+
 % \subsection{The SN Ia Delay-Time Distribution}
@@
 
+\subsection{Radial Migration}
+\label{sec:migration-discussion}
+
+This study is not the first to apply a prescription for radial migration to a two-infall GCE model.
+\citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
+They prescribed some fraction of stars from the inner and outer Galaxy which contribute to the local present-day population based on a constant migration speed, and they also assumed some fraction of stars born in the Solar neighborhood will have migrated elsewhere.
+This method can improve agreement with the observed local metallicity distribution, but does not scale to abundance distributions across the disk.
+\citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to the diffusion treatment of \citet{frankel_measuring_2018} and found similar results.
+
+% \citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
+They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
+This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
+They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
+Their only point of comparison with data is the local G-dwarf metallicity distribution.
+
+Our method described in Section \ref{sec:migration} can affect abundance distributions across the Galaxy via migration, not just for the Solar neighborhood.
+We also note an important distinction between our method and that of \citet{spitoni_effect_2015}: SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
+This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
+So, a significant fraction of SN Ia progenitors born in a given zone will enrich a disparate region of the Galaxy.
+
 \subsection{Radial Gas Flows}
@@
 
-Radial gas flows are hard :'(
+\todo{Radial gas flows are hard :'(}
+
+Some two-infall studies \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
+
+\citet{spitoni_effects_2011} find that a two-infall model of the disk without gas exchange produces a radial metallicity gradient which is too shallow.
+They implement an inward radial gas flow on the order of $\sim0-4$ km s$^{-1}$ which varies with radius, and find that it improves agreement with the observed gradient.
+However, they found that a variable star formation efficiency with radius in combination with a gas density threshold for star formation could also reproduce the observed gradient without radial flows.
 

### 2025-02-28 src/scripts/multizone/_globals.py
add diskmodel subclasses for BHG+16 and Palla+20

@@ -35,6 +35,3 @@ THIN_DISK_SCALE_RADIUS = 2.5 # kpc
 THICK_DISK_SCALE_RADIUS = 2.0 # kpc
 THICK_TO_THIN_RATIO = 0.27 # at r = 0
 GAS_DISK_SCALE_RADIUS = 3.6 # kpc
-
-# Exponential scale radius of the outflow mass-loading factor
-ETA_SCALE_RADIUS = 5 # kpc

### 2025-02-28 src/scripts/multizone/src/models/diskmodel.py

@@ -62,7 +62,7 @@ class two_component_disk(double_exponential):
         norm = self.normalize(rmax)
         self.first.norm *= mass * norm
         self.second.norm *= mass * norm
-    
+        
     def normalize(self, rmax, dr=0.1):
         """
         Normalize the total mass of the disk to 1.
@@ -139,7 +139,7 @@ class two_component_disk(double_exponential):
         """
         return self.ratio * self.second(radius)
         
-    def thick_to_thin(self, radius):
+    def thick_to_thin_ratio(self, radius):
         """
         Calculate the ratio of surface mass density between the components.
         
@@ -155,3 +155,47 @@ class two_component_disk(double_exponential):
         
         """
         return self.thick_disk(radius) / self.thin_disk(radius)
+
+
+class BHG16(two_component_disk):
+    """
+    Subclass of ``two_component_disk`` which adopts the disk parameters from
+    Bland-Hawthorn & Gerhard (2016).
+    """
+    def __init__(self):
+        super().__init__(ratio=0.27, rs_thin=2.5, rs_thick=2.0)
+
+
+class Palla20(two_component_disk):
+    """
+    Subclass of ``two_component_disk`` which adopts the disk parameters from
+    the Palla et al. (2020) multizone GCE model.
+    
+    Parameters
+    ----------
+    sigma_thin : float [default: 54.0]
+        Surface mass density of the thin disk in the Solar neighborhood in 
+        Msun pc^-2.
+    sigma_thick : float [default: 12.3]
+        Surface mass density of the thick disk in the Solar neighborhood in 
+        Msun pc^-2.
+    rs_thin : float [default: 3.5]
+        Thin disk scale radius in kpc.
+    rs_thick : float [default: 2.3]
+        Thick disk scale radius in kpc.
+    R0 : float [default: 8.0]
+        Galactocentric radius of the Sun in kpc.
+    """
+    def __init__(self, sigma_thin=54.0, sigma_thick=12.3, rs_thin=3.5, 
+                 rs_thick=2.3, R0=8.0):
+        # Stellar surface density ratio at the Solar neighborhood
+        solar_ratio = sigma_thick / sigma_thin
+        # Set the central thick-to-thin ratio
+        central_ratio = solar_ratio * m.exp(-R0 * (1 / rs_thin - 1 / rs_thick))
+        # Initialize with scale radii
[…]

### 2025-02-28 src/tex/outline.tex

@@
             \item Altering the outflow prescription
-            \item Radial gas flows
         \end{enumerate}
@@
         \end{enumerate}
+        \item Radial gas flows
         \item SF hiatus not driven by infall history
@@
 \end{enumerate}
+
+\subsection{Summary of Two-Infall Papers}
+
+% To add: Carme Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra
+
+% Summary of two-infall papers
+\citet{matteucci_galactic_1989} modeled the galaxy with a two-component model, a one-zone model for the halo and concentric shell zones for the disk.
+They used a simple exponential gas infall (so not yet a two-infall model), where the infall timescale increased proportionally with radius.
+They studied cases with primordial and pre-enriched gas infall, finding that the former produces a more realistic metallicity distribution in the Solar neighborhood.
+Their inside-out disk evolution produced good agreement with observed abundance gradients.
+
+\citet{chiappini_chemical_1997} presented the first two-infall model of the MW disk.
+They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall increasing linearly with radius.
+They assume the formation timescale of the thick disk is 1 Gyr, and the time of the second infall is 2 Gyr.
+They also assume a lower threshold on the gas density required for star formation, which produces a star formation hiatus at the end of the thick disk phase.
+They also noted the ``loop'' that appears in the \aFe--[Fe/H] relation during the thin disk phase.
+They mostly compare to Solar neighborhood data.
+
+\citet{chiappini_abundance_2001} updated their model to fit the observed abundance, stellar, and gas gradients in the Milky Way disk.
+They find that a density threshold for star formation, making a gap in star formation between the halo and disk phases, is necessary to reproduce observational data.
+They argue that the details of halo formation also have a strong impact on the outer disk.
+No radial flows or outflows.
+I'm confused about their distinction between halo and thick disk, if any.
+
+\citet{chiappini_oxygen_2003} compare model predictions of C, N, and O to Milky Way and other spiral galaxy data.
+They predict a very slow enrichment between the birth of the Sun and present day, which they claim is due to their adopted gas density threshold for star formation (the infall rate is low enough that the SFR oscillates from timestep to timestep).
+
+\citet{matteucci_effect_2009} investigated different SN Ia delay time distributions using the \citep{chiappini_chemical_1997,chiappini_abundance_2001} model.
+They use a model for the full disk but compare only to Solar neighborhood data.
+They concluded that some prompt SN Ia enrichment is necessary to match observed abundance patterns.
+
+\citet{spitoni_effects_2009} relaxed the instantaneous recycling approximation in two different ways: galactic fountains (i.e., SN ejecta are launched out of the disk and take some time to return) and metal cooling (i.e., newly-enriched hot gas takes time to cool before it can form stars).
+They found that fountains do not strongly affect the evolution of the $\alpha$-elements for short (few hundred Myr) timescales.
+The effect of a metal cooling timescale is similarly negligible if the yields are not dependent on metallicity.
+
+\citet{grisoni_ambre_2017} argue for a ``parallel'' scenario, where the thick and thin disks form simultaneously but with very different infall timescales (0.1 and 7 Gyr, respectively).
+They compare their models with stellar abundances from the AMBRE sample of solar-neighborhood dwarfs.
+They argue that the parallel scenario can produce metal-rich high-alpha stars in situ, whereas in the two-infall scenario these stars would have to migrate from the inner disk.
+
+\citet{spitoni_galactic_2019} compare a two-infall model for the Solar neighborhood to the parallel infall scenario of \citet{grisoni_ambre_2017}.
+They argue that the two-infall model reproduces the observed age distribution of the high-$\alpha$ and low-$\alpha$ sequences and the age--metallicity relation, but they argue that it requires a longer delay of $\sim4$ Gyr between the first and second infalls.
+
+\citet{palla_chemical_2020} explored radial gas flows, variable star formation efficiency of the thin disk, and the onset time of the second infall (but not the infall timescales).
+They find that inside-out formation (i.e., longer infall timescales in the outer disk) is not sufficient to reproduce observed abundance gradients, and that radial gas flows, possibly in combination with a radially-varying star formation law, are key.
+Pre-enriched infall in the inner disk ($R<8\,{\rm kpc}$) at the level of -0.5 dex also improves agreement with data.
+
+% Three-infall
+Motivated by constraints on the SFH by {\it Gaia}, \citet{spitoni_beyond_2023} proposed the three-infall model, an extension with a third phase of exponential gas infall in the last few Gyr.
+They argue that the Gaia DR3 data show a population of young stars with sub-Solar abundances which is predicted by the most recent infall.
+
+\citet{palla_mapping_2024} compare model predictions to abundances and ages of open clusters from the {\it Gaia}-ESO survey.
+They find that the two-infall model over-predicts the metallicity of the youngest clusters, a problem which is fixed by the three-infall model.
+A version of the three-infall model with milder dilution (mild pre-enrichment of the gas with a smaller amount of infall) compared to \citet{spitoni_beyond_2023} can simultaneously match the metalliticy of old, intermediate, and young clusters across the disk.
+
+\citet{spitoni_remind_2024} argue that the high- and low-$\alpha$ sequences being separated in [$\alpha$/Fe] but quite similar in [$\alpha$/H] implies a hiatus in star formation, which is produced by the two-infall model of \citet{spitoni_galactic_2019}.
+They look at birth radius estimates and find evidence for two modes in the low-$\alpha$ sequence.
+They use pre-enriched gas infall at the level of $\rm{[Fe/H]}=-0.8$.

### 2025-03-06 src/scripts/multizone/src/models/twoinfall.py
Update defaults; allow function for second timescale

@@ -16,12 +16,13 @@ from .normalize import normalize_ifrmode, integrate_infall
 from .gradient import gradient, thick_to_thin_ratio
 from .twoinfall_sf_law import twoinfall_sf_law
 from .diskmodel import two_component_disk
-import vice
+from ..outflows import equilibrium
 import math as m
 
 FIRST_TIMESCALE = 1. # Gyr
 SECOND_TIMESCALE = 15. # Gyr
 SECOND_ONSET = 4.2 # Gyr
+
 
 class twoinfall(double_exponential):
     r"""
@@ -37,8 +38,10 @@ class twoinfall(double_exponential):
         The onset time of the second exponential infall in Gyr.
     first_timescale : float [default: 1.0]
         The timescale of the first exponential infall in Gyr.
-    second_timescale : float [default: 10.0]
-        The timescale of the second exponential infall in Gyr.
+    second_timescale : float or function [default: 15.0]
+        The timescale of the second exponential infall in Gyr. If a function,
+        must take one argument, which is the radius in kpc, and return a
+        timescale in Gyr.
     vgas : float [default: 0.0]
         Radial gas velocity in kpc/Gyr. Positive for outward flow.
     dt : float [default : 0.01]
@@ -65,7 +68,7 @@ class twoinfall(double_exponential):
             self, 
             radius, 
             # diskmodel = two_component_disk(),
-            mass_loading = vice.milkyway.default_mass_loading, 
+            mass_loading = equilibrium(), 
             disk_ratio = thick_to_thin_ratio,
             onset = SECOND_ONSET, 
             first_timescale = FIRST_TIMESCALE, 
@@ -79,7 +82,10 @@ class twoinfall(double_exponential):
     ):
         super().__init__(onset=onset, ratio=1.)
         self.first.timescale = first_timescale 
-        self.second.timescale = second_timescale
+        if callable(second_timescale):
+            self.second.timescale = second_timescale(radius)
+        else:
+            self.second.timescale = second_timescale
         # Initialize the star formation law
         area = m.pi * ((radius + dr/2.)**2 - (radius - dr/2.)**2)
         self.tau_star = twoinfall_sf_law(

### 2025-03-06 src/tex/ms.tex

@@
 \newcommand{\aFe}{[$\alpha$/Fe]\xspace}
+\newcommand{\mathXH}{{\rm [X/H]}}
+\newcommand{\mathOH}{{\rm [O/H]}}
+\newcommand{\mathFeH}{{\rm [Fe/H]}}
+\newcommand{\mathOFe}{{\rm [O/Fe]}}
+\newcommand{\mathaFe}{{\rm [$\alpha$/Fe]}}
+\newcommand{\yZ}[1]{$y/Z_\odot=#1$}
 \newcommand{\vice}{{\tt VICE}\xspace}
@@
 % Title
-\title{A Two-Infall Star Formation History with Outflows and Radial Migration}
+\title{The Two-Infall Model Across Space and Time for a Milky Way in Equilibrium}
 
 % Author list
+% \author[]{Amanda Ash}
 \author[0000-0003-3781-0747]{Liam O.\ Dubay}
@@
 We find that the two-infall model struggles to reproduce all the observed characteristics of the chemical thin disk.
-Models with low nucleosynthetic yields and outflows experience long-lasting dilution of the gas-phase metallicity which contradicts the local age--metallicity relation.
-Conversely, models with higher yields and outflows fail to reproduce stellar [$\alpha$/Fe] distributions across the disk \todo{(should I be more specific?)}.
-These issues can be mitigated, but not completely solved, by enriching the accreted gas to low metallicity.
+Models with low nucleosynthetic yields and weak outflows experience long-lasting dilution of the gas-phase metallicity which contradicts the local age--metallicity relation.
+Conversely, models with higher yields and stronger outflows fail to reproduce the thin disk [$\alpha$/Fe] distribution.
+These issues can be mitigated, but not completely solved, by pre-enriching the accreted gas to low metallicity.
+In the context of the equilibrium scenario recently proposed by \citet{johnson_milky_2024}, the two-infall model must overcome these inherent limitations to be compatible with all observations.
 \end{abstract}
@@
 
-\todo{Hook, summary of alpha-bimodality.}
+% \todo{Hook, summary of alpha-bimodality.}
+Studies of galactic chemical evolution (GCE) aim to explain observed stellar abundance patterns by modeling the star formation history of the Milky Way.
+A long-standing paradigm of GCE has been that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars.
+In this view, one feature of the Milky Way disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
+The high-$\alpha$ sequence consists of old stars \citep[$\sim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk.
+The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
 
 % Summary of two-infall literature
-The two-infall model was first developed by \citet{chiappini_chemical_1997} to explain the origin of the thick and thin disks.
+The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the thick and thin disks.
 Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts.
-The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, and the delayed production of Fe by SNe Ia allows the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between.
-Varying the timescale of the second infall produced inside-out disk growth and a radial abundance gradient.
-Additionally, the two-infall model of \citet{chiappini_chemical_1997} successfully reproduced Solar neighborhood abundance distributions and the age--metallicity relation.
+The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between.
+% By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
+The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.
 
-Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, and others have explored in its context the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, modifications to the recycling treatment such as galactic fountains and a metal cooling timescale \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
+Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, and others have explored in its context the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
 Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.
 
-\todo{Observational evidence.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model.
+\todo{Observational evidence.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
+\citet{chen_recent_2025}
 
-\todo{Outflows. Their arguments against. Our arguments for.}
+\todo{Outflows.} Most previous studies of the two-infall model do not include mass-loaded outflows.
+Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to the point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal.
+However, other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \todo{(citations)}.
+Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \todo{(citations)} and dwarf galaxies \todo{(citations)} but not MW-like systems due to current detection limits \todo{(citations)}.
+We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient.
+
+\todo{Migration.} The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
+\todo{Talk about migration studies and why we don't need a single evolutionary track to explain the bimodality.}
 
@@
         [Fe/H]          & $0.0089$   & $0.0060$ \\
-        ${\rm [O/Fe]}$  & $0.019$    & $0.031$ \\
+        $\mathOFe$  & $0.019$    & $0.031$ \\
         $\log_{10}(\tau_{\rm latent}/{\rm Gyr})$    & 0.10   & $0.16$ \\
@@
 \todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
-This method has the benefit of providing age estimates for luminous giants, which increases the sample size at farther distances from the Sun.
+This method has the benefit of providing age estimates for luminous giants, which increases the sample size at larger distances from the Sun.
 However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr.
@@
         % Yields
-        y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
-        N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
-        f_{\rm Ia}(t)   & Plateau   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
+        % y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
+        % N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
+        f_{\rm Ia}(t)   & Equation \ref{eq:plateau-dtd}   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
         % t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
@@
         % Outflows
-        \eta_\odot      & 0.2       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
-        R_\eta          & 4.2 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
+        % \eta_\odot      & 0.2       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
+        R_\eta          & 5.0 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
         f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
-        {\rm [X/H]}_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
+        \mathXH_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
         \tau_1          & 1 Gyr     & \ref{sec:parameter-selection}     & Timescale of the first infall epoch \\
@@
 
-The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain.
-This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$ --- in other words, the scale of SN yields relative to the Solar abundance is of order unity.
-
 \begin{table}
@@
 
-We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the {\tt yZ1} and {\tt yZ2} yield sets, respectively, to ensure our models could reach ${\rm [O/Fe]}\approx0.0$ by the end time.
-The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
-The rate for the {\tt yZ1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
-The rate for the {\tt yZ2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}.
+The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain.
+This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
+Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$ --- in other words, the scale of SN yields is similar to the Solar abundance.
+However, \citet{johnson_milky_2024} found that GCE models with yields at this scale approach present-day abundances too slowly.
+We therefore investigate yield sets at multiple scales, which are presented in Table \ref{tab:yields}.
 
-The SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
+The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is calculated so that the combined Fe yield $y_{\rm Fe}^{\rm Ia+CC}=y/Z_\odot$.
+We further increase $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the \yZ{1} and \yZ{2} yield sets, respectively, to ensure that our models reach $\mathOFe\approx0.0$ by the end time.
+The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
+The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
+The rate for the \yZ{2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}, while the rate for the \yZ{3} yield set is generally higher than literature values.
+
+Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion.
+The time-dependent SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
 \begin{equation}
@@
 \end{equation}
-where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
-Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
+where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per unit mass of star formation, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
+Motivated by the finding by \citet{dubay_galactic_2024} that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence, we adopt a wide plateau DTD of the form
 \begin{equation}
@@
 
-\todo{Compare these yields to previous studies.}
+\todo{I'd like to compare these yields to previous studies, but it's been very difficult to make that comparison.
+I'm unsure whether the \citet{francois_evolution_2004} yields are net or gross (probably gross since their baseline is \citet{woosley_evolution_1995}).
+I tried to implement their yield tables in VICE, but the chemical evolution tracks came out looking very wrong.
+Also, they use a weird IMF.} \citet{francois_evolution_2004} report that their models are insensitive to changes in the yield at a factor of 2 level.
 
@@
 The data show that the evolution in [O/H] is close to flat over the past 5 Gyr.
-The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model shows significant evolution of $\sim0.2$ dex during the same time period.
+The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model increases significantly by $\sim0.2$ dex during the same time period.
 The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia.
-Between lookback times of $\sim5-9\,{\rm Gyr}$, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.
-The [O/Fe] evolution of all three models is nearly identical over the past 5 Gyr, and shows a similar evolution to the data apart from a $\sim0.05$ dex offset.
+Between lookback times of $\sim5-9\,{\rm Gyr}$, the modes of [O/H] and [Fe/H] are higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.
+
+The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset.
 \todo{Is this offset a problem?
-I could raise the SN Ia yields, but the global distributions would not match quite as well.}
+I could raise the SN Ia yields, but the global distributions would not match quite as well.} The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields.
+Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution.
+As the $y/Z_\odot=2$ and $y/Z_\odot=3$ models show generally similar behavior, we focus on the $y/Z_\odot=1$ and $y/Z_\odot=2$ yield sets for this work.
 
@@
 Table \ref{tab:yields} presents the population-averaged yields for each model.
-The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq|z|\leq0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
+The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
     \label{fig:yield-outflow}
@@
 
-Most of the previous two-infall studies assume no mass-loaded outflows.
-Even in studies such as \citet{palicio_analytic_2023} which do incorporate Galactic winds, they are relatively weak ($\eta\approx0.2$).
+Most studies of the two-infall model assume the Milky Way has no significant mass-loaded outflows.
+Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023}.
+To achieve a realistic radial metallicity gradient, many studies use a prescription for the infall timescale of the thin disk which increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
+Because we aim to study the effect of the yield assumptions on two-infall model predictions, we use mass-loaded outflows to control the final state of chemical evolution across the disk.
+As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
 
-\todo{Motivate our use of outflows. Connect to James' equilibrium paper.}
-
-\citet{weinberg_equilibrium_2017} showed that in the limit of continuous star formation, the ISM abundance approaches an equilibrium which is determined by the balance of yields, outflows, and star formation.
-We calculate the mass-loading factor required to reach equilibrium at the Solar abundance as
+\citet{weinberg_equilibrium_2017} showed that in the limit of continuous star formation, the ISM abundance approaches an equilibrium which is determined by the balance of yields, outflows, and star formation timescales.
+The mass-loading factor $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ required to reach equilibrium at Solar metallicity is
 \begin{equation}
+    \label{eq:equilibrium-eta}
     \eta_\odot = y_{\rm O}^{\rm CC} / Z_{\rm O,\odot} - 1 + r + \tau_\star / \tau_{\rm SFH},
@@
 where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, and $\tau_{\rm SFH}$ is the star formation timescale.
+Equation \ref{eq:equilibrium-eta} informs our choice of $\eta$, but it is inaccurate in the two-infall case because of the bursty star formation history.
+Therefore, we tune the value of $\eta_\odot$ so that the model reaches $\mathOH=0.0$ by the end for each yield set, shown in Table \ref{tab:yields}.
+% we find that if we adopt this prescription, models with $y/Z_\odot=1$ predict sub-Solar abundances at the present day because they have not yet reached their equilibrium value.
 
-We adopt a fiducial prescription for the outflow mass-loading factor which increases exponentially with radius:
+We adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
 \begin{equation}
@@
 \end{equation}
-where $R_\odot=8\,{\rm kpc}$. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
+where $R_\odot=8\,{\rm kpc}$. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla\mathOH_{\rm eq}$:
 \begin{equation}
-    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}.
+    R_\eta = -\frac{1}{\nabla\mathOH_{\rm eq} \times\ln(10)}.
 \end{equation}
-We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
+We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
 \todo{Motivate exponential scale radius.}
@@
     \label{eq:pre-enrichment}
-    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{{\rm [X/H]}_{\rm CGM}}.
+    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{\mathXH_{\rm CGM}}.
 \end{equation}
-In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$.
-We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.
+In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}$.
+We also investigate cases where the CGM is $\alpha$-enhanced, i.e., $\mathOFe_{\rm CGM}>0$.
 \todo{Other GCE models that do this:} \citet{palla_chemical_2020,spitoni_remind_2024,johnson_milky_2024}
@@
 Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
-We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx+0.3$.
+We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.3$.
 
@@
 The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}.
-We adopt a fiducial value of $t_{\rm max}=4.2\,{\rm Gyr}$ so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\,{\rm Gyr}$ \citep{pinsonneault_apokasc-3_2024}.
+We adopt a fiducial value of $t_{\rm max}=4.2\,{\rm Gyr}$ so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\,{\rm Gyr}$ \citep{pinsonneault_apokasc-3_2025}.
 This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
 
-We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio regardless of the infall parameters.
+We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
 The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus.
 In our multi-zone models, most of the high-$\alpha$ stars present in the Solar neighborhood have migrated from the inner Galaxy.
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/spitoni_comparison.pdf}
+    \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021}.
+All models use the $y/Z_\odot=1$ yield set.
+The time markers and marginal panels are the same as in Figure \ref{fig:twoinfall-parameters}.
+We also include a 2-D heatmap of the APOGEE stellar abundances in each panel for reference.
+APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<120$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.
+\todo{Should I instead compare to Palla et al.
+(2020), who have a more cohesive multi-zone model rather than three independent one-zone models?}}
+    \label{fig:spitoni-comparison}
+\end{figure*}
+
+\todo{Highlight differences between our models and those of \citet{spitoni_apogee_2021} in Figure \ref{fig:spitoni-comparison}.}
 
@@
 
+This study is not the first to apply a prescription for radial migration to a two-infall GCE model.
+\citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
+They prescribed some fraction of stars from the inner and outer Galaxy which contribute to the local present-day population based on a constant migration speed, and they also assumed some fraction of stars born in the Solar neighborhood will have migrated elsewhere.
+This method can improve agreement with the observed local metallicity distribution, but does not scale to abundance distributions across the disk.
+\citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to the diffusion treatment of \citet{frankel_measuring_2018} and found similar results.
+Our implementation, described below, affects abundance distributions across the Galaxy, not just at the Solar annulus.
+
+% \citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
+They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
+This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
+They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
+Their only point of comparison with data is the local G-dwarf metallicity distribution.
+
 The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
@@
 
+We note an important distinction between our method and that of \citet{spitoni_effect_2015}: SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
+This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
+So, a significant fraction of SN Ia progenitors born in a given zone will enrich a disparate region of the Galaxy.
+
 \section{Multi-Zone Model Results}
@@
 \label{sec:abundance-distributions}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/ofe_feh_density.pdf}
+    \caption{The density of stars in the [O/Fe]--[Fe/H] plane from multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
+The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
+Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\,{\rm kpc}$ and $0.5\leq|z|<1\,{\rm kpc}$ to highlight the $\alpha$-bimodality.}
+    \label{fig:ofe-feh-density}
+\end{figure}
+
+Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model at mid to high Galactic latitudes.
+Between $0.5\leq|z|<1\,{\rm kpc}$, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over ($\mathFeH\approx-0.3$, $\mathOFe\approx0.1-0.2$), which is not seen in the APOGEE sample.
+This over-density occurs because the overall rate of chemical evolution slows $\sim2\,{\rm Gyr}$ after the second infall, at the same time as the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
+This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in models (c) and (d) of Figure \ref{fig:ofe-df}.
+
+Additionally, the shape of the low-$\alpha$ sequence in the model results (a concave-down ``comma'') is clearly different from the data (a concave-up ``swoosh'').
+\todo{Not sure what this means because the inside-out SFH has the same issue.
+Maybe it's related to radial migration?}
+
+\subsection{Abundances Across the Disk}
+\label{sec:disk-abundances}
 
@@
 Model (a) assumes the fiducial parameters and the {\tt yZ1} yield set, whereas models (b--d) assume the {\tt yZ2} yield set.
-Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.
+Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.
 The distributions from APOGEE DR17 are plotted in column (e) for reference.}
@@
 
-Finally, in model (d) the metallicity of the infalling gas increases to ${\rm [X/H]}_{\rm CGM}=-0.7$ at late times.
+Finally, in model (d) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.7$ at late times.
 We choose this value because it is the maximum which can plausibly still reproduce the disk abundances; any higher and the infalling gas would be more metal-rich than the most metal-poor thin disk stars.
 This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
-We assume that the infalling gas has ${\rm [O/Fe]}=0$ at all times; an alternate run with ${\rm [O/Fe]}=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
+We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
 In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.
 
-\begin{figure}
-    \centering
-    \includegraphics{figures/ofe_feh_density.pdf}
-    \caption{The density of stars in the [O/Fe]--[Fe/H] plane from multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
-The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
-Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\,{\rm kpc}$ and $0.5\leq|z|<1\,{\rm kpc}$ to highlight the $\alpha$-bimodality.}
-    \label{fig:ofe-feh-density}
-\end{figure}
-
-Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model at mid to high Galactic latitudes.
-Between $0.5\leq|z|<1\,{\rm kpc}$, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over (${\rm [Fe/H]}\approx-0.3$, ${\rm [O/Fe]}\approx0.1-0.2$), which is not seen in the APOGEE sample.
-This over-density occurs because the overall rate of chemical evolution slows $\sim2\,{\rm Gyr}$ after the second infall, at the same time as the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
-This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in models (c) and (d) of Figure \ref{fig:ofe-df}.
-
-Additionally, the shape of the low-$\alpha$ sequence in the model results (a concave-down ``comma'') is clearly different from the data (a concave-up ``swoosh'').
-\todo{Not sure what this means because the inside-out SFH has the same issue.
-Maybe it's related to radial migration?}
-
-\subsection{Abundance Evolution}
+\subsection{Local Abundance Evolution}
 \label{sec:age-abundance}
@@
 Age estimates from APOGEE stars come from \citet{leung_variational_2023}.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$.}
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.}
     \label{fig:abundance-evolution}
@@
 
-Finally, as in Section \ref{sec:abundance-distributions}, we investigate a model where the gas infall is pre-enriched to ${\rm [O/H]}={\rm [Fe/H]}=-0.7$.
+Finally, as in Section \ref{sec:abundance-distributions}, we investigate a model where the gas infall is pre-enriched to $\mathOH=\mathFeH=-0.7$.
 As shown in column (d) of Figure \ref{fig:abundance-evolution}, this mitigates but does not completely solve the two discrepancies.
@@
 
-\subsection{Abundances Across the Disk}
-\label{sec:disk-abundances}
+\subsection{Abundance Evolution Across the Disk}
+\label{sec:disk-evolution}
 
@@
 The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference.
-Also in row (c), the gray dashed line marks the cut at ${\rm [Fe/H]}>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at ${\rm [Fe/H]}<+0.45$ for all stars with [C/N]-based ages.
+Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
 Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex}.}
@@
 The two-infall model predicts a bimodal distribution: the metal-rich component comprises stars formed during the last Gyr of the first infall epoch, and the metal-poor component is stars formed during the first Gyr of the second infall epoch (post-dilution).
-The data show this same bimodal structure in all but the outermost radial bin, with peaks at ${\rm [Fe/H]}\approx-0.3$ and $+0.3$.
+The data show this same bimodal structure in all but the outermost radial bin, with peaks at $\mathFeH\approx-0.3$ and $+0.3$.
 While the location of the model peaks depends on $R_{\rm gal}$, in the data they are quite consistent from the innermost to the outermost bin.
@@
 Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
-
-\subsection{Radial Migration}
-\label{sec:migration-discussion}
-
-This study is not the first to apply a prescription for radial migration to a two-infall GCE model.
-\citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
-They prescribed some fraction of stars from the inner and outer Galaxy which contribute to the local present-day population based on a constant migration speed, and they also assumed some fraction of stars born in the Solar neighborhood will have migrated elsewhere.
-This method can improve agreement with the observed local metallicity distribution, but does not scale to abundance distributions across the disk.
-\citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to the diffusion treatment of \citet{frankel_measuring_2018} and found similar results.
-
-% \citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
-They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
-This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
-They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
-Their only point of comparison with data is the local G-dwarf metallicity distribution.
-
-Our method described in Section \ref{sec:migration} can affect abundance distributions across the Galaxy via migration, not just for the Solar neighborhood.
-We also note an important distinction between our method and that of \citet{spitoni_effect_2015}: SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
-This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
-So, a significant fraction of SN Ia progenitors born in a given zone will enrich a disparate region of the Galaxy.
 
@@
 The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
-However, there are some differences in detail, such as the dearth of stars at ${\rm [O/Fe]}\approx+0.35$ due to the star formation hiatus.
+However, there are some differences in detail, such as the dearth of stars at $\mathOFe\approx+0.35$ due to the star formation hiatus.
 We intend this model to illustrate another path to reproducing the $\alpha$-bimodality.

### 2025-03-21 src/tex/ms.tex
Updates from Overleaf

@@
 % Title
-\title{The Two-Infall Model Across Space and Time for a Milky Way in Equilibrium}
+\title{Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs}
 
@@
 \begin{abstract}
-    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion episodes.
-It has successfully reproduced observed abundance patterns such as the [$\alpha$/Fe]-bimodality in the Solar neighborhood and across the disk.
-However, few studies have explored a two-infall model with significant mass-loaded outflows, nor compared model results with comprehensive age--abundance data across the disk.
-We run multi-zone galactic chemical evolution (GCE) models with a two-infall star formation history, radially-dependent mass-loaded outflows, and a prescription for radial migration of stellar populations.
-We compare our model results to abundance patterns across the disk from the Apache Point Observatory Galactic Evolution Experiment (APOGEE) data release 17, supplemented with stellar age estimates using multiple methods.
-We find that the two-infall model struggles to reproduce all the observed characteristics of the chemical thin disk.
-Models with low nucleosynthetic yields and weak outflows experience long-lasting dilution of the gas-phase metallicity which contradicts the local age--metallicity relation.
-Conversely, models with higher yields and stronger outflows fail to reproduce the thin disk [$\alpha$/Fe] distribution.
-These issues can be mitigated, but not completely solved, by pre-enriching the accreted gas to low metallicity.
-In the context of the equilibrium scenario recently proposed by \citet{johnson_milky_2024}, the two-infall model must overcome these inherent limitations to be compatible with all observations.
+    Stellar populations in the Milky Way exhibit a clear separation into two chemically distinct populations that are separated by their [$\alpha$/Fe] ratios.
+A popular explanation for this observation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
+However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow.
+Thanks to advances in stellar age measurements in recent years, we can now also compare this popular model to more direct measurements of the Galaxy's evolutionary timescales from large stellar catalogs.
+We run multi-zone galactic chemical evolution (GCE) models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamic simulation.
+We compare our model results to abundance patterns across the disk from APOGEE DR17 and early data from the SDSS-V Milky Way Mapper program, supplemented with stellar age estimates through multiple methods.
+Although the two-infall scenario offers a natural explanation for the [$\alpha$/Fe] bimodality, it struggles to explain several features of the age--abundances structure in the disk.
+The two-infall scenario generically predicts a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant with age across much of the Galactic disk.
+This apparent age-independence places considerable restrictions upon the two-infall parameter space.
+These issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
 \end{abstract}
@@
 \todo{Observational evidence.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
-\citet{chen_recent_2025}
+\citet{nataf_accurate_2024} also observe multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.
+\citet{chen_recent_2025} however argue that this trend can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
 
@@
 
-\todo{Summary of secular evolution models which claim alpha-bimodality.}
+\todo{Summary of secular evolution models which claim alpha-bimodality.} \citep{kubryk_evolution_2015}. \citep{sharma_chemical_2021} . \citep{chen_chemical_2023}.\citep{prantzos_origin_2023}.
 
 \todo{Introduce equilibrium model.}
+
+Recently, \citet{dubay_galactic_2024} studied the effect of the SN Ia delay-time distribution in the context of several different star formation histories, including a two-infall model.
+While the results did not greatly depend on the choice of SFH, the authors \todo{(we?)} noted that the two-infall model, as implemented, produced a stellar [O/Fe] distribution with three distinct peaks, at variance with the data.
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{figures/yield_outflow.pdf}
+    \caption{The abundance evolution of three one-zone models with different yield and outflow settings.
+Table \ref{tab:yields} presents the population-averaged yields for each model.
+The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
+    \label{fig:yield-outflow}
+\end{figure}
+
 Figure \ref{fig:yield-outflow} illustrates the effect of the yield scaling on the abundance evolution in one-zone models.
@@
 Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution.
-As the $y/Z_\odot=2$ and $y/Z_\odot=3$ models show generally similar behavior, we focus on the $y/Z_\odot=1$ and $y/Z_\odot=2$ yield sets for this work.
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/yield_outflow.pdf}
-    \caption{The abundance evolution of three one-zone models with different yield and outflow settings.
-Table \ref{tab:yields} presents the population-averaged yields for each model.
-The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
-    \label{fig:yield-outflow}
-\end{figure}
+As the $y/Z_\odot=2$ and $y/Z_\odot=3$ models show generally similar behavior, we focus on the $y/Z_\odot=1$ and $y/Z_\odot=2$ yield sets for the remainder of this work.
 
@@
 \end{equation}
-where $R_\odot=8\,{\rm kpc}$. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla\mathOH_{\rm eq}$:
-\begin{equation}
-    R_\eta = -\frac{1}{\nabla\mathOH_{\rm eq} \times\ln(10)}.
-\end{equation}
-We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
-\todo{Motivate exponential scale radius.}
+where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\,{\rm kpc}$.
+As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [Fe/H] with $R_{\rm gal}$.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\,{\rm kpc}^{-1}$ \todo{(citations)}.
+% The exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla\mathOH_{\rm eq}$:
+% \begin{equation}
+%     R_\eta = -\frac{1}{\nabla\mathOH_{\rm eq} \times\ln(10)}.
+% \end{equation}
+% We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
+% \todo{Motivate exponential scale radius.}
 
@@
 We adopt a thick disk scale radius of $R_1=2.0\,{\rm kpc}$, a thin disk scale radius of $R_2=2.5\,{\rm kpc}$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
+\todo{Compare with other two-infall papers, which generally have a higher thick-to-thin ratio.}
 
@@
 In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}$.
-We also investigate cases where the CGM is $\alpha$-enhanced, i.e., $\mathOFe_{\rm CGM}>0$.
-\todo{Other GCE models that do this:} \citet{palla_chemical_2020,spitoni_remind_2024,johnson_milky_2024}
+Previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
+% We also investigate cases where the CGM is $\alpha$-enhanced, i.e., $\mathOFe_{\rm CGM}>0$.
 
@@
 The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
-All models use the {\tt yZ1} yield set and assume $\eta=0.2$.}
+All models use the \yZ{1} yield set and assume $\eta=0.2$.}
     \label{fig:twoinfall-parameters}
@@
 % Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
+Previous studies have adopted a wide range of parameters for Equation \ref{eq:twoinfall-ifr}.
 Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
@@
 \end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$ with $\gamma=1/2$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$.
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ \todo{(?)} and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citet{leroy_star_2008}.
 Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\varepsilon$:
@@
 We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature.
+\todo{I actually think I can ditch the pre-factor, since the molecular timescale already decreases with lookback time.
+In fact, $\tau_{\rm mol}(4.2\,{\rm Gyr}) / \tau_{\rm mol}(13.2\,{\rm Gyr}) \approx 0.5$, which is pretty much the correct ratio to match the two-infall literature.
+The only catch is that $\tau_{\rm mol}$ is a very smooth transition, while with the prefactor it's an abrupt transition.}
 
@@
 
+The two-infall model explains the chemical evolution of the thin disk through the low-$\alpha$ loop (see discussion in Section \ref{sec:parameter-selection}).
+However, inspection of the marginal [O/Fe] distributions in, e.g., Figure \ref{fig:yield-outflow} reveals a different morphology of the low-$\alpha$ sequence: the two-infall model predicts two peaks in [O/Fe] in the thin disk where the data show only one.
+The location of the second peak, at intermediate [O/Fe], varies depending on the yields (Figure \ref{fig:yield-outflow}) and infall parameters (Figure \ref{fig:twoinfall-parameters}), but is always present.
+This morphology remains essentially consistent in our multi-zone models as well, despite the inclusion of radial mixing and vertical dispersion of stars.
+
 Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model at mid to high Galactic latitudes.
 Between $0.5\leq|z|<1\,{\rm kpc}$, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over ($\mathFeH\approx-0.3$, $\mathOFe\approx0.1-0.2$), which is not seen in the APOGEE sample.
-This over-density occurs because the overall rate of chemical evolution slows $\sim2\,{\rm Gyr}$ after the second infall, at the same time as the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
-This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in models (c) and (d) of Figure \ref{fig:ofe-df}.
+This over-density occurs because the overall rate of chemical evolution slows down $\sim2\,{\rm Gyr}$ after the second infall, and at the same time the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
+This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow}.
 
@@
 For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
-Model (a) assumes the fiducial parameters and the {\tt yZ1} yield set, whereas models (b--d) assume the {\tt yZ2} yield set.
+Model (a) assumes the fiducial parameters and the \yZ{1} yield set, whereas models (b--d) assume the \yZ{2} yield set.
 Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.
@@
 
-The dilution effect discussed in \ref{sec:yields} is clearly seen in the multi-zone model results.
+The dilution effect discussed in Section \ref{sec:yields} is clearly seen in the multi-zone model results.
 Figure \ref{fig:abundance-evolution} shows stellar age--abundance relations for four model outputs.
@@
 As shown in column (d) of Figure \ref{fig:abundance-evolution}, this mitigates but does not completely solve the two discrepancies.
-The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution is also reduced, \todo{because why?}.
+The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, because the enriched gas accretion imposes a lower limit on the metallicity of the outermost regions, from which the stars of the low-metallicity tail in the Solar neighborhood are drawn.
 The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity --- an effect which can be compensated by a slightly increased value of $\eta$.
@@
 The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4\,{\rm Gyr}$.
-Both models assume the {\tt yZ2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
+Both models assume the \yZ{2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
 The greyscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq|z|\leq2\,{\rm kpc}$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}

### 2025-03-21 src/tex/ms.tex
Manuscript updates

@@
     \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
-    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a--d) and as observed by APOGEE (e).
-Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows.
+    \caption{Stellar [O/Fe] distributions produced by select multi-zone models (a--d) and as observed by APOGEE (e).
+Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right.
+Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
 Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
-The median APOGEE abundance uncertainties were forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
+The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
 For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
 Model (a) assumes the fiducial parameters and the \yZ{1} yield set, whereas models (b--d) assume the \yZ{2} yield set.
-Model (c) also assumes a power-law SN Ia DTD, while model (d) assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.
-The distributions from APOGEE DR17 are plotted in column (e) for reference.}
+Model (c) also adopts a power-law SN Ia DTD, while in model (d) the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.
+{\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent when assuming higher yields and outflows.
+This effect can be mitigated by pre-enriched infall.}
     \label{fig:ofe-df}
@@
 A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
-For visual clarity, we plot a only random mass-weighted sample of \num{10000} points in each panel.
+For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
 The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time.
@@
 Age estimates from APOGEE stars come from \citet{leung_variational_2023}.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.}
+Each column shows results from a different multi-zone model: {\bf (a)} a model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with $y/Z_\odot=1$ and greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model with $y/Z_\odot=1$ and which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.
+{\bf Key takeaway:} All models feature a major dilution event at a lookback time of 9 Gyr, and for models with low yields and outflows the dilution persists throughout much of the thin disk epoch.}
     \label{fig:abundance-evolution}
@@
     \caption{Evolution of the MDF across the Galactic disk.
-Each panel presents the normalized stellar [Fe/H] distribution within a {2 kpc}-wide annulus, color-coded by the age bin.
+Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age.
 Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
@@
 Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
-Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex}.}
+Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
+{\bf Key takeaway:} The APOGEE data show remarkably little variation in the mode at all radii over the past $\sim6-8$ Gyr, while both GCE models produce a steady evolution toward higher [Fe/H] with time.}
     \label{fig:mdf-evolution}

### 2025-03-26 src/tex/ms.tex
Updates from Overleaf

@@
 
-\todo{Observational evidence.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
+\todo{Observational evidence other than $\alpha$-bimodality.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
 \citet{nataf_accurate_2024} also observe multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.
@@
 \todo{Migration.} The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
-\todo{Talk about migration studies and why we don't need a single evolutionary track to explain the bimodality.}
+\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating.
+It is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}.
+Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor requires assumptions about the evolution of the Milky Way's radial metallicity gradient.
+While the strength and speed of radial migration in the disk are not precisely measured, it is clear that a single chemical evolution track need not explain the entirety of the local observed abundance distribution.
 
-\todo{Summary of secular evolution models which claim alpha-bimodality.} \citep{kubryk_evolution_2015}. \citep{sharma_chemical_2021} . \citep{chen_chemical_2023}.\citep{prantzos_origin_2023}.
+\todo{Summary of secular evolution models which claim alpha-bimodality.} \citet{schonrich_chemical_2009}.
+\citet{kubryk_evolution_2015}.
+\citet{sharma_chemical_2021}, \citet{chen_chemical_2023}.
+\citet{prantzos_origin_2023}.
 
@@
 
-\todo{Goal of paper.}
+\todo{Goal and summary of paper.}
 
@@
 We adopt a thick disk scale radius of $R_1=2.0\,{\rm kpc}$, a thin disk scale radius of $R_2=2.5\,{\rm kpc}$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
-\todo{Compare with other two-infall papers, which generally have a higher thick-to-thin ratio.}
+In the Solar neighborhood, this produces a thick-to-thin disk mass ratio of $f_\Sigma(R_\odot)=0.12$.
+By comparison, \citet{mackereth_age-metallicity_2017} finds $f_\Sigma(R_\odot)=0.18\pm0.05$ from APOGEE.
+\todo{Compare with other two-infall papers, which generally have a higher thick-to-thin ratio.} \citet{spitoni_galactic_2020} explores $f_\Sigma(R_\odot)\approx0.23-0.31$, \citet{palla_chemical_2020} assumes $f_\Sigma(R_\odot)=0.23$, \citet{spitoni_apogee_2021} derives $f_\Sigma(R_\odot)=0.18$ (again from APOGEE), \citet{spitoni_remind_2024} assumes $f_\Sigma(R_\odot)=0.4$.
 
@@
 The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
-Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\,{\rm kpc}$ and $0.5\leq|z|<1\,{\rm kpc}$ to highlight the $\alpha$-bimodality.}
+Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\,{\rm kpc}$ and $0.5\leq|z|<1\,{\rm kpc}$ to highlight the $\alpha$-bimodality in the Solar neighborhood.
+{\bf Key takeaway:} the two-infall model generically predicts a stellar overdensity at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.}
     \label{fig:ofe-feh-density}
@@
 \label{sec:age-abundance}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{figures/abundance_evolution_yields.pdf}
+    \caption{Caption}
+    \label{fig:abundance-evolution-yields}
+\end{figure}
 

### 2025-03-26 src/tex/ms.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=0.5\linewidth]{figures/abundance_evolution_yields.pdf}
-    \caption{Caption}
+    \includegraphics[width=\linewidth]{figures/abundance_evolution_yields.pdf}
+    \caption{Stellar age--abundance relations produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
+Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius.
+A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
+The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time.
+The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
+Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
+{\bf Key takeaway:} Both models feature a major dilution event at a lookback time of 9 Gyr, and for model (a) the dilution persists throughout much of the thin disk epoch.}
     \label{fig:abundance-evolution-yields}
@@
     \centering
-    \includegraphics{figures/abundance_evolution.pdf}
-    \caption{Stellar age--abundance relations produced by select multi-zone models.
-Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius.
-A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
-For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
-The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time.
-The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
-Age estimates from APOGEE stars come from \citet{leung_variational_2023}.
-Each column shows results from a different multi-zone model: {\bf (a)} a model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with $y/Z_\odot=1$ and greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model with $y/Z_\odot=1$ and which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.
-{\bf Key takeaway:} All models feature a major dilution event at a lookback time of 9 Gyr, and for models with low yields and outflows the dilution persists throughout much of the thin disk epoch.}
-    \label{fig:abundance-evolution}
+    \includegraphics{figures/abundance_evolution_params.pdf}
+    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}.
+The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$.
+{\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
+    \label{fig:abundance-evolution-params}
 \end{figure*}

### 2025-03-26 src/tex/ms.tex
Updates from Overleaf

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_yields.pdf}
+    \caption{Caption}
+    \label{fig:ofe-distribution-yields}
+\end{figure}
+
 \begin{figure*}
     \centering
-    \includegraphics{src/tex/figures/ofe_df_comparison.pdf}
+    \includegraphics{src/tex/figures/ofe_distribution_params.pdf}
     \caption{Stellar [O/Fe] distributions produced by select multi-zone models (a--d) and as observed by APOGEE (e).
@@
 
+The dilution effect discussed in Section \ref{sec:yields} is clearly seen in the multi-zone model results.
+Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations produced by models with \yZ{1} and \yZ{2} with fiducial parameters (Table \ref{tab:multizone-parameters}).
+The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
+The evolution of [Fe/H] is similar, but the approach to Solar abundance is slower because of the additional delay imposed on Fe production from SNe Ia.
+The \yZ{2} yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
+However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is much steeper than the data.
+
 \begin{figure*}
@@
 
-The dilution effect discussed in Section \ref{sec:yields} is clearly seen in the multi-zone model results.
-Figure \ref{fig:abundance-evolution} shows stellar age--abundance relations for four model outputs.
-Column (a) plots the output of our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and $Z_{\rm CGM}=0$.
-The fiducial model shows two major discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
-The evolution of [Fe/H] is similar, but the approach to Solar abundance is slower because of the additional delay imposed on Fe production from SNe Ia.
-A higher yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
-However, model (b) produces a poorer fit to the age--[O/Fe] relation; the decline in [O/Fe] over the thin disk epoch is much steeper than the data.
+Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters on the \yZ{1} model.
 
 The observed rise in the median abundance of stars with ages of $\sim4-8\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
-Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in column (a) have sub-Solar abundances.
-Column (c) of Figure \ref{fig:abundance-evolution} presents a model with $y/Z_\odot=1$ but with a stronger migration prescription of $\sigma_{\rm RM8}=5\,{\rm kpc}$.
+Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
+Column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ but with a stronger migration prescription of $\sigma_{\rm RM8}=5\,{\rm kpc}$.
 Here, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
@@
 
-Finally, as in Section \ref{sec:abundance-distributions}, we investigate a model where the gas infall is pre-enriched to $\mathOH=\mathFeH=-0.7$.
-As shown in column (d) of Figure \ref{fig:abundance-evolution}, this mitigates but does not completely solve the two discrepancies.
+Second, as in Section \ref{sec:abundance-distributions}, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
+Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
+Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
 The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, because the enriched gas accretion imposes a lower limit on the metallicity of the outermost regions, from which the stars of the low-metallicity tail in the Solar neighborhood are drawn.
 The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity --- an effect which can be compensated by a slightly increased value of $\eta$.
-Overall, no modification to the $y/Z_\odot=1$ model is able to overcome both the dilution and late-time evolution issues.
+
+Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger, $f_\Sigma(R_\odot)=0.48$.
+This is higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
+Column (d) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase.
+The model produces the best agreement with the observed age--[Fe/H] relation (second row).
+However, agreement with the observed age--[O/Fe] relation is poor, as the [O/Fe] of the old low-$\alpha$ disk is $\sim0.1$ dex lower than observed.
+
+Overall, no modification to the \yZ{1} model is able to completely overcome both the dilution and late-time evolution issues.
 

### 2025-03-27 src/tex/ms.tex

@@
     \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_yields.pdf}
-    \caption{Caption}
+    \caption{Stellar [O/Fe] distributions produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
+Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right.
+Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
+Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
+The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
+For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
+{\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent in the \yZ{2} model at mid to high latitudes.}
     \label{fig:ofe-distribution-yields}
@@
     \centering
-    \includegraphics{src/tex/figures/ofe_distribution_params.pdf}
-    \caption{Stellar [O/Fe] distributions produced by select multi-zone models (a--d) and as observed by APOGEE (e).
-Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right.
-Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
-Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
-The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
-For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
-Model (a) assumes the fiducial parameters and the \yZ{1} yield set, whereas models (b--d) assume the \yZ{2} yield set.
-Model (c) also adopts a power-law SN Ia DTD, while in model (d) the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$.
-{\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent when assuming higher yields and outflows.
-This effect can be mitigated by pre-enriched infall.}
+    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
+    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e).
+The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
+Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.24$.
+{\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio}
     \label{fig:ofe-df}
@@
 The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$.
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$.
 {\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}

### 2025-03-27 src/tex/ms.tex
Manuscript updates

@@
 The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
-Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.24$.
-{\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio}
-    \label{fig:ofe-df}
+Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$.
+{\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
+    \label{fig:ofe-distribution-parameters}
 \end{figure*}

### 2025-03-28 src/tex/ms.tex

@@
 Figure \ref{fig:sfe-prefactor} illustrates that this pre-factor largely affects the metallicity of the high-$\alpha$ sequence, with a smaller $\varepsilon$ producing faster enrichment during the first infall and stronger dilution after $t_{\rm max}$.
-The pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
+The pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law, but a lower value of $\varepsilon$ does narrow the MDF by $\sim0.1$ dex in [Fe/H].
 We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature.
-\todo{I actually think I can ditch the pre-factor, since the molecular timescale already decreases with lookback time.
+We have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
+% \todo{I actually think I can ditch the pre-factor, since the molecular timescale already decreases with lookback time.
 In fact, $\tau_{\rm mol}(4.2\,{\rm Gyr}) / \tau_{\rm mol}(13.2\,{\rm Gyr}) \approx 0.5$, which is pretty much the correct ratio to match the two-infall literature.
@@
     \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_yields.pdf}
-    \caption{Stellar [O/Fe] distributions produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
-Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right.
+    \caption{Normalized stellar [O/Fe] distributions produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
+Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row.
 Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
-Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row.
 The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).

### 2025-04-01 src/tex/ms.tex

@@
     Stellar populations in the Milky Way exhibit a clear separation into two chemically distinct populations that are separated by their [$\alpha$/Fe] ratios.
+This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to the Milky Way's unique evolutionary history.
 A popular explanation for this observation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
 However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow.
-Thanks to advances in stellar age measurements in recent years, we can now also compare this popular model to more direct measurements of the Galaxy's evolutionary timescales from large stellar catalogs.
+Thanks to advances in stellar age measurements in recent years, we can now also compare this popular model to more direct measurements of the Galaxy's evolutionary timescales across the disk from large stellar catalogs.
 We run multi-zone galactic chemical evolution (GCE) models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamic simulation.
-We compare our model results to abundance patterns across the disk from APOGEE DR17 and early data from the SDSS-V Milky Way Mapper program, supplemented with stellar age estimates through multiple methods.
+We compare our model results to abundance patterns across the disk from APOGEE DR17,
+    % and early data from the SDSS-V Milky Way Mapper program,
+    supplemented with stellar age estimates through multiple methods.
 Although the two-infall scenario offers a natural explanation for the [$\alpha$/Fe] bimodality, it struggles to explain several features of the age--abundances structure in the disk.
@@
 In this view, one feature of the Milky Way disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
-The high-$\alpha$ sequence consists of old stars \citep[$\sim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk.
+The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk.
 The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
 
+An explanation for the $\alpha$-bimodality has yet to be broadly accepted in the GCE community \todo{(reword)}.
+An $\alpha$-bimodality is not a universal feature in simulated Milky Way-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our own galaxy may provide clues to its unique evolutionary history.
+GCE models that attempt to solve this problem generally fall into two camps: some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}; others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \todo{(citations)} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
+
 % Summary of two-infall literature
-The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the thick and thin disks.
+The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks.
 Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts.
@@
 
-Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, and others have explored in its context the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
+Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}.
+Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024} in a two-infall context.
 Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.
 
-\todo{Observational evidence other than $\alpha$-bimodality.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
+% \todo{Observational evidence other than $\alpha$-bimodality.} 
+The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model.
+\citet{spitoni_remind_2024} argued that the gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, supports a haitus in star formation which is a natural consequence of the two-infall model.
+\citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
 \citet{nataf_accurate_2024} also observe multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.
@@
 
-\todo{Goal and summary of paper.}
+% \todo{Goal and summary of paper.} 
+We run multi-zone GCE models with a two-infall accretion history, radially-dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
+We investigate the impact of the scale of SN yields and outflows, the strength of radial migration, the enrichment of the circumgalactic medium, and the local disk mass surface density ratio on the GCE model predictions.
+We compare our results to abundance distributions across the disk from APOGEE DR17, and to age--abundance relations from multiple age catalogs.
+We describe our observational sample in Section \ref{sec:observational-sample}, and we detail our chemical evolution models and parameter selection in Section \ref{sec:methods}.
+We compare our multi-zone model predictions to the data in Section \ref{sec:multizone-results}.
+We discuss in Section \ref{sec:discussion} and conclude in Section \ref{sec:conclusions}.
 
@@
 By comparison, \citet{mackereth_age-metallicity_2017} finds $f_\Sigma(R_\odot)=0.18\pm0.05$ from APOGEE.
+\citet{fuhrmann_local_2017} derive $f_\Sigma(R_\odot)=0.57$ from a very small volume (25 pc radius).
 \todo{Compare with other two-infall papers, which generally have a higher thick-to-thin ratio.} \citet{spitoni_galactic_2020} explores $f_\Sigma(R_\odot)\approx0.23-0.31$, \citet{palla_chemical_2020} assumes $f_\Sigma(R_\odot)=0.23$, \citet{spitoni_apogee_2021} derives $f_\Sigma(R_\odot)=0.18$ (again from APOGEE), \citet{spitoni_remind_2024} assumes $f_\Sigma(R_\odot)=0.4$.
@@
 
+The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+Figure \ref{fig:ofe-distribution-yields} compares [O/Fe] distributions from across the Galactic disk produced by models with the \yZ{1} and \yZ{2} yield sets.
+For model (a) with $y/Z_\odot=1$, the two thin disk peaks are close enough together that they approximate a single peak, especially once observational uncertainties are factored in.
+With the \yZ{2} yield set, however, there is a $\sim0.2$ dex separation between the low- and intermediate-$\alpha$ peaks thanks to increased efficiency of CCSN element production.
+As a result, model (b) predicts a high density of stars at $\mathOFe\approx+0.2$ where the data show a relatively low density.
+
 \begin{figure*}
@@
 The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
-Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$.
+Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
 {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
@@
 
-The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
-Figure \ref{fig:ofe-df} compares [O/Fe] distributions across the Galactic disk produced by four different multi-zone models with the distributions observed in APOGEE DR17.
-For the fiducial model (a) with $y/Z_\odot=1$, the latter two peaks are close together and the overall effect is similar to the observed distribution.
-With a higher yield set, however, there is a $\sim0.2$ dex separation between the low- and intermediate-$\alpha$ peaks, because the CCSN element production after the second infall is more efficient.
-As a result, model (b) predicts a high density of stars in the APOGEE ``trough.''
-
-In columns (c) and (d) of Figure \ref{fig:ofe-df}, we attempt to mitigate the issue of the intermediate-$\alpha$ peak for the $y/Z_\odot=2$ yield set.
+In Figure \ref{fig:ofe-distribution-parameters}, we show the result of our attempts to mitigate the intermediate-$\alpha$ peak discrepancy for the \yZ{2} yield set in a few different ways, namely by reducing the size of the thin disk loop seen in panel (b) of Figure \ref{fig:ofe-feh-density}.
+First, we substitute our fiducial SN Ia DTD with a simple power-law,
+\begin{equation}
+    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^{-1.1},
+    \label{eq:powerlaw-dtd}
+\end{equation}
+which reduces the median SN Ia delay time from $\sim2\,{\rm Gyr}$ to $\sim0.5\,{\rm Gyr}$.
+As shown in column (b), this has the intended effect on the low-$\alpha$ sequence, but it also entirely eliminates the high-$\alpha$ peak.
+\citet{dubay_galactic_2024} discuss in detail why such a DTD is disfavored by Milky Way stellar abundances, and their results hold true for the two-infall model as well.
+% In columns (c) and (d) of Figure \ref{fig:ofe-df}, we attempt to mitigate the issue of the intermediate-$\alpha$ peak for the $y/Z_\odot=2$ yield set.
 Model (c) switches out our fiducial DTD with a power-law DTD, which decreases the timescale for Fe production.
@@
 
-Finally, in model (d) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.7$ at late times.
+Next, in model (c) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
 We choose this value because it is the maximum which can plausibly still reproduce the disk abundances; any higher and the infalling gas would be more metal-rich than the most metal-poor thin disk stars.
@@
 We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
-In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.
+% In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.
+
+Finally, in model (d) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
+This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates \todo{(citations)}.
+The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the previous models.
+\todo{Note that APOGEE high-$\alpha$ sequence is over-emphasized by survey selection function.} In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \Z{2} case.
+These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.
 
@@
 The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$.
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
 {\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
@@
 Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age.
-Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
+Rows (a) and (b) present the distributions from multi-zone GCE models with different yield scales.
+For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$.
 A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+Row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
 The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference.

### 2025-04-02 src/scripts/yields.py
add labels to table

@@ -16,17 +16,19 @@ def main():
     from multizone.src.yields import yZ3
     yZ3_yields, yZ3_labels = make_column(eta=outflows.yZ3)
     df = pd.DataFrame({
-        '$y/Z_\\odot=1$': yZ1_yields,
-        '$y/Z_\\odot=2$': yZ2_yields,
-        '$y/Z_\\odot=3$': yZ3_yields,
-    }, index=yZ1_labels)
+        '$y/Z_\\odot=1$': ['(empirical)'] + yZ1_yields,
+        '$y/Z_\\odot=2$': ['(theoretical)'] + yZ2_yields,
+        '$y/Z_\\odot=3$': ['(extreme)'] + yZ3_yields,
+    }, index=[''] + yZ1_labels)
     latex_table = df.to_latex(column_format='c|ccc', index=True)
     # Replace float 0s with int
     latex_table = latex_table.replace('0.00e+00', '0')
     # Replace \toprule, \midrule, \bottomrule with \hline
     latex_table = latex_table.replace('\\toprule', '\\hline\\hline')
-    latex_table = latex_table.replace('\\midrule', '\\hline')
+    latex_table = latex_table.replace('\n\\midrule', '')
     latex_table = latex_table.replace('\\bottomrule', '\\hline')
+    # Add horizontal rule between column labels and yields
+    latex_table = latex_table.replace('$y_{\\rm O}^{\\rm CC}$', '\\hline\n$y_{\\rm %s}^{\\rm CC}$')
     # Add horizontal rule between yields and SN Ia rates
     latex_table = latex_table.replace('$N_', '\\hline\n$N_')
     # Write to output

### 2025-04-02 src/tex/ms.tex

@@
 \newcommand{\mathOFe}{{\rm [O/Fe]}}
-\newcommand{\mathaFe}{{\rm [$\alpha$/Fe]}}
+\newcommand{\mathaFe}{[\alpha/{\rm Fe}]}
 \newcommand{\yZ}[1]{$y/Z_\odot=#1$}
@@
     \centering
-    \caption{Sample selection parameters and median uncertainties from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
+    \caption{Sample selection parameters from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
     \label{tab:sample}
@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        Latent age          & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
+        NN age error        & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
         $R_{\rm gal}$     & $3 < R_{\rm gal} < 15\,{\rm kpc}$    & Eliminate bulge \& extreme outer-disk stars \\
@@
         $\mathOFe$  & $0.019$    & $0.031$ \\
-        $\log_{10}(\tau_{\rm latent}/{\rm Gyr})$    & 0.10   & $0.16$ \\
+        $\log_{10}(\tau_{\rm NN}/{\rm Gyr})$    & 0.10   & $0.16$ \\
         $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & \todo{N/A} \\
@@
 We supplement the APOGEE DR17 abundance data with two different age catalogs.
-The first is the ``latent'' age estimates from \citet{leung_variational_2023}, who train a variational encoder-decoder network on asteroseismic data for APOGEE red giants.
-This catalog has two main advantages for our purposes: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and the recovered ages do not plateau at $\sim10\,{\rm Gyr}$ as they do in some other neural network-derived age catalogs \citep[e.g.,][]{mackereth_dynamical_2019}.
+The first is from \citet{leung_variational_2023}, who train a variational encoder-decoder network on asteroseismic data for APOGEE red giants.
+This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and the recovered ages do not plateau at $\sim10\,{\rm Gyr}$ as they do in some other neural network-derived age catalogs \citep[e.g.,][]{mackereth_dynamical_2019}.
 Following the recommendations of \citet{leung_variational_2023}, we use an upper limit on the relative age uncertainty of 40\%.
-This produces a sample of \num{57607} stars with latent age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$).
+This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$).
 The median uncertainty in $\log({\rm age}/{\rm Gyr})$ is 0.10 (see Table \ref{tab:uncertainties}).
+We hereafter refer to the \citet{leung_variational_2023} ages as ``NN ages.''
 
@@
 
-\begin{deluxetable*}{Cccl}
+\begin{deluxetable*}{Ccccl}
     \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:multizone-parameters}}
     \tablehead{
-        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
+        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Alternatives} & \colhead{Section} & \colhead{Description}
     }
     \startdata
-        % Yields
-        % y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
-        % N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
-        f_{\rm Ia}(t)   & Equation \ref{eq:plateau-dtd}   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
-        % t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
-        % Star formation histories
-        % Outflows
-        % \eta_\odot      & 0.2       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
-        R_\eta          & 5.0 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
-        f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
-        \mathXH_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
-        \tau_1          & 1 Gyr     & \ref{sec:parameter-selection}     & Timescale of the first infall epoch \\
-        \tau_2(R_\odot)  & 15 Gyr    & \ref{sec:parameter-selection}     & Timescale of the second infall epoch at the Solar annulus \\
-        R_{\tau_2}   & 7 kpc     & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
-        t_{\rm max}      & 4.2 Gyr  & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
-        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength
+        f_{\rm Ia}(t)       & Equation \ref{eq:plateau-dtd} & Equation \ref{eq:powerlaw-dtd}    & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
+        R_\eta              & 5.0 kpc   & ---               & \ref{sec:outflows}            & Exponential outflow scale radius \\
+        f_\Sigma(R_\odot)   & 0.12      & 0.25, 0.5         & \ref{sec:sfh}                 & Local thick/thin disk surface density ratio \\
+        \mathXH_{\rm CGM}   & Pristine  & $-0.7$, $-0.5$    & \ref{sec:sfh}                 & Metallicity of infalling gas \\
+        \tau_1              & 1 Gyr     & $0.1-3$ Gyr       & \ref{sec:parameter-selection} & Timescale of the first infall epoch \\
+        \tau_2(R_\odot)     & 15 Gyr    & $3-30$ Gyr        & \ref{sec:parameter-selection} & Timescale of the second infall epoch at the Solar annulus \\
+        R_{\tau_2}          & 7 kpc     & ---               & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
+        t_{\rm max}         & 4.2 Gyr   & $1-5$ Gyr         & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
+        \sigma_{\rm RM8}    & 2.68 kpc  & 3.6, 5.0 kpc      & \ref{sec:migration}   & Radial migration strength
     \enddata
@@
 This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$ --- in other words, the scale of SN yields is similar to the Solar abundance.
-However, \citet{johnson_milky_2024} found that GCE models with yields at this scale approach present-day abundances too slowly.
-We therefore investigate yield sets at multiple scales, which are presented in Table \ref{tab:yields}.
+Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\textemdash in other words, the scale of SN yields is similar to the Solar abundance.
+However, \citet{johnson_milky_2024} found that GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006} ($y/Z_\odot\approx2.6$).
+
+We investigate yield sets at multiple scales of the Solar abundance.
+The CCSN yield of O is directly set by the Solar scale: $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$.
+For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathaFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathaFe}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
+We adopt the \citet{asplund_chemical_2009} Solar abundances: $Z_{\rm O,\odot}=5.72\times10^{-3}$ and $Z_{\rm Fe,\odot}=1.29\times10^{-3}$.
+Our yield sets are presented in Table \ref{tab:yields}.
 
 The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is calculated so that the combined Fe yield $y_{\rm Fe}^{\rm Ia+CC}=y/Z_\odot$.
-We further increase $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the \yZ{1} and \yZ{2} yield sets, respectively, to ensure that our models reach $\mathOFe\approx0.0$ by the end time.
+We further increase $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the \yZ{1} and \yZ{2} yield sets, respectively, to ensure that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
 The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
@@
 The discrepancies between the predicted and observed abundance evolution discussed in Section \ref{sec:age-abundance} are also seen across the disk.
-Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins.
-We select the $y/Z_\odot=1$ and $y/Z_\odot=2$ models with pre-enriched infall due to the relative success of these models in the previous sections.
-We use the [C/N]-derived age estimates for the APOGEE sample due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages $\leq10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
+Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the \yZ{1} and \yZ{2} models.
+We adopt pre-enriched infall ($\mathFeH_{\rm CGM}=-0.7$), stronger radial migration ($\sigma_{\rm RM8}=3.6$ kpc), and a higher disk mass ratio ($f_\Sigma(R_\odot)=0.25$) because these parameters were able to improve agreement with observations in previous sections.
+For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages $\leq10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
+
 The two-infall model predicts a very broad MDF for ages $>10$ Gyr because of the rapid enrichment of the ISM during the first infall epoch.

### 2025-04-02 src/scripts/yields.py
fix typo

@@ -28,7 +28,7 @@ def main():
     latex_table = latex_table.replace('\n\\midrule', '')
     latex_table = latex_table.replace('\\bottomrule', '\\hline')
     # Add horizontal rule between column labels and yields
-    latex_table = latex_table.replace('$y_{\\rm O}^{\\rm CC}$', '\\hline\n$y_{\\rm %s}^{\\rm CC}$')
+    latex_table = latex_table.replace('$y_{\\rm O}^{\\rm CC}$', '\\hline\n$y_{\\rm O}^{\\rm CC}$')
     # Add horizontal rule between yields and SN Ia rates
     latex_table = latex_table.replace('$N_', '\\hline\n$N_')
     # Write to output

### 2025-04-03 src/tex/ms.tex
Updates from Overleaf

@@
 However, \citet{johnson_milky_2024} found that GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
-Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006} ($y/Z_\odot\approx2.6$).
+Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
 
@@
 Our yield sets are presented in Table \ref{tab:yields}.
+We consider \yZ{1} representative of the empirical yield scale, whereas \yZ{2-3} span a range of theoretical predictions.
 
-The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is calculated so that the combined Fe yield $y_{\rm Fe}^{\rm Ia+CC}=y/Z_\odot$.
+The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is calculated so that the combined Fe yield $y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC}=y/Z_\odot$.
 We further increase $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the \yZ{1} and \yZ{2} yield sets, respectively, to ensure that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
-The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
+The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate
+\begin{equation}
+    \frac{N_{\rm Ia}}{M_\star} = \frac{y_{\rm Fe}^{\rm Ia}}{\bar m_{\rm Fe}^{\rm Ia}}
+    \label{eq:snia-rate}
+\end{equation}
+from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
 The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
@@
 
-\todo{I'd like to compare these yields to previous studies, but it's been very difficult to make that comparison.
-I'm unsure whether the \citet{francois_evolution_2004} yields are net or gross (probably gross since their baseline is \citet{woosley_evolution_1995}).
-I tried to implement their yield tables in VICE, but the chemical evolution tracks came out looking very wrong.
-Also, they use a weird IMF.} \citet{francois_evolution_2004} report that their models are insensitive to changes in the yield at a factor of 2 level.
+Many previous two-infall studies have adopted the yields of \citet{francois_evolution_2004}, who in turn adapted those of \citet{woosley_evolution_1995} for CCSNe and \citet{iwamoto_nucleosynthesis_1999} for SNe Ia to provide a better fit between GCE models and local abundance data.
+Notably, the yields for O and Fe were left unchanged from the original studies.
+However, because \citet{woosley_evolution_1995} report gross yields without detailed initial abundances for their CCSN progenitors, and because \citet{francois_evolution_2004} do not provide population-averaged yields, it is difficult to make a comparison with our yield sets.
+Ultimately, \citet{francois_evolution_2004} report that their GCE models are insensitive to changes in the CCSN yield of O by a factor of 2, so we consider it reasonable to explore the full range of yields given in Table \ref{tab:yields}.
 
@@
     \includegraphics{figures/yield_outflow.pdf}
-    \caption{The abundance evolution of three one-zone models with different yield and outflow settings.
+    \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors.
 Table \ref{tab:yields} presents the population-averaged yields for each model.
@@
 Figure \ref{fig:yield-outflow} illustrates the effect of the yield scaling on the abundance evolution in one-zone models.
+We vary the outflow mass-loading factor $\eta$ for each model to achieve a consistent endpoint to the abundance evolution (see Section \ref{sec:outflows} for further discussion on outflows).
 All models feature a rapid dilution of the ISM metallicity by $\sim0.5-0.8$ dex, visible in the top two panels, brought on by the infall of pristine gas at $t_{\rm max}$.
-For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the present day.
+For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the close to present day.
 The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5\,{\rm Gyr}$ ago.

### 2025-04-07 src/tex/ms.tex

@@
 This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
+\todo{How does this compare to the age of GSE?}
 
@@
     \includegraphics{figures/spitoni_comparison.pdf}
-    \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021}.
-All models use the $y/Z_\odot=1$ yield set.
+    \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021} at three different galactocentric radii.
+All models use the $y/Z_\odot=1$ yield set and corresponding outflow prescription (see Table \ref{tab:yields}).
 The time markers and marginal panels are the same as in Figure \ref{fig:twoinfall-parameters}.
 We also include a 2-D heatmap of the APOGEE stellar abundances in each panel for reference.
-APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<120$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.
-\todo{Should I instead compare to Palla et al.
-(2020), who have a more cohesive multi-zone model rather than three independent one-zone models?}}
+APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<120$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.}
     \label{fig:spitoni-comparison}
@@
 The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
-The evolution of [Fe/H] is similar, but the approach to Solar abundance is slower because of the additional delay imposed on Fe production from SNe Ia.
+The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed on Fe production from SNe Ia.
 The \yZ{2} yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
-However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is much steeper than the data.
+However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is steeper than the data, especially for ages $\sim4-8\,{\rm Gyr}$.
 
@@
 
-Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters on the \yZ{1} model.
+We attempt to mitigate these discrepancies in the age--metallicity relation for the empirical yield scale. 
+% Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters on the \yZ{1} model.
+In column (b), we approximately double the strength of radial migration to $\sigma_{\rm RM8}=5.0\,{\rm kpc}$.
+For instance, the observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
+Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
+Therefore, column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ and a stronger migration prescription of $\sigma_{\rm RM8}=5\,{\rm kpc}$.
+As a result, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
+However, even though this prescription is much stronger than the estimates of, e.g., \citet{frankel_measuring_2018}, the model still significantly under-predicts the metallicity of $\sim4-9\,{\rm Gyr}$ old stars.
 
-The observed rise in the median abundance of stars with ages of $\sim4-8\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
-Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
-Column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ but with a stronger migration prescription of $\sigma_{\rm RM8}=5\,{\rm kpc}$.
-Here, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
-However, even though this prescription is much stronger than the estimates of, e.g., \citet{frankel_measuring_2018}, the model cannot reproduce the observed age--abundance trends in [O/H] and [Fe/H].
-
-Second, as in Section \ref{sec:abundance-distributions}, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
+Next, as in Section \ref{sec:abundance-distributions}, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
 Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
@@
 The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity --- an effect which can be compensated by a slightly increased value of $\eta$.
+This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.
 
@@
 The model produces the best agreement with the observed age--[Fe/H] relation (second row).
-However, agreement with the observed age--[O/Fe] relation is poor, as the [O/Fe] of the old low-$\alpha$ disk is $\sim0.1$ dex lower than observed.
+However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting less evolution in [O/Fe] over the past $\sim9$ Gyr than observed by $\approx0.1$ dex.
 
 Overall, no modification to the \yZ{1} model is able to completely overcome both the dilution and late-time evolution issues.
+Pre-enrichment of the accreted gas and a higher disk mass ratio can reduce the discrepancy with the data, but they cause issues of their own in the age--[O/Fe] plane.
 

### 2025-04-08 src/tex/ms.tex

@@
 \usepackage{xspace}
+% Dropped capital
+\usepackage{lettrine}
+
+% ***Fancy*** dropped capital
+\input Zallman.fd
+\renewcommand{\LettrineFontHook}{\usefont{U}{Zallman}{xl}{n}}
+\setcounter{DefaultLines}{3}%
 
 % user-defined commands
-% \newcommand{\yes}{\textcolor{green}{\checkmark}\xspace}
-% \newcommand{\meh}{\textcolor{black}{$\sim$}\xspace}
-% \newcommand{\no}{\textcolor{red}{$\times$}\xspace}
+\newcommand{\vice}{{\tt VICE}\xspace}
+\newcommand{\todo}[1]{{\color{red}#1}}
 \newcommand{\osuaffil}{Department of Astronomy, The Ohio State University, 140 W. 18th Ave, Columbus OH 43210, USA}
@@
 \newcommand{\yZ}[1]{$y/Z_\odot=#1$}
-\newcommand{\vice}{{\tt VICE}\xspace}
-% \newcommand{\hydro}{{\tt h277}\xspace}
-\newcommand{\todo}[1]{{\color{red}#1}}
 
@@
 % \todo{Hook, summary of alpha-bimodality.}
-Studies of galactic chemical evolution (GCE) aim to explain observed stellar abundance patterns by modeling the star formation history of the Milky Way.
-A long-standing paradigm of GCE has been that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars.
+\lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the observed stellar abundance patterns in the Milky Way by modeling the star formation history and evolution of the Galaxy.
+A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars.
 In this view, one feature of the Milky Way disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
@@
     \centering
-\caption{Number of APOGEE stars in each Galactic region.}
-\label{tab:apogee-regions}
-\input{output/apogee_regions_table.tex}
-\end{table*}
-
-\begin{table*}
-    \centering
     \caption{Median and dispersion in APOGEE parameter uncertainties.}
@@
 
+\begin{table*}
+\centering
+\caption{Number of APOGEE stars in each Galactic region.}
+\label{tab:apogee-regions}
+\input{output/apogee_regions_table.tex}
+\end{table*}
+
 We compare our models against stellar abundances from the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{majewski_apache_2017} data release 17 \citep[DR17;][]{abdurrouf_seventeenth_2022}.
@@
 When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}.
-Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width.
+Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width \todo{(do I need this table?)}.
 
@@
 We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
-\todo{Note about metallicity cutoff for luminous giants.}
+\todo{Note about metallicity cutoff for luminous giants. Cite: \citet{cao_modeling_2025}}
 
@@
     \tablehead{
-        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Alternatives} & \colhead{Section} & \colhead{Description}
+        \colhead{Quantity} & \colhead{Fiducial Value} & \colhead{Alternatives} & \colhead{Section} & \colhead{Description}
     }
     \startdata
+        y/Z_\odot           & 1         & 2, 3              & \ref{sec:yields}              & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
         f_{\rm Ia}(t)       & Equation \ref{eq:plateau-dtd} & Equation \ref{eq:powerlaw-dtd}    & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
+        \eta_\odot          & 0.2       & 1.4, 2.4          & \ref{sec:outflows}            & Outflow mass-loading factor at $R_\odot$ (see Table \ref{tab:yields}) \\
         R_\eta              & 5.0 kpc   & ---               & \ref{sec:outflows}            & Exponential outflow scale radius \\
@@
 
-The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset.
-\todo{Is this offset a problem?
-I could raise the SN Ia yields, but the global distributions would not match quite as well.} The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields.
+The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset (which could be corrected by raising the SN Ia yield).
+The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields.
 Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution.
-As the $y/Z_\odot=2$ and $y/Z_\odot=3$ models show generally similar behavior, we focus on the $y/Z_\odot=1$ and $y/Z_\odot=2$ yield sets for the remainder of this work.
+As the \yZ{2} and \yZ{3} models show generally similar behavior, we focus on the \yZ{1} and \yZ{2} yield sets for the remainder of this study.
 
@@
 % we find that if we adopt this prescription, models with $y/Z_\odot=1$ predict sub-Solar abundances at the present day because they have not yet reached their equilibrium value. 
+\todo{This is not a constraint that most two-infall studies seem to care about.}
 
@@
 % \todo{Motivate exponential scale radius.}
+
+We use an outflow mass-loading factor because it allows us to test a range of yield scales while maintaining our desired endpoint of $Z_{\rm final}\approx Z_\odot$ \todo{(rewrite)}.
+
+The presence of outflows is not a necessary ingredient for the results of this study.
+We run a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, and find that it predicts similar abundance evolution and nearly identical stellar abundance distributions to the model with $\eta=0.2$ and \yZ{1}.
+If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.
 
@@
     \label{eq:pre-enrichment}
-    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{\mathXH_{\rm CGM}}.
+    Z_{\rm in}(t) = (1 - e^{-t/\tau_{\rm rise}}) Z_\odot 10^{\mathXH_{\rm CGM}}.
 \end{equation}
@@
 The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the previous models.
-\todo{Note that APOGEE high-$\alpha$ sequence is over-emphasized by survey selection function.} In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \Z{2} case.
+\todo{Note that APOGEE high-$\alpha$ sequence is over-emphasized by survey selection function.} In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \yZ{2} case.
 These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.
@@
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius.
-A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
 For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
@@
 In the model, the {\it right} peak is produced during the first infall (i.e., thick disk) and the {\it left} is immediately after the second infall (i.e., low-metallicity end of thin disk).}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/ofe_feh_best.pdf}
+    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\eta_\odot=1.8$.
+Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age.
+A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm NN}$) and abundance uncertainties in Table \ref{tab:uncertainties}.
+The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region.
+{\bf Key takeaway:} }
+    \label{fig:ofe-feh-best}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/lmr_ages.pdf}
+    \caption{Caption.}
+    \label{fig:lmr-ages}
+\end{figure*}
 

### 2025-04-09 src/tex/ms.tex
Updates from Overleaf

@@
 \newcommand{\yZ}[1]{$y/Z_\odot=#1$}
+\newcommand{\kpc}{\,{\rm kpc}}
 
@@
 \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
-\citet{nataf_accurate_2024} also observe multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.
-\citet{chen_recent_2025} however argue that this trend can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
+\citet{nataf_accurate_2024} also observed multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.
+\citet{chen_recent_2025}, however, argue that this trend can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
 
@@
         NN age error        & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
-        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15\,{\rm kpc}$    & Eliminate bulge \& extreme outer-disk stars \\
-        $|z|$               & $|z| < 2\,{\rm kpc}$                 & Eliminate halo stars \\
+        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15\kpc$    & Eliminate bulge \& extreme outer-disk stars \\
+        $|z|$               & $|z| < 2\kpc$                 & Eliminate halo stars \\
         \hline
@@
 Table \ref{tab:uncertainties} presents the median statistical uncertainty and uncertainty dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the calibrated [Fe/H] and [O/Fe] abundances for our sample.
-When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}.
+When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\kpc$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}.
 Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width \todo{(do I need this table?)}.
@@
 Following the recommendations of \citet{leung_variational_2023}, we use an upper limit on the relative age uncertainty of 40\%.
-This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$).
+This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
 The median uncertainty in $\log({\rm age}/{\rm Gyr})$ is 0.10 (see Table \ref{tab:uncertainties}).
@@
 The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}.
-We set up a disk with radial extent $0\leq R_{\rm gal}<20\,{\rm kpc}$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
+We set up a disk with radial extent $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
 We use a time-step size of $\Delta t=10\,{\rm Myr}$ and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
@@
 Stellar populations migrate between zones as described in Section \ref{sec:migration}, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones.
-We inhibit star formation past $R_{\rm gal}>15.5\,{\rm kpc}$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
+We inhibit star formation past $R_{\rm gal}>15.5\kpc$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
 We also assign a final midplane distance to each stellar population as described in Section \ref{sec:migration}.
@@
 Table \ref{tab:yields} presents the population-averaged yields for each model.
-The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\,{\rm kpc}$, $0\leq|z|<0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
+The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
     \label{fig:yield-outflow}
@@
 \end{equation}
-where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\,{\rm kpc}$.
+where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
 As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [Fe/H] with $R_{\rm gal}$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\,{\rm kpc}^{-1}$ \todo{(citations)}.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$ \todo{(citations)}.
 % The exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla\mathOH_{\rm eq}$:
@@
 % \end{equation}
-% We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
+% We adopt $R_\eta=7.2\kpc$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
 % \todo{Motivate exponential scale radius.}
@@
 \end{equation}
-We adopt a thick disk scale radius of $R_1=2.0\,{\rm kpc}$, a thin disk scale radius of $R_2=2.5\,{\rm kpc}$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
+We adopt a thick disk scale radius of $R_1=2.0\kpc$, a thin disk scale radius of $R_2=2.5\kpc$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
 In the Solar neighborhood, this produces a thick-to-thin disk mass ratio of $f_\Sigma(R_\odot)=0.12$.
@@
 This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
-We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\,{\rm Gyr}$ at the Solar annulus and a scale radius $R_{\tau_2}=7\,{\rm kpc}$.
+We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\,{\rm Gyr}$ at the Solar annulus and a scale radius $R_{\tau_2}=7\kpc$.
 This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
@@
 \end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ \todo{(?)} and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citet{leroy_star_2008}.
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ \todo{(?)} and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citet{leroy_star_2008}.
 Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\varepsilon$:
@@
     \caption{(a) The infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
-Each panel plots the history for six different zones of width $\delta R_{\rm gal}=0.1\,{\rm kpc}$, color-coded by Galactocentric radius.}
+Each panel plots the history for six different zones of width $\delta R_{\rm gal}=0.1\kpc$, color-coded by Galactocentric radius.}
     \label{fig:sfh}
@@
 \begin{equation}
-    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61},
+    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\kpc}\Big)^{0.61},
     \label{eq:radial-migration}
 \end{equation}
-where we adopt $\sigma_{\rm RM8}=2.68\,{\rm kpc}$ as the fiducial value for the strength of radial migration.
-This is smaller than the value of $\sigma_{\rm RM8}=3.6\,{\rm kpc}$ found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.
+where we adopt $\sigma_{\rm RM8}=2.68\kpc$ as the fiducial value for the strength of radial migration.
+This is smaller than the value of $\sigma_{\rm RM8}=3.6\kpc$ found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.
 
@@
 \begin{equation}
-    h_z(\tau,R_{\rm final}) = \Big(\frac{0.24\,{\rm kpc}}{e^2}\Big) \exp\Big(\frac{\tau}{7\,{\rm Gyr}} + \frac{R_{\rm final}}{6\,{\rm kpc}}\Big).
+    h_z(\tau,R_{\rm final}) = \Big(\frac{0.24\kpc}{e^2}\Big) \exp\Big(\frac{\tau}{7\,{\rm Gyr}} + \frac{R_{\rm final}}{6\kpc}\Big).
     \label{eq:scale-height}
@@
 
-\subsection{Local Abundance Patterns}
+\subsection{The Scale of Yields \& Outflows}
+\label{sec:multizone-yields}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figures/abundance_evolution_yields.pdf}
+    \caption{Stellar age--abundance relations produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
+Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
+A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
+The black curve plots the ISM abundance at $R_{\rm gal}=8\kpc$ over time.
+The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
+Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
+{\bf Key takeaway:} Both models feature a major dilution event at a lookback time of 9 Gyr, and for model (a) the dilution persists throughout much of the thin disk epoch.}
+    \label{fig:abundance-evolution-yields}
+\end{figure}
+
+We first examine the differences between multi-zone models which assume different yield and outflow scales.
+Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations produced by models with \yZ{1} and \yZ{2} with fiducial parameters (Table \ref{tab:multizone-parameters}).
+The dilution effect discussed in Section \ref{sec:yields} is clearly seen here.
+The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
+The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed on Fe production from SNe Ia.
+The \yZ{2} yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
+However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is steeper than the data, especially for ages $\sim4-8\,{\rm Gyr}$.
+
+\subsection{Local Abundance Evolution}
+\label{sec:age-abundance}
+
+\begin{figure*}
+    \centering
+    \includegraphics{figures/abundance_evolution_params.pdf}
+    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}.
+The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
+{\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
+    \label{fig:abundance-evolution-params}
+\end{figure*}
+
+We attempt to mitigate these discrepancies in the age--metallicity relation for the empirical yield scale. 
+% Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters on the \yZ{1} model.
+In column (b), we approximately double the strength of radial migration to $\sigma_{\rm RM8}=5.0\kpc$.
+For instance, the observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
+Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
+Therefore, column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ and a stronger migration prescription of $\sigma_{\rm RM8}=5\kpc$.
+As a result, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
+However, even though this prescription is much stronger than the estimates of, e.g., \citet{frankel_measuring_2018}, the model still significantly under-predicts the metallicity of $\sim4-9\,{\rm Gyr}$ old stars.
+
+Next, as in Section \ref{sec:abundance-distributions}, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
+Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
+Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
+The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, because the enriched gas accretion imposes a lower limit on the metallicity of the outermost regions, from which the stars of the low-metallicity tail in the Solar neighborhood are drawn.
+The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity --- an effect which can be compensated by a slightly increased value of $\eta$.
+This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.
+
+Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger, $f_\Sigma(R_\odot)=0.48$.
+This is higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
+Column (d) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase.
+The model produces the best agreement with the observed age--[Fe/H] relation (second row).
+However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting less evolution in [O/Fe] over the past $\sim9$ Gyr than observed by $\approx0.1$ dex.
+
+Overall, no modification to the \yZ{1} model is able to completely overcome both the dilution and late-time evolution issues.
+Pre-enrichment of the accreted gas and a higher disk mass ratio can reduce the discrepancy with the data, but they cause issues of their own in the age--[O/Fe] plane.
+
+\subsection{Abundance Evolution Across the Disk}
+\label{sec:disk-evolution}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
+    \caption{Evolution of the MDF across the Galactic disk.
+Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age.
+Rows (a) and (b) present the distributions from multi-zone GCE models with different yield scales.
+For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$.
+A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+Row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
+The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\kpc$ age bin for reference.
+Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
+Distributions in all panels are restricted to $0\leq|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
+{\bf Key takeaway:} The APOGEE data show remarkably little variation in the mode at all radii over the past $\sim6-8$ Gyr, while both GCE models produce a steady evolution toward higher [Fe/H] with time.}
+    \label{fig:mdf-evolution}
+\end{figure*}
+
+The discrepancies between the predicted and observed abundance evolution discussed in Section \ref{sec:age-abundance} are also seen across the disk.
+Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the \yZ{1} and \yZ{2} models.
+We adopt pre-enriched infall ($\mathFeH_{\rm CGM}=-0.7$), stronger radial migration ($\sigma_{\rm RM8}=3.6$ kpc), and a higher disk mass ratio ($f_\Sigma(R_\odot)=0.25$) because these parameters were able to improve agreement with observations in previous sections.
+For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages $\leq10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
+
+The two-infall model predicts a very broad MDF for ages $>10$ Gyr because of the rapid enrichment of the ISM during the first infall epoch.
+
+Figure \ref{fig:mdf-evolution} shows that even with pre-enriched infall, both of our models predict that the MDF shifts to the left going from younger to older populations.
+On the other hand, the data show that the MDF broadens with age, which we attribute to radial migration, but its peak does not shift substantially over the past $\sim6-8$ Gyr.
+While the mode of the MDF shifts depending on the radial bin, its evolution is remarkably consistent over the entire disk, in line with the equilibrium scenario of \citet{johnson_milky_2024}.
+\todo{Note about metallicity cutoff for luminous giants.}
+
+On the other hand, the model predictions for the MDF in the $8-10\,{\rm Gyr}$ age bin are strikingly similar to the APOGEE MDF.
+The two-infall model predicts a bimodal distribution: the metal-rich component comprises stars formed during the last Gyr of the first infall epoch, and the metal-poor component is stars formed during the first Gyr of the second infall epoch (post-dilution).
+The data show this same bimodal structure in all but the outermost radial bin, with peaks at $\mathFeH\approx-0.3$ and $+0.3$.
+While the location of the model peaks depends on $R_{\rm gal}$, in the data they are quite consistent from the innermost to the outermost bin.
+\todo{I actually think the two-infall model gets this right for the wrong reasons.
+In the data, the left peak is the high-$\alpha$ sequence and the right is the high-metallicity end of the low-$\alpha$ sequence.
+In the model, the {\it right} peak is produced during the first infall (i.e., thick disk) and the {\it left} is immediately after the second infall (i.e., low-metallicity end of thin disk).}
+
+\subsection{The Local Abundance Topology}
 \label{sec:abundance-distributions}
@@
 The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
-Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\,{\rm kpc}$ and $0.5\leq|z|<1\,{\rm kpc}$ to highlight the $\alpha$-bimodality in the Solar neighborhood.
+Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $0.5\leq|z|<1\kpc$ to highlight the $\alpha$-bimodality in the Solar neighborhood.
 {\bf Key takeaway:} the two-infall model generically predicts a stellar overdensity at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.}
@@
 Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model at mid to high Galactic latitudes.
-Between $0.5\leq|z|<1\,{\rm kpc}$, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over ($\mathFeH\approx-0.3$, $\mathOFe\approx0.1-0.2$), which is not seen in the APOGEE sample.
+Between $0.5\leq|z|<1\kpc$, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over ($\mathFeH\approx-0.3$, $\mathOFe\approx0.1-0.2$), which is not seen in the APOGEE sample.
 This over-density occurs because the overall rate of chemical evolution slows down $\sim2\,{\rm Gyr}$ after the second infall, and at the same time the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
@@
 
-\subsection{Abundances Across the Disk}
+\subsection{Global [O/Fe] Distributions: Two or Three Peaks?}
 \label{sec:disk-abundances}
@@
 
-\subsection{Local Abundance Evolution}
-\label{sec:age-abundance}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figures/abundance_evolution_yields.pdf}
-    \caption{Stellar age--abundance relations produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
-Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius.
-A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
-For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
-The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time.
-The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
-Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
-{\bf Key takeaway:} Both models feature a major dilution event at a lookback time of 9 Gyr, and for model (a) the dilution persists throughout much of the thin disk epoch.}
-    \label{fig:abundance-evolution-yields}
-\end{figure}
-
-The dilution effect discussed in Section \ref{sec:yields} is clearly seen in the multi-zone model results.
-Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations produced by models with \yZ{1} and \yZ{2} with fiducial parameters (Table \ref{tab:multizone-parameters}).
-The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major dilution of $\sim0.5$ dex at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
-The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed on Fe production from SNe Ia.
-The \yZ{2} yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
-However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is steeper than the data, especially for ages $\sim4-8\,{\rm Gyr}$.
-
-\begin{figure*}
-    \centering
-    \includegraphics{figures/abundance_evolution_params.pdf}
-    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}.
-The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
-{\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
-    \label{fig:abundance-evolution-params}
-\end{figure*}
-
-We attempt to mitigate these discrepancies in the age--metallicity relation for the empirical yield scale. 
-% Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters on the \yZ{1} model.
-In column (b), we approximately double the strength of radial migration to $\sigma_{\rm RM8}=5.0\,{\rm kpc}$.
-For instance, the observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
-Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
-Therefore, column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ and a stronger migration prescription of $\sigma_{\rm RM8}=5\,{\rm kpc}$.
-As a result, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
-However, even though this prescription is much stronger than the estimates of, e.g., \citet{frankel_measuring_2018}, the model still significantly under-predicts the metallicity of $\sim4-9\,{\rm Gyr}$ old stars.
-
-Next, as in Section \ref{sec:abundance-distributions}, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
-Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
-Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
-The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, because the enriched gas accretion imposes a lower limit on the metallicity of the outermost regions, from which the stars of the low-metallicity tail in the Solar neighborhood are drawn.
-The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity --- an effect which can be compensated by a slightly increased value of $\eta$.
-This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.
-
-Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger, $f_\Sigma(R_\odot)=0.48$.
-This is higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
-Column (d) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase.
-The model produces the best agreement with the observed age--[Fe/H] relation (second row).
-However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting less evolution in [O/Fe] over the past $\sim9$ Gyr than observed by $\approx0.1$ dex.
-
-Overall, no modification to the \yZ{1} model is able to completely overcome both the dilution and late-time evolution issues.
-Pre-enrichment of the accreted gas and a higher disk mass ratio can reduce the discrepancy with the data, but they cause issues of their own in the age--[O/Fe] plane.
-
-\subsection{Abundance Evolution Across the Disk}
-\label{sec:disk-evolution}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
-    \caption{Evolution of the MDF across the Galactic disk.
-Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age.
-Rows (a) and (b) present the distributions from multi-zone GCE models with different yield scales.
-For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$.
-A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
-Row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
-The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference.
-Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
-Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
-{\bf Key takeaway:} The APOGEE data show remarkably little variation in the mode at all radii over the past $\sim6-8$ Gyr, while both GCE models produce a steady evolution toward higher [Fe/H] with time.}
-    \label{fig:mdf-evolution}
-\end{figure*}
-
-The discrepancies between the predicted and observed abundance evolution discussed in Section \ref{sec:age-abundance} are also seen across the disk.
-Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the \yZ{1} and \yZ{2} models.
-We adopt pre-enriched infall ($\mathFeH_{\rm CGM}=-0.7$), stronger radial migration ($\sigma_{\rm RM8}=3.6$ kpc), and a higher disk mass ratio ($f_\Sigma(R_\odot)=0.25$) because these parameters were able to improve agreement with observations in previous sections.
-For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages $\leq10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
-
-The two-infall model predicts a very broad MDF for ages $>10$ Gyr because of the rapid enrichment of the ISM during the first infall epoch.
-
-Figure \ref{fig:mdf-evolution} shows that even with pre-enriched infall, both of our models predict that the MDF shifts to the left going from younger to older populations.
-On the other hand, the data show that the MDF broadens with age, which we attribute to radial migration, but its peak does not shift substantially over the past $\sim6-8$ Gyr.
-While the mode of the MDF shifts depending on the radial bin, its evolution is remarkably consistent over the entire disk, in line with the equilibrium scenario of \citet{johnson_milky_2024}.
-\todo{Note about metallicity cutoff for luminous giants.}
-
-On the other hand, the model predictions for the MDF in the $8-10\,{\rm Gyr}$ age bin are strikingly similar to the APOGEE MDF.
-The two-infall model predicts a bimodal distribution: the metal-rich component comprises stars formed during the last Gyr of the first infall epoch, and the metal-poor component is stars formed during the first Gyr of the second infall epoch (post-dilution).
-The data show this same bimodal structure in all but the outermost radial bin, with peaks at $\mathFeH\approx-0.3$ and $+0.3$.
-While the location of the model peaks depends on $R_{\rm gal}$, in the data they are quite consistent from the innermost to the outermost bin.
-\todo{I actually think the two-infall model gets this right for the wrong reasons.
-In the data, the left peak is the high-$\alpha$ sequence and the right is the high-metallicity end of the low-$\alpha$ sequence.
-In the model, the {\it right} peak is produced during the first infall (i.e., thick disk) and the {\it left} is immediately after the second infall (i.e., low-metallicity end of thin disk).}
+\subsection{Age Patterns}
 
@@
 The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region.
-{\bf Key takeaway:} }
+{\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.}
     \label{fig:ofe-feh-best}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/lmr_ages.pdf}
-    \caption{Caption.}
+    \includegraphics[width=0.8\textwidth]{figures/lmr_ages.pdf}
+    \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
+The left panel plots the output of our best two-infall model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\eta_\odot=1.8$.
+The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the abundances and ages according to Table \ref{tab:uncertainties}.
+The right panel plots the results from APOGEE using the \citet{leung_variational_2023} age catalog.
+The contours indicate the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
+    {\it Bottom}: Stellar age distributions in the Solar annulus for all stars (black) and LMR stars (gray).
+The left panel plots the results from the two-infall model after forward-modeling age uncertainties, and the right panel plots the \citet{leung_variational_2023} ages for APOGEE stars.
+    {\bf Key takeaway:} The two-infall model predicts a fundamentally different age pattern than what is observed, especially for LMR stars.}
     \label{fig:lmr-ages}
@@
 Both models assume the \yZ{2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
-The greyscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq|z|\leq2\,{\rm kpc}$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
+The greyscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq|z|\leq2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}

### 2025-04-18 src/tex/ms.tex
Updates from Overleaf

@@
 \newcommand{\kpc}{\,{\rm kpc}}
+\newcommand{\Gyr}{\,{\rm Gyr}}
 
@@
 An $\alpha$-bimodality is not a universal feature in simulated Milky Way-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our own galaxy may provide clues to its unique evolutionary history.
-GCE models that attempt to solve this problem generally fall into two camps: some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}; others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \todo{(citations)} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
+GCE models that attempt to solve this problem generally fall into two camps: some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}; others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
 
@@
 
-\todo{Outflows.} Most previous studies of the two-infall model do not include mass-loaded outflows.
+% \todo{Outflows.} 
+Most previous studies of the two-infall model do not include mass-loaded outflows.
 Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to the point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal.
@@
 We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient.
-
-\todo{Migration.} The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
+\todo{Trim down, move some to methods.}
+
+% \todo{Migration.} 
+The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
 \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating.
@@
 
-\todo{Summary of secular evolution models which claim alpha-bimodality.} \citet{schonrich_chemical_2009}.
-\citet{kubryk_evolution_2015}.
-\citet{sharma_chemical_2021}, \citet{chen_chemical_2023}.
+\todo{Summary of secular evolution models which claim alpha-bimodality.} By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}.
+\citet{kubryk_evolution_2015} produce two parallel sequences in \aFe vs [Fe/H] by making a simple age cut to the results of their multi-zone GCE model, though because they do not present stellar \aFe distributions it is hard to determine whether their distributions are truly bimodal.
+In the model of \citet{sharma_chemical_2021}, a sharp transition in stellar \aFe for $8-12\Gyr$ old stars plus radial migration are the key ingredients for predicting a MW-like bimodality; however, their approach to the chemical evolution is not {\it ab initio}, meaning that instead of integrating the enrichment equations for their adopted star formation history, they simply assume a functional form for the abundance evolution over time \todo{(rewrite)}.
+\todo{Sharma basically says that it's possible to have a continuous star formation history and reproduce the $\alpha$-bimodality.} \citet{chen_chemical_2023} confirmed the findings of \citet{sharma_chemical_2021} in an {\it ab initio} multi-zone GCE model (with a two-phase ISM and radial gas flows but no outflows) and were able to produce a bimodal \aFe distribution; however, some discrepancies remain, including that the metallicity of the high-$\alpha$ sequence is too low and not extended enough.
+\citet{chen_chemical_2023} found that the abundance gap is caused by the simultaneous decline in SFR and \aFe.
 \citet{prantzos_origin_2023}.
 
-\todo{Introduce equilibrium model.}
+% \todo{Introduce equilibrium model.} 
+As stellar age estimation techniques have improved over recent years, large catalogs have become available with ages for hundreds of thousands or even millions of stars from a wide swath of the Galaxy.
+In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, \citet{johnson_milky_2024} examined the age--metallicity relation at different radii from the astroNN catalog \citep{mackereth_dynamical_2019} and found that the mode of the metallicity distribution at a given radius is nearly independent from age over the past $\sim9\Gyr$.
+They propose an ``equilibrium scenario'' in which the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over $\sim\Gyr$ timescales.
+Whether the equilibrium metallicity is driven by outflows, as proposed by \citet{johnson_milky_2024}, or by other factors such as a radial gas flow, the current data suggest that the gas abundance across the Galaxy has evolved very little over most of the thin disk lifetime.
 
@@
 
-\subsection{The Scale of Yields \& Outflows}
-\label{sec:multizone-yields}
+\subsection{Dilution \& Approach to Equilibrium}
+\label{sec:age-abundance}
 
@@
 
+The dilution effect discussed in Section \ref{sec:yields} is clearly seen in the multi-zone model results.
 We first examine the differences between multi-zone models which assume different yield and outflow scales.
 Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations produced by models with \yZ{1} and \yZ{2} with fiducial parameters (Table \ref{tab:multizone-parameters}).
-The dilution effect discussed in Section \ref{sec:yields} is clearly seen here.
 The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
@@
 However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is steeper than the data, especially for ages $\sim4-8\,{\rm Gyr}$.
-
-\subsection{Local Abundance Evolution}
-\label{sec:age-abundance}
 
@@
 
-We attempt to mitigate these discrepancies in the age--metallicity relation for the empirical yield scale. 
-% Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters on the \yZ{1} model.
-In column (b), we approximately double the strength of radial migration to $\sigma_{\rm RM8}=5.0\kpc$.
-For instance, the observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
+We next attempt to mitigate the dilution and late-time evolution problems for the empirical (\yZ{1}) yield scale. 
+Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the metallicity of the infalling gas $\mathXH_{\rm CGM}$, and (d) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$.
+
+The observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
 Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
@@
 
-Next, as in Section \ref{sec:abundance-distributions}, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
-Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
+Next, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
+Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population \todo{(reword}).
 Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
 The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, because the enriched gas accretion imposes a lower limit on the metallicity of the outermost regions, from which the stars of the low-metallicity tail in the Solar neighborhood are drawn.
-The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity --- an effect which can be compensated by a slightly increased value of $\eta$.
+The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity---an effect which can be compensated by a slightly increased value of $\eta$.
 This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.
 
-Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger, $f_\Sigma(R_\odot)=0.48$.
+Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger that the fiducial value, $f_\Sigma(R_\odot)=0.5$.
 This is higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
@@
 
-\subsection{Global [O/Fe] Distributions: Two or Three Peaks?}
+\subsection{Global Abundance Distributions}
 \label{sec:disk-abundances}
+
+\subsubsection{The [O/Fe] Distribution: Two or Three Peaks?}
 
@@
 
-\subsection{Age Patterns}
+\subsubsection{The Best Model}
+\label{sec:ofe-feh-best}
 
@@
 \end{figure*}
+
+\subsection{Local Age Patterns}
 
@@
 
+The two-infall model makes a prediction about the local stellar age distribution that is fundamental to its construction: that the most metal-rich stars in any region of the Galaxy come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
+This prediction can be seen in any of the panels in Figure \ref{fig:ofe-feh-best}.
+In Figure \ref{fig:lmr-ages}, there is a sharp divide in the median age of local metal-rich (LMR; $\mathFeH\gtrsim+0.1$) stars when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
+
 \section{Discussion}
@@
 Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
+
+\subsection{Third Accretion Episode}
 

### 2025-04-22 src/tex/ms.tex

@@
 An $\alpha$-bimodality is not a universal feature in simulated Milky Way-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our own galaxy may provide clues to its unique evolutionary history.
-GCE models that attempt to solve this problem generally fall into two camps: some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}; others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
+GCE models that attempt to solve this problem generally fall into two camps.
+Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}.
+Others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
 
@@
 Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts.
-The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between.
+The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
 % By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
@@
 The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model.
-\citet{spitoni_remind_2024} argued that the gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, supports a haitus in star formation which is a natural consequence of the two-infall model.
-\citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
+\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a haitus in the star formation history, which is a natural consequence of the two-infall model.
+In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation, which would naturally be explained by the two-infall scenario.
+Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \todo{(citations)}, although these observables can also be matched by other models \todo{(citations)}.
+% \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
 \citet{nataf_accurate_2024} also observed multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.
-\citet{chen_recent_2025}, however, argue that this trend can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
 
@@
 Most previous studies of the two-infall model do not include mass-loaded outflows.
-Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to the point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal.
+Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal.
 However, other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \todo{(citations)}.
@@
 The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
-\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating.
-It is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}.
+However, the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
+\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}.
 Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor requires assumptions about the evolution of the Milky Way's radial metallicity gradient.
@@
 
-\todo{Summary of secular evolution models which claim alpha-bimodality.} By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}.
+% \todo{Summary of secular evolution models which claim alpha-bimodality.} 
+In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
+By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}.
 \citet{kubryk_evolution_2015} produce two parallel sequences in \aFe vs [Fe/H] by making a simple age cut to the results of their multi-zone GCE model, though because they do not present stellar \aFe distributions it is hard to determine whether their distributions are truly bimodal.
@@
 \citet{chen_chemical_2023} found that the abundance gap is caused by the simultaneous decline in SFR and \aFe.
-\citet{prantzos_origin_2023}.
+\todo{\citet{prantzos_origin_2023}.}
+\citet{chen_recent_2025} argue that the double age--metallicity sequences observed by \citet{nissen_high-precision_2020} can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
+\todo{Trim this WAY down.}
 
@@
     \centering
-    \includegraphics{figures/yield_outflow.pdf}
+    \includegraphics[width=\linewidth]{figures/yield_outflow.pdf}
     \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors.
 Table \ref{tab:yields} presents the population-averaged yields for each model.
-The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
+The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
+The black points with error bars indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
     \label{fig:yield-outflow}
@@
 Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution.
-As the \yZ{2} and \yZ{3} models show generally similar behavior, we focus on the \yZ{1} and \yZ{2} yield sets for the remainder of this study.
+As the \yZ{2} and \yZ{3} models behave qualitatively similarly, we focus on the \yZ{1} and \yZ{2} yield sets for the remainder of this study.
 
@@
 
-Most studies of the two-infall model assume the Milky Way has no significant mass-loaded outflows.
+Mass-loaded outflows are a useful tool for scaling the endpoint of GCE models.
+\citet{weinberg_equilibrium_2017} showed that in the case of exponentially declining star formation, the O abundance approaches an equilibrium value at
+\begin{equation}
+    \label{eq:equilibrium}
+    Z_{\rm O,eq} = \frac{y_{\rm O}^{\rm CC}}{1 + \eta - r - \tau_\star/\tau_{\rm SFH}},
+\end{equation}
+where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the star formation timescale, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
+Equation \ref{eq:equilibrium} can be inverted to calculate the value of $\eta$ required to reach a desired $Z_{\rm O,eq}$ with a given yield, but it is inaccurate in the limit of zero accretion.
+We adopt values of $\eta_\odot=\eta(R=R_\odot)$ for each of our yield sets presented in Table \ref{tab:yields}.
+Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than would be suggested by Equation \ref{eq:equilibrium} in order to reach Solar metallicity at the end of the model.
+
+Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
+In order to produce an exponentially declining radial metallicity gradient, we adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
+\begin{equation}
+    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
+\end{equation}
+where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
+As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [O/H] with $R_{\rm gal}$.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$ \todo{(citations)}.
+
+We use an outflow mass-loading factor because it allows us to test a range of yield scales while maintaining our desired endpoint of $Z_{\rm final}\approx Z_\odot$ \todo{(rewrite)}.
+
+Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
 Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023}.
-To achieve a realistic radial metallicity gradient, many studies use a prescription for the infall timescale of the thin disk which increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
+To achieve a realistic radial metallicity gradient, many studies adopt the yields of \citet{francois_evolution_2004} and use a prescription for the infall timescale of the thin disk which increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
+\todo{Additionally, many two-infall models reach a final metallicity higher than Solar.
+Citations for present-day gas abundance in the Solar neighborhood.}
+
+As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
 Because we aim to study the effect of the yield assumptions on two-infall model predictions, we use mass-loaded outflows to control the final state of chemical evolution across the disk.
-As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
-
-\citet{weinberg_equilibrium_2017} showed that in the limit of continuous star formation, the ISM abundance approaches an equilibrium which is determined by the balance of yields, outflows, and star formation timescales.
-The mass-loading factor $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ required to reach equilibrium at Solar metallicity is
-\begin{equation}
-    \label{eq:equilibrium-eta}
-    \eta_\odot = y_{\rm O}^{\rm CC} / Z_{\rm O,\odot} - 1 + r + \tau_\star / \tau_{\rm SFH},
-\end{equation}
-where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, and $\tau_{\rm SFH}$ is the star formation timescale.
-Equation \ref{eq:equilibrium-eta} informs our choice of $\eta$, but it is inaccurate in the two-infall case because of the bursty star formation history.
-Therefore, we tune the value of $\eta_\odot$ so that the model reaches $\mathOH=0.0$ by the end for each yield set, shown in Table \ref{tab:yields}.
-% we find that if we adopt this prescription, models with $y/Z_\odot=1$ predict sub-Solar abundances at the present day because they have not yet reached their equilibrium value. 
-\todo{This is not a constraint that most two-infall studies seem to care about.}
-
-We adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
-\begin{equation}
-    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
-\end{equation}
-where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
-As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [Fe/H] with $R_{\rm gal}$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$ \todo{(citations)}.
-% The exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla\mathOH_{\rm eq}$:
-% \begin{equation}
-%     R_\eta = -\frac{1}{\nabla\mathOH_{\rm eq} \times\ln(10)}.
-% \end{equation}
-% We adopt $R_\eta=7.2\kpc$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
-% \todo{Motivate exponential scale radius.}
-
-We use an outflow mass-loading factor because it allows us to test a range of yield scales while maintaining our desired endpoint of $Z_{\rm final}\approx Z_\odot$ \todo{(rewrite)}.
-
-The presence of outflows is not a necessary ingredient for the results of this study.
-We run a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, and find that it predicts similar abundance evolution and nearly identical stellar abundance distributions to the model with $\eta=0.2$ and \yZ{1}.
-If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.
+However, mass-loaded outflows are not a necessary ingredient for the results of this study.
+We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the model with $\eta=0.2$ and \yZ{1}.
+Therefore, our multizone models with \yZ{1} should predict similar behavior to a model without any mass-loaded outflows.
+%If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.
 
@@
 We also include a 2-D heatmap of the APOGEE stellar abundances in each panel for reference.
-APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<120$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.}
+APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<10$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.}
     \label{fig:spitoni-comparison}
@@
 \begin{itemize}
-    \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a low-$\alpha$ sequence with a fundamentally different abundance structure than observed.
-A low yield set ($y/Z_\odot=1$) coupled with lower outflows, or pre-enrichment of the infalling gas, can bring the stellar [O/Fe] distributions more in line with the data.
     \item The large quantity of pristine gas accreted in the Solar neighborhood during the second infall phase rapidly dilutes the ISM metallicity by $\sim0.5$ dex.
-Models with a low yield set ($y/Z_\odot=1$) remain at sub-Solar metallicity until the present day, in stark contrast to the observed local age--metallicity relation.
-This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
+Models with low nucleosynthetic yields (\yZ{1}) remain at sub-Solar metallicity until the present day, in stark contrast to the observed local age--metallicity relation.
+Models with higher yields and outflows approach the present-day metallicity more rapidly, while pre-enriched infall can reduce the magnitude of the dilution (but not eliminate it entirely).
+%This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
+    \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a double-peaked low-$\alpha$ sequence with a fundamentally different abundance structure than observed, especially for models with higher yields.
+A low yield set (\yZ{1}) coupled with lower outflows, or pre-enrichment of the infalling gas, can bring the stellar [O/Fe] distributions more in line with the data.
+    \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations.
+In contrast, the data show a smooth gradient between the oldest and youngest stars, with most of the metal-rich stars having intermediate ages.
     \item Our models predict that the MDF evolves to higher metallicity over time throughout the disk.

### 2025-04-24 src/tex/ms.tex
Updates from Overleaf

@@
 % \todo{Hook, summary of alpha-bimodality.}
-\lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the observed stellar abundance patterns in the Milky Way by modeling the star formation history and evolution of the Galaxy.
+\lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the observed stellar abundance patterns in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
 A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars.
-In this view, one feature of the Milky Way disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
+In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
 The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk.
@@
 
-An explanation for the $\alpha$-bimodality has yet to be broadly accepted in the GCE community \todo{(reword)}.
-An $\alpha$-bimodality is not a universal feature in simulated Milky Way-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our own galaxy may provide clues to its unique evolutionary history.
+An explanation for the MW $\alpha$-bimodality has yet to be broadly accepted in the GCE literature.
+An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our Galaxy may provide clues to its unique evolutionary history.
 GCE models that attempt to solve this problem generally fall into two camps.
-Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}.
-Others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
+Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \citep[e.g.,][]{kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
+Others argue for a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
 
@@
 The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
-% By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
+The infall timescale for the low-$\alpha$ disk can be varied to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
 The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.
@@
 
-% \todo{Observational evidence other than $\alpha$-bimodality.} 
-The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model.
-\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a haitus in the star formation history, which is a natural consequence of the two-infall model.
-In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation, which would naturally be explained by the two-infall scenario.
-Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \todo{(citations)}, although these observables can also be matched by other models \todo{(citations)}.
-% \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}.
-\citet{nataf_accurate_2024} also observed multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.
-
 % \todo{Outflows.} 
-Most previous studies of the two-infall model do not include mass-loaded outflows.
+Most previous studies of the two-infall model have not included mass-loaded outflows.
 Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal.
 However, other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \todo{(citations)}.
-Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \todo{(citations)} and dwarf galaxies \todo{(citations)} but not MW-like systems due to current detection limits \todo{(citations)}.
-We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient.
+Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \todo{(citations)} and dwarf galaxies \todo{(citations)} but not MW-like systems, although the predicted column densities are below current detection limits \todo{(citations)}.
+In the absence of outflows, some two-infall studies have implemented radial gas flows or a variable star formation efficiency in order to regulate the radial metallicity gradient \citep{spitoni_effects_2011,palla_chemical_2020}.
+% We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient.
 \todo{Trim down, move some to methods.}
@@
 
+% \todo{Observational evidence other than $\alpha$-bimodality.} 
+The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model.
+\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a haitus in the star formation history, which is a natural consequence of the two-infall model.
+In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation, which would naturally be explained by the two-infall scenario.
+Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \todo{(citations)}, although these observables can also be matched by other models \todo{(citations)}.
+
 % \todo{Summary of secular evolution models which claim alpha-bimodality.} 
 In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
-By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}.
-\citet{kubryk_evolution_2015} produce two parallel sequences in \aFe vs [Fe/H] by making a simple age cut to the results of their multi-zone GCE model, though because they do not present stellar \aFe distributions it is hard to determine whether their distributions are truly bimodal.
+Using a detailed prescription for radial migration, \citet{schonrich_chemical_2009} produced distinct high- and low-$\alpha$ sequences, but they did not overlap in metallicity space as would be found by later surveys \citep[e.g.,][]{bensby_exploring_2014}.
+Others have produced a more MW-like $\alpha$-bimdodality using a combination of radial migration and inside-out galaxy growth \citep[e.g.,][]{kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
+In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history.
+\citet{sharma_chemical_2021} and \citet{chen_chemical_2023} suggest that a simultaneous decline in the star formation rate and the \aFe ratio is needed to separate the sequences in chemical space.
+\citet{chen_recent_2025} additionally argue that the double sequence in the local age--metallicity relation observed by \citet{nissen_high-precision_2020} can also be explained by smooth star formation with inside-out growth.
+On the other hand, some GCE models that incorporate both radial migration and smooth, inside-out star formation have failed to produce an $\alpha$-bimodality \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024}.
+% While the two-infall scenario naturally produces an $\alpha$-bimodality, it is not the only model that can do so.
+While the $\alpha$-bimodality remains a key piece of evidence for the two-infall scenario, it has been reproduced by other models.
+
+% By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}.
+% \citet{kubryk_evolution_2015} produce two parallel sequences in \aFe vs [Fe/H] by making a simple age cut to the results of their multi-zone GCE model, though because they do not present stellar \aFe distributions it is hard to determine whether their distributions are truly bimodal.
 In the model of \citet{sharma_chemical_2021}, a sharp transition in stellar \aFe for $8-12\Gyr$ old stars plus radial migration are the key ingredients for predicting a MW-like bimodality; however, their approach to the chemical evolution is not {\it ab initio}, meaning that instead of integrating the enrichment equations for their adopted star formation history, they simply assume a functional form for the abundance evolution over time \todo{(rewrite)}.
@@
 \citet{chen_chemical_2023} found that the abundance gap is caused by the simultaneous decline in SFR and \aFe.
-\todo{\citet{prantzos_origin_2023}.}
-\citet{chen_recent_2025} argue that the double age--metallicity sequences observed by \citet{nissen_high-precision_2020} can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
+% \citet{prantzos_origin_2023} attribute the formation of their thick disk to a combination of inside-out disk formation and radial migration causing thick disk stars from the inner galaxy to end up in the Solar circle.
+% \citet{chen_recent_2025} argue that the double age--metallicity sequences observed by \citet{nissen_high-precision_2020} can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
 \todo{Trim this WAY down.}
@@
 They propose an ``equilibrium scenario'' in which the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over $\sim\Gyr$ timescales.
-Whether the equilibrium metallicity is driven by outflows, as proposed by \citet{johnson_milky_2024}, or by other factors such as a radial gas flow, the current data suggest that the gas abundance across the Galaxy has evolved very little over most of the thin disk lifetime.
-
-Recently, \citet{dubay_galactic_2024} studied the effect of the SN Ia delay-time distribution in the context of several different star formation histories, including a two-infall model.
+Whether the equilibrium metallicity is regulated by outflows, as proposed by \citet{johnson_milky_2024}, or by other factors such as a radial gas flow, the current data suggest that the gas abundance across the Galaxy has evolved very little over most of the thin disk lifetime.
+
+% Recently, \citet{dubay_galactic_2024} studied the effect of the SN Ia delay-time distribution in the context of several different star formation histories, including a two-infall model.
 While the results did not greatly depend on the choice of SFH, the authors \todo{(we?)} noted that the two-infall model, as implemented, produced a stellar [O/Fe] distribution with three distinct peaks, at variance with the data.
 
+% \todo{Tie it all together, motivate the paper.}
+In light of the findings of \citet{johnson_milky_2024} and a new empirical yield scale from \citet{weinberg_scale_2024}, we evaluate the predictions of the two-infall model against stellar age and abundance data across the MW disk.
 % \todo{Goal and summary of paper.} 
@@
 
-We use an outflow mass-loading factor because it allows us to test a range of yield scales while maintaining our desired endpoint of $Z_{\rm final}\approx Z_\odot$ \todo{(rewrite)}.
-
 Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
@@
 where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall, and $f_{2/1}$ is the ratio of the second infall amplitude to the first.
-We calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
-\begin{equation}
-    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_{\Sigma,0} e^{R(1/R_2 - 1/R_1)}.
-\end{equation}
-We adopt a thick disk scale radius of $R_1=2.0\kpc$, a thin disk scale radius of $R_2=2.5\kpc$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.
-In the Solar neighborhood, this produces a thick-to-thin disk mass ratio of $f_\Sigma(R_\odot)=0.12$.
-By comparison, \citet{mackereth_age-metallicity_2017} finds $f_\Sigma(R_\odot)=0.18\pm0.05$ from APOGEE.
-\citet{fuhrmann_local_2017} derive $f_\Sigma(R_\odot)=0.57$ from a very small volume (25 pc radius).
-\todo{Compare with other two-infall papers, which generally have a higher thick-to-thin ratio.} \citet{spitoni_galactic_2020} explores $f_\Sigma(R_\odot)\approx0.23-0.31$, \citet{palla_chemical_2020} assumes $f_\Sigma(R_\odot)=0.23$, \citet{spitoni_apogee_2021} derives $f_\Sigma(R_\odot)=0.18$ (again from APOGEE), \citet{spitoni_remind_2024} assumes $f_\Sigma(R_\odot)=0.4$.
+We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
+\begin{equation}
+    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_\Sigma(R_\odot) e^{(R-R_\odot)\cdot(1/R_2 - 1/R_1)}.
+\end{equation}
+We adopt a thick disk scale radius of $R_1=2.0\kpc$, a thin disk scale radius of $R_2=2.5\kpc$, and a fiducial value for the local surface density ratio of $f_\Sigma(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016}.
+
+The thick-to-thin disk density ratio is especially important for our GCE models as it controls the quantity of gas accreted during each infall epoch.
+Our fiducial value of $f_\Sigma(R_\odot)=0.12$ is on the low end of literature estimates, which range from $f_\Sigma(R_\odot)\sim0.06-0.6$ \citep[e.g.,][]{gilmore_new_1983,siegel_star_2002,juric_milky_2008,mackereth_age-metallicity_2017,fuhrmann_local_2017}.
+Previous two-infall studies have adopted a similarly broad range of values (e.g., $f_\Sigma(R_\odot)=0.18$ from \citealt{spitoni_apogee_2021}; $f_\Sigma(R_\odot)=0.4$ from \citealt{spitoni_remind_2024}).
+We therefore explore values up to $f_\Sigma(R_\odot)=0.5$ in our multi-zone models in Section \ref{sec:multizone-results}.
+% This value is on the low end of literature estimates; by comparison, \citet{mackereth_age-metallicity_2017} found $f_\Sigma(R_\odot)=0.18\pm0.05$ from APOGEE, and \citet{fuhrmann_local_2017} derived $f_\Sigma(R_\odot)=0.57$ from a very small volume (25 pc radius).
+% \citet{spitoni_galactic_2020} explores $f_\Sigma(R_\odot)\approx0.23-0.31$, \citet{palla_chemical_2020} assumes $f_\Sigma(R_\odot)=0.23$, \citet{spitoni_apogee_2021} derives $f_\Sigma(R_\odot)=0.18$ (again from APOGEE), \citet{spitoni_remind_2024} assumes $f_\Sigma(R_\odot)=0.4$.
 
@@
 In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
-Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1\,{\rm Gyr}$ in the inner disk and $\tau_2=7\,{\rm Gyr}$ at the Solar annulus.
+Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1\Gyr$ in the inner disk and $\tau_2=7\Gyr$ at the Solar annulus.
 This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
-We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\,{\rm Gyr}$ at the Solar annulus and a scale radius $R_{\tau_2}=7\kpc$.
+We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\Gyr$ at the Solar annulus and a scale radius $R_{\tau_2}=7\kpc$.
 This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
@@
 
-Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\,{\rm Gyr}$, but in this case the gas tracks do not produce the characteristic abundance loop.
-For $t_{\rm max}>2\,{\rm Gyr}$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
+Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
+For $t_{\rm max}>2\Gyr$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
 The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}.
-We adopt a fiducial value of $t_{\rm max}=4.2\,{\rm Gyr}$ so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\,{\rm Gyr}$ \citep{pinsonneault_apokasc-3_2025}.
-This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
-\todo{How does this compare to the age of GSE?}
+We adopt a fiducial value of $t_{\rm max}=4.2\Gyr$, i.e.
+a lookback time of $9\Gyr$, which is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
+This ensures that our models are compatible with the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
+
+The Milky Way's last major merger with the dwarf galaxy dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018} has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
+Our fiducial value of $t_{\rm max}=4.2\Gyr$ places the start of the formation of the thin disk close to the GSE merger (within uncertainties), which likely occurred $\sim10\Gyr$ ago \citep[e.g.,][]{helmi_merger_2018,gallart_uncovering_2019,naidu_reconstructing_2021,woody_rapid_2025}.
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics{figures/spitoni_comparison.pdf}
-    \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021} at three different galactocentric radii.
+% \begin{figure*}
+%     \centering
+%     \includegraphics{figures/spitoni_comparison.pdf}
+%     \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021} at three different galactocentric radii.
 All models use the $y/Z_\odot=1$ yield set and corresponding outflow prescription (see Table \ref{tab:yields}).
@@
 APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<10$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.}
-    \label{fig:spitoni-comparison}
-\end{figure*}
-
-\todo{Highlight differences between our models and those of \citet{spitoni_apogee_2021} in Figure \ref{fig:spitoni-comparison}.}
+%     \label{fig:spitoni-comparison}
+% \end{figure*}
+
+% \todo{Highlight differences between our models and those of \citet{spitoni_apogee_2021} in Figure \ref{fig:spitoni-comparison}.}
 
@@
 We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature.
-We have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
-% \todo{I actually think I can ditch the pre-factor, since the molecular timescale already decreases with lookback time.
-In fact, $\tau_{\rm mol}(4.2\,{\rm Gyr}) / \tau_{\rm mol}(13.2\,{\rm Gyr}) \approx 0.5$, which is pretty much the correct ratio to match the two-infall literature.
-The only catch is that $\tau_{\rm mol}$ is a very smooth transition, while with the prefactor it's an abrupt transition.}
+To guard against over-correcting the SFE in the early Galaxy, we have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
 
@@
 
-The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution, which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+We previously noted this feature in \citet{dubay_galactic_2024}.
 Figure \ref{fig:ofe-distribution-yields} compares [O/Fe] distributions from across the Galactic disk produced by models with the \yZ{1} and \yZ{2} yield sets.

### 2025-04-29 src/scripts/ofe_feh_best.py
update legend and colorbar

@@ -41,11 +41,9 @@ def main(style='paper'):
                           ylabel='[O/Fe]', row_label_pos=(0.07, 0.87),
                           width=TWO_COLUMN_WIDTH, 
                           galr_bins=GALR_BINS, absz_bins=ABSZ_BINS)
-    age_bins = np.arange(0, 16, 2)
-    cbar = setup_colorbar(fig, cmap=COLORMAP, vmin=0, vmax=14, 
+    age_bins = np.arange(0, 14.1, 2)
+    cbar = setup_colorbar(fig, cmap=COLORMAP, vmin=0, vmax=14, extend='max',
                           bounds=age_bins, label='Stellar age [Gyr]')
-    # cbar.ax.yaxis.set_major_locator(MultipleLocator(2))
-    # cbar.ax.yaxis.set_minor_locator(MultipleLocator(0.5))
     
     ism_track_color = 'k'
     ism_track_width = 1
@@ -76,19 +74,14 @@ def main(style='paper'):
     # Set y-axis ticks
     axs[0,0].yaxis.set_major_locator(MultipleLocator(0.2))
     axs[0,0].yaxis.set_minor_locator(MultipleLocator(0.05))
-    # Custom legend
-    # custom_lines = [Line2D([0], [0], color=ism_track_color, linestyle=ism_track_style, 
-    #                        linewidth=ism_track_width)]
-    # legend_labels = ['Gas abundance']
     # Custom legend for APOGEE contours
     custom_lines = [
-        (Line2D([0], [0], color=apogee_contour_color, linestyle='-', linewidth=apogee_contour_width),
-        Line2D([0], [0], color=apogee_contour_color, linestyle='--', linewidth=apogee_contour_width))
+        Line2D([0], [0], color=apogee_contour_color, linestyle='-', linewidth=apogee_contour_width),
+        Line2D([0], [0], color=apogee_contour_color, linestyle='--', linewidth=apogee_contour_width)
     ]
-    legend_labels = ['APOGEE 30/80%']
-    axs[2,-1].legend(custom_lines, legend_labels, frameon=False, 
-                     loc='upper center', handlelength=2, handletextpad=0.4,
-                     handler_map={tuple: HandlerTuple(ndivide=None)})
+    legend_labels = ['30%', '80%']
+    axs[0,-1].legend(custom_lines, legend_labels, title='Data contours',
+                     loc='upper right', alignment='right')
     
     # Save
     plt.savefig(paths.figures / 'ofe_feh_best', dpi=300)

### 2025-04-29 src/tex/ms.tex

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/lmr_ages.pdf}
+    \includegraphics[width=\linewidth]{figures/lmr_ages.pdf}
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
-The left panel plots the output of our best two-infall model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\eta_\odot=1.8$.
+The left and center panels plot the output of our best two-infall models, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\eta_\odot=1.8$.
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the abundances and ages according to Table \ref{tab:uncertainties}.
@@
 
-% \subsection{The SN Ia Delay-Time Distribution}
-% \label{sec:dtd-discussion}
-
-% \begin{figure*}
-%     \centering
-%     \includegraphics{figures/delay_time_distribution.pdf}
-%     \caption{The effect of the SN Ia delay-time distribution (DTD) on chemical abundance tracks and stellar distributions.
-{\it Left:} The relative SN Ia rate as a function of time after star formation for each DTD model.
-The points illustrate the median delay times for each DTD.
-{\it Right:} Output of one-zone models which assume different SN Ia DTDs with the {\tt yZ2} yield set.
-The infall parameters are fixed at $\tau_1=1\,{\rm Gyr}$, $\tau_2=10\,{\rm Gyr}$, and $\tau_{\rm on}=3\,{\rm Gyr}$.
-{\bf Key takeaway:} the extent of the low-$\alpha$ sequence can be reduced by a more prompt SN Ia DTD, but the high-$\alpha$ sequence is also shifted to a more metal-poor regime.}
-%     \label{fig:dtd}
-% \end{figure*}
-
-% Figure \ref{fig:dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model.
-The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks.
-The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal.
-Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.
+\subsection{The Empirical Yield Scale}
+
+The \yZ{1} empirical yield scale already has difficulties matching the local age--metallicity relation \citep{johnson_milky_2024}, but the problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
 

### 2025-04-29 src/scripts/scatter_plot_grid.py
fix column labels

@@ -190,5 +190,5 @@ def setup_axes(galr_bins=GALR_BINS[:-1], absz_bins=ABSZ_BINS,
     # Label bins in Rgal
     for i, ax in enumerate(axs[0]):
         galr_lim = (galr_bins[i], galr_bins[i+1])
-        ax.set_title(r'$%s\leq R_{\rm{Gal}} < %s$ kpc' % galr_lim)
+        ax.set_title(r'$%s\leq R_{\rm{gal}} < %s$ kpc' % galr_lim)
     return fig, axs

### 2025-04-29 src/tex/ms.tex

@@
     \includegraphics[width=\textwidth]{figures/ofe_feh_best.pdf}
-    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\eta_\odot=1.8$.
+    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$.
 Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age.
@@
 \end{figure*}
+
+Motivated by the results of the previous sections, we construct a model which attempts to solve all of the issues that have been outlined thus far.
+Our ``best attempt'' model uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:abundance-evolution-yields}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
+Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate, and we believe more realistic, than in previous sections to avoid extreme effects resulting from the combination of these parameters.
+We stress that our focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters through methods such as MCMC.
+
+Figure \ref{fig:ofe-feh-best} presents the stellar [O/Fe]--[Fe/H]--age distributions as a function of $R_{\rm gal}$ and $|z|$ predicted by the best multi-zone model.
 

### 2025-05-12 src/tex/ms.tex
Updates from Overleaf

@@
 Figure \ref{fig:ofe-feh-best} presents the stellar [O/Fe]--[Fe/H]--age distributions as a function of $R_{\rm gal}$ and $|z|$ predicted by the best multi-zone model.
+The model is generally successful at reproducing the observed distribution of stars in the [O/Fe]--[Fe/H] plane, especially in the inner Galaxy and close to the midplane (panels along the left and bottom sides of the figure, respectively).
+However, the predicted high-$\alpha$ sequence is less concentrated than in the data, and its presence is still significant even in the outer Galaxy---likely a consequence of the stronger migration prescription and higher thick-to-thin disk ratio.
+In general, the predicted distributions do not align with the data quite as well at large midplane distances ($1\leq|z|<2\kpc$), but this may partly be due to our prescription for vertical heating (see Section \ref{sec:migration}).
+
+The model makes two notable predictions about the age--abundance distributions.
+First, there is a population of $\sim8-9\Gyr$ old stars at sub-Solar [O/Fe], especially at $|z|\ge0.5\kpc$, formed immediately after the second infall during a period of rapid chemical evolution.
+These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but in this case they occupy a unique portion of the abundance space.
+A longer $\tau_1$ could shift this population to higher [O/Fe] where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
+Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall model predicts a steep age gradient for the most metal-rich stars in a given region.
 
@@
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
-The left and center panels plot the output of our best two-infall models, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\eta_\odot=1.8$.
+The left and center panels plot the output of our best two-infall models, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$.
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the abundances and ages according to Table \ref{tab:uncertainties}.
@@
     {\it Bottom}: Stellar age distributions in the Solar annulus for all stars (black) and LMR stars (gray).
-The left panel plots the results from the two-infall model after forward-modeling age uncertainties, and the right panel plots the \citet{leung_variational_2023} ages for APOGEE stars.
+The left and center panels plot the mass-weighted age distributions predicted by the models after forward-modeling age uncertainties, and the right panel plots the \citet{leung_variational_2023} ages for APOGEE stars.
     {\bf Key takeaway:} The two-infall model predicts a fundamentally different age pattern than what is observed, especially for LMR stars.}
@@
 The two-infall model makes a prediction about the local stellar age distribution that is fundamental to its construction: that the most metal-rich stars in any region of the Galaxy come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
-This prediction can be seen in any of the panels in Figure \ref{fig:ofe-feh-best}.
-In Figure \ref{fig:lmr-ages}, there is a sharp divide in the median age of local metal-rich (LMR; $\mathFeH\gtrsim+0.1$) stars when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
+As noted in the previous Section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.
+We investigate this prediction further here.
+
+The top row of Figure \ref{fig:lmr-ages} presents the median stellar age as a function of [O/Fe] and [Fe/H] for two multi-zone models and APOGEE.
+While the models predict a fairly accurate distribution of stars in abundance space, especially for the low-$\alpha$ population, the stellar age patterns are obviously quite different.
+In both the \yZ{1} and \yZ{2} models, there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
+The \yZ{2} model also predicts that the stars with the lowest [O/Fe] should be $\sim8-9\Gyr$ old, while these are some of the youngest stars in APOGEE.
+The latter issue can be mitigated by adjusting the parameters of the first infall, as discussed in the previous Section, but the former is not solved so easily.
+
+We further highlight the discrepant age patterns in the bottom panels of Figure \ref{fig:lmr-ages}, which compare the overall stellar age distribution against that of the locally metal rich (LMR) stars, defined here as $\mathFeH\ge+0.1$.\footnote{The precise location of the cut matters little, as we observe the same behavior for cuts ranging from $+0.05$ to $+0.2$ dex.} For APOGEE, the distributions are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
+Our two-infall models produce an age distribution for the overall sample that is similar to the data, but for LMR stars, both models predict a distinctly bimodal age distribution.
+There is a large contribution from the young, metal-rich end of the second infall, and a contribution from the old, metal-rich end of the first, but there are few stars in between.
+The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
+
+\todo{Mention some ways to try to resolve this (e.g., stronger radial migration) and that they don't work.}
+\todo{Note that our projected log age error of 0.1 dex is accurate for stars $<8\Gyr$ old, but too large for older stars, so the scatter in the high-$\alpha$ sequence is larger than the data.}
 

### 2025-05-16 src/tex/ms.tex

@@
 \newcommand{\Gyr}{\,{\rm Gyr}}
+\newcommand{\Msun}{\,{\rm M}_\odot}
 
@@
 % Title
-\title{Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs}
+\title{Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs}
 
@@
 These issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
+\todo{Add a sentence about larger implications for merger-dominated SFHs.}
 \end{abstract}
@@
 In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
-The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk.
+The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk.
 The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
@@
 Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts.
-The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
+The relatively low infall rate between the two bursts leads to a lower star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
 The infall timescale for the low-$\alpha$ disk can be varied to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
@@
 
+\todo{Discuss yields, degeneracy with outflows and Rodriguez measurements.
+Emphasize that degeneracy with outflows prohibits direct estimates of yields from GCE.
+We aim to study the effect of the yield assumptions, which necessitates adjusting the outflows as well.}
+
 % \todo{Migration.} 
@@
 \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}.
-Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor requires assumptions about the evolution of the Milky Way's radial metallicity gradient.
+Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor requires also reconstructing the evolution of the Milky Way's radial metallicity gradient.
 While the strength and speed of radial migration in the disk are not precisely measured, it is clear that a single chemical evolution track need not explain the entirety of the local observed abundance distribution.
@@
 The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model.
-\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a haitus in the star formation history, which is a natural consequence of the two-infall model.
+\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a period of reduced star formation, which is a natural consequence of the two-infall model.
 In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation, which would naturally be explained by the two-infall scenario.
@@
 This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and the recovered ages do not plateau at $\sim10\,{\rm Gyr}$ as they do in some other neural network-derived age catalogs \citep[e.g.,][]{mackereth_dynamical_2019}.
-Following the recommendations of \citet{leung_variational_2023}, we use an upper limit on the relative age uncertainty of 40\%.
+Following the recommendations of \citet{leung_variational_2023}, we cut all stars which have a relative age uncertainty greater than 40\%.
 This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
@@
 
-We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, and we detail our outflow prescription in Section \ref{sec:outflows}.
-We describe the gas supply in Section \ref{sec:sfh}, we detail the infall parameter selection in Section \ref{sec:parameter-selection}, and we present our star formation law in Section \ref{sec:sf-law}.
-We briefly summarize the stellar migration prescription in Section \ref{sec:migration}.
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the gas supply in Section \ref{sec:sfh}, the infall parameter selection in Section \ref{sec:parameter-selection}, the star formation law in Section \ref{sec:sf-law}, and the stellar migration prescription in Section \ref{sec:migration}.
 Table \ref{tab:multizone-parameters} summarizes the most relevant variables and their fiducial values in this work.
@@
 
-The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain.
+The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models.
 This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\textemdash in other words, the scale of SN yields is similar to the Solar abundance.
+Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a mass of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass in the Sun.
 However, \citet{johnson_milky_2024} found that GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
@@
 We investigate yield sets at multiple scales of the Solar abundance.
-The CCSN yield of O is directly set by the Solar scale: $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$.
+The CCSN yield of O is directly set by the Solar scale, $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$, because all O is assumed to form in CCSNe.
 For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathaFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathaFe}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
@@
 
-The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is calculated so that the combined Fe yield $y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC}=y/Z_\odot$.
-We further increase $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the \yZ{1} and \yZ{2} yield sets, respectively, to ensure that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
+The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is set so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
+For \yZ{3}, the combined Fe yield of CCSNe and SNe Ia matches the Solar yield scale: $(y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC})/Z_{\rm Fe,\odot}=y/Z_\odot$; for \yZ{1} and \yZ{2}, $y_{\rm Fe}^{\rm Ia}$ is increased from the given scale by a factor of 30\% and 10\%, respectively \todo{(rephrase)}.
 The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate
@@
 
-The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset (which could be corrected by raising the SN Ia yield).
+The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset (which could be corrected by increasing $y_{\rm Fe}^{\rm Ia}$ or adjusting the zero-point in the stellar abundances).
 The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields.
@@
 Mass-loaded outflows are a useful tool for scaling the endpoint of GCE models.
-\citet{weinberg_equilibrium_2017} showed that in the case of exponentially declining star formation, the O abundance approaches an equilibrium value at
+\citet{weinberg_equilibrium_2017} showed that in the case of exponentially declining star formation, the O abundance approaches an equilibrium at
 \begin{equation}
@@
 where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the star formation timescale, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
-Equation \ref{eq:equilibrium} can be inverted to calculate the value of $\eta$ required to reach a desired $Z_{\rm O,eq}$ with a given yield, but it is inaccurate in the limit of zero accretion.
-We adopt values of $\eta_\odot=\eta(R=R_\odot)$ for each of our yield sets presented in Table \ref{tab:yields}.
+% Equation \ref{eq:equilibrium} can be inverted to calculate the value of $\eta$ required to reach a desired $Z_{\rm O,eq}$ with a given yield, but it is inaccurate in the limit of zero accretion. 
+Motivated by Equation \ref{eq:equilibrium}, we adopt an outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
 Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than would be suggested by Equation \ref{eq:equilibrium} in order to reach Solar metallicity at the end of the model.
@@
 
-We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation effieciency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time.
+We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time.
 The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities according to our star formation law, which is described in Section \ref{sec:sf-law}, assuming zero initial gas mass in all zones.
@@
 % the second infall timescale $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions. 
-the second infall timescale $\tau_2$ controls the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
-A shorter $\tau_2$ produces a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces both a narrower low-$\alpha$ sequence and a narrower MDF.
-We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is very close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns.
+the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
+A shorter $\tau_2$ produces a bigger loop and therefore a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
+We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns.
 Between $\tau_2=3-30\,{\rm Gyr}$, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
-We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times.
+We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the size of the loop and width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times (see further discussion in Section \ref{sec:abundance-distributions}).
 This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}.
@@
 
-We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
+We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
 The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus.
@@
     \includegraphics{figures/abundance_evolution_params.pdf}
-    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}.
+    \caption{Stellar age--abundance relations in the Solar annulus produced by select multi-zone models with \yZ{1}.
 The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
@@
 
-The observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ is thought to be due to radial migration, as those stars are more likely to have migrated from the dense inner metal-rich regions of the Galaxy during that time.
+The observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the dense inner metal-rich regions of the Galaxy \citep{feuillet_age-resolved_2018}.
 Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
+    \includegraphics[width=\linewidth]{figures/mdf_evolution.pdf}
     \caption{Evolution of the MDF across the Galactic disk.
-Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age.
+Each panel presents normalized stellar [Fe/H] distributions as a function of stellar age within a {2 kpc}-wide annulus.
 Rows (a) and (b) present the distributions from multi-zone GCE models with different yield scales.
@@
 This over-density occurs because the overall rate of chemical evolution slows down $\sim2\,{\rm Gyr}$ after the second infall, and at the same time the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
-This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow}.
+This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow} or the models with longer $\tau_2$ in Figure \ref{fig:twoinfall-parameters}.
 

### 2025-05-16 src/scripts/lmr_ages.py
layout updates

@@ -32,14 +32,24 @@ GRIDSIZE = 30
 def main(style='paper', cmap='Spectral_r'):
     # Set up plot
     plt.style.use(paths.styles / f'{style}.mplstyle')
-    fig, axs = plt.subplots(2, 3, 
-                            figsize=(TWO_COLUMN_WIDTH, 0.67 * TWO_COLUMN_WIDTH), 
-                            sharex='row', sharey='row', 
-                            gridspec_kw={'wspace': 0.05, 'hspace': 0.22})
+    fig, axs = plt.subplots(
+        2, 3, 
+        figsize=(TWO_COLUMN_WIDTH, 0.6 * TWO_COLUMN_WIDTH), 
+        sharex='row', sharey='row', 
+        gridspec_kw={
+            'wspace': 0.05, 
+            'hspace': 0.25, 
+            'height_ratios': [3, 2],
+            'left': 0.,
+            'bottom': 0.
+        }
+    )
     cbar_age_bins = np.arange(0, 12.1, 1)
     hist_age_bins = np.arange(0, 15.1, 1)
-    cbar = setup_colorbar(fig, cmap=cmap, bounds=cbar_age_bins, extend='max',
-                          label='Median stellar age [Gyr]', bottom=0.53, labelpad=2)
+    cbar = setup_colorbar(
+        fig, cmap=cmap, bounds=cbar_age_bins, extend='max',
+        label='Median stellar age [Gyr]', bottom=0.41, labelpad=2
+    )
     
     # Load data and model outputs
     full_sample = APOGEESample.load()
@@ -128,14 +138,14 @@ def main(style='paper', cmap='Spectral_r'):
     axs[0,0].yaxis.set_minor_locator(MultipleLocator(0.05))
     axs[0,0].set_xlim(PLOT_EXTENT[:2])
     axs[0,0].set_ylim(PLOT_EXTENT[2:])
-    axs[1,2].legend(handlelength=0.7, handletextpad=0.5)
+    axs[1,2].legend(handlelength=0.8, handletextpad=0.5)
     axs[1,0].set_xlabel('Age [Gyr]')
     axs[1,1].set_xlabel('Age [Gyr]')
     axs[1,2].set_xlabel('Age [Gyr]')
     axs[1,0].xaxis.set_major_locator(MultipleLocator(5))
     axs[1,0].xaxis.set_minor_locator(MultipleLocator(1))
[…]

### 2025-05-16 src/tex/ms.tex

@@
 
+\todo{Discuss why we divided Figures \ref{fig:ofe-distribution-yields} and \ref{fig:ofe-distribution-parameters} into $|z|$ bins: (1) pattern changes as a function of midplane distance, and (2) we don't have to worry so much about correcting the APOGEE data to rebalance between the thin and thick disk fields.}
+
 \begin{figure*}
@@
     \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e).
-The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
+The layout is similar to Figure \ref{fig:ofe-distribution-yields}.
 Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
@@
 Next, in model (c) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
-We choose this value because it is the maximum which can plausibly still reproduce the disk abundances; any higher and the infalling gas would be more metal-rich than the most metal-poor thin disk stars.
+We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars.
 This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
@@
 Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age.
-A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm NN}$) and abundance uncertainties in Table \ref{tab:uncertainties}.
+A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm [C/N]}$) and abundance uncertainties in Table \ref{tab:uncertainties}.
 The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region.

### 2025-05-16 src/tex/ms.tex
Manuscript updates

@@
 
-The two-infall model makes a prediction about the local stellar age distribution that is fundamental to its construction: that the most metal-rich stars in any region of the Galaxy come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
+The two-infall model makes a prediction about the local stellar age distribution that is fundamental to its construction: that the most metal-rich stars born in-situ in any region of the Galaxy come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
 As noted in the previous Section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.

### 2025-05-22 src/scripts/ofe_feh_density.py
move v2 to original file name

@@ -9,9 +9,12 @@ import vice
 
 from multizone_stars import MultizoneStars
 from apogee_sample import APOGEESample
+from track_and_mdf import setup_axes, plot_mdf_curve
+import distribution_functions as dfs
 from _globals import ONE_COLUMN_WIDTH, ZONE_WIDTH
 import paths
 from colormaps import paultol
+from utils import get_bin_centers
 
 OUTPUT_NAMES = [
     'yZ1/fiducial/diskmodel',
@@ -22,81 +25,121 @@ LABELS = [
     r'(b) $y/Z_\odot=2$',
     '(c) APOGEE'
 ]
-FEH_LIM = (-1.2, 0.6)
+FEH_LIM = (-1.1, 0.6)
 OFE_LIM = (-0.15, 0.55)
 GALR_LIM = (7, 9)
-ABSZ_LIM = (0.5, 1)
-GRIDSIZE = 50
+ABSZ_LIM = (0, 2)
+GRIDSIZE = 30
 
 
-def main(style='paper', cmap='Blues'):
+def main(style='paper'):
     # Setup figure
     plt.style.use(paths.styles / f'{style}.mplstyle')
-    fig, axs = plt.subplots(len(OUTPUT_NAMES)+1, 1,
-                            figsize=(0.67 * ONE_COLUMN_WIDTH, 2 * ONE_COLUMN_WIDTH),
-                            sharex=True, sharey=True)
-    plt.subplots_adjust(right=0.98, left=0.06, bottom=0.08, top=0.95,
-                        wspace=0., hspace=0.)
+    fig = plt.figure(figsize=(ONE_COLUMN_WIDTH, 2.*ONE_COLUMN_WIDTH))
+    gs = fig.add_gridspec(22, 7, wspace=0., hspace=0.)
+    subfigs = [
+        fig.add_subfigure(gs[i:i+w,:]) for i, w in zip((0, 7, 14), (7, 7, 8))
+    ]
+    inset_axes_bounds = [1.28, 0., 0.07, 1.]
     
     apogee_sample = APOGEESample.load()
-    for i, ax in enumerate(axs[:-1]):
+    local_sample = apogee_sample.region(galr_lim=GALR_LIM, absz_lim=ABSZ_LIM)
+    ofe_kwargs = {'bins': 100, 'range': OFE_LIM, 'smoothing': 0.05}
[…]

### 2025-05-22 src/scripts/ofe_feh_density_v2.py

@@ -1,147 +1,0 @@
-"""
-This script plots 2D density histograms of multi-zone models.
-"""
-
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import MultipleLocator
-import vice
-
-from multizone_stars import MultizoneStars
-from apogee_sample import APOGEESample
-from track_and_mdf import setup_axes, plot_mdf_curve
-import distribution_functions as dfs
-from _globals import ONE_COLUMN_WIDTH, ZONE_WIDTH
-import paths
-from colormaps import paultol
-from utils import get_bin_centers
-
-OUTPUT_NAMES = [
-    'yZ1/fiducial/diskmodel',
-    'yZ2/fiducial/diskmodel'
-]
-LABELS = [
-    r'(a) $y/Z_\odot=1$',
-    r'(b) $y/Z_\odot=2$',
-    '(c) APOGEE'
-]
-FEH_LIM = (-1.1, 0.6)
-OFE_LIM = (-0.15, 0.55)
-GALR_LIM = (7, 9)
-ABSZ_LIM = (0, 2)
-GRIDSIZE = 30
-
-
-def main(style='paper'):
-    # Setup figure
-    plt.style.use(paths.styles / f'{style}.mplstyle')
-    fig = plt.figure(figsize=(ONE_COLUMN_WIDTH, 2.*ONE_COLUMN_WIDTH))
-    gs = fig.add_gridspec(22, 7, wspace=0., hspace=0.)
-    subfigs = [
-        fig.add_subfigure(gs[i:i+w,:]) for i, w in zip((0, 7, 14), (7, 7, 8))
-    ]
-    inset_axes_bounds = [1.28, 0., 0.07, 1.]
-    
-    apogee_sample = APOGEESample.load()
-    local_sample = apogee_sample.region(galr_lim=GALR_LIM, absz_lim=ABSZ_LIM)
-    ofe_kwargs = {'bins': 100, 'range': OFE_LIM, 'smoothing': 0.05}
-    feh_kwargs = {'bins': 100, 'range': FEH_LIM, 'smoothing': 0.2}
-    cmap_name = 'Blues'
-    for i, subfig in enumerate(subfigs[:-1]):
-        axs = setup_axes(
-            subfig, xlabel='[Fe/H]', xlim=FEH_LIM, ylim=OFE_LIM, 
-            show_xlabel=False,
-        )
-        axs[0].text(
-            0.5, 0.95, LABELS[i], 
-            ha='center', va='top', 
[…]

### 2025-05-22 src/tex/ms.tex
Updates from Overleaf

@@
 \begin{abstract}
-    Stellar populations in the Milky Way exhibit a clear separation into two chemically distinct populations that are separated by their [$\alpha$/Fe] ratios.
+    Stars in the Milky Way disk exhibit a clear separation into two chemically distinct populations based on [$\alpha$/Fe] ratios.
 This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to the Milky Way's unique evolutionary history.
-A popular explanation for this observation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
+A popular explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
     However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow.
     Thanks to advances in stellar age measurements in recent years, we can now also compare this popular model to more direct measurements of the Galaxy's evolutionary timescales across the disk from large stellar catalogs.
-We run multi-zone galactic chemical evolution (GCE) models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamic simulation.
+    We run multi-zone galactic chemical evolution (GCE) models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
     We compare our model results to abundance patterns across the disk from APOGEE DR17,
@@
     supplemented with stellar age estimates through multiple methods. 
-Although the two-infall scenario offers a natural explanation for the [$\alpha$/Fe] bimodality, it struggles to explain several features of the age--abundances structure in the disk.
+    Although the two-infall scenario offers a natural explanation for the [$\alpha$/Fe] bimodality, it struggles to explain several features of the age--abundance structure in the disk.
 The two-infall scenario generically predicts a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant with age across much of the Galactic disk.
@@
 These issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
-\todo{Add a sentence about larger implications for merger-dominated SFHs.}
+Additionally, the two-infall scenario predicts that local metal-rich stars should have a bimodal distribution of ages, whereas APOGEE data show most of these stars have intermediate ages.
+Restrictions upon the two-infall parameter space also limit the application of other merger-dominated star formation histories to the Milky Way.
 \end{abstract}
-
-% \section{Outline}
-% \input{outline.tex}
 
@@
 \lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the observed stellar abundance patterns in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
-A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars.
+A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars \citep[e.g.,][]{tinsley_stellar_1979,matteucci_relative_1986}.
 In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
@@
 An explanation for the MW $\alpha$-bimodality has yet to be broadly accepted in the GCE literature.
-An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our Galaxy may provide clues to its unique evolutionary history.
+An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, \todo{also mention external galaxies}, so its presence and characteristics in our Galaxy may provide clues to its unique evolutionary history.
 GCE models that attempt to solve this problem generally fall into two camps.
@@
     \includegraphics[width=\linewidth]{figures/abundance_evolution_yields.pdf}
-    \caption{Stellar age--abundance relations produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
+    \caption{Stellar age--abundance relations produced by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
@@
     \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_yields.pdf}
-    \caption{Normalized stellar [O/Fe] distributions produced by multi-zone models which assume different yield sets and outflow mass-loading factors.
+    \caption{Normalized stellar [O/Fe] distributions produced by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
 Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row.
@@
 
+Motivated by evidence of a recent period of enhanced star formation \citep[e.g.,][]{ruiz-lara_recurrent_2020}, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} extended the two-infall model with a recent third accretion episode.
+\citet{spitoni_beyond_2023} argued that the gas dilution resulting from the third infall could explain the population of young, metal-poor stars discovered in {\it Gaia} DR3 \citep{recio-blanco_gaia_2023}, in contrast to the two-infall model of \citet{spitoni_apogee_2021} which predicted a present-day gas metallicity of ${\rm [M/H]}\approx+0.3$ in the Solar neighborhood.
+\citet{palla_mapping_2024} were similarly motivated by the finding that open clusters with ages $<1\Gyr$ have similar metallicity to those with ages $>3\Gyr$ \todo{and younger than OCs in between}, while the classical two-infall model predicted a steady increase in metallicity over time.
+However, \citet{palla_mapping_2024} invoke a less massive infall, producing a milder dilution event, than \citet{spitoni_beyond_2023}.
+
+Some combination of metal-rich accretion and radial gas flows might reduce the amount of dilution predicted by a recent accretion episode.
+
 \subsection{Radial Gas Flows}
@@
 A low yield set (\yZ{1}) coupled with lower outflows, or pre-enrichment of the infalling gas, can bring the stellar [O/Fe] distributions more in line with the data.
+The parameter space is nonetheless restricted by the need to suppress this feature.
     \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations.

### 2025-05-22 src/tex/ms.tex
Updates from Overleaf

@@
     \includegraphics[width=\linewidth]{figures/mdf_evolution.pdf}
-    \caption{Evolution of the MDF across the Galactic disk.
-Each panel presents normalized stellar [Fe/H] distributions as a function of stellar age within a {2 kpc}-wide annulus.
-Rows (a) and (b) present the distributions from multi-zone GCE models with different yield scales.
-For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$.
-A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+    \caption{Evolution of the MDF over time across the Galactic disk.
+In each panel, normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus are color-coded by the stellar age range.
+The gray curve represents the total MDF in each region.
+Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters at different yield and outflow scales.
+    % For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$. 
+    A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}.
 Row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
@@
 Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
-Distributions in all panels are restricted to $0\leq|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
-{\bf Key takeaway:} The APOGEE data show remarkably little variation in the mode at all radii over the past $\sim6-8$ Gyr, while both GCE models produce a steady evolution toward higher [Fe/H] with time.}
+The distributions in all panels are restricted to $0\leq|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
+{\bf Key takeaway:} The APOGEE distributions show remarkably little variation in position over the past $\sim6-8$ Gyr at all radii, whereas both GCE models predict a steady evolution toward higher [Fe/H] with time.}
     \label{fig:mdf-evolution}
@@
     \centering
-    \includegraphics{figures/ofe_feh_density.pdf}
-    \caption{The density of stars in the [O/Fe]--[Fe/H] plane from multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
-The curves in panels (a) and (b) plot the ISM abundance of the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
-Stars are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $0.5\leq|z|<1\kpc$ to highlight the $\alpha$-bimodality in the Solar neighborhood.
-{\bf Key takeaway:} the two-infall model generically predicts a stellar overdensity at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.}
+    \includegraphics[width=\linewidth]{figures/ofe_feh_density.pdf}
+    \caption{The density of stars in the [O/Fe]--[Fe/H] plane predicted by multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
+The curves in panels (a) and (b) plot the ISM abundance at the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
+The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the predicted abundances according to Table \ref{tab:uncertainties}.
+Stars in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $0\leq|z|<2\kpc$.
+{\bf Key takeaway:} the two-infall model generically predicts a stellar over-density at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.}
     \label{fig:ofe-feh-density}
@@
 
-\section{Conclusions}
+\section{Summary \& Conclusions}
 \label{sec:conclusions}
+
+We have
 

### 2025-05-23 src/tex/ms.tex
Manuscript updates

@@
 % \author[0000-0001-7775-7261]{David H. Weinberg}
-\author{coauthors}
+% \author{coauthors}
 
@@
 \begin{abstract}
-    Stars in the Milky Way disk exhibit a clear separation into two chemically distinct populations based on [$\alpha$/Fe] ratios.
+    Stars in the Milky Way disk exhibit a clear separation into two chemically distinct populations by their [$\alpha$/Fe] ratios.
 This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to the Milky Way's unique evolutionary history.
@@
 Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal.
-However, other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \todo{(citations)}.
-Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \todo{(citations)} and dwarf galaxies \todo{(citations)} but not MW-like systems, although the predicted column densities are below current detection limits \todo{(citations)}.
+However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}, and other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
+Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} and dwarf galaxies \todo{(citations)} but not MW-like systems, although the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
+Even if the MW is not currently ejecting a substantial outflow, it is not unreasonable to suppose that it may have during a more active phase in its evolutionary history.
+
 In the absence of outflows, some two-infall studies have implemented radial gas flows or a variable star formation efficiency in order to regulate the radial metallicity gradient \citep{spitoni_effects_2011,palla_chemical_2020}.
@@
         $\log_{10}(\tau_{\rm NN}/{\rm Gyr})$    & 0.10   & $0.16$ \\
-        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & \todo{N/A} \\
+        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & 1.3 \\
         \hline
@@
 Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width \todo{(do I need this table?)}.
+
+\subsection{Stellar Age Estimates}
 
@@
 
-Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
-\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
-This method has the benefit of providing age estimates for luminous giants, which increases the sample size at larger distances from the Sun.
+% Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
+% \todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
+% This method has the benefit of providing age estimates for luminous giants, which increases the sample size at larger distances from the Sun.
 However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr.
 We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
-\todo{Note about metallicity cutoff for luminous giants. Cite: \citet{cao_modeling_2025}}
+% \todo{Note about metallicity cutoff for luminous giants. Cite: \citet{cao_modeling_2025}}
+
+Our second age catalog utilizes the [C/N]--age relation calibrated by \todo{Roberts et al.\ (hopefully submitted)} for red giant branch (RGB) and red clump stars.
+The relationship relies on the mass-dependent level of mixing during the first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
+This method has the benefit of providing age estimates for luminous giants, which increases the sample size at larger distances from the Sun.
+However, limitations from the efficiency of FDU mixing and the RGB age--mass relationship mean the ages are not trustworthy outside the range $1\sim10\Gyr$.
+Additional mixing effects in low-metallicity stars %later in their RGB evolution
+also prevent the relation from being applied to luminous giant ($\log(g)<2.5$) and red clump stars with $\mathFeH<-0.4$.
+The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \todo{Roberts et al.\ (hopefully submitted)}, the propagated errors underestimate the true age dispersion and so we enhance these uncertainties by 40\% to account for this \todo{(rewrite)}.
+With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
 
@@
 
+\subsection{Comparison with Previous Literature}
+
 \subsection{The Empirical Yield Scale}
@@
 
-We have
+We have compared the predictions of the two-infall scenario against abundance data from APOGEE DR17 supplemented with age estimates using two different methods.
+We ran multi-zone GCE models at two different yield scales with prescriptions for radially-dependent outflows and stellar migration.
+While the two-infall scenario can explain the local stellar abundance distribution, in particular the $\alpha$-bimodality, it faces challenges in matching the age--abundance structure of the full disk.
+We explored multiple parameter modifications to bring the model predictions closer to the data, including the yield scale, radial migration strength, metallicity of the accreted gas, thick-to-thin disk mass ratio, and the SN Ia DTD.
+Our conclusions are as follows:
 
@@
 \end{itemize}
+
+The apparent age-independence of stellar abundances in the disk places considerable restrictions upon the two-infall parameter space because it predicts a substantial dilution event at the start of the thin disk epoch.
+If the equilibrium scenario of \citet{johnson_milky_2024} is correct, then it restricts the two-infall scenario more than other GCE models.
+
+\todo{Implications for merger-driven SFHs.}
 

### 2025-06-27 src/tex/ms.tex

@@
 \documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
+% \documentclass[linenumbers]{aastex631}
 
@@
 \renewcommand{\LettrineFontHook}{\usefont{U}{Zallman}{xl}{n}}
-\setcounter{DefaultLines}{3}%
+\setcounter{DefaultLines}{3} % number of lines dropped capital should take up
 
@@
 \newcommand{\Gyr}{\,{\rm Gyr}}
+\newcommand{\dex}{\,{\rm dex}}
 \newcommand{\Msun}{\,{\rm M}_\odot}
+\newcommand{\kms}{\,{\rm km}\,{\rm s}^{-1}}
+\newcommand{\onecolumn}{0.47\textwidth}
 
@@
 \begin{abstract}
-    Stars in the Milky Way disk exhibit a clear separation into two chemically distinct populations by their [$\alpha$/Fe] ratios.
-This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to the Milky Way's unique evolutionary history.
+    Stars in the Milky Way disk exhibit a clear separation into two chemically distinct populations based on their [$\alpha$/Fe] ratios.
+This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to a unique evolutionary history.
 A popular explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
-    However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow.
-    Thanks to advances in stellar age measurements in recent years, we can now also compare this popular model to more direct measurements of the Galaxy's evolutionary timescales across the disk from large stellar catalogs.
-    We run multi-zone galactic chemical evolution (GCE) models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
-    We compare our model results to abundance patterns across the disk from APOGEE DR17,
-    % and early data from the SDSS-V Milky Way Mapper program,
-    supplemented with stellar age estimates through multiple methods. 
-    Although the two-infall scenario offers a natural explanation for the [$\alpha$/Fe] bimodality, it struggles to explain several features of the age--abundance structure in the disk.
-The two-infall scenario generically predicts a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant with age across much of the Galactic disk.
+    % However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow.
+    Thanks to recent advances in stellar age measurements, we can now compare this popular model to more direct measurements of the Galaxy's evolutionary timescales across the disk. 
+    % We run multi-zone galactic chemical evolution models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
+We compare our model results to abundance patterns across the disk from APOGEE DR17, supplemented with stellar age estimates through multiple methods.
+    We run multi-zone galactic chemical evolution models with a two-infall-driven star formation history and compare the results against abundance patterns across the disk from APOGEE DR17, supplemented with stellar ages estimated through multiple methods.
+    Although the two-infall scenario offers a natural explanation for the $\alpha$-bimodality, it struggles to explain several features of the age--abundance structure in the disk.
+First, our models generically predict a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant across much of the lifetime of the disk.
 This apparent age-independence places considerable restrictions upon the two-infall parameter space.
-These issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
-    Additionally, the two-infall scenario predicts that local metal-rich stars should have a bimodal distribution of ages, whereas APOGEE data show most of these stars have intermediate ages.
-Restrictions upon the two-infall parameter space also limit the application of other merger-dominated star formation histories to the Milky Way.
+Second, most local metal-rich stars in APOGEE have intermediate ages, yet our models predict these stars should either be very old or very young.
+Some of these issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
+    % Restrictions upon the two-infall parameter space also limit the application of other merger-dominated star formation histories to the Milky Way.
+    These restrictions also place limits on the role of merger events in shaping the chemical evolution of the thin disk in general.
 \end{abstract}
@@
 % \todo{Hook, summary of alpha-bimodality.}
-\lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the observed stellar abundance patterns in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
+\lettrine{G}{alactic chemical evolution} (GCE) aims to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
 A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars \citep[e.g.,][]{tinsley_stellar_1979,matteucci_relative_1986}.
 In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
-The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk.
+The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the kinematic thin disk.
 The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
@@
 An explanation for the MW $\alpha$-bimodality has yet to be broadly accepted in the GCE literature.
-An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, \todo{also mention external galaxies}, so its presence and characteristics in our Galaxy may provide clues to its unique evolutionary history.
+An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and tentatively does not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}).
+Its presence and characteristics in our Galaxy could potentially have arisen to a unique evolutionary history.
 GCE models that attempt to solve this problem generally fall into two camps.
-Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \citep[e.g.,][]{kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
-Others argue for a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.
+Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
+Others argue for a bursty star formation history driven by multiple accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023}.
+% Studies of simulations have suggested that the $\alpha$-bimodality could be driven by clumpy star formation at high redshift \citep{clarke_imprint_2019}, a major gas-rich merger \citep{buck_origin_2020}, or re-accretion of metal-rich outflows \citep{khoperskov_bimodality_2021}.
 
 % Summary of two-infall literature
-The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks.
-Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts.
-The relatively low infall rate between the two bursts leads to a lower star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
+The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks.
+Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive bursts that each decay with time.
+The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
 The infall timescale for the low-$\alpha$ disk can be varied to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
@@
 Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}.
-Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024} in a two-infall context.
-Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.
+Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
+\citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
+Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey (SDSS) \todo{(cite)}.
 
@@
 Most previous studies of the two-infall model have not included mass-loaded outflows.
-Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal.
-However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}, and other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
-Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} and dwarf galaxies \todo{(citations)} but not MW-like systems, although the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
-Even if the MW is not currently ejecting a substantial outflow, it is not unreasonable to suppose that it may have during a more active phase in its evolutionary history.
-
-In the absence of outflows, some two-infall studies have implemented radial gas flows or a variable star formation efficiency in order to regulate the radial metallicity gradient \citep{spitoni_effects_2011,palla_chemical_2020}.
-% We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient.
-\todo{Trim down, move some to methods.}
-
-\todo{Discuss yields, degeneracy with outflows and Rodriguez measurements.
+This decision is based on hydrodynamic simulations of Galactic fountains ejected by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
+However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}; other simulations of MW-like galaxies with different prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
+Empirically, mass-loading has been observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
+Even if the MW is not currently ejecting a substantial outflow, it may have at some point in the past.
+
+% \todo{Discuss yields, degeneracy with outflows and Rodriguez measurements.
 Emphasize that degeneracy with outflows prohibits direct estimates of yields from GCE.
 We aim to study the effect of the yield assumptions, which necessitates adjusting the outflows as well.}
+By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}.
+\citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
+This degeneracy prohibits direct estimates of the yield scale from GCE models, unless the effect of outflows is assumed to be insignificant \citep[e.g.,][]{francois_evolution_2004}.
+% Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of core-collapse supernovae (CCSNe) by \citet{rodriguez_iron_2023} to infer a supernova yield scale that is a factor of $\sim2$ lower than assumed by some previous GCE studies.
+The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of the yield scale on two-infall scenario predictions.
+Varying the yield scale while maintaining an evolutionary end point that is consistent with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
 
 % \todo{Migration.} 
-The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
+Previous two-infall models have reproduced the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
 However, the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
 \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}.
-Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor requires also reconstructing the evolution of the Milky Way's radial metallicity gradient.
-While the strength and speed of radial migration in the disk are not precisely measured, it is clear that a single chemical evolution track need not explain the entirety of the local observed abundance distribution.
+Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor depends on a model of the evolution of the radial metallicity profile in the MW.
+While the strength and speed of radial migration in the disk are not precisely measured, a single chemical evolution track need not explain the entire width of the local abundance distribution.
 
 % \todo{Observational evidence other than $\alpha$-bimodality.} 
-The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model.
-\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a period of reduced star formation, which is a natural consequence of the two-infall model.
-In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation, which would naturally be explained by the two-infall scenario.
-Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \todo{(citations)}, although these observables can also be matched by other models \todo{(citations)}.
+The observed chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary motivation for the two-infall scenario.
+\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a period of reduced star formation, which is a natural consequence of the delay between the two accretion epochs.
+In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario.
+However, \citet{plotnikova_chemical_2024} found no evidence for multiple sequences in the local AMR, and argued that such patterns can arise due to selection effects.
+Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000,spitoni_remind_2024}, although most GCE models in the literature benchmark against these observables \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021}.
 
@@
 In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history.
-\citet{sharma_chemical_2021} and \citet{chen_chemical_2023} suggest that a simultaneous decline in the star formation rate and the \aFe ratio is needed to separate the sequences in chemical space.
-\citet{chen_recent_2025} additionally argue that the double sequence in the local age--metallicity relation observed by \citet{nissen_high-precision_2020} can also be explained by smooth star formation with inside-out growth.
-On the other hand, some GCE models that incorporate both radial migration and smooth, inside-out star formation have failed to produce an $\alpha$-bimodality \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024}.
-% While the two-infall scenario naturally produces an $\alpha$-bimodality, it is not the only model that can do so.
-While the $\alpha$-bimodality remains a key piece of evidence for the two-infall scenario, it has been reproduced by other models.
+\citet{sharma_chemical_2021} and \citet{chen_chemical_2023} showed that a simultaneous decline in the star formation rate and the \aFe ratio is needed to separate the sequences in chemical space under this scenario.
+\citet{chen_recent_2025} additionally argued that the double sequence in the local age--metallicity relation observed by \citet{nissen_high-precision_2020} can also be explained by a smooth star formation history and inside-out disk growth.
+However, other GCE models that incorporate both radial migration and smooth, inside-out star formation have failed to predict an $\alpha$-bimodality \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024}.
+While the $\alpha$-bimodality remains a key piece of evidence for the two-infall scenario, it is not the only proposed explanation.
 
@@
 % \todo{Introduce equilibrium model.} 
-As stellar age estimation techniques have improved over recent years, large catalogs have become available with ages for hundreds of thousands or even millions of stars from a wide swath of the Galaxy.
-In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, \citet{johnson_milky_2024} examined the age--metallicity relation at different radii from the astroNN catalog \citep{mackereth_dynamical_2019} and found that the mode of the metallicity distribution at a given radius is nearly independent from age over the past $\sim9\Gyr$.
-They propose an ``equilibrium scenario'' in which the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over $\sim\Gyr$ timescales.
-Whether the equilibrium metallicity is regulated by outflows, as proposed by \citet{johnson_milky_2024}, or by other factors such as a radial gas flow, the current data suggest that the gas abundance across the Galaxy has evolved very little over most of the thin disk lifetime.
-
-% Recently, \citet{dubay_galactic_2024} studied the effect of the SN Ia delay-time distribution in the context of several different star formation histories, including a two-infall model.
-While the results did not greatly depend on the choice of SFH, the authors \todo{(we?)} noted that the two-infall model, as implemented, produced a stellar [O/Fe] distribution with three distinct peaks, at variance with the data.
-
-% \todo{Tie it all together, motivate the paper.}
-In light of the findings of \citet{johnson_milky_2024} and a new empirical yield scale from \citet{weinberg_scale_2024}, we evaluate the predictions of the two-infall model against stellar age and abundance data across the MW disk.
+As stellar age estimation techniques have improved over recent years, large catalogs have become available with measurements for large samples of stars from a wide swath of the Galaxy.
+In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time,
+% \citet{johnson_milky_2024} examined the age--metallicity relation at different radii from the astroNN catalog \citep{mackereth_dynamical_2019} and found that the mode of the metallicity distribution at a given radius is nearly independent from age over the past $\sim9\Gyr$.
+They propose an
+these catalogs have indicated that stellar metallicities are remarkably consistent with age across most of the thin disk epoch \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
+\citet{johnson_milky_2024} demonstrated that these results are readily explained by a scenario in which the Galaxy reaches a state of chemical equilibrium.
+In this so-called ``equilibrium scenario,'' the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over Gyr timescales.
+Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the thin disk epoch.
+
+% In light of the findings of \citet{johnson_milky_2024} and a new empirical yield scale from \citet{weinberg_scale_2024}, we evaluate the predictions of the two-infall model against stellar age and abundance data across the MW disk.
+Relative to even a few years ago, the availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
+Our study draws on the steadiness of the Milky Way stellar metallicity gradient found by \citet{johnson_milky_2024} and empirical constraints on the yield scale from \citet{weinberg_scale_2024}.
 % \todo{Goal and summary of paper.} 
 We run multi-zone GCE models with a two-infall accretion history, radially-dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
-We investigate the impact of the scale of SN yields and outflows, the strength of radial migration, the enrichment of the circumgalactic medium, and the local disk mass surface density ratio on the GCE model predictions.
+We investigate the impact of the scale of SN yields and outflows, the strength of radial migration, the composition of the circumgalactic medium, and the local disk mass surface density ratio on GCE model predictions.
 We compare our results to abundance distributions across the disk from APOGEE DR17, and to age--abundance relations from multiple age catalogs.
@@
 We compare our multi-zone model predictions to the data in Section \ref{sec:multizone-results}.
-We discuss in Section \ref{sec:discussion} and conclude in Section \ref{sec:conclusions}.
+We discuss our results in Section \ref{sec:discussion} and summarize our conclusions in Section \ref{sec:conclusions}.
 
@@
         \hline
-        [Fe/H]          & $0.0089$   & $0.0060$ \\
-        $\mathOFe$  & $0.019$    & $0.031$ \\
+        $\mathOH$   & $0.019$    & $0.031$ \\
+        $\mathFeH$  & $0.0089$   & $0.0060$ \\
+        % $\mathOFe$  & $0.019$    & $0.031$ \\
         $\log_{10}(\tau_{\rm NN}/{\rm Gyr})$    & 0.10   & $0.16$ \\
-        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.0   & 1.3 \\
+        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.4   & 1.8 \\
         \hline
@@
 
-\begin{table*}
-\centering
-\caption{Number of APOGEE stars in each Galactic region.}
-\label{tab:apogee-regions}
-\input{output/apogee_regions_table.tex}
-\end{table*}
+% \begin{table*}
+% \centering
+% \caption{Number of APOGEE stars in each Galactic region.}
+% \label{tab:apogee-regions}
+% \input{output/apogee_regions_table.tex}
+% \end{table*}
 
@@
 When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\kpc$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}.
-Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width \todo{(do I need this table?)}.
+% Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width \todo{(do I need this table?)}.
 
@@
 We supplement the APOGEE DR17 abundance data with two different age catalogs.
-The first is from \citet{leung_variational_2023}, who train a variational encoder-decoder network on asteroseismic data for APOGEE red giants.
-This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and the recovered ages do not plateau at $\sim10\,{\rm Gyr}$ as they do in some other neural network-derived age catalogs \citep[e.g.,][]{mackereth_dynamical_2019}.
+The first is from \citet{leung_variational_2023}, who train a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
+This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and they recover accurate ages up to $\sim13\Gyr$, while other neural network-derived age catalogues exhibit an age plateau \citep[e.g.,][]{mackereth_dynamical_2019}.
 Following the recommendations of \citet{leung_variational_2023}, we cut all stars which have a relative age uncertainty greater than 40\%.
 This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
-The median uncertainty in $\log({\rm age}/{\rm Gyr})$ is 0.10 (see Table \ref{tab:uncertainties}).
-We hereafter refer to the \citet{leung_variational_2023} ages as ``NN ages.''
+The median uncertainty in $\log({\rm age})$ is 0.10 (see Table \ref{tab:uncertainties}), although the oldest stars typically have smaller reported logarithmic uncertainties.
+% We hereafter refer to the \citet{leung_variational_2023} ages as ``NN ages.''
+% \todo{Note that our projected log age error of 0.1 dex is accurate for stars $<8\Gyr$ old, but too large for older stars, so the scatter in the high-$\alpha$ sequence is larger than the data.}
 
@@
 
-Our second age catalog utilizes the [C/N]--age relation calibrated by \todo{Roberts et al.\ (hopefully submitted)} for red giant branch (RGB) and red clump stars.
-The relationship relies on the mass-dependent level of mixing during the first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
-This method has the benefit of providing age estimates for luminous giants, which increases the sample size at larger distances from the Sun.
-However, limitations from the efficiency of FDU mixing and the RGB age--mass relationship mean the ages are not trustworthy outside the range $1\sim10\Gyr$.
+Our second age catalog utilizes the [C/N]--age relation calibrated by \todo{Roberts et al.\ (in prep)} for red giant branch (RGB) and red clump stars.
+The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
+This method has the benefit of providing age estimates for luminous giants ($\log g<2.5$), which increases the sample size at larger distances from the Sun.
+Limitations from the efficiency of FDU mixing and the RGB age--mass relationship mean the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
 Additional mixing effects in low-metallicity stars %later in their RGB evolution
-also prevent the relation from being applied to luminous giant ($\log(g)<2.5$) and red clump stars with $\mathFeH<-0.4$.
-The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \todo{Roberts et al.\ (hopefully submitted)}, the propagated errors underestimate the true age dispersion and so we enhance these uncertainties by 40\% to account for this \todo{(rewrite)}.
+also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
+The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \todo{Roberts et al.\ (in prep)}, the propagated errors underestimate the true age dispersion, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
 With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
@@
 We use a time-step size of $\Delta t=10\,{\rm Myr}$ and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
-
 Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling.
-Stellar populations migrate between zones as described in Section \ref{sec:migration}, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones.
+Stellar populations migrate between zones, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones, which couples the enrichment in nearby rings.
 We inhibit star formation past $R_{\rm gal}>15.5\kpc$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
-We also assign a final midplane distance to each stellar population as described in Section \ref{sec:migration}.
+This configuration results in $N=1,638,040$ stellar populations comtributing to metal enrichment in each model.
+
+% We assign a final radius and midplane distance to each stellar population as described in Section \ref{sec:migration}. 
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the gas supply in Section \ref{sec:sfh}, the infall parameter selection in Section \ref{sec:parameter-selection}, the star formation law in Section \ref{sec:sf-law}, and the stellar migration prescription in Section \ref{sec:migration}.
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
-
-We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the gas supply in Section \ref{sec:sfh}, the infall parameter selection in Section \ref{sec:parameter-selection}, the star formation law in Section \ref{sec:sf-law}, and the stellar migration prescription in Section \ref{sec:migration}.
 Table \ref{tab:multizone-parameters} summarizes the most relevant variables and their fiducial values in this work.
@@
 This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a mass of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass in the Sun.
-However, \citet{johnson_milky_2024} found that GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
+    In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$.
+We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
+}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a mass of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass in the Sun.
+However, \citet{johnson_milky_2024} found that their GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
 Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
 
-We investigate yield sets at multiple scales of the Solar abundance.
-The CCSN yield of O is directly set by the Solar scale, $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$, because all O is assumed to form in CCSNe.
-For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathaFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathaFe}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
+We therefore investigate yield sets at multiple scales. The CCSN yield of O is directly set by the Solar scale, $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$\footnote{
     We adopt the \citet{asplund_chemical_2009} Solar abundances: $Z_{\rm O,\odot}=5.72\times10^{-3}$ and $Z_{\rm Fe,\odot}=1.29\times10^{-3}$.
+We note that for this empirical scaling, choosing different Solar abundances \citep[e.g.,][]{magg_observational_2022} would lead us to change the yields proportionally, so that our GCE model predictions in Solar-scaled abundances would actually be unchanged.
+}, because we assume that all O is produced by CCSNe.
+For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathOFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathOFe_{\rm CC}}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
+We set the plateau at $\mathOFe_{\rm CC}=+0.45$, which corresponds to an Fe yield from CCSNe of $y_{\rm Fe}^{\rm CC}=4.58\times10^{-4}(y/Z_\odot)$.
 Our yield sets are presented in Table \ref{tab:yields}.
@@
 The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is set so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
-For \yZ{3}, the combined Fe yield of CCSNe and SNe Ia matches the Solar yield scale: $(y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC})/Z_{\rm Fe,\odot}=y/Z_\odot$; for \yZ{1} and \yZ{2}, $y_{\rm Fe}^{\rm Ia}$ is increased from the given scale by a factor of 30\% and 10\%, respectively \todo{(rephrase)}.
-The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate
-\begin{equation}
-    \frac{N_{\rm Ia}}{M_\star} = \frac{y_{\rm Fe}^{\rm Ia}}{\bar m_{\rm Fe}^{\rm Ia}}
+For \yZ{3}, the combined Fe yield of CCSNe and SNe Ia matches the Solar yield scale: $(y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC})/Z_{\rm Fe,\odot}=y/Z_\odot$; for \yZ{1} and \yZ{2}, we enhance $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\%, respectively, to reach the desired end-point.
+The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate or total number of SNe Ia per unit mass of star formation,
+\begin{equation}
+    \frac{N_{\rm Ia}}{M_\star} = \frac{y_{\rm Fe}^{\rm Ia}}{\bar m_{\rm Fe}^{\rm Ia}},
     \label{eq:snia-rate}
@@
 
-Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion.
-The time-dependent SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
+Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion. The time-dependent SN Ia rate per unit mass of star formation is defined as
 \begin{equation}
@@
 \end{equation}
-where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per unit mass of star formation, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
-Motivated by the finding by \citet{dubay_galactic_2024} that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence, we adopt a wide plateau DTD of the form
+where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is our assumed lifetime of the Galactic disk, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
+Motivated by recent results suggesting that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence \citep{palicio_analytic_2023,dubay_galactic_2024}, we adopt a wide plateau DTD of the form
 \begin{equation}
@@
 Notably, the yields for O and Fe were left unchanged from the original studies.
-However, because \citet{woosley_evolution_1995} report gross yields without detailed initial abundances for their CCSN progenitors, and because \citet{francois_evolution_2004} do not provide population-averaged yields, it is difficult to make a comparison with our yield sets.
+However, because \citet{woosley_evolution_1995} report gross yields without detailed initial abundances for their CCSN progenitors, and because \citet{francois_evolution_2004} do not provide population-averaged yields, it is difficult to make a comparison with our yields.
 Ultimately, \citet{francois_evolution_2004} report that their GCE models are insensitive to changes in the CCSN yield of O by a factor of 2, so we consider it reasonable to explore the full range of yields given in Table \ref{tab:yields}.
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/yield_outflow.pdf}
+    \includegraphics[width=\onecolumn]{figures/yield_outflow.pdf}
     \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors.
@@
 The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5\,{\rm Gyr}$ ago.
-However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.
+% However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.
+The primary timescale governing chemical evolution is the rate at which ISM gas is depleted by star formation or outflows \citep{weinberg_equilibrium_2017}, and it is the higher outflows of the higher-yield models that leads to faster evolution.
+For the same reason, the high-yield models give a larger jump in [O/Fe] at the start of the second infall because the O abundance can grow by a larger factor before enrichment from second-infall SNe Ia becomes important.
 
@@
 
+Not all GCE studies have constrained their models to reach an equilibrium at the Solar metallicity.
+For example, the models of \citet{palla_chemical_2020} and \citet{spitoni_remind_2024} predict somewhat super-Solar metallicity in the present-day Solar neighborhood.
+Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar abundances (Figure \ref{fig:yield-outflow}) indicate that the Solar neighborhood is presently close to Solar metallicity, so we use $\eta$ to fine-tune the chemical evolution end-point to to $\mathOH\approx0.0$.
+
 Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
@@
 As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [O/H] with $R_{\rm gal}$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$ \todo{(citations)}.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, in line with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
 
@@
 Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023}.
-To achieve a realistic radial metallicity gradient, many studies adopt the yields of \citet{francois_evolution_2004} and use a prescription for the infall timescale of the thin disk which increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
-\todo{Additionally, many two-infall models reach a final metallicity higher than Solar.
-Citations for present-day gas abundance in the Solar neighborhood.}
+To achieve a realistic radial metallicity gradient, many studies have adopted the yields of \citet{francois_evolution_2004} and a prescription for the infall timescale of the thin disk that increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
+Additionally, some studies have implemented radial gas flows or a variable star formation efficiency in order to regulate the radial metallicity gradient \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020}.
 
@@
 However, mass-loaded outflows are not a necessary ingredient for the results of this study.
-We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the model with $\eta=0.2$ and \yZ{1}.
-Therefore, our multizone models with \yZ{1} should predict similar behavior to a model without any mass-loaded outflows.
+We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
+%Therefore, our multi-zone models with \yZ{1} should predict similar behavior to a model without any mass-loaded outflows.
 %If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.
@@
 
-We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time.
+We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time at each radius.
 The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities according to our star formation law, which is described in Section \ref{sec:sf-law}, assuming zero initial gas mass in all zones.
@@
 In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, either from gas stripped from dwarf galaxies or from SNe in the halo \todo{(citations; any measurements of CGM metallicity?)}.
-For this reason, we also test cases where the infalling gas is pre-enriched and its metallicity is described by
+However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
+The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
+We investigate models where the infalling gas is pre-enriched and its metallicity is described by
 \begin{equation}
@@
     \centering
-    \includegraphics{figures/onezone_params.pdf}
+    \includegraphics[width=\textwidth]{figures/onezone_params.pdf}
     \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters.
@@
 A shorter $\tau_2$ produces a bigger loop and therefore a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
-We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns.
+We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is close to a constant infall rate, so a further increase in $\tau_2$ has diminishing effect.
 Between $\tau_2=3-30\,{\rm Gyr}$, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
@@
     \centering
-    \includegraphics{src/tex/figures/sfe_prefactor.pdf}
+    \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
     \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
@@
 \end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ \todo{(?)} and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citet{leroy_star_2008}.
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citet{leroy_star_2008}.
 Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\varepsilon$:
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{figures/star_formation_history.pdf}
+    \centering
+    \includegraphics[width=\onecolumn]{figures/star_formation_history.pdf}
     \caption{(a) The infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
@@
 This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
-So, a significant fraction of SN Ia progenitors born in a given zone will enrich a disparate region of the Galaxy.
+So, a significant fraction of SN Ia progenitors born in a given zone will enrich a different region of the Galaxy.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/abundance_evolution_yields.pdf}
-    \caption{Stellar age--abundance relations produced by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
+    \includegraphics[width=\onecolumn]{figures/abundance_evolution_yields.pdf}
+    \caption{Stellar age--abundance relations predicted by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
@@
 The dilution effect discussed in Section \ref{sec:yields} is clearly seen in the multi-zone model results.
-We first examine the differences between multi-zone models which assume different yield and outflow scales.
-Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations produced by models with \yZ{1} and \yZ{2} with fiducial parameters (Table \ref{tab:multizone-parameters}).
+Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations predicted by models which assume different yield and outflow scales, \yZ{1} and \yZ{2}, and the fiducial parameters (Table \ref{tab:multizone-parameters}).
 The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
@@
 However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is steeper than the data, especially for ages $\sim4-8\,{\rm Gyr}$.
+Note that we scatter simulated data points according to the median age and abundance errors in Table \ref{tab:uncertainties}, so the blurring impact of these statistical errors is incorporated in the model.
+The solid black curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
+Despite the effects of radial migration and statistical errors, the stellar populations mostly scatter around this gas phase curve, at least for $\tau\lesssim9\Gyr$.
 
@@
     \centering
-    \includegraphics{figures/abundance_evolution_params.pdf}
+    \includegraphics[width=0.9\textwidth]{figures/abundance_evolution_params.pdf}
     \caption{Stellar age--abundance relations in the Solar annulus produced by select multi-zone models with \yZ{1}.
@@
 
+Chemical evolution models which assume the \yZ{1} empirical yield scale already struggle to match the local age--metallicity relation, even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
+The problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
 We next attempt to mitigate the dilution and late-time evolution problems for the empirical (\yZ{1}) yield scale.
@@
 Next, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
-Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population \todo{(reword}).
+Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
 Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/mdf_evolution.pdf}
+    \includegraphics[width=\textwidth]{figures/mdf_evolution.pdf}
     \caption{Evolution of the MDF over time across the Galactic disk.
@@
 The gray curve represents the total MDF in each region.
-Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters at different yield and outflow scales.
+Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters (see Table \ref{tab:multizone-parameters}) at different yield and outflow scales.
     % For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$. 
@@
 The distributions in all panels are restricted to $0\leq|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
-{\bf Key takeaway:} The APOGEE distributions show remarkably little variation in position over the past $\sim6-8$ Gyr at all radii, whereas both GCE models predict a steady evolution toward higher [Fe/H] with time.}
+{\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both GCE models predict a steady evolution toward higher [Fe/H] with time.}
     \label{fig:mdf-evolution}
@@
 
-The discrepancies between the predicted and observed abundance evolution discussed in Section \ref{sec:age-abundance} are also seen across the disk.
-Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the \yZ{1} and \yZ{2} models.
-We adopt pre-enriched infall ($\mathFeH_{\rm CGM}=-0.7$), stronger radial migration ($\sigma_{\rm RM8}=3.6$ kpc), and a higher disk mass ratio ($f_\Sigma(R_\odot)=0.25$) because these parameters were able to improve agreement with observations in previous sections.
-For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages $\leq10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
-
-The two-infall model predicts a very broad MDF for ages $>10$ Gyr because of the rapid enrichment of the ISM during the first infall epoch.
-
-Figure \ref{fig:mdf-evolution} shows that even with pre-enriched infall, both of our models predict that the MDF shifts to the left going from younger to older populations.
-On the other hand, the data show that the MDF broadens with age, which we attribute to radial migration, but its peak does not shift substantially over the past $\sim6-8$ Gyr.
-While the mode of the MDF shifts depending on the radial bin, its evolution is remarkably consistent over the entire disk, in line with the equilibrium scenario of \citet{johnson_milky_2024}.
-\todo{Note about metallicity cutoff for luminous giants.}
-
-On the other hand, the model predictions for the MDF in the $8-10\,{\rm Gyr}$ age bin are strikingly similar to the APOGEE MDF.
-The two-infall model predicts a bimodal distribution: the metal-rich component comprises stars formed during the last Gyr of the first infall epoch, and the metal-poor component is stars formed during the first Gyr of the second infall epoch (post-dilution).
-The data show this same bimodal structure in all but the outermost radial bin, with peaks at $\mathFeH\approx-0.3$ and $+0.3$.
-While the location of the model peaks depends on $R_{\rm gal}$, in the data they are quite consistent from the innermost to the outermost bin.
-\todo{I actually think the two-infall model gets this right for the wrong reasons.
-In the data, the left peak is the high-$\alpha$ sequence and the right is the high-metallicity end of the low-$\alpha$ sequence.
-In the model, the {\it right} peak is produced during the first infall (i.e., thick disk) and the {\it left} is immediately after the second infall (i.e., low-metallicity end of thin disk).}
+The discrepancies between the predicted and observed abundance evolution in the Solar neighborhood discussed in Section \ref{sec:age-abundance} persist across the Galactic disk.
+Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the \yZ{1} and \yZ{2} models with the fiducial parameters.
+% We adopt pre-enriched infall ($\mathFeH_{\rm CGM}=-0.7$), stronger radial migration ($\sigma_{\rm RM8}=3.6$ kpc), and a higher disk mass ratio ($f_\Sigma(R_\odot)=0.25$) because these parameters were able to improve agreement with observations in previous sections.
+For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
+% The two-infall model predicts a very broad MDF for ages $>10$ Gyr because of the rapid enrichment of the ISM during the first infall epoch.
+
+The results of both models in Figure \ref{fig:mdf-evolution} show a clear evolutionary trend at all radii.
+The mode of the MDF shifts consistently to the right when moving from older to younger stars.
+The distance between the $1-2\Gyr$ and $2-4\Gyr$ age bins is smaller for the \yZ{2} model because of the faster approach to equilibrium (see also Figure \ref{fig:abundance-evolution-yields}).
+In the Solar annulus (center column), the mode of the $6-8\Gyr$ age MDF is $0.3\dex$ lower than the present-day metallicity in the \yZ{2} model, and $0.4\dex$ lower in the \yZ{1} model.
+
+In contrast, the APOGEE data show remarkably little evolution over the past $\sim8\Gyr$ at all radii.
+Row (c) of Figure \ref{fig:mdf-evolution} shows that the MDF broadens with age, but its peak does not shift much over the past $\sim8\Gyr$.
+The mode [Fe/H] for the youngest stars (indicated by the vertical blue dotted line) is nearly the same as for the $6-8\Gyr$ old stars.
+Inward of the Solar annulus, the MDF skews more to lower [Fe/H], but its mode does not shift by more than $\sim0.1\dex$.
+It is difficult to draw conclusions about the outer Galaxy because the mode [Fe/H] is close to the metallicity cut at $\mathFeH>-0.4$ for luminous giants (represented by the vertical gray dashed line), which comprise the majority of stars in the sample at that distance.
+The remarkable consistency of the MDF over time, in agreement with the equilibrium scenario of \citet{johnson_milky_2024}, contrasts with the predictions of our fiducial models.
+
+The oldest age bin in Figure \ref{fig:mdf-evolution} shows distinct behavior in both the models and data.
+The $8-10\Gyr$ age bin spans both the tail end of the thick disk phase and the beginning of the thin disk, so the MDF is bimodal: the higher peak consists of $>9\Gyr$ old stars, and the lower peak $8-9\Gyr$ old stars (post-dilution phase).
+Intriguingly, the APOGEE MDF in that age bin is also bimodal in all but the outer-most radial bin, with peaks at $\mathFeH\approx-0.3$ and $+0.3$ independent of the location in the Galaxy.
+While data and model show qualitatively similar behavior, they actually represent different populations.
+In the model, the metal-rich peak is composed of thick-disk stars while the metal-poor peak marks the formation of the thin disk.
+In the data, the metal-rich peak are all low-$\alpha$ stars, while the metal-poor peak is the locus of the high-$\alpha$ sequence \textemdash a reversal of the model predictions.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/ofe_feh_density.pdf}
+    \includegraphics[width=\onecolumn]{figures/ofe_feh_density.pdf}
     \caption{The density of stars in the [O/Fe]--[Fe/H] plane predicted by multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
@@
 
-Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model at mid to high Galactic latitudes.
-Between $0.5\leq|z|<1\kpc$, both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over ($\mathFeH\approx-0.3$, $\mathOFe\approx0.1-0.2$), which is not seen in the APOGEE sample.
-This over-density occurs because the overall rate of chemical evolution slows down $\sim2\,{\rm Gyr}$ after the second infall, and at the same time the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
+Figure \ref{fig:ofe-feh-density} illustrates the origin of the intermediate-$\alpha$ peak predicted by the two-infall model.
+Both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over ($\mathFeH\approx-0.3$, $\mathOFe\approx0.1-0.2$), which is not seen in the APOGEE sample.
+% This over-density occurs because the overall rate of chemical evolution slows down $\sim2\,{\rm Gyr}$ after the second infall, and at the same time the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
+The local maximum in $dN_\star/d\mathOFe$ comprises stars which formed in the second infall before SN Ia enrichment began to drive down [O/Fe].
 This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow} or the models with longer $\tau_2$ in Figure \ref{fig:twoinfall-parameters}.
@@
 Additionally, the shape of the low-$\alpha$ sequence in the model results (a concave-down ``comma'') is clearly different from the data (a concave-up ``swoosh'').
-\todo{Not sure what this means because the inside-out SFH has the same issue.
-Maybe it's related to radial migration?}
+This is a subtle distinction, on the $\sim0.05\dex$ level in [O/Fe].
+We have not accounted for the APOGEE selection function in our models, but there is no evident reason for observational effects to produce this difference in morphology.
+This problem is not unique to the two-infall scenario: it results from the concave-down track of the abundance evolution, and has stymied other models as well \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
+Nevertheless, it is worth mentioning because the two-infall scenario is otherwise quite successful at reproducing the local stellar distribution in [O/Fe]--[Fe/H] space.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_yields.pdf}
+    \includegraphics[width=\onecolumn]{src/tex/figures/ofe_distribution_yields.pdf}
     \caption{Normalized stellar [O/Fe] distributions produced by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
@@
 Figure \ref{fig:ofe-distribution-yields} compares [O/Fe] distributions from across the Galactic disk produced by models with the \yZ{1} and \yZ{2} yield sets.
+We present the distributions in multiple bins of $|z|$ as well as $R_{\rm gal}$ because the observed pattern varies as a function of midplane distance, and because the APOGEE selection function over-emphasizes high-$|z|$, and therefore high-$\alpha$, stars in the full sample \citep[see Figure 5 from][]{vincenzo_distribution_2021}.
 For model (a) with $y/Z_\odot=1$, the two thin disk peaks are close enough together that they approximate a single peak, especially once observational uncertainties are factored in.
@@
 
-\todo{Discuss why we divided Figures \ref{fig:ofe-distribution-yields} and \ref{fig:ofe-distribution-parameters} into $|z|$ bins: (1) pattern changes as a function of midplane distance, and (2) we don't have to worry so much about correcting the APOGEE data to rebalance between the thin and thick disk fields.}
+% \todo{Discuss why we divided Figures \ref{fig:ofe-distribution-yields} and \ref{fig:ofe-distribution-parameters} into $|z|$ bins: (1) pattern changes as a function of midplane distance, and (2) we don't have to worry so much about correcting the APOGEE data to rebalance between the thin and thick disk fields.}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
+    \includegraphics[width=\textwidth]{src/tex/figures/ofe_distribution_params.pdf}
     \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e).
@@
 Finally, in model (d) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
-This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates \todo{(citations)}.
+This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates (see Section \ref{sec:sfh}).
 The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the previous models.
-\todo{Note that APOGEE high-$\alpha$ sequence is over-emphasized by survey selection function.} In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \yZ{2} case.
+In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \yZ{2} case.
 These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.
@@
 A longer $\tau_1$ could shift this population to higher [O/Fe] where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
-Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall model predicts a steep age gradient for the most metal-rich stars in a given region.
+Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall model predicts a bimodal age distribution for metal-rich stars.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/lmr_ages.pdf}
+    \includegraphics[width=\textwidth]{figures/lmr_ages.pdf}
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
@@
 
-The two-infall model makes a prediction about the local stellar age distribution that is fundamental to its construction: that the most metal-rich stars born in-situ in any region of the Galaxy come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
+The two-infall model makes a fundamental prediction about the local stellar age distribution: the most metal-rich stars born in-situ in any region of the Galaxy should come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
 As noted in the previous Section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.
@@
 
-We further highlight the discrepant age patterns in the bottom panels of Figure \ref{fig:lmr-ages}, which compare the overall stellar age distribution against that of the locally metal rich (LMR) stars, defined here as $\mathFeH\ge+0.1$.\footnote{The precise location of the cut matters little, as we observe the same behavior for cuts ranging from $+0.05$ to $+0.2$ dex.} For APOGEE, the distributions are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
-Our two-infall models produce an age distribution for the overall sample that is similar to the data, but for LMR stars, both models predict a distinctly bimodal age distribution.
+We further highlight the discrepant age patterns in the bottom panels of Figure \ref{fig:lmr-ages}, which compare the overall stellar age distribution against that of the locally metal rich (LMR) stars, defined here as $\mathFeH\ge+0.1$.
+% The precise location of the cut matters little, as we observe the same behavior for cuts ranging from $+0.05$ to $+0.2$ dex. 
+For APOGEE, the distributions are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
+Our two-infall models predict an age distribution for the overall sample that is similar to the data, but for LMR stars, both models predict a distinctly bimodal age distribution.
 There is a large contribution from the young, metal-rich end of the second infall, and a contribution from the old, metal-rich end of the first, but there are few stars in between.
 The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
-
-\todo{Mention some ways to try to resolve this (e.g., stronger radial migration) and that they don't work.}
-\todo{Note that our projected log age error of 0.1 dex is accurate for stars $<8\Gyr$ old, but too large for older stars, so the scatter in the high-$\alpha$ sequence is larger than the data.}
+While the amplitude of the peaks is sensitive to the precise location of the LMR cutoff, the dearth of intermediate-age stars is robust to adjustments of $\pm0.05\dex$.
+
+It is difficult to predict a qualitatively different age distribution with the available parameter space.
+Pre-enriching the accreted gas shifts the equilibrium metallicity higher, increasing the proportion of young stars to old.
+Stronger radial migration similarly shifts more young stars into the LMR region.
+On the other hand, increasing the local thick-to-thin disk mass ratio produces more old, thick disk stars.
+None of these adjustments substantially increase the proportion of intermediate-age stars, which are the dominant component of the LMR population observed in APOGEE.
 
@@
 
-\todo{Summary of problem: the two-infall model is boxed in by data.}
-
-\subsection{Comparison with Previous Literature}
-
-\subsection{The Empirical Yield Scale}
-
-The \yZ{1} empirical yield scale already has difficulties matching the local age--metallicity relation \citep{johnson_milky_2024}, but the problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
+% \todo{Summary of problem: the two-infall model is boxed in by data.}
+Our results show that the APOGEE stellar age catalogs pose several challenges to the two-infall scenario.
+The [O/Fe] distribution was the easiest to resolve using the parameter space we explored, either by pre-enrichment of the accreted gas or a higher thick-to-thin disk mass ratio.
+These parameters also allowed us to mitigate, but not completely resolve, the issue of dilution.
+However, the predicted age distributions could not be reconciled with the data using any of the parameters we explored.
+In the remainder of this section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.
+
+% \subsection{Comparison with Previous Literature}
+
+% \subsection{The Empirical Yield Scale}
+
+% The \yZ{1} empirical yield scale already has difficulties matching the local age--metallicity relation \citep[see also][]{johnson_milky_2024}, but the problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
 
@@
 
-Motivated by evidence of a recent period of enhanced star formation \citep[e.g.,][]{ruiz-lara_recurrent_2020}, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} extended the two-infall model with a recent third accretion episode.
+Motivated by evidence of a recent period of enhanced star formation \citep[e.g.,][]{ruiz-lara_recurrent_2020}, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} extended the two-infall model with a recent $(\lesssim3\Gyr)$ third accretion episode.
 \citet{spitoni_beyond_2023} argued that the gas dilution resulting from the third infall could explain the population of young, metal-poor stars discovered in {\it Gaia} DR3 \citep{recio-blanco_gaia_2023}, in contrast to the two-infall model of \citet{spitoni_apogee_2021} which predicted a present-day gas metallicity of ${\rm [M/H]}\approx+0.3$ in the Solar neighborhood.
-\citet{palla_mapping_2024} were similarly motivated by the finding that open clusters with ages $<1\Gyr$ have similar metallicity to those with ages $>3\Gyr$ \todo{and younger than OCs in between}, while the classical two-infall model predicted a steady increase in metallicity over time.
+\citet{palla_mapping_2024} were similarly motivated by the finding that open clusters with ages $<1\Gyr$ have similar metallicity to those with ages $>3\Gyr$, while the classical two-infall model predicted a steady increase in metallicity over time.
 However, \citet{palla_mapping_2024} invoke a less massive infall, producing a milder dilution event, than \citet{spitoni_beyond_2023}.
 
-Some combination of metal-rich accretion and radial gas flows might reduce the amount of dilution predicted by a recent accretion episode.
+The flat AMR from both stellar age catalogs is even more restrictive of a recent dilution event because of the smaller age uncertainties for younger stars.
+Figure \ref{fig:yield-outflow} illustrates that the mode and overall distribution of [O/H] has evolved very little over the past $\sim5$ Gyr.
+Some combination of metal-rich accretion or radial gas flows might reduce the amount of dilution predicted by a recent accretion episode, but the parameter space is tightly constrained by the stellar age data.
 
@@
 
-\todo{Radial gas flows are hard :'(}
-
-Some two-infall studies \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
-
+% Radial gas flows allow GCE models to produce a radial metallicity gradient in the absence of mass-loaded outflows.
+Radial gas flows introduce multiple variables, such as the speed, direction, and angular momentum of the flow, which remain relatively unconstrained in the MW.
+\citet{spitoni_effects_2011} studied the effects of radial gas flows in the two-infall scenario and found that an inward radial flow with velocity $v_R\sim0-4\kms$ can steepen the radial abundance gradient to match observations.
+Subsequent studies \citep{palla_chemical_2020,palla_mapping_2024} implemented a $\sim-1\kms$ radial gas flow in order to reproduce the abundance gradient in the absence of Galactic outflows.
+Confirming these results, \todo{Johnson et al.
+(in prep)} find that an inward gas flow with a flat velocity profile has a similar effect on the radial metallicity gradient as the exponential outflow prescription in our models.
+We believe that switching from outflows to radial gas flows would not solve any of our models' issues regarding the age--abundance relation, [O/Fe] distributions, or stellar age distributions.
+
+% Some two-infall studies \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
 \citet{spitoni_effects_2011} find that a two-infall model of the disk without gas exchange produces a radial metallicity gradient which is too shallow.
@@
     \centering
-    \includegraphics{figures/onezone_sfe_hiatus.pdf}
+    \includegraphics[width=\onecolumn]{figures/onezone_sfe_hiatus.pdf}
     \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.
@@
 The onset time of the SFE hiatus controls the position of the high-$\alpha$ sequence: a later onset places the peak at lower [O/Fe].
-The duration of the star formation hiatus \todo{(and the $\tau_\star$ enhancement factor?)} controls the strength of the high-$\alpha$ peak.
+The duration of the star formation hiatus and the $\tau_\star$ enhancement factor control the strength of the high-$\alpha$ peak.
 
@@
 We ran multi-zone GCE models at two different yield scales with prescriptions for radially-dependent outflows and stellar migration.
-While the two-infall scenario can explain the local stellar abundance distribution, in particular the $\alpha$-bimodality, it faces challenges in matching the age--abundance structure of the full disk.
+While the two-infall scenario can explain the distinct high- and low-$\alpha$ sequences, it faces challenges in matching the age--abundance structure of the full disk.
 We explored multiple parameter modifications to bring the model predictions closer to the data, including the yield scale, radial migration strength, metallicity of the accreted gas, thick-to-thin disk mass ratio, and the SN Ia DTD.
@@
 %This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
+    \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations.
+In contrast, the data show a smooth gradient between the oldest and youngest stars, with most of the metal-rich stars having intermediate ages.
     \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a double-peaked low-$\alpha$ sequence with a fundamentally different abundance structure than observed, especially for models with higher yields.
@@
 The parameter space is nonetheless restricted by the need to suppress this feature.
-    \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations.
-In contrast, the data show a smooth gradient between the oldest and youngest stars, with most of the metal-rich stars having intermediate ages.
     \item Our models predict that the MDF evolves to higher metallicity over time throughout the disk.
 This contrasts with the APOGEE data, which show very little change in the mode over the past $\sim6-8$ Gyr.
-    \item The equilibrium scenario of chemical evolution, if correct, places stricter limits on the two-infall model than other evolutionary models.
+    % \item The equilibrium scenario of chemical evolution, if correct, places stricter limits on the two-infall model than other evolutionary models.
 \end{itemize}
@@
 If the equilibrium scenario of \citet{johnson_milky_2024} is correct, then it restricts the two-infall scenario more than other GCE models.
-
-\todo{Implications for merger-driven SFHs.}
+Restrictions on the two-infall scenario also translate more broadly to other merger-dominated SFHs, which must explain the MW's $\alpha$-bimodality without significantly diluting the metallicity of the ISM.
 

### 2025-06-27 src/tex/ms.tex
Manuscript updates

@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
-    \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
+%     \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
 All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
-    \label{fig:sfe-prefactor}
-\end{figure}
+%     \label{fig:sfe-prefactor}
+% \end{figure}
 
@@
 \end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citet{leroy_star_2008}.
-Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\varepsilon$:
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citep{leroy_star_2008}.
+Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through the pre-factor $\varepsilon$:
 \begin{equation}
@@
 \end{equation}
-A lower value of $\varepsilon(t<t_{\rm max})$ leads to more efficient star formation during the first infall epoch.
-Figure \ref{fig:sfe-prefactor} illustrates that this pre-factor largely affects the metallicity of the high-$\alpha$ sequence, with a smaller $\varepsilon$ producing faster enrichment during the first infall and stronger dilution after $t_{\rm max}$.
-The pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law, but a lower value of $\varepsilon$ does narrow the MDF by $\sim0.1$ dex in [Fe/H].
-We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature.
+A lower value of $\varepsilon(t<t_{\rm max})$ leads to more efficient star formation, and therefore more rapid enrichment, during the first infall epoch.
+However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
+We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature, though we find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
 To guard against over-correcting the SFE in the early Galaxy, we have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.

### 2025-07-01 src/scripts/mdf_evolution.py
add |z| labels

@@ -41,18 +41,6 @@ def main(style='paper', col='[fe/h]', cmap=CMAP, smoothing=SMOOTH_WIDTH):
                           width=0.015, pad=0.015, labelpad=2)
 
     # Plot multizone outputs
-    # output_names = [
-    #     'yZ1/best/cgm07_ratio025_eta04_migr36/diskmodel',
-    #     'yZ2/best/cgm07_ratio025_eta18_migr36/diskmodel'
-    # ]
-    # output_names = [
-    #     'yZ1/thick_thin_ratio/solar024/diskmodel',
-    #     'yZ2/thick_thin_ratio/solar024/diskmodel'
-    # ]
-    # model_labels = [
-    #     r'(a) $y/Z_\odot=1$, ${\rm %s}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6$ kpc' % capitalize_abundance(col),
-    #     r'(b) $y/Z_\odot=2$, ${\rm %s}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6$ kpc' % capitalize_abundance(col)
-    # ]
     output_names = [
         'yZ1/fiducial/diskmodel',
         'yZ2/fiducial/diskmodel'
@@ -72,7 +60,7 @@ def main(style='paper', col='[fe/h]', cmap=CMAP, smoothing=SMOOTH_WIDTH):
             )
             axs[i,j].plot(
                 get_bin_centers(bin_edges), mdf, 
-                color='0.7', linewidth=2, #alpha=0.6,
+                color='0.7', linewidth=2,
                 label='All stars'
             )
             for k in range(len(AGE_BINS)-1):
@@ -84,7 +72,7 @@ def main(style='paper', col='[fe/h]', cmap=CMAP, smoothing=SMOOTH_WIDTH):
                 )
                 axs[i,j].plot(
                     get_bin_centers(bin_edges), mdf, 
-                    color=colors[k], linewidth=1, #alpha=alpha,
+                    color=colors[k], linewidth=1,
                     label='%s - %s' % tuple(age_lim)
                 )
     
@@ -103,7 +91,7 @@ def main(style='paper', col='[fe/h]', cmap=CMAP, smoothing=SMOOTH_WIDTH):
         )
         axs[-1,j].plot(
             get_bin_centers(bin_edges), mdf, 
[…]

### 2025-07-01 src/tex/ms.tex

@@
 \section{Introduction}
+\label{sec:introduction}
 
@@
 The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks.
-Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive bursts that each decay with time.
+Though the model has since been refined, the basic premise remains the same: the rate of gas accretion onto the disk is described by two consecutive bursts that each decay with time.
 The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
-The infall timescale for the low-$\alpha$ disk can be varied to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
+The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
 The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.
 
-Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}.
-Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
+Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}.
+Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
 \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
-Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey (SDSS) \todo{(cite)}.
+Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey (SDSS; \todo{Hawkins et al.
+in prep}).
 
 % \todo{Outflows.} 
-Most previous studies of the two-infall model have not included mass-loaded outflows.
+While previous studies have explored a large parameter space, most have assumed that the Galactic disk never ejected a substantial outflow.
 This decision is based on hydrodynamic simulations of Galactic fountains ejected by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
@@
 
-% \todo{Discuss yields, degeneracy with outflows and Rodriguez measurements.
-Emphasize that degeneracy with outflows prohibits direct estimates of yields from GCE.
-We aim to study the effect of the yield assumptions, which necessitates adjusting the outflows as well.}
 By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}.
 \citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
-This degeneracy prohibits direct estimates of the yield scale from GCE models, unless the effect of outflows is assumed to be insignificant \citep[e.g.,][]{francois_evolution_2004}.
-% Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of core-collapse supernovae (CCSNe) by \citet{rodriguez_iron_2023} to infer a supernova yield scale that is a factor of $\sim2$ lower than assumed by some previous GCE studies.
+This degeneracy prohibits direct estimates of the yield scale from GCE models, unless the effect of outflows is assumed to be insignificant.
 The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of the yield scale on two-infall scenario predictions.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{figures/yield_outflow.pdf}
-    \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors.
-Table \ref{tab:yields} presents the population-averaged yields for each model.
-The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
-The black points with error bars indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
-    \label{fig:yield-outflow}
-\end{figure}
-
-Figure \ref{fig:yield-outflow} illustrates the effect of the yield scaling on the abundance evolution in one-zone models.
-We vary the outflow mass-loading factor $\eta$ for each model to achieve a consistent endpoint to the abundance evolution (see Section \ref{sec:outflows} for further discussion on outflows).
-All models feature a rapid dilution of the ISM metallicity by $\sim0.5-0.8$ dex, visible in the top two panels, brought on by the infall of pristine gas at $t_{\rm max}$.
-For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the close to present day.
-The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5\,{\rm Gyr}$ ago.
-% However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.
-The primary timescale governing chemical evolution is the rate at which ISM gas is depleted by star formation or outflows \citep{weinberg_equilibrium_2017}, and it is the higher outflows of the higher-yield models that leads to faster evolution.
-For the same reason, the high-yield models give a larger jump in [O/Fe] at the start of the second infall because the O abundance can grow by a larger factor before enrichment from second-infall SNe Ia becomes important.
-
-Figure \ref{fig:yield-outflow} also indicates the mode of the APOGEE abundance distributions in 1 Gyr-wide age bins.
-As explained by \citet{johnson_milky_2024}, the mode is expected to be less sensitive to the effects of radial migration than other statistical measures.
-The data show that the evolution in [O/H] is close to flat over the past 5 Gyr.
-The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model increases significantly by $\sim0.2$ dex during the same time period.
-The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia.
-Between lookback times of $\sim5-9\,{\rm Gyr}$, the modes of [O/H] and [Fe/H] are higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times.
-
-The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset (which could be corrected by increasing $y_{\rm Fe}^{\rm Ia}$ or adjusting the zero-point in the stellar abundances).
-The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields.
-Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution.
-As the \yZ{2} and \yZ{3} models behave qualitatively similarly, we focus on the \yZ{1} and \yZ{2} yield sets for the remainder of this study.
-
 \subsection{Outflows}
@@
 \end{equation}
-where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the star formation timescale, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
-% Equation \ref{eq:equilibrium} can be inverted to calculate the value of $\eta$ required to reach a desired $Z_{\rm O,eq}$ with a given yield, but it is inaccurate in the limit of zero accretion. 
-Motivated by Equation \ref{eq:equilibrium}, we adopt an outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
-Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than would be suggested by Equation \ref{eq:equilibrium} in order to reach Solar metallicity at the end of the model.
+where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the $e$-folding timescale of the star formation history, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
+Motivated by Equation \ref{eq:equilibrium}, we adopt the outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
+Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on age trends such as these.
 
@@
 For example, the models of \citet{palla_chemical_2020} and \citet{spitoni_remind_2024} predict somewhat super-Solar metallicity in the present-day Solar neighborhood.
-Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar abundances (Figure \ref{fig:yield-outflow}) indicate that the Solar neighborhood is presently close to Solar metallicity, so we use $\eta$ to fine-tune the chemical evolution end-point to to $\mathOH\approx0.0$.
+Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances  indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we use $\eta$ to fine-tune the chemical evolution end-point to $\mathOH\approx0.0$.
 
 Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
+\citet{johnson_milky_2024} used this approach to present a proof of concept for the equilibrium scenario.
 In order to produce an exponentially declining radial metallicity gradient, we adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
@@
 where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
-As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [O/H] with $R_{\rm gal}$.
 We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, in line with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
@@
 Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
-Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023}.
+Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023} or does not vary with radius \citep{hegedus_reconstructing_2025}.
 To achieve a realistic radial metallicity gradient, many studies have adopted the yields of \citet{francois_evolution_2004} and a prescription for the infall timescale of the thin disk that increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
@@
 As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
-Because we aim to study the effect of the yield assumptions on two-infall model predictions, we use mass-loaded outflows to control the final state of chemical evolution across the disk.
+Here, we aim to study the effect of the assumed yield scale on two-infall model predictions, so we use mass-loaded outflows to control the final state of chemical evolution across the disk.
 However, mass-loaded outflows are not a necessary ingredient for the results of this study.
@@
 We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time at each radius.
-The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from the two specified quantities according to our star formation law, which is described in Section \ref{sec:sf-law}, assuming zero initial gas mass in all zones.
+The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from these two inputs as a natural outcome of the time-stepping solution, assuming zero initial gas mass in all zones.
 
@@
 \end{equation}
-where $g(R_{\rm gal})=\Sigma_\star(R_{\rm gal}) / \Sigma_\star(R_{\rm gal}=0)$ is the stellar density gradient, $f_{\rm in}$ is the infall rate over time, and $A$ is the normalization.
+where $g(R_{\rm gal})=\Sigma_\star(R_{\rm gal}) / \Sigma_\star(R_{\rm gal}=0)$ is the stellar density gradient, $f_{\rm in}$ is the infall rate over time, and $A$ is a normalization constant.
 Because we incorporate mass-loaded outflows, $A$ is not analytically solvable, so first we numerically integrate the star formation rate $\dot\Sigma_\star(t,R_{\rm gal})$ and then follow the procedure outlined in Appendix B of \citet{johnson_stellar_2021} to calculate $A$.
-The infall rate is normalized to produce a total disk stellar mass of $(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and to match the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
-
-The infall rate is described by two successive, exponentially declining bursts in time.
+In short, the infall rate is normalized to produce a total disk stellar mass of $(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and to match the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
+
+Characteristic of the two-infall scenario, the infall rate is described by two successive, exponentially declining bursts in time.
 The first infall component induces the formation of the thick disk, and the second component produces the thin disk.
@@
     \label{eq:twoinfall-ifr}
-    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
-\end{equation}
-where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall, and $f_{2/1}$ is the ratio of the second infall amplitude to the first.
+    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + H(t-t_{\rm max}) f_{2/1} (R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
+\end{equation}
+\begin{equation*}
+    H(x) \equiv 
+    \begin{cases}
+        1, & x \ge 0 \\
+        0, & x < 0,
+    \end{cases}
+\end{equation*}
+where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall,  $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
 We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
@@
 We therefore explore values up to $f_\Sigma(R_\odot)=0.5$ in our multi-zone models in Section \ref{sec:multizone-results}.
-% This value is on the low end of literature estimates; by comparison, \citet{mackereth_age-metallicity_2017} found $f_\Sigma(R_\odot)=0.18\pm0.05$ from APOGEE, and \citet{fuhrmann_local_2017} derived $f_\Sigma(R_\odot)=0.57$ from a very small volume (25 pc radius).
-% \citet{spitoni_galactic_2020} explores $f_\Sigma(R_\odot)\approx0.23-0.31$, \citet{palla_chemical_2020} assumes $f_\Sigma(R_\odot)=0.23$, \citet{spitoni_apogee_2021} derives $f_\Sigma(R_\odot)=0.18$ (again from APOGEE), \citet{spitoni_remind_2024} assumes $f_\Sigma(R_\odot)=0.4$.
 
@@
 The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
-We investigate models where the infalling gas is pre-enriched and its metallicity is described by
+We investigate models where the infalling gas is pre-enriched, and its metallicity is described by
 \begin{equation}
@@
 \end{equation}
-In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}$.
+In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathFeH_{\rm CGM}$.
 Previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
+We assume the Solar-scaled metallicity of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
 % We also investigate cases where the CGM is $\alpha$-enhanced, i.e., $\mathOFe_{\rm CGM}>0$.
@@
 The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
-All models use the \yZ{1} yield set and assume $\eta=0.2$.}
+All models use the same fiducial parameters as the $R_{\rm gal}=8\kpc$ ring in the multi-zone models, with \yZ{1} and $\eta=0.2$.
+The black lines represent the same set of parameters in each panel.}
     \label{fig:twoinfall-parameters}
@@
 Previous studies have adopted a wide range of parameters for Equation \ref{eq:twoinfall-ifr}.
-Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model.
+Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}.
 The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
@@
 This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
-We also run models with a linear prescription and with a uniform value for $\tau_2$ and find little difference in our key results.
+We have also run models with a linear prescription and with a uniform value for $\tau_2$ and have found little difference in our key results.
 
@@
 
-The Milky Way's last major merger with the dwarf galaxy dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018} has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
+The Milky Way's last major merger with the dwarf galaxy, dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018}, has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
 Our fiducial value of $t_{\rm max}=4.2\Gyr$ places the start of the formation of the thin disk close to the GSE merger (within uncertainties), which likely occurred $\sim10\Gyr$ ago \citep[e.g.,][]{helmi_merger_2018,gallart_uncovering_2019,naidu_reconstructing_2021,woody_rapid_2025}.
+However, recent arguments suggest that the GSE merger would not have led to two-infall-like evolution because the mass ratio is too low to produce sufficient dilution \citet{orkney_milky_2025}.
 
 We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
-The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus.
+The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus, since they are one-zone models.
 In our multi-zone models, most of the high-$\alpha$ stars present in the Solar neighborhood have migrated from the inner Galaxy.
@@
 \end{equation}
-where we adopt $\sigma_{\rm RM8}=2.68\kpc$ as the fiducial value for the strength of radial migration.
+where we adopt $\sigma_{\rm RM8}=2.68\kpc$ as the fiducial value for the strength of radial migration from \citet{dubay_galactic_2024}.
 This is smaller than the value of $\sigma_{\rm RM8}=3.6\kpc$ found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.
@@
 \begin{equation}
-    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big),
+    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)\,
+    {\rm \citep{spitzer_dynamics_1942}},
     \label{eq:sech-pdf}
@@
 We note that the final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
-
 The parameters of Equations \ref{eq:radial-migration} and \ref{eq:scale-height} were chosen to fit the stellar migration patterns in the {\tt h277} hydrodynamical simulation \citep{christensen_implementing_2012}.
@@
 This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
-So, a significant fraction of SN Ia progenitors born in a given zone will enrich a different region of the Galaxy.
+Therefore, a significant fraction of SN Ia progenitors born in a given zone will enrich a different region of the Galaxy.
 
@@
 
-\subsection{Dilution \& Approach to Equilibrium}
-\label{sec:age-abundance}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{figures/abundance_evolution_yields.pdf}
-    \caption{Stellar age--abundance relations predicted by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
+\subsection{Dilution \& Re-enrichment}
+\label{sec:age-abundance}\begin{figure}
+    \centering
+    \includegraphics[width=\onecolumn]{figures/yield_outflow.pdf}
+    \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors.
+Table \ref{tab:yields} presents the population-averaged yields for each model.
+The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
+The black points with error bars indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
+    \label{fig:yield-outflow}
+\end{figure}
+
+Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions of mono-age populations in the Solar annulus.
+As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
+In agreement with recent work (see discussion in Section \ref{sec:introduction}), the trend with age is interestingly flat.
+[O/H] and [Fe/H] increase by $0.1-0.2\dex$ in the $\sim6-8\Gyr$ range of ages relative to young stars, likely due to metal-rich stars migrating outward from the inner Galaxy where the surface densities are higher.
+
+We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models at $R_{\rm gal}=8\kpc$ on Figure \ref{fig:yield-outflow} for comparison.
+The models are in broad agreement with each other and with the data at lookback times of $\lesssim5\Gyr$.
+At ages of $\sim5-8\Gyr$, the models appear to be in tension with the data, underpredicting the metallicities of the observed stars by up to half an order of magnitude.
+The low metallicities in the models are a natural consequence of the dilution associated with the second infall event.
+This discrepancy is potentially mitigated by the higher $y/Z_\odot$ models, which re-enrich more rapidly; signatures of substantial dilution in this scenario may be washed out by age uncertainties.
+However, these models exacerbate tensions with the age--[O/Fe] relation because the O abundance can grow by a larger factor before enrichment from second-infall SNe Ia becomes important, making the $\alpha$-enhancement from the ensuing starburst more pronounced.
+When each panel is considered, none of our models provide a good match to these age trends.
+Figure \ref{fig:yield-outflow} illustrates a point that will arise as a theme throughout the remainder of this paper, which is that the signatures of a substantial dilution event and subsequent re-enrichment, characteristic of the two-infall scenario, are simply not present in the observed age--abundance trends.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\onecolumn]{figures/abundance_evolution_yields.pdf}
+%     \caption{Stellar age--abundance relations predicted by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
@@
 {\bf Key takeaway:} Both models feature a major dilution event at a lookback time of 9 Gyr, and for model (a) the dilution persists throughout much of the thin disk epoch.}
-    \label{fig:abundance-evolution-yields}
-\end{figure}
-
-The dilution effect discussed in Section \ref{sec:yields} is clearly seen in the multi-zone model results.
-Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations predicted by models which assume different yield and outflow scales, \yZ{1} and \yZ{2}, and the fiducial parameters (Table \ref{tab:multizone-parameters}).
-The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and non-zero abundance evolution at late times where the data show very little abundance evolution.
-The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed on Fe production from SNe Ia.
-The \yZ{2} yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound post-$t_{\rm max}$, producing a much flatter abundance curve at late times.
+%     \label{fig:abundance-evolution-yields}
+% \end{figure}
+
+% The dilution effect discussed in Section \ref{sec:yields} is clearly seen in our multi-zone model results.
+Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations predicted by models assuming different yield and outflow scales, \yZ{1} and \yZ{2}, and the fiducial parameters (Table \ref{tab:multizone-parameters}).
+The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and noticeable abundance evolution at late times where the data show very little abundance evolution.
+The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed by SNe Ia.
+The \yZ{2} yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound, producing a much flatter abundance curve at late times.
 However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is steeper than the data, especially for ages $\sim4-8\,{\rm Gyr}$.
@@
     \includegraphics[width=0.9\textwidth]{figures/abundance_evolution_params.pdf}
-    \caption{Stellar age--abundance relations in the Solar annulus produced by select multi-zone models with \yZ{1}.
-The layout is similar to Figure \ref{fig:abundance-evolution-yields}.
+    \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}). 
+    % The layout is similar to Figure \ref{fig:abundance-evolution-yields}. 
+    Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
+A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
+The black curve plots the ISM abundance at $R_{\rm gal}=8\kpc$ over time.
+The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
+Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
     Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
-{\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
+{\bf Key takeaway:} Models with pre-enriched infall (c) or a higher thick-to-thin disk ratio (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
     \label{fig:abundance-evolution-params}
@@
 The problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
+The dilution of the ISM then gets baked into the stellar abundance record.
+Figure \ref{fig:abundance-evolution-params} shows stellar age--abundance relations predicted by models with \yZ{1}.
+The model with the fiducial parameters (column (a); see Table \ref{tab:multizone-parameters}) shows similar discrepancies with the \citet{leung_variational_2023} age--[O/H] relation as in Figure \ref{fig:yield-outflow}.
+% a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and noticeable abundance evolution at late times where the data show very little abundance evolution.
+The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed by SNe Ia.
+Note that we scatter simulated data points according to the median age and abundance errors in Table \ref{tab:uncertainties}, so the blurring impact of these statistical errors is incorporated in the model.
+The solid black curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
+Despite the effects of radial migration and statistical errors, the stellar populations mostly scatter around this gas phase curve, at least for $\tau\lesssim9\Gyr$.
+
 We next attempt to mitigate the dilution and late-time evolution problems for the empirical (\yZ{1}) yield scale. 
-Figure \ref{fig:abundance-evolution-params} shows the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the metallicity of the infalling gas $\mathXH_{\rm CGM}$, and (d) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$.
-
-The observed rise in the median metallicity of stars with ages of $\sim4-10\,{\rm Gyr}$ could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the dense inner metal-rich regions of the Galaxy \citep{feuillet_age-resolved_2018}.
-Although our fiducial model does include a prescription for radial migration, the majority of stars in that age range in Figure \ref{fig:abundance-evolution-yields} still have sub-Solar abundances.
-Therefore, column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ and a stronger migration prescription of $\sigma_{\rm RM8}=5\kpc$.
-As a result, the stars which make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution for any given age.
-However, even though this prescription is much stronger than the estimates of, e.g., \citet{frankel_measuring_2018}, the model still significantly under-predicts the metallicity of $\sim4-9\,{\rm Gyr}$ old stars.
+The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the metallicity of the infalling gas $\mathXH_{\rm CGM}$, and (d) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$.
+
+The observed rise in the median metallicity of stars in the $6-10\Gyr$ age range could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the metal-rich inner Galaxy \citep{feuillet_age-resolved_2018}.
+Column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ and a stronger migration prescription of $\sigma_{\rm RM8}=5\kpc$.
+As a result, the stars that make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution at fixed age.
+Even though this prescription is extreme compared to the estimates of, e.g., \citet{frankel_measuring_2018}, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
 
@@
 Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
-The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, because the enriched gas accretion imposes a lower limit on the metallicity of the outermost regions, from which the stars of the low-metallicity tail in the Solar neighborhood are drawn.
+The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced since the accreting gas is less chemically different from the ISM, diminishing the effects of dilution.
 The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity---an effect which can be compensated by a slightly increased value of $\eta$.
@@
 Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger that the fiducial value, $f_\Sigma(R_\odot)=0.5$.
-This is higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
+This choice places the ratio higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase.
 The model produces the best agreement with the observed age--[Fe/H] relation (second row).
-However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting less evolution in [O/Fe] over the past $\sim9$ Gyr than observed by $\approx0.1$ dex.
-
-Overall, no modification to the \yZ{1} model is able to completely overcome both the dilution and late-time evolution issues.
-Pre-enrichment of the accreted gas and a higher disk mass ratio can reduce the discrepancy with the data, but they cause issues of their own in the age--[O/Fe] plane.
+However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting a trend much flatter than observed, underpredicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.
+
+Overall, no modification to the \yZ{1} model is able to completely overcome the issues that dilution and re-enrichment naturally face when confronted with a flat age--metallicity relation.
+Pre-enrichment of the accreted gas and a higher disk mass ratio can reduce the discrepancy with the data, but these options introduce new issues in the age--[O/Fe] plane.
 
@@
 Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the \yZ{1} and \yZ{2} models with the fiducial parameters.
-% We adopt pre-enriched infall ($\mathFeH_{\rm CGM}=-0.7$), stronger radial migration ($\sigma_{\rm RM8}=3.6$ kpc), and a higher disk mass ratio ($f_\Sigma(R_\odot)=0.25$) because these parameters were able to improve agreement with observations in previous sections.
-For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because of large systematic uncertainties for the oldest stars, as discussed in Section \ref{sec:observational-sample}.
-% The two-infall model predicts a very broad MDF for ages $>10$ Gyr because of the rapid enrichment of the ISM during the first infall epoch.
-
-The results of both models in Figure \ref{fig:mdf-evolution} show a clear evolutionary trend at all radii.
-The mode of the MDF shifts consistently to the right when moving from older to younger stars.
+For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in Section \ref{sec:observational-sample}.
+
+The predictions of both models in Figure \ref{fig:mdf-evolution} show a clear trend in [Fe/H] with age at all radii.
+The MDF shifts consistently toward high metallicity when moving from older to younger stars.
 The distance between the $1-2\Gyr$ and $2-4\Gyr$ age bins is smaller for the \yZ{2} model because of the faster approach to equilibrium (see also Figure \ref{fig:abundance-evolution-yields}).
-In the Solar annulus (center column), the mode of the $6-8\Gyr$ age MDF is $0.3\dex$ lower than the present-day metallicity in the \yZ{2} model, and $0.4\dex$ lower in the \yZ{1} model.
-
-In contrast, the APOGEE data show remarkably little evolution over the past $\sim8\Gyr$ at all radii.
-Row (c) of Figure \ref{fig:mdf-evolution} shows that the MDF broadens with age, but its peak does not shift much over the past $\sim8\Gyr$.
+In the Solar annulus (center column), the peak of the $6-8\Gyr$ old MDF is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
+
+In contrast, the APOGEE data show remarkably little evolution in [Fe/H] up to ages of $\sim8\Gyr$ at all radii.
+Row (c) of Figure \ref{fig:mdf-evolution} shows that the MDF broadens with age, but its peak remains constant across this range.
 The mode [Fe/H] for the youngest stars (indicated by the vertical blue dotted line) is nearly the same as for the $6-8\Gyr$ old stars.
-Inward of the Solar annulus, the MDF skews more to lower [Fe/H], but its mode does not shift by more than $\sim0.1\dex$.
+At $R_{\rm gal}<7\kpc$, the MDF skews to lower [Fe/H] more noticeably with age, but its mode does not shift by more than $\sim0.1\dex$.
 It is difficult to draw conclusions about the outer Galaxy because the mode [Fe/H] is close to the metallicity cut at $\mathFeH>-0.4$ for luminous giants (represented by the vertical gray dashed line), which comprise the majority of stars in the sample at that distance.
-The remarkable consistency of the MDF over time, in agreement with the equilibrium scenario of \citet{johnson_milky_2024}, contrasts with the predictions of our fiducial models.
+The remarkable consistency of the MDF over time, the result that motivated the equilibrium scenario proposed by \citet{johnson_milky_2024}, contrasts with the predictions of our fiducial models.
 
 The oldest age bin in Figure \ref{fig:mdf-evolution} shows distinct behavior in both the models and data.
-The $8-10\Gyr$ age bin spans both the tail end of the thick disk phase and the beginning of the thin disk, so the MDF is bimodal: the higher peak consists of $>9\Gyr$ old stars, and the lower peak $8-9\Gyr$ old stars (post-dilution phase).
+The $8-10\Gyr$ age bin spans both the tail end of the thick disk phase and the beginning of the thin disk, so the MDF is bimodal.
+In the models, the higher peak consists of $>9\Gyr$ old stars (pre-dilution), and the lower peak $8-9\Gyr$ old stars (post-dilution).
 Intriguingly, the APOGEE MDF in that age bin is also bimodal in all but the outer-most radial bin, with peaks at $\mathFeH\approx-0.3$ and $+0.3$ independent of the location in the Galaxy.
-While data and model show qualitatively similar behavior, they actually represent different populations.
-In the model, the metal-rich peak is composed of thick-disk stars while the metal-poor peak marks the formation of the thin disk.
-In the data, the metal-rich peak are all low-$\alpha$ stars, while the metal-poor peak is the locus of the high-$\alpha$ sequence \textemdash a reversal of the model predictions.
+While the data and the models show qualitatively similar behavior, they actually represent different populations.
+In the data, the metal-rich peak are all low-$\alpha$ stars, while the metal-poor peak is the locus of the high-$\alpha$ sequence---a reversal of the model predictions.
 
@@
 The two-infall model explains the chemical evolution of the thin disk through the low-$\alpha$ loop (see discussion in Section \ref{sec:parameter-selection}).
-However, inspection of the marginal [O/Fe] distributions in, e.g., Figure \ref{fig:yield-outflow} reveals a different morphology of the low-$\alpha$ sequence: the two-infall model predicts two peaks in [O/Fe] in the thin disk where the data show only one.
-The location of the second peak, at intermediate [O/Fe], varies depending on the yields (Figure \ref{fig:yield-outflow}) and infall parameters (Figure \ref{fig:twoinfall-parameters}), but is always present.
+However, inspection of the marginal [O/Fe] distributions in Figure \ref{fig:ofe-feh-density} reveals a different morphology of the low-$\alpha$ sequence: the two-infall model predicts two peaks in [O/Fe] in the thin disk where the data show only one.
+The location of the second peak, at intermediate [O/Fe], varies depending on the yields and model parameters (Figure \ref{fig:twoinfall-parameters}), but is always present.
 This morphology remains essentially consistent in our multi-zone models as well, despite the inclusion of radial mixing and vertical dispersion of stars.
@@
 Both the models with $y/Z_\odot=1$ and $y/Z_\odot=2$ predict an over-density of stars near the abundance turn-over ($\mathFeH\approx-0.3$, $\mathOFe\approx0.1-0.2$), which is not seen in the APOGEE sample.
-% This over-density occurs because the overall rate of chemical evolution slows down $\sim2\,{\rm Gyr}$ after the second infall, and at the same time the delayed enrichment from SNe Ia reverses the evolution of [O/Fe].
 The local maximum in $dN_\star/d\mathOFe$ comprises stars which formed in the second infall before SN Ia enrichment began to drive down [O/Fe].
-This is a generic prediction of {\it any} two-infall model regardless of its specific parameters, though its impact can be mitigated through parameter choices which act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow} or the models with longer $\tau_2$ in Figure \ref{fig:twoinfall-parameters}.
-
-Additionally, the shape of the low-$\alpha$ sequence in the model results (a concave-down ``comma'') is clearly different from the data (a concave-up ``swoosh'').
+This prediction should therefore arise in {\it any} two-infall model regardless of its specific parameters, but its impact can be mitigated through parameter choices that act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow} or the models with longer $\tau_2$ in Figure \ref{fig:twoinfall-parameters}.
+
+Additionally, the shape of the low-$\alpha$ sequence predicted the model results (a concave-down ``comma'') is different from the data (a concave-up ``swoosh'').
 This is a subtle distinction, on the $\sim0.05\dex$ level in [O/Fe].
 We have not accounted for the APOGEE selection function in our models, but there is no evident reason for observational effects to produce this difference in morphology.
-This problem is not unique to the two-infall scenario: it results from the concave-down track of the abundance evolution, and has stymied other models as well \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
-Nevertheless, it is worth mentioning because the two-infall scenario is otherwise quite successful at reproducing the local stellar distribution in [O/Fe]--[Fe/H] space.
+This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and has stymied other models as well \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
+The two-infall scenario is otherwise fairly successful at reproducing the local stellar distribution in [O/Fe]--[Fe/H] space.
 
@@
 
-\subsubsection{The [O/Fe] Distribution: Two or Three Peaks?}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{src/tex/figures/ofe_distribution_yields.pdf}
-    \caption{Normalized stellar [O/Fe] distributions produced by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
+\subsubsection{The [O/Fe] Distribution}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\onecolumn]{src/tex/figures/ofe_distribution_yields.pdf}
+%     \caption{Normalized stellar [O/Fe] distributions produced by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
 Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row.
@@
 {\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent in the \yZ{2} model at mid to high latitudes.}
-    \label{fig:ofe-distribution-yields}
-\end{figure}
-
-The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution, which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+%     \label{fig:ofe-distribution-yields}
+% \end{figure}
+
+% The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution, which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
 We previously noted this feature in \citet{dubay_galactic_2024}.
@@
 
-% \todo{Discuss why we divided Figures \ref{fig:ofe-distribution-yields} and \ref{fig:ofe-distribution-parameters} into $|z|$ bins: (1) pattern changes as a function of midplane distance, and (2) we don't have to worry so much about correcting the APOGEE data to rebalance between the thin and thick disk fields.}
-
 \begin{figure*}
@@
     \includegraphics[width=\textwidth]{src/tex/figures/ofe_distribution_params.pdf}
-    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e).
-The layout is similar to Figure \ref{fig:ofe-distribution-yields}.
-Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
+    \caption{Normalized stellar [O/Fe] distributions predicted by multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). 
+    % The layout is similar to Figure \ref{fig:ofe-distribution-yields}. 
+    Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row.
+Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
+The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
+For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
+    Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$
+    % (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); 
+    {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
 {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
@@
 
-In Figure \ref{fig:ofe-distribution-parameters}, we show the result of our attempts to mitigate the intermediate-$\alpha$ peak discrepancy for the \yZ{2} yield set in a few different ways, namely by reducing the size of the thin disk loop seen in panel (b) of Figure \ref{fig:ofe-feh-density}.
+In Section \ref{sec:abundance-distributions}, we showed that our high-yield models predict {\it three} peaks in the [O/Fe] distribution, which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
+Here, we attempt to mitigate the intermediate peak through several parameter choices.
+% In Figure \ref{fig:ofe-distribution-parameters}, we show the result of our attempts to mitigate the intermediate-$\alpha$ peak discrepancy for the \yZ{2} yield set in a few different ways, namely by reducing the size of the thin disk loop seen in panel (b) of Figure \ref{fig:ofe-feh-density}.
+Figure \ref{fig:ofe-distribution-parameters} compares [O/Fe] distributions from across the Galactic disk predicted by models with \yZ{2}.
+We present the distributions in multiple bins of $|z|$ as well as $R_{\rm gal}$ because the observed pattern varies as a function of midplane distance, and because the APOGEE selection function over-emphasizes high-$|z|$, and therefore high-$\alpha$, stars in the full sample \citep[see Figure 5 from][]{vincenzo_distribution_2021}.
+The fiducial model (column a) predicts a high density of stars at $\mathOFe\approx+0.2$ where the data show a trough.
+The peak is most pronounced in the inner disk ($R_{\rm gal}=3-5\kpc$) because of the shorter infall timescale (see Figure \ref{fig:twoinfall-parameters}).
+
 First, we substitute our fiducial SN Ia DTD with a simple power-law,
@@
 
-Figure \ref{fig:ofe-feh-best} presents the stellar [O/Fe]--[Fe/H]--age distributions as a function of $R_{\rm gal}$ and $|z|$ predicted by the best multi-zone model.
-The model is generally successful at reproducing the observed distribution of stars in the [O/Fe]--[Fe/H] plane, especially in the inner Galaxy and close to the midplane (panels along the left and bottom sides of the figure, respectively).
-However, the predicted high-$\alpha$ sequence is less concentrated than in the data, and its presence is still significant even in the outer Galaxy---likely a consequence of the stronger migration prescription and higher thick-to-thin disk ratio.
-In general, the predicted distributions do not align with the data quite as well at large midplane distances ($1\leq|z|<2\kpc$), but this may partly be due to our prescription for vertical heating (see Section \ref{sec:migration}).
+Figure \ref{fig:ofe-feh-best} shows the stellar [O/Fe]--[Fe/H] distributions in different ranges of $R_{\rm gal}$ and $|z|$ color-coded by age as predicted by the best model.
+This model is generally successful at reproducing the observed distribution, especially in the inner Galaxy and close to the midplane.
+However, the predicted high-$\alpha$ sequence has a significant presence even in the outer Galaxy---likely a consequence of the stronger migration prescription and higher thick-to-thin disk ratio.
+In general, the predicted distributions do not align with the data as well at large midplane distances ($1\leq|z|<2\kpc$), but this may partly be due to our prescription for vertical heating (see Section \ref{sec:migration}).
 
@@
 
-The top row of Figure \ref{fig:lmr-ages} presents the median stellar age as a function of [O/Fe] and [Fe/H] for two multi-zone models and APOGEE.
-While the models predict a fairly accurate distribution of stars in abundance space, especially for the low-$\alpha$ population, the stellar age patterns are obviously quite different.
+The top row of Figure \ref{fig:lmr-ages} presents the median stellar age as a function of [O/Fe] and [Fe/H] for two multi-zone models and in APOGEE.
+While the models predict a fairly accurate distribution of stars in abundance space, especially for the low-$\alpha$ population, the stellar age patterns are starkly different.
 In both the \yZ{1} and \yZ{2} models, there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
@@
 
-We further highlight the discrepant age patterns in the bottom panels of Figure \ref{fig:lmr-ages}, which compare the overall stellar age distribution against that of the locally metal rich (LMR) stars, defined here as $\mathFeH\ge+0.1$.
-% The precise location of the cut matters little, as we observe the same behavior for cuts ranging from $+0.05$ to $+0.2$ dex. 
-For APOGEE, the distributions are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
-Our two-infall models predict an age distribution for the overall sample that is similar to the data, but for LMR stars, both models predict a distinctly bimodal age distribution.
-There is a large contribution from the young, metal-rich end of the second infall, and a contribution from the old, metal-rich end of the first, but there are few stars in between.
+We further highlight the discrepant age patterns in the bottom panels of Figure \ref{fig:lmr-ages}, which compare the overall stellar age distribution against that of the locally metal rich (LMR) stars, defined here as $\mathFeH\ge+0.1$.\footnote{
+    While the amplitude of the peaks is sensitive to the precise location of the LMR cutoff, the dearth of intermediate-age stars is robust to adjustments of $\pm0.05\dex$.
+} For APOGEE, the distributions are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
+Our two-infall models predict an overall age distribution that is similar to the data, but both models predict a distinctly bimodal age distribution for LMR stars.
+The two populations represent the metal-rich endpoints of the two successive infall epochs.
 The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
-While the amplitude of the peaks is sensitive to the precise location of the LMR cutoff, the dearth of intermediate-age stars is robust to adjustments of $\pm0.05\dex$.
-
-It is difficult to predict a qualitatively different age distribution with the available parameter space.
-Pre-enriching the accreted gas shifts the equilibrium metallicity higher, increasing the proportion of young stars to old.
-Stronger radial migration similarly shifts more young stars into the LMR region.
-On the other hand, increasing the local thick-to-thin disk mass ratio produces more old, thick disk stars.
-None of these adjustments substantially increase the proportion of intermediate-age stars, which are the dominant component of the LMR population observed in APOGEE.
+It is difficult to predict a unimodal age distribution with the available parameter space.
+A dearth of intermediate-age, high-metallicity stars is a natural outcome of a substantial dilution event, which is a defining feature of the two-infall scenario.
+None of the adjustments that we explored in Figure \ref{fig:abundance-evolution-params} substantially increase the proportion of intermediate-age stars.
 
@@
 Our results show that the APOGEE stellar age catalogs pose several challenges to the two-infall scenario.
-The [O/Fe] distribution was the easiest to resolve using the parameter space we explored, either by pre-enrichment of the accreted gas or a higher thick-to-thin disk mass ratio.
-These parameters also allowed us to mitigate, but not completely resolve, the issue of dilution.
-However, the predicted age distributions could not be reconciled with the data using any of the parameters we explored.
+The [O/Fe] distribution was the observable with the easiest discrepancy to resolve using the parameter space we explored, either by pre-enrichment of the accreted gas or a higher thick-to-thin disk mass ratio.
+These parameters also allowed us to mitigate, but not completely resolve, the issues with the age--abundance relations caused by dilution.
+The predicted age distributions could not be reconciled with the data using any of the variations we explored.
 In the remainder of this section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.
-
-% \subsection{Comparison with Previous Literature}
-
-% \subsection{The Empirical Yield Scale}
-
-% The \yZ{1} empirical yield scale already has difficulties matching the local age--metallicity relation \citep[see also][]{johnson_milky_2024}, but the problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
 
@@
     % \item The equilibrium scenario of chemical evolution, if correct, places stricter limits on the two-infall model than other evolutionary models.
+    \item Adjusting the strength of radial migration naturally affects the scatter in the age--metallicity relation but does not affect the median age.
 \end{itemize}

### 2025-07-01 src/tex/ms.tex

@@
 Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey (SDSS; \todo{Hawkins et al.
-in prep}).
+2025, in preparation}).
 
@@
 
-Our second age catalog utilizes the [C/N]--age relation calibrated by \todo{Roberts et al.\ (in prep)} for red giant branch (RGB) and red clump stars.
+Our second age catalog utilizes the [C/N]--age relation calibrated by \todo{Roberts et al.\ (2025, in preparation)} for red giant branch (RGB) and red clump stars.
 The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
@@
 also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
-The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \todo{Roberts et al.\ (in prep)}, the propagated errors underestimate the true age dispersion, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
+The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \todo{Roberts et al.\ (2025, in preparation)}, the propagated errors underestimate the true age dispersion, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
 With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
@@
 
+\subsection{The Star Formation Law}
+\label{sec:sf-law}
+
+The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^N$, with $N=1.5$ following \citet{kennicutt_global_1998}.
+Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
+%     \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
+All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
+%     \label{fig:sfe-prefactor}
+% \end{figure}
+
+In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
+\begin{equation}
+    \label{eq:sf-law}
+    \tau_\star = 
+    \begin{cases}
+        \varepsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
+        \varepsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
+    \end{cases}
+\end{equation}
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citep{leroy_star_2008}.
+Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through the pre-factor $\varepsilon$:
+\begin{equation}
+    \label{eq:sfe-prefactor}
+    \varepsilon(t) = 
+    \begin{cases}
+        0.5, & t < t_{\rm max} \\
+        1.0, & t \ge t_{\rm max}.
+    \end{cases}
+\end{equation}
+A lower value of $\varepsilon(t<t_{\rm max})$ leads to more efficient star formation, and therefore more rapid enrichment, during the first infall epoch.
+However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
+We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature, though we find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
+To guard against over-correcting the SFE in the early Galaxy, we have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
+
 \subsection{The Gas Supply}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\onecolumn]{figures/star_formation_history.pdf}
+    \caption{(a) The infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
+Each panel plots the history for six different zones of width $\delta R_{\rm gal}=0.1\kpc$, color-coded by Galactocentric radius.}
+    \label{fig:sfh}
+\end{figure}
+
+Figure \ref{fig:sfh} plots the star formation history of several different zones from our fiducial model with $y/Z_\odot=1$.
+In the inner Galaxy, the infall rate $\dot\Sigma_{\rm in}$ is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
+In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
+The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a maximum of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
+
 The thick-to-thin disk density ratio is especially important for our GCE models as it controls the quantity of gas accreted during each infall epoch.
@@
 
-% \begin{figure*}
-%     \centering
-%     \includegraphics{figures/spitoni_comparison.pdf}
-%     \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021} at three different galactocentric radii.
-All models use the $y/Z_\odot=1$ yield set and corresponding outflow prescription (see Table \ref{tab:yields}).
-The time markers and marginal panels are the same as in Figure \ref{fig:twoinfall-parameters}.
-We also include a 2-D heatmap of the APOGEE stellar abundances in each panel for reference.
-APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<10$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.}
-%     \label{fig:spitoni-comparison}
-% \end{figure*}
-
-% \todo{Highlight differences between our models and those of \citet{spitoni_apogee_2021} in Figure \ref{fig:spitoni-comparison}.}
-
-\subsection{The Star Formation Law}
-\label{sec:sf-law}
-
-The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^N$, with $N=1.5$ following \citet{kennicutt_global_1998}.
-Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
-%     \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
-All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
-%     \label{fig:sfe-prefactor}
-% \end{figure}
-
-In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
-\begin{equation}
-    \label{eq:sf-law}
-    \tau_\star = 
-    \begin{cases}
-        \varepsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
-        \varepsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
-    \end{cases}
-\end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citep{leroy_star_2008}.
-Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through the pre-factor $\varepsilon$:
-\begin{equation}
-    \label{eq:sfe-prefactor}
-    \varepsilon(t) = 
-    \begin{cases}
-        0.5, & t < t_{\rm max} \\
-        1.0, & t \ge t_{\rm max}.
-    \end{cases}
-\end{equation}
-A lower value of $\varepsilon(t<t_{\rm max})$ leads to more efficient star formation, and therefore more rapid enrichment, during the first infall epoch.
-However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
-We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature, though we find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
-To guard against over-correcting the SFE in the early Galaxy, we have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{figures/star_formation_history.pdf}
-    \caption{(a) The infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
-Each panel plots the history for six different zones of width $\delta R_{\rm gal}=0.1\kpc$, color-coded by Galactocentric radius.}
-    \label{fig:sfh}
-\end{figure}
-
-Figure \ref{fig:sfh} plots the star formation history of several different zones from our fiducial model with $y/Z_\odot=1$.
-In the inner Galaxy, the infall rate $\dot\Sigma_{\rm in}$ is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
-In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
-The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a maximum of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
-
 \subsection{Stellar Migration}
@@
 \subsection{Dilution \& Re-enrichment}
-\label{sec:age-abundance}\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{figures/yield_outflow.pdf}
+\label{sec:age-abundance}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\onecolumn]{figures/gas_abundance_evolution.pdf}
     \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors.
@@
 Our two-infall models predict an overall age distribution that is similar to the data, but both models predict a distinctly bimodal age distribution for LMR stars.
-The two populations represent the metal-rich endpoints of the two successive infall epochs.
+The two populations reflect the metal-rich endpoints of the two successive infall epochs.
 The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
@@
 
-% Radial gas flows allow GCE models to produce a radial metallicity gradient in the absence of mass-loaded outflows.
-Radial gas flows introduce multiple variables, such as the speed, direction, and angular momentum of the flow, which remain relatively unconstrained in the MW.
-\citet{spitoni_effects_2011} studied the effects of radial gas flows in the two-infall scenario and found that an inward radial flow with velocity $v_R\sim0-4\kms$ can steepen the radial abundance gradient to match observations.
-Subsequent studies \citep{palla_chemical_2020,palla_mapping_2024} implemented a $\sim-1\kms$ radial gas flow in order to reproduce the abundance gradient in the absence of Galactic outflows.
-Confirming these results, \todo{Johnson et al.
-(in prep)} find that an inward gas flow with a flat velocity profile has a similar effect on the radial metallicity gradient as the exponential outflow prescription in our models.
-We believe that switching from outflows to radial gas flows would not solve any of our models' issues regarding the age--abundance relation, [O/Fe] distributions, or stellar age distributions.
-
-% Some two-infall studies \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.
-\citet{spitoni_effects_2011} find that a two-infall model of the disk without gas exchange produces a radial metallicity gradient which is too shallow.
-They implement an inward radial gas flow on the order of $\sim0-4$ km s$^{-1}$ which varies with radius, and find that it improves agreement with the observed gradient.
-However, they found that a variable star formation efficiency with radius in combination with a gas density threshold for star formation could also reproduce the observed gradient without radial flows.
+Radial gas flows are a potential alternative to the outflow prescription that we use in this paper.
+Within the two-infall paradigm, \citet{spitoni_effects_2011} found that inward flow velocities of a $\sim$ few $\kms$ can steepen the predicted radial metallicity gradient to match observations.
+Similarly, \citet{palla_chemical_2020,palla_mapping_2024} used an inward flow with a speed of $\sim1\kms$ to reproduce the observed radial metallicity profile in the absence of Galactic outflows.
+Johnson et al.
+(2025, in preparation) considered several possible scenarios for the processes that drive radial gas flows.
+Their findings support these previous arguments that radial gas flows should regulate the overall metal abundance and radial gradient, even beyond the two-infall scenario.
+
+In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2024} demonstrated to improve agreement with age trends across the Galactic disk.
+Johnson et al.
+(2025, in preparation) found similar results for radial gas flows with velocities that are relatively constant in both Galactocentric radius and time.
+At least one radial gas flow scenario therefore has similar effects on metal enrichment as our outflow prescription.
+However, the outflow is simpler in implementation; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
+This approach allows us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
+A radial gas flow requires at least one assumption about the processes that drive the flow and generally do not afford the same level of flexibility.
+We have therefore focused on models with outflows in this paper for the sake of simplicity, and we clarify that some, but not all, radial gas flow models should have similar effects.
 

### 2025-07-03 src/scripts/smooth_vs_twoinfall.py
update smooth-vs-twoinfall plot

@@ -16,49 +16,41 @@ from multizone.src.yields import yZ1
 from multizone.src import models, outflows
 from _globals import ONEZONE_DEFAULTS
 
-OUTPUT_NAMES = [
-    'yZ1/fiducial/diskmodel',
-    'yZ2/fiducial/diskmodel'
-]
-LABELS = [
-    r'(a) $y/Z_\odot=1$',
-    r'(b) $y/Z_\odot=2$',
-    '(c) APOGEE'
-]
-FEH_LIM = (-1.1, 0.6)
+FEH_LIM = (-1.1, 1.1)
 OFE_LIM = (-0.15, 0.55)
 GALR_LIM = (7, 9)
 ABSZ_LIM = (0, 2)
 GRIDSIZE = 30
-RADII = [4, 6, 8, 10, 12]
 ZONE_WIDTH = 2
 
 
 def main(style='paper'):
     # Setup figure
     plt.style.use(paths.styles / f'{style}.mplstyle')
-    fig, axs = plt.subplots(
-        2, sharex=True, sharey=True, 
-        figsize=(ONE_COLUMN_WIDTH, 1.6 * ONE_COLUMN_WIDTH),
-        gridspec_kw={'hspace': 0.}
+    plt.rcParams['axes.prop_cycle'] = plt.cycler(
+        'color', paultol.highcontrast.colors)
+    fig, ax = plt.subplots(
+        sharex=True, sharey=True, 
+        figsize=(ONE_COLUMN_WIDTH, 0.6 * ONE_COLUMN_WIDTH),
+        gridspec_kw={'hspace': 0.},
+        tight_layout=True
     )
-    axs[0].set_xlim(FEH_LIM)
-    axs[0].set_ylim(OFE_LIM)
+    ax.set_xlim(FEH_LIM)
+    ax.set_ylim(OFE_LIM)
     
     # Plot APOGEE data
     apogee_sample = APOGEESample.load()
     apogee_solar = apogee_sample.region(galr_lim=(7, 9), absz_lim=(0, 2))
     cmap_name = 'binary'
-    for i, ax in enumerate(axs):
-        pcm = ax.hexbin(
-            apogee_solar('FE_H'), apogee_solar('O_FE'),
-            gridsize=GRIDSIZE,
-            extent=[FEH_LIM[0], FEH_LIM[1], OFE_LIM[0], OFE_LIM[1]],
-            cmap='binary', linewidths=0.2, 
-        )
[…]

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

@@
 The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
-Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
+Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
 We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.3$.
@@
     \includegraphics[width=\onecolumn]{figures/gas_abundance_evolution.pdf}
-    \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors.
-Table \ref{tab:yields} presents the population-averaged yields for each model.
+    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}).
 The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
-The black points with error bars indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
+The black points indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
+The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.
+    {\bf Key takeaway:} All models feature a major dilution event 9 Gyr ago, and the \yZ{1} model re-enriches the most slowly.}
     \label{fig:yield-outflow}
@@
 
-\subsection{The Local Abundance Topology}
+\subsection{The [O/Fe] Distribution}
 \label{sec:abundance-distributions}
@@
 
-\subsection{Global Abundance Distributions}
-\label{sec:disk-abundances}
-
-\subsubsection{The [O/Fe] Distribution}
+% \subsection{Global Abundance Distributions}
+% \label{sec:disk-abundances}
+
+% \subsubsection{The [O/Fe] Distribution}
 
@@
 
-\subsubsection{The Best Model}
+\subsection{The Best Model}
 \label{sec:ofe-feh-best}

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

@@
 Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000,spitoni_remind_2024}, although most GCE models in the literature benchmark against these observables \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figures/smooth_vs_twoinfall.pdf}
+    \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves).
+The two-infall model adopts the fiducial parameters according to Table \ref{tab:multizone-parameters}, while the smooth SFH adopts the parameters of the ``inside-out'' model of \citet{johnson_stellar_2021}.
+Both models assume the \yZ{2} yield scale (see Table \ref{tab:yields}).
+The 2-D histogram shows the number of stars from APOGEE DR17 in each bin of ([Fe/H], [O/Fe]).}
+    \label{fig:smooth-vs-twoinfall}
+\end{figure}
 

### 2025-07-03 src/scripts/smooth_vs_twoinfall.py
reverse color cycle

@@ -28,7 +28,7 @@ def main(style='paper'):
     # Setup figure
     plt.style.use(paths.styles / f'{style}.mplstyle')
     plt.rcParams['axes.prop_cycle'] = plt.cycler(
-        'color', paultol.highcontrast.colors)
+        'color', paultol.highcontrast.colors[::-1])
     fig, ax = plt.subplots(
         sharex=True, sharey=True, 
         figsize=(ONE_COLUMN_WIDTH, 0.6 * ONE_COLUMN_WIDTH),
@@ -129,7 +129,7 @@ def main(style='paper'):
     ax.set_xlabel('[Fe/H]')
     ax.set_ylabel('[O/Fe]')
 
-    plt.savefig(paths.figures / 'smooth_vs_twoinfall_yZ1')
+    plt.savefig(paths.figures / 'smooth_vs_twoinfall')
     plt.close()
 
 

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figures/smooth_vs_twoinfall.pdf}
+    \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves).
+The two-infall model adopts the fiducial parameters according to Table \ref{tab:multizone-parameters}, while the smooth SFH adopts the parameters of the ``inside-out'' model of \citet{johnson_stellar_2021}.
+Both models assume the \yZ{2} yield scale (see Table \ref{tab:yields}).
+The 2-D histogram shows the number of stars from APOGEE DR17 in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$) in each bin of ([Fe/H], [O/Fe]).}
+    \label{fig:smooth-vs-twoinfall}
+\end{figure}
+
 % \todo{Migration.} 
@@
 While the strength and speed of radial migration in the disk are not precisely measured, a single chemical evolution track need not explain the entire width of the local abundance distribution.
+Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against
 
@@
 Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000,spitoni_remind_2024}, although most GCE models in the literature benchmark against these observables \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figures/smooth_vs_twoinfall.pdf}
-    \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves).
-The two-infall model adopts the fiducial parameters according to Table \ref{tab:multizone-parameters}, while the smooth SFH adopts the parameters of the ``inside-out'' model of \citet{johnson_stellar_2021}.
-Both models assume the \yZ{2} yield scale (see Table \ref{tab:yields}).
-The 2-D histogram shows the number of stars from APOGEE DR17 in each bin of ([Fe/H], [O/Fe]).}
-    \label{fig:smooth-vs-twoinfall}
-\end{figure}
 

### 2025-07-03 src/scripts/ofe_distribution_params.py
update model order

@@ -16,14 +16,14 @@ from _globals import TWO_COLUMN_WIDTH, GALR_BINS, ABSZ_BINS
 OUTPUT_NAMES = [
     'yZ2/fiducial/diskmodel',
     'yZ2/dtd/powerlaw/diskmodel',
+    'yZ2/thick_thin_ratio/solar050/diskmodel',
     'yZ2/pre_enrichment/mh05_alpha00/diskmodel',
-    'yZ2/thick_thin_ratio/solar050/diskmodel'
 ]
 LABELS = [
     '(a)\nFiducial',
     '(b)\nPower-law DTD',
-    '(c)\n' + r'${\rm [X/H]}_{\rm CGM}=-0.5$',
-    '(d)\n' + r'$f_\Sigma(R_\odot)=0.5$',
+    '(c)\n' + r'$f_\Sigma(R_\odot)=0.5$',
+    '(d)\n' + r'${\rm [X/H]}_{\rm CGM}=-0.5$',
     '(e)\nAPOGEE'
 ]
 NBINS = 100

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

@@
 Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
-    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
-{\bf Key takeaway:} Models with pre-enriched infall (c) or a higher thick-to-thin disk ratio (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
+    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$.
+{\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
     \label{fig:abundance-evolution-params}
@@
 We next attempt to mitigate the dilution and late-time evolution problems for the empirical (\yZ{1}) yield scale. 
-The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the metallicity of the infalling gas $\mathXH_{\rm CGM}$, and (d) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$.
+The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$, and (d) the metallicity of the infalling gas $\mathXH_{\rm CGM}$.
 
@@
 
-Next, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
-Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
+Next, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger that the fiducial value, $f_\Sigma(R_\odot)=0.5$.
+This choice places the ratio higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
+Column (c) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase.
+The model produces the best agreement with the observed age--[Fe/H] relation (second row).
+However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting a trend much flatter than observed, underpredicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.
+
+Finally, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
+Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
 Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
@@
 This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.
-
-Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger that the fiducial value, $f_\Sigma(R_\odot)=0.5$.
-This choice places the ratio higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
-Column (d) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase.
-The model produces the best agreement with the observed age--[Fe/H] relation (second row).
-However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting a trend much flatter than observed, underpredicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.
 

### 2025-07-03 src/scripts/abundance_evolution_yields.py
minor plot tweaks

@@ -32,8 +32,8 @@ POSTER_LABELS = [
 ]
 # LABEL_PADS = [18, 18, 6, 6, 6]
 AXES_LIM = {
-    '[o/h]': (-1.2, 0.4),
-    '[fe/h]': (-1.2, 0.4),
+    '[o/h]': (-1.1, 0.4),
+    '[fe/h]': (-1.1, 0.4),
     '[o/fe]': (-0.15, 0.5),
     'age': (-1, 14.99)
 }
@@ -90,6 +90,7 @@ def compare_abundance_evolution(
         figsize=figsize,
         gridspec_kw={'hspace': 0, 'wspace': 0}
     )
+    fig.subplots_adjust(left=0.1, right=0.98)
     if label_pads == []:
         label_pads = [None] * len(output_names)
     # Add colorbar
@@ -106,11 +107,11 @@ def compare_abundance_evolution(
                           # scale colorbar width with figure width
                           width=cbar_width, pad=cbar_pad, 
                           labelpad=2, extend='both')
-    data_label = 'APOGEE data'
-    # data_label = {
-    #     'L23_AGE': 'APOGEE (NN ages)',
-    #     'CN_AGE': 'APOGEE ([C/N] ages)'
-    # }[age_col]
+    # data_label = 'APOGEE data'
+    data_label = {
+        'L23_AGE': 'APOGEE (NN ages)',
+        'CN_AGE': 'APOGEE ([C/N] ages)'
+    }[age_col]
 
     for j, output_name in enumerate(output_names):
         axs[0,j].set_title(labels[j], pad=label_pads[j])

### 2025-07-03 src/tex/ms.tex

@@
     % (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); 
-    {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$.
-{\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
+    {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$.
+{\bf Key takeaway:} For the \yZ{2} case, a higher thick-to-thin disk ratio or pre-enrichment of the accreted gas can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
     \label{fig:ofe-distribution-parameters}
@@
 
-Next, in model (c) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
+Next, in model (c) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
+This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates (see Section \ref{sec:sfh}).
+The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the other models.
+
+Finally, in model (d) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
 We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars.
@@
 We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
-% In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.
-
-Finally, in model (d) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
-This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates (see Section \ref{sec:sfh}).
-The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the previous models.
-In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \yZ{2} case.
+In summary, either an enhanced disk mass ratio or pre-enriched infall can improve agreement with the observed thin disk abundances for the \yZ{2} case.
 These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.

### 2025-07-03 src/scripts/ofe_feh_best.py
change colorscheme

@@ -22,7 +22,7 @@ import paths
 FEH_LIM = (-1.3, 0.7)
 OFE_LIM = (-0.199, 0.599)
 GALR_BINS = [3, 5, 7, 9, 11, 13]
-COLORMAP = 'Spectral_r'
+COLORMAP = 'jet'
 OUTPUT_NAME = 'yZ2/best/cgm07_ratio025_eta18_migr36/diskmodel'
 AGE_COL = 'CN_AGE' # for error forward-modeling
 

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/abundance_evolution_params.pdf}
+    \includegraphics[width=\linewidth]{figures/abundance_evolution_params.pdf}
     \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}).
-    % The layout is similar to Figure \ref{fig:abundance-evolution-yields}. 
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
@@
 For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
-The black curve plots the ISM abundance at $R_{\rm gal}=8\kpc$ over time.
-The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
+The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$ over time, and the black squares plot the median stellar abundance in in {2 Gyr}-wide age bins.
+The red line and points plot the median abundance for APOGEE stars in each age bin, and the shaded regions represent the 16th--84th abundance percentiles.
 Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
-    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$.
+    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$ and a higher mass-loading factor $\eta_\odot=0.6$.
 {\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}

### 2025-07-07 src/scripts/uncertainties.py
add script to generate uncertainties table

@@ -1,0 +1,49 @@
+"""
+This script generates a LaTeX table of the median measurement uncertainties
+for the APOGEE DR17 sample.
+"""
+
+import pandas as pd
+import paths
+from apogee_sample import APOGEESample
+
+def main():
+    sample = APOGEESample.load()
+    params = ['O_H_ERR', 'FE_H_ERR', 'L23_LOG_AGE_ERR', 'CN_AGE_ERR']
+    labels = pd.Series([
+        '[O/H]', 
+        '[Fe/H]', 
+        '$\\log_{10}(\\tau_{\\rm NN}/{\\rm Gyr})$', 
+        '$\\tau_{\\rm [C/N]}/{\\rm Gyr}$'
+    ], name='Parameter')
+    medians = sample.data[params].median()
+    medians.name = 'Median Uncertainty'
+    dispersions = sample.data[params].quantile(0.95) - sample.data[params].quantile(0.05)
+    dispersions.name = 'Uncertainty Dispersion ($95\\% - 5\\%$)'
+    df = pd.concat([medians, dispersions], axis=1)
+    df.set_index(labels, drop=True, inplace=True)
+    # Convert to LaTeX
+    latex_table = df.to_latex(
+        column_format='l|cc', 
+        index=True, 
+        float_format='%.2g'
+    )
+    # Replace \toprule, \midrule, \bottomrule with \hline
+    latex_table = latex_table.replace('\\toprule', '\\hline\\hline')
+    latex_table = latex_table.replace('\\midrule', '\\hline')
+    latex_table = latex_table.replace('\\bottomrule', '\\hline')
+    # Custom multi-row column labels
+    latex_table = latex_table.replace(
+        '& Median Uncertainty & Uncertainty Dispersion ($95\\% - 5\\%$)',
+        '& Median & Uncertainty '
+    )
+    latex_table = latex_table.replace(
+        'Parameter &  & ',
+        'Parameter & Uncertainty & Dispersion ($95\\% - 5\\%$)'
+    )
+    # Write to output
+    with open(paths.output / 'uncertainties.tex', 'w') as f:
+        f.write(latex_table)
+
+if __name__ == '__main__':
+    main()

### 2025-07-07 src/tex/ms.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=\linewidth]{figures/smooth_vs_twoinfall.pdf}
+    \includegraphics[width=0.5\textwidth]{figures/smooth_vs_twoinfall.pdf}
     \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves).
@@
 In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
-Using a detailed prescription for radial migration, \citet{schonrich_chemical_2009} produced distinct high- and low-$\alpha$ sequences, but they did not overlap in metallicity space as would be found by later surveys \citep[e.g.,][]{bensby_exploring_2014}.
+\citet{schonrich_chemical_2009} first showed that radial migration can produce an $\alpha$-bimodality through a superposition of chemical tracks, although they did not directly compare against MW data.
 Others have produced a more MW-like $\alpha$-bimdodality using a combination of radial migration and inside-out galaxy growth \citep[e.g.,][]{kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
@@
     \label{tab:uncertainties}
-    \begin{tabular}{lcc}
+    \begin{tabular}{l|cc}
         \hline\hline
-        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Median Uncertainty} & \multicolumn{1}{c}{Uncertainty Dispersion ($95\%-5\%$)} \\
+        & Median & Uncertainty \\
+        Parameter & Uncertainty & Dispersion ($95\%-5\%$) \\
         \hline
@@
     \end{tabular}
-\end{table*}
+\end{table}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/ofe_feh_best.pdf}
+    \includegraphics[width=\linewidth]{figures/ofe_feh_best.pdf}
     \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$.
@@
 The left and center panels plot the mass-weighted age distributions predicted by the models after forward-modeling age uncertainties, and the right panel plots the \citet{leung_variational_2023} ages for APOGEE stars.
-    {\bf Key takeaway:} The two-infall model predicts a fundamentally different age pattern than what is observed, especially for LMR stars.}
+    {\bf Key takeaway:} The two-infall models predict a fundamentally different age pattern than what is observed, especially for LMR stars.}
     \label{fig:lmr-ages}
@@
 
-The two-infall model makes a fundamental prediction about the local stellar age distribution: the most metal-rich stars born in-situ in any region of the Galaxy should come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
+The two-infall scenario makes a fundamental prediction about the local stellar age distribution: the most metal-rich stars born in-situ in any region of the Galaxy should come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
 As noted in the previous Section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.
@@
 % \todo{Summary of problem: the two-infall model is boxed in by data.}
-Our results show that the APOGEE stellar age catalogs pose several challenges to the two-infall scenario.
+% Our results show that the APOGEE stellar age catalogs pose several challenges to the two-infall scenario.
 The [O/Fe] distribution was the observable with the easiest discrepancy to resolve using the parameter space we explored, either by pre-enrichment of the accreted gas or a higher thick-to-thin disk mass ratio.
@@
 The predicted age distributions could not be reconciled with the data using any of the variations we explored.
-In the remainder of this section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.
+
+In this work, we have highlighted a few predictions of the two-infall scenario and compared against trends from large stellar age catalogs.
+We have explored a wide range of parameter space, but our investigation is not intended to be exhaustive.
+In the remainder of this Section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.
 
@@
 
-Motivated by evidence of a recent period of enhanced star formation \citep[e.g.,][]{ruiz-lara_recurrent_2020}, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} extended the two-infall model with a recent $(\lesssim3\Gyr)$ third accretion episode.
-\citet{spitoni_beyond_2023} argued that the gas dilution resulting from the third infall could explain the population of young, metal-poor stars discovered in {\it Gaia} DR3 \citep{recio-blanco_gaia_2023}, in contrast to the two-infall model of \citet{spitoni_apogee_2021} which predicted a present-day gas metallicity of ${\rm [M/H]}\approx+0.3$ in the Solar neighborhood.
-\citet{palla_mapping_2024} were similarly motivated by the finding that open clusters with ages $<1\Gyr$ have similar metallicity to those with ages $>3\Gyr$, while the classical two-infall model predicted a steady increase in metallicity over time.
+Motivated by evidence of a recent period of enhanced star formation across the MW disk \citep{ruiz-lara_recurrent_2020}, \citet{spitoni_beyond_2023} extended the two-infall scenario with a recent $(\lesssim3\Gyr)$ third accretion episode.
+In contrast to the two-infall model of \citet{spitoni_apogee_2021}, which predicted a present-day gas metallicity of ${\rm [M/H]}\approx+0.3$ in the Solar neighborhood, \citet{spitoni_beyond_2023} argued that the gas dilution resulting from the third infall could explain a population of young stars with slightly sub-Solar abundances discovered in {\it Gaia} DR3 \citep{recio-blanco_gaia_2023}.
+% \citet{palla_mapping_2024} were similarly motivated by the finding that open clusters with ages $<1\Gyr$ have similar metallicity to those with ages $>3\Gyr$, while the classical two-infall model predicted a steady increase in metallicity over time.
 However, \citet{palla_mapping_2024} invoke a less massive infall, producing a milder dilution event, than \citet{spitoni_beyond_2023}.
 
-The flat AMR from both stellar age catalogs is even more restrictive of a recent dilution event because of the smaller age uncertainties for younger stars.
-Figure \ref{fig:yield-outflow} illustrates that the mode and overall distribution of [O/H] has evolved very little over the past $\sim5$ Gyr.
-Some combination of metal-rich accretion or radial gas flows might reduce the amount of dilution predicted by a recent accretion episode, but the parameter space is tightly constrained by the stellar age data.
+Similarly, \citet{palla_mapping_2024} invoked a late-time accretion episode to explain largely age-independent metallicites in open clusters across the disk.
+Open clusters trace younger populations: most of their clusters are $\lesssim2\Gyr$ old.
+A third infall can help explain trends within this limited age range, but when compared to the full range of stellar age data, it faces the same challenges as the second infall.
+Successive epochs of dilution and re-enrichment will always struggle to explain chemical abundances that remain nearly constant with age over a $\sim10\Gyr$ period.
+As discussed in Section \ref{sec:age-abundance}, pre-enriched infall could reduce the magnitude of the dilution from a recent accretion episode, but the stellar age data place tight constraints on the parameter space.
 
@@
     \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.
-The blue dashed curve represents the fiducial model that has an exponentially declining infall rate and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
+The blue dashed curve represents the fiducial model that has an exponentially declining infall rate with timescale $\tau_{\rm in}=15\Gyr$, and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
 The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4\,{\rm Gyr}$.
 Both models assume the \yZ{2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
-The greyscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq|z|\leq2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
+The grayscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq|z|\leq2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}
@@
 
-The two-infall model falls into the broader category of GCE models which reproduce the $\alpha$-bimodality by halting or severely limiting star formation for some duration.
-For the two-infall model, this phase of low star formation immediately precedes the second infall epoch and is due to the relatively short timescale of the first infall epoch.
-However, as we have shown, the dilution of the ISM resulting from the second infall poses a challenge when comparing to age--abundance data.
-
-A bursty infall history is not the only way to produce a gap in the star formation history.
-\citet{beane_rising_2024} present a simulated galaxy from the Illustris TNG50 suite that exhibits MW-like bimodality.
-They argue that the $\alpha$-bimodality is brought on by a brief ($\sim300\,{\rm Myr}$) quiescent period caused by bar formation.
-The virial mass of their galaxy grows steadily throughout this period, unlike in our two-infall model where the mass grows by a factor of \todo{X} during the 1 Gyr following the second infall.
-
-While our semi-analytic model does not include a Galactic bar, we can explore the effects of a star formation hiatus by artificially boosting the SFE timescale $\tau_\star$ for a period of time.
-Figure \ref{fig:onezone-sfe-hiatus} illustrates the effect of this SFE-driven hiatus in a one-zone model with an exponentially declining infall rate.
+The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation for some duration.
+For the two-infall model, this phase of low star formation lasts for a few Gyr in between the $e$-folding timescale of the first infall and the onset of the second.
+However, as we have shown in Section \ref{sec:age-abundance}, the resulting dilution of the ISM is in tension with the observed stellar age--metallicity relation.
+
+An accretion-driven star formation history is not the only way to induce a hiatus in star formation.
+Investigating a simulated galaxy from the Illustris TNG50 suite \citep{pillepich_first_2019,nelson_first_2019,nelson_illustristng_2019}, \citet{beane_rising_2024} argued that its MW-like $\alpha$-bimodality is the result of a brief ($\sim300\,{\rm Myr}$) quiescent period caused by the formation of a bar.
+In this scenario, the newly-formed bar funnels gas into the galaxy's central black hole, prompting a burst of AGN activity which suppresses star formation.
+Unlike our two-infall model, where the gas mass suddenly grows by a factor of $\sim5$ during the 1 Gyr following the second infall, the mass of their galaxy grows slowly during the quiescent period, indicating a dearth of major accretion events.
+
+While our semi-analytic model does not include a Galactic bar, we can induce a star formation hiatus by artificially boosting the SFE timescale $\tau_\star$ for a period of time.
+Figure \ref{fig:onezone-sfe-hiatus} illustrates the effect of this efficiency-driven hiatus in a one-zone GCE model with an exponentially declining infall rate ($\tau_{\rm in}=15\Gyr$).
 During the quiescent period, the [O/Fe] ratio slowly declines due to the delayed contribution of Fe from SNe Ia.
 Meanwhile, the gas mass continues to increase even as star formation is suppressed.
-When $\tau_\star$ is lowered at the end of the quiescent period, the high gas mass sparks a moderate star formation burst which causes stellar abundances to ``pile up'' at similar [O/Fe] values.
+When $\tau_\star$ is lowered at the end of the quiescent period, it sparks a moderate star formation burst which causes stellar abundances to ``pile up'' at similar [O/Fe] values.
 The trough between the high- and low-$\alpha$ sequences results from the star formation returning to pre-quiescence behavior.
-
-Our simple hiatus model offers a few parameters which control the chemical evolution.
-The onset time of the SFE hiatus controls the position of the high-$\alpha$ sequence: a later onset places the peak at lower [O/Fe].
-The duration of the star formation hiatus and the $\tau_\star$ enhancement factor control the strength of the high-$\alpha$ peak.
+The onset time of the SFE hiatus controls the position of the high-$\alpha$ sequence\textemdash a later onset places the peak at lower [O/Fe]\textemdash while the duration and enhancement factor control the strength of the high-$\alpha$ peak.
 
 The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
-However, there are some differences in detail, such as the dearth of stars at $\mathOFe\approx+0.35$ due to the star formation hiatus.
-We intend this model to illustrate another path to reproducing the $\alpha$-bimodality.
+As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk as measured by \citet{pinsonneault_apokasc-3_2025}.
+This hiatus model illustrates an alternative scenario for reproducing the $\alpha$-bimodality, but a full multi-zone treatment is beyond the scope of this work.
+% We intend this model to illustrate another path to reproducing the $\alpha$-bimodality.
 Most of the high-$\alpha$ stars present in the Solar annulus have likely migrated from the inner Galaxy, where perhaps this SFE-driven hiatus was concentrated.
@@
 We explored multiple parameter modifications to bring the model predictions closer to the data, including the yield scale, radial migration strength, metallicity of the accreted gas, thick-to-thin disk mass ratio, and the SN Ia DTD.
-Our conclusions are as follows:
+We found that our two-infall models faced the following challenges when compared against the stellar age catalogs:
 
 \begin{itemize}
-    \item The large quantity of pristine gas accreted in the Solar neighborhood during the second infall phase rapidly dilutes the ISM metallicity by $\sim0.5$ dex.
-Models with low nucleosynthetic yields (\yZ{1}) remain at sub-Solar metallicity until the present day, in stark contrast to the observed local age--metallicity relation.
-Models with higher yields and outflows approach the present-day metallicity more rapidly, while pre-enriched infall can reduce the magnitude of the dilution (but not eliminate it entirely).
-%This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
+    \item By the model's design, the Galaxy undergoes a period of major, rapid dilution and subsequent re-enrichment.
+Models at a lower yield scale and weaker outflows predict slower re-enrichment.
+By contrast, the stellar age--metallicity relation is roughly constant over the past $\sim10\Gyr$.
+Pre-enriching the accreted gas can reduce the magnitude of the dilution, but not eliminate it entirely.
+    \item Due to this re-enrichment, our models predict that the MDF evolves to higher metallicity over time throughout the disk.
+This contrasts with the APOGEE data, which show very little change in the mode of the MDF over the past $\sim6-8$ Gyr.
     \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations.
 In contrast, the data show a smooth gradient between the oldest and youngest stars, with most of the metal-rich stars having intermediate ages.
+This discrepancy could not be reconciled using any of the model variations we explored.
     \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a double-peaked low-$\alpha$ sequence with a fundamentally different abundance structure than observed, especially for models with higher yields.
@@
 The parameter space is nonetheless restricted by the need to suppress this feature.
-    \item Our models predict that the MDF evolves to higher metallicity over time throughout the disk.
-This contrasts with the APOGEE data, which show very little change in the mode over the past $\sim6-8$ Gyr.
-    % \item The equilibrium scenario of chemical evolution, if correct, places stricter limits on the two-infall model than other evolutionary models.
-    \item Adjusting the strength of radial migration naturally affects the scatter in the age--metallicity relation but does not affect the median age.
+    % \item Adjusting the strength of radial migration naturally affects the scatter in the age--metallicity relation but does not affect the median age.
 \end{itemize}
+
+We note that we have not found a GCE model which is capable of reproducing all of the above observations.
+The ``inside-out'' models of \citet{johnson_stellar_2021} are better able to predict a slowly evolving metallicity gradient, but they do not predict an $\alpha$-bimodality.
+Even a smoothly-evolving SFH struggles to reproduce the flat age--metallicity relation at the lower empirical yield scale \citep{johnson_milky_2024}.
+We emphasize, though, that by its very construction the two-infall scenario trades success at reproducing certain observations for failure at others.
 
@@
 
-\todo{Personal acknowledgements.}
+\todo{Personal acknowledgements.} We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper.
 

### 2025-07-07 src/scripts/uncertainties.py
update row labels

@@ -11,8 +11,8 @@ def main():
     sample = APOGEESample.load()
     params = ['O_H_ERR', 'FE_H_ERR', 'L23_LOG_AGE_ERR', 'CN_AGE_ERR']
     labels = pd.Series([
-        '[O/H]', 
-        '[Fe/H]', 
+        '${\\rm [O/H]}$', 
+        '${\\rm [Fe/H]}$', 
         '$\\log_{10}(\\tau_{\\rm NN}/{\\rm Gyr})$', 
         '$\\tau_{\\rm [C/N]}/{\\rm Gyr}$'
     ], name='Parameter')

### 2025-07-08 src/tex/ms.tex
Updates from Overleaf

@@
     \label{tab:uncertainties}
-    \begin{tabular}{l|cc}
-        \hline\hline
-        & Median & Uncertainty \\
-        Parameter & Uncertainty & Dispersion ($95\%-5\%$) \\
-        \hline
-        $\mathOH$   & $0.019$    & $0.031$ \\
-        $\mathFeH$  & $0.0089$   & $0.0060$ \\
-        % $\mathOFe$  & $0.019$    & $0.031$ \\
-        $\log_{10}(\tau_{\rm NN}/{\rm Gyr})$    & 0.10   & $0.16$ \\
-        $\tau_{\rm [C/N]}/{\rm Gyr}$     & 1.4   & 1.8 \\
-        \hline
-    \end{tabular}
+    \input{output/uncertainties.tex}
 \end{table}
@@
 
+\begin{deluxetable*}{lCCcCCC}
+    \tablecaption{A summary of all of our multi-zone models.\label{tab:models}}
+    \tablehead{
+        \colhead{Name} & \colhead{$y/Z_\odot$} & \colhead{$\eta_\odot$} & \colhead{SN Ia DTD} & \colhead{$\sigma_{\rm RM8}$} & \colhead{$f_\Sigma(R_\odot)$} & \colhead{${\rm [X/H]}_{\rm CGM}$}
+    }
+    \startdata
+        {\tt yZ1-fiducial}  & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -\infty   \\
+        {\tt yZ1-migration} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 5.0\kpc   & 0.12  & -\infty   \\
+        {\tt yZ1-diskratio} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.5   & -\infty   \\
+        {\tt yZ1-preenrich} & 1 & 0.6   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -0.5      \\
+        {\tt yZ1-best}      & 1 & 0.4   & Equation \ref{eq:plateau-dtd}  & 3.6\kpc   & 0.25  & -0.7      \\
+        \hline
+        {\tt yZ2-fiducial}  & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -\infty   \\
+        {\tt yZ2-powerlaw}  & 2 & 1.4   & Equation \ref{eq:powerlaw-dtd} & 2.68\kpc  & 0.12  & -\infty   \\
+        {\tt yZ2-diskratio} & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.5   & -\infty   \\
+        {\tt yZ2-preenrich} & 2 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -0.5      \\
+        {\tt yZ2-best}      & 2 & 1.8   & Equation \ref{eq:plateau-dtd}  & 3.6\kpc   & 0.25  & -0.7      \\
+        \hline
+        {\tt yZ3-fiducial}  & 3 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -\infty   \\
+    \enddata
+\end{deluxetable*}
+\vspace{-24pt}
+
 \subsection{Nucleosynthetic Yields}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/onezone_params.pdf}
+    \includegraphics[width=\textwidth]{figures/infall_parameters.pdf}
     \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters.
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/abundance_evolution_params.pdf}
+    \includegraphics[width=\linewidth]{figures/stellar_abundance_evolution.pdf}
     \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}).
@@
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
+Pre-enriched infall raises the equilibrium metallicity, so we increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity.
 Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
@@
     \centering
-    \includegraphics[width=\textwidth]{src/tex/figures/ofe_distribution_params.pdf}
+    \includegraphics[width=\textwidth]{src/tex/figures/ofe_distributions.pdf}
     \caption{Normalized stellar [O/Fe] distributions predicted by multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). 
@@
     \centering
-    \includegraphics[width=\onecolumn]{figures/onezone_sfe_hiatus.pdf}
+    \includegraphics[width=\onecolumn]{figures/sfe_hiatus.pdf}
     \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.

### 2025-07-11 src/scripts/distribution_functions.py
update row labels

@@ -31,7 +31,7 @@ def plot_multizone_mdfs(mzs, axs, col='[fe/h]', colors=[], label='VICE',
     galr_bins: list of floats, optional
     absz_bins: list of floats, optional
     titlepad: int, optional
-        Vertical padding for axes title. The default is 18.
+        Vertical padding for axes title. The default is None.
     **kwargs passed to MultizoneStars.mdf()
     """
     if len(colors) != len(galr_bins) - 1:
@@ -103,7 +103,7 @@ def setup_axes(ncols=2, figure_width=3.25, xlabel='', xlim=None,
     figure_height = ax_height * nrows + 1
     fig, axs = plt.subplots(nrows, ncols, sharex=True, sharey='row',
                             figsize=(figure_width, figure_height))
-    fig.subplots_adjust(left=0.09, top=0.93, right=0.92, bottom=0.22,
+    fig.subplots_adjust(left=0.09, top=0.93, right=0.98, bottom=0.22,
                         wspace=0.07, hspace=0.07)
     # Format x-axis
     axs[0,0].set_xlim(xlim)
@@ -129,8 +129,12 @@ def setup_axes(ncols=2, figure_width=3.25, xlabel='', xlim=None,
     # Label rows
     for i in range(len(absz_bins)-1):
         absz_lim = tuple(absz_bins[-(i+2):len(absz_bins)-i])
-        axs[i,-1].yaxis.set_label_position('right')
-        axs[i,-1].set_ylabel(r'$|z| = %s - %s$' % absz_lim)
+        # axs[i,-1].yaxis.set_label_position('right')
+        # axs[i,-1].set_ylabel(r'$|z| = %s - %s$' % absz_lim)
+        axs[i,0].text(
+            0.5, 0.9, r'$|z| = %s - %s$' % absz_lim,
+            ha='center', va='top', transform=axs[i,0].transAxes
+        )
     # Add colorbar on bottom
     if type(cmap) == str:
         cmap = plt.get_cmap(cmap)

### 2025-07-11 src/scripts/ofe_distributions.py

@@ -24,7 +24,7 @@ LABELS = [
     '(b)\nPower-law DTD',
     '(c)\n' + r'$f_\Sigma(R_\odot)=0.5$',
     '(d)\n' + r'${\rm [X/H]}_{\rm CGM}=-0.5$',
-    '(e)\nAPOGEE'
+    'APOGEE\n(e)'
 ]
 NBINS = 100
 OFE_LIM = (-0.15, 0.55)
@@ -55,15 +55,15 @@ def main(style='paper', cmap=CMAP, verbose=False):
         dfs.plot_multizone_mdfs(mzs, axs[:,i], '[o/fe]', colors, label=LABELS[i],
                                 **mdf_kwargs)
     dfs.plot_multizone_mdfs(apogee_sample, axs[:,apogee_index], 'O_FE', colors, 
-                            label=LABELS[apogee_index], **mdf_kwargs)
+                            label=LABELS[apogee_index], titlepad=18, **mdf_kwargs)
     for ax in axs[:,0]:
         ax.set_ylim((0, None))
     highlight_panels(
         fig, axs, [(0,apogee_index), (1, apogee_index), (2, apogee_index)]
     )
     # Add figure title
-    fig.suptitle(r'$y/Z_\odot=2$', x=0.42, y=1.)
-    fig.subplots_adjust(top=0.85)
+    fig.suptitle(r'$y/Z_\odot=2$', x=0.44, y=1.06)
+    fig.subplots_adjust(top=0.92)
     # Save
     plt.savefig(paths.figures / 'ofe_distributions')
     plt.close()

### 2025-07-11 src/tex/ms.tex

@@
 \newcommand{\kpc}{\,{\rm kpc}}
+\newcommand{\Myr}{\,{\rm Myr}}
 \newcommand{\Gyr}{\,{\rm Gyr}}
@@
 \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
-Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey (SDSS; \todo{Hawkins et al.
-2025, in preparation}).
+Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey \citep[SDSS;][]{sdss_collaboration_nineteenth_2025}.
 
@@
     \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves).
-The two-infall model adopts the fiducial parameters according to Table \ref{tab:multizone-parameters}, while the smooth SFH adopts the parameters of the ``inside-out'' model of \citet{johnson_stellar_2021}.
+The two-infall model adopts the fiducial parameters according to Table \ref{tab:parameters}, while the smooth SFH adopts the parameters of the ``inside-out'' model of \citet{johnson_stellar_2021}.
 Both models assume the \yZ{2} yield scale (see Table \ref{tab:yields}).
@@
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
-Table \ref{tab:multizone-parameters} summarizes the most relevant variables and their fiducial values in this work.
+Table \ref{tab:parameters} summarizes the most relevant variables and their fiducial values in this work.
 
 \begin{deluxetable*}{Ccccl}
-    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:multizone-parameters}}
+    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:parameters}}
     \tablehead{
@@
     \startdata
+        R_{\rm gal}         & $[0,20]\kpc$  & ---           & \ref{sec:methods}     & Galactocentric radius \\
+        \delta R_{\rm gal}  & $0.1\kpc$ & ---               & \ref{sec:methods}     & Radial zone width \\
+        R_{\rm SF}          & $15.5\kpc$    & ---           & \ref{sec:methods}     & Maximum radius of star formation \\
+        t_{\rm final}       & $13.2\Gyr$ & ---              & \ref{sec:methods}     & Disk lifetime \\
+        \Delta t            & $10\Myr$  & ---               & \ref{sec:methods}     & Time-step size \\
+        n                   & 8         & ---               & \ref{sec:methods}     & Number of stellar populations formed per ring per timestep \\
+        \dot M_r            & continuous    & ---           & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
         y/Z_\odot           & 1         & 2, 3              & \ref{sec:yields}      & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
+        N_{\rm Ia}/M_\star  & $1.55\times10^{-3}\Msun^{-1}$ & 2.62, $3.57\times10^{-3}\Msun^{-1}$   & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \\
         f_{\rm Ia}(t)       & Equation \ref{eq:plateau-dtd} & Equation \ref{eq:powerlaw-dtd}    & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
-        \eta_\odot          & 0.2       & 1.4, 2.4          & \ref{sec:outflows}            & Outflow mass-loading factor at $R_\odot$ (see Table \ref{tab:yields}) \\
-        R_\eta              & 5.0 kpc   & ---               & \ref{sec:outflows}            & Exponential outflow scale radius \\
+        t_{\rm Ia}          & $40\Myr$  & ---               & \ref{sec:yields}              & Minimum SN Ia delay time \\
+        \eta_\odot          & 0.2       & 1.4, 2.4          & \ref{sec:outflows}            & Outflow mass-loading factor at $R_\odot$ ($\eta\equiv\dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
+        R_\eta              & $5.0\kpc$ & ---               & \ref{sec:outflows}            & Exponential outflow scale radius \\
+        \tau_\star          & Equation \ref{eq:sf-law}      & ---   & \ref{sec:sf-law}      & Star formation efficiency timescale ($\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$) \\
+        k                   & 1.5       & ---               & \ref{sec:sf-law}              & Star formation law exponent \citep{kennicutt_global_1998} \\
+        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & ---   & \ref{sec:sfh} & Total stellar mass of the disk \\
         f_\Sigma(R_\odot)   & 0.12      & 0.25, 0.5         & \ref{sec:sfh}                 & Local thick/thin disk surface density ratio \\
-        \mathXH_{\rm CGM}   & Pristine  & $-0.7$, $-0.5$    & \ref{sec:sfh}                 & Metallicity of infalling gas \\
-        \tau_1              & 1 Gyr     & $0.1-3$ Gyr       & \ref{sec:parameter-selection} & Timescale of the first infall epoch \\
-        \tau_2(R_\odot)     & 15 Gyr    & $3-30$ Gyr        & \ref{sec:parameter-selection} & Timescale of the second infall epoch at the Solar annulus \\
-        R_{\tau_2}          & 7 kpc     & ---               & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
-        t_{\rm max}         & 4.2 Gyr   & $1-5$ Gyr         & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
-        \sigma_{\rm RM8}    & 2.68 kpc  & 3.6, 5.0 kpc      & \ref{sec:migration}   & Radial migration strength
+        R_1                 & $2.0\kpc$ & ---               & \ref{sec:sfh}                 & Thick disk scale radius \\
+        R_2                 & $2.5\kpc$ & ---               & \ref{sec:sfh}                 & Thin disk scale radius \\
+        \mathXH_{\rm CGM}   & $-\infty$ & $-0.7$, $-0.5$    & \ref{sec:sfh}                 & Metallicity of infalling gas \\
+        f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & ---   & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
+        \tau_1              & $1\Gyr$   & $0.1-3\Gyr$       & \ref{sec:parameter-selection} & Timescale of the first infall epoch \\
+        \tau_2(R_\odot)     & $15\Gyr$  & $3-30\Gyr$        & \ref{sec:parameter-selection} & Timescale of the second infall epoch at the Solar annulus \\
+        R_{\tau_2}          & $7\kpc$   & ---               & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
+        t_{\rm max}         & $4.2\Gyr$ & $1-5\Gyr$         & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
+        % \Delta R_{\rm gal}  & ---       & ---               & \ref{sec:migration}   & Change in orbital radius due to stellar migration \\
+        \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & ---   & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
+        \sigma_{\rm RM8}    & $2.68\kpc$ & $3.6$, $5.0\kpc$ & \ref{sec:migration}   & Radial migration strength (width of $\sigma_{\rm RM}$ for $\tau=8\Gyr$) \\
+        z                   & $[-3,3]\kpc$  & ---           & \ref{sec:migration} & Distance from Galactic midplane at present day \\
+        % p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}    & ---   & \ref{sec:migration} & Probability density function of Galactic midplane distance\\
+        h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & ---   & \ref{sec:migration} & Disk scale height \\
     \enddata
@@
 
+\subsection{Nucleosynthetic Yields}
+\label{sec:yields}
+
+\begin{table}
+    \centering
+    \caption{Nucleosynthetic yields and outflow prescriptions (see Section \ref{sec:yields}).}
+    \include{output/yields.tex}
+    \label{tab:yields}
+\end{table}
+
+The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models.
+This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
+Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
+    In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$.
+We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
+}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a mass of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass in the Sun.
+However, \citet{johnson_milky_2024} found that their GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
+
+We therefore investigate yield sets at multiple scales. The CCSN yield of O is directly set by the Solar scale, $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$\footnote{
+    We adopt the \citet{asplund_chemical_2009} Solar abundances: $Z_{\rm O,\odot}=5.72\times10^{-3}$ and $Z_{\rm Fe,\odot}=1.29\times10^{-3}$.
+We note that for this empirical scaling, choosing different Solar abundances \citep[e.g.,][]{magg_observational_2022} would lead us to change the yields proportionally, so that our GCE model predictions in Solar-scaled abundances would actually be unchanged.
+}, because we assume that all O is produced by CCSNe.
+For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathOFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathOFe_{\rm CC}}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
+We set the plateau at $\mathOFe_{\rm CC}=+0.45$, which corresponds to an Fe yield from CCSNe of $y_{\rm Fe}^{\rm CC}=4.58\times10^{-4}(y/Z_\odot)$.
+Our yield sets are presented in Table \ref{tab:yields}.
+We consider \yZ{1} representative of the empirical yield scale, whereas \yZ{2-3} span a range of theoretical predictions.
+
+The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is set so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
+For \yZ{3}, the combined Fe yield of CCSNe and SNe Ia matches the Solar yield scale: $(y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC})/Z_{\rm Fe,\odot}=y/Z_\odot$; for \yZ{1} and \yZ{2}, we enhance $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\%, respectively, to reach the desired end-point.
+The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate or total number of SNe Ia per unit mass of star formation,
+\begin{equation}
+    \frac{N_{\rm Ia}}{M_\star} = \frac{y_{\rm Fe}^{\rm Ia}}{\bar m_{\rm Fe}^{\rm Ia}},
+    \label{eq:snia-rate}
+\end{equation}
+from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
+The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
+The rate for the \yZ{2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}, while the rate for the \yZ{3} yield set is generally higher than literature values.
+
+Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion. The time-dependent SN Ia rate per unit mass of star formation is defined as
+\begin{equation}
+    R_{\rm Ia}(t) = 
+    \begin{cases}
+        \frac{N_{\rm Ia}}{M_\star}
+        \frac{f_{\rm Ia}(t)}{\int_{t_{\rm Ia}}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_{\rm Ia} \\
+        0 & t < t_{\rm Ia},
+    \end{cases}
+    \label{eq:dtd-function}
+\end{equation}
+where $t_{\rm Ia}=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm final}=13.2\,{\rm Gyr}$ is our assumed lifetime of the Galactic disk, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
+Motivated by recent results suggesting that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence \citep{palicio_analytic_2023,dubay_galactic_2024}, we adopt a wide plateau DTD of the form
+\begin{equation}
+    \label{eq:plateau-dtd}
+    f_{\rm Ia}(t) =
+    \begin{cases}
+        1, & t < 1\,{\rm Gyr} \\
+        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
+    \end{cases}
+\end{equation}
+We also explore a simple power-law DTD,
+\begin{equation}
+    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^{-1.1}.
+    \label{eq:powerlaw-dtd}
+\end{equation}
+Equation \ref{eq:powerlaw-dtd} is consistent with SN Ia surveys \citep[e.g.,][]{maoz_star_2017} and results in more prompt Fe production.
+We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.
+
+Many previous two-infall studies have adopted the yields of \citet{francois_evolution_2004}, who in turn adapted those of \citet{woosley_evolution_1995} for CCSNe and \citet{iwamoto_nucleosynthesis_1999} for SNe Ia to provide a better fit between GCE models and local abundance data.
+Notably, the yields for O and Fe were left unchanged from the original studies.
+However, because \citet{woosley_evolution_1995} report gross yields without detailed initial abundances for their CCSN progenitors, and because \citet{francois_evolution_2004} do not provide population-averaged yields, it is difficult to make a comparison with our yields.
+Ultimately, \citet{francois_evolution_2004} report that their GCE models are insensitive to changes in the CCSN yield of O by a factor of 2, so we consider it reasonable to explore the full range of yields given in Table \ref{tab:yields}.
+
+\subsection{Outflows}
+\label{sec:outflows}
+
+Mass-loaded outflows are a useful tool for scaling the endpoint of GCE models.
+\citet{weinberg_equilibrium_2017} showed that in the case of exponentially declining star formation, the O abundance approaches an equilibrium at
+\begin{equation}
+    \label{eq:equilibrium}
+    Z_{\rm O,eq} = \frac{y_{\rm O}^{\rm CC}}{1 + \eta - r - \tau_\star/\tau_{\rm SFH}},
+\end{equation}
+where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the $e$-folding timescale of the star formation history, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
+Motivated by Equation \ref{eq:equilibrium}, we adopt the outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
+Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on age trends such as these.
+
+Not all GCE studies have constrained their models to reach an equilibrium at the Solar metallicity.
+For example, the models of \citet{palla_chemical_2020} and \citet{spitoni_remind_2024} predict somewhat super-Solar metallicity in the present-day Solar neighborhood.
+Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances  indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we use $\eta$ to fine-tune the chemical evolution end-point to $\mathOH\approx0.0$.
+
+Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
+\citet{johnson_milky_2024} used this approach to present a proof of concept for the equilibrium scenario.
+In order to produce an exponentially declining radial metallicity gradient, we adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
+\begin{equation}
+    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
+\end{equation}
+where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, in line with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
+
+Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
+Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023} or does not vary with radius \citep{hegedus_reconstructing_2025}.
+To achieve a realistic radial metallicity gradient, many studies have adopted the yields of \citet{francois_evolution_2004} and a prescription for the infall timescale of the thin disk that increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
+Additionally, some studies have implemented radial gas flows or a variable star formation efficiency in order to regulate the radial metallicity gradient \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020}.
+
+As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
+Here, we aim to study the effect of the assumed yield scale on two-infall model predictions, so we use mass-loaded outflows to control the final state of chemical evolution across the disk.
+However, mass-loaded outflows are not a necessary ingredient for the results of this study.
+We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
+%Therefore, our multi-zone models with \yZ{1} should predict similar behavior to a model without any mass-loaded outflows.
+%If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.
+
+\subsection{The Star Formation Law}
+\label{sec:sf-law}
+
+The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^k$, with $k=1.5$ following \citet{kennicutt_global_1998}.
+Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
+%     \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
+All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
+%     \label{fig:sfe-prefactor}
+% \end{figure}
+
+In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
+\begin{equation}
+    \label{eq:sf-law}
+    \tau_\star = 
+    \begin{cases}
+        \varepsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
+        \varepsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
+    \end{cases}
+\end{equation}
+where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citep{leroy_star_2008}.
+Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through the pre-factor $\varepsilon$:
+\begin{equation}
+    \label{eq:sfe-prefactor}
+    \varepsilon(t) = 
+    \begin{cases}
+        0.5, & t < t_{\rm max} \\
+        1.0, & t \ge t_{\rm max}.
+    \end{cases}
+\end{equation}
+A lower value of $\varepsilon(t<t_{\rm max})$ leads to more efficient star formation, and therefore more rapid enrichment, during the first infall epoch.
+However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
+We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature, though we find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
+To guard against over-correcting the SFE in the early Galaxy, we have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
+
+\subsection{The Gas Supply}
+\label{sec:sfh}
+
+We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time at each radius.
+The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from these two inputs as a natural outcome of the time-stepping solution, assuming zero initial gas mass in all zones.
+
+The infall rate as a function of time and galactocentric radius can generically be described by
+\begin{equation}
+    \label{eq:infall-rate}
+    \dot\Sigma_{\rm in}(t,R_{\rm gal}) = A f_{\rm in}(t|R_{\rm gal}) g(R_{\rm gal}),
+\end{equation}
+where $g(R_{\rm gal})=\Sigma_\star(R_{\rm gal}) / \Sigma_\star(R_{\rm gal}=0)$ is the stellar density gradient, $f_{\rm in}$ is the infall rate over time, and $A$ is a normalization constant.
+Because we incorporate mass-loaded outflows, $A$ is not analytically solvable, so first we numerically integrate the star formation rate $\dot\Sigma_\star(t,R_{\rm gal})$ and then follow the procedure outlined in Appendix B of \citet{johnson_stellar_2021} to calculate $A$.
+In short, the infall rate is normalized to produce a total disk stellar mass of $M_{\rm \star,tot}=(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and to match the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
+
+Characteristic of the two-infall scenario, the infall rate is described by two successive, exponentially declining bursts in time.
+The first infall component induces the formation of the thick disk, and the second component produces the thin disk.
+At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
+\begin{equation}
+    \label{eq:twoinfall-ifr}
+    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + H(t-t_{\rm max}) f_{2/1} (R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
+\end{equation}
+\begin{equation*}
+    H(x) \equiv 
+    \begin{cases}
+        1, & x \ge 0 \\
+        0, & x < 0,
+    \end{cases}
+\end{equation*}
+where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall,  $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
+We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
+\begin{equation}
+    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_\Sigma(R_\odot) e^{(R-R_\odot)\cdot(1/R_2 - 1/R_1)}.
+\end{equation}
+We adopt a thick disk scale radius of $R_1=2.0\kpc$, a thin disk scale radius of $R_2=2.5\kpc$, and a fiducial value for the local surface density ratio of $f_\Sigma(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\onecolumn]{figures/star_formation_history.pdf}
+    \caption{The evolution of (a) the infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
+Each panel plots the evolution in six different zones of width $\delta R_{\rm gal}=0.1\kpc$, color-coded by Galactocentric radius.}
+    \label{fig:sfh}
+\end{figure}
+
+Figure \ref{fig:sfh} plots the star formation history of several different zones from our fiducial model with $y/Z_\odot=1$.
+In the inner Galaxy, the infall rate $\dot\Sigma_{\rm in}$ is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
+In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
+The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a maximum of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
+
+The thick-to-thin disk density ratio is especially important for our GCE models as it controls the quantity of gas accreted during each infall epoch.
+Our fiducial value of $f_\Sigma(R_\odot)=0.12$ is on the low end of literature estimates, which range from $f_\Sigma(R_\odot)\sim0.06-0.6$ \citep[e.g.,][]{gilmore_new_1983,siegel_star_2002,juric_milky_2008,mackereth_age-metallicity_2017,fuhrmann_local_2017}.
+Previous two-infall studies have adopted a similarly broad range of values (e.g., $f_\Sigma(R_\odot)=0.18$ from \citealt{spitoni_apogee_2021}; $f_\Sigma(R_\odot)=0.4$ from \citealt{spitoni_remind_2024}).
+We therefore explore values up to $f_\Sigma(R_\odot)=0.5$ in our multi-zone models in Section \ref{sec:multizone-results}.
+
+In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
+However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
+The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
+We investigate models where the infalling gas is pre-enriched, and its metallicity is described by
+\begin{equation}
+    \label{eq:pre-enrichment}
+    Z_{\rm in}(t) = (1 - e^{-t/\tau_{\rm rise}}) Z_\odot 10^{\mathXH_{\rm CGM}}.
+\end{equation}
+In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathFeH_{\rm CGM}$.
+Previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
+We assume the Solar-scaled metallicity of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
+% We also investigate cases where the CGM is $\alpha$-enhanced, i.e., $\mathOFe_{\rm CGM}>0$.
+
+\subsection{Infall Rate Parameter Selection}
+\label{sec:parameter-selection}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/infall_parameters.pdf}
+    \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters.
+In each panel, one parameter is varied according to the legend while the other two are held fixed.
+The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b).
+The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
+All models use the same fiducial parameters as the $R_{\rm gal}=8\kpc$ ring in the multi-zone models, with \yZ{1} and $\eta=0.2$.
+The black lines represent the same set of parameters in each panel.}
+    \label{fig:twoinfall-parameters}
+\end{figure*}
+
+% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
+% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
+Previous studies have adopted a wide range of parameters for Equation \ref{eq:twoinfall-ifr}.
+Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}.
+The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
+Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
+We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.3$.
+
+Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that 
+% the second infall timescale $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions. 
+the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
+A shorter $\tau_2$ produces a bigger loop and therefore a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
+We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is close to a constant infall rate, so a further increase in $\tau_2$ has diminishing effect.
+Between $\tau_2=3-30\,{\rm Gyr}$, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
+We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the size of the loop and width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times (see further discussion in Section \ref{sec:abundance-distributions}).
+This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}.
+% In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.
+
+In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
+Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1\Gyr$ in the inner disk and $\tau_2=7\Gyr$ at the Solar annulus.
+This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
+We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\Gyr$ at the Solar annulus and a scale radius $R_{\tau_2}=7\kpc$.
+This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
+We have also run models with a linear prescription and with a uniform value for $\tau_2$ and have found little difference in our key results.
+
+Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
+For $t_{\rm max}>2\Gyr$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
+The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}.
+We adopt a fiducial value of $t_{\rm max}=4.2\Gyr$, i.e.
+a lookback time of $9\Gyr$, which is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
+This ensures that our models are compatible with the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
+
+The Milky Way's last major merger with the dwarf galaxy, dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018}, has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
+Our fiducial value of $t_{\rm max}=4.2\Gyr$ places the start of the formation of the thin disk close to the GSE merger (within uncertainties), which likely occurred $\sim10\Gyr$ ago \citep[e.g.,][]{helmi_merger_2018,gallart_uncovering_2019,naidu_reconstructing_2021,woody_rapid_2025}.
+However, recent arguments suggest that the GSE merger would not have led to two-infall-like evolution because the mass ratio is too low to produce sufficient dilution \citet{orkney_milky_2025}.
+
+We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
+The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus, since they are one-zone models.
+In our multi-zone models, most of the high-$\alpha$ stars present in the Solar neighborhood have migrated from the inner Galaxy.
+
+\subsection{Stellar Migration}
+\label{sec:migration}
+
+This study is not the first to apply a prescription for radial migration to a two-infall GCE model.
+\citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
+They prescribed some fraction of stars from the inner and outer Galaxy which contribute to the local present-day population based on a constant migration speed, and they also assumed some fraction of stars born in the Solar neighborhood will have migrated elsewhere.
+This method can improve agreement with the observed local metallicity distribution, but does not scale to abundance distributions across the disk.
+\citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to the diffusion treatment of \citet{frankel_measuring_2018} and found similar results.
+Our implementation, described below, affects abundance distributions across the Galaxy, not just at the Solar annulus.
+
+% \citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
+They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
+This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
+They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
+Their only point of comparison with data is the local G-dwarf metallicity distribution.
+
+The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
+\begin{equation}
+    \sigma_{\rm RM}(\tau,R_{\rm form}) = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\kpc}\Big)^{0.61},
+    \label{eq:radial-migration}
+\end{equation}
+where we adopt $\sigma_{\rm RM8}=2.68\kpc$ as the fiducial value for the strength of radial migration from \citet{dubay_galactic_2024}.
+This is smaller than the value of $\sigma_{\rm RM8}=3.6\kpc$ found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.
+
+All stellar populations are born at the Galactic midplane and are assigned a final midplane distance $z$ drawn from the distribution
+\begin{equation}
+    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)\quad 
+    {\rm \citep{spitzer_dynamics_1942}},
+    \label{eq:sech-pdf}
+\end{equation}
+where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The scale height $h_z$ is given by
+\begin{equation}
+    h_z(\tau,R_{\rm final}) = \Big(\frac{0.24\kpc}{e^2}\Big) \exp\Big(\frac{\tau}{7\,{\rm Gyr}} + \frac{R_{\rm final}}{6\kpc}\Big).
+    \label{eq:scale-height}
+\end{equation}
+We note that the final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
+The parameters of Equations \ref{eq:radial-migration} and \ref{eq:scale-height} were chosen to fit the stellar migration patterns in the {\tt h277} hydrodynamical simulation \citep{christensen_implementing_2012}.
+A more complete discussion of the migration scheme and its consequences can be found in Appendix C of \citet{dubay_galactic_2024}.
+
+We note an important distinction between our method and that of \citet{spitoni_effect_2015}: SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
+This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
+Therefore, a significant fraction of SN Ia progenitors born in a given zone will enrich a different region of the Galaxy.
+
+\section{Multi-Zone Model Results}
+\label{sec:multizone-results}
+
+We run 11 multi-zone models at three different yield scales.
+For our \yZ{1} and \yZ{2} yield scales, we vary the SN Ia DTD, the migration strength $\sigma_{\rm RM8}$, the thick-to-thin disk mass ratio $f_\Sigma(R_\odot)$, and the enrichment of the infalling gas ${\rm [X/H]}_{\rm CGM}$.
+Our models and relevant parameters are summarized in Table \ref{tab:models}.
+In the remainder of this Section, we present results from these models and compare against APOGEE data and stellar age estimates.
+
 \begin{deluxetable*}{lCCcCCC}
-    \tablecaption{A summary of all of our multi-zone models.\label{tab:models}}
+    \tablecaption{Summary of our multi-zone models and relevant parameters.\label{tab:models}}
     \tablehead{
@@
 
-\subsection{Nucleosynthetic Yields}
-\label{sec:yields}
-
-\begin{table}
-    \centering
-    \caption{Nucleosynthetic yields and outflow prescriptions.}
-    \include{output/yields.tex}
-    \label{tab:yields}
-\end{table}
-
-The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models.
-This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
-    In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$.
-We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
-}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a mass of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass in the Sun.
-However, \citet{johnson_milky_2024} found that their GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
-Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
-
-We therefore investigate yield sets at multiple scales. The CCSN yield of O is directly set by the Solar scale, $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$\footnote{
-    We adopt the \citet{asplund_chemical_2009} Solar abundances: $Z_{\rm O,\odot}=5.72\times10^{-3}$ and $Z_{\rm Fe,\odot}=1.29\times10^{-3}$.
-We note that for this empirical scaling, choosing different Solar abundances \citep[e.g.,][]{magg_observational_2022} would lead us to change the yields proportionally, so that our GCE model predictions in Solar-scaled abundances would actually be unchanged.
-}, because we assume that all O is produced by CCSNe.
-For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathOFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathOFe_{\rm CC}}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
-We set the plateau at $\mathOFe_{\rm CC}=+0.45$, which corresponds to an Fe yield from CCSNe of $y_{\rm Fe}^{\rm CC}=4.58\times10^{-4}(y/Z_\odot)$.
-Our yield sets are presented in Table \ref{tab:yields}.
-We consider \yZ{1} representative of the empirical yield scale, whereas \yZ{2-3} span a range of theoretical predictions.
-
-The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is set so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
-For \yZ{3}, the combined Fe yield of CCSNe and SNe Ia matches the Solar yield scale: $(y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC})/Z_{\rm Fe,\odot}=y/Z_\odot$; for \yZ{1} and \yZ{2}, we enhance $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\%, respectively, to reach the desired end-point.
-The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate or total number of SNe Ia per unit mass of star formation,
-\begin{equation}
-    \frac{N_{\rm Ia}}{M_\star} = \frac{y_{\rm Fe}^{\rm Ia}}{\bar m_{\rm Fe}^{\rm Ia}},
-    \label{eq:snia-rate}
-\end{equation}
-from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
-The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
-The rate for the \yZ{2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}, while the rate for the \yZ{3} yield set is generally higher than literature values.
-
-Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion. The time-dependent SN Ia rate per unit mass of star formation is defined as
-\begin{equation}
-    R_{\rm Ia}(t) = 
-    \begin{cases}
-        \frac{N_{\rm Ia}}{M_\star}
-        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
-        0 & t < t_D,
-    \end{cases}
-    \label{eq:dtd-function}
-\end{equation}
-where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is our assumed lifetime of the Galactic disk, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
-Motivated by recent results suggesting that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence \citep{palicio_analytic_2023,dubay_galactic_2024}, we adopt a wide plateau DTD of the form
-\begin{equation}
-    \label{eq:plateau-dtd}
-    f_{\rm Ia}(t) =
-    \begin{cases}
-        1, & t < 1\,{\rm Gyr} \\
-        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
-    \end{cases}
-\end{equation}
-We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.
-
-Many previous two-infall studies have adopted the yields of \citet{francois_evolution_2004}, who in turn adapted those of \citet{woosley_evolution_1995} for CCSNe and \citet{iwamoto_nucleosynthesis_1999} for SNe Ia to provide a better fit between GCE models and local abundance data.
-Notably, the yields for O and Fe were left unchanged from the original studies.
-However, because \citet{woosley_evolution_1995} report gross yields without detailed initial abundances for their CCSN progenitors, and because \citet{francois_evolution_2004} do not provide population-averaged yields, it is difficult to make a comparison with our yields.
-Ultimately, \citet{francois_evolution_2004} report that their GCE models are insensitive to changes in the CCSN yield of O by a factor of 2, so we consider it reasonable to explore the full range of yields given in Table \ref{tab:yields}.
-
-\subsection{Outflows}
-\label{sec:outflows}
-
-Mass-loaded outflows are a useful tool for scaling the endpoint of GCE models.
-\citet{weinberg_equilibrium_2017} showed that in the case of exponentially declining star formation, the O abundance approaches an equilibrium at
-\begin{equation}
-    \label{eq:equilibrium}
-    Z_{\rm O,eq} = \frac{y_{\rm O}^{\rm CC}}{1 + \eta - r - \tau_\star/\tau_{\rm SFH}},
-\end{equation}
-where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the $e$-folding timescale of the star formation history, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
-Motivated by Equation \ref{eq:equilibrium}, we adopt the outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
-Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on age trends such as these.
-
-Not all GCE studies have constrained their models to reach an equilibrium at the Solar metallicity.
-For example, the models of \citet{palla_chemical_2020} and \citet{spitoni_remind_2024} predict somewhat super-Solar metallicity in the present-day Solar neighborhood.
-Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances  indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we use $\eta$ to fine-tune the chemical evolution end-point to $\mathOH\approx0.0$.
-
-Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
-\citet{johnson_milky_2024} used this approach to present a proof of concept for the equilibrium scenario.
-In order to produce an exponentially declining radial metallicity gradient, we adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
-\begin{equation}
-    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
-\end{equation}
-where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, in line with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
-
-Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
-Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023} or does not vary with radius \citep{hegedus_reconstructing_2025}.
-To achieve a realistic radial metallicity gradient, many studies have adopted the yields of \citet{francois_evolution_2004} and a prescription for the infall timescale of the thin disk that increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
-Additionally, some studies have implemented radial gas flows or a variable star formation efficiency in order to regulate the radial metallicity gradient \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020}.
-
-As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
-Here, we aim to study the effect of the assumed yield scale on two-infall model predictions, so we use mass-loaded outflows to control the final state of chemical evolution across the disk.
-However, mass-loaded outflows are not a necessary ingredient for the results of this study.
-We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
-%Therefore, our multi-zone models with \yZ{1} should predict similar behavior to a model without any mass-loaded outflows.
-%If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.
-
-\subsection{The Star Formation Law}
-\label{sec:sf-law}
-
-The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^N$, with $N=1.5$ following \citet{kennicutt_global_1998}.
-Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
-%     \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
-All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
-%     \label{fig:sfe-prefactor}
-% \end{figure}
-
-In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
-\begin{equation}
-    \label{eq:sf-law}
-    \tau_\star = 
-    \begin{cases}
-        \varepsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
-        \varepsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
-    \end{cases}
-\end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citep{leroy_star_2008}.
-Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through the pre-factor $\varepsilon$:
-\begin{equation}
-    \label{eq:sfe-prefactor}
-    \varepsilon(t) = 
-    \begin{cases}
-        0.5, & t < t_{\rm max} \\
-        1.0, & t \ge t_{\rm max}.
-    \end{cases}
-\end{equation}
-A lower value of $\varepsilon(t<t_{\rm max})$ leads to more efficient star formation, and therefore more rapid enrichment, during the first infall epoch.
-However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
-We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature, though we find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
-To guard against over-correcting the SFE in the early Galaxy, we have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
-
-\subsection{The Gas Supply}
-\label{sec:sfh}
-
-We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time at each radius.
-The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from these two inputs as a natural outcome of the time-stepping solution, assuming zero initial gas mass in all zones.
-
-The infall rate as a function of time and galactocentric radius can generically be described by
-\begin{equation}
-    \label{eq:infall-rate}
-    \dot\Sigma_{\rm in}(t,R_{\rm gal}) = A f_{\rm in}(t|R_{\rm gal}) g(R_{\rm gal}),
-\end{equation}
-where $g(R_{\rm gal})=\Sigma_\star(R_{\rm gal}) / \Sigma_\star(R_{\rm gal}=0)$ is the stellar density gradient, $f_{\rm in}$ is the infall rate over time, and $A$ is a normalization constant.
-Because we incorporate mass-loaded outflows, $A$ is not analytically solvable, so first we numerically integrate the star formation rate $\dot\Sigma_\star(t,R_{\rm gal})$ and then follow the procedure outlined in Appendix B of \citet{johnson_stellar_2021} to calculate $A$.
-In short, the infall rate is normalized to produce a total disk stellar mass of $(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and to match the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
-
-Characteristic of the two-infall scenario, the infall rate is described by two successive, exponentially declining bursts in time.
-The first infall component induces the formation of the thick disk, and the second component produces the thin disk.
-At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
-\begin{equation}
-    \label{eq:twoinfall-ifr}
-    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + H(t-t_{\rm max}) f_{2/1} (R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
-\end{equation}
-\begin{equation*}
-    H(x) \equiv 
-    \begin{cases}
-        1, & x \ge 0 \\
-        0, & x < 0,
-    \end{cases}
-\end{equation*}
-where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall,  $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
-We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
-\begin{equation}
-    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_\Sigma(R_\odot) e^{(R-R_\odot)\cdot(1/R_2 - 1/R_1)}.
-\end{equation}
-We adopt a thick disk scale radius of $R_1=2.0\kpc$, a thin disk scale radius of $R_2=2.5\kpc$, and a fiducial value for the local surface density ratio of $f_\Sigma(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{figures/star_formation_history.pdf}
-    \caption{(a) The infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
-Each panel plots the history for six different zones of width $\delta R_{\rm gal}=0.1\kpc$, color-coded by Galactocentric radius.}
-    \label{fig:sfh}
-\end{figure}
-
-Figure \ref{fig:sfh} plots the star formation history of several different zones from our fiducial model with $y/Z_\odot=1$.
-In the inner Galaxy, the infall rate $\dot\Sigma_{\rm in}$ is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
-In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
-The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a maximum of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
-
-The thick-to-thin disk density ratio is especially important for our GCE models as it controls the quantity of gas accreted during each infall epoch.
-Our fiducial value of $f_\Sigma(R_\odot)=0.12$ is on the low end of literature estimates, which range from $f_\Sigma(R_\odot)\sim0.06-0.6$ \citep[e.g.,][]{gilmore_new_1983,siegel_star_2002,juric_milky_2008,mackereth_age-metallicity_2017,fuhrmann_local_2017}.
-Previous two-infall studies have adopted a similarly broad range of values (e.g., $f_\Sigma(R_\odot)=0.18$ from \citealt{spitoni_apogee_2021}; $f_\Sigma(R_\odot)=0.4$ from \citealt{spitoni_remind_2024}).
-We therefore explore values up to $f_\Sigma(R_\odot)=0.5$ in our multi-zone models in Section \ref{sec:multizone-results}.
-
-In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
-The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
-We investigate models where the infalling gas is pre-enriched, and its metallicity is described by
-\begin{equation}
-    \label{eq:pre-enrichment}
-    Z_{\rm in}(t) = (1 - e^{-t/\tau_{\rm rise}}) Z_\odot 10^{\mathXH_{\rm CGM}}.
-\end{equation}
-In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathFeH_{\rm CGM}$.
-Previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
-We assume the Solar-scaled metallicity of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
-% We also investigate cases where the CGM is $\alpha$-enhanced, i.e., $\mathOFe_{\rm CGM}>0$.
-
-\subsection{Infall Rate Parameter Selection}
-\label{sec:parameter-selection}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figures/infall_parameters.pdf}
-    \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters.
-In each panel, one parameter is varied according to the legend while the other two are held fixed.
-The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b).
-The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
-All models use the same fiducial parameters as the $R_{\rm gal}=8\kpc$ ring in the multi-zone models, with \yZ{1} and $\eta=0.2$.
-The black lines represent the same set of parameters in each panel.}
-    \label{fig:twoinfall-parameters}
-\end{figure*}
-
-% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
-% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
-Previous studies have adopted a wide range of parameters for Equation \ref{eq:twoinfall-ifr}.
-Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}.
-The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
-Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
-We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.3$.
-
-Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that 
-% the second infall timescale $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions. 
-the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
-A shorter $\tau_2$ produces a bigger loop and therefore a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
-We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is close to a constant infall rate, so a further increase in $\tau_2$ has diminishing effect.
-Between $\tau_2=3-30\,{\rm Gyr}$, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
-We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the size of the loop and width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times (see further discussion in Section \ref{sec:abundance-distributions}).
-This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}.
-% In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.
-
-In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
-Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1\Gyr$ in the inner disk and $\tau_2=7\Gyr$ at the Solar annulus.
-This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
-We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\Gyr$ at the Solar annulus and a scale radius $R_{\tau_2}=7\kpc$.
-This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
-We have also run models with a linear prescription and with a uniform value for $\tau_2$ and have found little difference in our key results.
-
-Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
-For $t_{\rm max}>2\Gyr$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
-The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}.
-We adopt a fiducial value of $t_{\rm max}=4.2\Gyr$, i.e.
-a lookback time of $9\Gyr$, which is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
-This ensures that our models are compatible with the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
-
-The Milky Way's last major merger with the dwarf galaxy, dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018}, has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
-Our fiducial value of $t_{\rm max}=4.2\Gyr$ places the start of the formation of the thin disk close to the GSE merger (within uncertainties), which likely occurred $\sim10\Gyr$ ago \citep[e.g.,][]{helmi_merger_2018,gallart_uncovering_2019,naidu_reconstructing_2021,woody_rapid_2025}.
-However, recent arguments suggest that the GSE merger would not have led to two-infall-like evolution because the mass ratio is too low to produce sufficient dilution \citet{orkney_milky_2025}.
-
-We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
-The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus, since they are one-zone models.
-In our multi-zone models, most of the high-$\alpha$ stars present in the Solar neighborhood have migrated from the inner Galaxy.
-
-\subsection{Stellar Migration}
-\label{sec:migration}
-
-This study is not the first to apply a prescription for radial migration to a two-infall GCE model.
-\citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
-They prescribed some fraction of stars from the inner and outer Galaxy which contribute to the local present-day population based on a constant migration speed, and they also assumed some fraction of stars born in the Solar neighborhood will have migrated elsewhere.
-This method can improve agreement with the observed local metallicity distribution, but does not scale to abundance distributions across the disk.
-\citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to the diffusion treatment of \citet{frankel_measuring_2018} and found similar results.
-Our implementation, described below, affects abundance distributions across the Galaxy, not just at the Solar annulus.
-
-% \citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
-They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
-This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
-They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
-Their only point of comparison with data is the local G-dwarf metallicity distribution.
-
-The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
-\begin{equation}
-    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\kpc}\Big)^{0.61},
-    \label{eq:radial-migration}
-\end{equation}
-where we adopt $\sigma_{\rm RM8}=2.68\kpc$ as the fiducial value for the strength of radial migration from \citet{dubay_galactic_2024}.
-This is smaller than the value of $\sigma_{\rm RM8}=3.6\kpc$ found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.
-
-All stellar populations are born at the Galactic midplane and are assigned a final midplane distance $z$ drawn from the distribution
-\begin{equation}
-    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)\,
-    {\rm \citep{spitzer_dynamics_1942}},
-    \label{eq:sech-pdf}
-\end{equation}
-where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The width of the distribution $h_z$ is given by
-\begin{equation}
-    h_z(\tau,R_{\rm final}) = \Big(\frac{0.24\kpc}{e^2}\Big) \exp\Big(\frac{\tau}{7\,{\rm Gyr}} + \frac{R_{\rm final}}{6\kpc}\Big).
-    \label{eq:scale-height}
-\end{equation}
-We note that the final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
-The parameters of Equations \ref{eq:radial-migration} and \ref{eq:scale-height} were chosen to fit the stellar migration patterns in the {\tt h277} hydrodynamical simulation \citep{christensen_implementing_2012}.
-A more complete discussion of the migration scheme and its consequences can be found in Appendix C of \citet{dubay_galactic_2024}.
-
-We note an important distinction between our method and that of \citet{spitoni_effect_2015}: SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
-This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
-Therefore, a significant fraction of SN Ia progenitors born in a given zone will enrich a different region of the Galaxy.
-
-\section{Multi-Zone Model Results}
-\label{sec:multizone-results}
-
 \subsection{Dilution \& Re-enrichment}
 \label{sec:age-abundance}
+
+% \subsubsection{The Solar Neighborhood}
 
@@
 
-Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions of mono-age populations in the Solar annulus.
+\todo{Section introduction.} Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions of mono-age populations in the Solar annulus.
 As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
@@
 
-We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models at $R_{\rm gal}=8\kpc$ on Figure \ref{fig:yield-outflow} for comparison.
+We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ on Figure \ref{fig:yield-outflow} for comparison.
 The models are in broad agreement with each other and with the data at lookback times of $\lesssim5\Gyr$.
@@
 % The dilution effect discussed in Section \ref{sec:yields} is clearly seen in our multi-zone model results.
-Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations predicted by models assuming different yield and outflow scales, \yZ{1} and \yZ{2}, and the fiducial parameters (Table \ref{tab:multizone-parameters}).
+Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations predicted by models assuming different yield and outflow scales, \yZ{1} and \yZ{2}, and the fiducial parameters (Table \ref{tab:parameters}).
 The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and noticeable abundance evolution at late times where the data show very little abundance evolution.
@@
 Figure \ref{fig:abundance-evolution-params} shows stellar age--abundance relations predicted by models with \yZ{1}.
-The model with the fiducial parameters (column (a); see Table \ref{tab:multizone-parameters}) shows similar discrepancies with the \citet{leung_variational_2023} age--[O/H] relation as in Figure \ref{fig:yield-outflow}.
+The model with the fiducial parameters (column (a); {\tt yZ1-fiducial}) shows similar discrepancies with the \citet{leung_variational_2023} age--[O/H] relation as in Figure \ref{fig:yield-outflow}.
 % a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and noticeable abundance evolution at late times where the data show very little abundance evolution.
@@
 The observed rise in the median metallicity of stars in the $6-10\Gyr$ age range could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the metal-rich inner Galaxy \citep{feuillet_age-resolved_2018}.
-Column (b) of Figure \ref{fig:abundance-evolution-params} presents a model with $y/Z_\odot=1$ and a stronger migration prescription of $\sigma_{\rm RM8}=5\kpc$.
+Column (b) of Figure \ref{fig:abundance-evolution-params} presents model {\tt yZ1-migration}, which has a stronger migration prescription of $\sigma_{\rm RM8}=5\kpc$.
 As a result, the stars that make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution at fixed age.
@@
 
-Next, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger that the fiducial value, $f_\Sigma(R_\odot)=0.5$.
+Next, we explore model {\tt yZ1-diskratio}, which has a local thick-to-thin disk surface density ratio $f_\Sigma(R_\odot)=0.5$, $\sim4$ times larger that the fiducial value.
 This choice places the ratio higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
@@
 
-Finally, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
+Finally, we investigate model {\tt yZ1-preenrich}, where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
@@
 The gray curve represents the total MDF in each region.
-Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters (see Table \ref{tab:multizone-parameters}) at different yield and outflow scales.
+Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters (see Table \ref{tab:parameters}) at different yield and outflow scales.
     % For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$. 
@@
 
-First, we substitute our fiducial SN Ia DTD with a simple power-law,
-\begin{equation}
-    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^{-1.1},
-    \label{eq:powerlaw-dtd}
-\end{equation}
+First, we substitute our fiducial SN Ia DTD with a simple power-law (Equation \ref{eq:powerlaw-dtd}),
 which reduces the median SN Ia delay time from $\sim2\,{\rm Gyr}$ to $\sim0.5\,{\rm Gyr}$.
@@
 These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but in this case they occupy a unique portion of the abundance space.
-A longer $\tau_1$ could shift this population to higher [O/Fe] where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
+A longer $\tau_1$ or smaller $t_{\rm max}$ could shift this population to higher [O/Fe] where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
 Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall model predicts a bimodal age distribution for metal-rich stars.

### 2025-07-15 src/tex/ms.tex
Manuscript updates

@@
 
+% \todo{Observational evidence other than $\alpha$-bimodality.} 
+The observed chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary motivation for the two-infall scenario.
+\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a period of reduced star formation, which is a natural consequence of the delay between the two accretion epochs.
+In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario.
+However, \citet{plotnikova_chemical_2024} found no evidence for multiple sequences in the local AMR, and argued that such patterns can arise due to selection effects.
+Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000,spitoni_remind_2024}, although most GCE models in the literature benchmark against these observables \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021}.
+
 \begin{figure}
@@
 While the strength and speed of radial migration in the disk are not precisely measured, a single chemical evolution track need not explain the entire width of the local abundance distribution.
-Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against
-
-% \todo{Observational evidence other than $\alpha$-bimodality.} 
-The observed chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary motivation for the two-infall scenario.
-\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a period of reduced star formation, which is a natural consequence of the delay between the two accretion epochs.
-In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario.
-However, \citet{plotnikova_chemical_2024} found no evidence for multiple sequences in the local AMR, and argued that such patterns can arise due to selection effects.
-Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000,spitoni_remind_2024}, although most GCE models in the literature benchmark against these observables \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021}.
+We illustrate this distinction in Figure \ref{fig:smooth-vs-twoinfall}, which contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
 
@@
 Models at a lower yield scale and weaker outflows predict slower re-enrichment.
-By contrast, the stellar age--metallicity relation is roughly constant over the past $\sim10\Gyr$.
+By contrast, the observed stellar age--metallicity relation is roughly constant over the past $\sim10\Gyr$.
 Pre-enriching the accreted gas can reduce the magnitude of the dilution, but not eliminate it entirely.
-    \item Due to this re-enrichment, our models predict that the MDF evolves to higher metallicity over time throughout the disk.
+    \item Due to this re-enrichment, our models predict that the MDF shifts to higher metallicity with decreasing age throughout the disk.
 This contrasts with the APOGEE data, which show very little change in the mode of the MDF over the past $\sim6-8$ Gyr.
     \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations.
-In contrast, the data show a smooth gradient between the oldest and youngest stars, with most of the metal-rich stars having intermediate ages.
+In contrast, the data show a unimodal age distribution, with most of the metal-rich stars having intermediate ages.
 This discrepancy could not be reconciled using any of the model variations we explored.
@@
 The apparent age-independence of stellar abundances in the disk places considerable restrictions upon the two-infall parameter space because it predicts a substantial dilution event at the start of the thin disk epoch.
-If the equilibrium scenario of \citet{johnson_milky_2024} is correct, then it restricts the two-infall scenario more than other GCE models.
+If the equilibrium scenario of \citet{johnson_milky_2024} is accurate, then it restricts the two-infall scenario more than other GCE models.
 Restrictions on the two-infall scenario also translate more broadly to other merger-dominated SFHs, which must explain the MW's $\alpha$-bimodality without significantly diluting the metallicity of the ISM.

### 2025-07-28 src/scripts/yields.py
remove outflows row from yield table

@@ -49,11 +49,11 @@ def make_column(elements = ['O', 'Fe'], mfeia=0.7, eta=outflows.yZ1):
     snia_labels.append('$N_{\\rm Ia}/M_\\star\\,[{\\rm M}_\\odot^{-1}]$')
     snia_yields.append('\\num{%.2e}' % (vice.yields.sneia.settings['fe'] / mfeia))
     # Yield-specific outflow parameters
-    outflow_params = [f'{eta.solar_value:.1f}']
-    outflow_labels = ['$\\eta_\\odot$']
+    # outflow_params = [f'{eta.solar_value:.1f}']
+    # outflow_labels = ['$\\eta_\\odot$']
     # All parameters and labels
-    params = ccsn_yields + snia_yields + outflow_params
-    labels = ccsn_labels + snia_labels + outflow_labels
+    params = ccsn_yields + snia_yields #+ outflow_params
+    labels = ccsn_labels + snia_labels #+ outflow_labels
     return params, labels
 
 if __name__ == '__main__':

### 2025-07-29 src/tex/ms.tex

@@
 % user-defined commands
+\newcommand{\GitHubURL}{https://github.com/lodubay/twoinfall}
 \newcommand{\vice}{{\tt VICE}\xspace}
@@
 
-Our second age catalog utilizes the [C/N]--age relation calibrated by \todo{Roberts et al.\ (2025, in preparation)} for red giant branch (RGB) and red clump stars.
+Our second age catalog utilizes the [C/N]--age relation calibrated by Roberts et al.\ (2025, submitted) for red giant branch (RGB) and red clump stars.
 The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
@@
 also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
-The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \todo{Roberts et al.\ (2025, in preparation)}, the propagated errors underestimate the true age dispersion, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
+The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by Roberts et al.\ (2025, submitted), the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
 With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
@@
 We inhibit star formation past $R_{\rm gal}>15.5\kpc$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
-This configuration results in $N=1,638,040$ stellar populations comtributing to metal enrichment in each model.
+This configuration results in $N=1,638,040$ stellar populations contributing to metal enrichment in each model.
 
 % We assign a final radius and midplane distance to each stellar population as described in Section \ref{sec:migration}. 
-We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the gas supply in Section \ref{sec:sfh}, the infall parameter selection in Section \ref{sec:parameter-selection}, the star formation law in Section \ref{sec:sf-law}, and the stellar migration prescription in Section \ref{sec:migration}.
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, the infall parameter selection in Section \ref{sec:parameter-selection}, and the stellar migration prescription in Section \ref{sec:migration}.
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
@@
 Our fiducial value of $t_{\rm max}=4.2\Gyr$ places the start of the formation of the thin disk close to the GSE merger (within uncertainties), which likely occurred $\sim10\Gyr$ ago \citep[e.g.,][]{helmi_merger_2018,gallart_uncovering_2019,naidu_reconstructing_2021,woody_rapid_2025}.
-However, recent arguments suggest that the GSE merger would not have led to two-infall-like evolution because the mass ratio is too low to produce sufficient dilution \citet{orkney_milky_2025}.
+However, recent arguments suggest that the GSE merger would not have led to two-infall-like evolution because the mass ratio is too low to produce sufficient dilution \citep{orkney_milky_2025}.
 
@@
 Note that we scatter simulated data points according to the median age and abundance errors in Table \ref{tab:uncertainties}, so the blurring impact of these statistical errors is incorporated in the model.
-The solid black curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
+The black dashed curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
 Despite the effects of radial migration and statistical errors, the stellar populations mostly scatter around this gas phase curve, at least for $\tau\lesssim9\Gyr$.
@@
 The discrepancies between the predicted and observed abundance evolution in the Solar neighborhood discussed in Section \ref{sec:age-abundance} persist across the Galactic disk.
-Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the \yZ{1} and \yZ{2} models with the fiducial parameters.
+Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models.
 For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in Section \ref{sec:observational-sample}.
@@
 The MDF shifts consistently toward high metallicity when moving from older to younger stars.
-The distance between the $1-2\Gyr$ and $2-4\Gyr$ age bins is smaller for the \yZ{2} model because of the faster approach to equilibrium (see also Figure \ref{fig:abundance-evolution-yields}).
+The distance between the $1-2\Gyr$ and $2-4\Gyr$ age bins is smaller for the \yZ{2} model because of the faster approach to equilibrium (see also Figure \ref{fig:yield-outflow}).
 In the Solar annulus (center column), the peak of the $6-8\Gyr$ old MDF is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
@@
 The two-infall model explains the chemical evolution of the thin disk through the low-$\alpha$ loop (see discussion in Section \ref{sec:parameter-selection}).
-However, inspection of the marginal [O/Fe] distributions in Figure \ref{fig:ofe-feh-density} reveals a different morphology of the low-$\alpha$ sequence: the two-infall model predicts two peaks in [O/Fe] in the thin disk where the data show only one.
-The location of the second peak, at intermediate [O/Fe], varies depending on the yields and model parameters (Figure \ref{fig:twoinfall-parameters}), but is always present.
+However, inspection of the marginal [O/Fe] distributions in Figure \ref{fig:ofe-feh-density} reveals a different morphology of the low-$\alpha$ sequence: the two-infall model predicts {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
+The location of the intermediate peak varies depending on the yields and model parameters (Figure \ref{fig:twoinfall-parameters}), but is always present.
 This morphology remains essentially consistent in our multi-zone models as well, despite the inclusion of radial mixing and vertical dispersion of stars.
@@
 
-In Section \ref{sec:abundance-distributions}, we showed that our high-yield models predict {\it three} peaks in the [O/Fe] distribution, which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
-Here, we attempt to mitigate the intermediate peak through several parameter choices.
+Next, we attempt to mitigate the intermediate peak through several parameter choices.
 % In Figure \ref{fig:ofe-distribution-parameters}, we show the result of our attempts to mitigate the intermediate-$\alpha$ peak discrepancy for the \yZ{2} yield set in a few different ways, namely by reducing the size of the thin disk loop seen in panel (b) of Figure \ref{fig:ofe-feh-density}.
@@
 We present the distributions in multiple bins of $|z|$ as well as $R_{\rm gal}$ because the observed pattern varies as a function of midplane distance, and because the APOGEE selection function over-emphasizes high-$|z|$, and therefore high-$\alpha$, stars in the full sample \citep[see Figure 5 from][]{vincenzo_distribution_2021}.
-The fiducial model (column a) predicts a high density of stars at $\mathOFe\approx+0.2$ where the data show a trough.
+The {\tt yZ2-fiducial} model (column a) predicts a high density of stars at $\mathOFe\approx+0.2$ where the data show a trough.
 The peak is most pronounced in the inner disk ($R_{\rm gal}=3-5\kpc$) because of the shorter infall timescale (see Figure \ref{fig:twoinfall-parameters}).
 
-First, we substitute our fiducial SN Ia DTD with a simple power-law (Equation \ref{eq:powerlaw-dtd}),
+First, we substitute our fiducial SN Ia DTD with a simple power-law (Equation \ref{eq:powerlaw-dtd}; {\tt yZ2-powerlaw}),
 which reduces the median SN Ia delay time from $\sim2\,{\rm Gyr}$ to $\sim0.5\,{\rm Gyr}$.
@@
 
-Next, in model (c) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
+Next, in model {\tt yZ2-diskratio} (column c) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
 This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates (see Section \ref{sec:sfh}).
@@
 
-Finally, in model (d) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
+Finally, in model {\tt yZ2-preenrich} (column dd) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
 We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars.
@@
 Motivated by the results of the previous sections, we construct a model which attempts to solve all of the issues that have been outlined thus far.
-Our ``best attempt'' model uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:abundance-evolution-yields}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
+Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
 Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate, and we believe more realistic, than in previous sections to avoid extreme effects resulting from the combination of these parameters.
@@
 
-Figure \ref{fig:ofe-feh-best} shows the stellar [O/Fe]--[Fe/H] distributions in different ranges of $R_{\rm gal}$ and $|z|$ color-coded by age as predicted by the best model.
+Figure \ref{fig:ofe-feh-best} shows the stellar [O/Fe]--[Fe/H] distributions in different ranges of $R_{\rm gal}$ and $|z|$ color-coded by age as predicted by the {\tt yZ2-best} model.
 This model is generally successful at reproducing the observed distribution, especially in the inner Galaxy and close to the midplane.
@@
 
-The model makes two notable predictions about the age--abundance distributions.
+The {\tt yZ2-best} model makes two notable predictions about the age--abundance distributions.
 First, there is a population of $\sim8-9\Gyr$ old stars at sub-Solar [O/Fe], especially at $|z|\ge0.5\kpc$, formed immediately after the second infall during a period of rapid chemical evolution.
@@
 While the models predict a fairly accurate distribution of stars in abundance space, especially for the low-$\alpha$ population, the stellar age patterns are starkly different.
-In both the \yZ{1} and \yZ{2} models, there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
+In both the {\tt yZ1-best} and {\tt yZ2-best} models (see Table \ref{tab:models}), there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
 The \yZ{2} model also predicts that the stars with the lowest [O/Fe] should be $\sim8-9\Gyr$ old, while these are some of the youngest stars in APOGEE.
@@
 
-\todo{Personal acknowledgements.} We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper.
+% Personal acknowledgements
+We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper. We would also like to thank Emanuele Spitoni for useful conversations about this work.
 
@@
 LOD acknowledges financial support from an Ohio State University Fellowship.
-JWJ acknowledges financial support from an Ohio State University Presidential Fellowship and a Carnegie Theoretical Astrophysics Center postdoctoral fellowship. \todo{Update grants and fellowships.}
+JWJ acknowledges financial support from a Carnegie Theoretical Astrophysics Center postdoctoral fellowship.
 
@@
 
-\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}.}
+\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}, NumPy \citep{harris_array_2020}, pandas \citep{jeff_reback_pandas-devpandas_2021,the_pandas_development_team_pandas-devpandas_2025}.}
 
@@
 
-\todo{Blah.}
+The figures, tables, and models in this paper are reproducible.
+The git repository associated to this study is publicly available at \url{\GitHubURL}, and the release \todo{v1.X.X} allows anyone to re-build the entire manuscript.
+The multi-zone model outputs and APOGEE sample dataset are stored at \todo{Zenodo URL}, and the source code for this manuscript is stored at \todo{Zenodo URL}.
 

### 2025-07-31 src/tex/ms.tex
Manuscript updates

@@
 A popular explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
-    % However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow.
 Thanks to recent advances in stellar age measurements, we can now compare this popular model to more direct measurements of the Galaxy's evolutionary timescales across the disk.
-    % We run multi-zone galactic chemical evolution models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
-We compare our model results to abundance patterns across the disk from APOGEE DR17, supplemented with stellar age estimates through multiple methods.
 We run multi-zone galactic chemical evolution models with a two-infall-driven star formation history and compare the results against abundance patterns across the disk from APOGEE DR17, supplemented with stellar ages estimated through multiple methods.
@@
 Second, most local metal-rich stars in APOGEE have intermediate ages, yet our models predict these stars should either be very old or very young.
-Some of these issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
-    % Restrictions upon the two-infall parameter space also limit the application of other merger-dominated star formation histories to the Milky Way.
+Some of these issues can be mitigated, but not completely resolved, by pre-enriching the accreted gas to low metallicity.
 These restrictions also place limits on the role of merger events in shaping the chemical evolution of the thin disk in general.
@@
 In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
-The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the kinematic thin disk.
+The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, has approximately Solar \aFe, and is associated with the kinematic thin disk.
 The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
@@
 An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and tentatively does not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}).
-Its presence and characteristics in our Galaxy could potentially have arisen to a unique evolutionary history.
+Its presence and characteristics in our Galaxy could potentially have arisen due to a unique evolutionary history.
 GCE models that attempt to solve this problem generally fall into two camps.
@@
 By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}.
-\citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
+\citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
 This degeneracy prohibits direct estimates of the yield scale from GCE models, unless the effect of outflows is assumed to be insignificant.
@@
 We illustrate this distinction in Figure \ref{fig:smooth-vs-twoinfall}, which contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
+If the effect of radial migration is significant, then the full local stellar abundance distribution can be explained without dramatic changes to the local gas abundance over time.
 
@@
 In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history.
-\citet{sharma_chemical_2021} and \citet{chen_chemical_2023} showed that a simultaneous decline in the star formation rate and the \aFe ratio is needed to separate the sequences in chemical space under this scenario.
+\citet{sharma_chemical_2021} and \citet{chen_chemical_2023} showed that a simultaneous decline in the star formation rate and the \aFe ratio is needed to separate the sequences in chemical space.
 \citet{chen_recent_2025} additionally argued that the double sequence in the local age--metallicity relation observed by \citet{nissen_high-precision_2020} can also be explained by a smooth star formation history and inside-out disk growth.
@@
 % \todo{Introduce equilibrium model.} 
-As stellar age estimation techniques have improved over recent years, large catalogs have become available with measurements for large samples of stars from a wide swath of the Galaxy.
+As stellar age estimation techniques have improved over recent years, large catalogs have become available with measurements for stars across a wide swath of the Galaxy.
 In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time,
@@
 We compare our multi-zone model predictions to the data in Section \ref{sec:multizone-results}.
-We discuss our results in Section \ref{sec:discussion} and summarize our conclusions in Section \ref{sec:conclusions}.
+We discuss possible extensions to our models in Section \ref{sec:discussion}, and we and summarize our conclusions in Section \ref{sec:conclusions}.
 
@@
 We obtain a sample of \num{171635} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}.
-Table \ref{tab:uncertainties} presents the median statistical uncertainty and uncertainty dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the calibrated [Fe/H] and [O/Fe] abundances for our sample.
+Table \ref{tab:uncertainties} presents the median statistical uncertainty and uncertainty dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the calibrated [Fe/H] and [O/Fe]\footnote{
+    In this paper, we use O as the representative $\alpha$-element in our GCE models and stellar abundance data.
+We refer to [O/Fe] and \aFe interchangeably, though observational studies often average several $\alpha$-element abundances to calculate \aFe.
+} abundances for our sample.
 When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\kpc$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}.
@@
 \subsection{Stellar Age Estimates}
+\label{sec:age-estimates}
 
@@
 
-Our second age catalog utilizes the [C/N]--age relation calibrated by Roberts et al.\ (2025, submitted) for red giant branch (RGB) and red clump stars.
+Our second age catalog utilizes the [C/N]--age relation calibrated by \citet[][submitted]{roberts_cn_2025} for red giant branch (RGB) and red clump stars.
 The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
@@
 also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
-The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by Roberts et al.\ (2025, submitted), the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
+The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
 With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
@@
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
-Table \ref{tab:parameters} summarizes the most relevant variables and their fiducial values in this work.
+Table \ref{tab:parameters} summarizes the model parameters and their fiducial values.
 
@@
         k                   & 1.5       & ---               & \ref{sec:sf-law}              & Star formation law exponent \citep{kennicutt_global_1998} \\
-        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & ---   & \ref{sec:sfh} & Total stellar mass of the disk \\
+        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & ---   & \ref{sec:sfh} & Total stellar mass of the disk \citep{licquia_improved_2015} \\
         f_\Sigma(R_\odot)   & 0.12      & 0.25, 0.5         & \ref{sec:sfh}                 & Local thick/thin disk surface density ratio \\
@@
     \centering
-    \caption{Nucleosynthetic yields and outflow prescriptions (see Section \ref{sec:yields}).}
+    \caption{Nucleosynthetic yields at each of the yield scales (see Section \ref{sec:yields}).}
     \include{output/yields.tex}
@@
 Equation \ref{eq:powerlaw-dtd} is consistent with SN Ia surveys \citep[e.g.,][]{maoz_star_2017} and results in more prompt Fe production.
-We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.
+We discuss the implications of using the power-law DTD in Section \ref{sec:abundance-distributions}.
 
@@
 where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the $e$-folding timescale of the star formation history, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
-Motivated by Equation \ref{eq:equilibrium}, we adopt the outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
-Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on age trends such as these.
+Motivated by Equation \ref{eq:equilibrium}, we adopt a different outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
+Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on stellar age trends.
+Table \ref{tab:models} reports the value of $\eta_\odot$ in each of our models.
 
@@
 Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
-Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023} or does not vary with radius \citep{hegedus_reconstructing_2025}.
+Even in studies that do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023} or does not vary with radius \citep{hegedus_reconstructing_2025}.
 To achieve a realistic radial metallicity gradient, many studies have adopted the yields of \citet{francois_evolution_2004} and a prescription for the infall timescale of the thin disk that increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
@@
 
-In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
+In detail, we calculate the star formation efficiency (SFE) timescale
 \begin{equation}
     \label{eq:sf-law}
-    \tau_\star = 
+    \tau_\star \equiv \frac{\Sigma_g}{\dot\Sigma_\star} = 
     \begin{cases}
         \varepsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
-        \varepsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
+        \varepsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0},
     \end{cases}
@@
 where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citep{leroy_star_2008}.
-Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through the pre-factor $\varepsilon$:
+Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through a pre-factor
 \begin{equation}
@@
 
-Figure \ref{fig:sfh} plots the star formation history of several different zones from our fiducial model with $y/Z_\odot=1$.
+Figure \ref{fig:sfh} plots the star formation history for several different zones from our fiducial model with $y/Z_\odot=1$.
 In the inner Galaxy, the infall rate $\dot\Sigma_{\rm in}$ is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
@@
 The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
-We investigate models where the infalling gas is pre-enriched, and its metallicity is described by
+We investigate models where the infalling gas is pre-enriched to a metallicity
 \begin{equation}
@@
 
-% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
-% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
-Previous studies have adopted a wide range of parameters for Equation \ref{eq:twoinfall-ifr}.
+Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
 Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}.
 The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
-Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
-We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.3$.
-
-Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that 
-% the second infall timescale $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions. 
-the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
-A shorter $\tau_2$ produces a bigger loop and therefore a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
+Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the corresponding effect on the stellar abundance distribution is small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
+It does, however, affect the position of the high-$\alpha$ peak, though this effect is more easily seen in the multi-zone model outputs.
+We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, similar to \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020}, \citet{spitoni_apogee_2021} or \citet{hegedus_reconstructing_2025}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.35$ in the multi-zone models.
+
+Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
+A shorter $\tau_2$ produces a bigger loop and therefore a broader MDF and [O/Fe] distribution, while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
 We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is close to a constant infall rate, so a further increase in $\tau_2$ has diminishing effect.
@@
 We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the size of the loop and width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times (see further discussion in Section \ref{sec:abundance-distributions}).
-This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}.
-% In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.
+This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020}, \citet{spitoni_apogee_2021}, and \citet{hegedus_reconstructing_2025}.
 
 In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
-Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1\Gyr$ in the inner disk and $\tau_2=7\Gyr$ at the Solar annulus.
+Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scaled $\tau_2$ linearly with radius, with $\tau_2\approx1\Gyr$ in the inner disk and $\tau_2=7\Gyr$ at the Solar annulus.
 This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
@@
 
-Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
+Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
 For $t_{\rm max}>2\Gyr$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
-The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}.
+The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}).
 We adopt a fiducial value of $t_{\rm max}=4.2\Gyr$, i.e.
-a lookback time of $9\Gyr$, which is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.
+a lookback time of $9\Gyr$, which is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021,hegedus_reconstructing_2025}.
 This ensures that our models are compatible with the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
@@
 We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
-The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the model outputs include only stars which were formed in-situ at the Solar annulus, since they are one-zone models.
+The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the one-zone model outputs include only stars formed in-situ at the Solar annulus.
 In our multi-zone models, most of the high-$\alpha$ stars present in the Solar neighborhood have migrated from the inner Galaxy.
@@
 \citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
-They prescribed some fraction of stars from the inner and outer Galaxy which contribute to the local present-day population based on a constant migration speed, and they also assumed some fraction of stars born in the Solar neighborhood will have migrated elsewhere.
-This method can improve agreement with the observed local metallicity distribution, but does not scale to abundance distributions across the disk.
-\citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to the diffusion treatment of \citet{frankel_measuring_2018} and found similar results.
-Our implementation, described below, affects abundance distributions across the Galaxy, not just at the Solar annulus.
+Assuming a constant migration speed, they prescribed some fraction of stars born in the inner and outer Galaxy that will contribute to the local present-day population, and they also assumed that some fraction of stars born in the Solar neighborhood will have migrated elsewhere by the present day.
+\citet{spitoni_effect_2015} improved agreement with the observed local metallicity distribution, but their method is difficult to apply to model predictions across the disk.
+Our implementation, based on the diffusion method of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
+\citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to that of \citet{frankel_measuring_2018} and found a similar effect on stellar abundance distributions.
 
@@
     \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}).
-The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
+The gray points plot the abundances of APOGEE stars in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
 The black points indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
@@
 
-\todo{Section introduction.} Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions of mono-age populations in the Solar annulus.
+The two-infall scenario requires a large quantity of pristine or low-metallicity gas to be accreted onto the disk over a short span of time.
+As a natural consequence, the gas disk experiences a period of metal dilution, which should be recorded in the stellar record.
+Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions of mono-age populations in the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
 As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
 In agreement with recent work (see discussion in Section \ref{sec:introduction}), the trend with age is interestingly flat.
-[O/H] and [Fe/H] increase by $0.1-0.2\dex$ in the $\sim6-8\Gyr$ range of ages relative to young stars, likely due to metal-rich stars migrating outward from the inner Galaxy where the surface densities are higher.
+[O/H] and [Fe/H] increase by $0.1-0.2\dex$, relative to young stars, in the $\sim6-8\Gyr$ age range, likely due to metal-rich stars migrating outward from the inner Galaxy where the surface densities are higher.
 
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\onecolumn]{figures/abundance_evolution_yields.pdf}
-%     \caption{Stellar age--abundance relations predicted by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
-Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
-A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
-For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
-The black curve plots the ISM abundance at $R_{\rm gal}=8\kpc$ over time.
-The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin.
-Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
-{\bf Key takeaway:} Both models feature a major dilution event at a lookback time of 9 Gyr, and for model (a) the dilution persists throughout much of the thin disk epoch.}
-%     \label{fig:abundance-evolution-yields}
-% \end{figure}
-
-% The dilution effect discussed in Section \ref{sec:yields} is clearly seen in our multi-zone model results.
-Figure \ref{fig:abundance-evolution-yields} shows stellar age--abundance relations predicted by models assuming different yield and outflow scales, \yZ{1} and \yZ{2}, and the fiducial parameters (Table \ref{tab:parameters}).
-The \yZ{1} model (column a) shows two clear discrepancies with the \citet{leung_variational_2023} age--abundance relation: a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and noticeable abundance evolution at late times where the data show very little abundance evolution.
-The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed by SNe Ia.
-The \yZ{2} yield set (column b) mitigates both of these issues by shortening the time it takes the ISM metallicity to rebound, producing a much flatter abundance curve at late times.
-However, model (b) produces a poorer fit to the age--[O/Fe] relation: the decline in [O/Fe] over the thin disk epoch is steeper than the data, especially for ages $\sim4-8\,{\rm Gyr}$.
-Note that we scatter simulated data points according to the median age and abundance errors in Table \ref{tab:uncertainties}, so the blurring impact of these statistical errors is incorporated in the model.
-The solid black curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
-Despite the effects of radial migration and statistical errors, the stellar populations mostly scatter around this gas phase curve, at least for $\tau\lesssim9\Gyr$.
-
 \begin{figure*}
@@
 The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$ over time, and the black squares plot the median stellar abundance in in {2 Gyr}-wide age bins.
-The red line and points plot the median abundance for APOGEE stars in each age bin, and the shaded regions represent the 16th--84th abundance percentiles.
-Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
-    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$ and a higher mass-loading factor $\eta_\odot=0.6$.
-{\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
+The red line and points plot the median abundance for APOGEE stars in each age bin, and the shaded regions represent the 16th--84th percentiles of stellar abundances.
+We adopt the NN age estimates for APOGEE stars from \citet{leung_variational_2023}.
+    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).
+{\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither can simultaneously match all of the observed age--abundance relation.}
     \label{fig:abundance-evolution-params}
@@
 
-Chemical evolution models which assume the \yZ{1} empirical yield scale already struggle to match the local age--metallicity relation, even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
+Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation, even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
 The problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
@@
 Figure \ref{fig:abundance-evolution-params} shows stellar age--abundance relations predicted by models with \yZ{1}.
-The model with the fiducial parameters (column (a); {\tt yZ1-fiducial}) shows similar discrepancies with the \citet{leung_variational_2023} age--[O/H] relation as in Figure \ref{fig:yield-outflow}.
-% a major $\sim0.5$ dex dilution at a lookback time of $\sim9\,{\rm Gyr}$ near where the data show a maximum in [O/H], and noticeable abundance evolution at late times where the data show very little abundance evolution.
+The model with the fiducial parameters (column (a); {\tt yZ1-fiducial}) shows similar discrepancies with the \citet{leung_variational_2023} NN age--[O/H] relation as in Figure \ref{fig:yield-outflow}.
 The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed by SNe Ia.
@@
 
-We next attempt to mitigate the dilution and late-time evolution problems for the empirical (\yZ{1}) yield scale. 
-The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$, and (d) the metallicity of the infalling gas $\mathXH_{\rm CGM}$.
-
-The observed rise in the median metallicity of stars in the $6-10\Gyr$ age range could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the metal-rich inner Galaxy \citep{feuillet_age-resolved_2018}.
+We next attempt to mitigate the dilution and late-time evolution problems for the \yZ{1} yield scale. 
+% The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$, and (d) the metallicity of the infalling gas $\mathXH_{\rm CGM}$.
+First, the observed rise in the median metallicity of stars in the $6-10\Gyr$ age range could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the metal-rich inner Galaxy \citep{feuillet_age-resolved_2018}.
 Column (b) of Figure \ref{fig:abundance-evolution-params} presents model {\tt yZ1-migration}, which has a stronger migration prescription of $\sigma_{\rm RM8}=5\kpc$.
@@
 Next, we explore model {\tt yZ1-diskratio}, which has a local thick-to-thin disk surface density ratio $f_\Sigma(R_\odot)=0.5$, $\sim4$ times larger that the fiducial value.
-This choice places the ratio higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
-Column (c) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase.
-The model produces the best agreement with the observed age--[Fe/H] relation (second row).
-However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting a trend much flatter than observed, underpredicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.
+This is higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}).
+Column (c) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM because more of the gas disk is built up during the first infall phase.
+Model {\tt yZ1-diskratio} produces the best agreement out of the four with the observed age--[Fe/H] relation (second row).
+However, agreement with the observed age--[O/Fe] relation is poor.
+The model predicts a much flatter trend than observed, under-predicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.
 
@@
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
-Pre-enriched infall raises the equilibrium metallicity, so we increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity.
+Pre-enriched infall also raises the equilibrium metallicity, so we increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity.
 Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
-The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced since the accreting gas is less chemically different from the ISM, diminishing the effects of dilution.
-The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity---an effect which can be compensated by a slightly increased value of $\eta$.
+The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, since the accreting gas is less chemically different from the ISM, diminishing the effects of dilution.
 This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.
@@
 The gray curve represents the total MDF in each region.
-Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters (see Table \ref{tab:parameters}) at different yield and outflow scales.
-    % For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$. 
+Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters (see Table \ref{tab:models}) at different yield and outflow scales.
 A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}.
-Row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}).
+Row (c) presents the distributions from APOGEE with ages derived from [C/N] abundances by \citet{roberts_cn_2025} (see Section \ref{sec:age-estimates}).
 The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\kpc$ age bin for reference.
@@
 The distributions in all panels are restricted to $0\leq|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
-{\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both GCE models predict a steady evolution toward higher [Fe/H] with time.}
+{\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both two-infall models predict a steady evolution toward higher [Fe/H] with time.}
     \label{fig:mdf-evolution}
@@
 The oldest age bin in Figure \ref{fig:mdf-evolution} shows distinct behavior in both the models and data.
-The $8-10\Gyr$ age bin spans both the tail end of the thick disk phase and the beginning of the thin disk, so the MDF is bimodal.
-In the models, the higher peak consists of $>9\Gyr$ old stars (pre-dilution), and the lower peak $8-9\Gyr$ old stars (post-dilution).
-Intriguingly, the APOGEE MDF in that age bin is also bimodal in all but the outer-most radial bin, with peaks at $\mathFeH\approx-0.3$ and $+0.3$ independent of the location in the Galaxy.
+The $8-10\Gyr$ age bin spans both the tail end of the thick disk phase and the beginning of the thin disk, so the MDF is much broader than in other age bins.
+In the models, the main, metal-poor peak consists of $8-9\Gyr$ old stars (post-dilution), and the extended high-[Fe/H] tail consists of $>9\Gyr$ old stars (pre-dilution).
+Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in all but the outer-most radial bin, peaking at $\mathFeH\approx-0.3$ and $+0.3$ independent of the location in the Galaxy.
 While the data and the models show qualitatively similar behavior, they actually represent different populations.
@@
 Stars in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $0\leq|z|<2\kpc$.
-{\bf Key takeaway:} the two-infall model generically predicts a stellar over-density at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.}
+{\bf Key takeaway:} both models predict a stellar over-density at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.}
     \label{fig:ofe-feh-density}
@@
 
-The two-infall model explains the chemical evolution of the thin disk through the low-$\alpha$ loop (see discussion in Section \ref{sec:parameter-selection}).
-However, inspection of the marginal [O/Fe] distributions in Figure \ref{fig:ofe-feh-density} reveals a different morphology of the low-$\alpha$ sequence: the two-infall model predicts {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
-The location of the intermediate peak varies depending on the yields and model parameters (Figure \ref{fig:twoinfall-parameters}), but is always present.
+In the two-infall scenario, the low-$\alpha$ loop governs the chemical evolution of the thin disk (see discussion in Section \ref{sec:parameter-selection}).
+However, careful inspection of the marginal [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} reveals a different morphology: the models predict {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
+The location of the intermediate peak varies depending on the yields and model parameters, but is always present.
 This morphology remains essentially consistent in our multi-zone models as well, despite the inclusion of radial mixing and vertical dispersion of stars.
@@
 
-Additionally, the shape of the low-$\alpha$ sequence predicted the model results (a concave-down ``comma'') is different from the data (a concave-up ``swoosh'').
+Additionally, the shape of the low-$\alpha$ sequence predicted by the models (a concave-down ``comma'') is different from the data (a concave-up ``swoosh'').
 This is a subtle distinction, on the $\sim0.05\dex$ level in [O/Fe].
@@
 
-% \subsection{Global Abundance Distributions}
-% \label{sec:disk-abundances}
-
-% \subsubsection{The [O/Fe] Distribution}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\onecolumn]{src/tex/figures/ofe_distribution_yields.pdf}
-%     \caption{Normalized stellar [O/Fe] distributions produced by multi-zone models which assume the fiducial parameters with different yield sets and outflow mass-loading factors.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/ofe_distributions.pdf}
+    \caption{Normalized stellar [O/Fe] distributions predicted by multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e).
 Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row.
@@
 For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
-{\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent in the \yZ{2} model at mid to high latitudes.}
-%     \label{fig:ofe-distribution-yields}
-% \end{figure}
-
-% The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution, which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence.
-We previously noted this feature in \citet{dubay_galactic_2024}.
-Figure \ref{fig:ofe-distribution-yields} compares [O/Fe] distributions from across the Galactic disk produced by models with the \yZ{1} and \yZ{2} yield sets.
-We present the distributions in multiple bins of $|z|$ as well as $R_{\rm gal}$ because the observed pattern varies as a function of midplane distance, and because the APOGEE selection function over-emphasizes high-$|z|$, and therefore high-$\alpha$, stars in the full sample \citep[see Figure 5 from][]{vincenzo_distribution_2021}.
-For model (a) with $y/Z_\odot=1$, the two thin disk peaks are close enough together that they approximate a single peak, especially once observational uncertainties are factored in.
-With the \yZ{2} yield set, however, there is a $\sim0.2$ dex separation between the low- and intermediate-$\alpha$ peaks thanks to increased efficiency of CCSN element production.
-As a result, model (b) predicts a high density of stars at $\mathOFe\approx+0.2$ where the data show a relatively low density.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{src/tex/figures/ofe_distributions.pdf}
-    \caption{Normalized stellar [O/Fe] distributions predicted by multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). 
-    % The layout is similar to Figure \ref{fig:ofe-distribution-yields}. 
-    Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row.
-Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
-The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
-For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
-    Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$
-    % (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); 
-    {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$.
+    Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, {\tt yZ2-fiducial}; {\bf (b)} a model with a power-law DTD, {\tt yZ2-powerlaw}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\tt yZ2-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ2-preenrich} (see Table \ref{tab:models} for details).
 {\bf Key takeaway:} For the \yZ{2} case, a higher thick-to-thin disk ratio or pre-enrichment of the accreted gas can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
@@
 Next, we attempt to mitigate the intermediate peak through several parameter choices.
-% In Figure \ref{fig:ofe-distribution-parameters}, we show the result of our attempts to mitigate the intermediate-$\alpha$ peak discrepancy for the \yZ{2} yield set in a few different ways, namely by reducing the size of the thin disk loop seen in panel (b) of Figure \ref{fig:ofe-feh-density}.
 Figure \ref{fig:ofe-distribution-parameters} compares [O/Fe] distributions from across the Galactic disk predicted by models with \yZ{2}.
 We present the distributions in multiple bins of $|z|$ as well as $R_{\rm gal}$ because the observed pattern varies as a function of midplane distance, and because the APOGEE selection function over-emphasizes high-$|z|$, and therefore high-$\alpha$, stars in the full sample \citep[see Figure 5 from][]{vincenzo_distribution_2021}.
-The {\tt yZ2-fiducial} model (column a) predicts a high density of stars at $\mathOFe\approx+0.2$ where the data show a trough.
+The {\tt yZ2-fiducial} model (column (a)) predicts a high density of stars at $\mathOFe\approx+0.2$, where the data instead show a trough.
 The peak is most pronounced in the inner disk ($R_{\rm gal}=3-5\kpc$) because of the shorter infall timescale (see Figure \ref{fig:twoinfall-parameters}).
@@
 As shown in column (b), this has the intended effect on the low-$\alpha$ sequence, but it also entirely eliminates the high-$\alpha$ peak.
-\citet{dubay_galactic_2024} discuss in detail why such a DTD is disfavored by Milky Way stellar abundances, and their results hold true for the two-infall model as well.
-% In columns (c) and (d) of Figure \ref{fig:ofe-df}, we attempt to mitigate the issue of the intermediate-$\alpha$ peak for the $y/Z_\odot=2$ yield set.
-Model (c) switches out our fiducial DTD with a power-law DTD, which decreases the timescale for Fe production.
-However, as shown by \citet{dubay_galactic_2024}, models with a power-law DTD struggle to reproduce the high-$\alpha$ sequence for a wide range of star formation histories, and the results are no different for this two-infall model.
-
-Next, in model {\tt yZ2-diskratio} (column c) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
-This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates (see Section \ref{sec:sfh}).
+\citet{dubay_galactic_2024} discuss in detail why such a DTD is disfavored by Milky Way stellar abundances for several different SFHs including for the two-infall scenario.
+
+Next, in model {\tt yZ2-diskratio} (column (c)) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
+This value means that 1 in 3 stars in the Solar annulus belong to the thick disk, which is on the high end of estimates (see Section \ref{sec:sfh}).
 The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the other models.
 
-Finally, in model {\tt yZ2-preenrich} (column dd) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
-We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars.
+Finally, in model {\tt yZ2-preenrich} (column (d)) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times. 
+% We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars. 
 This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
-We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
+We assume that the infalling gas has $\mathOFe_{\rm CGM}=0$ at all times; an alternate model with $\mathOFe_{\rm CGM}=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
 In summary, either an enhanced disk mass ratio or pre-enriched infall can improve agreement with the observed thin disk abundances for the \yZ{2} case.
@@
 Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age.
-A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm [C/N]}$) and abundance uncertainties in Table \ref{tab:uncertainties}.
+A Gaussian scatter is applied to each point according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}.
 The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region.
@@
 
-Motivated by the results of the previous sections, we construct a model which attempts to solve all of the issues that have been outlined thus far.
+Motivated by the results of the previous sections, we attempt to construct a model that solves all of the issues that have been outlined thus far.
 Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
-Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate, and we believe more realistic, than in previous sections to avoid extreme effects resulting from the combination of these parameters.
+Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate, and we believe more realistic, than in previous sections to avoid extreme effects resulting from the combination of all of these parameters.
 We stress that our focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters through methods such as MCMC.
@@
 Figure \ref{fig:ofe-feh-best} shows the stellar [O/Fe]--[Fe/H] distributions in different ranges of $R_{\rm gal}$ and $|z|$ color-coded by age as predicted by the {\tt yZ2-best} model.
-This model is generally successful at reproducing the observed distribution, especially in the inner Galaxy and close to the midplane.
+This model is generally successful at reproducing the observed abundance distributions, especially in the inner Galaxy and close to the midplane.
 However, the predicted high-$\alpha$ sequence has a significant presence even in the outer Galaxy---likely a consequence of the stronger migration prescription and higher thick-to-thin disk ratio.
-In general, the predicted distributions do not align with the data as well at large midplane distances ($1\leq|z|<2\kpc$), but this may partly be due to our prescription for vertical heating (see Section \ref{sec:migration}).
+In general, the predicted distributions do not align with the data as well at large midplane distances ($1\leq|z|<2\kpc$), but this may reflect inaccuracies in our prescription for vertical heating (see Section \ref{sec:migration}).
 
@@
 First, there is a population of $\sim8-9\Gyr$ old stars at sub-Solar [O/Fe], especially at $|z|\ge0.5\kpc$, formed immediately after the second infall during a period of rapid chemical evolution.
-These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but in this case they occupy a unique portion of the abundance space.
-A longer $\tau_1$ or smaller $t_{\rm max}$ could shift this population to higher [O/Fe] where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
-Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall model predicts a bimodal age distribution for metal-rich stars.
+These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but they occupy a unique portion of the abundance space.
+A longer $\tau_1$ or smaller $t_{\rm max}$ could shift this population to higher [O/Fe], where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
+Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
+The following section explores this second prediction in greater detail.
 
@@
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
-The left and center panels plot the output of our best two-infall models, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$.
+The left and center panels plot the output of the {\tt yZ1-best} and {\tt yZ2-best} models, with ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$ (see Table \ref{tab:models}).
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the abundances and ages according to Table \ref{tab:uncertainties}.
-The right panel plots the results from APOGEE using the \citet{leung_variational_2023} age catalog.
+The right panel plots the results from APOGEE using the \citet{leung_variational_2023} NN age catalog.
 The contours indicate the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
     {\it Bottom}: Stellar age distributions in the Solar annulus for all stars (black) and LMR stars (gray).
-The left and center panels plot the mass-weighted age distributions predicted by the models after forward-modeling age uncertainties, and the right panel plots the \citet{leung_variational_2023} ages for APOGEE stars.
-    {\bf Key takeaway:} The two-infall models predict a fundamentally different age pattern than what is observed, especially for LMR stars.}
+The left and center panels plot the mass-weighted age distributions predicted by the models after forward-modeling age uncertainties, and the right panel plots the NN ages for APOGEE stars.
+    {\bf Key takeaway:} Both two-infall models predict a fundamentally different age pattern than what is observed, especially for LMR stars.}
     \label{fig:lmr-ages}
@@
 
-The two-infall scenario makes a fundamental prediction about the local stellar age distribution: the most metal-rich stars born in-situ in any region of the Galaxy should come from the metal-rich tail of the first infall sequence, and are therefore older than all of the thin disk stars.
-As noted in the previous Section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.
-We investigate this prediction further here.
-
-The top row of Figure \ref{fig:lmr-ages} presents the median stellar age as a function of [O/Fe] and [Fe/H] for two multi-zone models and in APOGEE.
+The two-infall scenario makes a fundamental prediction about the local stellar age distribution: the most metal-rich stars born in-situ in any region of the Galaxy should come from the metal-rich tail of the first infall sequence, and should therefore be older than all of the thin disk stars.
+As noted in the previous section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.
+The top row of panels in Figure \ref{fig:lmr-ages} presents the median stellar age as a function of [O/Fe] and [Fe/H] predicted by the {\tt yZ1-best} and {\tt yZ2-best} models (see Table \ref{tab:models}) and observed in APOGEE using the \citet{leung_variational_2023} NN ages.
 While the models predict a fairly accurate distribution of stars in abundance space, especially for the low-$\alpha$ population, the stellar age patterns are starkly different.
-In both the {\tt yZ1-best} and {\tt yZ2-best} models (see Table \ref{tab:models}), there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
+In both models, there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
 The \yZ{2} model also predicts that the stars with the lowest [O/Fe] should be $\sim8-9\Gyr$ old, while these are some of the youngest stars in APOGEE.
@@
     While the amplitude of the peaks is sensitive to the precise location of the LMR cutoff, the dearth of intermediate-age stars is robust to adjustments of $\pm0.05\dex$.
-} For APOGEE, the distributions are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
+} For APOGEE, the distributions of all stars and only LMR stars are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
 Our two-infall models predict an overall age distribution that is similar to the data, but both models predict a distinctly bimodal age distribution for LMR stars.
@@
 A dearth of intermediate-age, high-metallicity stars is a natural outcome of a substantial dilution event, which is a defining feature of the two-infall scenario.
-None of the adjustments that we explored in Figure \ref{fig:abundance-evolution-params} substantially increase the proportion of intermediate-age stars.
+None of the adjustments that we explored in Sections \ref{sec:age-abundance} or \ref{sec:abundance-distributions} substantially increase the proportion of intermediate-age stars.
 
@@
 We have explored a wide range of parameter space, but our investigation is not intended to be exhaustive.
-In the remainder of this Section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.
+In this section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.
 
@@
 In contrast to the two-infall model of \citet{spitoni_apogee_2021}, which predicted a present-day gas metallicity of ${\rm [M/H]}\approx+0.3$ in the Solar neighborhood, \citet{spitoni_beyond_2023} argued that the gas dilution resulting from the third infall could explain a population of young stars with slightly sub-Solar abundances discovered in {\it Gaia} DR3 \citep{recio-blanco_gaia_2023}.
-% \citet{palla_mapping_2024} were similarly motivated by the finding that open clusters with ages $<1\Gyr$ have similar metallicity to those with ages $>3\Gyr$, while the classical two-infall model predicted a steady increase in metallicity over time.
-However, \citet{palla_mapping_2024} invoke a less massive infall, producing a milder dilution event, than \citet{spitoni_beyond_2023}.
 
 Similarly, \citet{palla_mapping_2024} invoked a late-time accretion episode to explain largely age-independent metallicites in open clusters across the disk.
-Open clusters trace younger populations: most of their clusters are $\lesssim2\Gyr$ old.
+Open clusters trace younger populations, and most of their clusters are $\lesssim2\Gyr$ old.
 A third infall can help explain trends within this limited age range, but when compared to the full range of stellar age data, it faces the same challenges as the second infall.
@@
 
-In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2024} demonstrated to improve agreement with age trends across the Galactic disk.
+In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2024} demonstrated can improve agreement with age trends across the Galactic disk.
 Johnson et al.
@@
 This approach allows us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
-A radial gas flow requires at least one assumption about the processes that drive the flow and generally do not afford the same level of flexibility.
+A radial gas flow requires at least one assumption about the processes that drive the flow and generally does not afford the same level of flexibility.
 We have therefore focused on models with outflows in this paper for the sake of simplicity, and we clarify that some, but not all, radial gas flow models should have similar effects.
@@
 During the quiescent period, the [O/Fe] ratio slowly declines due to the delayed contribution of Fe from SNe Ia.
-Meanwhile, the gas mass continues to increase even as star formation is suppressed.
+Meanwhile, the gas mass continues to increase through accretion even as star formation is suppressed.
 When $\tau_\star$ is lowered at the end of the quiescent period, it sparks a moderate star formation burst which causes stellar abundances to ``pile up'' at similar [O/Fe] values.
@@
 This contrasts with the APOGEE data, which show very little change in the mode of the MDF over the past $\sim6-8$ Gyr.
-    \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations.
-In contrast, the data show a unimodal age distribution, with most of the metal-rich stars having intermediate ages.
+    \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations: local metal-rich stars should either be very old or very young.
+In contrast, the data show a broad, unimodal age distribution, with most of the metal-rich stars having intermediate ages.
 This discrepancy could not be reconciled using any of the model variations we explored.
@@
 
-We note that we have not found a GCE model which is capable of reproducing all of the above observations.
+We note that we have not found a GCE model, two-infall or otherwise, that is capable of reproducing all of the above observations.
 The ``inside-out'' models of \citet{johnson_stellar_2021} are better able to predict a slowly evolving metallicity gradient, but they do not predict an $\alpha$-bimodality.
@@
 % Personal acknowledgements
-We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper. We would also like to thank Emanuele Spitoni for useful conversations about this work.
+We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper. We also thank Dr.\ Emanuele Spitoni for useful conversations about this work.
 
@@
 
-\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}, NumPy \citep{harris_array_2020}, pandas \citep{jeff_reback_pandas-devpandas_2021,the_pandas_development_team_pandas-devpandas_2025}.}
+\software{\vice \citep{johnson_impact_2020}, Astropy \citep{astropy_collaboration_astropy_2013,astropy_collaboration_astropy_2018,astropy_collaboration_astropy_2022}, scikit-learn \citep{pedregosa_scikit-learn_2011}, SciPy \citep{virtanen_scipy_2020}, Matplotlib \citep{hunter_matplotlib_2007}, NumPy \citep{harris_array_2020}, pandas \citep{reback_pandas-devpandas_2021,the_pandas_development_team_pandas-devpandas_2025}.}
 
@@
 The git repository associated to this study is publicly available at \url{\GitHubURL}, and the release \todo{v1.X.X} allows anyone to re-build the entire manuscript.
-The multi-zone model outputs and APOGEE sample dataset are stored at \todo{Zenodo URL}, and the source code for this manuscript is stored at \todo{Zenodo URL}.
+The multi-zone model outputs are stored at \todo{Zenodo URL}, and the source code for this manuscript is stored at \todo{Zenodo URL}.
 

### 2025-07-31 src/scripts/lmr_ages.py
update plot labels

@@ -19,8 +19,8 @@ OUTPUT_NAMES = [
     'yZ2/best/cgm07_ratio025_eta18_migr36/diskmodel'
 ]
 LABELS = [
-    r'Two-Infall ($y/Z_\odot=1$)',
-    r'Two-Infall ($y/Z_\odot=2$)'
+    r'(a) Two-Infall ($y/Z_\odot=1$)',
+    r'(b) Two-Infall ($y/Z_\odot=2$)'
 ]
 AGE_COL = 'L23_AGE'
 LMR_CUT = 0.1 # lower bound of locally metal-rich (LMR) stars
@@ -104,7 +104,7 @@ def main(style='paper', cmap='Spectral_r'):
         #             histtype='bar', color='gray', rwidth=0.8,)
     
     # APOGEE
-    axs[0,2].set_title('APOGEE (NN ages)')
+    axs[0,2].set_title('(c) APOGEE (NN ages)')
     pcm1 = axs[0,2].hexbin(
         local_sample('FE_H'), local_sample('O_FE'),
         C=local_sample(AGE_COL),

### 2025-07-31 src/tex/ms.tex
Fix references, remove comments

@@
 \usepackage{graphicx}
-% \usepackage{layouts}
 \usepackage{xcolor}
-% \usepackage{upgreek}
 \let\tablenum\relax
@@
 % Author list
-% \author[]{Amanda Ash}
 \author[0000-0003-3781-0747]{Liam O.\ Dubay}
@@
 \affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
-% \affiliation{\osuaffil}
-% \affiliation{\ccappaffil}
 \author[0000-0002-2854-5796]{John D.\ Roberts}
@@
 \affiliation{\ccappaffil}
-% \author[0000-0001-7775-7261]{David H. Weinberg}
-% \author{coauthors}
 
@@
 
-% \todo{Hook, summary of alpha-bimodality.}
 \lettrine{G}{alactic chemical evolution} (GCE) aims to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
@@
 Others argue for a bursty star formation history driven by multiple accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023}.
-% Studies of simulations have suggested that the $\alpha$-bimodality could be driven by clumpy star formation at high redshift \citep{clarke_imprint_2019}, a major gas-rich merger \citep{buck_origin_2020}, or re-accretion of metal-rich outflows \citep{khoperskov_bimodality_2021}.
-
-% Summary of two-infall literature
+
 The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks.
@@
 
-% \todo{Outflows.} 
 While previous studies have explored a large parameter space, most have assumed that the Galactic disk never ejected a substantial outflow.
@@
 
-% \todo{Observational evidence other than $\alpha$-bimodality.} 
 The observed chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary motivation for the two-infall scenario.
@@
 
-% \todo{Migration.} 
 Previous two-infall models have reproduced the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
@@
 
-% \todo{Summary of secular evolution models which claim alpha-bimodality.} 
 In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
@@
 
-% By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}.
-% \citet{kubryk_evolution_2015} produce two parallel sequences in \aFe vs [Fe/H] by making a simple age cut to the results of their multi-zone GCE model, though because they do not present stellar \aFe distributions it is hard to determine whether their distributions are truly bimodal.
-In the model of \citet{sharma_chemical_2021}, a sharp transition in stellar \aFe for $8-12\Gyr$ old stars plus radial migration are the key ingredients for predicting a MW-like bimodality; however, their approach to the chemical evolution is not {\it ab initio}, meaning that instead of integrating the enrichment equations for their adopted star formation history, they simply assume a functional form for the abundance evolution over time \todo{(rewrite)}.
-\todo{Sharma basically says that it's possible to have a continuous star formation history and reproduce the $\alpha$-bimodality.} \citet{chen_chemical_2023} confirmed the findings of \citet{sharma_chemical_2021} in an {\it ab initio} multi-zone GCE model (with a two-phase ISM and radial gas flows but no outflows) and were able to produce a bimodal \aFe distribution; however, some discrepancies remain, including that the metallicity of the high-$\alpha$ sequence is too low and not extended enough.
-\citet{chen_chemical_2023} found that the abundance gap is caused by the simultaneous decline in SFR and \aFe.
-% \citet{prantzos_origin_2023} attribute the formation of their thick disk to a combination of inside-out disk formation and radial migration causing thick disk stars from the inner galaxy to end up in the Solar circle.
-% \citet{chen_recent_2025} argue that the double age--metallicity sequences observed by \citet{nissen_high-precision_2020} can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.
-\todo{Trim this WAY down.}
-
-% \todo{Introduce equilibrium model.} 
 As stellar age estimation techniques have improved over recent years, large catalogs have become available with measurements for stars across a wide swath of the Galaxy.
-In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time,
-% \citet{johnson_milky_2024} examined the age--metallicity relation at different radii from the astroNN catalog \citep{mackereth_dynamical_2019} and found that the mode of the metallicity distribution at a given radius is nearly independent from age over the past $\sim9\Gyr$.
-They propose an
-these catalogs have indicated that stellar metallicities are remarkably consistent with age across most of the thin disk epoch \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
+In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs have indicated that stellar metallicities are remarkably consistent with age across most of the thin disk epoch \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
 \citet{johnson_milky_2024} demonstrated that these results are readily explained by a scenario in which the Galaxy reaches a state of chemical equilibrium.
@@
 
-% In light of the findings of \citet{johnson_milky_2024} and a new empirical yield scale from \citet{weinberg_scale_2024}, we evaluate the predictions of the two-infall model against stellar age and abundance data across the MW disk.
 Relative to even a few years ago, the availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
 Our study draws on the steadiness of the Milky Way stellar metallicity gradient found by \citet{johnson_milky_2024} and empirical constraints on the yield scale from \citet{weinberg_scale_2024}.
-% \todo{Goal and summary of paper.} 
 We run multi-zone GCE models with a two-infall accretion history, radially-dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
@@
 
-% \begin{table*}
-% \centering
-% \caption{Number of APOGEE stars in each Galactic region.}
-% \label{tab:apogee-regions}
-% \input{output/apogee_regions_table.tex}
-% \end{table*}
-
 We compare our models against stellar abundances from the Apache Point Observatory Galactic Evolution Experiment \citep[APOGEE;][]{majewski_apache_2017} data release 17 \citep[DR17;][]{abdurrouf_seventeenth_2022}.
@@
 When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog and we adopt the Galactic coordinates of the Sun $(R,z)_\odot=(8.122, 0.0208)\kpc$ \citep{gravity_collaboration_detection_2018,bennett_vertical_2019}.
-% Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width \todo{(do I need this table?)}.
 
@@
 The median uncertainty in $\log({\rm age})$ is 0.10 (see Table \ref{tab:uncertainties}), although the oldest stars typically have smaller reported logarithmic uncertainties.
-% We hereafter refer to the \citet{leung_variational_2023} ages as ``NN ages.''
-% \todo{Note that our projected log age error of 0.1 dex is accurate for stars $<8\Gyr$ old, but too large for older stars, so the scatter in the high-$\alpha$ sequence is larger than the data.}
-
-% Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
-% \todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
-% This method has the benefit of providing age estimates for luminous giants, which increases the sample size at larger distances from the Sun.
-However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr.
-We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
-% \todo{Note about metallicity cutoff for luminous giants. Cite: \citet{cao_modeling_2025}}
 
@@
 Limitations from the efficiency of FDU mixing and the RGB age--mass relationship mean the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
-Additional mixing effects in low-metallicity stars %later in their RGB evolution
-also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
+Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
 The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
@@
 
-% We assign a final radius and midplane distance to each stellar population as described in Section \ref{sec:migration}. 
 We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, the infall parameter selection in Section \ref{sec:parameter-selection}, and the stellar migration prescription in Section \ref{sec:migration}.
@@
         t_{\rm max}         & $4.2\Gyr$ & $1-5\Gyr$         & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
-        % \Delta R_{\rm gal}  & ---       & ---               & \ref{sec:migration}   & Change in orbital radius due to stellar migration \\
         \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & ---   & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
@@
         z                   & $[-3,3]\kpc$  & ---           & \ref{sec:migration} & Distance from Galactic midplane at present day \\
-        % p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}    & ---   & \ref{sec:migration} & Probability density function of Galactic midplane distance\\
         h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & ---   & \ref{sec:migration} & Disk scale height \\
@@
 We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
-%Therefore, our multi-zone models with \yZ{1} should predict similar behavior to a model without any mass-loaded outflows.
-%If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.
 
@@
 Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\onecolumn]{src/tex/figures/sfe_prefactor.pdf}
-%     \caption{Effect of the SFE timescale pre-factor $\varepsilon$ on abundance tracks and distributions in a one-zone model (see Section \ref{sec:sf-law}).
-All models are normalized to produce roughly the same ratio of thick to thin disk stars regardless of the value of $\varepsilon$ during the first infall epoch.}
-%     \label{fig:sfe-prefactor}
-% \end{figure}
 
@@
 We assume the Solar-scaled metallicity of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
-% We also investigate cases where the CGM is $\alpha$-enhanced, i.e., $\mathOFe_{\rm CGM}>0$.
 
@@
 \citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to that of \citet{frankel_measuring_2018} and found a similar effect on stellar abundance distributions.
-
-% \citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}.
-They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc).
-This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}.
-They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail.
-Their only point of comparison with data is the local G-dwarf metallicity distribution.
 
@@
 
-% \subsubsection{The Solar Neighborhood}
-
 \begin{figure}
@@
 We next attempt to mitigate the dilution and late-time evolution problems for the \yZ{1} yield scale.
-% The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$, and (d) the metallicity of the infalling gas $\mathXH_{\rm CGM}$.
 First, the observed rise in the median metallicity of stars in the $6-10\Gyr$ age range could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the metal-rich inner Galaxy \citep{feuillet_age-resolved_2018}.
@@
 Finally, in model {\tt yZ2-preenrich} (column (d)) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
-% We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars. 
 This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
@@
 
-% \todo{Summary of problem: the two-infall model is boxed in by data.}
-% Our results show that the APOGEE stellar age catalogs pose several challenges to the two-infall scenario.
-The [O/Fe] distribution was the observable with the easiest discrepancy to resolve using the parameter space we explored, either by pre-enrichment of the accreted gas or a higher thick-to-thin disk mass ratio.
-These parameters also allowed us to mitigate, but not completely resolve, the issues with the age--abundance relations caused by dilution.
-The predicted age distributions could not be reconciled with the data using any of the variations we explored.
-
 In this work, we have highlighted a few predictions of the two-infall scenario and compared against trends from large stellar age catalogs.
@@
 The trough between the high- and low-$\alpha$ sequences results from the star formation returning to pre-quiescence behavior.
-The onset time of the SFE hiatus controls the position of the high-$\alpha$ sequence\textemdash a later onset places the peak at lower [O/Fe]\textemdash while the duration and enhancement factor control the strength of the high-$\alpha$ peak.
+The onset time of the SFE hiatus controls the position of the high-$\alpha$ sequence\textemdash a later onset places the peak at lower [O/Fe]\textemdash while the duration and enhancement factor control the size of the high-$\alpha$ peak.
 
@@
 This hiatus model illustrates an alternative scenario for reproducing the $\alpha$-bimodality, but a full multi-zone treatment is beyond the scope of this work.
-% We intend this model to illustrate another path to reproducing the $\alpha$-bimodality.
-Most of the high-$\alpha$ stars present in the Solar annulus have likely migrated from the inner Galaxy, where perhaps this SFE-driven hiatus was concentrated.
 
@@
 The parameter space is nonetheless restricted by the need to suppress this feature.
-    % \item Adjusting the strength of radial migration naturally affects the scatter in the age--metallicity relation but does not affect the median age.
 \end{itemize}
@@
 
-% Personal acknowledgements
 We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper. We also thank Dr.\ Emanuele Spitoni for useful conversations about this work.

### 2025-07-31 src/scripts/apogee_sample.py
update [C/N] age uncertainties

@@ -33,7 +33,7 @@ SAMPLE_COLS = ['APOGEE_ID', 'RA', 'DEC', 'GALR', 'GALPHI', 'GALZ', 'SNREV',
                'L23_AGE', 'L23_AGE_ERR', 'L23_LOG_AGE', 'L23_LOG_AGE_ERR']
 
 def main():
-    sample_df = APOGEESample.generate(verbose=True)
+    sample = APOGEESample.generate(verbose=True)
 
 class APOGEESample:
     """
@@ -675,12 +675,12 @@ numeric or NoneType.')
             cn_age_region['C_N'].values, 
             cn_age_region['FE_H'].values, 
             CN_AGE_COEF,
-            cn_err = cn_err,
-            feh_err = feh_err
+            # cn_err = cn_err,
+            # feh_err = feh_err
         )
         # Convert years -> Gyr
         cn_age_region['CN_LOG_AGE'] = cn_log_age - 9.
-        cn_age_region['CN_LOG_AGE_ERR'] = 1.4 * cn_log_age_err # inflate by 40% per Jack
+        cn_age_region['CN_LOG_AGE_ERR'] = cn_log_age_err
         cn_age_region['CN_AGE'] = 10 ** cn_age_region['CN_LOG_AGE']
         cn_age_region['CN_AGE_ERR'] = cn_age_region['CN_AGE'] * np.log(10) * cn_age_region['CN_LOG_AGE_ERR']
         apogee_df = apogee_df.join(cn_age_region[
@@ -811,14 +811,16 @@ def recover_age_quad(cn_arr, feh_arr, params, cn_err=[], feh_err=[]):
     ages[badcn] = (c2*maxcn[badcn]**2) + (c1*maxcn[badcn]) + \
         (f2*feh_arr[badcn]**2) + (f1*feh_arr[badcn]) + \
         (c1f1*feh_arr[badcn]*maxcn[badcn]) + b 
-    # Generic age errors of 1 Gyr
-    age_errors = 1e9 / (np.log(10) * 10 ** ages)
+    # Generic age errors of 1.64 Gyr
+    age_errors = 1.64e9 / (np.log(10) * 10 ** ages)
     # Propagate errors
     if len(cn_err) > 0 and len(feh_err) > 0:
         age_errors = np.sqrt(
             cn_err**2 * (2*c2*cn_arr + c1 + c1f1*feh_arr)**2 +
[…]

### 2025-07-31 src/scripts/uncertainties.py

@@ -3,6 +3,7 @@ This script generates a LaTeX table of the median measurement uncertainties
 for the APOGEE DR17 sample.
 """
 
+import numpy as np
 import pandas as pd
 import paths
 from apogee_sample import APOGEESample
@@ -19,6 +20,8 @@ def main():
     medians = sample.data[params].median()
     medians.name = 'Median Uncertainty'
     dispersions = sample.data[params].quantile(0.95) - sample.data[params].quantile(0.05)
+    # Replace small floats with NaN
+    dispersions[dispersions < 1e-10] = np.nan
     dispersions.name = 'Uncertainty Dispersion ($95\\% - 5\\%$)'
     df = pd.concat([medians, dispersions], axis=1)
     df.set_index(labels, drop=True, inplace=True)
@@ -28,6 +31,8 @@ def main():
         index=True, 
         float_format='%.2g'
     )
+    # Replace NaN string with N/A
+    latex_table = latex_table.replace('NaN', 'N/A')
     # Replace \toprule, \midrule, \bottomrule with \hline
     latex_table = latex_table.replace('\\toprule', '\\hline\\hline')
     latex_table = latex_table.replace('\\midrule', '\\hline')

### 2025-07-31 src/tex/ms.tex

@@
 Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
-The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
+% The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
+Following the recommendation of \citet[][submitted]{roberts_cn_2025}, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
 With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.

### 2025-07-31 src/tex/ms.tex
Updates from Overleaf

@@
 
-\shorttitle{Two-Infall in VICE}
+\shorttitle{Two-Infall Challenges}
 \shortauthors{Dubay et al.}
@@
 Following the recommendation of \citet[][submitted]{roberts_cn_2025}, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
-With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
+With this relationship, we estimate ages for \num{113449} stars across the disk, including \num{20992} in the Solar neighborhood.
 
@@
 The figures, tables, and models in this paper are reproducible.
-The git repository associated to this study is publicly available at \url{\GitHubURL}, and the release \todo{v1.X.X} allows anyone to re-build the entire manuscript.
-The multi-zone model outputs are stored at \todo{Zenodo URL}, and the source code for this manuscript is stored at \todo{Zenodo URL}.
+The git repository associated to this study is publicly available at \url{\GitHubURL}, and the release {\tt v1.0.0} allows anyone to re-build the entire manuscript.
+The multi-zone model outputs are stored at \url{https://doi.org/10.5281/zenodo.16649938}, and the source code for this manuscript is stored at \todo{Zenodo URL}.
 

### 2025-07-31 src/tex/ms.tex
Abstract update

@@
 A popular explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
-Thanks to recent advances in stellar age measurements, we can now compare this popular model to more direct measurements of the Galaxy's evolutionary timescales across the disk.
-We run multi-zone galactic chemical evolution models with a two-infall-driven star formation history and compare the results against abundance patterns across the disk from APOGEE DR17, supplemented with stellar ages estimated through multiple methods.
+Thanks to recent advances in stellar age measurements, we can now compare this model to more direct measurements of the Galaxy's evolutionary timescales across the disk.
+We run multi-zone galactic chemical evolution models with a two-infall-driven star formation history and compare the results against abundance patterns from APOGEE DR17, supplemented with stellar ages estimated through multiple methods.
 Although the two-infall scenario offers a natural explanation for the $\alpha$-bimodality, it struggles to explain several features of the age--abundance structure in the disk.
@@
 Some of these issues can be mitigated, but not completely resolved, by pre-enriching the accreted gas to low metallicity.
-These restrictions also place limits on the role of merger events in shaping the chemical evolution of the thin disk in general.
+These restrictions also place limits on the role of merger events in shaping the chemical evolution of the thin disk.
 \end{abstract}
@@
 The git repository associated to this study is publicly available at \url{\GitHubURL}, and the release {\tt v1.0.0} allows anyone to re-build the entire manuscript.
-The multi-zone model outputs are stored at \url{https://doi.org/10.5281/zenodo.16649938}, and the source code for this manuscript is stored at \todo{Zenodo URL}.
+The multi-zone model outputs used to produce the figures in this work are stored at \url{https://doi.org/10.5281/zenodo.16649938}.
 

### 2025-10-10 src/tex/ms.tex
Updates from Overleaf

@@
 
+\submitjournal{The Astrophysical Journal}
+
 \begin{document}
@@
 Although the two-infall scenario offers a natural explanation for the $\alpha$-bimodality, it struggles to explain several features of the age--abundance structure in the disk.
-First, our models generically predict a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant across much of the lifetime of the disk.
+First, our models generically require a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant across much of the lifetime of the disk.
 This apparent age-independence places considerable restrictions upon the two-infall parameter space.
@@
 
-\lettrine{G}{alactic chemical evolution} (GCE) aims to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
+\lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
 A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars \citep[e.g.,][]{tinsley_stellar_1979,matteucci_relative_1986}.
 In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
-The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, has approximately Solar \aFe, and is associated with the kinematic thin disk.
+The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe that are associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, has approximately Solar \aFe, and is associated with the kinematic thin disk.
 The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
-
-An explanation for the MW $\alpha$-bimodality has yet to be broadly accepted in the GCE literature.
-An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and tentatively does not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}).
+An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and may not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}), suggesting that it could point to a unique evolutionary history for the MW.
+
+% An explanation for the MW $\alpha$-bimodality has yet to be broadly accepted in the GCE literature.
+An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and may not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}).
 Its presence and characteristics in our Galaxy could potentially have arisen due to a unique evolutionary history.
 GCE models that attempt to solve this problem generally fall into two camps.
-Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
+Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars or the inside-out growth of the disk \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
 Others argue for a bursty star formation history driven by multiple accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023}.
 
-The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks.
-Though the model has since been refined, the basic premise remains the same: the rate of gas accretion onto the disk is described by two consecutive bursts that each decay with time.
-The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between.
+The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the $\alpha$-bimodality in the MW.
+The basic premise is that the rate of gas accretion onto the disk occurs in two bursts.
+The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars.
 The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
-The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.
-
-Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}.
+The initial model of \citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time.
+
+Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
 Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
-\citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
+\citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.
+\citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the star formation history inferred from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
 Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey \citep[SDSS;][]{sdss_collaboration_nineteenth_2025}.
 
-While previous studies have explored a large parameter space, most have assumed that the Galactic disk never ejected a substantial outflow.
-This decision is based on hydrodynamic simulations of Galactic fountains ejected by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
+While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
+This decision is based on hydrodynamic simulations of Galactic fountains produced by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to its point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
 However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}; other simulations of MW-like galaxies with different prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
-Empirically, mass-loading has been observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
-Even if the MW is not currently ejecting a substantial outflow, it may have at some point in the past.
+Empirically, mass-loading is observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
+Even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.
 
@@
 \citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
-This degeneracy prohibits direct estimates of the yield scale from GCE models, unless the effect of outflows is assumed to be insignificant.
-The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of the yield scale on two-infall scenario predictions.
-Varying the yield scale while maintaining an evolutionary end point that is consistent with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
-
-The observed chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary motivation for the two-infall scenario.
+This degeneracy prohibits direct estimates of the yields from GCE models unless the effect of outflows is assumed to be insignificant.
+The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of varying the yield scale on two-infall scenario predictions.
+Varying the yield scale while maintaining an evolutionary end point consistent with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
+
+% The observed chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary motivation for the two-infall scenario.
 \citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a period of reduced star formation, which is a natural consequence of the delay between the two accretion epochs.
@@
 
-Previous two-infall models have reproduced the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
+The two-infall scenario reproduces the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
 However, the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
-\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}.
-Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor depends on a model of the evolution of the radial metallicity profile in the MW.
-While the strength and speed of radial migration in the disk are not precisely measured, a single chemical evolution track need not explain the entire width of the local abundance distribution.
-We illustrate this distinction in Figure \ref{fig:smooth-vs-twoinfall}, which contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
-If the effect of radial migration is significant, then the full local stellar abundance distribution can be explained without dramatic changes to the local gas abundance over time.
-
-In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
-\citet{schonrich_chemical_2009} first showed that radial migration can produce an $\alpha$-bimodality through a superposition of chemical tracks, although they did not directly compare against MW data.
+\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}.
+% Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor depends on a model of the evolution of the radial metallicity profile in the MW.
+% While the strength and speed of radial migration in the disk are not precisely measured, a single chemical evolution track need not explain the entire width of the local abundance distribution. 
+A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
+In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).
+Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
+If the effect of radial migration is significant, then the local $\alpha$-bimodality could be explained without dramatic changes to the local gas abundance over time.
+
+% In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
+% \citet{schonrich_chemical_2009} first showed that radial migration can produce an $\alpha$-bimodality through a superposition of chemical tracks, although they did not directly compare against MW data.
 Others have produced a more MW-like $\alpha$-bimdodality using a combination of radial migration and inside-out galaxy growth \citep[e.g.,][]{kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
@@
 
-As stellar age estimation techniques have improved over recent years, large catalogs have become available with measurements for stars across a wide swath of the Galaxy.
-In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs have indicated that stellar metallicities are remarkably consistent with age across most of the thin disk epoch \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
+As stellar age estimation techniques have improved over recent years, large catalogs have become available with age estimates for stars across a wide swath of the Galaxy.
+In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs suggest that stellar metallicities are remarkably consistent with age across most of the thin disk \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
 \citet{johnson_milky_2024} demonstrated that these results are readily explained by a scenario in which the Galaxy reaches a state of chemical equilibrium.
 In this so-called ``equilibrium scenario,'' the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over Gyr timescales.
-Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the thin disk epoch.
-
-Relative to even a few years ago, the availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
+Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the past $\sim8\Gyr$.
+
+The availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
 Our study draws on the steadiness of the Milky Way stellar metallicity gradient found by \citet{johnson_milky_2024} and empirical constraints on the yield scale from \citet{weinberg_scale_2024}.
@@
 We investigate the impact of the scale of SN yields and outflows, the strength of radial migration, the composition of the circumgalactic medium, and the local disk mass surface density ratio on GCE model predictions.
-We compare our results to abundance distributions across the disk from APOGEE DR17, and to age--abundance relations from multiple age catalogs.
+We compare our results to abundance distributions across the disk from APOGEE DR17, and to age--abundance relations from multiple catalogs.
 We describe our observational sample in Section \ref{sec:observational-sample}, and we detail our chemical evolution models and parameter selection in Section \ref{sec:methods}.
@@
 APOGEE data were obtained from infrared spectrographs \citep{wilson_apache_2019} mounted on the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory.
-The data reduction pipeline is described by \citet{nidever_data_2015}, and APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
+The data reduction pipeline is described by \citet{nidever_data_2015}, and the APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
 
@@
 We supplement the APOGEE DR17 abundance data with two different age catalogs.
-The first is from \citet{leung_variational_2023}, who train a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
-This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and they recover accurate ages up to $\sim13\Gyr$, while other neural network-derived age catalogues exhibit an age plateau \citep[e.g.,][]{mackereth_dynamical_2019}.
-Following the recommendations of \citet{leung_variational_2023}, we cut all stars which have a relative age uncertainty greater than 40\%.
+The first is from \citet{leung_variational_2023}, who trained a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
+% This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and they recover accurate ages up to $\sim13\Gyr$, while other neural network-derived age catalogs exhibit an age plateau \citep[e.g.,][]{mackereth_dynamical_2019}.
+Following the recommendations of \citet{leung_variational_2023}, we cut all stars which have an age uncertainty greater than 40\%.
 This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
-The median uncertainty in $\log({\rm age})$ is 0.10 (see Table \ref{tab:uncertainties}), although the oldest stars typically have smaller reported logarithmic uncertainties.
+The median uncertainty in $\log({\rm age})$ is 0.10 (see Table \ref{tab:uncertainties}), although the oldest stars typically have smaller uncertainties.
 
@@
 This method has the benefit of providing age estimates for luminous giants ($\log g<2.5$), which increases the sample size at larger distances from the Sun.
-Limitations from the efficiency of FDU mixing and the RGB age--mass relationship mean the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
+Uncertainties in the efficiency of FDU mixing and the RGB age--mass relationship mean that the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
 Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
@@
 The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}.
-We set up a disk with radial extent $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
-We use a time-step size of $\Delta t=10\,{\rm Myr}$ and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
+We set up a disk spanning $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
+We use a time-step of $\Delta t=10\,{\rm Myr}$, $n=8$ stellar populations per time-step per ring, and we run our models to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
 Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling.
@@
 We inhibit star formation past $R_{\rm gal}>15.5\kpc$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.
-This configuration results in $N=1,638,040$ stellar populations contributing to metal enrichment in each model.
 
@@
 The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models. 
-This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}.
-Recently, \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
+% This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. Recently, 
+\citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
     In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$.
 We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
-}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a mass of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass in the Sun.
-However, \citet{johnson_milky_2024} found that their GCE models with yields at this scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun.
+However, \citet{johnson_milky_2024} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed age--metallicity relation.
 Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
@@
 \end{equation}
-from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
+for each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
 The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
@@
         \frac{N_{\rm Ia}}{M_\star}
-        \frac{f_{\rm Ia}(t)}{\int_{t_{\rm Ia}}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_{\rm Ia} \\
+        \frac{f_{\rm Ia}(t)}{\int_{t_{\rm Ia}}^{t_{\rm final}} f_{\rm Ia}(t') dt'}, & t \ge t_{\rm Ia} \\
         0 & t < t_{\rm Ia},
@@
 Motivated by Equation \ref{eq:equilibrium}, we adopt a different outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
-Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on stellar age trends.
+Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we adjust $\eta_\odot$ to ensure that $Z_{\rm O,eq}\approx Z_{\rm O,\odot}$.
+% Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on stellar age trends.
 Table \ref{tab:models} reports the value of $\eta_\odot$ in each of our models.
 
-Not all GCE studies have constrained their models to reach an equilibrium at the Solar metallicity.
+% Not all GCE studies have constrained their models to reach an equilibrium at the Solar metallicity.
 For example, the models of \citet{palla_chemical_2020} and \citet{spitoni_remind_2024} predict somewhat super-Solar metallicity in the present-day Solar neighborhood.
@@
 
-Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
+% Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
 \citet{johnson_milky_2024} used this approach to present a proof of concept for the equilibrium scenario.
-In order to produce an exponentially declining radial metallicity gradient, we adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
+\citet{johnson_milky_2024} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
+To produce an exponentially declining radial [O/H] gradient, we adopt a prescription of
 \begin{equation}
@@
 \end{equation}
+for the outflow mass-loading factor,
 where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, in line with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
-
-Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, consistent with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
+We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study.
+We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
+
+% Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
 Even in studies that do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023} or does not vary with radius \citep{hegedus_reconstructing_2025}.
@@
 
-As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
+% As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
 Here, we aim to study the effect of the assumed yield scale on two-infall model predictions, so we use mass-loaded outflows to control the final state of chemical evolution across the disk.
@@
 
-The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^k$, with $k=1.5$ following \citet{kennicutt_global_1998}.
-Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law prescription in this work to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
-
+We use a power-law star formation prescription of $\dot\Sigma_\star\propto\Sigma_g^k$, with $k=1.5$ following \citet{kennicutt_global_1998}.
+Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
 In detail, we calculate the star formation efficiency (SFE) timescale
@@
 \end{equation}
-where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, with $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ \citep{leroy_star_2008}.
+with $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, where $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ are observationally calibrated \citep{leroy_star_2008}.
 Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through a pre-factor
@@
 However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
-We adopt $\varepsilon(t<t_{\rm max})=0.5$ for consistency with the two-infall literature, though we find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
-To guard against over-correcting the SFE in the early Galaxy, we have tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial difference to our results.
+We find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
+To guard against over-correcting the SFE in the early Galaxy, we tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial differences.
 
@@
 
-Characteristic of the two-infall scenario, the infall rate is described by two successive, exponentially declining bursts in time.
-The first infall component induces the formation of the thick disk, and the second component produces the thin disk.
-At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
-\begin{equation}
+The infall rate is described by two successive, exponentially declining bursts in time.
+The first infall component forms the thick disk, and the second produces the thin disk.
+The un-normalized form of the infall rate is
+\begin{multline}
     \label{eq:twoinfall-ifr}
-    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + H(t-t_{\rm max}) f_{2/1} (R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
-\end{equation}
+    f_{\rm in}(t|R_{\rm gal}) \propto e^{-t/\tau_1} + \\ H(t-t_{\rm max}) f_{2/1} (R_{\rm gal}) \exp\Big(\frac{-(t-t_{\rm max})}{\tau_2(R_{\rm gal})}\Big),
+\end{multline}
 \begin{equation*}
@@
 \end{equation*}
-where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall,  $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
-We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
+where $\tau_1$ and $\tau_2(R_{\rm gal})$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall, $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
+We vary $\tau_2$ exponentially with $R_{\rm gal}$ and adopt a scale radius $R_{\tau_2}=7\kpc$ to match the stellar age gradients in MW-like spirals observed by \citet{sanchez_spatially_2020}.
+We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar disk has a surface density ratio of the thick and thin disks of
 \begin{equation}
@@
 We adopt a thick disk scale radius of $R_1=2.0\kpc$, a thin disk scale radius of $R_2=2.5\kpc$, and a fiducial value for the local surface density ratio of $f_\Sigma(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016}.
+
+% Infall rate parameter selection
+Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
+After exploring the effect of the infall timescales in one-zone models, we adopt $\tau_1=1\Gyr$ and $\tau_2(R_\odot)=15\Gyr$, in line with the parameters adopted by \citet{spitoni_galactic_2020}, but longer than in \citet{nissen_high-precision_2020}, \citet{spitoni_apogee_2021}, and \citet{hegedus_reconstructing_2025}.
+We also adopt $t_{\rm max}=4.2\Gyr$ (i.e., a lookback time of $9\Gyr$) so that our models are compatible with the median stellar age of the thick disk of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
+\citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.
 
@@
 In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
-The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a maximum of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
+The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a present-day value of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
 
@@
 In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
+However, previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
+The circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
 The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
@@
 In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathFeH_{\rm CGM}$.
-Previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
-We assume the Solar-scaled metallicity of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
-
-\subsection{Infall Rate Parameter Selection}
-\label{sec:parameter-selection}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figures/infall_parameters.pdf}
-    \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models which assume different values for the infall history parameters.
+We assume the Solar-scaled abundance of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
+
+% \subsection{Infall Rate Parameter Selection}
+% \label{sec:parameter-selection}
+
+% \begin{figure*}
+%     \centering
+%     \includegraphics[width=\textwidth]{figures/infall_parameters.pdf}
+%     \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models with different infall history parameters.
 In each panel, one parameter is varied according to the legend while the other two are held fixed.
 The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b).
-The marginal panels show the corresponding stellar abundance distributions, which are convolved with a Gaussian kernel with a width of 0.02 dex for visual clarity.
+The marginal panels show the corresponding stellar abundance distributions, which are convolved with an 0.02 dex Gaussian kernel for visual clarity.
 All models use the same fiducial parameters as the $R_{\rm gal}=8\kpc$ ring in the multi-zone models, with \yZ{1} and $\eta=0.2$.
-The black lines represent the same set of parameters in each panel.}
-    \label{fig:twoinfall-parameters}
-\end{figure*}
-
-Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
+The black lines in each panel represent the fiducial parameters.}
+%     \label{fig:twoinfall-parameters}
+% \end{figure*}
+
+% Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
 Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}.
@@
 
-Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
+% Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
 A shorter $\tau_2$ produces a bigger loop and therefore a broader MDF and [O/Fe] distribution, while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
@@
 
-In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
+% In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
 Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scaled $\tau_2$ linearly with radius, with $\tau_2\approx1\Gyr$ in the inner disk and $\tau_2=7\Gyr$ at the Solar annulus.
@@
 
-Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
+% Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
 For $t_{\rm max}>2\Gyr$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
@@
 
-The Milky Way's last major merger with the dwarf galaxy, dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018}, has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
+% The Milky Way's last major merger with the dwarf galaxy, dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018}, has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
 Our fiducial value of $t_{\rm max}=4.2\Gyr$ places the start of the formation of the thin disk close to the GSE merger (within uncertainties), which likely occurred $\sim10\Gyr$ ago \citep[e.g.,][]{helmi_merger_2018,gallart_uncovering_2019,naidu_reconstructing_2021,woody_rapid_2025}.
@@
 
-We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
+% We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
 The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the one-zone model outputs include only stars formed in-situ at the Solar annulus.
@@
 \citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
-Assuming a constant migration speed, they prescribed some fraction of stars born in the inner and outer Galaxy that will contribute to the local present-day population, and they also assumed that some fraction of stars born in the Solar neighborhood will have migrated elsewhere by the present day.
+% Assuming a constant migration speed, they prescribed some fraction of stars born in the inner and outer Galaxy that will contribute to the local present-day population, and they also assumed that some fraction of stars born in the Solar neighborhood will have migrated elsewhere by the present day.
 \citet{spitoni_effect_2015} improved agreement with the observed local metallicity distribution, but their method is difficult to apply to model predictions across the disk.
@@
 \begin{equation}
-    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big)\quad 
-    {\rm \citep{spitzer_dynamics_1942}},
+    p(z|\tau,R_{\rm final}) = \frac{1}{4 h_z} {\rm sech}^2\Big(\frac{z}{2 h_z}\Big),
     \label{eq:sech-pdf}
 \end{equation}
-where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The scale height $h_z$ is given by
+\citep{spitzer_dynamics_1942} where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The scale height $h_z$ is given by
 \begin{equation}
@@
 \end{equation}
-We note that the final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
+The final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
 The parameters of Equations \ref{eq:radial-migration} and \ref{eq:scale-height} were chosen to fit the stellar migration patterns in the {\tt h277} hydrodynamical simulation \citep{christensen_implementing_2012}.
@@
 
-We note an important distinction between our method and that of \citet{spitoni_effect_2015}: SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
+An important distinction between our method and that of \citet{spitoni_effect_2015} is that SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
 This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
@@
 
-\begin{deluxetable*}{lCCcCCC}
+\begin{deluxetable*}{lCCcDDD}
     \tablecaption{Summary of our multi-zone models and relevant parameters.\label{tab:models}}
     \tablehead{
-        \colhead{Name} & \colhead{$y/Z_\odot$} & \colhead{$\eta_\odot$} & \colhead{SN Ia DTD} & \colhead{$\sigma_{\rm RM8}$} & \colhead{$f_\Sigma(R_\odot)$} & \colhead{${\rm [X/H]}_{\rm CGM}$}
+        \colhead{Name} & \colhead{$y/Z_\odot$} & \colhead{$\eta_\odot$} & \colhead{SN Ia DTD} & \multicolumn2c{$\sigma_{\rm RM8}$ [kpc]} & \multicolumn2c{$f_\Sigma(R_\odot)$} & \multicolumn2c{${\rm [X/H]}_{\rm CGM}$}
     }
+    \decimals
     \startdata
-        {\tt yZ1-fiducial}  & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -\infty   \\
-        {\tt yZ1-migration} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 5.0\kpc   & 0.12  & -\infty   \\
-        {\tt yZ1-diskratio} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.5   & -\infty   \\
-        {\tt yZ1-preenrich} & 1 & 0.6   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -0.5      \\
-        {\tt yZ1-best}      & 1 & 0.4   & Equation \ref{eq:plateau-dtd}  & 3.6\kpc   & 0.25  & -0.7      \\
+        {\tt yZ1-fiducial}  & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ1-migration} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 5.0   & 0.12  & $-\infty$   \\
+        {\tt yZ1-diskratio} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
+        {\tt yZ1-preenrich} & 1 & 0.6   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
+        {\tt yZ1-best}      & 1 & 0.4   & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
         \hline
-        {\tt yZ2-fiducial}  & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -\infty   \\
-        {\tt yZ2-powerlaw}  & 2 & 1.4   & Equation \ref{eq:powerlaw-dtd} & 2.68\kpc  & 0.12  & -\infty   \\
-        {\tt yZ2-diskratio} & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.5   & -\infty   \\
-        {\tt yZ2-preenrich} & 2 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -0.5      \\
-        {\tt yZ2-best}      & 2 & 1.8   & Equation \ref{eq:plateau-dtd}  & 3.6\kpc   & 0.25  & -0.7      \\
+        {\tt yZ2-fiducial}  & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-powerlaw}  & 2 & 1.4   & Equation \ref{eq:powerlaw-dtd} & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-diskratio} & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
+        {\tt yZ2-preenrich} & 2 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
+        {\tt yZ2-best}      & 2 & 1.8   & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
         \hline
-        {\tt yZ3-fiducial}  & 3 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68\kpc  & 0.12  & -\infty   \\
+        {\tt yZ3-fiducial}  & 3 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
     \enddata
@@
     \includegraphics[width=\onecolumn]{figures/gas_abundance_evolution.pdf}
-    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}).
-The gray points plot the abundances of APOGEE stars in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
+    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), each of which feature a major dilution event 9 Gyr ago.
+The gray points plot the abundances of APOGEE stars in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
 The black points indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
 The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.
-    {\bf Key takeaway:} All models feature a major dilution event 9 Gyr ago, and the \yZ{1} model re-enriches the most slowly.}
+    % {\bf Key takeaway:} All models feature a major dilution event 9 Gyr ago, and the \yZ{1} model re-enriches the most slowly.
+    }
     \label{fig:yield-outflow}
@@
 
-The two-infall scenario requires a large quantity of pristine or low-metallicity gas to be accreted onto the disk over a short span of time.
+% The two-infall scenario requires a large quantity of pristine or low-metallicity gas to be accreted onto the disk over a short span of time.
 As a natural consequence, the gas disk experiences a period of metal dilution, which should be recorded in the stellar record.
-Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions of mono-age populations in the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
+Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions as a function of age at the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
 As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
-In agreement with recent work (see discussion in Section \ref{sec:introduction}), the trend with age is interestingly flat.
+% In agreement with recent work (see discussion in Section \ref{sec:introduction}), the trend with age is interestingly flat.
 [O/H] and [Fe/H] increase by $0.1-0.2\dex$, relative to young stars, in the $\sim6-8\Gyr$ age range, likely due to metal-rich stars migrating outward from the inner Galaxy where the surface densities are higher.
-
-We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ on Figure \ref{fig:yield-outflow} for comparison.
+We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ for comparison.
 The models are in broad agreement with each other and with the data at lookback times of $\lesssim5\Gyr$.
-At ages of $\sim5-8\Gyr$, the models appear to be in tension with the data, underpredicting the metallicities of the observed stars by up to half an order of magnitude.
-The low metallicities in the models are a natural consequence of the dilution associated with the second infall event.
-This discrepancy is potentially mitigated by the higher $y/Z_\odot$ models, which re-enrich more rapidly; signatures of substantial dilution in this scenario may be washed out by age uncertainties.
-However, these models exacerbate tensions with the age--[O/Fe] relation because the O abundance can grow by a larger factor before enrichment from second-infall SNe Ia becomes important, making the $\alpha$-enhancement from the ensuing starburst more pronounced.
-When each panel is considered, none of our models provide a good match to these age trends.
+At ages of $\sim5-8\Gyr$, the models underpredict the metallicities of the observed stars by up to half an order of magnitude, a natural consequence of the dilution associated with the second infall event.
+This discrepancy is modestly reduced in the higher $y/Z_\odot$ models, which re-enrich more rapidly.
+However, these models exacerbate tensions with the age--[O/Fe] relation because the O abundance increases more before enrichment from second-infall SNe Ia becomes important, making the $\alpha$-enhancement from the ensuing starburst more pronounced.
+Overall, none of our models provide a good match to these age trends.
 Figure \ref{fig:yield-outflow} illustrates a point that will arise as a theme throughout the remainder of this paper, which is that the signatures of a substantial dilution event and subsequent re-enrichment, characteristic of the two-infall scenario, are simply not present in the observed age--abundance trends.
@@
     \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}).
-Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius.
-A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}< 9\kpc$, $|z| < 0.5\kpc$) color-coded by its birth radius.
+In this and subsequent figures, a Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
 For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
-The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$ over time, and the black squares plot the median stellar abundance in in {2 Gyr}-wide age bins.
-The red line and points plot the median abundance for APOGEE stars in each age bin, and the shaded regions represent the 16th--84th percentiles of stellar abundances.
-We adopt the NN age estimates for APOGEE stars from \citet{leung_variational_2023}.
+The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$, and the black squares plot the median stellar abundance in {2 Gyr}-wide age bins.
+The red line and points are the median abundance for APOGEE stars, and the shaded regions are the 16th--84th percentile ranges.
+    % We adopt the NN age estimates for APOGEE stars from \citet{leung_variational_2023}.
     Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).
-{\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither can simultaneously match all of the observed age--abundance relation.}
+    % {\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither can simultaneously match all of the observed age--abundance relation.
+    }
     \label{fig:abundance-evolution-params}
@@
 
-Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation, even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
-The problem is exacerbated in the two-infall case because of the delayed dilution event --- in effect, approach to equilibrium is ``reset'' by the second infall.
+Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
+The problem is exacerbated in the two-infall case because of the delayed dilution event---the approach to equilibrium is ``reset'' by the second infall.
 The dilution of the ISM then gets baked into the stellar abundance record.
@@
 The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed by SNe Ia.
-Note that we scatter simulated data points according to the median age and abundance errors in Table \ref{tab:uncertainties}, so the blurring impact of these statistical errors is incorporated in the model.
+We smoothed simulated data points based on the median age and abundance errors in Table \ref{tab:uncertainties} to incorporate these errors in the model.
 The black dashed curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
@@
 As a result, the stars that make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution at fixed age.
-Even though this prescription is extreme compared to the estimates of, e.g., \citet{frankel_measuring_2018}, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
+Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, for example, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
 
@@
 Column (c) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM because more of the gas disk is built up during the first infall phase.
-Model {\tt yZ1-diskratio} produces the best agreement out of the four with the observed age--[Fe/H] relation (second row).
+Model {\tt yZ1-diskratio} produces the best agreement of the four models in Figure \ref{fig:abundance-evolution-params} to the observed age--[Fe/H] relation (second row).
 However, agreement with the observed age--[O/Fe] relation is poor.
@@
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
-Pre-enriched infall also raises the equilibrium metallicity, so we increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity.
+% Pre-enriched infall also raises the equilibrium metallicity, so we
+.increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity. 
 Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
@@
     \includegraphics[width=\textwidth]{figures/mdf_evolution.pdf}
-    \caption{Evolution of the MDF over time across the Galactic disk.
-In each panel, normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus are color-coded by the stellar age range.
-The gray curve represents the total MDF in each region.
-Rows (a) and (b) present the distributions from multi-zone GCE models with the fiducial parameters (see Table \ref{tab:models}) at different yield and outflow scales.
-A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}.
+    \caption{Decomposition of the present-day MDF by stellar age across the Galactic disk. 
+    % In each panel, normalized MDFs within a {2 kpc}-wide annulus are color-coded by the stellar age range. 
+    The gray curve plots the total present-day MDF in each region.
+The distributions in all panels are restricted to $|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
+Rows (a) and (b) present the distributions from the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models, respectively (see Table \ref{tab:models}).
+    % A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}. 
     Row (c) presents the distributions from APOGEE with ages derived from [C/N] abundances by \citet{roberts_cn_2025} (see Section \ref{sec:age-estimates}).
-The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\kpc$ age bin for reference.
+The vertical blue dotted lines in row (c) mark the mode of the distribution of the $1-2\kpc$ age bin for reference.
 Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
-The distributions in all panels are restricted to $0\leq|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
-{\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both two-infall models predict a steady evolution toward higher [Fe/H] with time.}
+    % {\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both two-infall models predict a steady evolution toward higher [Fe/H] with time.
+    }
     \label{fig:mdf-evolution}
@@
 The discrepancies between the predicted and observed abundance evolution in the Solar neighborhood discussed in Section \ref{sec:age-abundance} persist across the Galactic disk.
-Figure \ref{fig:mdf-evolution} shows the evolution of the MDF with age across five radial bins for the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models.
-For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in Section \ref{sec:observational-sample}.
+Figure \ref{fig:mdf-evolution} breaks down the MDF by stellar age across five radial bins for the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models.
+For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in Section \ref{sec:age-estimates}.
 
@@
 The distance between the $1-2\Gyr$ and $2-4\Gyr$ age bins is smaller for the \yZ{2} model because of the faster approach to equilibrium (see also Figure \ref{fig:yield-outflow}).
-In the Solar annulus (center column), the peak of the $6-8\Gyr$ old MDF is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
+In the Solar annulus (center column), the peak of the MDF of $6-8\Gyr$ old stars is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
 
@@
 The curves in panels (a) and (b) plot the ISM abundance at the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
-The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the predicted abundances according to Table \ref{tab:uncertainties}.
-Stars in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $0\leq|z|<2\kpc$.
-{\bf Key takeaway:} both models predict a stellar over-density at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.}
+The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution.
+    % and a Gaussian scatter has been applied to the predicted abundances according to Table \ref{tab:uncertainties}. 
+    Stars in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$. 
+    % {\bf Key takeaway:} both models predict a stellar over-density at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.
+    }
     \label{fig:ofe-feh-density}
@@
 We have not accounted for the APOGEE selection function in our models, but there is no evident reason for observational effects to produce this difference in morphology.
-This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and has stymied other models as well \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
+This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and is typical of other models \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
 The two-infall scenario is otherwise fairly successful at reproducing the local stellar distribution in [O/Fe]--[Fe/H] space.
@@
 Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
-The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}).
+    % The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). 
     For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
     Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, {\tt yZ2-fiducial}; {\bf (b)} a model with a power-law DTD, {\tt yZ2-powerlaw}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\tt yZ2-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ2-preenrich} (see Table \ref{tab:models} for details).
-{\bf Key takeaway:} For the \yZ{2} case, a higher thick-to-thin disk ratio or pre-enrichment of the accreted gas can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
+    % {\bf Key takeaway:} For the \yZ{2} case, a higher thick-to-thin disk ratio or pre-enrichment of the accreted gas can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.
+    }
     \label{fig:ofe-distribution-parameters}
@@
     \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$.
-Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age.
-A Gaussian scatter is applied to each point according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}.
-The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region.
-{\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.}
+Each panel presents a random mass-weighted sample of \num{10000} stellar populations color-coded by age.
+    % A Gaussian scatter is applied to each point according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}. 
+    The solid (dashed) contours enclose 30\% (80\%) of the APOGEE stars in each region. 
+    % {\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.
+    }
     \label{fig:ofe-feh-best}
@@
 Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
-Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate, and we believe more realistic, than in previous sections to avoid extreme effects resulting from the combination of all of these parameters.
-We stress that our focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters through methods such as MCMC.
+Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate than the illustrative examples in the previous section.
+Our focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters.
 
@@
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
-The left and center panels plot the output of the {\tt yZ1-best} and {\tt yZ2-best} models, with ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$ (see Table \ref{tab:models}).
+The left and center panels show the {\tt yZ1-best} and {\tt yZ2-best} models, with ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$ (see Table \ref{tab:models}).
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the abundances and ages according to Table \ref{tab:uncertainties}.
 The right panel plots the results from APOGEE using the \citet{leung_variational_2023} NN age catalog.
-The contours indicate the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
+The contours show the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
     {\it Bottom}: Stellar age distributions in the Solar annulus for all stars (black) and LMR stars (gray).
-The left and center panels plot the mass-weighted age distributions predicted by the models after forward-modeling age uncertainties, and the right panel plots the NN ages for APOGEE stars.
-    {\bf Key takeaway:} Both two-infall models predict a fundamentally different age pattern than what is observed, especially for LMR stars.}
+The left and center panels plot the mass-weighted age distributions predicted by the models,
+    % after forward-modeling age uncertainties, 
+    and the right panel plots the NN ages for APOGEE stars.
+    % {\bf Key takeaway:} Both two-infall models predict a fundamentally different age pattern than what is observed, especially for LMR stars.
+    }
     \label{fig:lmr-ages}
@@
 The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
-It is difficult to predict a unimodal age distribution with the available parameter space.
+It is difficult to obtain a unimodal age distribution with the available parameter space.
 A dearth of intermediate-age, high-metallicity stars is a natural outcome of a substantial dilution event, which is a defining feature of the two-infall scenario.
@@
 Similarly, \citet{palla_chemical_2020,palla_mapping_2024} used an inward flow with a speed of $\sim1\kms$ to reproduce the observed radial metallicity profile in the absence of Galactic outflows.
-Johnson et al.
-(2025, in preparation) considered several possible scenarios for the processes that drive radial gas flows.
-Their findings support these previous arguments that radial gas flows should regulate the overall metal abundance and radial gradient, even beyond the two-infall scenario.
+\citet{johnson_constraints_2025} considered several possible scenarios for the processes that drive radial gas flows.
+Their findings support these previous arguments that radial gas flows can help to regulate the overall metal abundance and radial gradient.
 
 In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2024} demonstrated can improve agreement with age trends across the Galactic disk.
-Johnson et al.
+% Johnson et al.
 (2025, in preparation) found similar results for radial gas flows with velocities that are relatively constant in both Galactocentric radius and time.
 At least one radial gas flow scenario therefore has similar effects on metal enrichment as our outflow prescription.
-However, the outflow is simpler in implementation; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
+However,
+The outflow is simpler in implementation than a radial gas flow; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
 This approach allows us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
-A radial gas flow requires at least one assumption about the processes that drive the flow and generally does not afford the same level of flexibility.
-We have therefore focused on models with outflows in this paper for the sake of simplicity, and we clarify that some, but not all, radial gas flow models should have similar effects.
+% A radial gas flow requires at least one assumption about the processes that drive the flow and generally does not afford the same level of flexibility. 
+We have therefore focused on models with outflows in this paper for the sake of simplicity, but constant radial gas flow models should have similar effects.
 
@@
 The blue dashed curve represents the fiducial model that has an exponentially declining infall rate with timescale $\tau_{\rm in}=15\Gyr$, and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
-The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4\,{\rm Gyr}$.
+The red solid curve plots the output of a model which has an enhancement of $\tau_\star$ by a factor of 10 for 200 Myr starting at $t=1.4\,{\rm Gyr}$.
 Both models assume the \yZ{2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
-The grayscale histogram presents the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq|z|\leq2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
+The grayscale histogram is the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}< 9\kpc$, $|z|<2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}
@@
 
-The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation for some duration.
-For the two-infall model, this phase of low star formation lasts for a few Gyr in between the $e$-folding timescale of the first infall and the onset of the second.
+The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation temporarily.
+For the two-infall model, this phase of low star formation lasts for a few Gyr between the $e$-folding timescale of the first infall and the onset of the second.
 However, as we have shown in Section \ref{sec:age-abundance}, the resulting dilution of the ISM is in tension with the observed stellar age--metallicity relation.
@@
 The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
-As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk as measured by \citet{pinsonneault_apokasc-3_2025}.
+As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk measured by \citet{pinsonneault_apokasc-3_2025}.
 This hiatus model illustrates an alternative scenario for reproducing the $\alpha$-bimodality, but a full multi-zone treatment is beyond the scope of this work.
@@
 We explored multiple parameter modifications to bring the model predictions closer to the data, including the yield scale, radial migration strength, metallicity of the accreted gas, thick-to-thin disk mass ratio, and the SN Ia DTD.
-We found that our two-infall models faced the following challenges when compared against the stellar age catalogs:
+We found that our two-infall models faced the following challenges:
 
 \begin{itemize}
-    \item By the model's design, the Galaxy undergoes a period of major, rapid dilution and subsequent re-enrichment.
+    \item By the model's design, the Galaxy undergoes a period of rapid dilution and subsequent re-enrichment.
 Models at a lower yield scale and weaker outflows predict slower re-enrichment.
 By contrast, the observed stellar age--metallicity relation is roughly constant over the past $\sim10\Gyr$.
-Pre-enriching the accreted gas can reduce the magnitude of the dilution, but not eliminate it entirely.
+Pre-enriching the accreted gas can reduce the magnitude of the dilution, but cannot eliminate it entirely.
     \item Due to this re-enrichment, our models predict that the MDF shifts to higher metallicity with decreasing age throughout the disk.
@@
 
-We note that we have not found a GCE model, two-infall or otherwise, that is capable of reproducing all of the above observations.
+We have not found a GCE model, two-infall or otherwise, that is capable of reproducing all of the observations.
 The ``inside-out'' models of \citet{johnson_stellar_2021} are better able to predict a slowly evolving metallicity gradient, but they do not predict an $\alpha$-bimodality.
 Even a smoothly-evolving SFH struggles to reproduce the flat age--metallicity relation at the lower empirical yield scale \citep{johnson_milky_2024}.
-We emphasize, though, that by its very construction the two-infall scenario trades success at reproducing certain observations for failure at others.
+We emphasize, though, that by its very construction, the two-infall scenario trades success at reproducing certain observations for failure at others.
 
@@
 
-We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper. We also thank Dr.\ Emanuele Spitoni for useful conversations about this work.
+We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper, and to Prof.\ Christopher Kochanek for his useful comments on the manuscript.
+We also thank Dr.\ Emanuele Spitoni for useful conversations about this work.
 

### 2025-10-13 src/tex/ms.tex
Updates from Overleaf

@@
         EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
-        NN age error        & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
         $R_{\rm gal}$     & $3 < R_{\rm gal} < 15\kpc$    & Eliminate bulge \& extreme outer-disk stars \\
         $|z|$               & $|z| < 2\kpc$                 & Eliminate halo stars \\
+        \hline
+        NN age error        & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
+        Uncertainty on [C/N]    & $\sigma_{\rm [C/N]}\leq0.1$     & Precise [C/N] ages from \citet{roberts_cn_2025} \\
+        ${\rm [Fe/H]}$      & $\mathFeH\geq-0.4$            & Accurate [C/N] ages for upper RGB \& red clump stars \\
         \hline
@@
 
-Our second age catalog utilizes the [C/N]--age relation calibrated by \citet[][submitted]{roberts_cn_2025} for red giant branch (RGB) and red clump stars.
+Our second age catalog utilizes the [C/N]--age relation calibrated by \citet{roberts_cn_2025} for red giant branch (RGB) and red clump (RC) stars.
 The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
@@
 Uncertainties in the efficiency of FDU mixing and the RGB age--mass relationship mean that the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
-Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
+Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous RGB and RC stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
 % The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
-Following the recommendation of \citet[][submitted]{roberts_cn_2025}, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
-With this relationship, we estimate ages for \num{113449} stars across the disk, including \num{20992} in the Solar neighborhood.
+We use the sample selection criteria from \citet{roberts_cn_2025}, and following their recommendation, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
+With this relationship, we estimate ages for \num{124778} stars across the disk, including \num{21956} in the Solar neighborhood.
 
@@
     \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), each of which feature a major dilution event 9 Gyr ago.
-The gray points plot the abundances of APOGEE stars in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
-The black points indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
+The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
+The black line (black points) plots the median (mode) of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
 The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.

### 2025-10-21 src/tex/ms.tex
Manuscript revisions

@@
 This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to a unique evolutionary history.
-A popular explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
+A popular and well-studied explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
 Thanks to recent advances in stellar age measurements, we can now compare this model to more direct measurements of the Galaxy's evolutionary timescales across the disk.
@@
         Uncertainty on [C/N]    & $\sigma_{\rm [C/N]}\leq0.1$     & Precise [C/N] ages from \citet{roberts_cn_2025} \\
-        ${\rm [Fe/H]}$      & $\mathFeH\geq-0.4$            & Accurate [C/N] ages for upper RGB \& red clump stars \\
+        ${\rm [Fe/H]}$      & $\mathFeH\geq-0.4$            & Accurate [C/N] ages for upper RGB \& RC stars \\
         \hline
@@
 
-We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, the infall parameter selection in Section \ref{sec:parameter-selection}, and the stellar migration prescription in Section \ref{sec:migration}.
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh},
+% the infall parameter selection in Section \ref{sec:parameter-selection}, 
+and the stellar migration prescription in Section \ref{sec:migration}.
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
@@
     \startdata
-        R_{\rm gal}         & $[0,20]\kpc$  & ---           & \ref{sec:methods}     & Galactocentric radius \\
-        \delta R_{\rm gal}  & $0.1\kpc$ & ---               & \ref{sec:methods}     & Radial zone width \\
-        R_{\rm SF}          & $15.5\kpc$    & ---           & \ref{sec:methods}     & Maximum radius of star formation \\
-        t_{\rm final}       & $13.2\Gyr$ & ---              & \ref{sec:methods}     & Disk lifetime \\
-        \Delta t            & $10\Myr$  & ---               & \ref{sec:methods}     & Time-step size \\
-        n                   & 8         & ---               & \ref{sec:methods}     & Number of stellar populations formed per ring per timestep \\
-        \dot M_r            & continuous    & ---           & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
+        R_{\rm gal}         & $[0,20]\kpc$  & \nodata           & \ref{sec:methods}     & Galactocentric radius \\
+        \delta R_{\rm gal}  & $0.1\kpc$     & \nodata           & \ref{sec:methods}     & Radial zone width \\
+        R_{\rm SF}          & $15.5\kpc$    & \nodata           & \ref{sec:methods}     & Maximum radius of star formation \\
+        t_{\rm final}       & $13.2\Gyr$    & \nodata           & \ref{sec:methods}     & Disk lifetime \\
+        \Delta t            & $10\Myr$      & \nodata           & \ref{sec:methods}     & Time-step size \\
+        n                   & 8             & \nodata           & \ref{sec:methods}     & Number of stellar populations formed per ring per timestep \\
+        \dot M_r            & continuous    & \nodata           & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
         y/Z_\odot           & 1             & 2, 3              & \ref{sec:yields}      & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
@@
         f_{\rm Ia}(t)       & Equation \ref{eq:plateau-dtd} & Equation \ref{eq:powerlaw-dtd}    & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
-        t_{\rm Ia}          & $40\Myr$  & ---               & \ref{sec:yields}              & Minimum SN Ia delay time \\
-        \eta_\odot          & 0.2       & 1.4, 2.4          & \ref{sec:outflows}            & Outflow mass-loading factor at $R_\odot$ ($\eta\equiv\dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
-        R_\eta              & $5.0\kpc$ & ---               & \ref{sec:outflows}            & Exponential outflow scale radius \\
-        \tau_\star          & Equation \ref{eq:sf-law}      & ---   & \ref{sec:sf-law}      & Star formation efficiency timescale ($\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$) \\
-        k                   & 1.5       & ---               & \ref{sec:sf-law}              & Star formation law exponent \citep{kennicutt_global_1998} \\
-        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & ---   & \ref{sec:sfh} & Total stellar mass of the disk \citep{licquia_improved_2015} \\
+        t_{\rm Ia}          & $40\Myr$  & \nodata           & \ref{sec:yields}              & Minimum SN Ia delay time \\
+        \eta_\odot          & 0.2       & $0.6-2.4$         & \ref{sec:outflows}            & Outflow mass-loading factor at $R_\odot$ ($\eta\equiv\dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
+        R_\eta              & $5.0\kpc$ & \nodata           & \ref{sec:outflows}            & Exponential outflow scale radius \\
+        \tau_\star          & Equation \ref{eq:sf-law}      & \nodata & \ref{sec:sf-law}      & Star formation efficiency timescale ($\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$) \\
+        k                   & 1.5       & \nodata           & \ref{sec:sf-law}              & Star formation law exponent \citep{kennicutt_global_1998} \\
+        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & \nodata & \ref{sec:sfh} & Total stellar mass of the disk \citep{licquia_improved_2015} \\
         f_\Sigma(R_\odot)   & 0.12      & 0.25, 0.5         & \ref{sec:sfh}                 & Local thick/thin disk surface density ratio \\
-        R_1                 & $2.0\kpc$ & ---               & \ref{sec:sfh}                 & Thick disk scale radius \\
-        R_2                 & $2.5\kpc$ & ---               & \ref{sec:sfh}                 & Thin disk scale radius \\
+        R_1                 & $2.0\kpc$ & \nodata           & \ref{sec:sfh}                 & Thick disk scale radius \\
+        R_2                 & $2.5\kpc$ & \nodata           & \ref{sec:sfh}                 & Thin disk scale radius \\
         \mathXH_{\rm CGM}   & $-\infty$ & $-0.7$, $-0.5$    & \ref{sec:sfh}                 & Metallicity of infalling gas \\
-        f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & ---   & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
-        \tau_1              & $1\Gyr$   & $0.1-3\Gyr$       & \ref{sec:parameter-selection} & Timescale of the first infall epoch \\
-        \tau_2(R_\odot)     & $15\Gyr$  & $3-30\Gyr$        & \ref{sec:parameter-selection} & Timescale of the second infall epoch at the Solar annulus \\
-        R_{\tau_2}          & $7\kpc$   & ---               & \ref{sec:parameter-selection}      & Exponential scale radius of the second infall timescale \\
-        t_{\rm max}         & $4.2\Gyr$ & $1-5\Gyr$         & \ref{sec:parameter-selection}     & Time of maximum gas infall (onset of second infall) \\
-        \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & ---   & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
+        f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & \nodata   & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
+        \tau_1              & $1\Gyr$   & \nodata           & \ref{sec:sfh} & Timescale of the first infall epoch \\
+        \tau_2(R_\odot)     & $15\Gyr$  & \nodata           & \ref{sec:sfh} & Timescale of the second infall epoch at the Solar annulus \\
+        R_{\tau_2}          & $7\kpc$   & \nodata           & \ref{sec:sfh} & Exponential scale radius of the second infall timescale \\
+        t_{\rm max}         & $4.2\Gyr$ & \nodata           & \ref{sec:sfh} & Time of maximum gas infall (onset of second infall) \\
+        \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & \nodata & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
         \sigma_{\rm RM8}    & $2.68\kpc$ & $3.6$, $5.0\kpc$ & \ref{sec:migration}   & Radial migration strength (width of $\sigma_{\rm RM}$ for $\tau=8\Gyr$) \\
-        z                   & $[-3,3]\kpc$  & ---           & \ref{sec:migration} & Distance from Galactic midplane at present day \\
-        h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & ---   & \ref{sec:migration} & Disk scale height \\
+        z                   & $[-3,3]\kpc$  & \nodata       & \ref{sec:migration}   & Distance from Galactic midplane at present day \\
+        h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & \nodata       & \ref{sec:migration} & Disk scale height \\
     \enddata
@@
     Row (c) presents the distributions from APOGEE with ages derived from [C/N] abundances by \citet{roberts_cn_2025} (see Section \ref{sec:age-estimates}).
-The vertical blue dotted lines in row (c) mark the mode of the distribution of the $1-2\kpc$ age bin for reference.
-Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
+In row (c), the vertical blue dotted lines mark the mode of the distribution of the $1-2\kpc$ age bin for reference, and the gray dashed line marks the cut at $\mathFeH\ge-0.4$ for upper RGB and RC stars.%, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
     % {\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both two-infall models predict a steady evolution toward higher [Fe/H] with time.
@@
 In the models, the main, metal-poor peak consists of $8-9\Gyr$ old stars (post-dilution), and the extended high-[Fe/H] tail consists of $>9\Gyr$ old stars (pre-dilution).
-Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in all but the outer-most radial bin, peaking at $\mathFeH\approx-0.3$ and $+0.3$ independent of the location in the Galaxy.
+Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in the two inner-most radial bins, peaking at $\mathFeH\approx-0.3$ and $+0.3$.
 While the data and the models show qualitatively similar behavior, they actually represent different populations.
@@
 
-In the two-infall scenario, the low-$\alpha$ loop governs the chemical evolution of the thin disk (see discussion in Section \ref{sec:parameter-selection}).
-However, careful inspection of the marginal [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} reveals a different morphology: the models predict {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
+In the two-infall scenario, the low-$\alpha$ loop governs the chemical evolution of the thin disk \citep[see Section 6 of][]{spitoni_galactic_2019}.
+However, careful inspection of the marginal [O/Fe] distributions in Figure \ref{fig:yield-outflow} reveals a different morphology: the models predict {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
 The location of the intermediate peak varies depending on the yields and model parameters, but is always present.
@@
 The local maximum in $dN_\star/d\mathOFe$ comprises stars which formed in the second infall before SN Ia enrichment began to drive down [O/Fe].
-This prediction should therefore arise in {\it any} two-infall model regardless of its specific parameters, but its impact can be mitigated through parameter choices that act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow} or the models with longer $\tau_2$ in Figure \ref{fig:twoinfall-parameters}.
+This prediction should therefore arise in {\it any} two-infall model regardless of its specific parameters, but its impact can be mitigated through parameter choices that act to compress the distance between the low- and intermediate-$\alpha$ peaks, as in the $y/Z_\odot=1$ model in Figure \ref{fig:yield-outflow}.
 
@@
 The {\tt yZ2-fiducial} model (column (a)) predicts a high density of stars at $\mathOFe\approx+0.2$, where the data instead show a trough.
-The peak is most pronounced in the inner disk ($R_{\rm gal}=3-5\kpc$) because of the shorter infall timescale (see Figure \ref{fig:twoinfall-parameters}).
+The peak is most pronounced in the inner disk ($R_{\rm gal}=3-5\kpc$) because of the shorter infall timescale.
 
@@
 These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but they occupy a unique portion of the abundance space.
-A longer $\tau_1$ or smaller $t_{\rm max}$ could shift this population to higher [O/Fe], where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
+% A longer $\tau_1$ or smaller $t_{\rm max}$ could shift this population to higher [O/Fe], where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
 Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.

### 2025-10-21 src/tex/ms.tex
Fix typo
add trackchanges

@@
 % Define document class
-\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
+\documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex631}
 % \documentclass[linenumbers]{aastex631}
@@
 This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to a unique evolutionary history.
-A popular and well-studied explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
+A popular \added{and well-studied} explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
 Thanks to recent advances in stellar age measurements, we can now compare this model to more direct measurements of the Galaxy's evolutionary timescales across the disk.
@@
 
-\lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
+\lettrine{G}{alactic chemical evolution} (GCE) \added{studies aim} to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
 A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars \citep[e.g.,][]{tinsley_stellar_1979,matteucci_relative_1986}.
 In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
-The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe that are associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, has approximately Solar \aFe, and is associated with the kinematic thin disk.
+The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe \added{that are} associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, has approximately Solar \aFe, and is associated with the kinematic thin disk.
 The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
-An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and may not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}), suggesting that it could point to a unique evolutionary history for the MW.
+\added{An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and may not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}), suggesting that it could point to a unique evolutionary history for the MW.}
 
@@
 
-The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the $\alpha$-bimodality in the MW.
-The basic premise is that the rate of gas accretion onto the disk occurs in two bursts.
+\added{The two-infall scenario} was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the \added{$\alpha$-bimodality in the MW.
+The basic premise is that the rate of gas accretion onto the disk occurs in two bursts}.
 The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars.
 The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
-The initial model of \citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time.
-
-Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
+The initial model of \citet{chiappini_chemical_1997} successfully reproduced the \added{Solar neighborhood abundance data available at the time}.
+
+Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, \added{as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}}.
 Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
-\citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.
-\citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the star formation history inferred from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
+\added{\citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.} \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the star formation history \added{inferred} from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
 Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey \citep[SDSS;][]{sdss_collaboration_nineteenth_2025}.
 
-While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
-This decision is based on hydrodynamic simulations of Galactic fountains produced by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to its point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
+While previous studies have explored a large parameter space, most have assumed that the Galactic disk never \added{had} a substantial outflow.
+This decision is based on hydrodynamic simulations of Galactic fountains \added{produced} by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to \added{its} point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
 However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}; other simulations of MW-like galaxies with different prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
-Empirically, mass-loading is observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
-Even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.
+Empirically, mass-loading \added{is} observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
+Even if the MW is not currently ejecting a substantial outflow, it may have \added{done so} in the past.
 
@@
 \citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
-This degeneracy prohibits direct estimates of the yields from GCE models unless the effect of outflows is assumed to be insignificant.
-The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of varying the yield scale on two-infall scenario predictions.
-Varying the yield scale while maintaining an evolutionary end point consistent with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
+This degeneracy prohibits direct estimates of the \added{yields from GCE models} unless the effect of outflows is assumed to be insignificant.
+The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of \added{varying} the yield scale on two-infall scenario predictions.
+Varying the yield scale while maintaining an evolutionary end point \added{consistent} with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/smooth_vs_twoinfall.pdf}
+    \includegraphics[width=\linewidth]{figures/smooth_vs_twoinfall.pdf}
     \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves).
@@
 
-The two-infall scenario reproduces the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
+\added{The two-infall scenario reproduces} the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
 However, the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
@@
 % While the strength and speed of radial migration in the disk are not precisely measured, a single chemical evolution track need not explain the entire width of the local abundance distribution. 
-A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
-In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).
+\added{A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
+In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).}
 Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
-If the effect of radial migration is significant, then the local $\alpha$-bimodality could be explained without dramatic changes to the local gas abundance over time.
+If the effect of radial migration is significant, then the \added{local $\alpha$-bimodality could} be explained without dramatic changes to the local gas abundance over time.
 
@@
 
-As stellar age estimation techniques have improved over recent years, large catalogs have become available with age estimates for stars across a wide swath of the Galaxy.
-In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs suggest that stellar metallicities are remarkably consistent with age across most of the thin disk \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
+\added{As stellar age} estimation techniques have improved over recent years, large catalogs have become available with \added{age estimates} for stars across a wide swath of the Galaxy.
+In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs \added{suggest} that stellar metallicities are remarkably consistent with age across most of the \added{thin disk} \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
 \citet{johnson_milky_2024} demonstrated that these results are readily explained by a scenario in which the Galaxy reaches a state of chemical equilibrium.
 In this so-called ``equilibrium scenario,'' the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over Gyr timescales.
-Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the past $\sim8\Gyr$.
-
-The availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
+Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the \added{past $\sim8\Gyr$}.
+
+\added{The availability of} large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
 Our study draws on the steadiness of the Milky Way stellar metallicity gradient found by \citet{johnson_milky_2024} and empirical constraints on the yield scale from \citet{weinberg_scale_2024}.
@@
         NN age error        & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
-        Uncertainty on [C/N]    & $\sigma_{\rm [C/N]}\leq0.1$     & Precise [C/N] ages from \citet{roberts_cn_2025} \\
-        ${\rm [Fe/H]}$      & $\mathFeH\geq-0.4$            & Accurate [C/N] ages for upper RGB \& RC stars \\
+        \added{Uncertainty on [C/N]}    & $\sigma_{\rm [C/N]}\leq0.1$     & Precise [C/N] ages from \citet{roberts_cn_2025} \\
+        \added{${\rm [Fe/H]}$}      & $\mathFeH\geq-0.4$            & Accurate [C/N] ages for upper RGB \& RC stars \\
         \hline
@@
 APOGEE data were obtained from infrared spectrographs \citep{wilson_apache_2019} mounted on the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory.
-The data reduction pipeline is described by \citet{nidever_data_2015}, and the APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
+The data reduction pipeline is described by \citet{nidever_data_2015}, and \added{the} APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
 
@@
 We supplement the APOGEE DR17 abundance data with two different age catalogs.
-The first is from \citet{leung_variational_2023}, who trained a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
+The first is from \citet{leung_variational_2023}, who \added{trained} a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
 % This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and they recover accurate ages up to $\sim13\Gyr$, while other neural network-derived age catalogs exhibit an age plateau \citep[e.g.,][]{mackereth_dynamical_2019}.
-Following the recommendations of \citet{leung_variational_2023}, we cut all stars which have an age uncertainty greater than 40\%.
+\added{Following} the recommendations of \citet{leung_variational_2023}, we cut all stars which have an age uncertainty greater than 40\%.
 This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
@@
 
-Our second age catalog utilizes the [C/N]--age relation calibrated by \citet{roberts_cn_2025} for red giant branch (RGB) and red clump (RC) stars.
+Our second age catalog utilizes the [C/N]--age relation calibrated by \citet{roberts_cn_2025} for red giant branch (RGB) and red clump \added{(RC)} stars.
 The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
 This method has the benefit of providing age estimates for luminous giants ($\log g<2.5$), which increases the sample size at larger distances from the Sun.
-Uncertainties in the efficiency of FDU mixing and the RGB age--mass relationship mean that the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
-Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous RGB and RC stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
+\added{Uncertainties in} the efficiency of FDU mixing and the RGB age--mass relationship mean \added{that} the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
+Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous \added{RGB and RC} stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
 % The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
-We use the sample selection criteria from \citet{roberts_cn_2025}, and following their recommendation, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
+\added{We use the sample selection criteria from \citet{roberts_cn_2025}, and following their recommendation}, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
 With this relationship, we estimate ages for \num{124778} stars across the disk, including \num{21956} in the Solar neighborhood.
@@
 The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}.
-We set up a disk spanning $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
+We set up a disk \added{spanning} $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
 We use a time-step of $\Delta t=10\,{\rm Myr}$, $n=8$ stellar populations per time-step per ring, and we run our models to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
@@
 % the infall parameter selection in Section \ref{sec:parameter-selection}, 
-and the stellar migration prescription in Section \ref{sec:migration}.
+\added{and} the stellar migration prescription in Section \ref{sec:migration}.
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
@@
 % This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. Recently, 
-\citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
+\added{\citet{weinberg_scale_2024} used} a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
     In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$.
 We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
-}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun.
-However, \citet{johnson_milky_2024} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a \added{quantity} of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass \added{fraction} in the Sun.
+However, \citet{johnson_milky_2024} found that their GCE models with \added{this yield} scale approach present-day abundances too slowly to match the observed age--metallicity relation.
 Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
@@
 \end{equation}
-for each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
+\added{for} each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
 The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
@@
 Motivated by Equation \ref{eq:equilibrium}, we adopt a different outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
-Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we adjust $\eta_\odot$ to ensure that $Z_{\rm O,eq}\approx Z_{\rm O,\odot}$.
+\added{Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we adjust $\eta_\odot$ to ensure that $Z_{\rm O,eq}\approx Z_{\rm O,\odot}$.}
 % Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on stellar age trends.
@@
 \citet{johnson_milky_2024} used this approach to present a proof of concept for the equilibrium scenario.
-\citet{johnson_milky_2024} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
-To produce an exponentially declining radial [O/H] gradient, we adopt a prescription of
+\added{\citet{johnson_milky_2024} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
+To} produce an exponentially declining radial \added{[O/H]} gradient, we adopt a prescription of
 \begin{equation}
@@
 \end{equation}
-for the outflow mass-loading factor,
+\added{for the outflow mass-loading factor,}
 where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, consistent with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
-We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study.
-We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, \added{consistent} with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
+\added{We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study.
+We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.}
 
@@
 
-We use a power-law star formation prescription of $\dot\Sigma_\star\propto\Sigma_g^k$, with $k=1.5$ following \citet{kennicutt_global_1998}.
-Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
+\added{We use a power-law star formation prescription of} $\dot\Sigma_\star\propto\Sigma_g^k$, with $k=1.5$ following \citet{kennicutt_global_1998}.
+Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single \added{power-law to allow} for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
 In detail, we calculate the star formation efficiency (SFE) timescale
@@
 \end{equation}
-with $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, where $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ are observationally calibrated \citep{leroy_star_2008}.
+\added{with} $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, \added{where $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ are observationally calibrated} \citep{leroy_star_2008}.
 Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through a pre-factor
@@
 However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
-We find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
-To guard against over-correcting the SFE in the early Galaxy, we tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial differences.
+\added{We find} $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
+To guard against over-correcting the SFE in the early Galaxy, \added{we tested} eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial \added{differences}.
 
@@
 
-The infall rate is described by two successive, exponentially declining bursts in time.
-The first infall component forms the thick disk, and the second produces the thin disk.
-The un-normalized form of the infall rate is
+\added{The infall rate} is described by two successive, exponentially declining bursts in time.
+The first infall component \added{forms} the thick disk, and the second produces the thin disk.
+\added{The un-normalized} form of the infall rate is
 \begin{multline}
@@
 \end{equation*}
-where $\tau_1$ and $\tau_2(R_{\rm gal})$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall, $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
-We vary $\tau_2$ exponentially with $R_{\rm gal}$ and adopt a scale radius $R_{\tau_2}=7\kpc$ to match the stellar age gradients in MW-like spirals observed by \citet{sanchez_spatially_2020}.
-We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar disk has a surface density ratio of the thick and thin disks of
+where $\tau_1$ and \added{$\tau_2(R_{\rm gal})$} are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall, $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
+\added{We vary $\tau_2$ exponentially with $R_{\rm gal}$ and adopt a scale radius $R_{\tau_2}=7\kpc$ to match the stellar age gradients in MW-like spirals observed by \citet{sanchez_spatially_2020}.} We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar \added{disk has a} surface density ratio of the thick and thin disks \added{of}
 \begin{equation}
@@
 % Infall rate parameter selection
-Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
+\added{Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
 After exploring the effect of the infall timescales in one-zone models, we adopt $\tau_1=1\Gyr$ and $\tau_2(R_\odot)=15\Gyr$, in line with the parameters adopted by \citet{spitoni_galactic_2020}, but longer than in \citet{nissen_high-precision_2020}, \citet{spitoni_apogee_2021}, and \citet{hegedus_reconstructing_2025}.
 We also adopt $t_{\rm max}=4.2\Gyr$ (i.e., a lookback time of $9\Gyr$) so that our models are compatible with the median stellar age of the thick disk of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
-\citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.
+\citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.}
 
@@
 In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
-The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a present-day value of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
+The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a \added{present-day value} of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
 
@@
 In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
-The circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
+However, \added{previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.} The circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
 The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
@@
 In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathFeH_{\rm CGM}$.
-We assume the Solar-scaled abundance of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
+\added{We assume the Solar-scaled abundance} of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
 
@@
 \citet{spitoni_effect_2015} improved agreement with the observed local metallicity distribution, but their method is difficult to apply to model predictions across the disk.
-Our implementation, based on the diffusion method of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
+\added{Our implementation,} based on the diffusion method of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
 \citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to that of \citet{frankel_measuring_2018} and found a similar effect on stellar abundance distributions.
@@
 \end{equation}
-\citep{spitzer_dynamics_1942} where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The scale height $h_z$ is given by
+\added{\citep{spitzer_dynamics_1942}} where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The scale height $h_z$ is given by
 \begin{equation}
@@
 \end{equation}
-The final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
+\added{The} final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
 The parameters of Equations \ref{eq:radial-migration} and \ref{eq:scale-height} were chosen to fit the stellar migration patterns in the {\tt h277} hydrodynamical simulation \citep{christensen_implementing_2012}.
@@
 
-An important distinction between our method and that of \citet{spitoni_effect_2015} is that SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
+\added{An} important distinction between our method and that of \citet{spitoni_effect_2015} \added{is that} SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
 This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
@@
     \includegraphics[width=\onecolumn]{figures/gas_abundance_evolution.pdf}
-    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), each of which feature a major dilution event 9 Gyr ago.
-The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
-The black line (black points) plots the median (mode) of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
+    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), \added{each of which feature a major dilution event 9 Gyr ago.
+The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances} in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
+\added{The black line (black points) plots the median (mode)} of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
 The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.
@@
 As a natural consequence, the gas disk experiences a period of metal dilution, which should be recorded in the stellar record.
-Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions as a function of age at the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
+\added{Figure \ref{fig:yield-outflow}} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions \added{as a function of age at} the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
 As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
@@
 [O/H] and [Fe/H] increase by $0.1-0.2\dex$, relative to young stars, in the $\sim6-8\Gyr$ age range, likely due to metal-rich stars migrating outward from the inner Galaxy where the surface densities are higher.
-We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ for comparison.
+\added{We over-plot} the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ \added{for comparison}.
 The models are in broad agreement with each other and with the data at lookback times of $\lesssim5\Gyr$.
-At ages of $\sim5-8\Gyr$, the models underpredict the metallicities of the observed stars by up to half an order of magnitude, a natural consequence of the dilution associated with the second infall event.
-This discrepancy is modestly reduced in the higher $y/Z_\odot$ models, which re-enrich more rapidly.
-However, these models exacerbate tensions with the age--[O/Fe] relation because the O abundance increases more before enrichment from second-infall SNe Ia becomes important, making the $\alpha$-enhancement from the ensuing starburst more pronounced.
-Overall, none of our models provide a good match to these age trends.
+At ages of $\sim5-8\Gyr$, the models \added{underpredict} the metallicities of the observed stars by up to half an order of \added{magnitude, a natural} consequence of the dilution associated with the second infall event.
+This discrepancy is \added{modestly reduced in} the higher $y/Z_\odot$ models, which re-enrich more rapidly.
+\added{However}, these models exacerbate tensions with the age--[O/Fe] relation because the O abundance \added{increases more} before enrichment from second-infall SNe Ia becomes important, making the $\alpha$-enhancement from the ensuing starburst more pronounced.
+\added{Overall,} none of our models provide a good match to these age trends.
 Figure \ref{fig:yield-outflow} illustrates a point that will arise as a theme throughout the remainder of this paper, which is that the signatures of a substantial dilution event and subsequent re-enrichment, characteristic of the two-infall scenario, are simply not present in the observed age--abundance trends.
@@
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}< 9\kpc$, $|z| < 0.5\kpc$) color-coded by its birth radius.
-In this and subsequent figures, a Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+\added{In this and subsequent figures, a} Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
 For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
 The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$, and the black squares plot the median stellar abundance in {2 Gyr}-wide age bins.
-The red line and points are the median abundance for APOGEE stars, and the shaded regions are the 16th--84th percentile ranges.
+\added{The red line and points are the median abundance for APOGEE stars, and the shaded regions are the 16th--84th percentile ranges.
+}
     % We adopt the NN age estimates for APOGEE stars from \citet{leung_variational_2023}.
-    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).
+    \added{Each column} shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).
     % {\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither can simultaneously match all of the observed age--abundance relation.
@@
 Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
-The problem is exacerbated in the two-infall case because of the delayed dilution event---the approach to equilibrium is ``reset'' by the second infall.
+The problem is exacerbated in the two-infall case because of the delayed dilution \added{event---the approach} to equilibrium is ``reset'' by the second infall.
 The dilution of the ISM then gets baked into the stellar abundance record.
@@
 The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed by SNe Ia.
-We smoothed simulated data points based on the median age and abundance errors in Table \ref{tab:uncertainties} to incorporate these errors in the model.
+\added{We smoothed} simulated data points \added{based on} the median age and abundance errors in Table \ref{tab:uncertainties} \added{to incorporate these errors in the model}.
 The black dashed curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
@@
 As a result, the stars that make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution at fixed age.
-Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, for example, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
+Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, \added{for example}, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
 
@@
 Column (c) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM because more of the gas disk is built up during the first infall phase.
-Model {\tt yZ1-diskratio} produces the best agreement of the four models in Figure \ref{fig:abundance-evolution-params} to the observed age--[Fe/H] relation (second row).
+Model {\tt yZ1-diskratio} produces the best agreement \added{of the four models in Figure \ref{fig:abundance-evolution-params} to} the observed age--[Fe/H] relation (second row).
 However, agreement with the observed age--[O/Fe] relation is poor.
@@
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
-% Pre-enriched infall also raises the equilibrium metallicity, so we
-.increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity. 
-Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
+% Pre-enriched infall also raises the equilibrium metallicity, so we increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity. 
+\added{Pre-enriched infall} at this level mitigates but does not completely solve the two discrepancies.
 The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, since the accreting gas is less chemically different from the ISM, diminishing the effects of dilution.
@@
     \includegraphics[width=\textwidth]{figures/mdf_evolution.pdf}
-    \caption{Decomposition of the present-day MDF by stellar age across the Galactic disk. 
+    \caption{\added{Decomposition of the present-day MDF by stellar age across the Galactic disk. 
     % In each panel, normalized MDFs within a {2 kpc}-wide annulus are color-coded by the stellar age range. 
@@
 The distributions in all panels are restricted to $|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
-Rows (a) and (b) present the distributions from the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models, respectively (see Table \ref{tab:models}).
+Rows (a) and (b) present the distributions from the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models, respectively} (see Table \ref{tab:models}).
     % A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}. 
     Row (c) presents the distributions from APOGEE with ages derived from [C/N] abundances by \citet{roberts_cn_2025} (see Section \ref{sec:age-estimates}).
-In row (c), the vertical blue dotted lines mark the mode of the distribution of the $1-2\kpc$ age bin for reference, and the gray dashed line marks the cut at $\mathFeH\ge-0.4$ for upper RGB and RC stars.%, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
+\added{In row (c), the vertical blue dotted lines mark the mode of the distribution of the $1-2\kpc$ age bin for reference, and the gray dashed line marks the cut at $\mathFeH\ge-0.4$ for upper RGB and RC stars.}%, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
     % {\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both two-infall models predict a steady evolution toward higher [Fe/H] with time.
@@
 The discrepancies between the predicted and observed abundance evolution in the Solar neighborhood discussed in Section \ref{sec:age-abundance} persist across the Galactic disk.
-Figure \ref{fig:mdf-evolution} breaks down the MDF by stellar age across five radial bins for the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models.
-For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in Section \ref{sec:age-estimates}.
+Figure \ref{fig:mdf-evolution} \added{breaks down the MDF by stellar age} across five radial bins for the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models.
+For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in \added{Section \ref{sec:age-estimates}.}
 
@@
 The distance between the $1-2\Gyr$ and $2-4\Gyr$ age bins is smaller for the \yZ{2} model because of the faster approach to equilibrium (see also Figure \ref{fig:yield-outflow}).
-In the Solar annulus (center column), the peak of the MDF of $6-8\Gyr$ old stars is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
+In the Solar annulus (center column), the peak of \added{the MDF of $6-8\Gyr$ old stars} is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
 
@@
 In the models, the main, metal-poor peak consists of $8-9\Gyr$ old stars (post-dilution), and the extended high-[Fe/H] tail consists of $>9\Gyr$ old stars (pre-dilution).
-Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in the two inner-most radial bins, peaking at $\mathFeH\approx-0.3$ and $+0.3$.
-While the data and the models show qualitatively similar behavior, they actually represent different populations.
+Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in \added{the two inner-most radial bins}, peaking at $\mathFeH\approx-0.3$ and $+0.3$.
+\added{While} the data and the models show qualitatively similar behavior, they actually represent different populations.
 In the data, the metal-rich peak are all low-$\alpha$ stars, while the metal-poor peak is the locus of the high-$\alpha$ sequence---a reversal of the model predictions.
@@
     % and a Gaussian scatter has been applied to the predicted abundances according to Table \ref{tab:uncertainties}. 
-    Stars in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$. 
+    \added{Stars} in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$. 
     % {\bf Key takeaway:} both models predict a stellar over-density at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.
@@
 
-In the two-infall scenario, the low-$\alpha$ loop governs the chemical evolution of the thin disk \citep[see Section 6 of][]{spitoni_galactic_2019}.
-However, careful inspection of the marginal [O/Fe] distributions in Figure \ref{fig:yield-outflow} reveals a different morphology: the models predict {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
+In the two-infall scenario, the low-$\alpha$ loop governs the chemical evolution of the thin disk \added{\citep[see Section 6 of][]{spitoni_galactic_2019}}.
+However, careful inspection of the marginal [O/Fe] distributions in \added{Figure \ref{fig:yield-outflow}} reveals a different morphology: the models predict {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
 The location of the intermediate peak varies depending on the yields and model parameters, but is always present.
@@
 We have not accounted for the APOGEE selection function in our models, but there is no evident reason for observational effects to produce this difference in morphology.
-This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and is typical of other models \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
+This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and \added{is typical of other models} \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
 The two-infall scenario is otherwise fairly successful at reproducing the local stellar distribution in [O/Fe]--[Fe/H] space.
@@
     % The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). 
-    For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
+    \added{For visual clarity}, each distribution is smoothed with a box-car of width 0.05 dex.
     Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, {\tt yZ2-fiducial}; {\bf (b)} a model with a power-law DTD, {\tt yZ2-powerlaw}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\tt yZ2-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ2-preenrich} (see Table \ref{tab:models} for details).
@@
     % A Gaussian scatter is applied to each point according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}. 
-    The solid (dashed) contours enclose 30\% (80\%) of the APOGEE stars in each region. 
+    \added{The solid (dashed) contours enclose 30\% (80\%) of the APOGEE stars in each region.} 
     % {\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.
@@
 Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
-Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate than the illustrative examples in the previous section.
-Our focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters.
+Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate \added{than the illustrative examples in the previous section.
+Our} focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters.
 
@@
 % A longer $\tau_1$ or smaller $t_{\rm max}$ could shift this population to higher [O/Fe], where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
-Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
+\added{Second}, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
 The following section explores this second prediction in greater detail.
@@
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
-The left and center panels show the {\tt yZ1-best} and {\tt yZ2-best} models, with ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$ (see Table \ref{tab:models}).
+The left and center panels \added{show} the {\tt yZ1-best} and {\tt yZ2-best} models, with ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$ (see Table \ref{tab:models}).
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the abundances and ages according to Table \ref{tab:uncertainties}.
 The right panel plots the results from APOGEE using the \citet{leung_variational_2023} NN age catalog.
-The contours show the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
+The contours \added{show} the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
     {\it Bottom}: Stellar age distributions in the Solar annulus for all stars (black) and LMR stars (gray).
@@
     % after forward-modeling age uncertainties, 
-    and the right panel plots the NN ages for APOGEE stars.
+    \added{and the right panel plots the NN ages for APOGEE stars.}
     % {\bf Key takeaway:} Both two-infall models predict a fundamentally different age pattern than what is observed, especially for LMR stars.
@@
 The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
-It is difficult to obtain a unimodal age distribution with the available parameter space.
+It is difficult to \added{obtain} a unimodal age distribution with the available parameter space.
 A dearth of intermediate-age, high-metallicity stars is a natural outcome of a substantial dilution event, which is a defining feature of the two-infall scenario.
@@
 Similarly, \citet{palla_chemical_2020,palla_mapping_2024} used an inward flow with a speed of $\sim1\kms$ to reproduce the observed radial metallicity profile in the absence of Galactic outflows.
-\citet{johnson_constraints_2025} considered several possible scenarios for the processes that drive radial gas flows.
-Their findings support these previous arguments that radial gas flows can help to regulate the overall metal abundance and radial gradient.
+\added{\citet{johnson_constraints_2025}} considered several possible scenarios for the processes that drive radial gas flows.
+Their findings support these previous arguments that radial gas flows \added{can help to regulate the overall metal abundance and radial gradient.}
 
@@
 However,
-The outflow is simpler in implementation than a radial gas flow; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
+\added{The outflow is simpler in implementation than a radial gas flow}; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
 This approach allows us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
 % A radial gas flow requires at least one assumption about the processes that drive the flow and generally does not afford the same level of flexibility. 
-We have therefore focused on models with outflows in this paper for the sake of simplicity, but constant radial gas flow models should have similar effects.
+\added{We have therefore focused on models with outflows in this paper for the sake of simplicity, but constant} radial gas flow models should have similar effects.
 
@@
 The blue dashed curve represents the fiducial model that has an exponentially declining infall rate with timescale $\tau_{\rm in}=15\Gyr$, and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
-The red solid curve plots the output of a model which has an enhancement of $\tau_\star$ by a factor of 10 for 200 Myr starting at $t=1.4\,{\rm Gyr}$.
+The red solid curve plots the output of a model which \added{has an enhancement of $\tau_\star$ by a factor of 10 for 200 Myr} starting at $t=1.4\,{\rm Gyr}$.
 Both models assume the \yZ{2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
-The grayscale histogram is the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}< 9\kpc$, $|z|<2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
+The grayscale histogram \added{is} the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}< 9\kpc$, $|z|<2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}
@@
 
-The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation temporarily.
-For the two-infall model, this phase of low star formation lasts for a few Gyr between the $e$-folding timescale of the first infall and the onset of the second.
+The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation \added{temporarily}.
+For the two-infall model, this phase of low star formation lasts for a few Gyr \added{between} the $e$-folding timescale of the first infall and the onset of the second.
 However, as we have shown in Section \ref{sec:age-abundance}, the resulting dilution of the ISM is in tension with the observed stellar age--metallicity relation.
@@
 The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
-As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk measured by \citet{pinsonneault_apokasc-3_2025}.
+As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk \added{measured by} \citet{pinsonneault_apokasc-3_2025}.
 This hiatus model illustrates an alternative scenario for reproducing the $\alpha$-bimodality, but a full multi-zone treatment is beyond the scope of this work.
@@
 We explored multiple parameter modifications to bring the model predictions closer to the data, including the yield scale, radial migration strength, metallicity of the accreted gas, thick-to-thin disk mass ratio, and the SN Ia DTD.
-We found that our two-infall models faced the following challenges:
+We found that our two-infall models faced the following \added{challenges}:
 
 \begin{itemize}
-    \item By the model's design, the Galaxy undergoes a period of rapid dilution and subsequent re-enrichment.
+    \item By the model's design, the Galaxy undergoes a period of \added{rapid} dilution and subsequent re-enrichment.
 Models at a lower yield scale and weaker outflows predict slower re-enrichment.
 By contrast, the observed stellar age--metallicity relation is roughly constant over the past $\sim10\Gyr$.
-Pre-enriching the accreted gas can reduce the magnitude of the dilution, but cannot eliminate it entirely.
+Pre-enriching the accreted gas can reduce the magnitude of the dilution, but \added{cannot} eliminate it entirely.
     \item Due to this re-enrichment, our models predict that the MDF shifts to higher metallicity with decreasing age throughout the disk.
@@
 
-We have not found a GCE model, two-infall or otherwise, that is capable of reproducing all of the observations.
+\added{We} have not found a GCE model, two-infall or otherwise, that is capable of reproducing all of the \added{observations}.
 The ``inside-out'' models of \citet{johnson_stellar_2021} are better able to predict a slowly evolving metallicity gradient, but they do not predict an $\alpha$-bimodality.
@@
 
-We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper, and to Prof.\ Christopher Kochanek for his useful comments on the manuscript.
+We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper, \added{and to Prof.\ Christopher Kochanek for his useful comments on the manuscript}.
 We also thank Dr.\ Emanuele Spitoni for useful conversations about this work.

### 2025-10-21 src/tex/ms.tex
Add figure directory command

@@
 \newcommand{\onecolumn}{0.47\textwidth}
+\newcommand{\figpath}[1]{./figures/#1}
+\newcommand{\tabpath}[1]{./output/#1}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/smooth_vs_twoinfall.pdf}
+    \includegraphics[width=\onecolumn]{\figpath{smooth_vs_twoinfall.pdf}}
     \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves).
@@
     \label{tab:uncertainties}
-    \input{output/uncertainties.tex}
+    \input{\tabpath{uncertainties.tex}}
 \end{table}
@@
     \caption{Nucleosynthetic yields at each of the yield scales (see Section \ref{sec:yields}).}
-    \include{output/yields.tex}
+    \include{\tabpath{yields.tex}}
     \label{tab:yields}
@@
     \centering
-    \includegraphics[width=\onecolumn]{figures/star_formation_history.pdf}
+    \includegraphics[width=\onecolumn]{\figpath{star_formation_history.pdf}}
     \caption{The evolution of (a) the infall surface density, (b) the star formation surface density, (c) the gas surface density, and (d) the star formation efficiency timescale as a function of time for our fiducial multi-zone model with $y/Z_\odot=1$.
@@
     \centering
-    \includegraphics[width=\onecolumn]{figures/gas_abundance_evolution.pdf}
+    \includegraphics[width=\onecolumn]{\figpath{gas_abundance_evolution.pdf}}
     \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), \added{each of which feature a major dilution event 9 Gyr ago.
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/stellar_abundance_evolution.pdf}
+    \includegraphics[width=\linewidth]{\figpath{stellar_abundance_evolution.pdf}}
     \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}).
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/mdf_evolution.pdf}
+    \includegraphics[width=\textwidth]{\figpath{mdf_evolution.pdf}}
     \caption{\added{Decomposition of the present-day MDF by stellar age across the Galactic disk. 
@@
     \centering
-    \includegraphics[width=\onecolumn]{figures/ofe_feh_density.pdf}
+    \includegraphics[width=\onecolumn]{\figpath{ofe_feh_density.pdf}}
     \caption{The density of stars in the [O/Fe]--[Fe/H] plane predicted by multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/ofe_distributions.pdf}
+    \includegraphics[width=\textwidth]{\figpath{ofe_distributions.pdf}}
     \caption{Normalized stellar [O/Fe] distributions predicted by multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e).
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/ofe_feh_best.pdf}
+    \includegraphics[width=\linewidth]{\figpath{ofe_feh_best.pdf}}
     \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/lmr_ages.pdf}
+    \includegraphics[width=\textwidth]{\figpath{lmr_ages.pdf}}
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
@@
     \centering
-    \includegraphics[width=\onecolumn]{figures/sfe_hiatus.pdf}
+    \includegraphics[width=\onecolumn]{\figpath{sfe_hiatus.pdf}}
     \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.

### 2025-10-21 src/tex/ms.tex
Remove commented-out passages

@@
 
-% An explanation for the MW $\alpha$-bimodality has yet to be broadly accepted in the GCE literature.
-An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and may not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}).
-Its presence and characteristics in our Galaxy could potentially have arisen due to a unique evolutionary history.
-GCE models that attempt to solve this problem generally fall into two camps.
-Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars or the inside-out growth of the disk \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
-Others argue for a bursty star formation history driven by multiple accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023}.
-
 \added{The two-infall scenario} was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the \added{$\alpha$-bimodality in the MW.
@@
 Varying the yield scale while maintaining an evolutionary end point \added{consistent} with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
-
-% The observed chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary motivation for the two-infall scenario.
-\citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a period of reduced star formation, which is a natural consequence of the delay between the two accretion epochs.
-In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario.
-However, \citet{plotnikova_chemical_2024} found no evidence for multiple sequences in the local AMR, and argued that such patterns can arise due to selection effects.
-Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000,spitoni_remind_2024}, although most GCE models in the literature benchmark against these observables \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021}.
 
@@
 \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}.
-% Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor depends on a model of the evolution of the radial metallicity profile in the MW.
-% While the strength and speed of radial migration in the disk are not precisely measured, a single chemical evolution track need not explain the entire width of the local abundance distribution. 
 \added{A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
@@
 If the effect of radial migration is significant, then the \added{local $\alpha$-bimodality could} be explained without dramatic changes to the local gas abundance over time.
-
-% In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
-% \citet{schonrich_chemical_2009} first showed that radial migration can produce an $\alpha$-bimodality through a superposition of chemical tracks, although they did not directly compare against MW data.
-Others have produced a more MW-like $\alpha$-bimdodality using a combination of radial migration and inside-out galaxy growth \citep[e.g.,][]{kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
-In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history.
-\citet{sharma_chemical_2021} and \citet{chen_chemical_2023} showed that a simultaneous decline in the star formation rate and the \aFe ratio is needed to separate the sequences in chemical space.
-\citet{chen_recent_2025} additionally argued that the double sequence in the local age--metallicity relation observed by \citet{nissen_high-precision_2020} can also be explained by a smooth star formation history and inside-out disk growth.
-However, other GCE models that incorporate both radial migration and smooth, inside-out star formation have failed to predict an $\alpha$-bimodality \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024}.
-While the $\alpha$-bimodality remains a key piece of evidence for the two-infall scenario, it is not the only proposed explanation.
 
@@
 The first is from \citet{leung_variational_2023}, who \added{trained} a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
-% This catalog has two main advantages over other neural network (NN) age estimates: their method is designed to reduce contamination from abundance information (in particular [$\alpha$/Fe]), and they recover accurate ages up to $\sim13\Gyr$, while other neural network-derived age catalogs exhibit an age plateau \citep[e.g.,][]{mackereth_dynamical_2019}.
 \added{Following} the recommendations of \citet{leung_variational_2023}, we cut all stars which have an age uncertainty greater than 40\%.
@@
 Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous \added{RGB and RC} stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
-% The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
 \added{We use the sample selection criteria from \citet{roberts_cn_2025}, and following their recommendation}, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
@@
 
-We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh},
-% the infall parameter selection in Section \ref{sec:parameter-selection}, 
-\added{and} the stellar migration prescription in Section \ref{sec:migration}.
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, \added{and} the stellar migration prescription in Section \ref{sec:migration}.
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
@@
 The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models.
-% This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. Recently, 
 \added{\citet{weinberg_scale_2024} used} a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
@@
 \added{Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we adjust $\eta_\odot$ to ensure that $Z_{\rm O,eq}\approx Z_{\rm O,\odot}$.}
-% Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than Equation \ref{eq:equilibrium} would indicate as required to reach Solar metallicity at the present day, assuming that $Z_{\rm O,eq}\approx Z_{\rm O,\infty}$ as suggested by \citet{johnson_milky_2024} based on stellar age trends.
 Table \ref{tab:models} reports the value of $\eta_\odot$ in each of our models.
 
-% Not all GCE studies have constrained their models to reach an equilibrium at the Solar metallicity.
-For example, the models of \citet{palla_chemical_2020} and \citet{spitoni_remind_2024} predict somewhat super-Solar metallicity in the present-day Solar neighborhood.
-Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances  indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we use $\eta$ to fine-tune the chemical evolution end-point to $\mathOH\approx0.0$.
-
-% Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$.
-\citet{johnson_milky_2024} used this approach to present a proof of concept for the equilibrium scenario.
 \added{\citet{johnson_milky_2024} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
@@
 We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.}
-
-% Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows.
-Even in studies that do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023} or does not vary with radius \citep{hegedus_reconstructing_2025}.
-To achieve a realistic radial metallicity gradient, many studies have adopted the yields of \citet{francois_evolution_2004} and a prescription for the infall timescale of the thin disk that increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}.
-Additionally, some studies have implemented radial gas flows or a variable star formation efficiency in order to regulate the radial metallicity gradient \citep[e.g.,][]{spitoni_effects_2011,palla_chemical_2020}.
-
-% As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.
-Here, we aim to study the effect of the assumed yield scale on two-infall model predictions, so we use mass-loaded outflows to control the final state of chemical evolution across the disk.
-However, mass-loaded outflows are not a necessary ingredient for the results of this study.
-We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
 
@@
 
-% \subsection{Infall Rate Parameter Selection}
-% \label{sec:parameter-selection}
-
-% \begin{figure*}
-%     \centering
-%     \includegraphics[width=\textwidth]{figures/infall_parameters.pdf}
-%     \caption{Gas abundance tracks in the [O/Fe]--[Fe/H] plane for one-zone chemical evolution models with different infall history parameters.
-In each panel, one parameter is varied according to the legend while the other two are held fixed.
-The open symbols along each curve mark logarithmic steps in time, as denoted in panel (b).
-The marginal panels show the corresponding stellar abundance distributions, which are convolved with an 0.02 dex Gaussian kernel for visual clarity.
-All models use the same fiducial parameters as the $R_{\rm gal}=8\kpc$ ring in the multi-zone models, with \yZ{1} and $\eta=0.2$.
-The black lines in each panel represent the fiducial parameters.}
-%     \label{fig:twoinfall-parameters}
-% \end{figure*}
-
-% Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
-Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}.
-The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence.
-Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the corresponding effect on the stellar abundance distribution is small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$.
-It does, however, affect the position of the high-$\alpha$ peak, though this effect is more easily seen in the multi-zone model outputs.
-We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, similar to \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020}, \citet{spitoni_apogee_2021} or \citet{hegedus_reconstructing_2025}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.35$ in the multi-zone models.
-
-% Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that the second infall timescale $\tau_2$ controls the size of the low-$\alpha$ loop, which affects the width of the MDF and the low-$\alpha$ [O/Fe] distribution.
-A shorter $\tau_2$ produces a bigger loop and therefore a broader MDF and [O/Fe] distribution, while a longer $\tau_2$ produces a smaller loop, leading to both a narrower low-$\alpha$ sequence and a narrower MDF.
-We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is close to a constant infall rate, so a further increase in $\tau_2$ has diminishing effect.
-Between $\tau_2=3-30\,{\rm Gyr}$, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood.
-We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the size of the loop and width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times (see further discussion in Section \ref{sec:abundance-distributions}).
-This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020}, \citet{spitoni_apogee_2021}, and \citet{hegedus_reconstructing_2025}.
-
-% In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk.
-Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scaled $\tau_2$ linearly with radius, with $\tau_2\approx1\Gyr$ in the inner disk and $\tau_2=7\Gyr$ at the Solar annulus.
-This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}.
-We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\Gyr$ at the Solar annulus and a scale radius $R_{\tau_2}=7\kpc$.
-This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}.
-We have also run models with a linear prescription and with a uniform value for $\tau_2$ and have found little difference in our key results.
-
-% Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\Gyr$, but in this case the gas tracks do not produce the characteristic abundance loop.
-For $t_{\rm max}>2\Gyr$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different.
-The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}).
-We adopt a fiducial value of $t_{\rm max}=4.2\Gyr$, i.e.
-a lookback time of $9\Gyr$, which is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021,hegedus_reconstructing_2025}.
-This ensures that our models are compatible with the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
-
-% The Milky Way's last major merger with the dwarf galaxy, dubbed Gaia Sausage-Enceladus \citep[GSE;][]{belokurov_co-formation_2018,helmi_merger_2018}, has been proposed as an important influence on the transition from the thick disk to the thin disk, as in \citet{spitoni_remind_2024}.
-Our fiducial value of $t_{\rm max}=4.2\Gyr$ places the start of the formation of the thin disk close to the GSE merger (within uncertainties), which likely occurred $\sim10\Gyr$ ago \citep[e.g.,][]{helmi_merger_2018,gallart_uncovering_2019,naidu_reconstructing_2021,woody_rapid_2025}.
-However, recent arguments suggest that the GSE merger would not have led to two-infall-like evolution because the mass ratio is too low to produce sufficient dilution \citep{orkney_milky_2025}.
-
-% We note that all our models are normalized to produce the same thick-to-thin-disk mass ratio of $f_{\Sigma}(R_\odot)=0.12$ \citep{bland-hawthorn_galaxy_2016} at the Solar annulus regardless of the infall parameters.
-The high-$\alpha$ sequence appears much less prominent in our [O/Fe] distributions in Figure \ref{fig:twoinfall-parameters} than in the data because the one-zone model outputs include only stars formed in-situ at the Solar annulus.
-In our multi-zone models, most of the high-$\alpha$ stars present in the Solar neighborhood have migrated from the inner Galaxy.
-
 \subsection{Stellar Migration}
@@
 \citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
-% Assuming a constant migration speed, they prescribed some fraction of stars born in the inner and outer Galaxy that will contribute to the local present-day population, and they also assumed that some fraction of stars born in the Solar neighborhood will have migrated elsewhere by the present day.
-\citet{spitoni_effect_2015} improved agreement with the observed local metallicity distribution, but their method is difficult to apply to model predictions across the disk.
 \added{Our implementation,} based on the diffusion method of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
@@
 \added{The black line (black points) plots the median (mode)} of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
-The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.
-    % {\bf Key takeaway:} All models feature a major dilution event 9 Gyr ago, and the \yZ{1} model re-enriches the most slowly.
-    }
+The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
     \label{fig:yield-outflow}
@@
 
-% The two-infall scenario requires a large quantity of pristine or low-metallicity gas to be accreted onto the disk over a short span of time.
-As a natural consequence, the gas disk experiences a period of metal dilution, which should be recorded in the stellar record.
 \added{Figure \ref{fig:yield-outflow}} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions \added{as a function of age at} the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
 As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
-% In agreement with recent work (see discussion in Section \ref{sec:introduction}), the trend with age is interestingly flat.
-[O/H] and [Fe/H] increase by $0.1-0.2\dex$, relative to young stars, in the $\sim6-8\Gyr$ age range, likely due to metal-rich stars migrating outward from the inner Galaxy where the surface densities are higher.
 \added{We over-plot} the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ \added{for comparison}.
@@
 \added{The red line and points are the median abundance for APOGEE stars, and the shaded regions are the 16th--84th percentile ranges.
-}
-    % We adopt the NN age estimates for APOGEE stars from \citet{leung_variational_2023}.
-    \added{Each column} shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).
-    % {\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither can simultaneously match all of the observed age--abundance relation.
-    }
+Each column} shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).}
     \label{fig:abundance-evolution-params}
@@
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
-% Pre-enriched infall also raises the equilibrium metallicity, so we increase the mass-loading factor to $\eta=0.6$ to maintain the end-point at roughly Solar metallicity. 
 \added{Pre-enriched infall} at this level mitigates but does not completely solve the two discrepancies.
@@
     \caption{\added{Decomposition of the present-day MDF by stellar age across the Galactic disk. 
-    % In each panel, normalized MDFs within a {2 kpc}-wide annulus are color-coded by the stellar age range. 
     The gray curve plots the total present-day MDF in each region.
@@
 Rows (a) and (b) present the distributions from the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models, respectively} (see Table \ref{tab:models}).
-    % A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}. 
 Row (c) presents the distributions from APOGEE with ages derived from [C/N] abundances by \citet{roberts_cn_2025} (see Section \ref{sec:age-estimates}).
-\added{In row (c), the vertical blue dotted lines mark the mode of the distribution of the $1-2\kpc$ age bin for reference, and the gray dashed line marks the cut at $\mathFeH\ge-0.4$ for upper RGB and RC stars.}%, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages.
-    % {\bf Key takeaway:} The APOGEE distributions show remarkably little variation in mode [Fe/H] over the past $\sim6-8$ Gyr at all radii, whereas both two-infall models predict a steady evolution toward higher [Fe/H] with time.
-    }
+\added{In row (c), the vertical blue dotted lines mark the mode of the distribution of the $1-2\kpc$ age bin for reference, and the gray dashed line marks the cut at $\mathFeH\ge-0.4$ for upper RGB and RC stars.}}
     \label{fig:mdf-evolution}
@@
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution.
-    % and a Gaussian scatter has been applied to the predicted abundances according to Table \ref{tab:uncertainties}. 
-    \added{Stars} in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$. 
-    % {\bf Key takeaway:} both models predict a stellar over-density at intermediate [O/Fe] and low metallicity, which is not observed in APOGEE.
-    }
+    \added{Stars} in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$.}
     \label{fig:ofe-feh-density}
@@
 Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
-    % The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). 
 \added{For visual clarity}, each distribution is smoothed with a box-car of width 0.05 dex.
-    Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, {\tt yZ2-fiducial}; {\bf (b)} a model with a power-law DTD, {\tt yZ2-powerlaw}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\tt yZ2-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ2-preenrich} (see Table \ref{tab:models} for details).
-    % {\bf Key takeaway:} For the \yZ{2} case, a higher thick-to-thin disk ratio or pre-enrichment of the accreted gas can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.
-    }
+    Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, {\tt yZ2-fiducial}; {\bf (b)} a model with a power-law DTD, {\tt yZ2-powerlaw}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\tt yZ2-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ2-preenrich} (see Table \ref{tab:models} for details).}
     \label{fig:ofe-distribution-parameters}
@@
 Each panel presents a random mass-weighted sample of \num{10000} stellar populations color-coded by age.
-    % A Gaussian scatter is applied to each point according to the median [C/N]-derived age and abundance uncertainties in Table \ref{tab:uncertainties}. 
-    \added{The solid (dashed) contours enclose 30\% (80\%) of the APOGEE stars in each region.} 
-    % {\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.
-    }
+\added{The solid (dashed) contours enclose 30\% (80\%) of the APOGEE stars in each region.}}
     \label{fig:ofe-feh-best}
@@
 These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but they occupy a unique portion of the abundance space.
-% A longer $\tau_1$ or smaller $t_{\rm max}$ could shift this population to higher [O/Fe], where it would be obscured by the rest of the low-$\alpha$ sequence (see Figure \ref{fig:twoinfall-parameters}).
 \added{Second}, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
@@
     {\it Bottom}: Stellar age distributions in the Solar annulus for all stars (black) and LMR stars (gray).
-The left and center panels plot the mass-weighted age distributions predicted by the models,
-    % after forward-modeling age uncertainties, 
-    \added{and the right panel plots the NN ages for APOGEE stars.}
-    % {\bf Key takeaway:} Both two-infall models predict a fundamentally different age pattern than what is observed, especially for LMR stars.
-    }
+The left and center panels plot the mass-weighted age distributions predicted by the models, \added{and the right panel plots the NN ages for APOGEE stars.}}
     \label{fig:lmr-ages}
@@
 In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2024} demonstrated can improve agreement with age trends across the Galactic disk.
-% Johnson et al.
-(2025, in preparation) found similar results for radial gas flows with velocities that are relatively constant in both Galactocentric radius and time.
-At least one radial gas flow scenario therefore has similar effects on metal enrichment as our outflow prescription.
-However,
 \added{The outflow is simpler in implementation than a radial gas flow}; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
 This approach allows us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
-% A radial gas flow requires at least one assumption about the processes that drive the flow and generally does not afford the same level of flexibility. 
 \added{We have therefore focused on models with outflows in this paper for the sake of simplicity, but constant} radial gas flow models should have similar effects.

### 2025-11-10 src/tex/ms.tex

@@
 % Define document class
-\documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex631}
+\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
 % \documentclass[linenumbers]{aastex631}
@@
 This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to a unique evolutionary history.
-A popular \added{and well-studied} explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
+A popular and well-studied explanation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy.
 Thanks to recent advances in stellar age measurements, we can now compare this model to more direct measurements of the Galaxy's evolutionary timescales across the disk.
@@
 
-\lettrine{G}{alactic chemical evolution} (GCE) \added{studies aim} to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
+\lettrine{G}{alactic chemical evolution} (GCE) studies aim to explain the metal abundance patterns observed in the Milky Way (MW) by modeling the star formation history and evolution of the Galaxy.
 A long-standing paradigm of GCE is that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars \citep[e.g.,][]{tinsley_stellar_1979,matteucci_relative_1986}.
 In this view, one feature of the MW disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}.
-The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe \added{that are} associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, has approximately Solar \aFe, and is associated with the kinematic thin disk.
+The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr; e.g.,][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe that are associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, has approximately Solar \aFe, and is associated with the kinematic thin disk.
 The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.
-\added{An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and may not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}), suggesting that it could point to a unique evolutionary history for the MW.}
+An $\alpha$-bimodality is not a universal feature in simulated MW-mass galaxies \citep[e.g.,][]{mackereth_origin_2018,parul_effect_2025}, and may not exist in M31 (\citealt{nidever_prevalence_2024}; but see also \citealt{kobayashi_fe_2023}), suggesting that it could point to a unique evolutionary history for the MW.
 
-\added{The two-infall scenario} was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the \added{$\alpha$-bimodality in the MW.
-The basic premise is that the rate of gas accretion onto the disk occurs in two bursts}.
+The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the $\alpha$-bimodality in the MW.
+The basic premise is that the rate of gas accretion onto the disk occurs in two bursts.
 The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars.
 The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
-The initial model of \citet{chiappini_chemical_1997} successfully reproduced the \added{Solar neighborhood abundance data available at the time}.
+The initial model of \citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time.
 
-Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, \added{as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}}.
+Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
 Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
-\added{\citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.} \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the star formation history \added{inferred} from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
+\citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.
+\citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the star formation history inferred from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
 Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey \citep[SDSS;][]{sdss_collaboration_nineteenth_2025}.
 
-While previous studies have explored a large parameter space, most have assumed that the Galactic disk never \added{had} a substantial outflow.
-This decision is based on hydrodynamic simulations of Galactic fountains \added{produced} by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to \added{its} point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
+While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
+This decision is based on hydrodynamic simulations of Galactic fountains produced by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to its point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
 However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}; other simulations of MW-like galaxies with different prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
-Empirically, mass-loading \added{is} observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
-Even if the MW is not currently ejecting a substantial outflow, it may have \added{done so} in the past.
+Empirically, mass-loading is observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
+Even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.
 
@@
 \citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
-This degeneracy prohibits direct estimates of the \added{yields from GCE models} unless the effect of outflows is assumed to be insignificant.
-The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of \added{varying} the yield scale on two-infall scenario predictions.
-Varying the yield scale while maintaining an evolutionary end point \added{consistent} with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
+This degeneracy prohibits direct estimates of the yields from GCE models unless the effect of outflows is assumed to be insignificant.
+The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of varying the yield scale on two-infall scenario predictions.
+Varying the yield scale while maintaining an evolutionary end point consistent with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.
 
@@
 
-\added{The two-infall scenario reproduces} the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
+The two-infall scenario reproduces the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
 However, the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
 \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}.
-\added{A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
-In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).}
+A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
+In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).
 Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
-If the effect of radial migration is significant, then the \added{local $\alpha$-bimodality could} be explained without dramatic changes to the local gas abundance over time.
+If the effect of radial migration is significant, then the local $\alpha$-bimodality could be explained without dramatic changes to the local gas abundance over time.
 
-\added{As stellar age} estimation techniques have improved over recent years, large catalogs have become available with \added{age estimates} for stars across a wide swath of the Galaxy.
-In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs \added{suggest} that stellar metallicities are remarkably consistent with age across most of the \added{thin disk} \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
+As stellar age estimation techniques have improved over recent years, large catalogs have become available with age estimates for stars across a wide swath of the Galaxy.
+In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs suggest that stellar metallicities are remarkably consistent with age across most of the thin disk \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
 \citet{johnson_milky_2024} demonstrated that these results are readily explained by a scenario in which the Galaxy reaches a state of chemical equilibrium.
 In this so-called ``equilibrium scenario,'' the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over Gyr timescales.
-Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the \added{past $\sim8\Gyr$}.
+Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the past $\sim8\Gyr$.
 
-\added{The availability of} large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
+The availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
 Our study draws on the steadiness of the Milky Way stellar metallicity gradient found by \citet{johnson_milky_2024} and empirical constraints on the yield scale from \citet{weinberg_scale_2024}.
@@
         NN age error        & $\sigma_\tau/\tau < 40\%$     & Age uncertainty from \citet{leung_variational_2023} \\
-        \added{Uncertainty on [C/N]}    & $\sigma_{\rm [C/N]}\leq0.1$     & Precise [C/N] ages from \citet{roberts_cn_2025} \\
-        \added{${\rm [Fe/H]}$}      & $\mathFeH\geq-0.4$            & Accurate [C/N] ages for upper RGB \& RC stars \\
+        Uncertainty on [C/N]    & $\sigma_{\rm [C/N]}\leq0.1$     & Precise [C/N] ages from \citet{roberts_cn_2025} \\
+        ${\rm [Fe/H]}$     & $\mathFeH\geq-0.4$            & Accurate [C/N] ages for upper RGB \& RC stars \\
         \hline
@@
 APOGEE data were obtained from infrared spectrographs \citep{wilson_apache_2019} mounted on the 2.5-meter Sloan Foundation Telescope \citep{gunn_25_2006} at Apache Point Observatory and the Ir{\'e}n{\'e}e DuPont Telescope \citep{bowen_optical_1973} at Las Campanas Observatory.
-The data reduction pipeline is described by \citet{nidever_data_2015}, and \added{the} APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
+The data reduction pipeline is described by \citet{nidever_data_2015}, and the APOGEE Stellar Parameter and Chemical Abundance Pipeline (ASPCAP) is detailed by \citet{holtzman_abundances_2015}, \citet{garcia_perez_aspcap_2016}, and \citet{jonsson_apogee_2020}.
 
@@
 We supplement the APOGEE DR17 abundance data with two different age catalogs.
-The first is from \citet{leung_variational_2023}, who \added{trained} a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
-\added{Following} the recommendations of \citet{leung_variational_2023}, we cut all stars which have an age uncertainty greater than 40\%.
+The first is from \citet{leung_variational_2023}, who trained a variational encoder-decoder network on asteroseismic data for APOGEE red giants with $2.5<\log g<3.6$.
+Following the recommendations of \citet{leung_variational_2023}, we cut all stars which have an age uncertainty greater than 40\%.
 This produces a sample of \num{57607} stars with NN age estimates, of which \num{14871} are in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$).
@@
 
-Our second age catalog utilizes the [C/N]--age relation calibrated by \citet{roberts_cn_2025} for red giant branch (RGB) and red clump \added{(RC)} stars.
+Our second age catalog utilizes the [C/N]--age relation calibrated by \citet{roberts_cn_2025} for red giant branch (RGB) and red clump (RC) stars.
 The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry.
 This method has the benefit of providing age estimates for luminous giants ($\log g<2.5$), which increases the sample size at larger distances from the Sun.
-\added{Uncertainties in} the efficiency of FDU mixing and the RGB age--mass relationship mean \added{that} the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
-Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous \added{RGB and RC} stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
-\added{We use the sample selection criteria from \citet{roberts_cn_2025}, and following their recommendation}, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
+Uncertainties in the efficiency of FDU mixing and the RGB age--mass relationship mean that the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway.
+Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous RGB and RC stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem.
+We use the sample selection criteria from \citet{roberts_cn_2025}, and following their recommendation, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
 With this relationship, we estimate ages for \num{124778} stars across the disk, including \num{21956} in the Solar neighborhood.
@@
 The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}.
-We set up a disk \added{spanning} $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
+We set up a disk spanning $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$.
 We use a time-step of $\Delta t=10\,{\rm Myr}$, $n=8$ stellar populations per time-step per ring, and we run our models to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
@@
 
-We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, \added{and} the stellar migration prescription in Section \ref{sec:migration}.
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, and the stellar migration prescription in Section \ref{sec:migration}.
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
@@
 The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models.
-\added{\citet{weinberg_scale_2024} used} a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
+\citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
     In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$.
 We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
-}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a \added{quantity} of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass \added{fraction} in the Sun.
-However, \citet{johnson_milky_2024} found that their GCE models with \added{this yield} scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun.
+However, \citet{johnson_milky_2024} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed age--metallicity relation.
 Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
@@
 \end{equation}
-\added{for} each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
+for each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}.
 The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies.
@@
 Motivated by Equation \ref{eq:equilibrium}, we adopt a different outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
-\added{Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we adjust $\eta_\odot$ to ensure that $Z_{\rm O,eq}\approx Z_{\rm O,\odot}$.}
+Measurements of gas-phase \citep[e.g.,][]{mendez-delgado_gradients_2022} and stellar (Figure \ref{fig:yield-outflow}) abundances indicate that the Solar neighborhood ISM is presently close to Solar metallicity, so we adjust $\eta_\odot$ to ensure that $Z_{\rm O,eq}\approx Z_{\rm O,\odot}$.
 Table \ref{tab:models} reports the value of $\eta_\odot$ in each of our models.
 
-\added{\citet{johnson_milky_2024} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
-To} produce an exponentially declining radial \added{[O/H]} gradient, we adopt a prescription of
+\citet{johnson_milky_2024} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
+To produce an exponentially declining radial [O/H] gradient, we adopt a prescription of
 \begin{equation}
@@
 \end{equation}
-\added{for the outflow mass-loading factor,}
+for the outflow mass-loading factor,
 where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, \added{consistent} with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
-\added{We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study.
-We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.}
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, consistent with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
+We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study.
+We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
 
@@
 
-\added{We use a power-law star formation prescription of} $\dot\Sigma_\star\propto\Sigma_g^k$, with $k=1.5$ following \citet{kennicutt_global_1998}.
-Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single \added{power-law to allow} for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
+We use a power-law star formation prescription of $\dot\Sigma_\star\propto\Sigma_g^k$, with $k=1.5$ following \citet{kennicutt_global_1998}.
+Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a single power-law to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}.
 In detail, we calculate the star formation efficiency (SFE) timescale
@@
 \end{equation}
-\added{with} $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, \added{where $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ are observationally calibrated} \citep{leroy_star_2008}.
+with $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\kpc^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$, where $\gamma=1/2$, $t_0=13.8\,{\rm Gyr}$ and $\tau_{\rm mol,0}=2\,{\rm Gyr}$ are observationally calibrated \citep{leroy_star_2008}.
 Previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_galactic_2020,palla_chemical_2020} have adopted a higher SFE during the first infall epoch than the second, which we emulate through a pre-factor
@@
 However, the pre-factor has virtually no effect on the overall [O/Fe] distribution because the model is normalized to produce the same thick-to-thin-disk mass ratio regardless of the details of the star formation law.
-\added{We find} $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
-To guard against over-correcting the SFE in the early Galaxy, \added{we tested} eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial \added{differences}.
+We find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
+To guard against over-correcting the SFE in the early Galaxy, we tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial differences.
 
@@
 
-\added{The infall rate} is described by two successive, exponentially declining bursts in time.
-The first infall component \added{forms} the thick disk, and the second produces the thin disk.
-\added{The un-normalized} form of the infall rate is
+The infall rate is described by two successive, exponentially declining bursts in time.
+The first infall component forms the thick disk, and the second produces the thin disk.
+The un-normalized form of the infall rate is
 \begin{multline}
@@
 \end{equation*}
-where $\tau_1$ and \added{$\tau_2(R_{\rm gal})$} are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall, $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
-\added{We vary $\tau_2$ exponentially with $R_{\rm gal}$ and adopt a scale radius $R_{\tau_2}=7\kpc$ to match the stellar age gradients in MW-like spirals observed by \citet{sanchez_spatially_2020}.} We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar \added{disk has a} surface density ratio of the thick and thin disks \added{of}
+where $\tau_1$ and $\tau_2(R_{\rm gal})$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall, $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
+We vary $\tau_2$ exponentially with $R_{\rm gal}$ and adopt a scale radius $R_{\tau_2}=7\kpc$ to match the stellar age gradients in MW-like spirals observed by \citet{sanchez_spatially_2020}.
+We numerically calculate $f_{2/1}$ for each zone such that the resulting stellar disk has a surface density ratio of the thick and thin disks of
 \begin{equation}
@@
 % Infall rate parameter selection
-\added{Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
+Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
 After exploring the effect of the infall timescales in one-zone models, we adopt $\tau_1=1\Gyr$ and $\tau_2(R_\odot)=15\Gyr$, in line with the parameters adopted by \citet{spitoni_galactic_2020}, but longer than in \citet{nissen_high-precision_2020}, \citet{spitoni_apogee_2021}, and \citet{hegedus_reconstructing_2025}.
 We also adopt $t_{\rm max}=4.2\Gyr$ (i.e., a lookback time of $9\Gyr$) so that our models are compatible with the median stellar age of the thick disk of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
-\citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.}
+\citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.
 
@@
 In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
-The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a \added{present-day value} of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
+The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a present-day value of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
 
@@
 In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, \added{previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.} The circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
+However, previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
+The circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
 The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
@@
 In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at $\mathFeH_{\rm CGM}$.
-\added{We assume the Solar-scaled abundance} of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
+We assume the Solar-scaled abundance of the accreted gas is the same for all elements (i.e., $\mathXH_{\rm CGM}=\mathOH_{\rm CGM}$).
 
@@
 \citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
-\added{Our implementation,} based on the diffusion method of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
+Our implementation, based on the diffusion method of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
 \citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to that of \citet{frankel_measuring_2018} and found a similar effect on stellar abundance distributions.
@@
 \end{equation}
-\added{\citep{spitzer_dynamics_1942}} where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The scale height $h_z$ is given by
+\citep{spitzer_dynamics_1942} where $R_{\rm final}$ is the final Galactocentric radius of the stellar population. The scale height $h_z$ is given by
 \begin{equation}
@@
 \end{equation}
-\added{The} final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
+The final midplane distance is assigned at the end of the model run and therefore does not affect the chemical evolution.
 The parameters of Equations \ref{eq:radial-migration} and \ref{eq:scale-height} were chosen to fit the stellar migration patterns in the {\tt h277} hydrodynamical simulation \citep{christensen_implementing_2012}.
@@
 
-\added{An} important distinction between our method and that of \citet{spitoni_effect_2015} \added{is that} SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
+An important distinction between our method and that of \citet{spitoni_effect_2015} is that SNe Ia from long-lived progenitors contribute Fe to each zone they migrate through, not just their birth zone.
 This is important because the median delay time of our SN Ia DTD is $\sim2$ Gyr, for which the width of the migration distribution is $\sigma_{\rm RM}\approx2$ kpc (Equation \ref{eq:radial-migration}).
@@
     \includegraphics[width=\onecolumn]{\figpath{gas_abundance_evolution.pdf}}
-    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), \added{each of which feature a major dilution event 9 Gyr ago.
-The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances} in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
-\added{The black line (black points) plots the median (mode)} of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
+    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), each of which feature a major dilution event 9 Gyr ago.
+The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
+The black line (black points) plots the median (mode) of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
 The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
@@
 
-\added{Figure \ref{fig:yield-outflow}} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions \added{as a function of age at} the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
+Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions as a function of age at the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
 As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
-\added{We over-plot} the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ \added{for comparison}.
+We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ for comparison.
 The models are in broad agreement with each other and with the data at lookback times of $\lesssim5\Gyr$.
-At ages of $\sim5-8\Gyr$, the models \added{underpredict} the metallicities of the observed stars by up to half an order of \added{magnitude, a natural} consequence of the dilution associated with the second infall event.
-This discrepancy is \added{modestly reduced in} the higher $y/Z_\odot$ models, which re-enrich more rapidly.
-\added{However}, these models exacerbate tensions with the age--[O/Fe] relation because the O abundance \added{increases more} before enrichment from second-infall SNe Ia becomes important, making the $\alpha$-enhancement from the ensuing starburst more pronounced.
-\added{Overall,} none of our models provide a good match to these age trends.
+At ages of $\sim5-8\Gyr$, the models underpredict the metallicities of the observed stars by up to half an order of magnitude, a natural consequence of the dilution associated with the second infall event.
+This discrepancy is modestly reduced in the higher $y/Z_\odot$ models, which re-enrich more rapidly.
+However, these models exacerbate tensions with the age--[O/Fe] relation because the O abundance increases more before enrichment from second-infall SNe Ia becomes important, making the $\alpha$-enhancement from the ensuing starburst more pronounced.
+Overall, none of our models provide a good match to these age trends.
 Figure \ref{fig:yield-outflow} illustrates a point that will arise as a theme throughout the remainder of this paper, which is that the signatures of a substantial dilution event and subsequent re-enrichment, characteristic of the two-infall scenario, are simply not present in the observed age--abundance trends.
@@
 Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}< 9\kpc$, $|z| < 0.5\kpc$) color-coded by its birth radius.
-\added{In this and subsequent figures, a} Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
+In this and subsequent figures, a Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}.
 For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
 The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$, and the black squares plot the median stellar abundance in {2 Gyr}-wide age bins.
-\added{The red line and points are the median abundance for APOGEE stars, and the shaded regions are the 16th--84th percentile ranges.
-Each column} shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).}
+The red line and points are the median abundance for APOGEE stars, and the shaded regions are the 16th--84th percentile ranges.
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).}
     \label{fig:abundance-evolution-params}
@@
 Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
-The problem is exacerbated in the two-infall case because of the delayed dilution \added{event---the approach} to equilibrium is ``reset'' by the second infall.
+The problem is exacerbated in the two-infall case because of the delayed dilution event---the approach to equilibrium is ``reset'' by the second infall.
 The dilution of the ISM then gets baked into the stellar abundance record.
@@
 The evolution of [Fe/H] is similar, but the approach to the final metallicity is slower because of the additional delay imposed by SNe Ia.
-\added{We smoothed} simulated data points \added{based on} the median age and abundance errors in Table \ref{tab:uncertainties} \added{to incorporate these errors in the model}.
+We smoothed simulated data points based on the median age and abundance errors in Table \ref{tab:uncertainties} to incorporate these errors in the model.
 The black dashed curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
@@
 As a result, the stars that make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution at fixed age.
-Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, \added{for example}, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
+Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, for example, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
 
@@
 Column (c) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM because more of the gas disk is built up during the first infall phase.
-Model {\tt yZ1-diskratio} produces the best agreement \added{of the four models in Figure \ref{fig:abundance-evolution-params} to} the observed age--[Fe/H] relation (second row).
+Model {\tt yZ1-diskratio} produces the best agreement of the four models in Figure \ref{fig:abundance-evolution-params} to the observed age--[Fe/H] relation (second row).
 However, agreement with the observed age--[O/Fe] relation is poor.
@@
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
-\added{Pre-enriched infall} at this level mitigates but does not completely solve the two discrepancies.
+Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies.
 The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced, since the accreting gas is less chemically different from the ISM, diminishing the effects of dilution.
@@
     \includegraphics[width=\textwidth]{\figpath{mdf_evolution.pdf}}
-    \caption{\added{Decomposition of the present-day MDF by stellar age across the Galactic disk. 
+    \caption{Decomposition of the present-day MDF by stellar age across the Galactic disk. 
     The gray curve plots the total present-day MDF in each region.
 The distributions in all panels are restricted to $|z|<0.5\kpc$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity.
-Rows (a) and (b) present the distributions from the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models, respectively} (see Table \ref{tab:models}).
+Rows (a) and (b) present the distributions from the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models, respectively (see Table \ref{tab:models}).
 Row (c) presents the distributions from APOGEE with ages derived from [C/N] abundances by \citet{roberts_cn_2025} (see Section \ref{sec:age-estimates}).
-\added{In row (c), the vertical blue dotted lines mark the mode of the distribution of the $1-2\kpc$ age bin for reference, and the gray dashed line marks the cut at $\mathFeH\ge-0.4$ for upper RGB and RC stars.}}
+In row (c), the vertical blue dotted lines mark the mode of the distribution of the $1-2\kpc$ age bin for reference, and the gray dashed line marks the cut at $\mathFeH\ge-0.4$ for upper RGB and RC stars.}
     \label{fig:mdf-evolution}
@@
 The discrepancies between the predicted and observed abundance evolution in the Solar neighborhood discussed in Section \ref{sec:age-abundance} persist across the Galactic disk.
-Figure \ref{fig:mdf-evolution} \added{breaks down the MDF by stellar age} across five radial bins for the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models.
-For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in \added{Section \ref{sec:age-estimates}.}
+Figure \ref{fig:mdf-evolution} breaks down the MDF by stellar age across five radial bins for the {\tt yZ1-fiducial} and {\tt yZ2-fiducial} models.
+For the APOGEE sample, we use the [C/N]-derived age estimates due to the larger sample size in the most distant regions of the disk; we limit the comparison to ages in the range $1-10$ Gyr because the [C/N] ages are most reliable in this range, as discussed in Section \ref{sec:age-estimates}.
 
@@
 The distance between the $1-2\Gyr$ and $2-4\Gyr$ age bins is smaller for the \yZ{2} model because of the faster approach to equilibrium (see also Figure \ref{fig:yield-outflow}).
-In the Solar annulus (center column), the peak of \added{the MDF of $6-8\Gyr$ old stars} is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
+In the Solar annulus (center column), the peak of the MDF of $6-8\Gyr$ old stars is $0.3\dex$ lower in the \yZ{2} model than observed, and $0.4\dex$ lower in the \yZ{1} model.
 
@@
 In the models, the main, metal-poor peak consists of $8-9\Gyr$ old stars (post-dilution), and the extended high-[Fe/H] tail consists of $>9\Gyr$ old stars (pre-dilution).
-Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in \added{the two inner-most radial bins}, peaking at $\mathFeH\approx-0.3$ and $+0.3$.
-\added{While} the data and the models show qualitatively similar behavior, they actually represent different populations.
+Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in the two inner-most radial bins, peaking at $\mathFeH\approx-0.3$ and $+0.3$.
+While the data and the models show qualitatively similar behavior, they actually represent different populations.
 In the data, the metal-rich peak are all low-$\alpha$ stars, while the metal-poor peak is the locus of the high-$\alpha$ sequence---a reversal of the model predictions.
@@
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution.
-    \added{Stars} in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$.}
+    Stars in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$.}
     \label{fig:ofe-feh-density}
@@
 
-In the two-infall scenario, the low-$\alpha$ loop governs the chemical evolution of the thin disk \added{\citep[see Section 6 of][]{spitoni_galactic_2019}}.
-However, careful inspection of the marginal [O/Fe] distributions in \added{Figure \ref{fig:yield-outflow}} reveals a different morphology: the models predict {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
+In the two-infall scenario, the low-$\alpha$ loop governs the chemical evolution of the thin disk \citep[see Section 6 of][]{spitoni_galactic_2019}.
+However, careful inspection of the marginal [O/Fe] distributions in Figure \ref{fig:yield-outflow} reveals a different morphology: the models predict {\it three} peaks in the [O/Fe] distribution, whereas the data show only two.
 The location of the intermediate peak varies depending on the yields and model parameters, but is always present.
@@
 We have not accounted for the APOGEE selection function in our models, but there is no evident reason for observational effects to produce this difference in morphology.
-This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and \added{is typical of other models} \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
+This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and is typical of other models \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
 The two-infall scenario is otherwise fairly successful at reproducing the local stellar distribution in [O/Fe]--[Fe/H] space.
@@
 Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn.
-\added{For visual clarity}, each distribution is smoothed with a box-car of width 0.05 dex.
+For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
     Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, {\tt yZ2-fiducial}; {\bf (b)} a model with a power-law DTD, {\tt yZ2-powerlaw}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\tt yZ2-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ2-preenrich} (see Table \ref{tab:models} for details).}
@@
 Each panel presents a random mass-weighted sample of \num{10000} stellar populations color-coded by age.
-\added{The solid (dashed) contours enclose 30\% (80\%) of the APOGEE stars in each region.}}
+The solid (dashed) contours enclose 30\% (80\%) of the APOGEE stars in each region.}
     \label{fig:ofe-feh-best}
@@
 Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
-Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate \added{than the illustrative examples in the previous section.
-Our} focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters.
+Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate than the illustrative examples in the previous section.
+Our focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters.
 
@@
 These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but they occupy a unique portion of the abundance space.
-\added{Second}, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
+Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
 The following section explores this second prediction in greater detail.
@@
     \caption{{\it Top:} The median stellar age as a function of [O/Fe] and [Fe/H] in the Solar annulus ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<2\kpc$).
-The left and center panels \added{show} the {\tt yZ1-best} and {\tt yZ2-best} models, with ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$ (see Table \ref{tab:models}).
+The left and center panels show the {\tt yZ1-best} and {\tt yZ2-best} models, with ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\sigma_{\rm RM8}=3.6\kpc$ (see Table \ref{tab:models}).
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution, and a Gaussian scatter has been applied to the abundances and ages according to Table \ref{tab:uncertainties}.
 The right panel plots the results from APOGEE using the \citet{leung_variational_2023} NN age catalog.
-The contours \added{show} the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
+The contours show the density of stars in the [Fe/H]--[O/Fe] plane, and the vertical dashed line denotes the boundary for locally metal-rich (LMR) stars.
     {\it Bottom}: Stellar age distributions in the Solar annulus for all stars (black) and LMR stars (gray).
-The left and center panels plot the mass-weighted age distributions predicted by the models, \added{and the right panel plots the NN ages for APOGEE stars.}}
+The left and center panels plot the mass-weighted age distributions predicted by the models, and the right panel plots the NN ages for APOGEE stars.}
     \label{fig:lmr-ages}
@@
 The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
-It is difficult to \added{obtain} a unimodal age distribution with the available parameter space.
+It is difficult to obtain a unimodal age distribution with the available parameter space.
 A dearth of intermediate-age, high-metallicity stars is a natural outcome of a substantial dilution event, which is a defining feature of the two-infall scenario.
@@
 Similarly, \citet{palla_chemical_2020,palla_mapping_2024} used an inward flow with a speed of $\sim1\kms$ to reproduce the observed radial metallicity profile in the absence of Galactic outflows.
-\added{\citet{johnson_constraints_2025}} considered several possible scenarios for the processes that drive radial gas flows.
-Their findings support these previous arguments that radial gas flows \added{can help to regulate the overall metal abundance and radial gradient.}
+\citet{johnson_constraints_2025} considered several possible scenarios for the processes that drive radial gas flows.
+Their findings support these previous arguments that radial gas flows can help to regulate the overall metal abundance and radial gradient.
 
 In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2024} demonstrated can improve agreement with age trends across the Galactic disk.
-\added{The outflow is simpler in implementation than a radial gas flow}; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
+The outflow is simpler in implementation than a radial gas flow; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
 This approach allows us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
-\added{We have therefore focused on models with outflows in this paper for the sake of simplicity, but constant} radial gas flow models should have similar effects.
+We have therefore focused on models with outflows in this paper for the sake of simplicity, but constant radial gas flow models should have similar effects.
 
@@
 The blue dashed curve represents the fiducial model that has an exponentially declining infall rate with timescale $\tau_{\rm in}=15\Gyr$, and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
-The red solid curve plots the output of a model which \added{has an enhancement of $\tau_\star$ by a factor of 10 for 200 Myr} starting at $t=1.4\,{\rm Gyr}$.
+The red solid curve plots the output of a model which has an enhancement of $\tau_\star$ by a factor of 10 for 200 Myr starting at $t=1.4\,{\rm Gyr}$.
 Both models assume the \yZ{2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
-The grayscale histogram \added{is} the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}< 9\kpc$, $|z|<2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
+The grayscale histogram is the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}< 9\kpc$, $|z|<2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
     \label{fig:onezone-sfe-hiatus}
@@
 
-The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation \added{temporarily}.
-For the two-infall model, this phase of low star formation lasts for a few Gyr \added{between} the $e$-folding timescale of the first infall and the onset of the second.
+The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation temporarily.
+For the two-infall model, this phase of low star formation lasts for a few Gyr between the $e$-folding timescale of the first infall and the onset of the second.
 However, as we have shown in Section \ref{sec:age-abundance}, the resulting dilution of the ISM is in tension with the observed stellar age--metallicity relation.
@@
 The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
-As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk \added{measured by} \citet{pinsonneault_apokasc-3_2025}.
+As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk measured by\citet{pinsonneault_apokasc-3_2025}.
 This hiatus model illustrates an alternative scenario for reproducing the $\alpha$-bimodality, but a full multi-zone treatment is beyond the scope of this work.
@@
 We explored multiple parameter modifications to bring the model predictions closer to the data, including the yield scale, radial migration strength, metallicity of the accreted gas, thick-to-thin disk mass ratio, and the SN Ia DTD.
-We found that our two-infall models faced the following \added{challenges}:
+We found that our two-infall models faced the following challenges:
 
 \begin{itemize}
-    \item By the model's design, the Galaxy undergoes a period of \added{rapid} dilution and subsequent re-enrichment.
+    \item By the model's design, the Galaxy undergoes a period of rapid dilution and subsequent re-enrichment.
 Models at a lower yield scale and weaker outflows predict slower re-enrichment.
 By contrast, the observed stellar age--metallicity relation is roughly constant over the past $\sim10\Gyr$.
-Pre-enriching the accreted gas can reduce the magnitude of the dilution, but \added{cannot} eliminate it entirely.
+Pre-enriching the accreted gas can reduce the magnitude of the dilution, but cannot eliminate it entirely.
     \item Due to this re-enrichment, our models predict that the MDF shifts to higher metallicity with decreasing age throughout the disk.
@@
 
-\added{We} have not found a GCE model, two-infall or otherwise, that is capable of reproducing all of the \added{observations}.
+We have not found a GCE model, two-infall or otherwise, that is capable of reproducing all of the observations.
 The ``inside-out'' models of \citet{johnson_stellar_2021} are better able to predict a slowly evolving metallicity gradient, but they do not predict an $\alpha$-bimodality.
@@
 
-We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper, \added{and to Prof.\ Christopher Kochanek for his useful comments on the manuscript}.
+We are grateful to Prof.\ David Weinberg for his thoughtful comments and input on this paper, and to Prof.\ Christopher Kochanek for his useful comments on the manuscript.
 We also thank Dr.\ Emanuele Spitoni for useful conversations about this work.

### 2025-12-02 src/scripts/multizone/__main__.py
allow for command line specification of evolutionary parameters

@@ -87,6 +87,12 @@ def parse():
         choices = _EVOLUTION_MODELS_,
         default = "twoinfall_expvar"
     )
+    parser.add_argument("--evol-params",
+        help = "Keyword arguments for SFH evolution model, separated by commas\
+ (Default: '')",
+        type = str,
+        default = ""
+    )
     parser.add_argument("--RIa",
         help = "The SN Ia delay-time distribution to assume (Default: plateau)",
         type = str,
@@ -95,7 +101,7 @@ def parse():
     )
     parser.add_argument("--RIa-params",
         help = "Parameters for the SN Ia delay-time distribution separated by \
-underscores. (Default: '')",
+commas. (Default: '')",
         type = str,
         default = ""
     )
@@ -197,12 +203,9 @@ def model(args):
     with open(str(fullpath) + "_args.txt", "w") as f:
         f.write(args.name + "\n")
         f.writelines(["%s: %s\n" % (k, v) for k, v in vars(args).items() if k != "name"])
-    # Parse RIa params into dict
-    RIa_kwargs = {}
-    if '=' in args.RIa_params:
-        for p in args.RIa_params.split("_"):
-            key, value = p.split("=")
-            RIa_kwargs[key] = float(value)
+    # Parse kwarg strings into dicts
+    RIa_kwargs = parse_kwargs(args.RIa_params)
+    evol_kwargs = parse_kwargs(args.evol_params)
     config = src.config(
         timestep_size = args.dt,
         star_particle_density = args.nstars,
@@ -212,6 +215,7 @@ def model(args):
     kwargs = dict(
         name = str(fullpath),
         spec = args.evolution,
+        evol_kwargs = evol_kwargs,
         RIa = args.RIa,
         RIa_kwargs = RIa_kwargs,
         delay = args.minimum_delay,
@@ -244,6 +248,34 @@ def main():
     model_.run([_ * model_.dt for _ in range(round(
         _globals.END_TIME / model_.dt) + 1)],
         overwrite = args.force, pickle = args.pickle)
+    
+
+def parse_kwargs(kwarg_string):
+    """
+    Convert a string of keyword arguments separated by commas into a dict.
+
+    Parameters
+    ----------
+    kwarg_string : str
+        String of keyword arguments in the format:
+        'key1=value1,key2=value2,...,keyN=valueN'
+    
+    Returns
+    -------
+    dict
+
+    Raises
+    ------
[…]

### 2025-12-02 src/scripts/multizone/src/disks.py

@@ -21,7 +21,6 @@ from . import dtds
 from . import outflows
 from .models.utils import get_bin_number, interpolate, modified_exponential
 from .models.diskmodel import two_component_disk, BHG16
-from .models.twoinfall import SECOND_ONSET
 import math as m
 
 _SECONDS_PER_GYR_ = 3.1536e16
@@ -56,6 +55,8 @@ class diskmodel(vice.milkyway):
         - "static_infall"
         - "oneinfall"
     
+    evol_kwargs : ``dict'' [default: {}]
+        Keyword arguments to pass to the star formation history initialization.
     verbose : ``bool`` [default : True]
         Whether or not the run the models with verbose output.
     migration_mode : ``str`` [default : "diffusion"]
@@ -114,13 +115,30 @@ class diskmodel(vice.milkyway):
     Attributes and functionality are inherited from ``vice.milkyway``.
     """
 
-    def __init__(self, zone_width = 0.1, name = "diskmodel", spec = "twoinfall",
-                 verbose = True, migration_mode = "gaussian", yields="yZ1",
-                 delay = 0.04, RIa = "plateau", RIa_kwargs={}, seed=42, 
-                 radial_gas_velocity = 0., has_outflows=True, eta_solar=None,
-                 migration_time_dep=0.33, migration_radius_dep=0.61,
-                 migration_strength=2.68, pre_enrichment=float("-inf"), 
-                 pre_alpha_enhancement=0., local_disk_ratio=0.12, **kwargs):
+    def __init__(
+            self, 
+            zone_width = 0.1, 
+            name = "diskmodel", 
+            spec = "twoinfall",
+            evol_kwargs = {},
+            verbose = True, 
+            migration_mode = "gaussian", 
+            yields="yZ1",
+            delay = 0.04, 
+            RIa = "plateau", 
+            RIa_kwargs={}, 
+            seed=42, 
+            radial_gas_velocity = 0., 
+            has_outflows=True, 
+            eta_solar=None,
+            migration_time_dep=0.33, 
+            migration_radius_dep=0.61,
+            migration_strength=2.68, 
+            pre_enrichment=float("-inf"), 
+            pre_alpha_enhancement=0., 
+            local_disk_ratio=0.12, 
+            **kwargs
+        ):
         # Set the yields
         if yields == "JW20":
             from vice.yields.presets import JW20
@@ -188,7 +206,6 @@ class diskmodel(vice.milkyway):
             local_ratio = local_disk_ratio
         )
[…]

### 2025-12-02 src/scripts/ofe_distributions.py
add yZ2 model with tmax=3 Gyr

@@ -14,7 +14,7 @@ import paths
 from _globals import TWO_COLUMN_WIDTH, GALR_BINS, ABSZ_BINS
 
 OUTPUT_NAMES = [
-    'yZ2-fiducial/diskmodel',
+    'yZ2-earlyonset/diskmodel',
     'yZ2-powerlaw/diskmodel',
     'yZ2-diskratio/diskmodel',
     'yZ2-preenrich/diskmodel',

### 2025-12-02 src/scripts/ofe_feh_density.py

@@ -19,7 +19,7 @@ from utils import get_bin_centers
 
 OUTPUT_NAMES = [
     'yZ1-fiducial/diskmodel',
-    'yZ2-fiducial/diskmodel'
+    'yZ2-earlyonset/diskmodel'
 ]
 LABELS = [
     r'(a) $y/Z_\odot=1$',

### 2025-12-02 src/scripts/run_all_models.sh

@@ -33,24 +33,29 @@ echo $NAME
 python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION
 echo ""
 
+NAME="yZ2-earlyonset/diskmodel"
+echo $NAME
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --evol-params="onset=3"
+echo ""
+
 NAME="yZ2-powerlaw/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --RIa=powerlaw
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --RIa=powerlaw --evol-params="onset=3"
 echo ""
 
 NAME="yZ2-diskratio/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --local-disk-ratio=0.5
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --local-disk-ratio=0.5 --evol-params="onset=3"
 echo ""
 
 NAME="yZ2-preenrich/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --pre-enrichment=-0.5 --eta=2.4
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --pre-enrichment=-0.5 --eta=2.4 --evol-params="onset=3"
 echo ""
 
 NAME="yZ2-best/diskmodel"
 echo $NAME
-python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --pre-enrichment=-0.7 --local-disk-ratio=0.25 --eta-solar=1.8 --migration-strength=3.6
+python -m multizone -f --nstars=$NSTARS --name=$NAME --yields=yZ2 --evolution=$EVOLUTION --pre-enrichment=-0.7 --local-disk-ratio=0.25 --eta-solar=1.8 --migration-strength=3.6 --evol-params="onset=3"
 echo ""
 
 NAME="yZ2-insideout/diskmodel"

### 2025-12-02 src/scripts/smooth_vs_twoinfall.py

@@ -58,7 +58,7 @@ def main(style='paper'):
                     label=r'%s kpc' % radius)
 
     # Plot twoinfall predictions
-    output_name = 'yZ2-fiducial/diskmodel'
+    output_name = 'yZ2-earlyonset/diskmodel'
     radius = 8
     zone = int(radius / ZONE_WIDTH)
     multioutput = vice.output(str(paths.multizone / output_name))

### 2025-12-02 src/tex/ms.tex

@@
 % Define document class
-\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
-% \documentclass[linenumbers]{aastex631}
+\documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex631}
 
@@
 The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars.
-The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
-The initial model of \citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time.
-
-Subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
+% The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
+% The initial model of 
+\citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time, and
+subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
 Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
-\citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.
 \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the star formation history inferred from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
@@
 Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the past $\sim8\Gyr$.
+
+\todo{Integrate into previous para:} \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.
+\todo{Also: multiple sequences in Anders et al. (2023), Xiang \& Rix (2022), Sahlholdt et al. (2022).}
 
@@
 We use a time-step of $\Delta t=10\,{\rm Myr}$, $n=8$ stellar populations per time-step per ring, and we run our models to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.
-Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling.
+\added{We adopt a \citet{kroupa_variation_2001} initial mass function (IMF).} Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling.
 Stellar populations migrate between zones, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones, which couples the enrichment in nearby rings.
@@
 \end{equation}
-where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the $e$-folding timescale of the star formation history, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
+where $r=0.4$ is the instantaneous recycling parameter \added{for a \citet{kroupa_variation_2001} IMF}, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the $e$-folding timescale of the star formation history, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor.
 Motivated by Equation \ref{eq:equilibrium}, we adopt a different outflow mass-loading factor at the Solar radius $\eta_\odot\equiv\eta(R=R_\odot)$ for each of the yield sets in Table \ref{tab:yields}.
@@
 Figure \ref{fig:yield-outflow} illustrates a point that will arise as a theme throughout the remainder of this paper, which is that the signatures of a substantial dilution event and subsequent re-enrichment, characteristic of the two-infall scenario, are simply not present in the observed age--abundance trends.
+
+\todo{Contrast with: multiple sequences in Anders et al. (2023), Xiang \& Rix (2022), Sahlholdt et al. (2022).}
 

### 2025-12-02 src/tex/ms.tex

@@
 
-While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
+% While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
 This decision is based on hydrodynamic simulations of Galactic fountains produced by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to its point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
@@
 
-By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}.
-\citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
+\added{While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
+The presence of mass-loaded outflows in MW-like galaxies is heavily debated \citep[see discussion in][]{johnson_milky_2025}, but even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.}
+By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,weinberg_equilibrium_2017,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}.
+% \citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
 This degeneracy prohibits direct estimates of the yields from GCE models unless the effect of outflows is assumed to be insignificant.
@@
 In a challenge to the traditional view of GCE, which expects the ISM metallicity to continually increase over time, these catalogs suggest that stellar metallicities are remarkably consistent with age across most of the thin disk \citep[e.g.,][]{spina_mapping_2022,magrini_gaia-eso_2023,willett_evolution_2023,carbajo-hijarrubia_occaso_2024,gallart_chronology_2024}.
-\citet{johnson_milky_2024} demonstrated that these results are readily explained by a scenario in which the Galaxy reaches a state of chemical equilibrium.
+\citet{johnson_milky_2025} demonstrated that these results are readily explained by a scenario in which the Galaxy reaches a state of chemical equilibrium.
 In this so-called ``equilibrium scenario,'' the local metallicity is driven by the ratio of star formation to accretion at a given radius, which evolves to a constant over Gyr timescales.
-Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2024} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the past $\sim8\Gyr$.
+Whether the equilibrium metallicity is regulated by outflows, as in the  \citet{johnson_milky_2025} models, or by other factors such as a radial gas flow \citep{spitoni_effects_2011,bilitewski_radial_2012,sharda_interplay_2024}, the current data suggest that metal abundances in the ISM evolved minimally during the past $\sim8\Gyr$.
 
@@
 The availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
-Our study draws on the steadiness of the Milky Way stellar metallicity gradient found by \citet{johnson_milky_2024} and empirical constraints on the yield scale from \citet{weinberg_scale_2024}.
+Our study draws on the steadiness of the Milky Way stellar metallicity gradient found by \citet{johnson_milky_2025} and empirical constraints on the yield scale from \citet{weinberg_scale_2024}.
 We run multi-zone GCE models with a two-infall accretion history, radially-dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation.
@@
 }\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun.
-However, \citet{johnson_milky_2024} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+However, \citet{johnson_milky_2025} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed age--metallicity relation.
 Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
@@
 
-\citet{johnson_milky_2024} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
+\citet{johnson_milky_2025} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
 To produce an exponentially declining radial [O/H] gradient, we adopt a prescription of
@@
 where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
-We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, consistent with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2024}.
+We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2025}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, consistent with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2025}.
 We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study.
@@
 In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2024,spitoni_remind_2024}.
+However, previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2025,spitoni_remind_2024}.
 The circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
@@
 
-\begin{deluxetable*}{lCCcDDD}
+\begin{deluxetable*}{lCCCcDDD}
     \tablecaption{Summary of our multi-zone models and relevant parameters.\label{tab:models}}
     \tablehead{
-        \colhead{Name} & \colhead{$y/Z_\odot$} & \colhead{$\eta_\odot$} & \colhead{SN Ia DTD} & \multicolumn2c{$\sigma_{\rm RM8}$ [kpc]} & \multicolumn2c{$f_\Sigma(R_\odot)$} & \multicolumn2c{${\rm [X/H]}_{\rm CGM}$}
+        \colhead{Name} & \colhead{$y/Z_\odot$} & \colhead{$\eta_\odot$} & \colhead{$t_{\rm max}$ [Gyr]} & \colhead{SN Ia DTD} & \multicolumn2c{$\sigma_{\rm RM8}$ [kpc]} & \multicolumn2c{$f_\Sigma(R_\odot)$} & \multicolumn2c{${\rm [X/H]}_{\rm CGM}$}
     }
@@
     \startdata
-        {\tt yZ1-fiducial}  & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
-        {\tt yZ1-migration} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 5.0   & 0.12  & $-\infty$   \\
-        {\tt yZ1-diskratio} & 1 & 0.2   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
-        {\tt yZ1-preenrich} & 1 & 0.6   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
-        {\tt yZ1-best}      & 1 & 0.4   & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
+        {\tt yZ1-fiducial}  & 1 & 0.2   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ1-migration} & 1 & 0.2   & 4.0 & Equation \ref{eq:plateau-dtd}  & 5.0   & 0.12  & $-\infty$   \\
+        {\tt yZ1-diskratio} & 1 & 0.2   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
+        {\tt yZ1-preenrich} & 1 & 0.6   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
+        {\tt yZ1-best}      & 1 & 0.4   & 4.0 & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
         \hline
-        {\tt yZ2-fiducial}  & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
-        {\tt yZ2-powerlaw}  & 2 & 1.4   & Equation \ref{eq:powerlaw-dtd} & 2.68  & 0.12  & $-\infty$   \\
-        {\tt yZ2-diskratio} & 2 & 1.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
-        {\tt yZ2-preenrich} & 2 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
-        {\tt yZ2-best}      & 2 & 1.8   & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
+        {\tt yZ2-fiducial}  & 2 & 1.4   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-earlyonset}& 2 & 1.4   & 3.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-powerlaw}  & 2 & 1.4   & 3.0 & Equation \ref{eq:powerlaw-dtd} & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-diskratio} & 2 & 1.4   & 3.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
+        {\tt yZ2-preenrich} & 2 & 2.4   & 3.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
+        {\tt yZ2-best}      & 2 & 1.8   & 3.0 & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
         \hline
-        {\tt yZ3-fiducial}  & 3 & 2.4   & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ3-fiducial}  & 3 & 2.4   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
     \enddata
@@
 Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions as a function of age at the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
-As shown by \citet{johnson_milky_2024}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
+As shown by \citet{johnson_milky_2025}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
 We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ for comparison.
@@
 
-Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation even with a smooth SFH \citep[see also][]{johnson_milky_2024}.
+Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation even with a smooth SFH \citep[see also][]{johnson_milky_2025}.
 The problem is exacerbated in the two-infall case because of the delayed dilution event---the approach to equilibrium is ``reset'' by the second infall.
@@
 It is difficult to draw conclusions about the outer Galaxy because the mode [Fe/H] is close to the metallicity cut at $\mathFeH>-0.4$ for luminous giants (represented by the vertical gray dashed line), which comprise the majority of stars in the sample at that distance.
-The remarkable consistency of the MDF over time, the result that motivated the equilibrium scenario proposed by \citet{johnson_milky_2024}, contrasts with the predictions of our fiducial models.
+The remarkable consistency of the MDF over time, the result that motivated the equilibrium scenario proposed by \citet{johnson_milky_2025}, contrasts with the predictions of our fiducial models.
 
@@
 
-In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2024} demonstrated can improve agreement with age trends across the Galactic disk.
+In our models, the outflows regulate the overall metallicity in a radially dependent manner, which \citet{johnson_milky_2025} demonstrated can improve agreement with age trends across the Galactic disk.
 The outflow is simpler in implementation than a radial gas flow; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
@@
 The ``inside-out'' models of \citet{johnson_stellar_2021} are better able to predict a slowly evolving metallicity gradient, but they do not predict an $\alpha$-bimodality.
-Even a smoothly-evolving SFH struggles to reproduce the flat age--metallicity relation at the lower empirical yield scale \citep{johnson_milky_2024}.
+Even a smoothly-evolving SFH struggles to reproduce the flat age--metallicity relation at the lower empirical yield scale \citep{johnson_milky_2025}.
 We emphasize, though, that by its very construction, the two-infall scenario trades success at reproducing certain observations for failure at others.
@@
 The apparent age-independence of stellar abundances in the disk places considerable restrictions upon the two-infall parameter space because it predicts a substantial dilution event at the start of the thin disk epoch.
-If the equilibrium scenario of \citet{johnson_milky_2024} is accurate, then it restricts the two-infall scenario more than other GCE models.
+If the equilibrium scenario of \citet{johnson_milky_2025} is accurate, then it restricts the two-infall scenario more than other GCE models.
 Restrictions on the two-infall scenario also translate more broadly to other merger-dominated SFHs, which must explain the MW's $\alpha$-bimodality without significantly diluting the metallicity of the ISM.

### 2025-12-03 src/tex/ms.tex
Updates from Overleaf

@@
 We also adopt $t_{\rm max}=4.2\Gyr$ (i.e., a lookback time of $9\Gyr$) so that our models are compatible with the median stellar age of the thick disk of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
-\citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.
+\added{This value of $t_{\rm max}$ is sub-optimal for models with \yZ{2}, producing a poorer agreement with the APOGEE data in [O/Fe]--[Fe/H] space, so we also run models with $t_{\rm max}=3.2\Gyr$ (see Table \ref{tab:models}.) This change has only a small effect on the [Fe/H] and [O/Fe] abundance distributions.} \citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.
 
@@
     \startdata
-        {\tt yZ1-fiducial}  & 1 & 0.2   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
-        {\tt yZ1-migration} & 1 & 0.2   & 4.0 & Equation \ref{eq:plateau-dtd}  & 5.0   & 0.12  & $-\infty$   \\
-        {\tt yZ1-diskratio} & 1 & 0.2   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
-        {\tt yZ1-preenrich} & 1 & 0.6   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
-        {\tt yZ1-best}      & 1 & 0.4   & 4.0 & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
+        {\tt yZ1-fiducial}  & 1 & 0.2   & 4.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ1-migration} & 1 & 0.2   & 4.2 & Equation \ref{eq:plateau-dtd}  & 5.0   & 0.12  & $-\infty$   \\
+        {\tt yZ1-diskratio} & 1 & 0.2   & 4.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
+        {\tt yZ1-preenrich} & 1 & 0.6   & 4.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
+        {\tt yZ1-best}      & 1 & 0.4   & 4.2 & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
         \hline
-        {\tt yZ2-fiducial}  & 2 & 1.4   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
-        {\tt yZ2-earlyonset}& 2 & 1.4   & 3.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
-        {\tt yZ2-powerlaw}  & 2 & 1.4   & 3.0 & Equation \ref{eq:powerlaw-dtd} & 2.68  & 0.12  & $-\infty$   \\
-        {\tt yZ2-diskratio} & 2 & 1.4   & 3.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
-        {\tt yZ2-preenrich} & 2 & 2.4   & 3.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
-        {\tt yZ2-best}      & 2 & 1.8   & 3.0 & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
+        {\tt yZ2-fiducial}  & 2 & 1.4   & 4.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-earlyonset}& 2 & 1.4   & 3.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-powerlaw}  & 2 & 1.4   & 4.2 & Equation \ref{eq:powerlaw-dtd} & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ2-diskratio} & 2 & 1.4   & 4.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.5   & $-\infty$   \\
+        {\tt yZ2-preenrich} & 2 & 2.4   & 4.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & -0.5      \\
+        {\tt yZ2-best}      & 2 & 1.8   & 3.2 & Equation \ref{eq:plateau-dtd}  & 3.6   & 0.25  & -0.7      \\
         \hline
-        {\tt yZ3-fiducial}  & 3 & 2.4   & 4.0 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
+        {\tt yZ3-fiducial}  & 3 & 2.4   & 4.2 & Equation \ref{eq:plateau-dtd}  & 2.68  & 0.12  & $-\infty$   \\
     \enddata
@@
     \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), each of which feature a major dilution event 9 Gyr ago.
-The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
+    % The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
 The black line (black points) plots the median (mode) of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
-The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
+    \added{The 2-D histograms show the APOGEE stellar age--abundance distributions in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$), adopting the \citet{leung_variational_2023} ages.
+The black points plot the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
+    The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions \added{in the same region}, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
     \label{fig:yield-outflow}

### 2025-12-03 src/tex/ms.tex
Updates from Overleaf

@@
     \added{The 2-D histograms show the APOGEE stellar age--abundance distributions in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$), adopting the \citet{leung_variational_2023} ages.
-The black points plot the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
+The black curve (points) plots the rolling median (binned mode) of the abundance data as a function of age, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
     The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions \added{in the same region}, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
@@
 
-Figure \ref{fig:yield-outflow} shows the mode of the APOGEE [O/H], [Fe/H], and [O/Fe] distributions as a function of age at the Solar annulus, using the NN ages from \citet{leung_variational_2023}.
+Figure \ref{fig:yield-outflow} shows the \added{APOGEE age--abundance distributions at the Solar annulus, as well as the binned mode abundance and rolling median as a function of age}, using the NN ages from \citet{leung_variational_2023}.
 As shown by \citet{johnson_milky_2025}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
+\added{While the age--metallicity distribution is clumpy in places (see Section \ref{sec:amr}), we observe that ${\rm mode}(\mathOH)\gtrsim0$ for the past 10 Gyr.}
+
 We over-plot the ISM abundance evolution in our $y/Z_\odot=1,2,$ and $3$ models with the fiducial parameters at $R_{\rm gal}=8\kpc$ for comparison.
@@
 Figure \ref{fig:yield-outflow} illustrates a point that will arise as a theme throughout the remainder of this paper, which is that the signatures of a substantial dilution event and subsequent re-enrichment, characteristic of the two-infall scenario, are simply not present in the observed age--abundance trends.
-
-\todo{Contrast with: multiple sequences in Anders et al. (2023), Xiang \& Rix (2022), Sahlholdt et al. (2022).}
 
@@
 
+\subsection{The Age--Metallicity Relation}
+\label{sec:amr}
+
+\added{A few recent studies have reported the discovery of multiple disconnected sequences in the local age--metallicity relation \citep[e.g.,][]{sahlholdt_characterizing_2022,xiang_time-resolved_2022,anders_spectroscopic_2023}.
+\citet{nissen_high-precision_2020} argued that these sequences provide evidence for the two-infall scenario, although \citet{plotnikova_chemical_2024} showed that multiple sequences can arise due to selection effects, and \citet{chen_recent_2025} showed that radial migration can also lead to such patterns.
+There are hints of multiple sequences in Figure \ref{fig:yield-outflow}, where a break in the distribution at ages of $\sim5\Gyr$ coincides with a $\sim0.2\dex$ drop in [O/H] and [Fe/H].
+The sequences are less pronounced in the \citet{leung_variational_2023} catalog than reported by \citet{anders_spectroscopic_2023}, likely related to a systematic offset between the two catalogs around the same age \citep[see Figure 6 of][]{anders_spectroscopic_2023}.
+On the other hand, the [C/N] age-metallicity relation of \citet{roberts_cn_2025} is even flatter and does not appear to have multiple sequences.
+Even if these sequences are real, we find it difficult to explain them using the two-infall scenario\textemdash the observed dilution is much smaller than predicted by any of our models, and the timing of the split between the sequences is too late for the birth of the thin disk, although it is interestingly close to the first pericentric passage of the Sagittarius dwarf galaxy \citep{ruiz-lara_recurrent_2020}.}
+\todo{Mention APOGEE selection function?}
+% Anders+ use APOGEE clump stars. Their split is 5-6 Gyr ago
+% Xiang & Rix use Gaia subgiants. Their split is 8 Gyr ago
+% Sahlholdt+ use GALAH turnoff stars. Their split is 7-9 Gyr ago.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{\figpath{compare_age_catalogs.pdf}}
+    \caption{Comparison between NN- and [C/N]-derived ages for our sample.}
+    \label{fig:compare-age-catalogs}
+\end{figure*}
+
 \subsection{Third Accretion Episode}

### 2025-12-08 src/tex/ms.tex
Updates from Overleaf

@@
 The two-infall scenario reproduces the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track. 
-However, the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
-\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}.
-A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth \citep[e.g.,][]{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}.
-In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).
+However, 
+% the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
+\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and
+it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{sellwood_radial_2002,schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}.
+A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth (e.g., \citealt{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}; \added{but see also \citealt{johnson_stellar_2021,dubay_galactic_2024}}).
+In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history.
+% (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).
 Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
@@
 
-\todo{Integrate into previous para:} \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation (AMR), which could be interpreted as evidence supporting the two-infall scenario, but \citet{plotnikova_chemical_2024} argued that such patterns can arise due to selection effects.
-\todo{Also: multiple sequences in Anders et al. (2023), Xiang \& Rix (2022), Sahlholdt et al. (2022).}
-
 The availability of large stellar catalogs with [Fe/H], \aFe, {\it and} age covering a large portion of the Galactic disk enables much more comprehensive tests of the two-infall GCE scenario (and other models).
@@
 We compare our multi-zone model predictions to the data in Section \ref{sec:multizone-results}.
-We discuss possible extensions to our models in Section \ref{sec:discussion}, and we and summarize our conclusions in Section \ref{sec:conclusions}.
+We discuss possible extensions to our models in Section \ref{sec:discussion}, and we summarize our conclusions in Section \ref{sec:conclusions}.
 
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{\figpath{compare_age_catalogs.pdf}}
+    \caption{\added{Comparison between NN \citep{leung_variational_2023} and [C/N] \citep{roberts_cn_2025} ages for our sample.
+{\it Left:} Comparison of age estimates from both methods for all APOGEE stars.
+{\it Right:} The local ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) age--metallicity relation for each age estimation method.}}
+    \label{fig:compare-age-catalogs}
+\end{figure*}
+
 We supplement the APOGEE DR17 abundance data with two different age catalogs.
@@
 With this relationship, we estimate ages for \num{124778} stars across the disk, including \num{21956} in the Solar neighborhood.
+
+\added{Figure \ref{fig:compare-age-catalogs} compares the NN ages from \citet{leung_variational_2023} and the [C/N]-derived ages from \citet{roberts_cn_2025} for our sample.
+Below an age of $\sim10\Gyr$, the two methods trace each other closely, although there is a small systematic offset for $\lesssim4\Gyr$ old stars.
+The Solar neighborhood age--metallicity relation (AMR) of \citet{leung_variational_2023} features substructure not seen in the \citet{roberts_cn_2025} AMR, possibly washed out due to the larger uncertainty in the latter sample.
+We compare these AMRs to others in the literature in Section \ref{sec:amr}.
+Overall, the AMRs derived from both methods are remarkably flat out to $\sim8-9\Gyr$, with variations of $\lesssim0.1\dex$ on the order of $1\Gyr$.}
 
@@
 The black curve (points) plots the rolling median (binned mode) of the abundance data as a function of age, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
-    The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions \added{in the same region}, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
+    The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
     \label{fig:yield-outflow}
@@
 
-Figure \ref{fig:yield-outflow} shows the \added{APOGEE age--abundance distributions at the Solar annulus, as well as the binned mode abundance and rolling median as a function of age}, using the NN ages from \citet{leung_variational_2023}.
-As shown by \citet{johnson_milky_2025}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
-\added{While the age--metallicity distribution is clumpy in places (see Section \ref{sec:amr}), we observe that ${\rm mode}(\mathOH)\gtrsim0$ for the past 10 Gyr.}
+Figure \ref{fig:yield-outflow} shows the \added{APOGEE age--abundance distributions in the Solar annulus, as well as the binned mode and rolling median abundance as a function of age}, using the NN ages from \citet{leung_variational_2023}.
+\added{While the age--abundance distributions are clumpy in places (see Section \ref{sec:amr}), we caution that the APOGEE selection function can affect the stellar age distribution \citep[see][]{imig_galactic_2025}.} As shown by \citet{johnson_milky_2025}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
+\added{Strikingly, we observe that ${\rm mode}(\mathOH)\gtrsim0$ over the past 10 Gyr.}
 
@@
 Motivated by the results of the previous sections, we attempt to construct a model that solves all of the issues that have been outlined thus far.
-Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
+Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), \added{$t_{\rm max}=3.2\Gyr$ to better match the local [O/Fe]--[Fe/H] distribution (Section \ref{sec:sfh}),} pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
 Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate than the illustrative examples in the previous section.
@@
 This model is generally successful at reproducing the observed abundance distributions, especially in the inner Galaxy and close to the midplane.
-However, the predicted high-$\alpha$ sequence has a significant presence even in the outer Galaxy---likely a consequence of the stronger migration prescription and higher thick-to-thin disk ratio.
+However, the predicted high-$\alpha$ sequence has a significant presence even in the outer Galaxy---likely a consequence of the stronger migration prescription and higher thick-to-thin disk ratio \added{than in the fiducial model}.
 In general, the predicted distributions do not align with the data as well at large midplane distances ($1\leq|z|<2\kpc$), but this may reflect inaccuracies in our prescription for vertical heating (see Section \ref{sec:migration}).
@@
 The sequences are less pronounced in the \citet{leung_variational_2023} catalog than reported by \citet{anders_spectroscopic_2023}, likely related to a systematic offset between the two catalogs around the same age \citep[see Figure 6 of][]{anders_spectroscopic_2023}.
-On the other hand, the [C/N] age-metallicity relation of \citet{roberts_cn_2025} is even flatter and does not appear to have multiple sequences.
+On the other hand, the [C/N] age--metallicity relation of \citet{roberts_cn_2025} is even flatter and does not appear to have multiple sequences (Figure \ref{fig:compare-age-catalogs}).
 Even if these sequences are real, we find it difficult to explain them using the two-infall scenario\textemdash the observed dilution is much smaller than predicted by any of our models, and the timing of the split between the sequences is too late for the birth of the thin disk, although it is interestingly close to the first pericentric passage of the Sagittarius dwarf galaxy \citep{ruiz-lara_recurrent_2020}.}
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{\figpath{compare_age_catalogs.pdf}}
-    \caption{Comparison between NN- and [C/N]-derived ages for our sample.}
-    \label{fig:compare-age-catalogs}
-\end{figure*}
+\todo{Even if the Anders et al.
+(2023) sequences are right, it still doesn't look like two-infall.
+The Anders AMR reaches Solar-ish metallicity 8 Gyr ago, then drops to $\mathFeH\approx-0.2$ by 4 Gyr ago.
+A 0.2 dex dilution over 4 Gyr is {\it far} weaker and more gradual than predicted by any of our two-infall models.}
 

### 2025-12-09 src/tex/ms.tex

@@
 For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel.
-The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$, and the black squares plot the median stellar abundance in {2 Gyr}-wide age bins.
-The red line and points are the median abundance for APOGEE stars, and the shaded regions are the 16th--84th percentile ranges.
+The dashed curve plots the predicted ISM abundance at $R_{\rm gal}=8\kpc$, \added{and the solid black curve plots the rolling median stellar abundance.
+The red curve plots the rolling median abundance of the APOGEE sample}, and the shaded regions are the 16th--84th percentile ranges.
 Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).}
@@
     \includegraphics[width=\onecolumn]{\figpath{ofe_feh_density.pdf}}
-    \caption{The density of stars in the [O/Fe]--[Fe/H] plane predicted by multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$, and (c) from the APOGEE DR17 catalog.
-The curves in panels (a) and (b) plot the ISM abundance at the Solar annulus over time, and the alternating black and white segments mark time intervals of {1 Gyr}.
+    \caption{The density of stars in the [O/Fe]--[Fe/H] plane predicted by multi-zone models with (a) $y/Z_\odot=1$ and (b) $y/Z_\odot=2$.
+The curves plot the ISM abundance at the Solar annulus over time, and the alternating black and white segments mark time intervals of 1~Gyr.
 The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution.
-    Stars in all panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$.}
+    Stars in \added{both} panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$.}
     \label{fig:ofe-feh-density}
@@
 
-\added{A few recent studies have reported the discovery of multiple disconnected sequences in the local age--metallicity relation \citep[e.g.,][]{sahlholdt_characterizing_2022,xiang_time-resolved_2022,anders_spectroscopic_2023}.
-\citet{nissen_high-precision_2020} argued that these sequences provide evidence for the two-infall scenario, although \citet{plotnikova_chemical_2024} showed that multiple sequences can arise due to selection effects, and \citet{chen_recent_2025} showed that radial migration can also lead to such patterns.
-There are hints of multiple sequences in Figure \ref{fig:yield-outflow}, where a break in the distribution at ages of $\sim5\Gyr$ coincides with a $\sim0.2\dex$ drop in [O/H] and [Fe/H].
-The sequences are less pronounced in the \citet{leung_variational_2023} catalog than reported by \citet{anders_spectroscopic_2023}, likely related to a systematic offset between the two catalogs around the same age \citep[see Figure 6 of][]{anders_spectroscopic_2023}.
-On the other hand, the [C/N] age--metallicity relation of \citet{roberts_cn_2025} is even flatter and does not appear to have multiple sequences (Figure \ref{fig:compare-age-catalogs}).
-Even if these sequences are real, we find it difficult to explain them using the two-infall scenario\textemdash the observed dilution is much smaller than predicted by any of our models, and the timing of the split between the sequences is too late for the birth of the thin disk, although it is interestingly close to the first pericentric passage of the Sagittarius dwarf galaxy \citep{ruiz-lara_recurrent_2020}.}
-\todo{Mention APOGEE selection function?}
+\added{A few recent studies report the discovery of multiple disconnected sequences in the local age--metallicity relation \citep[e.g.,][]{sahlholdt_characterizing_2022,xiang_time-resolved_2022,anders_spectroscopic_2023}.
+\citet{nissen_high-precision_2020} argued that the existence of multiple sequences is evidence for the two-infall scenario.
+However, \citet{plotnikova_chemical_2024} showed that multiple sequences can arise due to selection effects, and the APOGEE selection function in particular affects the observed stellar age distribution \citep{imig_galactic_2025}.
+Furthermore, \citet{chen_recent_2025} demonstrated that multiple sequences in the local AMR can arise naturally due to radial migration, even in the absence of major accretion or starburst events.
 % Anders+ use APOGEE clump stars. Their split is 5-6 Gyr ago
@@
 
-\todo{Even if the Anders et al.
-(2023) sequences are right, it still doesn't look like two-infall.
-The Anders AMR reaches Solar-ish metallicity 8 Gyr ago, then drops to $\mathFeH\approx-0.2$ by 4 Gyr ago.
-A 0.2 dex dilution over 4 Gyr is {\it far} weaker and more gradual than predicted by any of our two-infall models.}
+Figure \ref{fig:yield-outflow} shows hints of multiple sequences in the \citet{leung_variational_2023} AMR, specifically where an under-density of $\sim5\Gyr$ old stars coincides with a $\sim0.2\dex$ drop in [O/H] and [Fe/H].
+This is less pronounced, but otherwise similar to, the sequences found by \citet{anders_spectroscopic_2023}.
+We note a systematic offset between the two catalogs around the same age \citep[see Figure 6 of][]{anders_spectroscopic_2023}.
+On the other hand, the [C/N] AMR of \citet{roberts_cn_2025} is flatter and does not appear to have multiple sequences (Figure \ref{fig:compare-age-catalogs}), although the larger age uncertainties may wash out such patterns.
+
+Even if these AMR sequences are real, the two-infall scenario does not offer a natural explanation.
+The difference in metallicity between the sequences in our sample is $\sim0.2\dex$, smaller than the dilution predicted by any of our models.
+Additionally, the transition between the sequences occurs $\sim5\Gyr$ ago \citep[matching][]{anders_spectroscopic_2023}, much younger than the oldest thin disk stars \citep{pinsonneault_apokasc-3_2025}.
+Interestingly, the transition does align with the first pericentric passage of the Sagittarius dwarf galaxy \citep{ruiz-lara_recurrent_2020}.}
 
@@
 The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
-As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk measured by\citet{pinsonneault_apokasc-3_2025}.
+As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk measured by \citet{pinsonneault_apokasc-3_2025}.
 This hiatus model illustrates an alternative scenario for reproducing the $\alpha$-bimodality, but a full multi-zone treatment is beyond the scope of this work.

### 2025-12-11 src/tex/ms.tex
Updates from Overleaf

@@
 % For TeXworks
-\makeatletter
-\declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
-\makeatother
+% \makeatletter
+% \declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
+% \makeatother
 
 % Define document class
-\documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex631}
+\documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex701}
 
@@
 \affiliation{\ccappaffil}
+\email{dubay.11@osu.edu}
 \author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
@@
 \affiliation{\ccappaffil}
+\email{}
 \author[0000-0002-6534-8783]{James W.\ Johnson}
 \affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
+\email{}
 \author[0000-0002-2854-5796]{John D.\ Roberts}
@@
 \affiliation{\ccappaffil}
+\email{}
 
@@
 % The initial model of 
-\citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time, and
+\added{\citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time, and}
 subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
-Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}.
-\citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the star formation history inferred from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and to explain the recent abundance evolution (or lack thereof) in the Solar neighborhood.
+Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}, \added{and additional episodes of gas accretion \citep{spitoni_beyond_2023,palla_mapping_2024}}.
 Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey \citep[SDSS;][]{sdss_collaboration_nineteenth_2025}.
-
-% While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
-This decision is based on hydrodynamic simulations of Galactic fountains produced by CC SNe, which predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to its point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
-However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}; other simulations of MW-like galaxies with different prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
-Empirically, mass-loading is observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
-Even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.
 
@@
 {\it Left:} Comparison of age estimates from both methods for all APOGEE stars.
-{\it Right:} The local ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) age--metallicity relation for each age estimation method.}}
+The solid black curve plots the rolling median (window size 1000 stars) of the [C/N] age estimate as a function of the NN age, the dashed line indicates the one-to-one correspondence, and the white error bars indicate the age uncertainty as a function of NN age.
+{\it Right:} The local ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) age--metallicity relation for each age estimation method.
+The black curve plots the rolling median [Fe/H] as a function of age.}}
     \label{fig:compare-age-catalogs}
@@
 
-\begin{deluxetable*}{Ccccl}
-    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:parameters}}
+\begin{deluxetable*}{Cccl}
+    \tablecaption{A summary of variables for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:parameters}}
     \tablehead{
-        \colhead{Quantity} & \colhead{Fiducial Value} & \colhead{Alternatives} & \colhead{Section} & \colhead{Description}
+        \colhead{Quantity} & \colhead{Value or Range} & \colhead{Section} & \colhead{Description}
     }
     \startdata
-        R_{\rm gal}         & $[0,20]\kpc$  & \nodata           & \ref{sec:methods}     & Galactocentric radius \\
-        \delta R_{\rm gal}  & $0.1\kpc$     & \nodata           & \ref{sec:methods}     & Radial zone width \\
-        R_{\rm SF}          & $15.5\kpc$    & \nodata           & \ref{sec:methods}     & Maximum radius of star formation \\
-        t_{\rm final}       & $13.2\Gyr$    & \nodata           & \ref{sec:methods}     & Disk lifetime \\
-        \Delta t            & $10\Myr$      & \nodata           & \ref{sec:methods}     & Time-step size \\
-        n                   & 8             & \nodata           & \ref{sec:methods}     & Number of stellar populations formed per ring per timestep \\
-        \dot M_r            & continuous    & \nodata           & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
-        y/Z_\odot           & 1             & 2, 3              & \ref{sec:yields}      & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
-        N_{\rm Ia}/M_\star  & $1.55\times10^{-3}\Msun^{-1}$ & 2.62, $3.57\times10^{-3}\Msun^{-1}$   & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \\
-        f_{\rm Ia}(t)       & Equation \ref{eq:plateau-dtd} & Equation \ref{eq:powerlaw-dtd}    & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
-        t_{\rm Ia}          & $40\Myr$  & \nodata           & \ref{sec:yields}              & Minimum SN Ia delay time \\
-        \eta_\odot          & 0.2       & $0.6-2.4$         & \ref{sec:outflows}            & Outflow mass-loading factor at $R_\odot$ ($\eta\equiv\dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
-        R_\eta              & $5.0\kpc$ & \nodata           & \ref{sec:outflows}            & Exponential outflow scale radius \\
-        \tau_\star          & Equation \ref{eq:sf-law}      & \nodata & \ref{sec:sf-law}      & Star formation efficiency timescale ($\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$) \\
-        k                   & 1.5       & \nodata           & \ref{sec:sf-law}              & Star formation law exponent \citep{kennicutt_global_1998} \\
-        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & \nodata & \ref{sec:sfh} & Total stellar mass of the disk \citep{licquia_improved_2015} \\
-        f_\Sigma(R_\odot)   & 0.12      & 0.25, 0.5         & \ref{sec:sfh}                 & Local thick/thin disk surface density ratio \\
-        R_1                 & $2.0\kpc$ & \nodata           & \ref{sec:sfh}                 & Thick disk scale radius \\
-        R_2                 & $2.5\kpc$ & \nodata           & \ref{sec:sfh}                 & Thin disk scale radius \\
-        \mathXH_{\rm CGM}   & $-\infty$ & $-0.7$, $-0.5$    & \ref{sec:sfh}                 & Metallicity of infalling gas \\
-        f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & \nodata   & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
-        \tau_1              & $1\Gyr$   & \nodata           & \ref{sec:sfh} & Timescale of the first infall epoch \\
-        \tau_2(R_\odot)     & $15\Gyr$  & \nodata           & \ref{sec:sfh} & Timescale of the second infall epoch at the Solar annulus \\
-        R_{\tau_2}          & $7\kpc$   & \nodata           & \ref{sec:sfh} & Exponential scale radius of the second infall timescale \\
-        t_{\rm max}         & $4.2\Gyr$ & \nodata           & \ref{sec:sfh} & Time of maximum gas infall (onset of second infall) \\
-        \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & \nodata & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
-        \sigma_{\rm RM8}    & $2.68\kpc$ & $3.6$, $5.0\kpc$ & \ref{sec:migration}   & Radial migration strength (width of $\sigma_{\rm RM}$ for $\tau=8\Gyr$) \\
-        z                   & $[-3,3]\kpc$  & \nodata       & \ref{sec:migration}   & Distance from Galactic midplane at present day \\
-        h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & \nodata       & \ref{sec:migration} & Disk scale height \\
+        R_{\rm gal}         & $[0,20]\kpc$  & \ref{sec:methods}     & Galactocentric radius \\
+        \delta R_{\rm gal}  & $0.1\kpc$     & \ref{sec:methods}     & Radial zone width \\
+        R_{\rm SF}          & $15.5\kpc$    & \ref{sec:methods}     & Maximum radius of star formation \\
+        t_{\rm final}       & $13.2\Gyr$    & \ref{sec:methods}     & Disk lifetime \\
+        \Delta t            & $10\Myr$      & \ref{sec:methods}     & Time-step size \\
+        n                   & 8             & \ref{sec:methods}     & Number of stellar populations formed per ring per timestep \\
+        \dot M_r            & continuous    & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
+        y/Z_\odot           & $[1,3]$       & \ref{sec:yields}      & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
+        N_{\rm Ia}/M_\star  & $[1.55,3.57]\times10^{-3}\Msun^{-1}$  & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \\
+        f_{\rm Ia}(t)       & Equations \ref{eq:plateau-dtd}, \ref{eq:powerlaw-dtd}     & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
+        t_{\rm Ia}          & $40\Myr$  & \ref{sec:yields}          & Minimum SN Ia delay time \\
+        \eta_\odot          & $[0.2,2.4]$   & \ref{sec:outflows}    & Outflow mass-loading factor at $R_\odot$ ($\eta\equiv\dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
+        R_\eta              & $5.0\kpc$     & \ref{sec:outflows}    & Exponential outflow scale radius \\
+        \tau_\star          & Equation \ref{eq:sf-law}              & \ref{sec:sf-law}      & Star formation efficiency timescale ($\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$) \\
+        k                   & 1.5           & \ref{sec:sf-law}      & Star formation law exponent \citep{kennicutt_global_1998} \\
+        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & \ref{sec:sfh} & Total stellar mass of the disk \citep{licquia_improved_2015} \\
+        f_\Sigma(R_\odot)   & $[0.12, 0.5]$     & \ref{sec:sfh}     & Local thick/thin disk surface density ratio \\
+        R_1                 & $2.0\kpc$         & \ref{sec:sfh}     & Thick disk scale radius \\
+        R_2                 & $2.5\kpc$         & \ref{sec:sfh}     & Thin disk scale radius \\
+        \mathXH_{\rm CGM}   & $(-\infty,-0.5]$  & \ref{sec:sfh}     & Metallicity of accreted gas \\
+        f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
+        \tau_1              & $1\Gyr$       & \ref{sec:sfh}         & Timescale of the first infall epoch \\
+        \tau_2(R_\odot)     & $15\Gyr$      & \ref{sec:sfh}         & Timescale of the second infall epoch at the Solar annulus \\
+        R_{\tau_2}          & $7\kpc$       & \ref{sec:sfh}         & Exponential scale radius of the second infall timescale \\
+        t_{\rm max}         & $4.2\Gyr$     & \ref{sec:sfh}         & Time of maximum gas infall (onset of second infall) \\
+        \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
+        \sigma_{\rm RM8}    & $[2.68,5.0]\kpc$  & \ref{sec:migration}   & Radial migration strength (width of $\sigma_{\rm RM}$ for $\tau=8\Gyr$) \\
+        z                   & $[-3,3]\kpc$      & \ref{sec:migration}   & Distance from Galactic midplane at present day \\
+        h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & \ref{sec:migration} & Disk scale height \\
     \enddata
 \end{deluxetable*}
-\vspace{-24pt}
 
@@
 }\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun.
-However, \citet{johnson_milky_2025} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed age--metallicity relation.
+However, \citet{johnson_milky_2025} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed AMR.
 Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
@@
 \end{deluxetable*}
-\vspace{-24pt}
 
@@
 The red curve plots the rolling median abundance of the APOGEE sample}, and the shaded regions are the 16th--84th percentile ranges.
-Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).}
+Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, {\tt yZ1-fiducial}; {\bf (b)} a model with stronger radial migration, {\tt yZ1-migration}; {\bf (c)} a model with a higher local thick-to-thin disk ratio, {\tt yZ1-diskratio}; and {\bf (d)} a model with pre-enriched gas infall, {\tt yZ1-preenrich} (see Table \ref{tab:models} for details).}
     \label{fig:abundance-evolution-params}
@@
 
-Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local age--metallicity relation even with a smooth SFH \citep[see also][]{johnson_milky_2025}.
+Chemical evolution models that assume the \yZ{1} (empirical) yield scale already struggle to match the local AMR even with a smooth SFH \citep[see also][]{johnson_milky_2025}.
 The problem is exacerbated in the two-infall case because of the delayed dilution event---the approach to equilibrium is ``reset'' by the second infall.
@@
 We smoothed simulated data points based on the median age and abundance errors in Table \ref{tab:uncertainties} to incorporate these errors in the model.
-The black dashed curve shows the evolution of gas phase abundances at $R_{\rm gal}=8\kpc$.
-Despite the effects of radial migration and statistical errors, the stellar populations mostly scatter around this gas phase curve, at least for $\tau\lesssim9\Gyr$.
+Despite the effects of radial migration and statistical errors, the stellar populations mostly scatter around \added{the gas phase abundance track}, at least for $\tau\lesssim9\Gyr$.
+\added{Between ages $\sim5-9\Gyr$, the predicted median stellar metallicity is $\sim0.5\dex$ lower than observed, well below the 16\textsuperscript{th} percentile of the data.}
 
 We next attempt to mitigate the dilution and late-time evolution problems for the \yZ{1} yield scale.
-First, the observed rise in the median metallicity of stars in the $6-10\Gyr$ age range could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the metal-rich inner Galaxy \citep{feuillet_age-resolved_2018}.
+First, the observed rise in the median metallicity of stars in the $5-9\Gyr$ age range could be due to radial migration, as those stars were probably not born in-situ, but rather migrated from the metal-rich inner Galaxy \citep{feuillet_age-resolved_2018}.
 Column (b) of Figure \ref{fig:abundance-evolution-params} presents model {\tt yZ1-migration}, which has a stronger migration prescription of $\sigma_{\rm RM8}=5\kpc$.
 As a result, the stars that make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution at fixed age.
-Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, for example, the model still significantly under-predicts the metallicity of $\sim6-10\,{\rm Gyr}$ old stars.
+Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, for example, the model still significantly under-predicts the \added{median} metallicity of $\sim5-9\,{\rm Gyr}$ old stars.
 
@@
 However, agreement with the observed age--[O/Fe] relation is poor.
-The model predicts a much flatter trend than observed, under-predicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.
+The model predicts a much flatter trend than observed, under-predicting [O/Fe] by $\sim0.1$ dex in the $\sim5-9\Gyr$ age range.
 
@@
 
-Overall, no modification to the \yZ{1} model is able to completely overcome the issues that dilution and re-enrichment naturally face when confronted with a flat age--metallicity relation.
+Overall, no modification to the \yZ{1} model is able to completely overcome the issues that dilution and re-enrichment naturally face when confronted with a flat AMR.
 Pre-enrichment of the accreted gas and a higher disk mass ratio can reduce the discrepancy with the data, but these options introduce new issues in the age--[O/Fe] plane.
@@
 In summary, either an enhanced disk mass ratio or pre-enriched infall can improve agreement with the observed thin disk abundances for the \yZ{2} case.
-These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.
+These parameters also help the model better fit the AMR, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.
 
@@
 Motivated by the results of the previous sections, we attempt to construct a model that solves all of the issues that have been outlined thus far.
-Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:yield-outflow}), \added{$t_{\rm max}=3.2\Gyr$ to better match the local [O/Fe]--[Fe/H] distribution (Section \ref{sec:sfh}),} pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
+Our ``best attempt'' model {\tt yZ2-best} uses the \yZ{2} yield set to flatten the local AMR (Figure \ref{fig:yield-outflow}), \added{$t_{\rm max}=3.2\Gyr$ to better match the local [O/Fe]--[Fe/H] distribution (Section \ref{sec:sfh}),} pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}).
 Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate than the illustrative examples in the previous section.
@@
 In both models, there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
-The \yZ{2} model also predicts that the stars with the lowest [O/Fe] should be $\sim8-9\Gyr$ old, while these are some of the youngest stars in APOGEE.
+% The \yZ{2} model also predicts that the stars with the lowest [O/Fe] should be $\sim8-9\Gyr$ old, while these are some of the youngest stars in APOGEE.
 The latter issue can be mitigated by adjusting the parameters of the first infall, as discussed in the previous Section, but the former is not solved so easily.
@@
 We further highlight the discrepant age patterns in the bottom panels of Figure \ref{fig:lmr-ages}, which compare the overall stellar age distribution against that of the locally metal rich (LMR) stars, defined here as $\mathFeH\ge+0.1$.\footnote{
-    While the amplitude of the peaks is sensitive to the precise location of the LMR cutoff, the dearth of intermediate-age stars is robust to adjustments of $\pm0.05\dex$.
+    While the amplitude of the peaks is sensitive to the precise location of the LMR cutoff, the dearth of intermediate-age stars is \added{insensitive} to adjustments of $\pm0.05\dex$.
 } For APOGEE, the distributions of all stars and only LMR stars are similar, both peaking near $\sim5\Gyr$, although very few of the LMR stars have ages $\gtrsim10\Gyr$.
-Our two-infall models predict an overall age distribution that is similar to the data, but both models predict a distinctly bimodal age distribution for LMR stars.
-The two populations reflect the metal-rich endpoints of the two successive infall epochs.
-The trough between the modes lies at $\sim5\Gyr$ for both models, right where the APOGEE distribution peaks.
-It is difficult to obtain a unimodal age distribution with the available parameter space.
-A dearth of intermediate-age, high-metallicity stars is a natural outcome of a substantial dilution event, which is a defining feature of the two-infall scenario.
+Our two-infall models predict an overall age distribution that is similar to the data, but both models predict a distinctly \added{different} age distribution for LMR stars.
+\added{For the \yZ{1} model, the LMR age distribution is strongly bimodal;} the two populations reflect the metal-rich endpoints of the two successive infall epochs.
+\added{For the \yZ{2} model, the LMR ages are not bimodal but are heavily skewed to younger ($\lesssim6\Gyr$) ages (note that the models have different values of $t_{\rm max}$, which affects the predicted age distributions).
+Both models predict few LMR stars with intermediate ($\sim4-8\Gyr$) ages, whereas these stars dominate the LMR population in APOGEE.} A dearth of intermediate-age, high-metallicity stars is a natural outcome of a substantial dilution event, which is a defining feature of the two-infall scenario.
 None of the adjustments that we explored in Sections \ref{sec:age-abundance} or \ref{sec:abundance-distributions} substantially increase the proportion of intermediate-age stars.
+
+\added{Two other discrepancies between the models and data in Figure \ref{fig:lmr-ages} reflect our specific parameter choices, not intrinsic limitations of the two-infall framework.
+First, the predicted ages of high-$\alpha$ stars are $\sim1-2$ Gyr older than observed in APOGEE.
+Delaying the onset of thick disk formation (e.g., by introducing an early ``simmering'' phase of low star formation efficiency proposed by \citealt{conroy_birth_2022}) could alleviate this tension, but it would not improve the dearth of intermediate-aged LMR stars.
+Second, the youngest APOGEE stars have [O/Fe] ratios $\sim0.05-0.1\dex$ lower than predicted by the models (see also the bottom panel of Figure \ref{fig:yield-outflow}).
+Increasing $y_{\rm Fe}^{\rm Ia}$ by a factor of $10^{0.05}\approx1.1$ brings the present-day gas abundance in line with the data, but worsens agreement with the overall stellar [O/Fe] distribution.}
 
@@
 
-\added{A few recent studies report the discovery of multiple disconnected sequences in the local age--metallicity relation \citep[e.g.,][]{sahlholdt_characterizing_2022,xiang_time-resolved_2022,anders_spectroscopic_2023}.
+\added{A few recent studies report the discovery of multiple disconnected sequences in the local AMR \citep[e.g.,][]{sahlholdt_characterizing_2022,xiang_time-resolved_2022,anders_spectroscopic_2023}.
 \citet{nissen_high-precision_2020} argued that the existence of multiple sequences is evidence for the two-infall scenario.
@@
 Additionally, the transition between the sequences occurs $\sim5\Gyr$ ago \citep[matching][]{anders_spectroscopic_2023}, much younger than the oldest thin disk stars \citep{pinsonneault_apokasc-3_2025}.
-Interestingly, the transition does align with the first pericentric passage of the Sagittarius dwarf galaxy \citep{ruiz-lara_recurrent_2020}.}
+Interestingly, the transition does align with the first pericentric passage of the Sagittarius dwarf galaxy, which has been linked to periods of enhanced star formation in the disk \citep{ruiz-lara_recurrent_2020}.
+It is possible that the Milky Way has seen multiple episodes of star formation without experiencing the dilution associated with the two-infall scenario.}
 
@@
 
-\subsection{Radial Gas Flows}
+\subsection{Outflows Versus Radial Gas Flows}
 \label{sec:radial-flows}
+
+\added{The role of Galactic winds in the Milky Way's evolution is uncertain.
+Some simulations of CCSN feedback predict that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} close to its point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting that the effect on GCE should be minimal.
+However, the effects of feedback in simulations are sensitive to its implementation \citep[e.g.,][]{li_effects_2020,hu_code_2023}; other simulations of MW-like galaxies with different prescriptions do produce mass-loaded outflows \citep[e.g.,][]{brook_hierarchical_2011,gutcke_nihao_2017,nelson_first_2019,peschken_angular_2021,kopenhafer_seeking_2023}.
+Empirically, mass-loading is observed in nearby starburst galaxies \citep[e.g.,][]{lopez_temperature_2020,cameron_duvet_2021,lopez_x-ray_2023} but not MW-like systems because the predicted column densities are below current detection limits \citep[see reviews by][]{veilleux_cool_2020,thompson_theory_2024}.
+Additionally, observed wind velocities in external galaxies suggest that outflowing gas may remain gravitationally bound \citep{concas_two-faces_2019}.}
 
@@
 The outflow is simpler in implementation than a radial gas flow; we can simply adjust the mass loading factors up or down in combination with a given scale of yields.
-This approach allows us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
+\added{Additionally, our models with pre-enriched CGM are a step toward modeling the re-accretion of material from Galactic winds, as suggested by simulations of Galactic fountains and the observations of \citet{concas_two-faces_2019}.
+Outflows allow} us to easily consider models that predict metallicity to evolve on different timescales but reach similar abundances at the present day (see, e.g., Figure \ref{fig:yield-outflow}).
 We have therefore focused on models with outflows in this paper for the sake of simplicity, but constant radial gas flow models should have similar effects.
 
-\subsection{Star Formation Hiatus}
+\subsection{Star Formation Hiatus Models}
 \label{sec:sfe-hiatus}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\onecolumn]{\figpath{sfe_hiatus.pdf}}
-    \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\onecolumn]{\figpath{sfe_hiatus.pdf}}
+%     \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.
 The blue dashed curve represents the fiducial model that has an exponentially declining infall rate with timescale $\tau_{\rm in}=15\Gyr$, and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
@@
 The grayscale histogram is the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}< 9\kpc$, $|z|<2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
-    \label{fig:onezone-sfe-hiatus}
-\end{figure}
-
-The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation temporarily.
-For the two-infall model, this phase of low star formation lasts for a few Gyr between the $e$-folding timescale of the first infall and the onset of the second.
-However, as we have shown in Section \ref{sec:age-abundance}, the resulting dilution of the ISM is in tension with the observed stellar age--metallicity relation.
-
-An accretion-driven star formation history is not the only way to induce a hiatus in star formation.
-Investigating a simulated galaxy from the Illustris TNG50 suite \citep{pillepich_first_2019,nelson_first_2019,nelson_illustristng_2019}, \citet{beane_rising_2024} argued that its MW-like $\alpha$-bimodality is the result of a brief ($\sim300\,{\rm Myr}$) quiescent period caused by the formation of a bar.
+%     \label{fig:onezone-sfe-hiatus}
+% \end{figure}
+
+% The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation temporarily.
+\added{In our models,} this phase of low star formation lasts for a few Gyr between the $e$-folding timescale of the first infall and the onset of the second.
+However, as we have shown in Section \ref{sec:age-abundance}, the resulting dilution of the ISM is in tension with the observed stellar AMR.
+
+\added{The two-infall scenario produces an $\alpha$-bimodality due to a few Gyr long quiescent period between the two major accretion epochs.
+However, significant gas accretion is not a necessary ingredient to produce a hiatus in star formation.} Investigating a simulated galaxy from the Illustris TNG50 suite \citep{pillepich_first_2019,nelson_first_2019,nelson_illustristng_2019}, \citet{beane_rising_2024} argued that its MW-like $\alpha$-bimodality is the result of a brief ($\sim300\,{\rm Myr}$) quiescent period caused by the formation of a bar.
 In this scenario, the newly-formed bar funnels gas into the galaxy's central black hole, prompting a burst of AGN activity which suppresses star formation.
-Unlike our two-infall model, where the gas mass suddenly grows by a factor of $\sim5$ during the 1 Gyr following the second infall, the mass of their galaxy grows slowly during the quiescent period, indicating a dearth of major accretion events.
-
-While our semi-analytic model does not include a Galactic bar, we can induce a star formation hiatus by artificially boosting the SFE timescale $\tau_\star$ for a period of time.
+% Unlike our two-infall model, where the gas mass suddenly grows by a factor of $\sim5$ during the 1 Gyr following the second infall, the mass of their galaxy grows slowly during the quiescent period, indicating a dearth of major accretion events.
+\todo{Mention James' recent retrograde mergers paper.}
+\added{Alternatively, \citet{johnson_thats_2025} showed that a retrograde merger can induce much of the ISM to sink to the center of the Galaxy, lowering the local gas surface density and thereby creating an $\alpha$-bimodality.
+The low mass ratio of the merger ($\sim3:1$) means the thin disk is not formed directly from gas accreted during the merger, but rather that radial gas flows induced by the merging galaxy's trajectory alter the stellar \aFe distributions.
+Both of these scenarios explain the observed \aFe distribution without invoking significant dilution and re-enrichment of the ISM.}
+
+% While our semi-analytic model does not include a Galactic bar, we can induce a star formation hiatus by artificially boosting the SFE timescale $\tau_\star$ for a period of time.
 Figure \ref{fig:onezone-sfe-hiatus} illustrates the effect of this efficiency-driven hiatus in a one-zone GCE model with an exponentially declining infall rate ($\tau_{\rm in}=15\Gyr$).
@@
 
-The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
+% The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
 As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk measured by \citet{pinsonneault_apokasc-3_2025}.
@@
 Models at a lower yield scale and weaker outflows predict slower re-enrichment.
-By contrast, the observed stellar age--metallicity relation is roughly constant over the past $\sim10\Gyr$.
+By contrast, \added{observed stellar metallicities are} roughly constant over the past $\sim10\Gyr$.
 Pre-enriching the accreted gas can reduce the magnitude of the dilution, but cannot eliminate it entirely.
     \item Due to this re-enrichment, our models predict that the MDF shifts to higher metallicity with decreasing age throughout the disk.
-This contrasts with the APOGEE data, which show very little change in the mode of the MDF over the past $\sim6-8$ Gyr.
+This contrasts with the APOGEE data, which show little change in the mode of the MDF over the past $\sim6-8$ Gyr.
     \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations: local metal-rich stars should either be very old or very young.
@@
 The ``inside-out'' models of \citet{johnson_stellar_2021} are better able to predict a slowly evolving metallicity gradient, but they do not predict an $\alpha$-bimodality.
-Even a smoothly-evolving SFH struggles to reproduce the flat age--metallicity relation at the lower empirical yield scale \citep{johnson_milky_2025}.
+Even a smoothly-evolving SFH struggles to reproduce the flat AMR at the lower empirical yield scale \citep{johnson_milky_2025}.
 We emphasize, though, that by its very construction, the two-infall scenario trades success at reproducing certain observations for failure at others.
@@
 \bibliography{references}
+\bibliographystyle{aasjournalv7}
 

### 2025-12-15 src/tex/ms.tex
Manuscript updates for referee report

@@
-% For TeXworks
-% \makeatletter
-% \declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
-% \makeatother
-
-% Define document class
 \documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex701}
 
-% \usepackage{showyourwork}
 \usepackage{amsmath}
@@
 The basic premise is that the rate of gas accretion onto the disk occurs in two bursts.
-The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars.
-% The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
-% The initial model of 
-\added{\citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time, and}
-subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
+The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas \added{metallicity} to evolve between the high- and low-$\alpha$ sequences while producing few stars.
+\added{\citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time, and} subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}.
 Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}, \added{and additional episodes of gas accretion \citep{spitoni_beyond_2023,palla_mapping_2024}}.
@@
 \added{While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow.
-The presence of mass-loaded outflows in MW-like galaxies is heavily debated \citep[see discussion in][]{johnson_milky_2025}, but even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.}
-By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,weinberg_equilibrium_2017,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}.
-% \citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point.
+The presence of mass-loaded outflows in MW-like galaxies is heavily debated \citep[see discussion in][]{johnson_milky_2025}, but even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.} By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,weinberg_equilibrium_2017,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}.
 This degeneracy prohibits direct estimates of the yields from GCE models unless the effect of outflows is assumed to be insignificant.
@@
 The two-infall scenario reproduces the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track.
-However, 
-% the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy.
-\citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and
-it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{sellwood_radial_2002,schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}.
+However, it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{sellwood_radial_2002,schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}.
 A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth (e.g., \citealt{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}; \added{but see also \citealt{johnson_stellar_2021,dubay_galactic_2024}}).
 In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history.
-% (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).
 Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii.
@@
 We run multi-zone GCE models using the Versatile Integrator for Chemical Evolution \citep[{\tt VICE};][]{johnson_impact_2020}.
+\added{We wish to both approximate the Milky Way in gas and stellar density, present-day metallicity, and stellar abundance patterns, and to be able to tune parameters to help the two-infall scenario better match the observations and to reproduce the work of previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_apogee_2021,spitoni_remind_2024,palla_chemical_2020}.}
+
 The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}.
@@
 
-We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, and the stellar migration prescription in Section \ref{sec:migration}.
+We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, \added{the infall parameters in Section \ref{sec:infall-parameters}, the enrichment of the accreted gas in Section \ref{sec:cgm-enrichment},} and the stellar migration prescription in Section \ref{sec:migration}.
 We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.
@@
         \dot M_r            & continuous    & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
+        {\rm IMF}           & \citet{kroupa_variation_2001} & \ref{sec:methods} & Initial stellar mass function \\
         y/Z_\odot           & $[1,3]$       & \ref{sec:yields}      & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
@@
         R_2                 & $2.5\kpc$         & \ref{sec:sfh}     & Thin disk scale radius \\
-        \mathXH_{\rm CGM}   & $(-\infty,-0.5]$  & \ref{sec:sfh}     & Metallicity of accreted gas \\
         f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
-        \tau_1              & $1\Gyr$       & \ref{sec:sfh}         & Timescale of the first infall epoch \\
-        \tau_2(R_\odot)     & $15\Gyr$      & \ref{sec:sfh}         & Timescale of the second infall epoch at the Solar annulus \\
+        \tau_1              & $1\Gyr$       & \ref{sec:infall-parameters}         & Timescale of the first infall epoch \\
+        \tau_2(R_\odot)     & $15\Gyr$      & \ref{sec:infall-parameters}         & Timescale of the second infall epoch at the Solar annulus \\
         R_{\tau_2}          & $7\kpc$       & \ref{sec:sfh}         & Exponential scale radius of the second infall timescale \\
-        t_{\rm max}         & $4.2\Gyr$     & \ref{sec:sfh}         & Time of maximum gas infall (onset of second infall) \\
+        t_{\rm max}         & $[3.2,4.2]\Gyr$     & \ref{sec:infall-parameters}         & Time of maximum gas infall (onset of second infall) \\
+        \mathXH_{\rm CGM}   & $(-\infty,-0.5]$  & \ref{sec:cgm-enrichment}     & Metallicity of accreted gas \\
         \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
@@
 The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models.
-\citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
+\citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$.\footnote{
     In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$.
 We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
-}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun.
+} In other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun.
 However, \citet{johnson_milky_2025} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed AMR.
-Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.
+Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted a \added{high} integrated SN Ia rate compared to the measurement of \citet{maoz_star_2017}.
 
@@
 }, because we assume that all O is produced by CCSNe.
-For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathOFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathOFe_{\rm CC}}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
+For Fe, the CCSN yield is set by the \aFe plateau at low metallicity, $\mathOFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathOFe_{\rm CC}}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}.
 We set the plateau at $\mathOFe_{\rm CC}=+0.45$, which corresponds to an Fe yield from CCSNe of $y_{\rm Fe}^{\rm CC}=4.58\times10^{-4}(y/Z_\odot)$.
@@
 
-The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is set so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
-For \yZ{3}, the combined Fe yield of CCSNe and SNe Ia matches the Solar yield scale: $(y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC})/Z_{\rm Fe,\odot}=y/Z_\odot$; for \yZ{1} and \yZ{2}, we enhance $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\%, respectively, to reach the desired end-point.
+The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is \added{calibrated} so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$.
 The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate or total number of SNe Ia per unit mass of star formation,
@@
 \end{equation}
-where $t_{\rm Ia}=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm final}=13.2\,{\rm Gyr}$ is our assumed lifetime of the Galactic disk, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
+where $t_{\rm Ia}=40\,{\rm Myr}$ is the minimum SN Ia delay time and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD.
 Motivated by recent results suggesting that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence \citep{palicio_analytic_2023,dubay_galactic_2024}, we adopt a wide plateau DTD of the form
@@
 
-\citet{johnson_milky_2025} used variations in $\eta$ with $R_{\rm gal}$ to produce variations in $Z_{\rm O,eq}$.
-To produce an exponentially declining radial [O/H] gradient, we adopt a prescription of
+\added{Variations in $\eta$ with $R_{\rm gal}$ produce variations in $Z_{\rm O,eq}$.} To produce a radial [O/H] gradient, we adopt a prescription \added{for the outflow mass-loading factor from \citet{johnson_milky_2025}} of
 \begin{equation}
-    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
+    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big),
 \end{equation}
-for the outflow mass-loading factor,
 where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$.
 We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2025}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$, consistent with recent measurements from HII regions \citep{mendez-delgado_gradients_2022} and stars \citep{myers_open_2022,johnson_milky_2025}.
-We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study.
-We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
+We note, however, that mass-loaded outflows are not a necessary ingredient for the results of this study \added{(see discussion in Section \ref{sec:radial-flows})}.
+A one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the fiducial model with $\eta=0.2$ and \yZ{1}.
 
@@
 We find $\epsilon(t<t_{\rm max})=0.2$ or $1.0$ produce similar results in one-zone models.
-To guard against over-correcting the SFE in the early Galaxy, we tested eliminating either $\varepsilon(t)$ or $\tau_{\rm mol}(t)$ from our SFE prescription in multi-zone models and found no substantial differences.
 
@@
 
-We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the star formation efficiency (SFE) timescale $\tau_\star\equiv \Sigma_g / \dot\Sigma_\star$ as functions of time at each radius.
+We run {\tt VICE} in ``infall mode,'' where we specify the gas infall density $\dot\Sigma_{\rm in}$ and the \added{SFE} timescale $\tau_\star$ as functions of time at each radius.
 The gas surface density $\Sigma_g$ and star formation rate $\dot\Sigma_\star$ are calculated from these two inputs as a natural outcome of the time-stepping solution, assuming zero initial gas mass in all zones.
 
-The infall rate as a function of time and galactocentric radius can generically be described by
+The infall rate as a function of time and galactocentric radius \added{is} generically described by
 \begin{equation}
@@
 where $g(R_{\rm gal})=\Sigma_\star(R_{\rm gal}) / \Sigma_\star(R_{\rm gal}=0)$ is the stellar density gradient, $f_{\rm in}$ is the infall rate over time, and $A$ is a normalization constant.
-Because we incorporate mass-loaded outflows, $A$ is not analytically solvable, so first we numerically integrate the star formation rate $\dot\Sigma_\star(t,R_{\rm gal})$ and then follow the procedure outlined in Appendix B of \citet{johnson_stellar_2021} to calculate $A$.
-In short, the infall rate is normalized to produce a total disk stellar mass of $M_{\rm \star,tot}=(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and to match the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
+Because we incorporate mass-loaded outflows, $A$ is not analytically solvable, so we numerically integrate $\dot\Sigma_\star(t,R_{\rm gal})$ and \added{then normalize $\dot\Sigma_{\rm in}$} to produce a total disk stellar mass of $M_{\rm \star,tot}=(5.17\pm1.11)\times 10^{10}\,{\rm M}_\odot$ \citep{licquia_improved_2015} and match the stellar surface density gradient of \citet{bland-hawthorn_galaxy_2016}.
 
-The infall rate is described by two successive, exponentially declining bursts in time.
-The first infall component forms the thick disk, and the second produces the thin disk.
-The un-normalized form of the infall rate is
+The infall rate is described by two successive \added{decaying exponential components, which form the thick and thin disks.} The un-normalized form of the infall rate is
 \begin{multline}
@@
 \end{multline}
+where $\tau_1$ and $\tau_2(R_{\rm gal})$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall, $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function,
 \begin{equation*}
@@
         1, & x \ge 0 \\
-        0, & x < 0,
+        0, & x < 0.
     \end{cases}
 \end{equation*}
-where $\tau_1$ and $\tau_2(R_{\rm gal})$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall, $f_{2/1}$ is the ratio of the second infall amplitude to the first, and $H$ is the Heaviside step function.
 We vary $\tau_2$ exponentially with $R_{\rm gal}$ and adopt a scale radius $R_{\tau_2}=7\kpc$ to match the stellar age gradients in MW-like spirals observed by \citet{sanchez_spatially_2020}.
@@
 
-% Infall rate parameter selection
+The thick-to-thin disk density ratio is especially important for our GCE models as it controls the quantity of gas accreted during each infall epoch.
+Our fiducial value of $f_\Sigma(R_\odot)=0.12$ is on the low end of literature estimates, which range from $f_\Sigma(R_\odot)\sim0.06-0.6$ \citep[e.g.,][]{gilmore_new_1983,siegel_star_2002,juric_milky_2008,mackereth_age-metallicity_2017,fuhrmann_local_2017}.
+Previous two-infall studies have adopted a similarly broad range of values (e.g., $f_\Sigma(R_\odot)=0.18$ from \citealt{spitoni_apogee_2021}; $f_\Sigma(R_\odot)=0.4$ from \citealt{spitoni_remind_2024}).
+We therefore explore values up to $f_\Sigma(R_\odot)=0.5$ in our multi-zone models in Section \ref{sec:multizone-results}.
+
+\subsection{Infall Rate Parameter Selection}
+\label{sec:infall-parameters}
+
 Previous studies have adopted a wide range of parameter values for Equation \ref{eq:twoinfall-ifr}.
@@
 We also adopt $t_{\rm max}=4.2\Gyr$ (i.e., a lookback time of $9\Gyr$) so that our models are compatible with the median stellar age of the thick disk of $9.14\pm0.05\Gyr$ \citep{pinsonneault_apokasc-3_2025}.
-\added{This value of $t_{\rm max}$ is sub-optimal for models with \yZ{2}, producing a poorer agreement with the APOGEE data in [O/Fe]--[Fe/H] space, so we also run models with $t_{\rm max}=3.2\Gyr$ (see Table \ref{tab:models}.) This change has only a small effect on the [Fe/H] and [O/Fe] abundance distributions.} \citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.
+\added{This value of $t_{\rm max}$ is sub-optimal for models with \yZ{2}, producing a poorer agreement with the APOGEE data in [O/Fe]--[Fe/H] space, so we also run models with $t_{\rm max}=3.2\Gyr$ (see Table \ref{tab:models}).} \citet{spitoni_galactic_2019} discuss the effect of these parameters on the GCE model predictions in detail.
 
@@
 Figure \ref{fig:sfh} plots the star formation history for several different zones from our fiducial model with $y/Z_\odot=1$.
-In the inner Galaxy, the infall rate $\dot\Sigma_{\rm in}$ is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
+In the inner Galaxy, the infall rate is similar at the start of the first and second infall epochs, and the star formation rate peaks at $t\approx7\,{\rm Gyr}$.
 In the outer Galaxy, the infall rate at $t_{\rm max}$ is significantly higher than at $t=0$, and the star formation rate is highest at the present day.
-The star formation efficiency timescale $\tau_\star$ spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a present-day value of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
+The \added{SFE} timescale spikes near $t=0$ and $t_{\rm max}$, but otherwise increases throughout the model's duration, reaching a present-day value of $\tau_\star\approx2\,{\rm Gyr}$ in the inner disk and $\tau_\star\approx 9\,{\rm Gyr}$ in the outer disk.
 
-The thick-to-thin disk density ratio is especially important for our GCE models as it controls the quantity of gas accreted during each infall epoch.
-Our fiducial value of $f_\Sigma(R_\odot)=0.12$ is on the low end of literature estimates, which range from $f_\Sigma(R_\odot)\sim0.06-0.6$ \citep[e.g.,][]{gilmore_new_1983,siegel_star_2002,juric_milky_2008,mackereth_age-metallicity_2017,fuhrmann_local_2017}.
-Previous two-infall studies have adopted a similarly broad range of values (e.g., $f_\Sigma(R_\odot)=0.18$ from \citealt{spitoni_apogee_2021}; $f_\Sigma(R_\odot)=0.4$ from \citealt{spitoni_remind_2024}).
-We therefore explore values up to $f_\Sigma(R_\odot)=0.5$ in our multi-zone models in Section \ref{sec:multizone-results}.
+\subsection{Infalling Gas Metallicity}
+\label{sec:cgm-enrichment}
 
 In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$).
-However, previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,johnson_milky_2025,spitoni_remind_2024}.
+However, previous GCE studies suggest that some level of enrichment of the infalling gas can improve agreement with observations \citep[e.g.,][]{palla_chemical_2020,spitoni_remind_2024,johnson_milky_2025}.
 The circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, possibly from contributions from Galactic outflows, gas stripped from dwarf galaxies, or from SNe in the halo.
-The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, recent observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
+The Milky Way's CGM is diffuse, multiphase, and inhomogeneous, making it difficult to study \citep[e.g.,][]{tumlinson_circumgalactic_2017,mathur_probing_2022}; still, observations have confirmed the existence of metals at non-Solar abundance ratios in the CGM \citep[e.g.,][]{das_discovery_2019,das_hot_2021,gupta_supervirial_2021}.
 We investigate models where the infalling gas is pre-enriched to a metallicity
@@
 \citet{spitoni_effect_2015} explored the effect of migration speeds of order $\sim1\,{\rm km}{\rm s}^{-1}$ on the metallicity distribution of the Solar neighborhood.
-Our implementation, based on the diffusion method of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
+Our implementation, based on the \added{functional form} of \citet{frankel_measuring_2018}, allows stellar populations to migrate between zones during each timestep, which allows us to explore the effects of radial migration over the entire disk.
 \citet{palla_mgfe_2022} compared the \citet{spitoni_effect_2015} prescription to that of \citet{frankel_measuring_2018} and found a similar effect on stellar abundance distributions.
@@
 
-We run 11 multi-zone models at three different yield scales.
+We run \added{12} multi-zone models at three different yield scales.
 For our \yZ{1} and \yZ{2} yield scales, we vary the SN Ia DTD, the migration strength $\sigma_{\rm RM8}$, the thick-to-thin disk mass ratio $f_\Sigma(R_\odot)$, and the enrichment of the infalling gas ${\rm [X/H]}_{\rm CGM}$.
@@
     \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}), each of which feature a major dilution event 9 Gyr ago.
-    % The dark gray (light gray) shaded region plots the 68\textsuperscript{th} (95\textsuperscript{th}) percentile of APOGEE abundances in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$) with NN ages from \citet{leung_variational_2023}.
-The black line (black points) plots the median (mode) of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.
 \added{The 2-D histograms show the APOGEE stellar age--abundance distributions in the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $|z|<0.5\kpc$), adopting the \citet{leung_variational_2023} ages.
-The black curve (points) plots the rolling median (binned mode) of the abundance data as a function of age, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
-    The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
+The black curve (points) plots the rolling median (binned mode) of the abundance data as a function of age, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.} The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.}
     \label{fig:yield-outflow}
@@
 
-Figure \ref{fig:yield-outflow} shows the \added{APOGEE age--abundance distributions in the Solar annulus, as well as the binned mode and rolling median abundance as a function of age}, using the NN ages from \citet{leung_variational_2023}.
+Figure \ref{fig:yield-outflow} shows the \added{APOGEE age--abundance relations in the Solar annulus}, using the NN ages from \citet{leung_variational_2023}.
 \added{While the age--abundance distributions are clumpy in places (see Section \ref{sec:amr}), we caution that the APOGEE selection function can affect the stellar age distribution \citep[see][]{imig_galactic_2025}.} As shown by \citet{johnson_milky_2025}, the peak of the MDF is less susceptible to modification by radial migration, making it a more reliable proxy for ISM chemistry at a given lookback time than the mean or median.
@@
 The models are in broad agreement with each other and with the data at lookback times of $\lesssim5\Gyr$.
-At ages of $\sim5-8\Gyr$, the models underpredict the metallicities of the observed stars by up to half an order of magnitude, a natural consequence of the dilution associated with the second infall event.
+At ages of $\sim5-8\Gyr$, the models underpredict the \added{APOGEE} metallicities by up to half an order of magnitude, a natural consequence of the dilution associated with the second infall event.
 This discrepancy is modestly reduced in the higher $y/Z_\odot$ models, which re-enrich more rapidly.
@@
 As a result, the stars that make up the present-day Solar neighborhood are drawn from a wider range of birth $R_{\rm gal}$, producing a broader abundance distribution at fixed age.
-Even though this prescription is extreme compared to the estimates of \citet{frankel_measuring_2018}, for example, the model still significantly under-predicts the \added{median} metallicity of $\sim5-9\,{\rm Gyr}$ old stars.
+Even though this prescription is extreme compared to \added{our fiducial model or the measurement of} \citet{frankel_measuring_2018}, the model still significantly under-predicts the \added{median} metallicity of $\sim5-9\,{\rm Gyr}$ old stars.
 
@@
 However, agreement with the observed age--[O/Fe] relation is poor.
-The model predicts a much flatter trend than observed, under-predicting [O/Fe] by $\sim0.1$ dex in the $\sim5-9\Gyr$ age range.
+The model predicts a much flatter trend than observed, under-predicting \added{the median} [O/Fe] by $\sim0.1$ dex in the $\sim5-9\Gyr$ age range.
 
-Finally, we investigate model {\tt yZ1-preenrich}, where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk.
+Finally, we investigate model {\tt yZ1-preenrich}, where the infalling gas is enriched before accreting onto the disk.
 Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population.
@@
 
-The oldest age bin in Figure \ref{fig:mdf-evolution} shows distinct behavior in both the models and data.
-The $8-10\Gyr$ age bin spans both the tail end of the thick disk phase and the beginning of the thin disk, so the MDF is much broader than in other age bins.
-In the models, the main, metal-poor peak consists of $8-9\Gyr$ old stars (post-dilution), and the extended high-[Fe/H] tail consists of $>9\Gyr$ old stars (pre-dilution).
-Intriguingly, the APOGEE MDF in that age bin is also very broad and is bimodal in the two inner-most radial bins, peaking at $\mathFeH\approx-0.3$ and $+0.3$.
-While the data and the models show qualitatively similar behavior, they actually represent different populations.
-In the data, the metal-rich peak are all low-$\alpha$ stars, while the metal-poor peak is the locus of the high-$\alpha$ sequence---a reversal of the model predictions.
-
 \subsection{The [O/Fe] Distribution}
@@
 The curves plot the ISM abundance at the Solar annulus over time, and the alternating black and white segments mark time intervals of 1~Gyr.
-The model output has been re-sampled to match the APOGEE stellar $|z|$ distribution.
-    Stars in \added{both} panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$.}
+\added{The gray curves in the marginal panels plot the APOGEE stellar abundance distributions.}
+    Stars in \added{both} panels are restricted to the region defined by $7\leq R_{\rm gal}< 9\kpc$ and $|z|<2\kpc$, \added{and the model output has been re-sampled to match the APOGEE stellar $|z|$ distribution.}}
     \label{fig:ofe-feh-density}
@@
 
-Additionally, the shape of the low-$\alpha$ sequence predicted by the models (a concave-down ``comma'') is different from the data (a concave-up ``swoosh'').
-This is a subtle distinction, on the $\sim0.05\dex$ level in [O/Fe].
-We have not accounted for the APOGEE selection function in our models, but there is no evident reason for observational effects to produce this difference in morphology.
-This problem is not unique to the two-infall scenario: it results from the evolution toward the lower right of the [O/Fe]--[Fe/H] plane and is typical of other models \citep[e.g.,][]{minchev_chemodynamical_2013,johnson_stellar_2021,prantzos_origin_2023}.
-The two-infall scenario is otherwise fairly successful at reproducing the local stellar distribution in [O/Fe]--[Fe/H] space.
-
 \begin{figure*}
@@
 
-Next, we attempt to mitigate the intermediate peak through several parameter choices.
 Figure \ref{fig:ofe-distribution-parameters} compares [O/Fe] distributions from across the Galactic disk predicted by models with \yZ{2}.
@@
 
-First, we substitute our fiducial SN Ia DTD with a simple power-law (Equation \ref{eq:powerlaw-dtd}; {\tt yZ2-powerlaw}),
+\added{We attempt to mitigate the intermediate peak through several parameter choices.} First, we substitute our fiducial SN Ia DTD with a simple power-law (Equation \ref{eq:powerlaw-dtd}; {\tt yZ2-powerlaw}),
 which reduces the median SN Ia delay time from $\sim2\,{\rm Gyr}$ to $\sim0.5\,{\rm Gyr}$.
 As shown in column (b), this has the intended effect on the low-$\alpha$ sequence, but it also entirely eliminates the high-$\alpha$ peak.
-\citet{dubay_galactic_2024} discuss in detail why such a DTD is disfavored by Milky Way stellar abundances for several different SFHs including for the two-infall scenario.
+\citet{dubay_galactic_2024} discuss in detail why such a DTD is disfavored by Milky Way stellar abundances for several different SFHs, including for the two-infall scenario.
+Next, in model {\tt yZ2-diskratio} (column (c)) we increase the local thick-to-thin disk surface density ratio by a factor of 4, to $f_\Sigma(R_\odot)=0.5$.
+The result is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the other models.
+Finally, in model {\tt yZ2-preenrich} (column (d)) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
+This model \added{predicts} similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
+We assume that the infalling gas has $\mathOFe_{\rm CGM}=0$ at all times; an alternate model with $\mathOFe_{\rm CGM}=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
 
-Next, in model {\tt yZ2-diskratio} (column (c)) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$.
-This value means that 1 in 3 stars in the Solar annulus belong to the thick disk, which is on the high end of estimates (see Section \ref{sec:sfh}).
-The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the other models.
-
-Finally, in model {\tt yZ2-preenrich} (column (d)) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times.
-This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case.
-We assume that the infalling gas has $\mathOFe_{\rm CGM}=0$ at all times; an alternate model with $\mathOFe_{\rm CGM}=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations.
 In summary, either an enhanced disk mass ratio or pre-enriched infall can improve agreement with the observed thin disk abundances for the \yZ{2} case.
@@
     \includegraphics[width=\linewidth]{\figpath{ofe_feh_best.pdf}}
-    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$.
+    \caption{Stellar abundance distributions across the disk predicted by \added{the {\tt yZ2-best} model (see Table \ref{tab:models})}.
 Each panel presents a random mass-weighted sample of \num{10000} stellar populations color-coded by age.
@@
 This model is generally successful at reproducing the observed abundance distributions, especially in the inner Galaxy and close to the midplane.
-However, the predicted high-$\alpha$ sequence has a significant presence even in the outer Galaxy---likely a consequence of the stronger migration prescription and higher thick-to-thin disk ratio \added{than in the fiducial model}.
+\added{However, due to the stronger migration prescription and higher thick-to-thin disk ratio, implemented to solve the dilution problem in the Solar neighborhood, the high-$\alpha$ sequence is too prominent in the outer Galaxy}.
 In general, the predicted distributions do not align with the data as well at large midplane distances ($1\leq|z|<2\kpc$), but this may reflect inaccuracies in our prescription for vertical heating (see Section \ref{sec:migration}).
-
-The {\tt yZ2-best} model makes two notable predictions about the age--abundance distributions.
-First, there is a population of $\sim8-9\Gyr$ old stars at sub-Solar [O/Fe], especially at $|z|\ge0.5\kpc$, formed immediately after the second infall during a period of rapid chemical evolution.
-These stars form a small percentage of the overall distribution \citep[see also Figure 11 from][]{spitoni_remind_2024} but they occupy a unique portion of the abundance space.
-Second, the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
-The following section explores this second prediction in greater detail.
 
@@
 
-The two-infall scenario makes a fundamental prediction about the local stellar age distribution: the most metal-rich stars born in-situ in any region of the Galaxy should come from the metal-rich tail of the first infall sequence, and should therefore be older than all of the thin disk stars.
-As noted in the previous section, this prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.
+The two-infall scenario makes a fundamental prediction about the local stellar age distribution: \added{the stars born at the tail end of the thick and thin disk epochs are adjacent to each other in abundance space, meaning the two-infall scenario predicts a bimodal age distribution for metal-rich stars.
+This} prediction is apparent in any of the panels in Figure \ref{fig:ofe-feh-best}, especially where $|z|<0.5\kpc$.
 The top row of panels in Figure \ref{fig:lmr-ages} presents the median stellar age as a function of [O/Fe] and [Fe/H] predicted by the {\tt yZ1-best} and {\tt yZ2-best} models (see Table \ref{tab:models}) and observed in APOGEE using the \citet{leung_variational_2023} NN ages.
@@
 In both models, there is a sharp divide in the median stellar age when moving from the thick disk ($\tau\ge9\Gyr$) to the thin disk ($\tau\lesssim5\Gyr$).
-% The \yZ{2} model also predicts that the stars with the lowest [O/Fe] should be $\sim8-9\Gyr$ old, while these are some of the youngest stars in APOGEE.
-The latter issue can be mitigated by adjusting the parameters of the first infall, as discussed in the previous Section, but the former is not solved so easily.
 
@@
 We have explored a wide range of parameter space, but our investigation is not intended to be exhaustive.
-In this section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.
+In this section, we discuss \added{further extensions to the two-infall model as well as other recent evidence of the Galaxy's evolution.}
 
@@
 \citet{nissen_high-precision_2020} argued that the existence of multiple sequences is evidence for the two-infall scenario.
-However, \citet{plotnikova_chemical_2024} showed that multiple sequences can arise due to selection effects, and the APOGEE selection function in particular affects the observed stellar age distribution \citep{imig_galactic_2025}.
+However, \citet{plotnikova_chemical_2024} showed that this pattern can arise due to selection effects, and the APOGEE selection function in particular affects the observed stellar age distribution \citep{imig_galactic_2025}.
 Furthermore, \citet{chen_recent_2025} demonstrated that multiple sequences in the local AMR can arise naturally due to radial migration, even in the absence of major accretion or starburst events.
-% Anders+ use APOGEE clump stars. Their split is 5-6 Gyr ago
-% Xiang & Rix use Gaia subgiants. Their split is 8 Gyr ago
-% Sahlholdt+ use GALAH turnoff stars. Their split is 7-9 Gyr ago.
 
@@
 
-Even if these AMR sequences are real, the two-infall scenario does not offer a natural explanation.
+Even if these patterns in the AMR are real, the two-infall scenario does not offer a natural explanation.
 The difference in metallicity between the sequences in our sample is $\sim0.2\dex$, smaller than the dilution predicted by any of our models.
@@
 Interestingly, the transition does align with the first pericentric passage of the Sagittarius dwarf galaxy, which has been linked to periods of enhanced star formation in the disk \citep{ruiz-lara_recurrent_2020}.
-It is possible that the Milky Way has seen multiple episodes of star formation without experiencing the dilution associated with the two-infall scenario.}
+It is possible that the Milky Way has seen multiple episodes of high star formation without experiencing the dilution associated with the two-infall scenario.}
 
@@
 Radial gas flows are a potential alternative to the outflow prescription that we use in this paper.
-Within the two-infall paradigm, \citet{spitoni_effects_2011} found that inward flow velocities of a $\sim$ few $\kms$ can steepen the predicted radial metallicity gradient to match observations.
+Within the two-infall paradigm, \citet{spitoni_effects_2011} found that inward flow velocities of a few $\kms$ can steepen the predicted radial metallicity gradient to match observations.
 Similarly, \citet{palla_chemical_2020,palla_mapping_2024} used an inward flow with a speed of $\sim1\kms$ to reproduce the observed radial metallicity profile in the absence of Galactic outflows.
-\citet{johnson_constraints_2025} considered several possible scenarios for the processes that drive radial gas flows.
-Their findings support these previous arguments that radial gas flows can help to regulate the overall metal abundance and radial gradient.
+\added{Recently,} \citet{johnson_constraints_2025} considered several possible scenarios for the processes that drive radial gas flows \added{and confirmed} that radial gas flows can help to regulate the overall metal abundance and radial gradient.
 
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\onecolumn]{\figpath{sfe_hiatus.pdf}}
-%     \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst.
-The blue dashed curve represents the fiducial model that has an exponentially declining infall rate with timescale $\tau_{\rm in}=15\Gyr$, and constant star formation efficiency timescale $\tau_\star=2\,{\rm Gyr}$.
-The red solid curve plots the output of a model which has an enhancement of $\tau_\star$ by a factor of 10 for 200 Myr starting at $t=1.4\,{\rm Gyr}$.
-Both models assume the \yZ{2} yield set, with $y_{\rm Fe}^{\rm Ia}$ reduced by 20\% to better match the model endpoint with the data, and $\eta=1.4$.
-The grayscale histogram is the number density of APOGEE stars in the Solar annulus ($7\leq R_{\rm gal}< 9\kpc$, $|z|<2\kpc$) in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
-%     \label{fig:onezone-sfe-hiatus}
-% \end{figure}
-
-% The two-infall scenario falls into the broader category of GCE models that reproduce the $\alpha$-bimodality by halting or severely limiting star formation temporarily.
-\added{In our models,} this phase of low star formation lasts for a few Gyr between the $e$-folding timescale of the first infall and the onset of the second.
-However, as we have shown in Section \ref{sec:age-abundance}, the resulting dilution of the ISM is in tension with the observed stellar AMR.
-
 \added{The two-infall scenario produces an $\alpha$-bimodality due to a few Gyr long quiescent period between the two major accretion epochs.
@@
 In this scenario, the newly-formed bar funnels gas into the galaxy's central black hole, prompting a burst of AGN activity which suppresses star formation.
-% Unlike our two-infall model, where the gas mass suddenly grows by a factor of $\sim5$ during the 1 Gyr following the second infall, the mass of their galaxy grows slowly during the quiescent period, indicating a dearth of major accretion events.
-\todo{Mention James' recent retrograde mergers paper.}
 \added{Alternatively, \citet{johnson_thats_2025} showed that a retrograde merger can induce much of the ISM to sink to the center of the Galaxy, lowering the local gas surface density and thereby creating an $\alpha$-bimodality.
@@
 Both of these scenarios explain the observed \aFe distribution without invoking significant dilution and re-enrichment of the ISM.}
-
-% While our semi-analytic model does not include a Galactic bar, we can induce a star formation hiatus by artificially boosting the SFE timescale $\tau_\star$ for a period of time.
-Figure \ref{fig:onezone-sfe-hiatus} illustrates the effect of this efficiency-driven hiatus in a one-zone GCE model with an exponentially declining infall rate ($\tau_{\rm in}=15\Gyr$).
-During the quiescent period, the [O/Fe] ratio slowly declines due to the delayed contribution of Fe from SNe Ia.
-Meanwhile, the gas mass continues to increase through accretion even as star formation is suppressed.
-When $\tau_\star$ is lowered at the end of the quiescent period, it sparks a moderate star formation burst which causes stellar abundances to ``pile up'' at similar [O/Fe] values.
-The trough between the high- and low-$\alpha$ sequences results from the star formation returning to pre-quiescence behavior.
-The onset time of the SFE hiatus controls the position of the high-$\alpha$ sequence\textemdash a later onset places the peak at lower [O/Fe]\textemdash while the duration and enhancement factor control the size of the high-$\alpha$ peak.
-
-% The parameters of the SFE hiatus in Figure \ref{fig:onezone-sfe-hiatus} were chosen to match the APOGEE stellar [O/Fe] distribution as closely as possible.
-As such, we start the hiatus at $t=1.4\Gyr$ to match the high-$\alpha$ locus, even though this is $\sim3\Gyr$ before the median age of the thick disk measured by \citet{pinsonneault_apokasc-3_2025}.
-This hiatus model illustrates an alternative scenario for reproducing the $\alpha$-bimodality, but a full multi-zone treatment is beyond the scope of this work.
 
@@
 The figures, tables, and models in this paper are reproducible.
-The git repository associated to this study is publicly available at \url{\GitHubURL}, and the release {\tt v1.0.0} allows anyone to re-build the entire manuscript.
+The git repository associated to this study is publicly available at \url{\GitHubURL}, and the release {\tt v1.1.0} allows anyone to re-build the entire manuscript.
 The multi-zone model outputs used to produce the figures in this work are stored at \url{https://doi.org/10.5281/zenodo.16649938}.
